### 2017-06-02 paper/distraction/main.tex
added-tex-formula

% This is based on the LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
% See http://www.springer.com/computer/lncs/lncs+authors?SGWID=0-40209-0-0-0
% for the full guidelines.
%
\documentclass{llncs}
\usepackage{graphicx}
% \usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

\renewcommand{\figurename}{Fig.{}}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% Use package Listing to add code in our Manuscript
\usepackage{listings}

% Added for the sub-pictures
\usepackage{subcaption}

% Added for the multi-column 
\usepackage[british]{babel}
\usepackage{hhline}
\usepackage{multirow}
\usepackage[figurename=Fig]{caption}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}
\renewcommand{\thesubfigure}{\Alph{subfigure}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in
% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}
\renewcommand{\thesubfigure}{\Alph{subfigure}}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\usepackage{epstopdf}
\AppendGraphicsExtensions{.tif}

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{ Vesicle traffic system and constraints.} % Please use 
}
\newline
\\
\end{flushleft}

\section{Vesiular traffic system}
The process of vesicle traffic is a linear process involving:
\begin{enumerate}
\item Sorting of cargo molecules from the source compartment for packaging
into the vesicle.
\item Budding of the vesicle.
\item Tethering of the vesicle to the target compartment.
\item Vesicle fusion.
\end{enumerate}

We are going to focus on two of them Buddying of the vesicle from the source and fusion of the vesicle to the target and think whole mechanism as Fig1. Molecules such as Rabs, Arf GTPases, and Sec/Munc proteins on vesicles and compartments can activate or inhibit SNAREs.

\begin{figure}[!h]
\caption{\textbf{Vesicle budding and fusion}}
\includegraphics[width=0.6\textwidth]{2.jpg}
\label{fig1}
\end{figure}
In the abstract model of vesicular traffic system compartments are the nodes, and vesicles are the directed edges, of a transport graph.

\subsection{The model}
The following assumptions reasonably capture the important aspects of the Rothman-Schekman-Sudhof (RSS) model of vesicle traffic.

\begin{enumerate}
\item[1.] A cell is a set of compartments exchanging vesicles.
\item[2.] Compartments are neither created nor destroyed.
\item[3.] Each compartment is in steady state, gain and loss balance.
\item[4.] Molecules are neither created nor destroyed. 
\item[5.] Molecules move via vesicles of uniform size.
\item[6.] Identical vesicles have identical target compartments.
\item[7.] Fusion of vesicles to compartments is driven by specific SNARE pairing.
\item[8.] The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
\item[9.] An active SNARE pair is necessary and sufficient for fusion.
\end{enumerate}

Self loops are not allowed.

\subsection{Biological model overview}
Let us assume there are M molecular types in the system. These include SNARE proteins, but also include their regulators, and structural molecules such as lipids. Each compartment is a node, specified by an M-length vector giving the amount of various molecular types it contains. Each vesicle is an edge connecting one compartment to another, specified by an M-length vector giving the flux of each molecular type. For this graph to be in steady state, the total incoming and outgoing flux of each molecular type must balance at every node (Fig 2). We assume throughout that self-edges are not permitted (biologically, this could be justified by efficiency considerations).

\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{5.png}
\caption{{\bf The vesicle traffic graph in steady state.} Nodes (large circles) are compartments; vesicles are associated with directed edges. The binary labels represent the presence/absence of four molecular types in this example. The actual amounts of these molecules on each compartment, and actual fluxes along each vesicle edge, can be positive real numbers. By construction, the total incoming flux can be made to balance the total outgoing flux of each molecular type at every node. Note that no pair of vesicles has the identical composition, yet all molecular components move in closed cycles. This is related to the fact that this graph is 3-connected.}
\end{figure}

We next have to specify precisely how SNAREs prefer to pair with one-another, and how the activity of these molecules might be regulated by other molecules in the system. We assume M/2 Q-SNARE types and M/2 R-SNARE types. Fusion is defined by an $M\times M$ binary SNARE pairing matrix, where each non-zero entry states that the corresponding Q-SNARE and R-SNARE pair is fusion competent (Fig 2A,C). The rows/columns represent SNAREs on vesicles/compartments respectively. There are only non-zero entries for Q-R or R-Q pairs. We assume that, due to size and curvature differences, the behavior of molecules on vesicles can be distinct from their behavior on compartments; the matrix is therefore not necessarily symmetric. Rather than invoking further molecular types, we assume the most general situation in which each molecule can take on SNARE-based fusion roles as specified above, or additional regulatory roles. Non-SNARE molecules in this format are those that do not participate in fusion (have no corresponding non-zero entries in the SNARE pairing matrix) but do influence the activity of other SNAREs as described below. Molecules that are to be involved in both fusion and regulation could represent two real molecular types that are always co-localized. This representation is therefore without loss of generality.

We determine all possible topologies of steady-state vesicle traffic networks that are consistent with models of SNARE regulation.
\begin{figure}
\centering
  \includegraphics[width=0.85\textwidth]{1.png}
\caption{\textbf{SNARE pairing matrices and the resulting steady state vesicle traffic networks.} SNARE interactions generate the vesicle traffic network. (A,C) Examples of SNARE pairing matrices. Q0, Q1, etc. are Q-SNAREs, R0, R1, etc. are R-SNARES. Dark squares represent SNARE pairings that result in fusion. Each column represents a SNARE type on compartments (nodes), and each row represent a SNARE type on vesicles (edges). SNAREs can be active or inactive depending on the other molecules present on the same vesicle or compartment. If at least one active Q-SNARE type on one membrane interacts with at least one active R-SNARE type on the opposite membrane, compartment-vesicle fusions will occur. (B,D) Steady state vesicle traffic networks governed by SNARE pairings. Nodes (large circles) are compartments; vesicles (small circles) are associated with directed edges. As in Fig 2, we only show the presence or absence of each molecular type on each compartment or vesicle: the first half of the binary vector represents Q-SNAREs, and the second half represents R-SNAREs. The actual fluxes can be positive real numbers, values of which can always be found in order to keep the system in steady state. Active SNAREs are shown in red, inactive SNAREs in black. (A,B) The case of Table 1 row 2, where there is no regulation on compartments (all SNAREs are active) but there is Boolean regulation on vesicles (so only those SNAREs shown in red are active). The necessary and sufficient condition for this case is a 3-connected graph. (C,D) The case of Table 1 row 3, where SNAREs on compartments have Boolean regulation, and SNAREs on vesicles are regulated by SNARE-SNARE inhibition (i.e. if pairing-compatible SNAREs exist on the vesicle, they neutralize one another). The necessary and sufficient condition for this case is a 4-connected graph.}
   \label{fig2} 
\end{figure}

We study a hierarchy of models for varying degrees of regulation of SNARE activity (Table 1). In the simplest case, each SNARE is always considered to be constitutively active (no-regulation model). In the most complex case, the activity state of each SNARE could depend on the presence or absence (defined by a logical Boolean function) of all the other molecules on the corresponding vesicle or compartment (Boolean regulation model). Intermediate between these cases are those in which activity is regulated only on the compartment, or only on the vesicle. We also consider a special case, in which regulation on vesicles has a very restricted form. In this case, we assume that if a fusion-competent Q-R SNARE pair is present on a vesicle (i.e. pair with a non-zero entry in any part of the SNARE pairing matrix) then both molecules are rendered inactive. This is motivated by the fact that these two molecules are likely to zip together, and that NSF is not present on vesicles to unzip them. We refer to this version of regulation as SNARE-SNARE inhibition.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\def\arraystretch{1.6}
\caption{
{\bf SNARE regulation and graph connectedness.}}
  \begin{tabular}{|c|l|l|c|c|}
    \hline
  \multirow{2}{*}{\textbf{Sr.No}}  & \multirow{2}{*} {\bf{Regulation on compartment}} & \multirow{2}{*} {\bf{Regulation on vesicle}} & \multicolumn{2}{c|}{\textbf{Required graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{4-5}
    {} & {} & {} & \textbf{\textbf{Necessary}} & \textbf{Sufficient}\\
    %\hhline{~--}
    \hline
1. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
2. & None & Boolean function & 3-connected & 3-connected \\  \hline
3. & Boolean function & SNARE-SNARE inhibition & 4-connected & 4-connected \\ \hline
4. & None & SNARE-SNARE inhibition & No graph & No graph \\ \hline
5. & Boolean function & None & No graph & No graph \\ \hline
6. &  None & None & No graph & No graph \\ \hline
  \end{tabular}
\label{table1}
\end{table}

\section{Formula variables}
Basic notation for the formula we are trying to generate.
\begin{enumerate}
\item edge = e(i,j,q)
      There is an qth edge between node i and j.

\item dump = d(i,j,q)
       drop edge(i,j,q) from the graph.

\item presence node = n(i,k) 
	  kth molecule is present on the node i.

\item active\_node = a(i,k) 
      kth molecule is active on the node i.

\item presence\_edge = e(i,j,q,k)
      There is an qth edge between node i and j with kth molecule present.

\item active\_edge = b(i,j,q,k)
      There is an qth edge between node i and j with kth molecule active.

\item reachability = r(i,j,k,z)
      Node i and j are reachable with kth molecule present in z steps.

\item pairing matrix = p(k,k')
      Molecule k and k' are pairing molecules in the matrix.

\item Type of the Boolean function = sorts (takes k-1 arguments Bool and return Bool) 
\item Boolean function on nodes Function (fn\_{m},*sorts)

\item Boolean function on edge Function(fe\_{m},*sorts)

\end{enumerate}

\section{Regulation on nodes and edges}
Regulation of a model is based on the kind of the model under consideration. for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by SNARE-SNARE inhibition.

We have build constraints A0, A1 for these two regulations. \newline

A0: No regulation on nodes.
\[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]

A1: No regulation on edges.
\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]

A0: Boolean regulation on nodes. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]

A1: Boolean regulation on edges. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e(i,j,q,k')) \, \]

A1: SNARE-SNARE inhibition. Inhibition of the edges are driven by the pairing matrix.
\[ \bigwedge\limits_{i,j,i != j, q, k} (\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'}) \supset \neg b(i,j,q,k)) \, \]

\[ \bigwedge\limits_{i,j,i != j, q, k} \neg [(\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] \supset b(i,j,q,k)) \, \]

\section{Basic constraints on the edges and nodes}
The edge labels are subset of the node label of source and target compartment. \newline

C0: The edge labels are subset of the node label of source compartment.

\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset a_{i,k} \, \]

C1: The edge labels are subset of the node label of target compartment.

\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset a_{j,k} \, \]  
%C1 =  e_ijk -> aik and e_ijk -> ajk

C2: Self edges are not allowed.

\[  \bigwedge\limits_{i,q} \neg e_{i,i,q} \, \]

C4: Condition on p\_kk'. Diagonal blocks should be all 0's.

\[ \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y) \, \]

C5: Activity on the node. A molecule should be present to be active on a node.  
\[ \bigwedge\limits_{i,k} a_{i,k} \supset n_{j,k} \, \]

% - F0: b(i,j,k) $\supset$ e(i,j,k)

\section{Main constraints}
Main constraints to be followed. \newline

F0:  An edge has to have one present molecule. F0 looks redundant.

\[ \bigwedge\limits_{i,j,q} \bigvee_k e_{i,j,q,k} \supset e_{i,j,q} \, \]

F1: If molecule is active on an edge then it should be present on the edge.

\[ \bigwedge\limits_{i,j,q,k} a_{i,j,q,k} \supset e_{i,j,q,k}\, \]

\section{Steady state specification}
Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.

\subsection{Reachability definition and stability condition}
If molecule is active on an edge then it should be present on the edge. \newline

F3: stability condition. Source node is reachable by target node with that molecule present in p steps.

% I have implemented: Changed the implementation in code too.
%\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]

% Update: Better 
\[ \bigwedge\limits_{i,j,k} (\bigvee_{q} e_{i,j,q,k}) \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]

F2: Reachability definition.
\[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \supset (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]

\section{ Fusion rule Formula}

Fusion rules consist of two different mechanisms.

\begin{enumerate}
\item  A \textbf{SNARE pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate SNARE activity based on the presence/absence of other molecules on the corresponding node or edge.
\end{enumerate}

F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active, and have a non-zero entry in the pairing matrix.

\[ \bigwedge\limits_{i,j,q} e_{i,j,q} \supset \bigvee_{k,k^{\prime}} (b_{i,j,q,k} \land a_{j,k^{\prime}} \land p_{k,k^{\prime}}) \, \]

F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.

\[ \bigwedge\limits_{i,j,k} b_{i,j,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]

\section{Connectivity}
To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph. We can go down or up using -C \_ option.  \newline

D0: Only present edges can be dropped.
\[ \bigwedge\limits_{i,j,q} d_{i,j,q} \supset e_{i,j,q}  \]

D1,D2: We are dropping c edges from the graph. exactly c are dropped.
\[ \sum_{i,j,q} d_{i,j,q} == c \]

D3:  Graph becomes disconnected. Ensure that there is no path between some nodes i,j in the underlying undirected graph. Different reachability.
\[ \bigwedge\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})]  \]

D4: New reachability definition for grph connectedness: dReachable. Node i,j are reachable either if there is a direct edge and its not dropped. 
Or there is an node i' such that, there is a direct edge between i,i' which is not dropped and i' and j is dReachable.

\[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \supset r^{\prime}(i,j)  \]

\end{document}

### 2017-06-02 paper/main.tex
added-tex-formula

--- 2017-06-02 paper/distraction/main.tex
@@
 \end{flushleft}
-
-\section{Vesiular traffic system}
-The process of vesicle traffic is a linear process involving:
-\begin{enumerate}
-\item Sorting of cargo molecules from the source compartment for packaging
-into the vesicle.
-\item Budding of the vesicle.
-\item Tethering of the vesicle to the target compartment.
-\item Vesicle fusion.
-\end{enumerate}
-
-We are going to focus on two of them Buddying of the vesicle from the source and fusion of the vesicle to the target and think whole mechanism as Fig1.
-Molecules such as Rabs, Arf GTPases, and Sec/Munc proteins on vesicles and compartments can activate or inhibit SNAREs.
-
-\begin{figure}[!h]
-\caption{\textbf{Vesicle budding and fusion}}
-\includegraphics[width=0.6\textwidth]{2.jpg}
-\label{fig1}
-\end{figure}
-In the abstract model of vesicular traffic system compartments are the nodes, and vesicles are the directed edges, of a transport graph.
-
-\subsection{The model}
-The following assumptions reasonably capture the important aspects of the Rothman-Schekman-Sudhof (RSS) model of vesicle traffic.
-
-\begin{enumerate}
-\item[1.] A cell is a set of compartments exchanging vesicles.
-\item[2.] Compartments are neither created nor destroyed.
-\item[3.] Each compartment is in steady state, gain and loss balance.
-\item[4.] Molecules are neither created nor destroyed. 
-\item[5.] Molecules move via vesicles of uniform size.
-\item[6.] Identical vesicles have identical target compartments.
-\item[7.] Fusion of vesicles to compartments is driven by specific SNARE pairing.
-\item[8.] The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
-\item[9.] An active SNARE pair is necessary and sufficient for fusion.
-\end{enumerate}
-
-Self loops are not allowed.
-
-\subsection{Biological model overview}
-Let us assume there are M molecular types in the system.
-These include SNARE proteins, but also include their regulators, and structural molecules such as lipids.
-Each compartment is a node, specified by an M-length vector giving the amount of various molecular types it contains.
-Each vesicle is an edge connecting one compartment to another, specified by an M-length vector giving the flux of each molecular type.
-For this graph to be in steady state, the total incoming and outgoing flux of each molecular type must balance at every node (Fig 2).
-We assume throughout that self-edges are not permitted (biologically, this could be justified by efficiency considerations).
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.75\textwidth]{5.png}
-\caption{{\bf The vesicle traffic graph in steady state.} Nodes (large circles) are compartments; vesicles are associated with directed edges.
-The binary labels represent the presence/absence of four molecular types in this example.
-The actual amounts of these molecules on each compartment, and actual fluxes along each vesicle edge, can be positive real numbers.
-By construction, the total incoming flux can be made to balance the total outgoing flux of each molecular type at every node.
-Note that no pair of vesicles has the identical composition, yet all molecular components move in closed cycles.
-This is related to the fact that this graph is 3-connected.}
-\end{figure}
-
-We next have to specify precisely how SNAREs prefer to pair with one-another, and how the activity of these molecules might be regulated by other molecules in the system.
-We assume M/2 Q-SNARE types and M/2 R-SNARE types.
-Fusion is defined by an $M\times M$ binary SNARE pairing matrix, where each non-zero entry states that the corresponding Q-SNARE and R-SNARE pair is fusion competent (Fig 2A,C).
-The rows/columns represent SNAREs on vesicles/compartments respectively.
-There are only non-zero entries for Q-R or R-Q pairs.
-We assume that, due to size and curvature differences, the behavior of molecules on vesicles can be distinct from their behavior on compartments; the matrix is therefore not necessarily symmetric.
-Rather than invoking further molecular types, we assume the most general situation in which each molecule can take on SNARE-based fusion roles as specified above, or additional regulatory roles.
-Non-SNARE molecules in this format are those that do not participate in fusion (have no corresponding non-zero entries in the SNARE pairing matrix) but do influence the activity of other SNAREs as described below.
-Molecules that are to be involved in both fusion and regulation could represent two real molecular types that are always co-localized.
-This representation is therefore without loss of generality.
-
-We determine all possible topologies of steady-state vesicle traffic networks that are consistent with models of SNARE regulation.
-\begin{figure}
-\centering
-  \includegraphics[width=0.85\textwidth]{1.png}
-\caption{\textbf{SNARE pairing matrices and the resulting steady state vesicle traffic networks.} SNARE interactions generate the vesicle traffic network.
-(A,C) Examples of SNARE pairing matrices.
-Q0, Q1, etc.
-are Q-SNAREs, R0, R1, etc.
-are R-SNARES.
-Dark squares represent SNARE pairings that result in fusion.
-Each column represents a SNARE type on compartments (nodes), and each row represent a SNARE type on vesicles (edges).
-SNAREs can be active or inactive depending on the other molecules present on the same vesicle or compartment.
-If at least one active Q-SNARE type on one membrane interacts with at least one active R-SNARE type on the opposite membrane, compartment-vesicle fusions will occur.
-(B,D) Steady state vesicle traffic networks governed by SNARE pairings.
-Nodes (large circles) are compartments; vesicles (small circles) are associated with directed edges.
-As in Fig 2, we only show the presence or absence of each molecular type on each compartment or vesicle: the first half of the binary vector represents Q-SNAREs, and the second half represents R-SNAREs.
-The actual fluxes can be positive real numbers, values of which can always be found in order to keep the system in steady state.
-Active SNAREs are shown in red, inactive SNAREs in black.
-(A,B) The case of Table 1 row 2, where there is no regulation on compartments (all SNAREs are active) but there is Boolean regulation on vesicles (so only those SNAREs shown in red are active).
-The necessary and sufficient condition for this case is a 3-connected graph.
-(C,D) The case of Table 1 row 3, where SNAREs on compartments have Boolean regulation, and SNAREs on vesicles are regulated by SNARE-SNARE inhibition (i.e.
-if pairing-compatible SNAREs exist on the vesicle, they neutralize one another).
-The necessary and sufficient condition for this case is a 4-connected graph.}
-   \label{fig2} 
-\end{figure}
-
-We study a hierarchy of models for varying degrees of regulation of SNARE activity (Table 1).
-In the simplest case, each SNARE is always considered to be constitutively active (no-regulation model).
-In the most complex case, the activity state of each SNARE could depend on the presence or absence (defined by a logical Boolean function) of all the other molecules on the corresponding vesicle or compartment (Boolean regulation model).
-Intermediate between these cases are those in which activity is regulated only on the compartment, or only on the vesicle.
-We also consider a special case, in which regulation on vesicles has a very restricted form.
-In this case, we assume that if a fusion-competent Q-R SNARE pair is present on a vesicle (i.e.
-pair with a non-zero entry in any part of the SNARE pairing matrix) then both molecules are rendered inactive.
-This is motivated by the fact that these two molecules are likely to zip together, and that NSF is not present on vesicles to unzip them.
-We refer to this version of regulation as SNARE-SNARE inhibition.
-
-\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\def\arraystretch{1.6}
-\caption{
-{\bf SNARE regulation and graph connectedness.}}
-  \begin{tabular}{|c|l|l|c|c|}
-    \hline
-  \multirow{2}{*}{\textbf{Sr.No}}  & \multirow{2}{*} {\bf{Regulation on compartment}} & \multirow{2}{*} {\bf{Regulation on vesicle}} & \multicolumn{2}{c|}{\textbf{Required graph connectivity}}  \\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{4-5}
-    {} & {} & {} & \textbf{\textbf{Necessary}} & \textbf{Sufficient}\\
-    %\hhline{~--}
-    \hline
-1. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
-2. & None & Boolean function & 3-connected & 3-connected \\  \hline
-3. & Boolean function & SNARE-SNARE inhibition & 4-connected & 4-connected \\ \hline
-4. & None & SNARE-SNARE inhibition & No graph & No graph \\ \hline
-5. & Boolean function & None & No graph & No graph \\ \hline
-6. &  None & None & No graph & No graph \\ \hline
-  \end{tabular}
-\label{table1}
-\end{table}
 

### 2017-06-02 biology.py

@@ -250,6 +250,7 @@ for i in range(N):
         for q in range(Q):
             rhs = False
             for k in range(M):
+                # Change the presence to activity from the last change on 1st June.
                 rhs = Or( presence_edge[i][j][q][k], rhs )
             F0 = And (Implies(rhs, edge[i][j][q]),F0)
 #print F0
@@ -280,13 +281,15 @@ for i in range(N):
     for j in range(N):
 	if i == j:
 	    continue
-        for q in range(Q):
-            for k in range(M):
-                lhs = False
-                for z in range(N-1):
-                    lhs = Or(r[j][i][k][z], lhs)
-                l  = Implies(presence_edge[i][j][q][k],lhs)
-                A_list.append(l)
+        for k in range(M):
+            lhs = False
+            rhs = False
+            for q in range(Q):
+                rhs = Or( presence_edge[i][j][q][k]
+            for z in range(N-1):
+                lhs = Or(r[j][i][k][z], lhs)
+            l  = Implies(rhs,lhs)
+            A_list.append(l)
 F3 = And(A_list)
 # print F3
 
@@ -493,13 +496,14 @@ def Lfive_conn():
                         D1_list.append( And( d1[m], rhs2 ))
     return Or(D1_list)                
 
-if V == 1:
+# C is the neccesary condition.
+if C == 2:
     D1 = Ltwo_conn()
     D2 = Not( Lthree_conn())
-elif V == 2:
+elif C == 3:
     D1 = Lthree_conn()
     D2 = Not( Lfour_conn())
-elif V == 3:
+elif C == 4:
     D1 = Lfour_conn()
     D2 = Not( Lfive_conn())
 else:
@@ -650,16 +654,16 @@ if s.check() == sat:
 #    print "Printing the model..."
     for d in m.decls():
        print "{} = {}".format(d.name(), m[d])
-    print m
+#    print m
     r = [ [ m[p[i][j]] for j in range(M) ]
           for i in range(M) ]
     s = [[ [ [m[active_edge[i][j][q][k]] for k in range (M)] for q in range(Q)] for j in range(N) ] for i in range(N) ]
     t = [ [ [m[edge[i][j][q]]  for q in range(Q)] for j in range(N) ]
           for i in range(N) ]
-#    print "\n Pairing matrix p[{}][{}] = ".format(M,M)
-#    print_matrix(r)
[…]

### 2017-06-04 biology.py
updated-paper-fixed-a-bug

@@ -99,7 +99,7 @@ def f_ne():
 # Other molecule present on that node/edge.
 # A0. active_node[k] =  f_n[k](\/_{k1 != k} node(k1)) 
 def f_bn():
-    print "I am here!!"
+   # print "I am here!!"
     s = []
     A_list = []
     for k in range(M):
@@ -137,7 +137,12 @@ def f_be():
     return And( A_list )
 
 # Inhibition of the edges are driven by the pairing matrix.
-# And(p[k][k1] -> edge[k]) -> active[k]
+# If there is a molecule k present on the edge(i,j) and with non-zero pairing matrix
+# the evry pairing matrix elements are present on that node makes that molecule inactive.
+# else its active.
+# { e(i,j,k) and (exists_k': p(k,k') and [p(k,k') -> e(i,j,k')] )) } -> ~ b(i,j,k)   
+# { e(i,j,k) and ~(exists_k': p(k,k') and [p(k,k') -> e(i,j,k')] )) } -> b(i,j,k)   
+
 def f_se():
     A_list = []
     for i in range(N):
@@ -146,15 +151,36 @@ def f_se():
                 continue
             for q in range(Q):
                 for k in range(M):
-                    l = True
+                    lhs = presence_edge[i][j][q][k]
+                    l1 = False
+                    l2 = True
                     for k1 in range(M):
-                        if k == k1:
+                        if k1 == k:
                             continue
-                        l = And (Implies( p[k][k1], presence_edge[i][j][q][k1]),l)
-                    l1 = Implies( l, Not(active_edge[i][j][q][k]))
-                    l2 = Implies ( Not(l), active_edge[i][j][q][k])
-                    A_list.append(And(l1,l2))
-    return And(A_list)
+                        l1 = Or( p[k][k1], l1)
+                        l2 = And( Implies( p[k][k1], presence_edge[i][j][q][k1]) , l2)   
+                    l = Implies ( And( lhs, And( l1,l2)), Not( active_edge[i][j][q][k]) )
+                    ll = Implies ( And ( lhs, Not (And ( l1,l2)) ), active_edge[i][j][q][k]) 
+                    A_list.append(And ( l, ll) )
+    return And (A_list)
+
+#def f_se():
+#    A_list = []
+#    for i in range(N):
+#        for j in range(N):
+#            if i == j:
+#                continue
[…]

### 2017-06-06 paper/main.tex
updated-paper-fixed-a-bug
paper folder organized

@@
 \begin{document}
-\vspace*{0.2in}
 
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{ Vesicle traffic system and constraints.} % Please use 
-}
-\newline
-\\
-\end{flushleft}
+\title{SAT Solving for Vesicle Traffic Systems in Cells}
 
-\section{Formula variables}
-Basic notation for the formula we are trying to generate.
-\begin{enumerate}
-\item edge = e(i,j,q)
-      There is an qth edge between node i and j.
+\author{to be announced}
 
-\item dump = d(i,j,q)
-       drop edge(i,j,q) from the graph.
+\date{\today}
 
-\item presence node = n(i,k) 
-	  kth molecule is present on the node i.
+\maketitle
 
-\item active\_node = a(i,k) 
-      kth molecule is active on the node i.
+% \vspace*{0.2in}
+% % Title must be 250 characters or less.
+% \begin{flushleft}
+% {\Large
+% \textbf\newline{ Vesicle traffic system and constraints.} % Please use 
+% }
+% \newline
+% \\
+% \end{flushleft}
 
-\item presence\_edge = e(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule present.
+\begin{abstract}
+\input{abstract}
+\end{abstract}
 
-\item active\_edge = b(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule active.
+\section{Introduction}
+\label{sec:intro}
+\input{intro}
 
-\item reachability = r(i,j,k,z)
-      Node i and j are reachable with kth molecule present in z steps.
+% \input{bio}
+% \input{conc}
 
-\item pairing matrix = p(k,k')
-      Molecule k and k' are pairing molecules in the matrix.
+\section{Implementation and Experiments}
+\label{sec:experiments}
+\input{experiments}
 
-\item Type of the Boolean function = sorts (takes k-1 arguments Bool and return Bool) 
-\item Boolean function on nodes Function (fn\_{m},*sorts)
+\section{Related Work}
+\label{sec:related}
+\input{related}
 
-\item Boolean function on edge Function(fe\_{m},*sorts)
+\section{Conclusion}
+\label{sec:conclusion}
+\input{conclusion}
 
-\end{enumerate}
-
-\section{Regulation on nodes and edges}
-Regulation of a model is based on the kind of the model under consideration.
-for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by SNARE-SNARE inhibition.
-
-We have build constraints A0, A1 for these two regulations. \newline
-
-A0: No regulation on nodes.
-\[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]
-
-A1: No regulation on edges.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]
-
-A0: Boolean regulation on nodes. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
-
-A1: Boolean regulation on edges. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e(i,j,q,k')) \, \]
-
-A1: SNARE-SNARE inhibition. Inhibition of the edges are driven by the pairing matrix.
-\[ \bigwedge\limits_{i,j,i != j, q, k} (\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'}) \supset \neg b(i,j,q,k)) \, \]
-
-\[ \bigwedge\limits_{i,j,i != j, q, k} \neg [(\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] \supset b(i,j,q,k)) \, \]
-
-\section{Basic constraints on the edges and nodes}
-The edge labels are subset of the node label of source and target compartment. \newline
-
-C0: The edge labels are subset of the node label of source compartment.
-
-\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset a_{i,k} \, \]
-
-C1: The edge labels are subset of the node label of target compartment.
-
-\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset a_{j,k} \, \]  
-%C1 =  e_ijk -> aik and e_ijk -> ajk
-
-C2: Self edges are not allowed.
-
-\[  \bigwedge\limits_{i,q} \neg e_{i,i,q} \, \]
-
-C4: Condition on p\_kk'. Diagonal blocks should be all 0's.
-
-\[ \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y) \, \]
-
-C5: Activity on the node. A molecule should be present to be active on a node.  
-\[ \bigwedge\limits_{i,k} a_{i,k} \supset n_{j,k} \, \]
-
-% - F0: b(i,j,k) $\supset$ e(i,j,k)
-
-\section{Main constraints}
-Main constraints to be followed. \newline
-
-F0:  An edge has to have one present molecule. F0 looks redundant.
-
-\[ \bigwedge\limits_{i,j,q} \bigvee_k e_{i,j,q,k} \supset e_{i,j,q} \, \]
-
-F1: If molecule is active on an edge then it should be present on the edge.
-
-\[ \bigwedge\limits_{i,j,q,k} a_{i,j,q,k} \supset e_{i,j,q,k}\, \]
-
-\section{Steady state specification}
-Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.
-
-\subsection{Reachability definition and stability condition}
-If molecule is active on an edge then it should be present on the edge. \newline
-
-F3: stability condition. Source node is reachable by target node with that molecule present in p steps.
-
-% I have implemented: Changed the implementation in code too.
-%\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
-
-% Update: Better 
-\[ \bigwedge\limits_{i,j,k} (\bigvee_{q} e_{i,j,q,k}) \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
-
-F2: Reachability definition.
-\[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \supset (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]
-
-\section{ Fusion rule Formula}
-
-Fusion rules consist of two different mechanisms.
-
-\begin{enumerate}
-\item  A \textbf{SNARE pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate SNARE activity based on the presence/absence of other molecules on the corresponding node or edge.
-\end{enumerate}
-
-F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active, and have a non-zero entry in the pairing matrix.
-
-\[ \bigwedge\limits_{i,j,q} e_{i,j,q} \supset \bigvee_{k,k^{\prime}} (b_{i,j,q,k} \land a_{j,k^{\prime}} \land p_{k,k^{\prime}}) \, \]
-
-F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.
-
-\[ \bigwedge\limits_{i,j,k} b_{i,j,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]
-
-\section{Connectivity}
-To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph.
-We can go down or up using -C \_ option.
-\newline
-
-D0: Only present edges can be dropped.
-\[ \bigwedge\limits_{i,j,q} d_{i,j,q} \supset e_{i,j,q}  \]
-
-D1,D2: We are dropping c edges from the graph. exactly c are dropped.
-\[ \sum_{i,j,q} d_{i,j,q} == c \]
-
-D3:  Graph becomes disconnected. Ensure that there is no path between some nodes i,j in the underlying undirected graph. Different reachability.
-\[ \bigwedge\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})]  \]
-
-D4: New reachability definition for grph connectedness: dReachable. Node i,j are reachable either if there is a direct edge and its not dropped. 
-Or there is an node i' such that, there is a direct edge between i,i' which is not dropped and i' and j is dReachable.
-
-\[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \supset r^{\prime}(i,j)  \]
+\bibliographystyle{unsrt}
+\bibliography{biblio}
 
 \end{document}
+
+%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2017-06-06 paper/conclusion.tex
added more org

--- 2017-06-02 paper/main.tex
@@
-% This is based on the LLNCS.DEM the demonstration file of
-% the LaTeX macro package from Springer-Verlag
-% for Lecture Notes in Computer Science,
-% version 2.4 for LaTeX2e as of 16. April 2010
-%
-% See http://www.springer.com/computer/lncs/lncs+authors?SGWID=0-40209-0-0-0
-% for the full guidelines.
-%
-\documentclass{llncs}
-\usepackage{graphicx}
-% \usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
 
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-\renewcommand{\figurename}{Fig.{}}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% Use package Listing to add code in our Manuscript
-\usepackage{listings}
-
-% Added for the sub-pictures
-\usepackage{subcaption}
-
-% Added for the multi-column 
-\usepackage[british]{babel}
-\usepackage{hhline}
-\usepackage{multirow}
-\usepackage[figurename=Fig]{caption}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-\renewcommand{\thesubfigure}{\Alph{subfigure}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-\renewcommand{\thesubfigure}{\Alph{subfigure}}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-\usepackage{epstopdf}
-\AppendGraphicsExtensions{.tif}
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-\begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{ Vesicle traffic system and constraints.} % Please use 
-}
-\newline
-\\
-\end{flushleft}
-
-\section{Formula variables}
-Basic notation for the formula we are trying to generate.
-\begin{enumerate}
-\item edge = e(i,j,q)
-      There is an qth edge between node i and j.
-
-\item dump = d(i,j,q)
-       drop edge(i,j,q) from the graph.
-
-\item presence node = n(i,k) 
-	  kth molecule is present on the node i.
-
-\item active\_node = a(i,k) 
-      kth molecule is active on the node i.
-
-\item presence\_edge = e(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule present.
-
-\item active\_edge = b(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule active.
-
-\item reachability = r(i,j,k,z)
-      Node i and j are reachable with kth molecule present in z steps.
-
-\item pairing matrix = p(k,k')
-      Molecule k and k' are pairing molecules in the matrix.
-
-\item Type of the Boolean function = sorts (takes k-1 arguments Bool and return Bool) 
-\item Boolean function on nodes Function (fn\_{m},*sorts)
-
-\item Boolean function on edge Function(fe\_{m},*sorts)
-
-\end{enumerate}
-
-\section{Regulation on nodes and edges}
-Regulation of a model is based on the kind of the model under consideration.
-for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by SNARE-SNARE inhibition.
-
-We have build constraints A0, A1 for these two regulations. \newline
-
-A0: No regulation on nodes.
-\[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]
-
-A1: No regulation on edges.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]
-
-A0: Boolean regulation on nodes. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
-
-A1: Boolean regulation on edges. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e(i,j,q,k')) \, \]
-
-A1: SNARE-SNARE inhibition. Inhibition of the edges are driven by the pairing matrix.
-\[ \bigwedge\limits_{i,j,i != j, q, k} (\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'}) \supset \neg b(i,j,q,k)) \, \]
-
-\[ \bigwedge\limits_{i,j,i != j, q, k} \neg [(\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] \supset b(i,j,q,k)) \, \]
-
-\section{Basic constraints on the edges and nodes}
-The edge labels are subset of the node label of source and target compartment. \newline
-
-C0: The edge labels are subset of the node label of source compartment.
-
-\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset a_{i,k} \, \]
-
-C1: The edge labels are subset of the node label of target compartment.
-
-\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset a_{j,k} \, \]  
-%C1 =  e_ijk -> aik and e_ijk -> ajk
-
-C2: Self edges are not allowed.
-
-\[  \bigwedge\limits_{i,q} \neg e_{i,i,q} \, \]
-
-C4: Condition on p\_kk'. Diagonal blocks should be all 0's.
-
-\[ \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y) \, \]
-
-C5: Activity on the node. A molecule should be present to be active on a node.  
-\[ \bigwedge\limits_{i,k} a_{i,k} \supset n_{j,k} \, \]
-
-% - F0: b(i,j,k) $\supset$ e(i,j,k)
-
-\section{Main constraints}
-Main constraints to be followed. \newline
-
-F0:  An edge has to have one present molecule. F0 looks redundant.
-
-\[ \bigwedge\limits_{i,j,q} \bigvee_k e_{i,j,q,k} \supset e_{i,j,q} \, \]
-
-F1: If molecule is active on an edge then it should be present on the edge.
-
-\[ \bigwedge\limits_{i,j,q,k} a_{i,j,q,k} \supset e_{i,j,q,k}\, \]
-
-\section{Steady state specification}
-Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.
-
-\subsection{Reachability definition and stability condition}
-If molecule is active on an edge then it should be present on the edge. \newline
-
-F3: stability condition. Source node is reachable by target node with that molecule present in p steps.
-
-% I have implemented: Changed the implementation in code too.
-%\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
-
-% Update: Better 
-\[ \bigwedge\limits_{i,j,k} (\bigvee_{q} e_{i,j,q,k}) \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
-
-F2: Reachability definition.
-\[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \supset (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]
-
-\section{ Fusion rule Formula}
-
-Fusion rules consist of two different mechanisms.
-
-\begin{enumerate}
-\item  A \textbf{SNARE pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate SNARE activity based on the presence/absence of other molecules on the corresponding node or edge.
-\end{enumerate}
-
-F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active, and have a non-zero entry in the pairing matrix.
-
-\[ \bigwedge\limits_{i,j,q} e_{i,j,q} \supset \bigvee_{k,k^{\prime}} (b_{i,j,q,k} \land a_{j,k^{\prime}} \land p_{k,k^{\prime}}) \, \]
-
-F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.
-
-\[ \bigwedge\limits_{i,j,k} b_{i,j,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]
-
-\section{Connectivity}
-To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph.
-We can go down or up using -C \_ option.
-\newline
-
-D0: Only present edges can be dropped.
-\[ \bigwedge\limits_{i,j,q} d_{i,j,q} \supset e_{i,j,q}  \]
-
-D1,D2: We are dropping c edges from the graph. exactly c are dropped.
-\[ \sum_{i,j,q} d_{i,j,q} == c \]
-
-D3:  Graph becomes disconnected. Ensure that there is no path between some nodes i,j in the underlying undirected graph. Different reachability.
-\[ \bigwedge\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})]  \]
-
-D4: New reachability definition for grph connectedness: dReachable. Node i,j are reachable either if there is a direct edge and its not dropped. 
-Or there is an node i' such that, there is a direct edge between i,i' which is not dropped and i' and j is dReachable.
-
-\[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \supset r^{\prime}(i,j)  \]
-
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2017-06-07 paper/abstract.tex
abstract added

In Biology, there are several questions that translate to combinatorial 
search.
%
For example, vesicle traffic systems in biological cells exhibit
several graph properties such as three connectivity and
a natural question arises for biologists that what are all possible
networks for various combinations of those properties.
%
It will help biologists for .....
%
In this paper, we present a SAT/QBF encodings of the properties over
vesicle traffic systems and a tool that searches for the networks
that satisfies the properties using SAT/QBF solvers.
%
In our experiments, we show that our tool can search for networks of
sizes that are considered to be relevant by biologists.

%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2017-06-07 paper/intro.tex
paper folder organized
abstract added

--- 2017-06-02 paper/main.tex
@@
-% This is based on the LLNCS.DEM the demonstration file of
-% the LaTeX macro package from Springer-Verlag
-% for Lecture Notes in Computer Science,
-% version 2.4 for LaTeX2e as of 16. April 2010
+% What is vesicle traffic systems
+
+% Graph properties of the systems
+
+% Search queries; why bio imp
+
+% Using SAT/QBF solvers to encode
+
 %
-% See http://www.springer.com/computer/lncs/lncs+authors?SGWID=0-40209-0-0-0
-% for the full guidelines.
-%
-\documentclass{llncs}
-\usepackage{graphicx}
-% \usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
 
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
 
-\renewcommand{\figurename}{Fig.{}}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% Use package Listing to add code in our Manuscript
-\usepackage{listings}
-
-% Added for the sub-pictures
-\usepackage{subcaption}
-
-% Added for the multi-column 
-\usepackage[british]{babel}
-\usepackage{hhline}
-\usepackage{multirow}
-\usepackage[figurename=Fig]{caption}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-\renewcommand{\thesubfigure}{\Alph{subfigure}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-\renewcommand{\thesubfigure}{\Alph{subfigure}}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-\usepackage{epstopdf}
-\AppendGraphicsExtensions{.tif}
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-\begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{ Vesicle traffic system and constraints.} % Please use 
-}
-\newline
-\\
-\end{flushleft}
-
-\section{Formula variables}
-Basic notation for the formula we are trying to generate.
-\begin{enumerate}
-\item edge = e(i,j,q)
-      There is an qth edge between node i and j.
-
-\item dump = d(i,j,q)
-       drop edge(i,j,q) from the graph.
-
-\item presence node = n(i,k) 
-	  kth molecule is present on the node i.
-
-\item active\_node = a(i,k) 
-      kth molecule is active on the node i.
-
-\item presence\_edge = e(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule present.
-
-\item active\_edge = b(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule active.
-
-\item reachability = r(i,j,k,z)
-      Node i and j are reachable with kth molecule present in z steps.
-
-\item pairing matrix = p(k,k')
-      Molecule k and k' are pairing molecules in the matrix.
-
-\item Type of the Boolean function = sorts (takes k-1 arguments Bool and return Bool) 
-\item Boolean function on nodes Function (fn\_{m},*sorts)
-
-\item Boolean function on edge Function(fe\_{m},*sorts)
-
-\end{enumerate}
-
-\section{Regulation on nodes and edges}
-Regulation of a model is based on the kind of the model under consideration.
-for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by SNARE-SNARE inhibition.
-
-We have build constraints A0, A1 for these two regulations. \newline
-
-A0: No regulation on nodes.
-\[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]
-
-A1: No regulation on edges.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]
-
-A0: Boolean regulation on nodes. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
-
-A1: Boolean regulation on edges. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e(i,j,q,k')) \, \]
-
-A1: SNARE-SNARE inhibition. Inhibition of the edges are driven by the pairing matrix.
-\[ \bigwedge\limits_{i,j,i != j, q, k} (\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'}) \supset \neg b(i,j,q,k)) \, \]
-
-\[ \bigwedge\limits_{i,j,i != j, q, k} \neg [(\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] \supset b(i,j,q,k)) \, \]
-
-\section{Basic constraints on the edges and nodes}
-The edge labels are subset of the node label of source and target compartment. \newline
-
-C0: The edge labels are subset of the node label of source compartment.
-
-\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset a_{i,k} \, \]
-
-C1: The edge labels are subset of the node label of target compartment.
-
-\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset a_{j,k} \, \]  
-%C1 =  e_ijk -> aik and e_ijk -> ajk
-
-C2: Self edges are not allowed.
-
-\[  \bigwedge\limits_{i,q} \neg e_{i,i,q} \, \]
-
-C4: Condition on p\_kk'. Diagonal blocks should be all 0's.
-
-\[ \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y) \, \]
-
-C5: Activity on the node. A molecule should be present to be active on a node.  
-\[ \bigwedge\limits_{i,k} a_{i,k} \supset n_{j,k} \, \]
-
-% - F0: b(i,j,k) $\supset$ e(i,j,k)
-
-\section{Main constraints}
-Main constraints to be followed. \newline
-
-F0:  An edge has to have one present molecule. F0 looks redundant.
-
-\[ \bigwedge\limits_{i,j,q} \bigvee_k e_{i,j,q,k} \supset e_{i,j,q} \, \]
-
-F1: If molecule is active on an edge then it should be present on the edge.
-
-\[ \bigwedge\limits_{i,j,q,k} a_{i,j,q,k} \supset e_{i,j,q,k}\, \]
-
-\section{Steady state specification}
-Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.
-
-\subsection{Reachability definition and stability condition}
-If molecule is active on an edge then it should be present on the edge. \newline
-
-F3: stability condition. Source node is reachable by target node with that molecule present in p steps.
-
-% I have implemented: Changed the implementation in code too.
-%\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
-
-% Update: Better 
-\[ \bigwedge\limits_{i,j,k} (\bigvee_{q} e_{i,j,q,k}) \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
-
-F2: Reachability definition.
-\[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \supset (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]
-
-\section{ Fusion rule Formula}
-
-Fusion rules consist of two different mechanisms.
-
-\begin{enumerate}
-\item  A \textbf{SNARE pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate SNARE activity based on the presence/absence of other molecules on the corresponding node or edge.
-\end{enumerate}
-
-F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active, and have a non-zero entry in the pairing matrix.
-
-\[ \bigwedge\limits_{i,j,q} e_{i,j,q} \supset \bigvee_{k,k^{\prime}} (b_{i,j,q,k} \land a_{j,k^{\prime}} \land p_{k,k^{\prime}}) \, \]
-
-F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.
-
-\[ \bigwedge\limits_{i,j,k} b_{i,j,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]
-
-\section{Connectivity}
-To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph.
-We can go down or up using -C \_ option.
-\newline
-
-D0: Only present edges can be dropped.
-\[ \bigwedge\limits_{i,j,q} d_{i,j,q} \supset e_{i,j,q}  \]
-
-D1,D2: We are dropping c edges from the graph. exactly c are dropped.
-\[ \sum_{i,j,q} d_{i,j,q} == c \]
-
-D3:  Graph becomes disconnected. Ensure that there is no path between some nodes i,j in the underlying undirected graph. Different reachability.
-\[ \bigwedge\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})]  \]
-
-D4: New reachability definition for grph connectedness: dReachable. Node i,j are reachable either if there is a direct edge and its not dropped. 
-Or there is an node i' such that, there is a direct edge between i,i' which is not dropped and i' and j is dReachable.
-
-\[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \supset r^{\prime}(i,j)  \]
-
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2017-06-10 paper/abstract.tex
removed auto generated files

@@
 %
-In this paper, we present a SAT/QBF encodings of the properties over
+In this paper, we present SAT/QBF encodings of the properties over
 vesicle traffic systems and a tool that searches for the networks

### 2017-06-10 paper/encoding.tex
added more org
removed auto generated files

--- 2017-06-02 paper/main.tex
@@
-% This is based on the LLNCS.DEM the demonstration file of
-% the LaTeX macro package from Springer-Verlag
-% for Lecture Notes in Computer Science,
-% version 2.4 for LaTeX2e as of 16. April 2010
-%
-% See http://www.springer.com/computer/lncs/lncs+authors?SGWID=0-40209-0-0-0
-% for the full guidelines.
-%
-\documentclass{llncs}
-\usepackage{graphicx}
-% \usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+In this section, we will present our encoding of the search problem.
 
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+\subsection{Network description}
 
-\renewcommand{\figurename}{Fig.{}}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% Use package Listing to add code in our Manuscript
-\usepackage{listings}
-
-% Added for the sub-pictures
-\usepackage{subcaption}
-
-% Added for the multi-column 
-\usepackage[british]{babel}
-\usepackage{hhline}
-\usepackage{multirow}
-\usepackage[figurename=Fig]{caption}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-\renewcommand{\thesubfigure}{\Alph{subfigure}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-\renewcommand{\thesubfigure}{\Alph{subfigure}}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-\usepackage{epstopdf}
-\AppendGraphicsExtensions{.tif}
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-\begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{ Vesicle traffic system and constraints.} % Please use 
-}
-\newline
-\\
-\end{flushleft}
-
-\section{Formula variables}
 Basic notation for the formula we are trying to generate.
@@
 
-\section{Regulation on nodes and edges}
+\subsubsection{Regulation on nodes and edges}
 Regulation of a model is based on the kind of the model under consideration.
@@
 A1: Boolean regulation on edges. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e(i,j,q,k')) \, \]
+\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]
 
 A1: SNARE-SNARE inhibition. Inhibition of the edges are driven by the pairing matrix.
-\[ \bigwedge\limits_{i,j,i != j, q, k} (\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'}) \supset \neg b(i,j,q,k)) \, \]
+\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]
 
-\[ \bigwedge\limits_{i,j,i != j, q, k} \neg [(\bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] \supset b(i,j,q,k)) \, \]
+\[ \bigwedge\limits_{i,j, q, k}  (e_{i,j,q,k} \land \neg [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset b_{i,j,q,k}) \, \]
 
-\section{Basic constraints on the edges and nodes}
+\subsubsection{Basic constraints on the edges and nodes}
 The edge labels are subset of the node label of source and target compartment. \newline
@@
 
-\section{Main constraints}
+\subsubsection{Main constraints}
 Main constraints to be followed. \newline
@@
 
-\[ \bigwedge\limits_{i,j,q,k} a_{i,j,q,k} \supset e_{i,j,q,k}\, \]
+\[ \bigwedge\limits_{i,j,q,k} b_{i,j,q,k} \supset e_{i,j,q,k}\, \]
 
-\section{Steady state specification}
+\subsubsection{Steady state specification}
 Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.
 
-\subsection{Reachability definition and stability condition}
+\subsubsection{Reachability definition and stability condition}
 If molecule is active on an edge then it should be present on the edge. \newline
@@
 
-\section{ Fusion rule Formula}
+\subsubsection{ Fusion rule Formula}
 
@@
 
-\section{Connectivity}
+\subsubsection{Connectivity}
 To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph.
@@
 
-\end{document}
+%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2017-06-11 biology.py
cnf

@@ -164,24 +164,6 @@ def f_se():
                     A_list.append(And ( l, ll) )
     return And (A_list)
 
-#def f_se():
-#    A_list = []
-#    for i in range(N):
-#        for j in range(N):
-#            if i == j:
-#                continue
-#            for q in range(Q):
-#                for k in range(M):
-#                    l = True
-#                    for k1 in range(M):
-#                        if k == k1:
-#                            continue
-#                        l = And (Implies( p[k][k1], presence_edge[i][j][q][k1]),l)
-#                    l1 = Implies( l, Not(active_edge[i][j][q][k]))
-#                    l2 = Implies ( Not(l), active_edge[i][j][q][k])
-#                    A_list.append(And(l1,l2))
-#    return And(A_list)
-
 A0 = True 
 A1 = True
 
@@ -238,7 +220,7 @@ for i in range(N):
 C2 = True
 for i in range(N):
     for q in range(Q):
-        C2 = And(Not(edge[i][i][q]), C2)
+        C2 = And( Not(edge[i][i][q]), C2)
 
 
 #3. Multiple(parallel) edges are allowed between two nodes. 
@@ -592,7 +574,7 @@ print ' '
 
 # forall_{i,j} r'(i,j) -> exists_{q} [e(i,j,q) and not d(i,j,q)] Or  exists_{i'!=i}: [r'(i',j) and [exists_{q}: e(i,i',q) and ~d(i,i',q)] ]   
 # do we need length reach?
-#D3 = True
+# D3 = True
 A_list = []
 for i in range(N):
     for j in range(N):
@@ -612,25 +594,7 @@ for i in range(N):
         w = Implies( Or(bhs , rhs), r1[i][j] )
         A_list.append(w)
 D4 = And(A_list)
-print D4
-
-# Initial D3 u have encoded.
-# do we need length reach?
-#D3 = True
-#for i in range(N):
-#    for j in range(N):
-#        rhs = And( edge[i][j], Not(dump[i][j]) )
-#        for l in range(N):
-#            if i == l:
-#                continue
-#            rhs = Or( And(And(edge[i][l],Not(dump[i][l])),r1[l][j] ), rhs) 
-#        D3 = And( Implies( r1[i][j], rhs ), D3)
[…]

### 2017-06-11 qbf_bio.py

@@ -1,93 +1,0 @@
-#!/usr/bin/python
-
-from z3 import *
-import argparse
-import time
-
-#----------------------------------------------------
-# input parsing
-# input number of nodes and molecules
-parser = argparse.ArgumentParser(description='Auto testing for TARA')
-parser.add_argument("-M","--mols", type=int, default=32, help = "number of molecules")
-parser.add_argument("-N","--nodes", type=int, default=8, help = "number of nodes")
-parser.add_argument("-Q","--pedges", type=int, default=2, help = "max no.of parallel edges btw two nodes")
-parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
-parser.add_argument("-C","--connected", type=int, default=3, help = "graph connectivity want to check")
-args = parser.parse_args()
-
-M = args.mols
-N = args.nodes
-Q = args.pedges
-V = args.variation
-C = args.connected
-
-bag = []
-bag.append ('1. Boolean function on nodes and Boolean function on the edges.') 
-bag.append ('2. Only Boolean function on the edges.') 
-bag.append ('3. Boolean function on nodes and SNARE-SNARE inhibition on edges.')
-bag.append ('4. Only SNARE-SNARE inhibition on edges.')
-bag.append ('5. Only Boolean function on nodes.')
-bag.append ('6. No regulation at all.')
-
-for i in range(6):
-    if V == i + 1:
-        print ' '
-        print 'Default/choosen vesicular traffic system is regulated by ...',
-        print bag[i]
-        print ' '
-        print 'Use -V option to change the regulated variation.' 
-        for i in bag:
-            print i 
-        print ' '
-        break
-
-#----------------------------------------------------
-# Constraint generation 
-dump = [ [ [Bool ("d_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
-
-node = [ [Bool ("n_{}_{}".format(i,k)) for k in range(M)] for i in range(N)]
-
-active_node = [ [Bool ("a_{}_{}".format(i,k)) for k in range(M)] for i in range(N)]
-
[…]

### 2017-06-12 paper/experiments.tex
some reorg

--- 2017-06-10 paper/abstract.tex
@@
-In Biology, there are several questions that translate to combinatorial 
-search.
-%
-For example, vesicle traffic systems in biological cells exhibit
-several graph properties such as three connectivity and
-a natural question arises for biologists that what are all possible
-networks for various combinations of those properties.
-%
-It will help biologists for .....
-%
-In this paper, we present SAT/QBF encodings of the properties over
-vesicle traffic systems and a tool that searches for the networks
-that satisfies the properties using SAT/QBF solvers.
-%
-In our experiments, we show that our tool can search for networks of
-sizes that are considered to be relevant by biologists.
+We have implemented the encoding of the constraints
+in the python interface of $\zthree$
 

### 2017-06-13 paper/experiments.tex
table added

@@
 We have implemented the encoding of the constraints
-in the python interface of $\zthree$
+in the python interface of $\zthree$.
+%
+Our implementation supports several versions of the
+models of vesicle traffic systems.
+\todo{describe the variations}
+\begin{itemize}
+\item 
+\end{itemize}
+
+We have applied the tool for the above variations
+for searching the vesicle traffic systems that satisfies
+their corresponding properties.
+%
+\input{tbl-qf-graph}
+In table~\ref{tbl:qf-results}
+
+\todo{Make table for all sizes and variants of the tool}
 

### 2017-06-13 paper/abstract.tex
cnf
back-abstract

@@
-In Biology, there are several questions that translate to combinatorial 
-search.
-%
-For example, vesicle traffic systems in biological cells exhibit
-several graph properties such as three connectivity and
-a natural question arises for biologists that what are all possible
-networks for various combinations of those properties.
-%
-It will help biologists for .....
-%
-In this paper, we present SAT/QBF encodings of the properties over
-vesicle traffic systems and a tool that searches for the networks
-that satisfies the properties using SAT/QBF solvers.
-%
-In our experiments, we show that our tool can search for networks of
-sizes that are considered to be relevant by biologists.
+In biology, there are several questions that translate to combinatorial
+search. For example, vesicle traffic systems that move cargo within
+eukaryotic cells have been proposed to exhibit several graph properties
+such as three connectivity. These properties are consequences of underlying
+biophysical constraints. A natural question for biologists is: what are all
+possible networks for various combinations of those properties? In this
+paper, we present SAT/QBF encodings of the properties over vesicle traffic
+systems and a tool that searches for the networks that satisfies the
+properties using SAT/QBF solvers. In our experiments, we show that our tool
+can search for networks of sizes that are considered to be relevant by
+biologists.
 

### 2017-06-13 biology.py
for-all-fix

@@ -65,6 +65,9 @@ RX = [ r1[i][j] for i in range(N) for j in range(N) if i != j ]
 funE = len(E) + len(DX) + len(RX)
 lenE = funE + 1
 
+QVars = E + RX + DX
+print QVars
+
 #print funE
 #print lenE
 #sys.exit(0)
@@ -84,12 +87,8 @@ for i in range(N):
     for k in range(M):
         s = []
         nxx = fnode[i][k] 
-        for t in E:
+        for t in QVars:
             s.append( t )
-        for tt in DX:
-            s.append( tt )
-        for ttt in RX:
-            s.append( ttt )
         node[i][k] = nxx( s )
 
 # Skolemized dumped edges
@@ -112,12 +111,8 @@ for i in range(N):
     for k in range(M):
         s = []
         nxx = factive_node[i][k] 
-        for t in E:
+        for t in QVars:
             s.append( t )
-        for tt in DX:
-            s.append( tt )
-        for ttt in RX:
-            s.append( ttt )
         active_node[i][k] = nxx( s )
 
 # Skolemized presence_edges :
@@ -130,12 +125,8 @@ for i in range(N):
             for k in range(M):
                 s = []
                 nxx = fpresence_edge[i][j][q][k] 
-                for t in E:
+                for t in QVars:
                     s.append( t )
-                for tt in DX:
-                    s.append( tt )
-                for ttt in RX:
-                    s.append( ttt )
                 presence_edge[i][j][q][k] = nxx( s )
 
 
@@ -149,12 +140,8 @@ for i in range(N):
             for k in range(M):
                 s = []
                 nxx = factive_edge[i][j][q][k] 
-                for t in E:
+                for t in QVars:
                     s.append( t )
-                for tt in DX:
-                    s.append( tt )
-                for ttt in RX:
-                    s.append( ttt )
                 active_edge[i][j][q][k] = nxx( s )
 
 
@@ -168,12 +155,8 @@ for i in range(N):
             for z in range(N-1):
                 s = []
                 nxx = fr[i][j][k][z] 
-                for t in E:
+                for t in QVars:
                     s.append( t )
-                for tt in DX:
-                    s.append( tt )
-                for ttt in RX:
-                    s.append( ttt )
                 r[i][j][q][z] = nxx( s )
 
 # Skolemized pairing matrix
@@ -184,12 +167,8 @@ for k in range(M):
     for k1 in range(M):
         nxx = fp[k][k1]
         s  = []
-        for t in E:
[…]

### 2017-06-14 paper/encoding.tex
cnf
experiments-table-versions-encoding

@@
 Regulation of a model is based on the kind of the model under consideration.
-for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by SNARE-SNARE inhibition.
+for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by pairing inhibition.
 
@@
 
+A0: Boolean regulation on nodes. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
+\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
+
 A1: No regulation on edges.
 \[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]
-
-A0: Boolean regulation on nodes. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
 
@@
 
-A1: SNARE-SNARE inhibition. Inhibition of the edges are driven by the pairing matrix.
+A1: Pairing inhibition. Inhibition of the edges are driven by the pairing matrix.
 \[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]
@@
 
-\subsubsection{Basic constraints on the edges and nodes}
-The edge labels are subset of the node label of source and target compartment. \newline
+\subsubsection{Constraints on the structure of the edges, nodes and pairing matrix}
 
@@
 
-\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset a_{i,k} \, \]
+\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset n_{i,k} \, \]
 
@@
 
-\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset a_{j,k} \, \]  
+\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset n_{j,k} \, \]  
 %C1 =  e_ijk -> aik and e_ijk -> ajk
@@
 
-\subsubsection{Main constraints}
-Main constraints to be followed. \newline
+\subsubsection{Constraints on presence and activity of the molecule}
+Few additional constrints are required on the molesules presence and activity. \newline
 
@@
 
-\subsubsection{Steady state specification}
+\subsubsection{Constraints for stability condition}
+The whole cell should be in stable condition i.e global flow of the molecule is balanced at every point.
 Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.
 
-\subsubsection{Reachability definition and stability condition}
+\bf{Reachability definition and stability condition}
+We have encoded this requiremnt by using reachability definition. 
 If molecule is active on an edge then it should be present on the edge. \newline
@@
 
-\subsubsection{ Fusion rule Formula}
+\subsubsection{Fusion rule constraints}
 
@@
 \begin{enumerate}
-\item  A \textbf{SNARE pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate SNARE activity based on the presence/absence of other molecules on the corresponding node or edge.
+\item  A \textbf{Pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
+\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
 \end{enumerate}
@@
 
-\[ \bigwedge\limits_{i,j,k} b_{i,j,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]
+\[ \bigwedge\limits_{i,j,q,k} b_{i,j,q,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]
 
-\subsubsection{Connectivity}
+\subsubsection{Graph connectivity constraints}
 To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph.

### 2017-06-14 paper/experiments.tex
experiments-table-versions-encoding

@@
 \todo{describe the variations}
-\begin{itemize}
-\item 
-\end{itemize}
+
+\begin{enumerate}[label=\Alph*]
+\item Every present molecule is considered to be active.
+\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
+\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
+\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
+\item Activity of molecules on the edges is driven by pairing inhibition.
+\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
+\item Version F with additional constraint that every edge is distinct.
+%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
+%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
+\item Version F but self-edges are allowed.
+\end{enumerate}
 
@@
 their corresponding properties.
-%
+
 \input{tbl-qf-graph}
 In table~\ref{tbl:qf-results} 
+\b PARTIAL ...
+
+\begin{table}[!ht]
+\centering
+\def\arraystretch{1.6}
+\caption{
+{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
+  \begin{tabular}{|c|l|l|c|c|}
+    \hline
+  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity mechanism}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
+    % \hline
+    % \textbf{Inactive Modes} & \textbf{Description}\\
+    \cline{2-5}
+    {} & \multirow{1}{*} {\bf{ On compartment}} & \multirow{1}{*} {\bf{On vesicle}}  & \textbf{\textbf{Least}} & \textbf{Highest}\\
+    %\hhline{~--}
+    \hline
+E. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
+C. & None & Boolean function & 3-connected & 3-connected \\  \hline
+F. & Boolean function & Pairing inhibition & 4-connected & 4-connected \\ \hline
+D. & None & Pairing inhibition & No graph & No graph \\ \hline
+B. & Boolean function & None & No graph & No graph \\ \hline
+A. & None & None & No graph & No graph \\ \hline
+G. & Boolean function & Every edge is distict & 3-connected & 3-connected \\ \hline
+H. & Self edges are allowed & Boolean funcion & No-idea & No-idea \\ \hline
+
+  \end{tabular}
+\label{table1}
+\end{table}
 

### 2017-06-14 biology.py

@@ -51,21 +51,23 @@ E = [ edge[i][j][q] for i in range(N) for j in range(N) for q in range(Q) if i !
 
 # Un_Skolemized dumped edges and reachability.
 dump = [ [ [Bool ("d_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
-DX = [ dump[i][j][q] for i in range(N) for j in range(N) for k in range(Q) if i != j ]
+#DX = [ dump[i][j][q] for i in range(N) for j in range(N) for k in range(Q) if i != j ]
 
 #print DX
 #print len(DX)
 
 r1 = [ [Bool ("r1_{}_{}".format(i,j)) for j in range(N)] for i in range(N)]
-RX = [ r1[i][j] for i in range(N) for j in range(N) if i != j ]
+#RX = [ r1[i][j] for i in range(N) for j in range(N) if i != j ]
 
 #print RX
 #print len(RX)
 
-funE = len(E) + len(DX) + len(RX)
+funE = len(E)
+#funE = len(E) + len(DX) + len(RX)
 lenE = funE + 1
 
-QVars = E + RX + DX
+QVars = E
+#QVars = E + RX + DX
 print QVars
 
 #print funE
@@ -80,17 +82,17 @@ nodeSort = [BoolSort() for x in range(lenE)]
 
 #print nodeSort 
 # Skolemized presence edge
-fnode = [ [Function ("fn_{}_{}".format(i,k), *nodeSort) for k in range(M)] for i in range(N)]
+#fnode = [ [Function ("fn_{}_{}".format(i,k), *nodeSort) for k in range(M)] for i in range(N)]
 node = [ [Bool ("n_{}_{}".format(i,k)) for k in range(M)] for i in range(N)]
 
-for i in range(N):
-    for k in range(M):
-        s = []
-        nxx = fnode[i][k] 
-        for t in QVars:
-            s.append( t )
-        node[i][k] = nxx( s )
-
+#for i in range(N):
+#    for k in range(M):
+#        s = []
+#        nxx = fnode[i][k] 
+#        for t in QVars:
+#            s.append( t )
+#        node[i][k] = nxx( s )
+#
 # Skolemized dumped edges
 #fdump = [ [ [Function ("fd_{}_{}_{}".format(i,j,q), *nodeSort) for q in range(Q)] for j in range(N)] for i in range(N)]
 #for i in range(N):
@@ -104,73 +106,73 @@ for i in range(N):
 #
 
 # Skolemized Active node 
[…]

### 2017-06-16 paper/experiments.tex
local changes

--- 2017-06-13 paper/experiments.tex
@@
 \end{itemize}
+%
+Our tool allows user to choose a model and the size of
+the network.
+%
+It builds the needed constraints and applies $\zthree$
+on the constraints.
+%
+Our tool also translates the model found by $\zthree$
+into a vesicle traffic system and presents a visual
+output to the user.
 
@@
 \input{tbl-qf-graph}
-In table~\ref{tbl:qf-results}
+In table~\ref{tab:qf-graph}, we present the running times
+for the search of vesicle traffic systems of sizes 2 to 10
+that satisfies the model variants.
+%
+The experiments were done on a machine with ... processor 
+and ... RAM.
+%
 
-\todo{Make table for all sizes and variants of the tool}
+%
+$\zthree$ was able to solve the constraints up to 10
+nodes.
+%
 

### 2017-06-16 paper/encoding.tex

@@
 In this section, we will present our encoding of the search problem.
+Every variable is a Boolean bit, for example, n(0,1) represents node 0 with type 1 molecule present.
+Assignment to the Boolean variable n(0,1) to True will mean that at node 0 type 1 molecule is present.
 
@@
 \begin{enumerate}
+
 \item edge = e(i,j,q)      
-      There is an qth edge between node i and j.
+      we will assign e(i,j,q) for a qth edge between node i and j.
 
 \item dump = d(i,j,q)
-       drop edge(i,j,q) from the graph.
+      to represent drop of edge(i,j,q) from the graph we will use d(i,j,q).
 
@@
 \subsubsection{Regulation on nodes and edges}
-Regulation of a model is based on the kind of the model under consideration.
-for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by pairing inhibition.
+Regulation of the molecules is based on the kind of the model under consideration.
+For example, model 1 (-V 1) has two different arbitrary Boolean functions dictating the activity of the molecules on edge and nodes.
+For variation 3 (-V 3) activity on edge is driven by pairing inhibition.
 
-We have build constraints A0, A1 for these two regulations. \newline
+We use two Boolean variables A0 and A1 to build these two constraints. \newline
 
-A0: No regulation on nodes.
+A0: No regulation on nodes i.e all the present molecules on the nodes are active.
 \[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]
 
-A0: Boolean regulation on nodes. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
+A0: Boolean regulation on nodes. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
 \[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
 
-A1: No regulation on edges.
+A1: No regulation on edges i.e all the present molecules on the edges are active.
 \[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]
 
-A1: Boolean regulation on edges. Activity of a molecule k on a node is defined as a Boolean function of presence of other molecule present on that node.
+A1: Boolean regulation on edges. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
 \[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]
 
-A1: Pairing inhibition. Inhibition of the edges are driven by the pairing matrix.
+A1: Pairing inhibition. The activity of the molecules is defined by inhibition by other molecules based on the pairing matrix. 
 \[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]
@@
 \subsubsection{Constraints on the structure of the edges, nodes and pairing matrix}
+A few additional constraints are required on the nodes, edges and pairing matrix to set up the essential conditions. We use Boolean variables C0-C5 to build all these constraints.
 
@@
 \subsubsection{Constraints on presence and activity of the molecule}
-Few additional constrints are required on the molesules presence and activity. \newline
+Few additional constraints that are required for the molecules presence and activity is build using F0 and F1. \newline
 
@@
 \subsubsection{Constraints for stability condition}
-The whole cell should be in stable condition i.e global flow of the molecule is balanced at every point.
-Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.
+The whole cell should be in stable condition i.e flow of the molecule is balanced at every point and globally.
+Each molecule leaving its source node on a vesicle should come back in a cycle.
+Boolean variable F3 and F2 are used to model these constraints.
 
-\bf{Reachability definition and stability condition}
-We have encoded this requiremnt by using reachability definition. 
-If molecule is active on an edge then it should be present on the edge. \newline
+\textbf {Reachability definition and stability condition.}
+We have encoded stable condition by using reachability definition. \newline
 
-F3: stability condition. Source node is reachable by target node with that molecule present in p steps.
+F3: Stability condition. For every leaving molecule, the source node is reachable from the target node with that molecule present, in maximum p steps.
 
@@
 F2: Reachability definition.
+Node j is reachable from node i with kth molecule present in maximum p steps if either there is a direct edge between i-j with that molecule present or there is a direct edge between $i^{\prime \prime}$ $(i != i^{\prime \prime})$ and j with kth molecule present on that edge and $i^{\prime \prime}$ are reachable from i in p steps.
+
 \[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \supset (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]
@@
 \begin{enumerate}
-\item  A \textbf{Pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
+\item  A \textbf{pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
+\item \textbf{regulatory mechanisms} on the edges and nodes (possibly distinct) which regulates molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
 \end{enumerate}
 
-F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active, and have a non-zero entry in the pairing matrix.
+Boolean variable F4 and F5 are used to model these constraints.
+
+F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active and have a non-zero entry in the pairing matrix.
 
@@
 \subsubsection{Graph connectivity constraints}
-To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph.
+To check the whether that n connected is a necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have an n connected satisfying graph.
 We can go down or up using -C \_ option.
@@
 
-D4: New reachability definition for grph connectedness: dReachable. Node i,j are reachable either if there is a direct edge and its not dropped. 
-Or there is an node i' such that, there is a direct edge between i,i' which is not dropped and i' and j is dReachable.
+D4: New reachability definition for graph connectedness: dReachable.
+Node i,j are reachable either if there is a direct edge and its not dropped or there is an node $i^{\prime}$ such that, there is a direct edge between i, $i^{\prime}$ which is not dropped and $i^{\prime}$ and j is dReachable.
 
 \[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \supset r^{\prime}(i,j)  \]
+
+\subsection{Creating a solver and solving these constraints}
+We will create a solver and add these build formula using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
+
+\begin{figure}[ht]
+%\vspace{-3mm}
+\begin{verbatim}
+# Create a solver
+s = Solver()
+# Add these formulas to it.
+s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)
+
+# Check for the satisfiability assignment.
+print s.check()   
+\end{verbatim}
+\caption{Solving for these constraints.}
+\label{code:motivate}
+\end{figure}
 

### 2017-06-16 paper/experiments.tex

--- 2017-06-14 paper/experiments.tex
@@
 \end{enumerate}
+%
+Our tool allows user to choose a model and the size of
+the network.
+%
+It builds the needed constraints and applies $\zthree$
+on the constraints.
+%
+Our tool also translates the model found by $\zthree$
+into a vesicle traffic system and presents a visual
+output to the user.
 
@@
 \input{tbl-qf-graph}
+
+In table~\ref{tab:qf-graph}, we present the running times
+for the search of vesicle traffic systems of sizes 2 to 10
+that satisfies the model variants.
+%
+The experiments were done on a machine with ... processor 
+and ... RAM.
+%
+
+%
+$\zthree$ was able to solve the constraints up to 10
+nodes.
+%
+
 In table~\ref{tbl:qf-results} 
@@
 
-\todo{Make table for all sizes and variants of the tool}
-
 %--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

### 2017-06-16 paper/bio.tex
added

--- 2017-06-16 paper/experiments.tex
@@
-We have implemented the encoding of the constraints
-in the python interface of $\zthree$.
-%
-Our implementation supports several versions of the
-models of vesicle traffic systems.
-\todo{describe the variations}
+Again about two pages long
+
 \begin{itemize}
-\item 
+\item \mukund{Detailed BIO motivation}
+\item \srivas{Detailed BIO to Graph problem}
 \end{itemize}
-%
-Our tool allows user to choose a model and the size of
-the network.
-%
-It builds the needed constraints and applies $\zthree$
-on the constraints.
-%
-Our tool also translates the model found by $\zthree$
-into a vesicle traffic system and presents a visual
-output to the user.
 
-We have applied the tool for the above variations
-for searching the vesicle traffic systems that satisfies
-their corresponding properties.
-%
-\input{tbl-qf-graph}
-In table~\ref{tab:qf-graph}, we present the running times
-for the search of vesicle traffic systems of sizes 2 to 10
-that satisfies the model variants.
-%
-The experiments were done on a machine with ... processor 
-and ... RAM.
-%
+The following terms must be defined  in this section
 
-%
-$\zthree$ was able to solve the constraints up to 10
-nodes.
-%
+\begin{itemize}
+\item 3 connected
+\item  ....
+\end{itemize}
 

### 2017-06-16 paper/abstract.tex
second half of the intro

@@
 possible networks for various combinations of those properties? In this
-paper, we present SAT/QBF encodings of the properties over vesicle traffic
+paper, we present novel SAT encodings of the properties over vesicle traffic
 systems and a tool that searches for the networks that satisfies the
-properties using SAT/QBF solvers. In our experiments, we show that our tool
+properties using SAT solvers. In our experiments, we show that our tool
 can search for networks of sizes that are considered to be relevant by

### 2017-06-16 paper/intro.tex
added
second half of the intro

@@
+Total two pages
+
+\begin{itemize}
+\item \mukund{BIO motivation ( 1 paragraph ) }
+
+\item \srivas{BIO to Graph problem ( a couple of paragraph) }
+
+\item \srivas{Graph to previous encoding}
+
+\end{itemize}
+
+% \noindent
+
 % What is vesicle traffic systems
+
+vesicle traffic systems(VTS)
 
@@
 
+In this paper, we have developed a novel SAT encoding for
+searching a VTS that satisfy the given properties.
+%
+We improved the encoding of some of the conditions for VTSs.
+%
+In the earlier implementation, reachability was encoded as
+by enumeration of paths.
+%
+In our encoding, we have recursively defined the reachability condition
+such that that we avoid exponential enumeration.
+%
+We have also encoded $k$-connectivity in the similar fashion and
+avoided a blowup in the formula size.
+%
+
+We have implemented the encoding using Z3~\cite{z3} python API and searched for
+VTS satisfying various properties upto size \ankit{....} nodes as compare
+earlier tool that could only search graph upto size 6 nodes.
+%
+Since most VTSs in the cells are less than \ankit{....} nodes,
+our tool will be useful for biologists to study VTSs.
+%
+Furthermore, our encoding supports several variations of
+the conditions.
+
+The following are the contributions of this work:
+\begin{itemize}
+\item We have added novel encoding reachability and 3-4 connectivity
+\item Direct encoding into the SAT solver
+\item A user friendly and scalable tool based on well known SMT solver Z3
+\end{itemize}
+
 %--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

### 2017-06-16 paper/intro.tex
fixed

@@
 %
-In the earlier implementation, reachability was encoded as
-by enumeration of paths.
+In the earlier implementation, reachability was encoded by
+enumeration of paths.
 %
 In our encoding, we have recursively defined the reachability condition
-such that that we avoid exponential enumeration.
+such that that we avoid the exponential enumeration.
 %

### 2017-06-17 paper/related.tex
added
related-work

--- 2017-06-16 paper/bio.tex
@@
-Again about two pages long
-
-\begin{itemize}
-\item \mukund{Detailed BIO motivation}
-\item \srivas{Detailed BIO to Graph problem}
-\end{itemize}
-
-The following terms must be defined  in this section
-
-\begin{itemize}
-\item 3 connected
-\item  ....
-\end{itemize}
+\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
+\begin{enumerate}
+\item Reasoning over Biological Networks using Maximum Satisfiability.
+\item BioGraphE: high-performance bionetwork analysis using the Biological Graph Environment.
+\item Generalized k-ary tanglegrams on level graphs: A satisfiability-based approach and its evaluation.
+\item Faster than classical quantum algorithm for dense formulas of exact
+satisfiability and occupation problems.
+\item Model Checking Gene Regulatory Networks.
+\item SMT-Based Analysis of Biological Computation.
+\item A SAT-based algorithm for finding attractors in synchronous Boolean networks.
+\item ILP/SMT-Based Method for Design of Boolean Networks Based on Singleton Attractors.
+\item Efficient parameter search for qualitative models of regulatory networks using symbolic model checking.
+\end{enumerate}
+Who will do the related work?
 

### 2017-06-17 paper/experiments.tex
related-work

@@
 In table~\ref{tbl:qf-results} 
-\b PARTIAL ...
+\b PARTIAL .... Form change is proposed in the table and table will consists of constraints used in the model rather than the model itself.
 
@@
 A. & None & None & No graph & No graph \\ \hline
-G. & Boolean function & Every edge is distict & 3-connected & 3-connected \\ \hline
-H. & Self edges are allowed & Boolean funcion & No-idea & No-idea \\ \hline
+G. & Boolean function & Every edge is distinct & 3-connected & 3-connected \\ \hline
+H. & Self edges are allowed & Boolean function & No-idea & No-idea \\ \hline
 

### 2017-06-18 paper/intro.tex
fix

@@
 We have implemented the encoding using Z3~\cite{z3} python API and searched for
-VTS satisfying various properties upto size \ankit{....} nodes as compare
-earlier tool that could only search graph upto size 6 nodes.
+VTS satisfying various properties upto size \ankit{15} nodes as compare
+earlier tool that could only search graph upto size 8 nodes.
 %
-Since most VTSs in the cells are less than \ankit{....} nodes,
+Since most VTSs in the cells are less than \ankit{10} nodes,
 our tool will be useful for biologists to study VTSs.

### 2017-06-18 paper/related.tex
fix

@@
 \ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
+
+\textbf{SAT, Bio and Graph}
 \begin{enumerate}
@@
 \item Generalized k-ary tanglegrams on level graphs: A satisfiability-based approach and its evaluation.
-\item Faster than classical quantum algorithm for dense formulas of exact
-satisfiability and occupation problems.
-\item Model Checking Gene Regulatory Networks.
 \item SMT-Based Analysis of Biological Computation.
@@
 \item ILP/SMT-Based Method for Design of Boolean Networks Based on Singleton Attractors.
+\item Exact DFA Identification Using SAT Solvers
+\item Timing Robustness in the Budding and Fission Yeast Cell Cycles.
+\end{enumerate}
+
+\textbf{GNR and SAT}
+\begin{enumerate}
+\item Model Checking Gene Regulatory Networks.
+\item Inference of Boolean Networks from Gene Interaction Graphs Using a SAT Solver
 \item Efficient parameter search for qualitative models of regulatory networks using symbolic model checking.
 \end{enumerate}
+
 Who will do the related work?

### 2017-06-19 paper/encoding.tex
added
update

@@
+\subsection{Model}
+
+\begin{df}
+  A VTS $G$ consists of ...... most general model 
+\end{df}
+
+Variants of the model : restrictions...
+
+formal definition of the properties in the terms of VTS.
+
+State the SAT problem
+
+\subsection{Boolean satisfiability of the problem}
+
 In this section, we will present our encoding of the search problem.
@@
 
-We use two Boolean variables A0 and A1 to build these two constraints. \newline
+We use two Boolean variables A\_* to build these two constraints. \newline
 
-A0: No regulation on nodes i.e all the present molecules on the nodes are active.
+A\_nn: No regulation on nodes i.e all the present molecules on the nodes are active.
 \[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]
 
-A0: Boolean regulation on nodes. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
+A\_nb: Boolean regulation on nodes. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
 \[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
 
-A1: No regulation on edges i.e all the present molecules on the edges are active.
+A\_en: No regulation on edges i.e all the present molecules on the edges are active.
 \[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]
 
-A1: Boolean regulation on edges. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
+A\_eb: Boolean regulation on edges. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
 \[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]
 
-A1: Pairing inhibition. The activity of the molecules is defined by inhibition by other molecules based on the pairing matrix. 
+A\_ep: Pairing inhibition. The activity of the molecules is defined by inhibition by other molecules based on the pairing matrix. 
 \[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]

### 2017-06-19 paper/encoding.tex
changes

--- 2017-06-16 paper/encoding.tex
@@
-In this section, we will present our encoding of the search problem.
+In this section, we will formally define VTSs as a labelled graph
+and the conditions on the graphs that are discussed in the previous
+section.
+Subsequently, we will present the SAT encoding of the search problems
+for the graphs that satisfies the conditions.
+
+\subsection{Model}
+
+We model VTSs as labelled directed graphs.
+The graph labels both edges and labels with sets of molecules to denote
+the set of molecules present in the node.
+The graph is formally defined as follows.
+
+\begin{df}
+  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pair,\edgef,\nodef)$, where
+  \begin{itemize}
+  \item $\nodes$ is a set of nodes representing compartments in the VTS,
+  \item $\mols$ is the set of molecules flowing in the network, 
+  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes  
+  \item $ \nodes \times \powerset{\mols} \times \nodes \subseteq \edges$ is the set of edges
+    with molecule sets as labels
+  \item $\pair : \mols \times \mols$ is pairing relating
+  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
+  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges
+  \end{itemize}
+\end{df}
+$\pair$, $\nodef$, and $\edgef$ defines activity of a molecule on nodes and edges.
+A molecule $k$ is {\em active} at node $n$ if $\nodef(k,\nlabel(n))$ is true.
+A molecule $k$ is {\em active} at edges $(n,M',n')$ if $\edgef(k,M')$ is true.
+
+Variants of the model : restrictions...
+
+formal definition of the properties in the terms of VTS.
+
+State the SAT problem
+
+\subsection{Boolean satisfiability of the problem}
+
 Every variable is a Boolean bit, for example, n(0,1) represents node 0 with type 1 molecule present.

### 2017-06-20 paper/encoding.tex

@@
   \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes  
-  \item $ \nodes \times \powerset{\mols} \times \nodes \subseteq \edges$ is the set of edges
+  \item $ \nodes \times (\powerset{\mols}-\emptyset) \times \nodes \subseteq \edges$ is the set of edges
     with molecule sets as labels
@@
 \end{df}
-$\pair$, $\nodef$, and $\edgef$ defines activity of a molecule on nodes and edges.
-A molecule $k$ is {\em active} at node $n$ if $\nodef(k,\nlabel(n))$ is true.
-A molecule $k$ is {\em active} at edges $(n,M',n')$ if $\edgef(k,M')$ is true.
+$\pair$ defines which molecules can fuse with which molecules. 
+$\nodef$ and $\edgef$ are used to define activity of molecules on nodes and edges.
+A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and $\nodef(k,\nlabel(n))$ is true.
+A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and $\edgef(k,M')$ is true.
 
-Variants of the model : restrictions...
+We will also consider several variations of the model.
+%
+For example, unique edge between two nodes, activity of molecules is not constrained by
+$\nodef$ and $\edgef$, and \ashu{other variations?}.
+%
 
-formal definition of the properties in the terms of VTS.
+A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
+such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
+%
+For a molecule $m \in M$,
+An {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
+such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
+each $ 0 < i < \ell$.
+%
+A node $n'$ is {\em reachable} from node $n$ in $G$ if there is a path
+$n,...,n'$ in $G$.
+%
+A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
+$m$-path $n,...,n'$ in $G$.
+%
+We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
+$n$ is $m$-reachable from $n'$.
+%
+We call $G$ {\em connected} if for each $n,n' \in \nodes$,
+$n'$ is reachable from $n$ in $G$.
+%
+We call $G$ $k$-connected if for each $E' \subseteq \edges$ and $|E'| < k$,
+$(\nodes,\mols,\edges-E',\nlabel,\pair,\edgef,\nodef)$ is connected.
+%
+An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
+if
 

### 2017-06-20 paper/experiments.tex

--- 2017-06-16 paper/experiments.tex
@@
 %
-$\zthree$ was able to solve the constraints up to 10
+$\zthree$ was able to solve the constraints up to 15
 nodes.
@@
 In table~\ref{tbl:qf-results}
-\b PARTIAL ...
 
@@
 {\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
-  \begin{tabular}{|c|l|l|c|c|}
+  \begin{tabular}{|c|c|c|c|c|}
     \hline
-  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity mechanism}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
+  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity constraint}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
     % \hline
@@
     \hline
-E. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
-C. & None & Boolean function & 3-connected & 3-connected \\  \hline
-F. & Boolean function & Pairing inhibition & 4-connected & 4-connected \\ \hline
-D. & None & Pairing inhibition & No graph & No graph \\ \hline
-B. & Boolean function & None & No graph & No graph \\ \hline
-A. & None & None & No graph & No graph \\ \hline
-G. & Boolean function & Every edge is distict & 3-connected & 3-connected \\ \hline
-H. & Self edges are allowed & Boolean funcion & No-idea & No-idea \\ \hline
+E. & A\_nb & A\_eb & 2-connected & 3-connected \\ \hline
+C. & A\_nn & A\_eb & 3-connected & 3-connected \\  \hline
+F. & A\_nb & A\_ep & 4-connected & 4-connected \\ \hline
+D. & A\_nn & A\_ep & No graph & No graph \\ \hline
+B. & A\_nb & A\_en & No graph & No graph \\ \hline
+A. & A\_nn & A\_en & No graph & No graph \\ \hline
+G. & A\_nb & A\_eb + C\_ed & 3-connected & 3-connected \\ \hline
+H. & A\_nb & A\_eb + C\_es & No-idea & No-idea \\ \hline
 
+% C_es :Self edges are allowed
+% C_ed : Every edge is distinct 
   \end{tabular}

### 2017-06-20 paper/experiments.tex
exp

@@
 in the python interface of $\zthree$.
+Basic idea is to constraint the variables such that vesicular transport rules are respected and using constraints (D0-D5) connect this system with the connectivity of the underlying structure (graph).
+We are interested in both least connectivity that is required for a vesicular transport version to work and least connectivity that guarantees that vesicular transport system with that connectivity will always satisfies the rules.
+
+% Whether a valid vesicular transport system is of certain connectiviity.   
+After creating the formula we ship them directly to the solver without any additional overhead.
+Besides using the default Z3 solvers we have used for these experiments \ankit{Z3, picoSAT, Lingeling}.
+The performance of Z3 was ...
 %
 Our implementation supports several versions of the
-models of vesicle traffic systems.
+models of vesicle traffic systems listed in Table 2. Starting from most basic model  \Ankit{add...}
 \todo{describe the variations}
@@
 Our tool allows user to choose a model and the size of
-the network.
+the network besides other parameters like connectivity and number of parallel edges. 
 %
-It builds the needed constraints and applies $\zthree$
-on the constraints.
+Our tool uses Z3 python interface to build the needed constraints and applies $\zthree$
+on the constraints. \Ankit{In other solver variations ...}
 %
@@
 output to the user.
+The graph provides an overview of the vesicle transport system with directed labeled edges and nodes providing the complete information about the shown graph.
+The output graph will satisfy the underlying rules of the system, so it is a valid vesicle transport network.
 
-We have applied the tool for the above variations
-for searching the vesicle traffic systems that satisfies
-their corresponding properties.
+We have applied the tool for the above variations for searching the vesicle traffic systems that satisfies
+their corresponding properties. In case the solver finds an satisfying assignment to the generated formula i
 

### 2017-06-20 paper/experiments.tex
expmt

@@
-We have implemented the encoding of the constraints
-in the python interface of $\zthree$.
-Basic idea is to constraint the variables such that vesicular transport rules are respected and using constraints (D0-D5) connect this system with the connectivity of the underlying structure (graph).
-We are interested in both least connectivity that is required for a vesicular transport version to work and least connectivity that guarantees that vesicular transport system with that connectivity will always satisfies the rules.
+Given a system that follows the VTS, we are interested in its connectivity (graph) property.
+We have implemented the encoding of the constraints in the python interface of $\zthree$.
+The basic idea is to constraint the variables such that vesicular transport rules are respected and using constraints (D0-D5) reason about the connectivity of the underlying structure (graph).
+We are interested in both least connectivity requirement (LRC) and least guarantee connectivity (LGC).
+%LCR, that is required for a vesicular transport version to work and least connectivity that guarantees that vesicular transport system with that connectivity will always satisfies the rules.
 
 % Whether a valid vesicular transport system is of certain connectiviity.   
-After creating the formula we ship them directly to the solver without any additional overhead.
-Besides using the default Z3 solvers we have used for these experiments \ankit{Z3, picoSAT, Lingeling}.
-The performance of Z3 was ...
+%negation of the property .... STATE THE MEANING OF RESULT.
+
+%Besides using the default Z3 solvers we have used for these experiments \ankit{Z3, picoSAT, Lingeling}. The performance of Z3 was ...
 %
-Our implementation supports several versions of the
-models of vesicle traffic systems listed in Table 2. Starting from most basic model  \Ankit{add...}
-\todo{describe the variations}
+Our implementation supports several versions of the models of vesicle traffic systems listed in Table 2.
+Starting from most basic version (A) where every present molecule is considered to be active.
+Other cases includes different combinations of constraints on the activity on nodes and edges.
+Most general restriction is activity of the molecule is dependent on the other molecule present on the node (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
+In very special case (E,F,G,H) activity of the molecules on the edges is dictated by pairing matrix, we call this process ``pairing inhibition".
+
+% DIVIDE INTO COLUMNS and TALK ABOUT A/1 or A/0.
+%\todo{describe the variations}
 
@@
 %
-Our tool allows user to choose a model and the size of
-the network besides other parameters like connectivity and number of parallel edges. 
+We have applied the tool for the above variations for searching the vesicle traffic systems that satisfies
+their corresponding properties.
+Our tool allows user to choose a model and the size of the network besides other parameters like connectivity and number of parallel edges.
+Our tool uses Z3 python interface to build the needed constraints and applies $\zthree$ on the constraints.
+
+After creating the formula using different Boolean variables we ship them directly to the solver.
+In case of a satisfying (SAT) assignment of the added constraints the Z3 theorem prover gives a model with the variable assignment.
+In case no possible satisfying assignment the solver returns UNSAT.
 %
-Our tool uses Z3 python interface to build the needed constraints and applies $\zthree$
-on the constraints. \Ankit{In other solver variations ...}
-%
-Our tool also translates the model found by $\zthree$
-into a vesicle traffic system and presents a visual
+% \Ankit{In other solver variations ...}
+Our tool also translates the model found by $\zthree$ into a vesicle traffic system and presents a visual
 output to the user.
@@
 The output graph will satisfy the underlying rules of the system, so it is a valid vesicle transport network.
-
-We have applied the tool for the above variations for searching the vesicle traffic systems that satisfies
-their corresponding properties. In case the solver finds an satisfying assignment to the generated formula i
+Dashed lines are used in the resultant visual network output to specify which edges edges are dropped to make the graph disconnected specifying the connectivity of the graph.
 

### 2017-06-20 paper/experiments.tex
expmt

@@
 
-In table~\ref{tab:qf-graph}, we present the running times
-for the search of vesicle traffic systems of sizes 2 to 10
-that satisfies the model variants.
-%
+In table~\ref{tab:qf-graph}, we present the running times for the search of vesicle traffic systems of sizes 2 to 10 that satisfies the model variants.
+Formula for N = 10 returns in 45 mins with a SAT result.
+In CBMC N = 10 results in OUT OF MEMORY.
+Hence with use of this novel encoding we are able to scale the system to much larger compartmentalized systems especially eukaryotics cells with ten compartments.
+This additional cushion of scalability can provide us leverage to ask for more questions that were not previously possible for example what is the minimum number of molecules required to satisfy the vesicular traffic system in eukaryotes.
+
+% REQUIRE COMPARISION WITH CBMC RUN TIME ?
 The experiments were done on a machine with ... processor 
@@
 %
-$\zthree$ was able to solve the constraints up to 15
-nodes.
+$\zthree$ was able to solve the constraints up to 15 nodes.
 %

### 2017-06-21 paper/encoding.tex
added text

@@
 \begin{df}
-  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pair,\edgef,\nodef)$, where
+  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$, where
   \begin{itemize}
@@
     with molecule sets as labels
-  \item $\pair : \mols \times \mols$ is pairing relating
+  \item $\pairs : \mols \times \mols$ is pairing relating
   \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
@@
 \end{df}
-$\pair$ defines which molecules can fuse with which molecules. 
-$\nodef$ and $\edgef$ are used to define activity of molecules on nodes and edges.
-A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and $\nodef(k,\nlabel(n))$ is true.
-A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and $\edgef(k,M')$ is true.
+$\pairs$ defines which molecules can fuse with which molecules.
+%
+Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
+%
+$\nodef$ and $\edgef$ are used to define activity of molecules on
+nodes and edges.
+%
+A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
+$\nodef(k,\nlabel(n))$ is true.
+%
+A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
+$\edgef(k,M')$ is true.
 
@@
 %
-For example, unique edge between two nodes, activity of molecules is not constrained by
-$\nodef$ and $\edgef$, and \ashu{other variations?}.
+For example, unique edge between two nodes, activity of molecules is
+not constrained by $\nodef$ and $\edgef$, and \ashu{other
+variations?}.
 %
@@
 %
+An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
+if there are molecules $m,m' \in \mols$ such that $m$ is active in
+$(n,M',n')$, $m'$ is active in $n'$, and $(m,m') \in \pairs$.
+%
+We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
+with non-empty fusing molecules $M'' \subseteq M'$
+and $\pairs(M'')$ are not active in any other node.
+
+%
 We call $G$ {\em connected} if for each $n,n' \in \nodes$,
@@
 We call $G$ $k$-connected if for each $E' \subseteq \edges$ and $|E'| < k$,
-$(\nodes,\mols,\edges-E',\nlabel,\pair,\edgef,\nodef)$ is connected.
+VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
+
+\paragraph{Search problem}
+
+Based upon earlier discussion, we need to answer the following search
+question for ......\ashu{match with the earlier text}
+For a given $k$, size $\nu$, and molecule number $\mu$,
+we are searching for stable and well-fused VTS
+$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
+$|\nodes| = \nu$, $|\mols = \mu|$, and
+$G$ is not $k$-connected.
+
+\subsection{Boolean satisfiability of the search problem}
+
+We translate the search problem into a Boolean satisfiability
+problem and use SAT solvers to find the satisfying VTSs.
 %
-An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
-if
+We will first present the variables used to encode the
+VTSs and the properties.
+%
+Afterwards, we will present the formulas corresponding to the
+properties.
 
-State the SAT problem
+\subsubsection{Variables for VTS description}
+%
+We assume that size of the graph is $\nu$ and number of molecules is
+$\mu$.
+%
+Furthermore, we also limit the maximum number $\pi$ of edges present
+between two nodes.
+%
+Here, we list the vector of Boolean variables and uninterpreted function symbols
+that encode the VTSs.
+\begin{enumerate}
 
-\subsection{Boolean satisfiability of the problem}
+\item $n_{i,m}$ indicates if $m \in \nlabel(i)$
+\item $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
+\item $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains molecule $m$.
 
-Every variable is a Boolean bit, for example, n(0,1) represents node 0 with type 1 molecule present.
-Assignment to the Boolean variable n(0,1) to True will mean that at node 0 type 1 molecule is present.
+\item $p_{k,k'}$ indicates if $(m,m') \in \pairs$
+\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
+encoding $\nodef(m)$ map
+\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
+encoding $\edgef(m)$ map
+\end{enumerate}
 
-\subsection{Network description}
+We also have auxiliary variables that will help us encode the properties 
+\begin{enumerate}
+\item dump = d{i,j,q}
+      to represent drop of edge{i,j,q} from the graph we will use d{i,j,q}.
+
+\item active\_node = a{i,k} 
+      kth molecule is active on the node i.
+
+\item presence\_edge = e{i,j,q,k}
+      There is an qth edge between node i and j with kth molecule present.
+
+\item active\_edge = b{i,j,q,k}
+      There is an qth edge between node i and j with kth molecule active.
+
+\item reachability = r{i,j,k,z}
+      Node i and j are reachable with kth molecule present in z steps.
+
+\end{enumerate}
+
+Every variable is a Boolean bit, for example, n(0,1) represents node 0
+with type 1 molecule present. Assignment to the Boolean variable
+n(0,1) to True will mean that at node 0 type 1 molecule is present.
 

### 2017-06-22 paper/experiments.tex
added new file in running-file for exp

@@
 %
-Our implementation supports several versions of the models of vesicle traffic systems listed in Table 2.
-Starting from most basic version (A) where every present molecule is considered to be active.
+Our implementation supports several versions of the models of vesicle traffic systems listed in below.
+Starting from most basic version (A) where every present molecule is consider to be active.
 Other cases includes different combinations of constraints on the activity on nodes and edges.
-Most general restriction is activity of the molecule is dependent on the other molecule present on the node (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
+Most general restriction is activity of the molecule is dependent on the other molecule present on the node/edge (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
 In very special case (E,F,G,H) activity of the molecules on the edges is dictated by pairing matrix, we call this process ``pairing inhibition".
@@
 their corresponding properties.
-Our tool allows user to choose a model and the size of the network besides other parameters like connectivity and number of parallel edges.
-Our tool uses Z3 python interface to build the needed constraints and applies $\zthree$ on the constraints.
+Our tool allows the user to choose a model and the size of the network besides other parameters like connectivity and number of parallel edges.
+It uses Z3 Python interface to build the needed constraints and applies $\zthree$ on the constraints.
 
 After creating the formula using different Boolean variables we ship them directly to the solver.
-In case of a satisfying (SAT) assignment of the added constraints the Z3 theorem prover gives a model with the variable assignment.
+Searching is reduced to SAT solving the resultant formula.
+In the case of a satisfying (SAT) assignment of the added constraints, the Z3 theorem prover gives a model with the variable assignment.
 In case no possible satisfying assignment the solver returns UNSAT.
@@
 The output graph will satisfy the underlying rules of the system, so it is a valid vesicle transport network.
-Dashed lines are used in the resultant visual network output to specify which edges edges are dropped to make the graph disconnected specifying the connectivity of the graph.
+Dashed lines are used in the resultant visual network output to specify which edges are dropped to make the graph disconnected specifying the connectivity of the graph.
+For example if removing two edges disconnects the graph; the graph is not 3-connected.
 
@@
 In table~\ref{tab:qf-graph}, we present the running times for the search of vesicle traffic systems of sizes 2 to 10 that satisfies the model variants.
-Formula for N = 10 returns in 45 mins with a SAT result.
-In CBMC N = 10 results in OUT OF MEMORY.
-Hence with use of this novel encoding we are able to scale the system to much larger compartmentalized systems especially eukaryotics cells with ten compartments.
+The formula for N = 10 returns in approximately 45 mins with a SAT result.
+The previous encoding with CBMC was unable to handle this case for N = 10 [Refer PLOSONE paper] for variation 2 and SAT solving results in OUT OF MEMORY.
+Hence with the use of this novel encoding, we are able to scale the system to much larger compartmentalized systems especially eukaryotic cells with ten compartments.
 This additional cushion of scalability can provide us leverage to ask for more questions that were not previously possible for example what is the minimum number of molecules required to satisfy the vesicular traffic system in eukaryotes.

### 2017-06-22 file1.py

@@ -1,0 +1,723 @@
+#!/usr/bin/python
+
+from z3 import *
+import argparse
+import time
+
+#----------------------------------------------------
+# input parsing
+# input number of nodes and molecules
+parser = argparse.ArgumentParser(description='Auto testing for TARA')
+parser.add_argument("-M","--mols", type=int, default=4, help = "number of molecules")
+parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes")
+parser.add_argument("-Q","--pedges", type=int, default=1, help = "max no.of parallel edges btw two nodes")
+parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
+parser.add_argument("-C","--connected", type=int, default=3, help = "graph connectivity want to check")
+parser.add_argument("-E","--edges", type=int, default=3, help = "graph connectivity want to check")
+
+args = parser.parse_args()
+
+M = args.mols
+N = args.nodes
+Q = args.pedges
+V = args.variation
+C = args.connected
+
+bag = []
+bag.append ('1. Boolean function on nodes and Boolean function on the edges.') 
+bag.append ('2. Only Boolean function on the edges.') 
+bag.append ('3. Boolean function on nodes and SNARE-SNARE inhibition on edges.')
+bag.append ('4. Only SNARE-SNARE inhibition on edges.')
+bag.append ('5. Only Boolean function on nodes.')
+bag.append ('6. No regulation at all.')
+
+for i in range(6):
+    if V == i + 1:
+        print ' '
+        print 'Default/choosen vesicular traffic system is regulated by ...',
+        print bag[i]
+        print ' '
+        print 'Use -V option to change the regulated variation.' 
+        for i in bag:
+            print i 
+        print ' '
+        break
+
+#----------------------------------------------------
+# Constraint generation 
+edge = [ [ [ Bool ("e_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+
+dump = [ [ [Bool ("d_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+
+r1 = [ [Bool ("r1_{}_{}".format(i,j)) for j in range(N)] for i in range(N)]
+
[…]

### 2017-06-22 paper/encoding.tex
more formulas

@@
 $\edgef(k,M')$ is true.
+%
+\ashu{define missing conds V1-V7}
 
@@
 
-\item $n_{i,m}$ indicates if $m \in \nlabel(i)$
-\item $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
-\item $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains molecule $m$.
+\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
+\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
+\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains molecule $m$.
 
-\item $p_{k,k'}$ indicates if $(m,m') \in \pairs$
+\item Boolean variable $p_{k,k'}$ indicates if $(m,m') \in \pairs$
 \item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
@@
 \begin{enumerate}
-\item dump = d{i,j,q}
-      to represent drop of edge{i,j,q} from the graph we will use d{i,j,q}.
-
-\item active\_node = a{i,k} 
-      kth molecule is active on the node i.
-
-\item presence\_edge = e{i,j,q,k}
-      There is an qth edge between node i and j with kth molecule present.
-
-\item active\_edge = b{i,j,q,k}
-      There is an qth edge between node i and j with kth molecule active.
-
-\item reachability = r{i,j,k,z}
-      Node i and j are reachable with kth molecule present in z steps.
-
+\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
+  holds
+\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
+\item $r_{i,j,m,z}$ indicates that there is a path from $i$ to $j$ of length $z$
+\item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped(used in encoding
+  $k$-connected property)
 \end{enumerate}
 
-Every variable is a Boolean bit, for example, n(0,1) represents node 0
-with type 1 molecule present. Assignment to the Boolean variable
-n(0,1) to True will mean that at node 0 type 1 molecule is present.
+% Every variable is a Boolean bit, for example, $n_{0,1}$ represents node 0
+% with type 1 molecule present. Assignment to the Boolean variable
+% n(0,1) to True will mean that at node 0 type 1 molecule is present.
 
-Basic notation for the formula we are trying to generate.
-\begin{enumerate}
+% Basic notation for the formula we are trying to generate.
+% \begin{enumerate}
 
-\item edge = e(i,j,q)      
-      we will assign e(i,j,q) for a qth edge between node i and j.
+% \item edge = e(i,j,q)      
+%       we will assign e(i,j,q) for a qth edge between node i and j.
 
-\item dump = d(i,j,q)
-      to represent drop of edge(i,j,q) from the graph we will use d(i,j,q).
+% \item dump = d(i,j,q)
+%       to represent drop of edge(i,j,q) from the graph we will use d(i,j,q).
 
-\item presence node = n(i,k) 
-	  kth molecule is present on the node i.
+% \item presence node = n(i,k) 
+% 	  kth molecule is present on the node i.
 
-\item active\_node = a(i,k) 
-      kth molecule is active on the node i.
+% \item active\_node = a(i,k) 
+%       kth molecule is active on the node i.
 
-\item presence\_edge = e(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule present.
+% \item presence\_edge = e(i,j,q,k)
+%       There is an qth edge between node i and j with kth molecule present.
 
-\item active\_edge = b(i,j,q,k)
-      There is an qth edge between node i and j with kth molecule active.
+% \item active\_edge = b(i,j,q,k)
+%       There is an qth edge between node i and j with kth molecule active.
 
-\item reachability = r(i,j,k,z)
-      Node i and j are reachable with kth molecule present in z steps.
+% \item reachability = r(i,j,k,z)
+%       Node i and j are reachable with kth molecule present in z steps.
 
-\item pairing matrix = p(k,k')
-      Molecule k and k' are pairing molecules in the matrix.
+% \item pairing matrix = p(k,k')
+%       Molecule k and k' are pairing molecules in the matrix.
 
-\item Type of the Boolean function = sorts (takes k-1 arguments Bool and return Bool) 
-\item Boolean function on nodes Function (fn\_{m},*sorts)
+% \item Type of the Boolean function = sorts (takes k-1 arguments Bool and return Bool) 
+% \item Boolean function on nodes Function (fn\_{m},*sorts)
 
-\item Boolean function on edge Function(fe\_{m},*sorts)
+% \item Boolean function on edge Function(fe\_{m},*sorts)
 
-\end{enumerate}
+% \end{enumerate}
+
+We will describe the Boolean formulas that encode VTSs in several categories.
+%
+In the end, we will present in a table the formulas needed for the
+model variants.
+%
+To avoid cumbersome notation, we will not explicitly write the ranges of the indexing
+in the formulas.
+%
+$i$ and $j$ will be ranged over nodes.
+%
+$m$ will be ranged over molecules.
+%
+$q$ will be ranged over edges between two nodes.
+%
+
+% \subsubsection{Constraints on the structure of the edges, nodes and }
+\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
+%
+We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
+to encode the basic structure of VTSs.
+%
+For an edge to exist it should have one molecule present. 
+%
+\begin{align}
+  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
+\end{align}
+
+If a molecule is active on an edge, it should be present on the edge.
+%
+\begin{align}
+  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
+\end{align}
+
+A molecule should be present to be active on a node.  
+\begin{align}
+  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
+  \tag{V3}\label{eq:c4}
+\end{align}
+
+The edge labels are subset of the node label of source and target compartments.
+
+\begin{align}
+  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies n_{i,m}\tag{V4}\label{eq:c0}\\
+  \bigwedge\limits_{i,j,q,m}  e_{i,j,q,m} \limplies n_{j,m}\tag{V5}\label{eq:c1}
+\end{align}
+
+%C1 =  e_ijk -> aik and e_ijk -> ajk
+
+Self edges are not allowed.
+
+\begin{align}
+   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V6}\label{eq:c2}
+\end{align}
+
+Condition on $p_{kk'}$. \ashu{why???} Diagonal blocks should be all 0's.
+
+\begin{align}
+  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
+  \tag{V7}\label{eq:c3}
+\end{align}
+
+\subsubsection{Well-fused constraints}
+Boolean constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
+destination node.
+%
+Boolean constraint~\eqref{eq:fuse2} encodes the each should not be able to
+potentially fuse with any other node.
+
+% Fusion rules consist of two different mechanisms.
+% \begin{enumerate}
+% \item  A \textbf{pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
+% \item \textbf{regulatory mechanisms} on the edges and nodes (possibly distinct) which regulates molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
+% \end{enumerate}
+% Boolean constraint~\eqref{eq:fuse1} and~\eqref{eq:fuse2} are used to encode well-fused
+% property.
+
+% F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active and have a non-zero entry in the pairing matrix.  
+\begin{align}
+  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
+  \tag{V8}\label{eq:fuse1}  \\
+\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
+  \tag{V9}\label{eq:fuse2}  
+\end{align}
+
+% F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.
 
 \subsubsection{Regulation on nodes and edges}
-Regulation of the molecules is based on the kind of the model under consideration.
-For example, model 1 (-V 1) has two different arbitrary Boolean functions dictating the activity of the molecules on edge and nodes.
-For variation 3 (-V 3) activity on edge is driven by pairing inhibition.
+%
+Regulation of the molecules is based on the kind of the model under
+consideration.
+%
+For example, model 1 (-V 1) has two different arbitrary
+Boolean functions dictating the activity of the molecules on edge and
+nodes.
+%
+For variation 3 (-V 3) activity on edge is driven by pairing
+inhibition.
 
@@
 A\_nn: No regulation on nodes i.e all the present molecules on the nodes are active.
-\[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]
+\[
+\bigwedge\limits_{i,m} n_{i,m} = a_{i,m} \,
+\]
 
 A\_nb: Boolean regulation on nodes. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]
+\[ \bigwedge\limits_{i,k} n_{i,m} \limplies a_{i,m} =   f_m (n_{i,1},\dots,n_{i,\mu}) \, \]
 
 A\_en: No regulation on edges i.e all the present molecules on the edges are active.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]
+\[ \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m} \, \]
 
 A\_eb: Boolean regulation on edges. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]
+\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \limplies b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]
 
 A\_ep: Pairing inhibition. The activity of the molecules is defined by inhibition by other molecules based on the pairing matrix. 
-\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]
+\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies \neg b_{i,j,q,k}) \, \]
 
-\[ \bigwedge\limits_{i,j, q, k}  (e_{i,j,q,k} \land \neg [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset b_{i,j,q,k}) \, \]
+\[ \bigwedge\limits_{i,j, q, k}  (e_{i,j,q,k} \land \neg [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies b_{i,j,q,k}) \, \]
 
-\subsubsection{Constraints on the structure of the edges, nodes and pairing matrix}
-A few additional constraints are required on the nodes, edges and pairing matrix to set up the essential conditions. We use Boolean variables C0-C5 to build all these constraints.
-
-C0: The edge labels are subset of the node label of source compartment.
-
-\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset n_{i,k} \, \]
-
-C1: The edge labels are subset of the node label of target compartment.
-
-\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset n_{j,k} \, \]  
-%C1 =  e_ijk -> aik and e_ijk -> ajk
-
-C2: Self edges are not allowed.
-
-\[  \bigwedge\limits_{i,q} \neg e_{i,i,q} \, \]
-
-C4: Condition on p\_kk'. Diagonal blocks should be all 0's.
-
-\[ \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y) \, \]
-
-C5: Activity on the node. A molecule should be present to be active on a node.  
-\[ \bigwedge\limits_{i,k} a_{i,k} \supset n_{j,k} \, \]
-
-% - F0: b(i,j,k) $\supset$ e(i,j,k)
-
-\subsubsection{Constraints on presence and activity of the molecule}
-Few additional constraints that are required for the molecules presence and activity is build using F0 and F1. \newline
-
-F0: An edge has to have one present molecule. F0 looks redundant.
-
-\[ \bigwedge\limits_{i,j,q} \bigvee_k e_{i,j,q,k} \supset e_{i,j,q} \, \]
-
-F1: If molecule is active on an edge then it should be present on the edge.
-
-\[ \bigwedge\limits_{i,j,q,k} b_{i,j,q,k} \supset e_{i,j,q,k}\, \]
+% - F0: b(i,j,k) $\limplies$ e(i,j,k)
 
@@
 % I have implemented: Changed the implementation in code too.
-%\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
+%\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \limplies (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
 
 % Update: Better 
-\[ \bigwedge\limits_{i,j,k} (\bigvee_{q} e_{i,j,q,k}) \supset (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
+\[ \bigwedge\limits_{i,j,k} (\bigvee_{q} e_{i,j,q,k}) \limplies (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
 
@@
 
-\[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \supset (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]
-
-\subsubsection{Fusion rule constraints}
-
-Fusion rules consist of two different mechanisms.
-
-\begin{enumerate}
-\item  A \textbf{pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-\item \textbf{regulatory mechanisms} on the edges and nodes (possibly distinct) which regulates molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
-\end{enumerate}
-
-Boolean variable F4 and F5 are used to model these constraints.
-
-F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active and have a non-zero entry in the pairing matrix.
-
-\[ \bigwedge\limits_{i,j,q} e_{i,j,q} \supset \bigvee_{k,k^{\prime}} (b_{i,j,q,k} \land a_{j,k^{\prime}} \land p_{k,k^{\prime}}) \, \]
-
-F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.
-
-\[ \bigwedge\limits_{i,j,q,k} b_{i,j,q,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]
+\[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \limplies (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]
 
@@
 D0: Only present edges can be dropped.
-\[ \bigwedge\limits_{i,j,q} d_{i,j,q} \supset e_{i,j,q}  \]
+\[ \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \]
 
@@
 
-\[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \supset r^{\prime}(i,j)  \]
+\[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}(i,j)  \]
 

### 2017-06-22 biology.py
removed

@@ -13,6 +13,8 @@ parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes
 parser.add_argument("-Q","--pedges", type=int, default=1, help = "max no.of parallel edges btw two nodes")
 parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
 parser.add_argument("-C","--connected", type=int, default=3, help = "graph connectivity want to check")
+parser.add_argument("-E","--edges", type=int, default=3, help = "graph connectivity want to check")
+
 args = parser.parse_args()
 
 M = args.mols
@@ -44,193 +46,88 @@ for i in range(6):
 #----------------------------------------------------
 # Constraint generation 
 edge = [ [ [ Bool ("e_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
-E = [ edge[i][j][q] for i in range(N) for j in range(N) for q in range(Q) if i != j]
 
-#print len(E)
-#print E
-
-# Un_Skolemized dumped edges and reachability.
 dump = [ [ [Bool ("d_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
-#DX = [ dump[i][j][q] for i in range(N) for j in range(N) for k in range(Q) if i != j ]
-
-#print DX
-#print len(DX)
 
 r1 = [ [Bool ("r1_{}_{}".format(i,j)) for j in range(N)] for i in range(N)]
-#RX = [ r1[i][j] for i in range(N) for j in range(N) if i != j ]
 
-#print RX
-#print len(RX)
-
-funE = len(E)
-#funE = len(E) + len(DX) + len(RX)
-lenE = funE + 1
-
-QVars = E
-#QVars = E + RX + DX
-print QVars
-
-#print funE
-#print lenE
-#sys.exit(0)
-
-# Define nodeSort that will server the purpose of the total number
-# Arguments skolem nodes,edges takes.
-nodeSort = [BoolSort() for x in range(lenE)]
-#print nodeSort
-#print len(nodeSort)
-
-#print nodeSort 
-# Skolemized presence edge
-#fnode = [ [Function ("fn_{}_{}".format(i,k), *nodeSort) for k in range(M)] for i in range(N)]
 node = [ [Bool ("n_{}_{}".format(i,k)) for k in range(M)] for i in range(N)]
 
-#for i in range(N):
-#    for k in range(M):
-#        s = []
[…]

### 2017-06-22 file1.py

@@ -651,6 +651,7 @@ print s.check()
 
 b = time.time() - st
 print "Solving took...", str(b)
+print "Total took...", str(a + b)
 
 
 
@@ -715,9 +716,9 @@ if s.check() == sat:
     s = [[ [ [m[active_edge[i][j][q][k]] for k in range (M)] for q in range(Q)] for j in range(N) ] for i in range(N) ]
     t = [ [ [m[edge[i][j][q]]  for q in range(Q)] for j in range(N) ] for i in range(N) ]
     print 'Printing the pairing matrix'
-    print_matrix(xc)
-    print ' '
-    print t
+    #print_matrix(xc)
+    #print ' '
+    #print t
     dump_dot( "/tmp/bio.dot", m )
 else:
     print "failed to solve"

### 2017-06-22 paper/related.tex
update
removed
related-work

@@
 \ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
+
+Satisfiability was the first NP-complete problem discovered by Cook in his famous paper [ref].
+Every NP-complete problem can be reduced to solving for satisfiability.
+The fact is that SAT solvers have seen a surge in the handling of millions of variables, hence many general problems are encoded as a SAT problem.
+Due to the nature of the searching (exhaustive), solving the combinatorial problem is the natural fit for the SAT solvers.
+There are many graphs related combinatorial work [1-4] that have used SAT solvers.
+Thanks to the improvement in SAT solver and formal techniques tools like model checkers and theorem provers scalability and combinatorial solving capability are now being used to model complex biological problems [1-3].
+% Many network questions are being reduced to solving a SAT question.
+Many of these biological system uses model checkers to reason about graphs and networks rules with possible exhaustive search [5-6].
+
+Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) [7-9].
+GNR is a complex system driven by many complex rules.
+We extended this work and have applied model checkers to the more complex transport network (VTS) [Mani and Thattai].
+Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge.
 
@@
 \item Timing Robustness in the Budding and Fission Yeast Cell Cycles.
+\item Solving Subgraph Epimorphism Problems using CLP
+and SAT.
 \end{enumerate}
@@
 
-Who will do the related work?
-
 %--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

### 2017-06-22 bio.py
related-work

@@ -1,0 +1,677 @@
+#!/usr/bin/python
+
+from z3 import *
+import argparse
+import time
+
+#----------------------------------------------------
+# input parsing
+# input number of nodes and molecules
+parser = argparse.ArgumentParser(description='Auto testing for TARA')
+parser.add_argument("-M","--mols", type=int, default=4, help = "number of molecules")
+parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes")
+parser.add_argument("-Q","--pedges", type=int, default=1, help = "max no.of parallel edges btw two nodes")
+parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
+parser.add_argument("-C","--connected", type=int, default=3, help = "graph connectivity want to check")
+parser.add_argument("-E","--edges", type=int, default=3, help = "graph connectivity want to check")
+
+args = parser.parse_args()
+
+M = args.mols
+N = args.nodes
+Q = args.pedges
+V = args.variation
+C = args.connected
+
+bag = []
+bag.append ('1. Boolean function on nodes and Boolean function on the edges.') 
+bag.append ('2. Only Boolean function on the edges.') 
+bag.append ('3. Boolean function on nodes and SNARE-SNARE inhibition on edges.')
+bag.append ('4. Only SNARE-SNARE inhibition on edges.')
+bag.append ('5. Only Boolean function on nodes.')
+bag.append ('6. No regulation at all.')
+
+for i in range(6):
+    if V == i + 1:
+        print ' '
+        print 'Default/choosen vesicular traffic system is regulated by ...',
+        print bag[i]
+        print ' '
+        print 'Use -V option to change the regulated variation.' 
+        for i in bag:
+            print i 
+        print ' '
+        break
+
+#----------------------------------------------------
+# Constraint generation 
+edge = [ [ [ Bool ("e_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+
+dump = [ [ [Bool ("d_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+
+r1 = [ [Bool ("r1_{}_{}".format(i,j)) for j in range(N)] for i in range(N)]
+
[…]

### 2017-06-22 paper/bio.tex
expmt
first cut

@@
 \begin{itemize}
-\item \mukund{Detailed BIO motivation}
+\item \mukund{Detailed BIO}
 \item \srivas{Detailed BIO to Graph problem}
 \end{itemize}
+
+The whole cell should be in stable condition i.e flow of the molecule
+is balanced at every point and globally. Each molecule leaving its
+source node on a vesicle should come back in a cycle.
 
@@
 \begin{itemize}
-\item 3 connected
-\item  ....
+\item Vesicular traffic network.
+\item Recycling of molecules, steady state.
+\item Maximum connectivity [LGC, Least guarantee connectivity] and minimal connective [LRC (least required connectivity)] (rather than necc and suff cond) required by the graph. 
+\item Connected-ness. 3 and 4.
+\item Pairing mechanism (matrix).
+\item Fusion rules, inhibition/regulation mechanism, Pairing inhibition.
+\item Potential to connect.
+\item Property of interest.
+\item Reachability definition.
 \end{itemize}

### 2017-06-22 paper/encoding.tex
first cut

@@
 section.
+%
 Subsequently, we will present the SAT encoding of the search problems
@@
 %
-\ashu{define missing conds V1-V7}
+We call $G$ {\em well-structured} if 
+Molecules $M$ is divided into two partitions $M_1$ and $M_2$
+such that $M_1 \times M_2 \intersection P = \emptyset$, and
+for each $(n,M',n')$, $n \neq n'$, 
+$M' \subseteq \nlabel(n)$, and $M' \subseteq \nlabel(n')$.
+%
 
@@
 For a given $k$, size $\nu$, and molecule number $\mu$,
-we are searching for stable and well-fused VTS
+we are searching for well-structured, stable, and well-fused VTS
 $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
@@
 \end{enumerate}
-
-We also have auxiliary variables that will help us encode the properties 
+We also have auxiliary Boolean variables that will help us encode the well-fused and stability properties 
 \begin{enumerate}
@@
 \item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\item $r_{i,j,m,z}$ indicates that there is a path from $i$ to $j$ of length $z$
-\item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped(used in encoding
-  $k$-connected property)
+\item $r_{i,j,m,p}$ indicates that there is a path from $i$ to $j$ of length less than or equal to $p$
 \end{enumerate}
-
-% Every variable is a Boolean bit, for example, $n_{0,1}$ represents node 0
-% with type 1 molecule present. Assignment to the Boolean variable
-% n(0,1) to True will mean that at node 0 type 1 molecule is present.
-
-% Basic notation for the formula we are trying to generate.
-% \begin{enumerate}
-
-% \item edge = e(i,j,q)      
-%       we will assign e(i,j,q) for a qth edge between node i and j.
-
-% \item dump = d(i,j,q)
-%       to represent drop of edge(i,j,q) from the graph we will use d(i,j,q).
-
-% \item presence node = n(i,k) 
-% 	  kth molecule is present on the node i.
-
-% \item active\_node = a(i,k) 
-%       kth molecule is active on the node i.
-
-% \item presence\_edge = e(i,j,q,k)
-%       There is an qth edge between node i and j with kth molecule present.
-
-% \item active\_edge = b(i,j,q,k)
-%       There is an qth edge between node i and j with kth molecule active.
-
-% \item reachability = r(i,j,k,z)
-%       Node i and j are reachable with kth molecule present in z steps.
-
-% \item pairing matrix = p(k,k')
-%       Molecule k and k' are pairing molecules in the matrix.
-
-% \item Type of the Boolean function = sorts (takes k-1 arguments Bool and return Bool) 
-% \item Boolean function on nodes Function (fn\_{m},*sorts)
-
-% \item Boolean function on edge Function(fe\_{m},*sorts)
-
-% \end{enumerate}
+For $k$-connected property, we also use the following auxiliary Boolean variables
+\begin{enumerate}
+\item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped
+\item $r'_{i,j}$ indicates that there is a path from $i$ to $j$ is a modified VTS
+\end{enumerate}
 
@@
 \end{align}
-
 If a molecule is active on an edge, it should be present on the edge.
@@
 Boolean constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
-destination node.
+its destination node.
 %
-Boolean constraint~\eqref{eq:fuse2} encodes the each should not be able to
-potentially fuse with any other node.
+Boolean constraint~\eqref{eq:fuse2} encodes that each edge should not
+be able to potentially fuse with any node other than its destination node.
+\begin{align}
+  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
+  \tag{V8}\label{eq:fuse1}  \\
+\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
+  \tag{V9}\label{eq:fuse2}  
+\end{align}
 
@@
 % F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active and have a non-zero entry in the pairing matrix.
-\begin{align}
-  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
-  \tag{V8}\label{eq:fuse1}  \\
-\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
-  \tag{V9}\label{eq:fuse2}  
-\end{align}
 
@@
 \subsubsection{Regulation on nodes and edges}
+We are considering several models that differ in constraints on
+the activity of molecules.
 %
-Regulation of the molecules is based on the kind of the model under
-consideration.
+We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
+the varying constraints.
 %
-For example, model 1 (-V 1) has two different arbitrary
-Boolean functions dictating the activity of the molecules on edge and
-nodes.
+The following formula encodes no conditions on activities on nodes,
+i.e., all the present molecules on the nodes are active.
+\begin{align}
+\bigwedge\limits_{i,m} n_{i,m} = a_{i,m}    \tag{Ann}\label{eq:ann}
+\end{align}
+The following formula encodes that activity of a molecule $m$ on the node is
+defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
+\begin{align}
+\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
+\tag{Anb}\label{eq:anb}
+\end{align}
+The following formula encodes no conditions on activities on edges,
+i.e., all the present molecules on the edges are active.
+\begin{align}
+  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
+\tag{Aen}\label{eq:aen}
+\end{align}
+The following formula encodes that activity of a molecule $m$ on the edge is
+defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
+\begin{align}
+   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
+  \tag{Aeb}\label{eq:aeb}
+\end{align}
 %
-For variation 3 (-V 3) activity on edge is driven by pairing
-inhibition.
+The following formula encodes that the activity of the molecules on
+edges is defined by inhibition by other molecules based on the pairing
+matrix. 
+\begin{align}
+   \bigwedge\limits_{i,j,q, m}  e_{i,j,q,m} \limplies(  [ ( \bigvee_{m'} p_{m,m'} \land \bigwedge_{m' != m} p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv \neg b_{i,j,q,m})
+  \tag{Aep}\label{eq:aep}
+\end{align}
+% \[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies \neg b_{i,j,q,k}) \, \]
 
-We use two Boolean variables A\_* to build these two constraints. \newline
-
-A\_nn: No regulation on nodes i.e all the present molecules on the nodes are active.
-\[
-\bigwedge\limits_{i,m} n_{i,m} = a_{i,m} \,
-\]
-
-A\_nb: Boolean regulation on nodes. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,k} n_{i,m} \limplies a_{i,m} =   f_m (n_{i,1},\dots,n_{i,\mu}) \, \]
-
-A\_en: No regulation on edges i.e all the present molecules on the edges are active.
-\[ \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m} \, \]
-
-A\_eb: Boolean regulation on edges. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
-\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \limplies b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]
-
-A\_ep: Pairing inhibition. The activity of the molecules is defined by inhibition by other molecules based on the pairing matrix. 
-\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies \neg b_{i,j,q,k}) \, \]
-
-\[ \bigwedge\limits_{i,j, q, k}  (e_{i,j,q,k} \land \neg [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies b_{i,j,q,k}) \, \]
+% \[ \bigwedge\limits_{i,j, q, k}  (e_{i,j,q,k} \land \neg [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies b_{i,j,q,k}) \, \]
 
@@
 \subsubsection{Constraints for stability condition}
-The whole cell should be in stable condition i.e flow of the molecule is balanced at every point and globally.
-Each molecule leaving its source node on a vesicle should come back in a cycle.
-Boolean variable F3 and F2 are used to model these constraints.
+%
+We use $m$-reachability to encode the stability condition in VTSs.
+%
+The following formula recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
+if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
+$(i != i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
+%
+\begin{align}
+  \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+  \tag{R1}\label{eq:reach1}
+\end{align}
+Now we can encode stability using the reachability variables.
+and say if there is an $m$-edge between $i$ and $j$, there is
+$m$-reachable path from $j$ to $i$.\ashu{disjunction needed??}
+\begin{align}
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies (r_{j,i,m,0}  \lor r_{j,i,m,1} \lor ... \lor r_{j,i,m,p})  
+  \tag{R2}\label{eq:reach2}
+\end{align}
 
-\textbf {Reachability definition and stability condition.}
-We have encoded stable condition by using reachability definition. \newline
+% Boolean variable
+% F3 and F2 are used to model these constraints.
 
-F3: Stability condition. For every leaving molecule, the source node is reachable from the target node with that molecule present, in maximum p steps.
+% % \textbf {Reachability definition and stability condition.}
+% We have encoded stable condition by using reachability definition. \newline
 
-% I have implemented: Changed the implementation in code too.
-%\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \limplies (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
+% F3: Stability condition. For every leaving molecule, the source node is reachable from the target node with that molecule present, in maximum p steps.
 
-% Update: Better 
-\[ \bigwedge\limits_{i,j,k} (\bigvee_{q} e_{i,j,q,k}) \limplies (r_{j,i,k,0}  \lor r_{j,i,k,1} \lor ... \lor r_{j,i,k,p}) \, \]
-
-F2: Reachability definition.
+% F2: Reachability definition.
 Node j is reachable from node i with kth molecule present in maximum p steps if either there is a direct edge between i-j with that molecule present or there is a direct edge between $i^{\prime \prime}$ $(i != i^{\prime \prime})$ and j with kth molecule present on that edge and $i^{\prime \prime}$ are reachable from i in p steps.
 
-\[ \bigwedge\limits_{i,j,k,p} r_{i,j,k,p} \limplies (\bigvee_{q} \, e_{i,j,q,k} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,k}) \land r_{i^{\prime},j,k,p-1} ) \, \]
+\subsubsection{$k$-connectivity constraints}
+To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
+disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
+The following formulas encode the relevant constraints for reachability in the modified VTS.
 
-\subsubsection{Graph connectivity constraints}
-To check the whether that n connected is a necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have an n connected satisfying graph.
-We can go down or up using -C \_ option.
-\newline
+The following formulas encode that only existing edges can be dropped
+and exactly $k-1$ edges are dropped.
+\begin{align}
+  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \tag{D1}\label{eq:drop1}\\
+  \sum_{i,j,q} d_{i,j,q} = k-1
+  \tag{D2}\label{eq:drop2}
+\end{align}
+We need to define reachability in the modified VTS, therefore we use
+a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
+In the following formula, we encode $r'_{i,j}$ is true if there is an
+edge $(i,\_,j)$ and it is not dropped, or there is a node
+$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
+not dropped and $r'_{i',j}$ is true.
+\begin{align}
+\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}(i,j)  
+  \tag{D3}\label{eq:drop3}
+\end{align}
+Since we are looking for a graph that is not $k$-connected,
+the following formula encodes that there are nodes $i$ and $j$ such that
+there is no path between them in the underlying undirected graph.
+\begin{align}
+   \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
+  \tag{D4}\label{eq:drop4}
+\end{align}
 
-D0: Only present edges can be dropped.
-\[ \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \]
+The key improvement in our work over the earlier tool is the
+encoding of reachability, which was done using enumeration of paths.
+%
+We have encoded reachability in two different ways in~\eqref{eq:reach1} and~\eqref{eq:drop3}.
+%
+The reachability is recursively defined~\eqref{eq:drop3} and has trivial solution by
+making all $r'$s true.
+%
+However, the trivial solution is disallowed by~\eqref{eq:drop3} and we find only the
+solutions that captures the evidence of unreachability.
+%
+In~\eqref{eq:reach1}, we have added length of paths in our reachability encoding.
+%
+This is because~\eqref{eq:reach2} has only positive occurrences of the reachability variables
+and circular dependencies in the recursive definition in~\eqref{eq:reach1} 
+may result in spurious satisfying assignments that do not encode reachability.
+%
+By adding the path length, we break the circular dependencies and the formula remain polynomial in size.
 
-D1,D2: We are dropping c edges from the graph. exactly c are dropped.
-\[ \sum_{i,j,q} d_{i,j,q} == c \]
+% We can go down or up using -C \_ option.  \newline
 
-D3:  Graph becomes disconnected. Ensure that there is no path between some nodes i,j in the underlying undirected graph. Different reachability.
-\[ \bigwedge\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})]  \]
+\subsection{SAT problems different variants}
+\ankit{Bring model variant table here}
 
-D4: New reachability definition for graph connectedness: dReachable.
-Node i,j are reachable either if there is a direct edge and its not dropped or there is an node $i^{\prime}$ such that, there is a direct edge between i, $i^{\prime}$ which is not dropped and $i^{\prime}$ and j is dReachable.
+% \subsection{Creating a solver and solving these constraints}
+% We will create a solver and add these build formula using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
 
-\[ \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}(i,j)  \]
+% \begin{figure}[ht]
+% %\vspace{-3mm}
+% \begin{verbatim}
+% # Create a solver
+% s = Solver()
+% # Add these formulas to it.
+% s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)
 
-\subsection{Creating a solver and solving these constraints}
-We will create a solver and add these build formula using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
-
-\begin{figure}[ht]
-%\vspace{-3mm}
-\begin{verbatim}
-# Create a solver
-s = Solver()
-# Add these formulas to it.
-s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)
-
-# Check for the satisfiability assignment.
-print s.check()   
-\end{verbatim}
-\caption{Solving for these constraints.}
-\label{code:motivate}
-\end{figure}
+% # Check for the satisfiability assignment.
+% print s.check()   
+% \end{verbatim}
+% \caption{Solving for these constraints.}
+% \label{code:motivate}
+% \end{figure}
 

### 2017-06-22 paper/related.tex
related-work

@@
 The fact is that SAT solvers have seen a surge in the handling of millions of variables, hence many general problems are encoded as a SAT problem.
-Due to the nature of the searching (exhaustive), solving the combinatorial problem is the natural fit for the SAT solvers.
+Due to the nature of the searching (exhaustive), solving the combinatorial problem is a natural fit for the SAT solvers.
 There are many graphs related combinatorial work [1-4] that have used SAT solvers.
-Thanks to the improvement in SAT solver and formal techniques tools like model checkers and theorem provers scalability and combinatorial solving capability are now being used to model complex biological problems [1-3].
+Thanks to the improvement in SAT solver and formal techniques, tools like model checkers and theorem provers scalability and combinatorial solving capability are now being used to model complex biological problems [1-3].
 % Many network questions are being reduced to solving a SAT question.
@@
 Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge.
+In this paper we have achieved the scalability required for analyzing vesicular transport network for eukaryotic cells, of total ten compartments (N = 10).
 

### 2017-06-22 paper/encoding.tex
encoding

@@
 
+We have encoded several versions of the models of vesicle traffic systems listed.
+Starting from most basic version (A) where every present molecule is considered to be active.
+Other cases includes different combinations of constraints on the activity on nodes and edges.
+Most general restriction is activity of the molecule is dependent on the other molecule present on the node (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
+In very special case (E,F,G,H) activity of the molecules on the edges is dictated by pairing matrix, we call this process ``pairing inhibition".
+
+% DIVIDE INTO COLUMNS and TALK ABOUT A/1 or A/0.
+%\todo{describe the variations}
+
+\begin{enumerate}[label=\Alph*]
+\item Every present molecule is considered to be active.
+\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
+\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
+\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
+\item Activity of molecules on the edges is driven by pairing inhibition.
+\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
+\item Version F with additional constraint that every edge is distinct.
+%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
+%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
+\item Version F but self-edges are allowed.
+\end{enumerate}
+%
+
 % \subsection{Creating a solver and solving these constraints}

### 2017-06-22 paper/experiments.tex
related-work
encoding

--- 2017-06-20 paper/experiments.tex
@@
 %Besides using the default Z3 solvers we have used for these experiments \ankit{Z3, picoSAT, Lingeling}. The performance of Z3 was ...
-%
-Our implementation supports several versions of the models of vesicle traffic systems listed in Table 2.
-Starting from most basic version (A) where every present molecule is considered to be active.
-Other cases includes different combinations of constraints on the activity on nodes and edges.
-Most general restriction is activity of the molecule is dependent on the other molecule present on the node (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
-In very special case (E,F,G,H) activity of the molecules on the edges is dictated by pairing matrix, we call this process ``pairing inhibition".
-
-% DIVIDE INTO COLUMNS and TALK ABOUT A/1 or A/0.
-%\todo{describe the variations}
-
-\begin{enumerate}[label=\Alph*]
-\item Every present molecule is considered to be active.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
-\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
-\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
-\item Activity of molecules on the edges is driven by pairing inhibition.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
-\item Version F with additional constraint that every edge is distinct.
-%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
-%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
-\item Version F but self-edges are allowed.
-\end{enumerate}
 %

### 2017-06-23 paper/intro.tex
update
changes
mukund-add

@@
 \begin{itemize}
-\item \mukund{BIO motivation ( 1 paragraph ) }
+\item \mukund{BIO motivation}
 
-\item \srivas{BIO to Graph problem ( a couple of paragraph) }
+The conservation of basic molecular processes across all living cells, including the genetic code, suggests that life on Earth arose only once: all extant organisms are presumed to trace their lineages back to a last universal common ancestor (LUCA).
+However, there are still vast differences in cellular and molecular architecture among the three kingdoms of life: bacteria, archaea, and eukaryotes [1].
+Eukaryotic cells have larger genomes and have more complex cellular architectures than the prokaryotic bacteria and archaea.
+In particular, the cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
+Cargo is moved between these organelles in small membrane-bound transporters known as vesicles [2].
+
+This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
+Membrane traffic underpins nearly every aspect of eukaryotic cellular physiology, including human cellular physiology.
+Defects in membrane traffic lead to a variety of disorders or even cell death [2].
+Understanding how membrane traffic functions is therefore one of the central challenges of cell biology.
+Some progress has been made, as cell biologists have assembled a “parts list” of molecules that drive vesicle traffic [3].
+The essential processes involve the creation of vesicles loaded with cargo from source organelles, known as “budding”, and the depositing of those vesicles and cargo into target organelles, known as “fusion” [4].
+Budding is regulated by proteins known as coats and adaptors that select cargo.
+Fusion is regulated by proteins known as SNAREs and tethers, that ensure that vesicles fuse to the correct target [5].
+Although we know a great deal about molecular-level details, there has been very little work done on how such processes are integrated across scales to build the entire vesicle traffic system.
+We have recently attempted to use ideas of graph theory to address this question [5,6].
+The SNARE proteins are the focus of our current work.
+Abstractly, we can think of these proteins as labels that are collected from the source compartment and taken to the target compartment on vesicles.
+There is a corresponding set of label molecules on the target compartments.
+If the two sets of labels (on vesicles and targets) are compatible, then the vesicle will fuse.
+The question is: does this physical picture place any constrains on the global topology of the traffic graph?
+We have previously shown that one informative constraint is graph connectivity [6].
+
+1. Embley, T. M., and Martin, W. (2006). Eukaryotic evolution: changes and challenges. Nature 440, 623-630.
+
+2. Stenmark, Harald. "Rab GTPases as coordinators of vesicle traffic." Nature Reviews Molecular Cell Biology 10, no. 8 (2009): 513-525.
+
+3. Dacks, J. B., & Field, M. C. (2007). Evolution of the eukaryotic membrane-trafficking system: origin, tempo and mode. Journal of cell science, 120(17), 2977-2985.
+
+4. Munro S. 2004. Organelle identity and the organization of membrane traffic. Nature Cell Biology 6:469–472. doi: 10.1038/ncb0604-469.
+
+5. Mani, S., and Thattai, M. (2016b). Stacking the odds for Golgi cisternal maturation. eLife 10.7554/eLife.16231.
+
+6. Shukla, A., Bhattacharyya, A., Kuppusamy, L., Srivas, M., & Thattai, M. (2017). Discovering vesicle traffic network constraints by model checking. PLoS ONE, in press.
+
+\item \srivas{BIO to Graph problem}
 
@@
 %
-Since most VTSs in the cells are less than \ankit{10} nodes,
+Since most VTSs in the cells are of \ankit{10} compartments,
 our tool will be useful for biologists to study VTSs.

### 2017-06-23 paper/encoding.tex
minor fix

@@
 We model VTSs as labelled directed graphs.
-The graph labels both edges and labels with sets of molecules to denote
-the set of molecules present in the node.
+The graph labels both nodes and edges with sets of molecules to denote
+the set of molecules present in them.
 The graph is formally defined as follows.
@@
   \item $\nodes$ is a set of nodes representing compartments in the VTS,
-  \item $\mols$ is the set of molecules flowing in the network, 
+  \item $\mols$ is the set of molecules flowing in the system, 
   \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes  
-  \item $ \nodes \times (\powerset{\mols}-\emptyset) \times \nodes \subseteq \edges$ is the set of edges
-    with molecule sets as labels
-  \item $\pairs : \mols \times \mols$ is pairing relating
+  \item $ \nodes \times (\powerset{\mols}-\emptyset) \times \nodes \subseteq \edges$ is the
+    set of edges with molecule sets as labels
+  \item $\pairs : \mols \times \mols$ is pairing relation
   \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
@@
 $\nodef$ and $\edgef$ are used to define activity of molecules on
-nodes and edges.
+nodes and edges respectively.
 %
@@
 %
-We call $G$ {\em well-structured} if 
-Molecules $M$ is divided into two partitions $M_1$ and $M_2$
-such that $M_1 \times M_2 \intersection P = \emptyset$, and
-for each $(n,M',n')$, $n \neq n'$, 
+We call $G$ {\em well-structured} if molecules $M$ is divided into
+two equal partitions $M_1$ and $M_2$ such that $P \subseteq M_1 \times M_2$, and
+for each $(n,M',n') \in \edges$, $n \neq n'$, 
 $M' \subseteq \nlabel(n)$, and $M' \subseteq \nlabel(n')$.
@@
 For a molecule $m \in M$,
-An {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
+an {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
 such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
@@
 %
-We call $G$ $k$-connected if for each $E' \subseteq \edges$ and $|E'| < k$,
+We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
 VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
@@
 \begin{align}
-   \bigwedge\limits_{i,j,q, m}  e_{i,j,q,m} \limplies(  [ ( \bigvee_{m'} p_{m,m'} \land \bigwedge_{m' != m} p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv \neg b_{i,j,q,m})
+   \bigwedge\limits_{i,j,q, m}  e_{i,j,q,m} \limplies(  [ ( \bigvee_{m'} p_{m,m'} \land \bigwedge_{m' \neq m} p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv \neg b_{i,j,q,m})
   \tag{Aep}\label{eq:aep}
@@
 if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
-$(i != i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
+$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
 %
@@
 % F2: Reachability definition.
-Node j is reachable from node i with kth molecule present in maximum p steps if either there is a direct edge between i-j with that molecule present or there is a direct edge between $i^{\prime \prime}$ $(i != i^{\prime \prime})$ and j with kth molecule present on that edge and $i^{\prime \prime}$ are reachable from i in p steps.
+Node j is reachable from node i with kth molecule present in maximum p steps if either there is a direct edge between i-j with that molecule present or there is a direct edge between $i^{\prime \prime}$ $(i \neq i^{\prime \prime})$ and j with kth molecule present on that edge and $i^{\prime \prime}$ are reachable from i in p steps.
 
@@
 \begin{align}
-\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' != i}  r^{\prime}(i',j) \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}(i,j)  
+\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}
   \tag{D3}\label{eq:drop3}
@@
 %
-We have encoded reachability in two different ways in~\eqref{eq:reach1} and~\eqref{eq:drop3}.
+In the current work, we have encoded reachability in two different
+ways in formulas~\eqref{eq:reach1} and~\eqref{eq:drop3}.
 %
-The reachability is recursively defined~\eqref{eq:drop3} and has trivial solution by
-making all $r'$s true.
+The reachability is recursively defined in~\eqref{eq:drop3} and has
+trivial solution by making all $r'$s true.
 %
-However, the trivial solution is disallowed by~\eqref{eq:drop3} and we find only the
-solutions that captures the evidence of unreachability.
+However, the trivial solution is disallowed by formula~\eqref{eq:drop4} and we find
+only the solutions that captures the evidence of unreachability.
 %
-In~\eqref{eq:reach1}, we have added length of paths in our reachability encoding.
+On the other hand,
+we have added length of paths in our reachability encoding in formula~\eqref{eq:reach1},
+which needs relatively more auxiliary variables.
 %
-This is because~\eqref{eq:reach2} has only positive occurrences of the reachability variables
-and circular dependencies in the recursive definition in~\eqref{eq:reach1} 
-may result in spurious satisfying assignments that do not encode reachability.
+This is because formula~\eqref{eq:reach2} has only positive
+occurrences of the reachability variables and circular dependencies in
+the recursive definition of $r'$s in ~\eqref{eq:reach1} may result
+in spurious satisfying assignments that do not encode reachability.
 %
-By adding the path length, we break the circular dependencies and the formula remain polynomial in size.
+By adding the path length, we break the circular dependencies, the
+formula remains polynomial in size, and satisfying assignments only
+corresponds to correct reachability.
 
@@
 
-\subsection{SAT problems different variants}
+\subsection{SAT problems for different variants}
 \ankit{Bring model variant table here}

### 2017-06-28 paper/intro.tex
fixed_bib

@@
 The conservation of basic molecular processes across all living cells, including the genetic code, suggests that life on Earth arose only once: all extant organisms are presumed to trace their lineages back to a last universal common ancestor (LUCA).
-However, there are still vast differences in cellular and molecular architecture among the three kingdoms of life: bacteria, archaea, and eukaryotes [1].
+However, there are still vast differences in cellular and molecular architecture among the three kingdoms of life: bacteria, archaea, and eukaryotes \cite{embley2006eukaryotic}.
 Eukaryotic cells have larger genomes and have more complex cellular architectures than the prokaryotic bacteria and archaea.
 In particular, the cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
-Cargo is moved between these organelles in small membrane-bound transporters known as vesicles [2].
+Cargo is moved between these organelles in small membrane-bound transporters known as vesicles \cite{stenmark2009rab}.
 
@@
 Membrane traffic underpins nearly every aspect of eukaryotic cellular physiology, including human cellular physiology.
-Defects in membrane traffic lead to a variety of disorders or even cell death [2].
+Defects in membrane traffic lead to a variety of disorders or even cell death \cite{stenmark2009rab}.
 Understanding how membrane traffic functions is therefore one of the central challenges of cell biology.
-Some progress has been made, as cell biologists have assembled a “parts list” of molecules that drive vesicle traffic [3].
-The essential processes involve the creation of vesicles loaded with cargo from source organelles, known as “budding”, and the depositing of those vesicles and cargo into target organelles, known as “fusion” [4].
+Some progress has been made, as cell biologists have assembled a “parts list” of molecules that drive vesicle traffic \cite{dacks2007evolution}.
+The essential processes involve the creation of vesicles loaded with cargo from source organelles, known as “budding”, and the depositing of those vesicles and cargo into target organelles, known as “fusion” \cite{munro2004organelle}.
 Budding is regulated by proteins known as coats and adaptors that select cargo.
-Fusion is regulated by proteins known as SNAREs and tethers, that ensure that vesicles fuse to the correct target [5].
+Fusion is regulated by proteins known as SNAREs and tethers, that ensure that vesicles fuse to the correct target \cite{mani2016stacking}.
 Although we know a great deal about molecular-level details, there has been very little work done on how such processes are integrated across scales to build the entire vesicle traffic system.
-We have recently attempted to use ideas of graph theory to address this question [5,6].
+We have recently attempted to use ideas of graph theory to address this question \cite{mani2016stacking,shukla}.
 The SNARE proteins are the focus of our current work.
@@
 The question is: does this physical picture place any constrains on the global topology of the traffic graph?
-We have previously shown that one informative constraint is graph connectivity [6].
-
-1. Embley, T. M., and Martin, W. (2006). Eukaryotic evolution: changes and challenges. Nature 440, 623-630.
-
-2. Stenmark, Harald. "Rab GTPases as coordinators of vesicle traffic." Nature Reviews Molecular Cell Biology 10, no. 8 (2009): 513-525.
-
-3. Dacks, J. B., & Field, M. C. (2007). Evolution of the eukaryotic membrane-trafficking system: origin, tempo and mode. Journal of cell science, 120(17), 2977-2985.
-
-4. Munro S. 2004. Organelle identity and the organization of membrane traffic. Nature Cell Biology 6:469–472. doi: 10.1038/ncb0604-469.
-
-5. Mani, S., and Thattai, M. (2016b). Stacking the odds for Golgi cisternal maturation. eLife 10.7554/eLife.16231.
-
-6. Shukla, A., Bhattacharyya, A., Kuppusamy, L., Srivas, M., & Thattai, M. (2017). Discovering vesicle traffic network constraints by model checking. PLoS ONE, in press.
+We have previously shown that one informative constraint is graph connectivity \cite{shukla}.
 
@@
 
-vesicle traffic systems(VTS)
+Vesicle traffic systems(VTS)
 

### 2017-06-28 paper/related.tex
fixed_bib

@@
 Due to the nature of the searching (exhaustive), solving the combinatorial problem is a natural fit for the SAT solvers.
-There are many graphs related combinatorial work [1-4] that have used SAT solvers.
-Thanks to the improvement in SAT solver and formal techniques, tools like model checkers and theorem provers scalability and combinatorial solving capability are now being used to model complex biological problems [1-3].
+There are many graphs related combinatorial work \cite{gay2013solving,wotzlaw2012generalized} that have used SAT solvers.
+Thanks to the improvement in SAT solver and formal techniques, tools like model checkers and theorem provers scalability and combinatorial solving capability are now being used to model complex biological systems \cite{heule2010exact,yordanov2013smt,mangla2010timing}.
 % Many network questions are being reduced to solving a SAT question.
-Many of these biological system uses model checkers to reason about graphs and networks rules with possible exhaustive search [5-6].
+Many of these biological system uses model checkers to reason about graphs and networks rules with possible exhaustive search \cite{guerra2012reasoning,chin2008biographe}.
 
-Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) [7-9].
+Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient}.
 GNR is a complex system driven by many complex rules.
-We extended this work and have applied model checkers to the more complex transport network (VTS) [Mani and Thattai].
+We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking}.
 Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge.
 In this paper we have achieved the scalability required for analyzing vesicular transport network for eukaryotic cells, of total ten compartments (N = 10).
-
-\textbf{SAT, Bio and Graph}
-\begin{enumerate}
-\item Reasoning over Biological Networks using Maximum Satisfiability.
-\item BioGraphE: high-performance bionetwork analysis using the Biological Graph Environment.
-\item Generalized k-ary tanglegrams on level graphs: A satisfiability-based approach and its evaluation.
-\item SMT-Based Analysis of Biological Computation.
-\item A SAT-based algorithm for finding attractors in synchronous Boolean networks.
-\item ILP/SMT-Based Method for Design of Boolean Networks Based on Singleton Attractors.
-\item Exact DFA Identification Using SAT Solvers
-\item Timing Robustness in the Budding and Fission Yeast Cell Cycles.
-\item Solving Subgraph Epimorphism Problems using CLP
-and SAT.
-\end{enumerate}
-
-\textbf{GNR and SAT}
-\begin{enumerate}
-\item Model Checking Gene Regulatory Networks.
-\item Inference of Boolean Networks from Gene Interaction Graphs Using a SAT Solver
-\item Efficient parameter search for qualitative models of regulatory networks using symbolic model checking.
-\end{enumerate}
+\\
 

### 2017-07-02 paper/bio.tex
added-bio-section2

@@
 \item \mukund{Detailed BIO}
+The cell as a transport graph: We consider a cell to be a collection of
+compartments (nodes) and vesicles (edges), thus defining a transport graph.
+Compartments represent the large membrane-bound organelles, which are
+connected by constant fluxes of small transport vesicles. Every compartment
+or vesicle has a set of molecules associated with it. These include SNAREs
+and other biomolecules that regulate membrane traffic, or that play the
+role of passive cargo. Here we consider an abstract set of molecules and do
+not explicitly associate them with particular protein varieties.
+
+Molecular flows and steady state: The total amount of each molecular type
+on each compartment can increase or decrease: this is due to gain or loss
+of that molecular type driven by incoming or outgoing vesicles. Each edge
+is thus associated with a flux of all the molecular types carried by the
+corresponding vesicle. We assume the cell is in a steady state where each
+compartments composition does not vary over time, meaning that all
+incoming and outgoing fluxes are balanced for each molecular type at each
+compartment.
+
+Vesicle targeting driven by molecular interactions: The model specification
+includes a description of how molecular properties influence vesicle
+transport. A vesicle can only contain a set of molecules that are present
+on its source compartment. Once a vesicle has budded out of the source, the
+molecules it carries determine its properties. In particular, for any given
+pair of a vesicle and a compartment, the set of molecules that label the
+former and latter determine whether the vesicle will fuse to that
+compartment. Biophysically, fusion requires a direct physical interaction
+between at least one molecular type on the vesicle and one molecular type
+on the compartment. The list of molecular pairs that can drive a fusion
+event is given an a fusion pairing matrix.
+
+Molecular regulation: The final layer of our framework involves how the
+molecules are regulated. We assume that for fusion to occur, the pair of
+molecular types involved on the vesicle and compartment must both be in an
+“active” state. Whether these molecules are active or inactive depends on
+the remaining molecules found on the vesicle or compartment, respectively.
+This embodies the biological fact that other molecules can regulate the
+fusion-driving molecules. We test many different versions of molecular
+regulation. Most generally, the activity state of a given molecule can be a
+Boolean function of all the molecular types on a compartment or vesicles.
+We have also tested a particularly simple regulation mechanism in which two
+molecules that can pair to drive fusion inhibit one another. This is
+motivated by the idea that pairing must generate an inactive bi-molecular
+complex.
+
+Synthesis: We now combine all the above ingredients. Given a particular
+transport graph, a particular labeling of all the compartments and edges,
+a particular fusion pairing matrix, and a particular regulatory model we do
+the following. 1. We determine which molecules are “active” on every
+compartment or vesicle. 2. For every vesicle fusing to a compartment, we
+determine whether there exists an active pair (one molecule on the vesicle,
+one on the compartment) which drives that fusion event. 3. For every
+vesicle-compartment pair where the vesicle does not fuse to the
+compartment, we verify that there is no pairing of active molecules on the
+vesicle and compartment that could drive their fusion. 4. We verify that
+every molecular type entering a compartment also leaves the compartment,
+and also that every molecular type entering a set of compartments also
+leaves that set; this is the steady state condition. This tells us that the
+particular graph and molecular labeling does represent an allowed steady
+state configuration of a VTS.
+
 \item \srivas{Detailed BIO to Graph problem}

### 2017-07-06 paper/bio.tex
updated-paper

@@
-Again about two pages long
+%Again about two pages long
 
-\begin{itemize}
-\item \mukund{Detailed BIO}
-The cell as a transport graph: We consider a cell to be a collection of
+%\item \mukund{Detailed BIO}
+\textbf{The cell as a transport graph:} We consider a cell to be a collection of
 compartments (nodes) and vesicles (edges), thus defining a transport graph.
@@
 
-Molecular flows and steady state: The total amount of each molecular type
+\textbf{Molecular flows and steady state:} The total amount of each molecular type
 on each compartment can increase or decrease: this is due to gain or loss
@@
 
-Vesicle targeting driven by molecular interactions: The model specification
+\textbf{Vesicle targeting driven by molecular interactions:} The model specification
 includes a description of how molecular properties influence vesicle
@@
 
-Molecular regulation: The final layer of our framework involves how the
+\textbf{Molecular regulation:} The final layer of our framework involves how the
 molecules are regulated. We assume that for fusion to occur, the pair of
@@
 
-Synthesis: We now combine all the above ingredients. Given a particular
+\textbf{Synthesis:} We now combine all the above ingredients. Given a particular
 transport graph, a particular labeling of all the compartments and edges,
 a particular fusion pairing matrix, and a particular regulatory model we do
-the following. 1. We determine which molecules are “active” on every
-compartment or vesicle. 2. For every vesicle fusing to a compartment, we
+the following.
+\begin{enumerate}
+\item We determine which molecules are ``active" on every
+compartment or vesicle.
+\item or every vesicle fusing to a compartment, we
 determine whether there exists an active pair (one molecule on the vesicle,
-one on the compartment) which drives that fusion event. 3. For every
-vesicle-compartment pair where the vesicle does not fuse to the
+one on the compartment) which drives that fusion event.
+\item For every vesicle-compartment pair where the vesicle does not fuse to the
 compartment, we verify that there is no pairing of active molecules on the
-vesicle and compartment that could drive their fusion. 4. We verify that
-every molecular type entering a compartment also leaves the compartment,
+vesicle and compartment that could drive their fusion.
+\item We verify that every molecular type entering a compartment also leaves the compartment,
 and also that every molecular type entering a set of compartments also
@@
 state configuration of a VTS.
+\end{enumerate}
 
+\begin{itemize}
 \item \srivas{Detailed BIO to Graph problem}
@@
 
-The whole cell should be in stable condition i.e flow of the molecule
-is balanced at every point and globally. Each molecule leaving its
-source node on a vesicle should come back in a cycle.
+%he whole cell should be in stable condition i.e flow of the molecule is balanced at every point and globally. Each molecule leaving its source node on a vesicle should come back in a cycle.
 
 The following terms must be defined in this section
-
 \begin{itemize}

### 2017-07-06 paper/encoding.tex
updated-paper

@@
-In this section, we will formally define VTSs as a labelled graph
+In this section, we will formally define VTSs as a labeled graph
 and the conditions on the graphs that are discussed in the previous
@@
 
-We model VTSs as labelled directed graphs.
+We model VTSs as labeled directed graphs.
 The graph labels both nodes and edges with sets of molecules to denote
@@
 \begin{align}
-   \bigwedge\limits_{i,j,q, m}  e_{i,j,q,m} \limplies(  [ ( \bigvee_{m'} p_{m,m'} \land \bigwedge_{m' \neq m} p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv \neg b_{i,j,q,m})
+   \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \limplies  \bigwedge_{m' \neq m} (p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv (\neg b_{i,j,q,m} \land  \bigwedge_{m' \neq m, p_{m,m'}} \neg b_{i,j,q,m'})
   \tag{Aep}\label{eq:aep}
@@
 \subsection{SAT problems for different variants}
-\ankit{Bring model variant table here}
+%\ankit{Bring model variant table here}
 
@@
 Other cases includes different combinations of constraints on the activity on nodes and edges.
-Most general restriction is activity of the molecule is dependent on the other molecule present on the node (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
+Most general restriction is activity of the molecule is dependent on the other molecules presence on the node (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
 In very special case (E,F,G,H) activity of the molecules on the edges is dictated by pairing matrix, we call this process ``pairing inhibition".
+%In this case if the corresponding pairing molecules present on the edge with the molecules , both the molecule and all corresponding molecules gets inhibited/become inactive.
 
@@
 \end{enumerate}
+
+We have applied the tool for the above variations for searching the vesicle traffic systems that satisfies
+their corresponding properties.
+
+After creating the formula using different Boolean variables we ship them directly to the solver.
+In case of a satisfying (SAT) assignment of the added constraints the Z3 theorem prover gives a model with the variable assignment.
+In case no possible satisfying assignment the solver returns UNSAT.
+%
 %

### 2017-07-06 paper/experiments.tex
updated-paper

@@
 %
-We have applied the tool for the above variations for searching the vesicle traffic systems that satisfies
-their corresponding properties.
+% \Ankit{In other solver variations ...}
 Our tool allows user to choose a model and the size of the network besides other parameters like connectivity and number of parallel edges.
@@
 
-After creating the formula using different Boolean variables we ship them directly to the solver.
-In case of a satisfying (SAT) assignment of the added constraints the Z3 theorem prover gives a model with the variable assignment.
-In case no possible satisfying assignment the solver returns UNSAT.
-%
-% \Ankit{In other solver variations ...}
 Our tool also translates the model found by $\zthree$ into a vesicle traffic system and presents a visual
 output to the user.
-The graph provides an overview of the vesicle transport system with directed labeled edges and nodes providing the complete information about the shown graph.
 The output graph will satisfy the underlying rules of the system, so it is a valid vesicle transport network.
-Dashed lines are used in the resultant visual network output to specify which edges edges are dropped to make the graph disconnected specifying the connectivity of the graph.
+The graph provides an overview of the underlying vesicle transport system with directed labeled edges and nodes providing the complete information about the system.
+Dashed lines are used in the resultant visual network output to specify the dropped edges to make the graph disconnected, which gives information about the connectivity of the graph.
 
 \input{tbl-qf-graph}
-
-In table~\ref{tab:qf-graph}, we present the running times for the search of vesicle traffic systems of sizes 2 to 10 that satisfies the model variants.
-Formula for N = 10 returns in 45 mins with a SAT result.
+\input{tbl-qf1-graph}
+In Table 1. and Table 2.
+%~\ref{tab:qf-graph},
+we present the running times for the search of vesicle traffic systems of sizes 2 to 10 that satisfies the model variants.
+Formula for N = 10 returns in 45 minutes with a SAT result.
 In CBMC N = 10 results in OUT OF MEMORY.
@@
 % REQUIRE COMPARISION WITH CBMC RUN TIME ?
-The experiments were done on a machine with ... processor 
-and ... RAM.
+The experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor 
+and 4GB RAM.
+%
+$\zthree$ was able to solve the constraints up to 18 nodes.
 %
 
-%
-$\zthree$ was able to solve the constraints up to 15 nodes.
-%
-
-In table~\ref{tbl:qf-results}
+%table~\ref{tbl:qf-results}
 
@@
 {\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|}
     \hline
-  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity constraint}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
+  {\textbf{Version}}  & {\textbf{Constraints} &  {\textbf{Least graph connectivity}}  \\
     % \hline
     % \textbf{Inactive Modes} & \textbf{Description}\\
-    \cline{2-5}
-    {} & \multirow{1}{*} {\bf{ On compartment}} & \multirow{1}{*} {\bf{On vesicle}}  & \textbf{\textbf{Least}} & \textbf{Highest}\\
+  %  \cline{3-4}
+  %  {} & {} & \textbf{\textbf{Least}} & \textbf{Highest}\\
     %\hhline{~--}
     \hline
-E. & A\_nb & A\_eb & 2-connected & 3-connected \\ \hline
-C. & A\_nn & A\_eb & 3-connected & 3-connected \\  \hline
-F. & A\_nb & A\_ep & 4-connected & 4-connected \\ \hline
-D. & A\_nn & A\_ep & No graph & No graph \\ \hline
-B. & A\_nb & A\_en & No graph & No graph \\ \hline
-A. & A\_nn & A\_en & No graph & No graph \\ \hline
-G. & A\_nb & A\_eb + C\_ed & 3-connected & 3-connected \\ \hline
-H. & A\_nb & A\_eb + C\_es & No-idea & No-idea \\ \hline
+
+    A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph  \\ \hline
+B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph  \\ \hline
+C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected  \\  \hline
+D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph  \\ \hline
+E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected  \\ \hline
+F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected  \\ \hline
+G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected \\ \hline
+
+%A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph & No graph \\ \hline
+%B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph & No graph \\ \hline
+%C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected & 3-connected \\  \hline
+%D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph & No graph \\ \hline
+%E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected & 3-connected \\ \hline
+%F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected & 4-connected \\ \hline
+%G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected & 3-connected \\ \hline
+%H. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb  A\_eb + C\_es & No-idea & No-idea \\ \hline
 

### 2017-07-06 paper/intro.tex
updated-paper

@@
-Total two pages
+%Total two pages
 
-\begin{itemize}
-\item \mukund{BIO motivation}
+%\begin{itemize}
+%\item \mukund{BIO motivation}
 
@@
 We have recently attempted to use ideas of graph theory to address this question \cite{mani2016stacking,shukla}.
-The SNARE proteins are the focus of our current work.
+
+The SNARE proteins and the constraints that SNARE-to-SNARE regulations impose on feasibile behaviors of vesicular systems are the focus of our current work.
 Abstractly, we can think of these proteins as labels that are collected from the source compartment and taken to the target compartment on vesicles.
@@
 We have previously shown that one informative constraint is graph connectivity \cite{shukla}.
+The intricacies of SNARE regulation are largely unknown.
+How stringent SNARE regulation is can determine whether graph topologies of particular level of connectivity are biologically realizable.
+For example, if SNAREs are completely unregulated and thus always active, they cannot be used to generate a traffic network.
+If these SNAREs are regulated by relatively simple rules then only highly connected traffic networks can be generated using them.
+The question is can we work toward a predictive analytical framework of vesicle traffic?
 
-\item \srivas{BIO to Graph problem}
+The analysis of vesicle traffic systems is a difficult problem because of the combinatorial scaling of possible traffic topologies and regulatory rules.
+Previous analyses of vesicle traffic networks dealt with this combinatorial explosion by using a sampling approach: simulating randomly generated regulatory rules and taking averages over many samples \cite{mani2016stacking}.
+The outcome of such simulations is necessarily statistical rather than rigorous and precise.
+To make definite predictions about vesicle traffic network topologies, we need to efficiently check useful system properties over all possible graphs and all possible variations of rules, preferably without enumerating them.
+Formal verification tools, such as model checkers \cite{clarke1996symbolic, biere2003bounded, clarke2008birth, cimatti2000nusmv, holzmann1997model} and SAT solvers \cite{moskewicz2001chaff,een2004extensible} serve precisely this purpose.
+These tools encode the problem symbolically, and check various properties without explicit enumeration of the graphs up to large but finite size of the models.
+%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18].
 
-\item \srivas{Graph to previous encoding}
+In a recent work, we employed the model checker CBMC \cite{CKY03, ckl2004} meant to analyze ANSI C programs for studying this problem.
+In this work, vesicular systems and SNARE regulations were modeled as C code mostly using arrays to represent graphs and boolean tables.
+Queries about graph connectivity requirements for different variations of SNARE Regulations were modeled as logical assertions to be checked by the model checker.
+CBMC uses its own built-in encodings to reduce the analysis problem to boolean satisfiability problem which is solved using SAT solvers.
+This work was successful in demonstrating the feasibility of this technology to this domain.
+However, the scalability of this approach was limited (up to vesicular systems with 7-8 nodes) due to the following reasons:
+\begin{enumerate}
+\item The encoding used to model vesicular systems was not fine-tuned to the structure of the problem.
+\item The queries to be solved involve quantified formulas, i.e., we needed to solve queries of the form ``\emph{for all} graphs does  there \emph{exist} SNARE regulation constraints that satisfy biological steady state.
+\end{enumerate}
+As CBMC does not directly support solving such quantified formulas, we had to use a technique that combined non-determinism and partial enumeration that is not as efficient.\newline
+%\item \srivas{BIO to Graph problem}
 
-\end{itemize}
+%\item \srivas{Graph to previous encoding}
+
+%\end{itemize}
 
@@
 % What is vesicle traffic systems
-
-Vesicle traffic systems(VTS)
 
@@
 %
-
-In this paper, we have developed a novel SAT encoding for
+\textbf{Vesicle traffic systems(VTS)} In this paper, we have developed a novel SAT encoding for
 searching a VTS that satisfy the given properties.
@@
 We have implemented the encoding using Z3~\cite{z3} python API and searched for
-VTS satisfying various properties upto size \ankit{15} nodes as compare
-earlier tool that could only search graph upto size 8 nodes.
+VTS satisfying various properties upto size 14-18 nodes as compare
+earlier tool that could only search graph upto size 7-8 nodes.
 %
-Since most VTSs in the cells are of \ankit{10} compartments,
+Since most VTSs in the cells are of 10 compartments,
 our tool will be useful for biologists to study VTSs.
@@
 Furthermore, our encoding supports several variations of
-the conditions.
+the conditions.\newline
 

### 2017-07-06 paper/related.tex
updated-paper

@@
-\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
-
-Satisfiability was the first NP-complete problem discovered by Cook in his famous paper [ref].
-Every NP-complete problem can be reduced to solving for satisfiability.
+%\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
+Satisfiability was the first NP-complete problem discovered.
+Stephen cook's (he used the word tatutology) \cite{cook1971complexity} in his famous paper shown that every NP-complete problem can be reduced to solving for the satisfiability.
 The fact is that SAT solvers have seen a surge in the handling of millions of variables, hence many general problems are encoded as a SAT problem.
-Due to the nature of the searching (exhaustive), solving the combinatorial problem is a natural fit for the SAT solvers.
+Due to the echaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT solvers.
 There are many graphs related combinatorial work \cite{gay2013solving,wotzlaw2012generalized} that have used SAT solvers.

### 2017-07-06 qbf_bio.py

@@ -13,8 +13,6 @@ parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes
 parser.add_argument("-Q","--pedges", type=int, default=1, help = "max no.of parallel edges btw two nodes")
 parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
 parser.add_argument("-C","--connected", type=int, default=3, help = "graph connectivity want to check")
-parser.add_argument("-E","--edges", type=int, default=3, help = "graph connectivity want to check")
-
 args = parser.parse_args()
 
 M = args.mols
@@ -46,32 +44,193 @@ for i in range(6):
 #----------------------------------------------------
 # Constraint generation 
 edge = [ [ [ Bool ("e_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+E = [ edge[i][j][q] for i in range(N) for j in range(N) for q in range(Q) if i != j]
 
+#print len(E)
+#print E
+
+# Un_Skolemized dumped edges and reachability.
 dump = [ [ [Bool ("d_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+#DX = [ dump[i][j][q] for i in range(N) for j in range(N) for k in range(Q) if i != j ]
+
+#print DX
+#print len(DX)
 
 r1 = [ [Bool ("r1_{}_{}".format(i,j)) for j in range(N)] for i in range(N)]
+#RX = [ r1[i][j] for i in range(N) for j in range(N) if i != j ]
 
+#print RX
+#print len(RX)
+
+funE = len(E)
+#funE = len(E) + len(DX) + len(RX)
+lenE = funE + 1
+
+QVars = E
+#QVars = E + RX + DX
+print QVars
+
+#print funE
+#print lenE
+#sys.exit(0)
+
+# Define nodeSort that will server the purpose of the total number
+# Arguments skolem nodes,edges takes.
+nodeSort = [BoolSort() for x in range(lenE)]
+#print nodeSort
+#print len(nodeSort)
+
+#print nodeSort 
+# Skolemized presence edge
+#fnode = [ [Function ("fn_{}_{}".format(i,k), *nodeSort) for k in range(M)] for i in range(N)]
 node = [ [Bool ("n_{}_{}".format(i,k)) for k in range(M)] for i in range(N)]
 
+#for i in range(N):
+#    for k in range(M):
+#        s = []
[…]

### 2017-07-07 paper/experiments.tex
table-update
Better-tables with M/O

@@
 \input{tbl-qf-graph}
-\input{tbl-qf1-graph}
+%\input{tbl-qf1-graph}
 In Table 1. and Table 2.
@@
 and 4GB RAM.
+On this machine the CBMC encoding ran out of memory (M/O) for N $\geq$ 6 whereas new novel encoding was able to handle the case fairly easily.
+We think the main reason for such improvement are:
+\begin{enumerate}
+\item Direct encoding into the solver rather than using CFE (CBMC C front end), which treats front end variables as C variable and similarly other C overheads.
+\item Current novel encoding is fine-tuned to the structure of the problem.
+\item Improved encoding based on reachability rather than complete enumeration and non-determinism.
+\end{enumerate} 
 % 
-$\zthree$ was able to solve the constraints up to 18 nodes.
+$\zthree$ was able to solve the constraints up to 14-18 nodes (based on the versions).
 %
@@
     \hline
-  {\textbf{Version}}  & {\textbf{Constraints} &  {\textbf{Least graph connectivity}}  \\
+  {\multirow{2}{*}{\textbf{Version}}}  & {\multirow{2}{*}{\textbf{Constraints}}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
     % \hline
     % \textbf{Inactive Modes} & \textbf{Description}\\
-  %  \cline{3-4}
-  %  {} & {} & \textbf{\textbf{Least}} & \textbf{Highest}\\
+   \cline{3-4}
+   {} & {} & \textbf{\textbf{Least}} & \textbf{Highest}\\
     %\hhline{~--}
@@
 
-    A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph  \\ \hline
-B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph  \\ \hline
-C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected  \\  \hline
-D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph  \\ \hline
-E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected  \\ \hline
-F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected  \\ \hline
-G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected \\ \hline
+%    A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph  \\ \hline
+%B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph  \\ \hline
+%C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected  \\  \hline
+%D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph  \\ \hline
+%E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected  \\ \hline
+%F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected  \\ \hline
+%G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected \\ \hline
 
-%A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph & No graph \\ \hline
-%B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph & No graph \\ \hline
-%C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected & 3-connected \\  \hline
-%D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph & No graph \\ \hline
-%E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected & 3-connected \\ \hline
-%F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected & 4-connected \\ \hline
-%G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected & 3-connected \\ \hline
+A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph & No graph \\ \hline
+B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph & No graph \\ \hline
+C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected & 3-connected \\  \hline
+D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph & No graph \\ \hline
+E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected & 3-connected \\ \hline
+F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected & 4-connected \\ \hline
+G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected & 3-connected \\ \hline
 %H. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb  A\_eb + C\_es & No-idea & No-idea \\ \hline

### 2017-07-08 paper/experiments.tex
table with cheap comparisison

@@
 
+\begin{tikzpicture}
+
+  \begin{axis}[title  = CBMC Vs Z3 encoding for N $\equal$ 5 (in secs),
+    xbar,
+    y axis line style = { opacity = 0 },
+    axis x line       = none,
+    tickwidth         = 0pt,
+    enlarge y limits  = 0.32,
+    enlarge x limits  = 0.04,
+    symbolic y coords = {Version F, Version E, Version C, Version A},
+    nodes near coords,
+    legend pos=outer north east,
+  ]
+  \legend{CBMC, Z3}
+  \addplot coordinates { (3053.8,Version A)         (500.03,Version C)
+                         (890.84,Version E)  (2482.71,Version F) };
+  \addplot coordinates { (7.7,Version A)         (7.60,Version C)
+                         (10.27,Version E)   (33.36,Version F)  };
+
+  \end{axis}
+\end{tikzpicture}
+
 % REQUIRE COMPARISION WITH CBMC RUN TIME ?
@@
    \cline{3-4}
-   {} & {} & \textbf{\textbf{Least}} & \textbf{Highest}\\
+   {} & {} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\
     %\hhline{~--}

### 2017-07-08 paper/pm-1-matrix.tex
added-pairing matrix

\begin{figure}
\centering
\begin{tikzpicture}
\matrix [matrix of math nodes,left delimiter=(,right delimiter=),row sep=0.5cm,column sep=0.5cm] (m) {
\times & \times & \times &\times&\times&\times & 1 & \times\\
\times & \times & \times&\times&\times&1& \times &\times \\
\times & \times & \times&\times&1&\times&\times &\times\\
\times & \times & \times&\times & \times & \times &\times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times &\times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times&\times & \times\\};

\draw[dashed] ($0.5*(m-1-4.north east)+0.5*(m-1-5.north west)$) --
     ($0.5*(m-8-5.south east)+0.5*(m-8-4.south west)$);

\draw[dashed] ($0.5*(m-4-1.south west)+0.5*(m-5-1.north west)$) --
 ($0.5*(m-4-8.south east)+0.5*(m-5-8.north east)$);

\node[above=10pt of m-1-1] (top-1) {$M_1$};
\node[above=10pt of m-1-2] (top-2) {$M_2$};
\node[above=10pt of m-1-3] (top-3) {$M_3$};
\node[above=10pt of m-1-4] (top-4) {$M_4$};
\node[above=10pt of m-1-5] (top-5) {$M_5$};
\node[above=10pt of m-1-6] (top-6) {$M_6$};
\node[above=10pt of m-1-7] (top-7) {$M_7$};
\node[above=10pt of m-1-8] (top-8) {$M_8$};

\node[left=12pt of m-1-1] (left-1) {$M_1$};
\node[left=12pt of m-2-1] (left-2) {$M_2$};
\node[left=12pt of m-3-1] (left-3) {$M_3$};
\node[left=12pt of m-4-1] (left-4) {$M_4$};
\node[left=12pt of m-5-1] (left-5) {$M_5$};
\node[left=12pt of m-6-1] (left-6) {$M_6$};
\node[left=12pt of m-7-1] (left-7) {$M_7$};
\node[left=12pt of m-8-1] (left-8) {$M_8$};

\node[rectangle,above delimiter=\{] (del-top-1) at ($0.5*(top-1.south) +0.5*(top-4.south)$) {\tikz{\path (top-1.south west) rectangle (top-4.north east);}};
\node[above=10pt] at (del-top-1.north) {$Q-Snares$};
\node[rectangle,above delimiter=\{] (del-top-2) at ($0.5*(top-5.south) +0.5*(top-8.south)$) {\tikz{\path (top-4.south west) rectangle (top-6.north east);}};
\node[above=10pt] at (del-top-2.north) {$R-Snares$};

\node[rectangle,left delimiter=\{] (del-left-1) at ($0.5*(left-1.east) +0.5*(left-4.east)$) {\tikz{\path (left-1.north east) rectangle (left-4.south west);}};
\node[left=10pt] at (del-left-1.west) {$Q-Snares$};
\node[rectangle,left delimiter=\{] (del-left-2) at ($0.5*(left-5.east) +0.5*(left-8.east)$) {\tikz{\path (left-5.north east) rectangle (left-8.south west);}};
\node[left=10pt] at (del-left-2.west) {$R-Snares$};

\begin{pgfonlayer}{myback}

%\foreach \element in {m-1-1,m-6-5,m-5-3}{
%\highlight[pink]{\element}{\element}
%}
\foreach \element in {m-1-7,m-2-6,m-3-5}{
\highlight[blue!50]{\element}{\element}
}
\end{pgfonlayer}

\end{tikzpicture}

\caption{Pairing matrix} \label{fig:M1}
\end{figure}

### 2017-07-11 paper/experiments.tex
added-pairing matrix
added dia

--- 2017-07-07 paper/experiments.tex
@@
 The basic idea is to constraint the variables such that vesicular transport rules are respected and using constraints (D0-D5) reason about the connectivity of the underlying structure (graph).
-We are interested in both least connectivity requirement (LRC) and least guarantee connectivity (LGC).
+
+% We are interested in both least connectivity requirement (LRC) and least guarantee connectivity (LGC).
 %LCR, that is required for a vesicular transport version to work and least connectivity that guarantees that vesicular transport system with that connectivity will always satisfies the rules.
@@
 % \Ankit{In other solver variations ...}
-Our tool allows user to choose a model and the size of the network besides other parameters like connectivity and number of parallel edges.
-Our tool uses Z3 python interface to build the needed constraints and applies $\zthree$ on the constraints.
-
-Our tool also translates the model found by $\zthree$ into a vesicle traffic system and presents a visual
-output to the user.
-The output graph will satisfy the underlying rules of the system, so it is a valid vesicle transport network.
-The graph provides an overview of the underlying vesicle transport system with directed labeled edges and nodes providing the complete information about the system.
+Our tool allows the user to choose a model and the size of the network besides other parameters like connectivity and number of parallel edges.
+It uses Z3 Python interface to build the needed constraints and applies $\zthree$ solver on the constraints to find a model ( a satisfying assignment that respects the constraints).
+This tool also translates the satisfying model found by $\zthree$ into a vesicle traffic system and presents a visual output to the user in form of annotated graph.
+The output graph will satisfy the underlying rules of the system, so it always is a valid vesicle transport network.
+The resultant graph provides an overview of the underlying vesicle transport system where directed labeled edges and nodes provide the complete information about the system.
 Dashed lines are used in the resultant visual network output to specify the dropped edges to make the graph disconnected, which gives information about the connectivity of the graph.
@@
 %\input{tbl-qf1-graph}
-In Table 1. and Table 2.
+In Table 1. 
 %~\ref{tab:qf-graph},
 we present the running times for the search of vesicle traffic systems of sizes 2 to 10 that satisfies the model variants.
-Formula for N = 10 returns in 45 minutes with a SAT result.
-In CBMC N = 10 results in OUT OF MEMORY.
-Hence with use of this novel encoding we are able to scale the system to much larger compartmentalized systems especially eukaryotics cells with ten compartments.
-This additional cushion of scalability can provide us leverage to ask for more questions that were not previously possible for example what is the minimum number of molecules required to satisfy the vesicular traffic system in eukaryotes.
+For example, the formula for variation F, the total number of compartments (N) equals to 10, returns in 129.78 minutes (7786.8 secs) with a SAT result.
+In comparison, CBMC encoding results in OUT OF MEMORY for the same variation and same compartment size.
+Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to eukaryotic cells with a total number of ten compartments.
+This additional cushion of scalability can provide us leverage to ask for related open questions that were not previously possible, for example, what is the minimum number of molecules required to satisfy the vesicular traffic system in eukaryotes.
+
+\input{cz-comparision}
 
 % REQUIRE COMPARISION WITH CBMC RUN TIME ?
-The experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor 
-and 4GB RAM.
-On this machine the CBMC encoding ran out of memory (M/O) for N $\geq$ 6 whereas new novel encoding was able to handle the case fairly easily.
-We think the main reason for such improvement are:
+The experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM.
+On this machine, the CBMC encoding ran out of memory (M/O) for N $\geq$ 6 whereas new novel encoding was able to handle the case fairly easily.
+We think the main reasons for such an improvement are the following:
 \begin{enumerate}

### 2017-07-11 paper/related.tex
added dia

@@
 Satisfiability was the first NP-complete problem discovered.
-Stephen cook's (he used the word tatutology) \cite{cook1971complexity} in his famous paper shown that every NP-complete problem can be reduced to solving for the satisfiability.
+Stephen cook's in his famous paper \cite{cook1971complexity} (he used the word tautology) shown that every NP-complete problem can be reduced to solving for the satisfiability.
 The fact is that SAT solvers have seen a surge in the handling of millions of variables, hence many general problems are encoded as a SAT problem.
-Due to the echaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT solvers.
+Due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT solvers.
 There are many graphs related combinatorial work \cite{gay2013solving,wotzlaw2012generalized} that have used SAT solvers.
@@
 Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge.
-In this paper we have achieved the scalability required for analyzing vesicular transport network for eukaryotic cells, of total ten compartments (N = 10).
+In this paper, we have achieved the scalability required for analyzing vesicular transport network for eukaryotic cells, of total ten compartments (N = 10).
 \\

### 2017-07-13 paper/bio.tex
changes

@@
 %Again about two pages long
+%
+In this section, we will describe the model of VTSs and the properties
+relevant to the biologists.
 
-%\item \mukund{Detailed BIO}
-\textbf{The cell as a transport graph:} We consider a cell to be a collection of
-compartments (nodes) and vesicles (edges), thus defining a transport graph.
+\textbf{The cell as a transport graph:} We consider a cell to be a
+collection of compartments (nodes) and vesicles (edges), thus defining
+a transport graph.
+%
 Compartments represent the large membrane-bound organelles, which are
-connected by constant fluxes of small transport vesicles. Every compartment
-or vesicle has a set of molecules associated with it. These include SNAREs
-and other biomolecules that regulate membrane traffic, or that play the
-role of passive cargo. Here we consider an abstract set of molecules and do
+connected by constant fluxes of small transport vesicles.
+%
+Every compartment or vesicle has a set of molecules associated with
+it.
+%
+These include SNAREs and other biomolecules that regulate membrane
+traffic, or that play the role of passive cargo.
+%
+Here we consider an abstract set of molecules and do
 not explicitly associate them with particular protein varieties.
 
-\textbf{Molecular flows and steady state:} The total amount of each molecular type
-on each compartment can increase or decrease: this is due to gain or loss
-of that molecular type driven by incoming or outgoing vesicles. Each edge
-is thus associated with a flux of all the molecular types carried by the
-corresponding vesicle. We assume the cell is in a steady state where each
-compartments composition does not vary over time, meaning that all
-incoming and outgoing fluxes are balanced for each molecular type at each
+\textbf{Molecular flows and steady state:} The total amount of each
+molecular type on each compartment can increase or decrease: this is
+due to gain or loss of that molecular type driven by incoming or
+outgoing vesicles.
+%
+Each edge is thus associated with a flux of all the molecular types
+carried by the corresponding vesicle.
+%
+We assume the cell is in a steady state where each compartments
+composition does not vary over time, meaning that all incoming and
+outgoing fluxes are balanced for each molecular type at each
 compartment.
 
-\textbf{Vesicle targeting driven by molecular interactions:} The model specification
-includes a description of how molecular properties influence vesicle
-transport. A vesicle can only contain a set of molecules that are present
-on its source compartment. Once a vesicle has budded out of the source, the
-molecules it carries determine its properties. In particular, for any given
-pair of a vesicle and a compartment, the set of molecules that label the
-former and latter determine whether the vesicle will fuse to that
-compartment. Biophysically, fusion requires a direct physical interaction
-between at least one molecular type on the vesicle and one molecular type
-on the compartment. The list of molecular pairs that can drive a fusion
-event is given an a fusion pairing matrix.
+\textbf{Vesicle targeting driven by molecular interactions:} The model
+specification includes a description of how molecular properties
+influence vesicle transport.
+%
+A vesicle can only contain a set of molecules that are present
+on its source compartment.
+%
+Once a vesicle has budded out of the source, the molecules it carries
+determine its properties.
+%
+In particular, for any given pair of a vesicle and a compartment, the
+set of molecules that label the former and latter determine whether
+the vesicle will fuse to that compartment.
+%
+Biophysically, fusion requires a direct physical interaction between
+at least one molecular type on the vesicle and one molecular type on
+the compartment.
+%
+The list of molecular pairs that can drive a fusion event is given an
+a fusion pairing matrix.
 
-\textbf{Molecular regulation:} The final layer of our framework involves how the
-molecules are regulated. We assume that for fusion to occur, the pair of
-molecular types involved on the vesicle and compartment must both be in an
-“active” state. Whether these molecules are active or inactive depends on
-the remaining molecules found on the vesicle or compartment, respectively.
+\textbf{Molecular regulation:} The final layer of our framework
+involves how the molecules are regulated.
+%
+We assume that for fusion to occur, the pair of molecular types
+involved on the vesicle and compartment must both be in an
+“active” state.
+%
+Whether these molecules are active or inactive depends on the
+remaining molecules found on the vesicle or compartment, respectively.
+%
 This embodies the biological fact that other molecules can regulate the
-fusion-driving molecules. We test many different versions of molecular
-regulation. Most generally, the activity state of a given molecule can be a
+fusion-driving molecules.
+%
+VTSs also require that if molecule is involved in fusion of some
+vesicle and compartment, it must not be possible that the molecule 
+can potentially fuse with some molecule in some other compartment.
+%
+
+We test many different versions of molecular
+regulation.
+%
+Most generally, the activity state of a given molecule can be a
 Boolean function of all the molecular types on a compartment or vesicles.
 We have also tested a particularly simple regulation mechanism in which two
-molecules that can pair to drive fusion inhibit one another. This is
+molecules that can pair to drive fusion inhibit one another.
+%
+This is
 motivated by the idea that pairing must generate an inactive bi-molecular
@@
 
-\textbf{Synthesis:} We now combine all the above ingredients. Given a particular
+\textbf{Synthesis:} We now combine all the above ingredients.
+%
+Given a particular
 transport graph, a particular labeling of all the compartments and edges,
@@
 and also that every molecular type entering a set of compartments also
-leaves that set; this is the steady state condition. This tells us that the
+leaves that set; this is the steady state condition.
+%
+This tells us that the
 particular graph and molecular labeling does represent an allowed steady
@@
 
-\begin{itemize}
-\item \srivas{Detailed BIO to Graph problem}
-\end{itemize}
-
-%he whole cell should be in stable condition i.e flow of the molecule is balanced at every point and globally. Each molecule leaving its source node on a vesicle should come back in a cycle.
-
-The following terms must be defined in this section
-\begin{itemize}
-\item Vesicular traffic network.
-\item Recycling of molecules, steady state.
-\item Maximum connectivity [LGC, Least guarantee connectivity] and minimal connective [LRC (least required connectivity)] (rather than necc and suff cond) required by the graph. 
-\item Connected-ness. 3 and 4.
-\item Pairing mechanism (matrix).
-\item Fusion rules, inhibition/regulation mechanism, Pairing inhibition.
-\item Potential to connect.
-\item Property of interest.
-\item Reachability definition.
-\end{itemize}
+Given the above conditions, the biologists search for VTSs that are
+not $k$-connected, i.e., every pair of compartments remain reachable
+after dropping $k$ vesicles.\ashu{why asking this question}
+\ankit{Maximum connectivity [LGC, Least guarantee connectivity] and minimal connective [LRC (least required connectivity)] (rather than necc and suff cond) required by the graph.}
 

### 2017-07-13 paper/encoding.tex
table-update
added-pairing matrix
added dia
changes

@@
 For example, unique edge between two nodes, activity of molecules is
-not constrained by $\nodef$ and $\edgef$, and \ashu{other
-variations?}.
+not constrained by $\nodef$ and $\edgef$, etc.
 %
@@
 \paragraph{Search problem}
-
 Based upon earlier discussion, we need to answer the following search
-question for ......\ashu{match with the earlier text}
+question among VTSs.
 For a given $k$, size $\nu$, and molecule number $\mu$,
@@
 
-Condition on $p_{kk'}$. \ashu{why???} Diagonal blocks should be all 0's.
-
+Since a molecule cannot be both SNARE and tether,
+we set diagonal blocks in pairing matrix to be 0's.
+It reduces the search space.
+% Condition on $p_{kk'}$. \ashu{why???} .
 \begin{align}
@@
 %\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
-\item Version F but self-edges are allowed.
+%\item Version F but self-edges are allowed.
 \end{enumerate}
@@
 their corresponding properties.
+
+\input{pm-1-matrix}
+\input{v2-dia}
 

### 2017-07-13 paper/intro.tex
changes

@@
 
-The conservation of basic molecular processes across all living cells, including the genetic code, suggests that life on Earth arose only once: all extant organisms are presumed to trace their lineages back to a last universal common ancestor (LUCA).
-However, there are still vast differences in cellular and molecular architecture among the three kingdoms of life: bacteria, archaea, and eukaryotes \cite{embley2006eukaryotic}.
-Eukaryotic cells have larger genomes and have more complex cellular architectures than the prokaryotic bacteria and archaea.
-In particular, the cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
-Cargo is moved between these organelles in small membrane-bound transporters known as vesicles \cite{stenmark2009rab}.
+The conservation of basic molecular processes across all living cells,
+including the genetic code, suggests that life on Earth arose only
+once: all extant organisms are presumed to trace their lineages back
+to a last universal common ancestor (LUCA).
+%
+However, there are still vast differences in cellular and molecular
+architecture among the three kingdoms of life: bacteria, archaea, and
+eukaryotes~\cite{embley2006eukaryotic}.
+%
+Eukaryotic cells have larger genomes and have more complex cellular
+architectures than the prokaryotic bacteria and archaea.
+%
+In particular, the cytoplasm of all eukaryotic cells is broken up into
+distinct membrane-bound locations known as organelles: the nuclear
+membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and
+lysosomes are examples of these.
+%
+Cargo is moved between these organelles in small membrane-bound
+transporters known as vesicles \cite{stenmark2009rab}.
 
-This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
-Membrane traffic underpins nearly every aspect of eukaryotic cellular physiology, including human cellular physiology.
-Defects in membrane traffic lead to a variety of disorders or even cell death \cite{stenmark2009rab}.
-Understanding how membrane traffic functions is therefore one of the central challenges of cell biology.
-Some progress has been made, as cell biologists have assembled a “parts list” of molecules that drive vesicle traffic \cite{dacks2007evolution}.
-The essential processes involve the creation of vesicles loaded with cargo from source organelles, known as “budding”, and the depositing of those vesicles and cargo into target organelles, known as “fusion” \cite{munro2004organelle}.
-Budding is regulated by proteins known as coats and adaptors that select cargo.
-Fusion is regulated by proteins known as SNAREs and tethers, that ensure that vesicles fuse to the correct target \cite{mani2016stacking}.
-Although we know a great deal about molecular-level details, there has been very little work done on how such processes are integrated across scales to build the entire vesicle traffic system.
-We have recently attempted to use ideas of graph theory to address this question \cite{mani2016stacking,shukla}.
+This organization resembles a transport logistics network, and is
+commonly known as the membrane traffic system.
+%
+Membrane traffic underpins nearly every aspect of eukaryotic cellular
+physiology, including human cellular physiology.
+%
+Defects in membrane traffic lead to a variety of disorders or even
+cell death \cite{stenmark2009rab}.
+%
+Understanding how membrane traffic functions is therefore one of the
+central challenges of cell biology.
+%
+Some progress has been made, as cell biologists have assembled a
+“parts list” of molecules that drive vesicle
+traffic~\cite{dacks2007evolution}.
+%
+The essential processes involve the creation of vesicles loaded with
+cargo from source organelles, known as “budding”, and the depositing
+of those vesicles and cargo into target organelles, known as “fusion”
+\cite{munro2004organelle}.
+%
+Budding is regulated by proteins known as coats and adaptors that
+select cargo.
+%
+Fusion is regulated by proteins known as SNAREs and tethers, that
+ensure that vesicles fuse to the correct target
+\cite{mani2016stacking}.
+%
+Although we know a great deal about molecular-level details, there has
+been very little work done on how such processes are integrated across
+scales to build the entire vesicle traffic system (VTS).
+%
+We have recently attempted to use ideas of graph theory to address
+this question \cite{mani2016stacking,shukla}.
 
-The SNARE proteins and the constraints that SNARE-to-SNARE regulations impose on feasibile behaviors of vesicular systems are the focus of our current work.
-Abstractly, we can think of these proteins as labels that are collected from the source compartment and taken to the target compartment on vesicles.
+The SNARE proteins and the constraints that SNARE-to-SNARE regulations
+impose on feasibile behaviors of VTSs are the focus of
+our current work.
+%
+Abstractly, we can think of these proteins as labels that are
+collected from the source compartment and taken to the target
+compartment on vesicles.
+%
 There is a corresponding set of label molecules on the target compartments.
-If the two sets of labels (on vesicles and targets) are compatible, then the vesicle will fuse.
-The question is: does this physical picture place any constrains on the global topology of the traffic graph?
-We have previously shown that one informative constraint is graph connectivity \cite{shukla}.
+%
+If the two sets of labels (on vesicles and targets) are compatible,
+then the vesicle will fuse.
+%
+The question is: does this physical picture place any constrains on
+the global topology of the traffic graph? We have previously shown
+that one informative constraint is graph connectivity \cite{shukla}.
+%
 The intricacies of SNARE regulation are largely unknown.
-How stringent SNARE regulation is can determine whether graph topologies of particular level of connectivity are biologically realizable.
-For example, if SNAREs are completely unregulated and thus always active, they cannot be used to generate a traffic network.
-If these SNAREs are regulated by relatively simple rules then only highly connected traffic networks can be generated using them.
-The question is can we work toward a predictive analytical framework of vesicle traffic?
+%
+How stringent SNARE regulation is can determine whether graph
+topologies of particular level of connectivity are biologically
+realizable.
+%
+For example, if SNAREs are completely unregulated and thus always
+active, they cannot be used to generate a traffic network.
+%
+If these SNAREs are regulated by relatively simple rules then only
+highly connected traffic networks can be generated using them.
+%
+The question is can we work toward a predictive analytical framework
+of VTSs?
 
-The analysis of vesicle traffic systems is a difficult problem because of the combinatorial scaling of possible traffic topologies and regulatory rules.
-Previous analyses of vesicle traffic networks dealt with this combinatorial explosion by using a sampling approach: simulating randomly generated regulatory rules and taking averages over many samples \cite{mani2016stacking}.
-The outcome of such simulations is necessarily statistical rather than rigorous and precise.
-To make definite predictions about vesicle traffic network topologies, we need to efficiently check useful system properties over all possible graphs and all possible variations of rules, preferably without enumerating them.
-Formal verification tools, such as model checkers \cite{clarke1996symbolic, biere2003bounded, clarke2008birth, cimatti2000nusmv, holzmann1997model} and SAT solvers \cite{moskewicz2001chaff,een2004extensible} serve precisely this purpose.
-These tools encode the problem symbolically, and check various properties without explicit enumeration of the graphs up to large but finite size of the models.
+The analysis of VTSs is a difficult problem because
+of the combinatorial scaling of possible traffic topologies and
+regulatory rules.
+%
+Previous analyses of VTSs dealt with this combinatorial explosion by
+using a sampling approach: simulating randomly generated regulatory
+rules and taking averages over many samples~\cite{mani2016stacking}.
+%
+The outcome of such simulations is necessarily statistical rather than
+rigorous and precise.
+%
+To make definite predictions about VTS topologies, we need to
+efficiently check useful system properties over all possible graphs
+and all possible variations of rules, preferably without enumerating
+them.
+%
+Formal verification tools, such as model checkers
+\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
+cimatti2000nusmv, holzmann1997model} and SAT solvers
+\cite{moskewicz2001chaff,een2004extensible} serve precisely this
+purpose.
+%
+These tools encode the problem symbolically, and check various
+properties without explicit enumeration of the graphs up to large but
+finite size of the models.
+
 %These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18].
 
-In a recent work, we employed the model checker CBMC \cite{CKY03, ckl2004} meant to analyze ANSI C programs for studying this problem.
-In this work, vesicular systems and SNARE regulations were modeled as C code mostly using arrays to represent graphs and boolean tables.
-Queries about graph connectivity requirements for different variations of SNARE Regulations were modeled as logical assertions to be checked by the model checker.
-CBMC uses its own built-in encodings to reduce the analysis problem to boolean satisfiability problem which is solved using SAT solvers.
-This work was successful in demonstrating the feasibility of this technology to this domain.
-However, the scalability of this approach was limited (up to vesicular systems with 7-8 nodes) due to the following reasons:
+In a recent work, we employed the model checker CBMC \cite{CKY03,
+ckl2004} meant to analyze ANSI C programs for studying this problem.
+%
+In this work, VTSs and SNARE regulations were modeled as C code mostly
+using arrays to represent graphs and boolean tables.
+%
+Queries about graph connectivity requirements for different variations
+of SNARE Regulations were modeled as logical assertions to be checked
+by the model checker.
+%
+CBMC uses its own built-in encodings to reduce the analysis problem to
+boolean satisfiability problem which is solved using SAT solvers.
+%
+This work was successful in demonstrating the feasibility of this
+technology to this domain.
+%
+However, the scalability of this approach was limited (up to VTSs
+with 7-8 nodes) due to the following reasons:
 \begin{enumerate}
-\item The encoding used to model vesicular systems was not fine-tuned to the structure of the problem.
-\item The queries to be solved involve quantified formulas, i.e., we needed to solve queries of the form ``\emph{for all} graphs does  there \emph{exist} SNARE regulation constraints that satisfy biological steady state.
-\end{enumerate}
-As CBMC does not directly support solving such quantified formulas, we had to use a technique that combined non-determinism and partial enumeration that is not as efficient.\newline
-%\item \srivas{BIO to Graph problem}
-
-%\item \srivas{Graph to previous encoding}
-
-%\end{itemize}
-
-% \noindent
-
-% What is vesicle traffic systems
-
-% Graph properties of the systems
-
-% Search queries; why bio imp
-
-% Using SAT/QBF solvers to encode
+\item The encoding used to model VTSs was not fine-tuned
+to the structure of the problem.
+\item The queries to be solved involve quantified formulas, i.e., we
+needed to solve queries of the form ``\emph{for all} graphs does there
+\emph{exist} SNARE regulation constraints that satisfy biological
+steady state.
+\end{enumerate} As CBMC does not directly support solving such
+quantified formulas, we had to use a technique that combined
+non-determinism and partial enumeration that is not as
+efficient.\newline
 
 %
-\textbf{Vesicle traffic systems(VTS)} In this paper, we have developed a novel SAT encoding for
+In this paper, we have developed a novel SAT encoding for
 searching a VTS that satisfy the given properties.

### 2017-07-13 paper/pm-1-matrix.tex
added dia
changes

@@
 \centering
+\begin{minipage}{0.45\linewidth}
+  \hspace{-4ex}
 \begin{tikzpicture}
-\matrix [matrix of math nodes,left delimiter=(,right delimiter=),row sep=0.5cm,column sep=0.5cm] (m) {
-\times & \times & \times &\times&\times&\times & 1 & \times\\
-\times & \times & \times&\times&\times&1& \times &\times \\
-\times & \times & \times&\times&1&\times&\times &\times\\
-\times & \times & \times&\times & \times & \times &\times & \times\\
+\matrix [matrix of math nodes,left delimiter=(,right delimiter=),row sep=0.16cm,column sep=0.1cm] (m) {
+\times & \times & \times &\times&\times&\times & \times & \times\\
+\times & \times & \times&\times&\times&\times& 1 &\times \\
+\times & \times & \times&\times&\times&1&\times &\times\\
+\times & \times & \times&\times & 1 & \times &\times & \times\\
  \times & \times & \times & \times & \times & \times & \times & \times\\
@@
 
-\node[above=10pt of m-1-1] (top-1) {$M_1$};
-\node[above=10pt of m-1-2] (top-2) {$M_2$};
-\node[above=10pt of m-1-3] (top-3) {$M_3$};
-\node[above=10pt of m-1-4] (top-4) {$M_4$};
-\node[above=10pt of m-1-5] (top-5) {$M_5$};
-\node[above=10pt of m-1-6] (top-6) {$M_6$};
-\node[above=10pt of m-1-7] (top-7) {$M_7$};
-\node[above=10pt of m-1-8] (top-8) {$M_8$};
+\node[above=4pt of m-1-1] (top-1) {$M_1$};
+\node[above=4pt of m-1-2] (top-2) {$M_2$};
+\node[above=4pt of m-1-3] (top-3) {$M_3$};
+\node[above=4pt of m-1-4] (top-4) {$M_4$};
+\node[above=4pt of m-1-5] (top-5) {$M_5$};
+\node[above=4pt of m-1-6] (top-6) {$M_6$};
+\node[above=4pt of m-1-7] (top-7) {$M_7$};
+\node[above=4pt of m-1-8] (top-8) {$M_8$};
 
@@
 \node[rectangle,left delimiter=\{] (del-left-1) at ($0.5*(left-1.east) +0.5*(left-4.east)$) {\tikz{\path (left-1.north east) rectangle (left-4.south west);}};
-\node[left=10pt] at (del-left-1.west) {$Q-Snares$};
+\node[left=15pt,rotate=90,xshift=9mm] at (del-left-1.west) {$Q-Snares$};
 \node[rectangle,left delimiter=\{] (del-left-2) at ($0.5*(left-5.east) +0.5*(left-8.east)$) {\tikz{\path (left-5.north east) rectangle (left-8.south west);}};
-\node[left=10pt] at (del-left-2.west) {$R-Snares$};
+\node[left=15pt,rotate=90,xshift=9mm] at (del-left-2.west) {$R-Snares$};
 
@@
 
-%\foreach \element in {m-1-1,m-6-5,m-5-3}{
-%\highlight[pink]{\element}{\element}
-%}
-\foreach \element in {m-1-7,m-2-6,m-3-5}{
-\highlight[blue!50]{\element}{\element}
+\foreach \element in {m-1-7,m-3-8,m-5-1,m-5-2,m-5-3,m-5-4,m-6-1,m-6-2,m-6-3,m-6-4,m-7-1,m-7-2,m-7-3,m-7-4,m-8-1,m-8-2,m-8-3,m-8-4}{
+\highlight[pink]{\element}{\element}
+}
+\foreach \element in {m-2-7,m-3-6,m-4-5}{
+\fhighlight[blue!10]{\element}{\element}
 }
@@
 \end{tikzpicture}  
+\end{minipage}
+\begin{minipage}{0.45\linewidth}
+  \tikzset{
+    ln/.style  = { draw, thick, fill=black, circle, inner sep=0.3mm},
+    sqloc/.style  = { draw, thick, inner sep=1.0mm },
+    loc/.style    = { draw, circle, thick, inner sep=1.0mm },
+  }
+\begin{tikzpicture}
+  \node[draw] (n0) {$n_1:\{0,1,2,3,4\}$};
+  \node[draw,below left of=n0] (n1) {$n_1:\{0,1,2,3,4\}$};
+  \node[draw] (n2) {$n_1:\{0,1,2,3,4\}$};
+
+    \entity[yshift=-20mm] (E) {$n_1$ $[m_0 m_1 m_2 m_3 m_4]$};
+    % \entity (E) {Node1\\[]};
+    \binary[left=of E.north west, unique=2] (h) {};
+
+       % \binary[left=of E.north west, unique=1-2] (w) {};
+
+    \binary[left=of E.south west, unique=1-2](i) [below=6mm of h]{};
+    \node[role name, at=(i.north),anchor=south] {[$m_{0} m_{1} m_{3}$]};
+    \plays[] (E) to (i.east);
+   % \plays(h) to (i);
+%         label=below:\ormleft{uses] (u) {};
+\node[role name,
+at=(h.north),anchor=south] {[$m_{0} m_{1}$]};
+
+    \entity[left=of h] (Rank) {$n_0:m_0 m_1 m_2 m_3 m_6$};
+
+    \plays[mandatory] (E) to (h.east);
+    \plays (h) to (Rank) (E);
+    \plays[mandatory] (Rank) to (i.west);
+    %to (u.east) (u) to (Car);
+
+    \binary[right=of E.north east] (b) {};
+    \node[role name,
+at=(b.north),anchor=south] {[$m_{0} m_{1}$]};
+       % \binary[right=of E.north east] (dd) {};
+
+    \binary[right=of E.south east, unique,] (i) {};
+    \node[role name,
+at=(i.north),anchor=south] {[$m_{1} m_{2} m_{3}$]};
+\binary[unique=1-2,skip unique=1-2] (xyz) [above=6mm of h] {};
+% describes blue label above h Left uppermost
+\node[role name,
+at=(xyz.north),anchor=south] {[$m_{0} m_{1} m_{3}$]};
+
+      \plays (Rank) to (xyz.west); 
+    \plays[mandatory] (E) to (xyz.east);
+
+    \entity[right=1.8 of E] (Date) {$n_2: m_1 m_2 m_3 m_6 m_8$};
+
+    \plays[mandatory] (E) to (b.west); 
+    \plays (E) to (i.west);
+    \plays (b.east) to (Date);
+    \plays[mandatory] (Date) to (i.east);
+
+%    \entity[label={[constraint]\#=$n$}] {E};
+%\draw (Rank) to node[vroles,label=has,label=below:\ormup{of}]{} (E);
+%\node[constraint,anchor=north west,inner ysep=0]
+%at (h.) {\ormbraces{a, b, c}};
+%\draw (E) to node[roles,
+%label=below:drives]{} (Rank);
+
+\node[roles=2][,unique=1-2,skip unique=2] (abc) [below=11mm of E] {};
+\node[role name,
+at=(abc.north),anchor=south] {[$m_{2} m_{3}$]};
+\plays[mandatory] (Rank.south) -- (abc.west);  
+\plays (abc.east) -- (Date.south);
+
+  %  \node[role name, anchor=south west] at (b.east) {[birthdate]};
+  %  \node[role name, anchor=north west] at (i.east) {[hiredate]};
+
+%     \rules at (-.4, -2) {
+%          \node[rule=1] {{$m_{2}$} $m_{3}$};\\
+%      };
+\end{tikzpicture}
+\end{minipage}
 
@@
 \end{figure}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2017-07-13 paper/pm-1-matrix.tex
new figure

@@
   }
-\begin{tikzpicture}
-  \node[draw] (n0) {$n_1:\{0,1,2,3,4\}$};
-  \node[draw,below left of=n0] (n1) {$n_1:\{0,1,2,3,4\}$};
-  \node[draw] (n2) {$n_1:\{0,1,2,3,4\}$};
+\begin{tikzpicture}[node distance = 30mm]
+  \node[draw] (n0) {$n_1:\{01234\}$};
+  \node[draw,below left of=n0] (n1) {$n_0:\{01236\}$};
+  \node[draw,below right of=n0] (n2) {$n_2:\{012368\}$};
 
-    \entity[yshift=-20mm] (E) {$n_1$ $[m_0 m_1 m_2 m_3 m_4]$};
-    % \entity (E) {Node1\\[]};
-    \binary[left=of E.north west, unique=2] (h) {};
+  \draw[->,thick] (n1) -- node[left=1mm]  {$01$} (n0);
+  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$013$} (n0);
+  \draw [->,thick] (n0) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n1);
 
-       % \binary[left=of E.north west, unique=1-2] (w) {};
+  \draw [->,thick] (n1) -- node[below=1mm]  {$123$} (n2);
+  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$01$} (n1);
 
-    \binary[left=of E.south west, unique=1-2](i) [below=6mm of h]{};
-    \node[role name, at=(i.north),anchor=south] {[$m_{0} m_{1} m_{3}$]};
-    \plays[] (E) to (i.east);
-   % \plays(h) to (i);
-%         label=below:\ormleft{uses] (u) {};
-\node[role name,
-at=(h.north),anchor=south] {[$m_{0} m_{1}$]};
+  \draw [->,thick] (n2) -- node[left=2pt]  {$23$} (n0);
 
-    \entity[left=of h] (Rank) {$n_0:m_0 m_1 m_2 m_3 m_6$};
-
-    \plays[mandatory] (E) to (h.east);
-    \plays (h) to (Rank) (E);
-    \plays[mandatory] (Rank) to (i.west);
-    %to (u.east) (u) to (Car);
-
-    \binary[right=of E.north east] (b) {};
-    \node[role name,
-at=(b.north),anchor=south] {[$m_{0} m_{1}$]};
-       % \binary[right=of E.north east] (dd) {};
-
-    \binary[right=of E.south east, unique,] (i) {};
-    \node[role name,
-at=(i.north),anchor=south] {[$m_{1} m_{2} m_{3}$]};
-\binary[unique=1-2,skip unique=1-2] (xyz) [above=6mm of h] {};
-% describes blue label above h Left uppermost
-\node[role name,
-at=(xyz.north),anchor=south] {[$m_{0} m_{1} m_{3}$]};
-
-      \plays (Rank) to (xyz.west); 
-    \plays[mandatory] (E) to (xyz.east);
-
-    \entity[right=1.8 of E] (Date) {$n_2: m_1 m_2 m_3 m_6 m_8$};
-
-    \plays[mandatory] (E) to (b.west); 
-    \plays (E) to (i.west);
-    \plays (b.east) to (Date);
-    \plays[mandatory] (Date) to (i.east);
-
-%    \entity[label={[constraint]\#=$n$}] {E};
-%\draw (Rank) to node[vroles,label=has,label=below:\ormup{of}]{} (E);
-%\node[constraint,anchor=north west,inner ysep=0]
-%at (h.) {\ormbraces{a, b, c}};
-%\draw (E) to node[roles,
-%label=below:drives]{} (Rank);
-
-\node[roles=2][,unique=1-2,skip unique=2] (abc) [below=11mm of E] {};
-\node[role name,
-at=(abc.north),anchor=south] {[$m_{2} m_{3}$]};
-\plays[mandatory] (Rank.south) -- (abc.west);  
-\plays (abc.east) -- (Date.south);
-
-  %  \node[role name, anchor=south west] at (b.east) {[birthdate]};
-  %  \node[role name, anchor=north west] at (i.east) {[hiredate]};
-
-%     \rules at (-.4, -2) {
-%          \node[rule=1] {{$m_{2}$} $m_{3}$};\\
-%      };
 \end{tikzpicture}

### 2017-07-13 paper/bio.tex
my changes

@@
 
+\input{pm-1-matrix}
+
+\begin{example}
+In figure~\ref{fig:M1}(a), we present a VTS that has three compartments as nodes, vesicles as edges,
+and 8 molecules.
+Each node and edge is labelled with a set of molecules that present in them.
+Overline on a molecule indicates activation.
+In figure~\ref{fig:M1}(b), we present the corresponding fusion matrix.
+\ashu{discuss the properties on the figure.}
+\end{example}
+
 %--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

### 2017-07-13 paper/conclusion.tex
added
my changes

@@
+In the experiments, we have demonstrated the power of SMT solvers and the value
+of careful encoding of the problems into SMT queries.
+%
+We manage to scale the tool upto the size that interests biologists.
+%
+However, there are many further search problems are of interest to
+biologists about the VTSs.
+%
+For example, are there any k-connected graphs that can not be
+converted into a VTS?
+%
+This encoding induces a quantifier alternation in the problem.
+%
+Therefore, a simple quantifier free encoding will not work.
+%
+We are planning to use QBF solvers to solve such queries or develop
+iterative search algorithm for such queries.
+%
+
+% \ankit{interpret experiments (3-4 lines)}
+
+% \srivas{Future work(quantifier problem etc)}
+
 %--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

### 2017-07-13 paper/pm-1-matrix.tex
more stuff
fixed-dia
my changes
more new

@@
 \centering
-\begin{minipage}{0.45\linewidth}
+\begin{minipage}{0.50\linewidth}
   \hspace{-4ex}
@@
 \begin{minipage}{0.45\linewidth}
-  \tikzset{
-    ln/.style  = { draw, thick, fill=black, circle, inner sep=0.3mm},
-    sqloc/.style  = { draw, thick, inner sep=1.0mm },
-    loc/.style    = { draw, circle, thick, inner sep=1.0mm },
-  }
+
 \begin{tikzpicture}[node distance = 30mm]
-  \node[draw] (n0) {$n_1:\{01234\}$};
-  \node[draw,below left of=n0] (n1) {$n_0:\{01236\}$};
-  \node[draw,below right of=n0] (n2) {$n_2:\{012368\}$};
+  \node[draw] (n0) {$n_1:\overline{01234}$};
+  \node[draw,below left of=n0] (n1) {$n_0:\overline{01236}$};
+  \node[draw,below right of=n0] (n2) {$n_2:\overline{012368}$};
 
-  \draw[->,thick] (n1) -- node[left=1mm]  {$01$} (n0);
-  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$013$} (n0);
+  \draw[->,thick] (n1) -- node[left=1mm]  {$0\overline{1}$} (n0);
+  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$\overline{01}23$} (n0);
   \draw [->,thick] (n0) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n1);

### 2017-07-13 paper/pm-1-matrix.tex
more new

@@
 \begin{tikzpicture}[node distance = 30mm]
-  \node[draw] (n0) {$n_1:\overline{01234}$};
-  \node[draw,below left of=n0] (n1) {$n_0:\overline{01236}$};
-  \node[draw,below right of=n0] (n2) {$n_2:\overline{012368}$};
+  \node[draw] (n1) {$n_1:\overline{01234}$};
+  \node[draw,below left of=n1] (n0) {$n_0:\overline{01236}$};
+  \node[draw,below right of=n1] (n2) {$n_2:\overline{012368}$};
 
-  \draw[->,thick] (n1) -- node[left=1mm]  {$0\overline{1}$} (n0);
-  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$\overline{01}23$} (n0);
-  \draw [->,thick] (n0) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n1);
+  \draw[->,thick] (n0) -- node[left=1mm]  {$0\overline{1}$} (n1);
+  \draw [->,thick] (n0) to [bend right=-30] node[left=1mm]  {$\overline{01}23$} (n1);
+  \draw [->,thick] (n1) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n0);
 
-  \draw [->,thick] (n1) -- node[below=1mm]  {$123$} (n2);
-  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$01$} (n1);
+  \draw [->,thick] (n0) -- node[below=1mm]  {$123$} (n2);
+  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$01$} (n0);
 
-  \draw [->,thick] (n2) -- node[left=2pt]  {$23$} (n0);
+  \draw [->,thick] (n2) -- node[left=2pt]  {$23$} (n1);
 

### 2017-07-13 paper/pm-1-matrix.tex
fixed-dia

@@
 \begin{tikzpicture}[node distance = 30mm]
-  \node[draw] (n1) {$n_1:\overline{01234}$};
-  \node[draw,below left of=n1] (n0) {$n_0:\overline{01236}$};
-  \node[draw,below right of=n1] (n2) {$n_2:\overline{012368}$};
+  \node[draw] (n0) {$n_0:\overline{01234}$};
+  \node[draw,below left of=n0] (n1) {$n_1:\overline{01236}$};
+  \node[draw,below right of=n0] (n2) {$n_2:\overline{12357}$};
 
@@
   \draw [->,thick] (n0) to [bend right=-30] node[left=1mm]  {$\overline{01}23$} (n1);
-  \draw [->,thick] (n1) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n0);
+  \draw [->,thick] (n1) to [bend right=-30] node[below=2pt,xshift=3pt]  {$01\overline{3}$} (n0);
 
-  \draw [->,thick] (n0) -- node[below=1mm]  {$123$} (n2);
-  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$01$} (n0);
+  \draw [->,thick] (n1) -- node[below=1mm]  {$1\overline{2}3$} (n2);
+  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$1\overline{3}$} (n1);
 
-  \draw [->,thick] (n2) -- node[left=2pt]  {$23$} (n1);
+  \draw [->,thick] (n2) -- node[left=2pt]  {$2\overline{3}$} (n0);
 

### 2017-07-13 paper/pm-1-matrix.tex
fixed-dia

@@
   \draw[->,thick] (n0) -- node[left=1mm]  {$0\overline{1}$} (n1);
-  \draw [->,thick] (n0) to [bend right=-30] node[left=1mm]  {$\overline{01}23$} (n1);
-  \draw [->,thick] (n1) to [bend right=-30] node[below=2pt,xshift=3pt]  {$01\overline{3}$} (n0);
+  \draw [->,thick] (n0) to [bend right=-30] node[right=1mm]  {$\overline{01}23$} (n1);
+  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$01\overline{3}$} (n0);
 
@@
 
-  \draw [->,thick] (n2) -- node[left=2pt]  {$2\overline{3}$} (n0);
+  \draw [->,thick] (n2) -- node[right=2pt]  {$2\overline{3}$} (n0);
 

### 2017-07-13 paper/pm-1-matrix.tex
fixed-dia

@@
 
-\node[above=4pt of m-1-1] (top-1) {$M_1$};
-\node[above=4pt of m-1-2] (top-2) {$M_2$};
-\node[above=4pt of m-1-3] (top-3) {$M_3$};
-\node[above=4pt of m-1-4] (top-4) {$M_4$};
-\node[above=4pt of m-1-5] (top-5) {$M_5$};
-\node[above=4pt of m-1-6] (top-6) {$M_6$};
-\node[above=4pt of m-1-7] (top-7) {$M_7$};
-\node[above=4pt of m-1-8] (top-8) {$M_8$};
+\node[above=4pt of m-1-1] (top-1) {$M_0$};
+\node[above=4pt of m-1-2] (top-2) {$M_1$};
+\node[above=4pt of m-1-3] (top-3) {$M_2$};
+\node[above=4pt of m-1-4] (top-4) {$M_3$};
+\node[above=4pt of m-1-5] (top-5) {$M_4$};
+\node[above=4pt of m-1-6] (top-6) {$M_5$};
+\node[above=4pt of m-1-7] (top-7) {$M_6$};
+\node[above=4pt of m-1-8] (top-8) {$M_7$};
 
-\node[left=12pt of m-1-1] (left-1) {$M_1$};
-\node[left=12pt of m-2-1] (left-2) {$M_2$};
-\node[left=12pt of m-3-1] (left-3) {$M_3$};
-\node[left=12pt of m-4-1] (left-4) {$M_4$};
-\node[left=12pt of m-5-1] (left-5) {$M_5$};
-\node[left=12pt of m-6-1] (left-6) {$M_6$};
-\node[left=12pt of m-7-1] (left-7) {$M_7$};
-\node[left=12pt of m-8-1] (left-8) {$M_8$};
+\node[left=12pt of m-1-1] (left-1) {$M_0$};
+\node[left=12pt of m-2-1] (left-2) {$M_1$};
+\node[left=12pt of m-3-1] (left-3) {$M_2$};
+\node[left=12pt of m-4-1] (left-4) {$M_3$};
+\node[left=12pt of m-5-1] (left-5) {$M_4$};
+\node[left=12pt of m-6-1] (left-6) {$M_5$};
+\node[left=12pt of m-7-1] (left-7) {$M_6$};
+\node[left=12pt of m-8-1] (left-8) {$M_7$};
 
@@
 
-\caption{Pairing matrix} \label{fig:M1}
+\caption{\textbf{Pairing matrix}.
+VTS has 3 compartments and 8 molecules.
+Molecules are numbered 0-7 and and intersection matrix entry describes the fusion dependency.
+The entry 1 represents pairing, entry $\times$ represents no dependency and rectangles colored $\times$ one represents don't cares.
+In the right side of the pairing matrix is the graph VTS representation.
+Everwhere in the graph you can see the flux is maintained, that is every molecule is coming back to it's source node in a cycle.
+} \label{fig:M1}
 \end{figure}

### 2017-07-13 paper/pm-1-matrix.tex
fixed-dia

@@
 In the right side of the pairing matrix is the graph VTS representation.
+This graph is an example of version where every present molecule on the node is considered as active and activity of the molecules on the edges are described by presence of other molecules.
+Activity is shown by use of an overline in the grap both on the nodes and the edges.
 Everwhere in the graph you can see the flux is maintained, that is every molecule is coming back to it's source node in a cycle.
-} \label{fig:M1}
+The graph follows the fusion rules described in later sections.
+The resultant graph is a 3-connected graph.} \label{fig:M1}
 \end{figure}

### 2017-07-14 paper/bio.tex
more text

--- 2017-07-13 paper/bio.tex
@@
 %
-This is
-motivated by the idea that pairing must generate an inactive bi-molecular
-complex.
+This is motivated by the idea that pairing must generate an inactive
+bi-molecular complex.
 
@@
 not $k$-connected, i.e., every pair of compartments remain reachable
-after dropping $k$ vesicles.\ashu{why asking this question}
+after dropping $k-1$ vesicles.
+%
+It has been observed in nature, most VTSs are 3-connected.
+%
+It raised the natural question what are the properties of VTSs
+that are not 3-connected.
+%
+To study them, we have build a tool that finds VTSs that are not
+$k$-connected from some $k$.
+
 \ankit{Maximum connectivity [LGC, Least guarantee connectivity] and minimal connective [LRC (least required connectivity)] (rather than necc and suff cond) required by the graph.}
+
+\input{pm-1-matrix}
+
+\begin{example}
+%
+In figure~\ref{fig:M1}, we present a VTS that has 3
+compartments and 8 molecules, and corresponding pairing matrix that
+describes the fusion dependency.
+%
+Molecules are numbered 0-7.
+%
+In the VTS, labels consists of sting of molecule ids and overline
+over an id indicates that the molecule is active.
+%
+This VTS is an example of version where every present molecule on
+the node is active and activity of the molecules on the
+edges are controlled by presence of the other molecules.
+%
+On the right side of the figure, we present pairing matrix.
+%
+An entry 1 represents pairing between molecules and
+entry $\times$ represents no pairing.
+% rectangles colored $\times$ one represents don't cares.
+%
+Everywhere in the graph the flux is maintained, i.e.,
+every molecule is coming back to it's source node in a cycle.
+%
+The graph follows the fusion rules as discussed earlier and
+is a 3-connected graph.
+\ashu{R Q molecule types are not discussed anywhere.}
+\end{example}
 

### 2017-07-14 paper/pm-1-matrix.tex
more text

--- 2017-07-13 paper/pm-1-matrix.tex
@@
-\begin{figure}
+\begin{figure}[t]
 \centering
+\begin{minipage}{0.45\linewidth}
+
+\begin{tikzpicture}[node distance = 26mm]
+  \node[draw] (n0) {$n_0:\overline{01234}$};
+  \node[draw,below left of=n0] (n1) {$n_1:\overline{01236}$};
+  \node[draw,below right of=n0] (n2) {$n_2:\overline{12357}$};
+
+  \draw[->,thick] (n0) -- node[left=1mm]  {$0\overline{1}$} (n1);
+  \draw [->,thick] (n0) to [bend right=-30] node[right=1mm]  {$\overline{01}23$} (n1);
+  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$01\overline{3}$} (n0);
+
+  \draw [->,thick] (n1) -- node[below=1mm]  {$1\overline{2}3$} (n2);
+  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$1\overline{3}$} (n1);
+
+  \draw [->,thick] (n2) -- node[right=2pt]  {$2\overline{3}$} (n0);
+
+\end{tikzpicture}
+\end{minipage}
 \begin{minipage}{0.50\linewidth}
-  \hspace{-4ex}
+  \center
 \begin{tikzpicture}
-\matrix [matrix of math nodes,left delimiter=(,right delimiter=),row sep=0.16cm,column sep=0.1cm] (m) {
+\matrix [matrix of math nodes,left delimiter=(,right delimiter=),
+         row sep=0.07cm,column sep=0.07cm] (m) {
 \times & \times & \times &\times&\times&\times & \times & \times\\
@@
 
-\begin{pgfonlayer}{myback}
-
-\foreach \element in {m-1-7,m-3-8,m-5-1,m-5-2,m-5-3,m-5-4,m-6-1,m-6-2,m-6-3,m-6-4,m-7-1,m-7-2,m-7-3,m-7-4,m-8-1,m-8-2,m-8-3,m-8-4}{
-\highlight[pink]{\element}{\element}
-}
-\foreach \element in {m-2-7,m-3-6,m-4-5}{
-\fhighlight[blue!10]{\element}{\element}
-}
-\end{pgfonlayer}
-
-\end{tikzpicture}  
-\end{minipage}
-\begin{minipage}{0.45\linewidth}
-
-\begin{tikzpicture}[node distance = 30mm]
-  \node[draw] (n0) {$n_0:\overline{01234}$};
-  \node[draw,below left of=n0] (n1) {$n_1:\overline{01236}$};
-  \node[draw,below right of=n0] (n2) {$n_2:\overline{12357}$};
-
-  \draw[->,thick] (n0) -- node[left=1mm]  {$0\overline{1}$} (n1);
-  \draw [->,thick] (n0) to [bend right=-30] node[right=1mm]  {$\overline{01}23$} (n1);
-  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$01\overline{3}$} (n0);
-
-  \draw [->,thick] (n1) -- node[below=1mm]  {$1\overline{2}3$} (n2);
-  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$1\overline{3}$} (n1);
-
-  \draw [->,thick] (n2) -- node[right=2pt]  {$2\overline{3}$} (n0);
+% \begin{pgfonlayer}{myback}
+% \foreach \element in {m-1-7,m-3-8,m-5-1,m-5-2,m-5-3,m-5-4,m-6-1,m-6-2,m-6-3,m-6-4,m-7-1,m-7-2,m-7-3,m-7-4,m-8-1,m-8-2,m-8-3,m-8-4}{
+% \highlight[pink]{\element}{\element}
+% }
+% \foreach \element in {m-2-7,m-3-6,m-4-5}{
+% \fhighlight[blue!10]{\element}{\element}
+% }
+% \end{pgfonlayer}
 
@@
 
-\caption{\textbf{Pairing matrix}.
-VTS has 3 compartments and 8 molecules.
-Molecules are numbered 0-7 and and intersection matrix entry describes the fusion dependency.
-The entry 1 represents pairing, entry $\times$ represents no dependency and rectangles colored $\times$ one represents don't cares.
-In the right side of the pairing matrix is the graph VTS representation.
-Everwhere in the graph you can see the flux is maintained, that is every molecule is coming back to it's source node in a cycle.
-} \label{fig:M1}
+\caption{An example of VTS and corresponding pairing matrix.} \label{fig:M1}
 \end{figure}

### 2017-07-14 paper/conclusion.tex
many changes

@@
 For example, are there any k-connected graphs that can not be
-converted into a VTS?
+annotated into a VTS?
 %
-This encoding induces a quantifier alternation in the problem.
+This problem induces a quantifier alternation in the problem.
 %
@@
 %
-We are planning to use QBF solvers to solve such queries or develop
+We are planning to use QBF solvers or develop
 iterative search algorithm for such queries.

### 2017-07-14 paper/encoding.tex
my changes
many changes

@@
 \end{align}
-
 A molecule should be present to be active on a node.  
@@
 \begin{align}
-  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies n_{i,m}\tag{V4}\label{eq:c0}\\
-  \bigwedge\limits_{i,j,q,m}  e_{i,j,q,m} \limplies n_{j,m}\tag{V5}\label{eq:c1}
+  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
 \end{align}
-
-%C1 =  e_ijk -> aik and e_ijk -> ajk
-
 Self edges are not allowed. 
-
 \begin{align}
-   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V6}\label{eq:c2}
+   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
 \end{align}
-
 Since a molecule cannot be both SNARE and tether,
@@
   \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
-  \tag{V7}\label{eq:c3}
+  \tag{V6}\label{eq:c3}
 \end{align}
@@
   \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
-  \tag{V8}\label{eq:fuse1}  \\
+  \tag{V7}\label{eq:fuse1}  \\
 \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
-  \tag{V9}\label{eq:fuse2}  
+  \tag{V8}\label{eq:fuse2}  
 \end{align}
@@
 \begin{align}
-   \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \limplies  \bigwedge_{m' \neq m} (p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv (\neg b_{i,j,q,m} \land  \bigwedge_{m' \neq m, p_{m,m'}} \neg b_{i,j,q,m'})
+   \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \limplies  \bigwedge_{m' \neq m} (p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv (\neg b_{i,j,q,m} \land\;\;\;\;  \bigwedge_{\mathclap{m' \neq m, p_{m,m'}}} \neg b_{i,j,q,m'})
   \tag{Aep}\label{eq:aep}
 \end{align}
-% \[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies \neg b_{i,j,q,k}) \, \]
-
-% \[ \bigwedge\limits_{i,j, q, k}  (e_{i,j,q,k} \land \neg [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \limplies e_{i,j,q,k'})] ) \limplies b_{i,j,q,k}) \, \]
-
-% - F0: b(i,j,k) $\limplies$ e(i,j,k)
-
+%
 \subsubsection{Constraints for stability condition}
@@
 and say if there is an $m$-edge between $i$ and $j$, there is
-$m$-reachable path from $j$ to $i$.\ashu{disjunction needed??}
+$m$-reachable path from $j$ to $i$.
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies (r_{j,i,m,0}  \lor r_{j,i,m,1} \lor ... \lor r_{j,i,m,p})  
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,|N|}
   \tag{R2}\label{eq:reach2}
@@
 disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
-The following formulas encode the relevant constraints for reachability in the modified VTS.
-
-The following formulas encode that only existing edges can be dropped
-and exactly $k-1$ edges are dropped.
+%
+Boolean constraints~\ref{eq:drop1}-\ref{eq:drop4}
+encode the relevant constraints for reachability
+in the modified VTS. 
+%
+The following formulas encode that only
+existing edges can be dropped and exactly $k-1$ edges are dropped.
 \begin{align}
@@
 
-We have encoded several versions of the models of vesicle traffic systems listed.
-Starting from most basic version (A) where every present molecule is considered to be active.
-Other cases includes different combinations of constraints on the activity on nodes and edges.
-Most general restriction is activity of the molecule is dependent on the other molecules presence on the node (a Boolean function of N-1 parameters) (B,C,D,F,G,H).
-In very special case (E,F,G,H) activity of the molecules on the edges is dictated by pairing matrix, we call this process ``pairing inhibition".
+We have encoded several versions of the models of VTSs listed.
+%
+The cases includes different combinations of constraints on the
+activity on nodes and edges.
+%
+
 %In this case if the corresponding pairing molecules present on the edge with the molecules , both the molecule and all corresponding molecules gets inhibited/become inactive.
@@
 \item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
-\item Version F with additional constraint that every edge is distinct.
+\item Version F with additional constraint that every edge is distinct.\ashu{encode this??}
 %\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
@@
 \end{enumerate}
+%
+The version (A) is most basic where every present molecule is active.
+%
+In versions (B-D,F-H),
+most general restriction is activity of the molecule is dependent on
+the other molecules presence on the node.
+%
+In the versions (E-H), activity of the molecules on the edges
+is dictated by pairing matrix; we call this process ``pairing
+inhibition".
+%
+In the column 2-3 of table~\ref{table1}, we list the constraints involved
+in each version.
 
-We have applied the tool for the above variations for searching the vesicle traffic systems that satisfies
-their corresponding properties.
+% We have applied the tool for the above variations for searching the
+% VTSs that satisfies their corresponding properties. 
+%
+% After creating the formula using different Boolean variables 
+% we ship them directly to the solver.
+% %
+% In case of a satisfying (SAT) assignment of the added constraints the
+% Z3 theorem prover gives a model with the variable assignment.
+% %
+% In case no possible satisfying assignment the solver returns UNSAT.
 
-\input{pm-1-matrix}
-\input{v2-dia}
-
-After creating the formula using different Boolean variables we ship them directly to the solver.
-In case of a satisfying (SAT) assignment of the added constraints the Z3 theorem prover gives a model with the variable assignment.
-In case no possible satisfying assignment the solver returns UNSAT.
 %

### 2017-07-14 paper/experiments.tex
many changes

@@
-Given a system that follows the VTS, we are interested in its connectivity (graph) property.
-We have implemented the encoding of the constraints in the python interface of $\zthree$.
-The basic idea is to constraint the variables such that vesicular transport rules are respected and using constraints (D0-D5) reason about the connectivity of the underlying structure (graph).
+\begin{table}[t]
+\centering
+% \def\arraystretch{1.6}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    {\multirow{2}{*}{\textbf{Version}}}  & 
+    \multicolumn{2}{c|}{\multirow{2}{*}{\textbf{Constraints}}} & 
+    \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
+   \cline{4-5}
+   &  &  & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline
+
+A. & \multirow{5}{*}{
+     \makecell{ \ref{eq:f0}--\ref{eq:fuse2},\\
+     \ref{eq:reach1},\ref{eq:reach2},\\
+     \ref{eq:drop1}--\ref{eq:drop4}}
+     } 
+& \ref{eq:ann},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
+B. & & \ref{eq:anb},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
+C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected & 3-connected \\  \cline{3-5}
+D. & & \ref{eq:ann},\ref{eq:aep} & No graph & No graph \\ \cline{3-5}
+E. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected & 3-connected \\ \cline{3-5}
+F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected & 4-connected \\ \cline{3-5}
+G. & & \ref{eq:anb},\ref{eq:aeb},\ref{eq:ced} & 3-connected & 3-connected \\ \hline
+
+% C_es :Self edges are allowed
+% C_ed : Every edge is distinct 
+  \end{tabular}
+\caption{{\bf Activity regulation of molecules vs. graph connectivity.}}
+\label{tab:grph}
+\end{table}
+
+% Given a system that follows the VTS, we are interested in its connectivity (graph) property.
+
+% The basic idea is to constraint the variables such that vesicular
+% transport rules are respected and using constraints (D0-D5) reason
+% about the connectivity of the underlying structure (graph).
 
@@
 % \Ankit{In other solver variations ...}
-Our tool allows the user to choose a model and the size of the network besides other parameters like connectivity and number of parallel edges.
-It uses Z3 Python interface to build the needed constraints and applies $\zthree$ solver on the constraints to find a model ( a satisfying assignment that respects the constraints).
-This tool also translates the satisfying model found by $\zthree$ into a vesicle traffic system and presents a visual output to the user in form of annotated graph.
-The output graph will satisfy the underlying rules of the system, so it always is a valid vesicle transport network.
-The resultant graph provides an overview of the underlying vesicle transport system where directed labeled edges and nodes provide the complete information about the system.
-Dashed lines are used in the resultant visual network output to specify the dropped edges to make the graph disconnected, which gives information about the connectivity of the graph.
+
+We have implemented the encoding of the constraints for each version
+using the python interface of $\zthree$ in a tool.
+%
+Our tool allows the user to choose a model and the size of the network
+besides other parameters like connectivity and number of parallel
+edges.
+%
+It uses Z3 Python interface to build the needed constraints and
+applies $\zthree$ solver on the constraints to find a model ( a
+satisfying assignment that respects the constraints).
+%
+This tool also translates the satisfying model found by $\zthree$ into
+a VTS and presents a visual output to the user in form of annotated graph.
+%
+The output graph will satisfy the underlying rules of the system, so
+it always is a valid vesicle transport network.
+%
+The resultant graph provides an overview of the underlying VTS
+where directed labeled edges and nodes provide the
+complete information about the system.
+%
+We also visually report the dropped edges to make the graph
+disconnected, which gives information about the connectivity of the
+graph.
+
+% Dashed lines are used in the resultant visual network output to
+% specify the dropped edges to make the graph disconnected, which gives
+% information about the connectivity of the graph.
+\ashu{discuss table~\ref{tab:grph}}
 
 \input{tbl-qf-graph}
-%\input{tbl-qf1-graph}
-In Table 1. 
-%~\ref{tab:qf-graph},
-we present the running times for the search of vesicle traffic systems of sizes 2 to 10 that satisfies the model variants.
-For example, the formula for variation F, the total number of compartments (N) equals to 10, returns in 129.78 minutes (7786.8 secs) with a SAT result.
-In comparison, CBMC encoding results in OUT OF MEMORY for the same variation and same compartment size.
-Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to eukaryotic cells with a total number of ten compartments.
-This additional cushion of scalability can provide us leverage to ask for related open questions that were not previously possible, for example, what is the minimum number of molecules required to satisfy the vesicular traffic system in eukaryotes.
 
-\input{cz-comparision}
+In Table~\ref{tab:qf-grabh}, we present the running times for the search of
+vesicle traffic systems of sizes 2 to 10 that satisfies the model
+variants.
+%
+The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
+CPU @ 1.90GHz processor and 4GB RAM.
+%
+We have compared our performance with the performance of our earlier 
+CBMC based implementation.
+%
+For example, the formula for variation F, the total number of
+compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
+with a SAT result.
+%
+In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
+%
+Hence with the use of this novel encoding, we are able to scale the
+system to a much larger compartmentalized system, especially to
+eukaryotic cells with a total number of ten compartments.
+%
+This additional scalability can provide us leverage to ask for related
+open questions that were not previously possible, for example, what is
+the minimum number of molecules required to satisfy the vesicular
+traffic system in eukaryotes.
+%
+Furthermore, we experimented with limits of our tools and found
+that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.
+
+% \input{cz-comparision}
 
 % REQUIRE COMPARISION WITH CBMC RUN TIME ?
-The experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM.
-On this machine, the CBMC encoding ran out of memory (M/O) for N $\geq$ 6 whereas new novel encoding was able to handle the case fairly easily.
-We think the main reasons for such an improvement are the following:
-\begin{enumerate}
-\item Direct encoding into the solver rather than using CFE (CBMC C front end), which treats front end variables as C variable and similarly other C overheads.
-\item Current novel encoding is fine-tuned to the structure of the problem.
-\item Improved encoding based on reachability rather than complete enumeration and non-determinism.
-\end{enumerate} 
-% 
-$\zthree$ was able to solve the constraints up to 14-18 nodes (based on the versions).
-%
+
+% %
+% On this machine, the CBMC encoding ran out of memory (M/O) for N
+% $\geq$ 6 whereas new novel encoding was able to handle the case fairly
+% easily.
+% %
+% We think the main reasons for such an improvement are the following:
+% \begin{enumerate}
+% \item Direct encoding into the solver rather than using CFE (CBMC C front end), which treats front end variables as C variable and similarly other C overheads.
+% \item Current novel encoding is fine-tuned to the structure of the problem.
+% \item Improved encoding based on reachability rather than complete enumeration and non-determinism.
+% \end{enumerate} 
+% % 
+% %
 
 %table~\ref{tbl:qf-results}
-
-\begin{table}[!ht]
-\centering
-\def\arraystretch{1.6}
-\caption{
-{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
-  \begin{tabular}{|c|c|c|c|}
-    \hline
-  {\multirow{2}{*}{\textbf{Version}}}  & {\multirow{2}{*}{\textbf{Constraints}}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
-    % \hline
-    % \textbf{Inactive Modes} & \textbf{Description}\\
-   \cline{3-4}
-   {} & {} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\
-    %\hhline{~--}
-    \hline
-
-%    A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph  \\ \hline
-%B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph  \\ \hline
-%C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected  \\  \hline
-%D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph  \\ \hline
-%E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected  \\ \hline
-%F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected  \\ \hline
-%G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected \\ \hline
-
-A. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_en & No graph & No graph \\ \hline
-B. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_en & No graph & No graph \\ \hline
-C. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_eb & 3-connected & 3-connected \\  \hline
-D. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nn A\_ep & No graph & No graph \\ \hline
-E. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb & 2-connected & 3-connected \\ \hline
-F. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_ep & 4-connected & 4-connected \\ \hline
-G. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb A\_eb C\_ed & 3-connected & 3-connected \\ \hline
-%H. & V1-V7 V8 V9 R1 R2 D1-D4 A\_nb  A\_eb + C\_es & No-idea & No-idea \\ \hline
-
-% C_es :Self edges are allowed
-% C_ed : Every edge is distinct 
-  \end{tabular}
-\label{table1}
-\end{table}
 

### 2017-07-14 paper/encoding.tex
added table fix and G out

@@
 \item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
-\item Version F with additional constraint that every edge is distinct.\ashu{encode this??}
+%\item Version F with additional constraint that every edge is distinct.\ashu{encode this??}
 %\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
@@
 %
-In versions (B-D,F-H),
+In versions (B-D,F),
 most general restriction is activity of the molecule is dependent on
@@
 %
-In the versions (E-H), activity of the molecules on the edges
+In the versions (E,F), activity of the molecules on the edges
 is dictated by pairing matrix; we call this process ``pairing

### 2017-07-14 paper/experiments.tex
added table fix and G out

@@
     {\multirow{2}{*}{\textbf{Version}}}  & 
-    \multicolumn{2}{c|}{\multirow{2}{*}{\textbf{Constraints}}} & 
+    \multicolumn{2}{c|}{\textbf{Constraints}} & 
     \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
-   \cline{4-5}
-   &  &  & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline
+   \cline{2-5}
+   &  \textbf{Rest} & \textbf{Activity} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline
 
@@
 E. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected & 3-connected \\ \cline{3-5}
-F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected & 4-connected \\ \cline{3-5}
-G. & & \ref{eq:anb},\ref{eq:aeb},\ref{eq:ced} & 3-connected & 3-connected \\ \hline
+F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected & 4-connected \\ \hline
+%G. & & \ref{eq:anb},\ref{eq:aeb},\ref{eq:ced} & 3-connected & 3-connected \\ \hline
 

### 2017-07-15 paper/bio.tex
added srivas wworkline
fixed table refereing
V6
fixed table and added line numb and fixed description table 1

@@
 Here we consider an abstract set of molecules and do
-not explicitly associate them with particular protein varieties.
-
+not explicitly associate them with particular protein varieties.\textbf{But consider them to be either of  
+the two categories Q and R.}
 \textbf{Molecular flows and steady state:} The total amount of each
@@
 The list of molecular pairs that can drive a fusion event is given an
-a fusion pairing matrix.
+a fusion pairing matrix. \textbf{For convenience, we divide Q and R SNAREs evenly 
+and allow only opposite types to become a pair.}
 
@@
 \end{enumerate}
+%The fusion is a process where SNAREs on the vesicles target compartment is driven by the zipping together of vesicle
+%and compartment SNAREs [8, 9].
+%The SNAREs can be 
+%Typically a Q-SNARE triple-helix is confined to one mem-
+%brane surface (e.g the compartment), while an R-SNARE single helix is confined to its fusion
+%partner (e.g. the vesicle). When these two types of SNAREs are in close proximity they zip
+%together into a four-helix bundle, forcing the vesicle to fuse with the compartment. There are
+%many types of Q-SNAREs and R-SNAREs spread between different vesicles and compart-
+%ments. Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
+%contain higher numbers (humans have 41) [12]. Only certain Q and R-SNARE combinations
+%can zip into complexes, regulating precisely which vesicles fuse with which targets. For our
+%analysis, we consider a Q-SNARE triple helix as a single complex and the R-SNARE as its cog-
+%nate partner. We refer to zipping as SNARE pairing.
+
+\begin{itemize}
+\item \srivas{Detailed BIO to Graph problem}
+\end{itemize}
 

### 2017-07-15 paper/encoding.tex
V6
fixed table and added line numb and fixed description table 1

@@
 \end{align}
-Since a molecule cannot be both SNARE and tether,
+Since we have fixed first half as Q-SNAREs and rest as R-SNAREs,
 we set diagonal blocks in pairing matrix to be 0's.
-It reduces the search space.
+%It reduces the search space.
 % Condition on $p_{kk'}$. \ashu{why???} .
@@
 %
-The version (A) is most basic where every present molecule is active.
+For the version A, every present molecule is in active state.
+In the table~\ref{table1}, we list the constraints involved in each version.
+Constraints V1-V8, R1-R2 and D1-D4 are same for every version but the difference is the constraint deciding the activity of the molecules.
+One type of restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
+For example in version B, E, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
+Similarly for the case of the edge in version C and E; Aeb.
+In the case of versions F the activity of the molecules on the edges is described by pairing matrix, if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
 %
-In versions (B-D,F),
-most general restriction is activity of the molecule is dependent on
-the other molecules presence on the node.
-%
-In the versions (E,F), activity of the molecules on the edges
-is dictated by pairing matrix; we call this process ``pairing
-inhibition".
-%
-In the column 2-3 of table~\ref{table1}, we list the constraints involved
-in each version.
 

### 2017-07-15 paper/experiments.tex
fixed table and added line numb and fixed description table 1

@@
 C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected & 3-connected \\  \cline{3-5}
-D. & & \ref{eq:ann},\ref{eq:aep} & No graph & No graph \\ \cline{3-5}
-E. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected & 3-connected \\ \cline{3-5}
+D. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected & 3-connected \\ \cline{3-5}
+E. & & \ref{eq:ann},\ref{eq:aep} & No graph & No graph \\ \cline{3-5}
 F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected & 4-connected \\ \hline
@@
 % information about the connectivity of the graph.
-\ashu{discuss table~\ref{tab:grph}}
-
+%\ashu{discuss table~\ref{tab:grph}}
+table~\ref{tab:grph} shows the result of the different variations of the VTS.
+We haven't found any graph for the version A with constraints Ann and Aen.
+Replacing constraint on the node of Ann with Anb (version B) does not affect the outcome and hence there is no graph that is a valid VTS following these constraints.
+Interestingly if we allow every present molecule to stay active (Ann) but constraint the edge by a boolean function (Aeb) the resultant graph is a 3-connected graph.
+Constraining the activity of both the edge and the nodes with the boolean function (Anb Aeb) results in 2 connected graphs.
+Again there is no graph for the case where every molecule on the node is active but the activity on the edge is driven by pairing inhibition (Aep).
+But if we replace the constraint on the node to be a boolean function (Anb) with Aep we have found that 4 connected graphs satisfies all the constraints.
 \input{tbl-qf-graph}

### 2017-07-18 paper/conclusion.tex
added srivas wworkline
some changes

--- 2017-06-06 paper/conclusion.tex
@@
+In the experiments, we have demonstrated the power of SMT solvers and the value
+of careful encoding of the problems into SMT queries.
+%
+We manage to scale the tool upto the size that makes tool
+biologically relevant.
+%
+However, there are many further search problems that are of interest.
+%
+For example, are there any k-connected graphs that can not be
+annotated into a VTS?
+%
+This problem induces a quantifier alternation in an encoding.
+%
+Therefore, a simple call to SAT solver will not work.
+%
+We are planning to use QBF(quantified Boolean formulas) solvers or develop
+iterative search algorithm for such queries.
+%
+
+% \ankit{interpret experiments (3-4 lines)}
+
+ \srivas{Future work(quantifier problem etc)}
+
 %--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

### 2017-07-18 paper/encoding.tex
some changes

@@
 
-We have encoded several versions of the models of VTSs listed.
+We have encoded the following variants of VTSs.
 %
-The cases includes different combinations of constraints on the
+The variants are due to different combinations of constraints on the
 activity on nodes and edges.
 %
-
-%In this case if the corresponding pairing molecules present on the edge with the molecules , both the molecule and all corresponding molecules gets inhibited/become inactive.
-
-% DIVIDE INTO COLUMNS and TALK ABOUT A/1 or A/0.
-%\todo{describe the variations}
-
 \begin{enumerate}[label=\Alph*]
@@
 \item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
-%\item Version F with additional constraint that every edge is distinct.\ashu{encode this??}
-%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
-%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
-%\item Version F but self-edges are allowed.
 \end{enumerate}
 %
-For the version A, every present molecule is in active state.
-In the table~\ref{table1}, we list the constraints involved in each version.
-Constraints V1-V8, R1-R2 and D1-D4 are same for every version but the difference is the constraint deciding the activity of the molecules.
-One type of restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
-For example in version B, E, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
+% For the version A, every present molecule is in active state.
+%
+In the table~\ref{table1}, we present the constraints involved in each version.
+%
+The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
+for every variant.
+%
+The column three of the table lists the constraints that are different among the variants.
+%
+%
+One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
+%
+For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
+%
 Similarly for the case of the edge in version C and E; Aeb.
-In the case of versions F the activity of the molecules on the edges is described by pairing matrix, if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
 %
+In the case of versions F the activity of the molecules on the edges
+is described by pairing matrix, if all the pairs of the present
+molecule are present on the same edge than all of them inhibit each
+other resulting in making all the molecules inactive, we term this
+process ``pairing inhibition".
+%
+The constraints for the variants can be given to a SAT solver to find
+VTSs that belong to the variants.
 

### 2017-07-18 paper/experiments.tex
some changes

--- 2017-07-14 paper/experiments.tex
@@
 
-We have implemented the encoding of the constraints for each version
+We have implemented the encodings for each variants
 using the python interface of $\zthree$ in a tool.
@@
 It uses Z3 Python interface to build the needed constraints and
-applies $\zthree$ solver on the constraints to find a model ( a
-satisfying assignment that respects the constraints).
+applies $\zthree$ solver on the constraints to find a model (
+a satisfying assignment that respects the constraints).
 %
@@
 %
-The output graph will satisfy the underlying rules of the system, so
-it always is a valid vesicle transport network.
+% The output graph will satisfy the underlying rules of the system, so
+% it always is a valid vesicle transport network.
 %
-The resultant graph provides an overview of the underlying VTS
-where directed labeled edges and nodes provide the
-complete information about the system.
+% The resultant graph provides an overview of the underlying VTS
+% where directed labeled edges and nodes provide the
+% complete information about the system.
 %
@@
 % information about the connectivity of the graph.
-\ashu{discuss table~\ref{tab:grph}}
+%\ashu{discuss table~\ref{tab:grph}}
+
+In the table~\ref{tab:grph}, we also present the minimum connectedness needed for
+the different variants after applying our tool for sizes from 2 to 10.
+%
+We haven't found any graph for the variant A with constraints Ann and Aen.
+%
+Replacing constraint on the node of Ann with Anb (version B) does not affect the outcome.
+%
+If we allow every present molecule to stay active (Ann) but constraint the edge
+by a boolean function (Aeb) the resultant VTS has to be at least 3-connected.
+%
+If we constrain the activity of both the edge and the nodes with the boolean function (Anb and Aeb), 
+the VTS has to be 2-connected.
+%
+Similarly, the results for the other cases are also presented in the table.
+
+% Again there is no graph for the case where every molecule on the node is active, but the activity on the edge is driven by pairing inhibition (Aep).
+% %
+% If we replace the constraint on the node to be a boolean function (Anb) with Aep, we have found that 4-connected graphs satisfies all the constraints.
 
@@
 In Table~\ref{tab:qf-grabh}, we present the running times for the search of
-vesicle traffic systems of sizes 2 to 10 that satisfies the model
-variants.
+VTSs of sizes 2 to 10 that satisfy the variants.
 %
@@
 In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
+%
+``!'' indicate that the constraints were unsatisfiable.
 %

### 2017-07-18 paper/experiments.tex
more changes
many more changes

@@
     \hline
-    {\multirow{2}{*}{\textbf{Version}}}  & 
+    {\multirow{2}{*}{\textbf{Variant}}}  & 
     \multicolumn{2}{c|}{\textbf{Constraints}} & 
@@
 %
+\ankit{
 This additional scalability can provide us leverage to ask for related
@@
 the minimum number of molecules required to satisfy the vesicular
-traffic system in eukaryotes.
+traffic system in eukaryotes.}
 %

### 2017-07-18 paper/encoding.tex
many more changes

@@
 \end{align}
-Since we have fixed first half as Q-SNAREs and rest as R-SNAREs,
+\ankit{Without loss of generality, we can fix first half as Q-SNAREs and rest as R-SNAREs},
 we set diagonal blocks in pairing matrix to be 0's.
@@
 %
-Similarly for the case of the edge in version C and E; Aeb.
+Similarly for the case of the edge in version C and D; Aeb.
 %

### 2017-07-19 paper/bio_MTedit.tex
sad

%Again about two pages long

In this section, we will describe the model of VTSs and the basic constraints imposed by cell biology.

\textbf{The cell as a transport graph:} We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph. Every compartment or vesicle has a set of molecular labels, such as SNARE proteins, associated with it.

\textbf{Molecular flows and steady state:} Each edge is associated with a flux of all the molecular types carried by the corresponding vesicle. The total amount of each molecular type on each compartment can therefore increase or decrease. We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales. This implies incoming and outgoing fluxes are balanced for each molecular type at each compartment.

\textbf{Vesicle targeting driven by molecular interactions:} Once a vesicle has budded out of the source, the molecules it carries determine its properties. In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment. Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment. SNAREs fall into two classes (known as Q and R in the cell biology literature) and vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE. The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. Without loss of generality we assume equal numbers of Q and R SNARE types.

\textbf{Molecular regulation:} We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state. Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively. We test many different versions of this kind of molecular regulation. Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. We have also tested \cite{shukla} a particularly simple regulation mechanism in which a two SNAREs that can pair to drive fusion inhibit one another. This is motivated by the idea that pairing must generate an inactive bi-molecular complex.

\textbf{Synthesis:} Given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model, we do the following.

\begin{enumerate}
\item We determine which molecules are active on every compartment or vesicle.
\item For every vesicle fusing to a compartment, we determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we verify that there is no pairing of active molecules on the
vesicle and compartment that could drive their fusion.
\item We verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set; this is the steady state condition.
\end{enumerate}

If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies. We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].

\input{pm-1-matrix}

\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix. Molecules are numbered 0-7. In the VTS, labels are a string of molecule ids, and an overline over a an id indicates that the molecule is active. This VTS is an example of one where every molecule on the node is active, and the activity of the molecules on the edges are controlled by presence of the other molecules. On the right side of the figure, we show the pairing matrix. An entry 1 represents pairing between molecules; $\times$ represents no pairing. Rows are labels on vesicles, columns are labels on compartments. Every molecule flows on a cycle, ensuring steady state. This is a 3-connected graph.
\end{example}

\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
Since a VTS are a transport graph, it is but natural to formally model VTS as graphs (as used in computer science) with their nodes denoting compartments and labeled edges denoting transport vesicles with labels denoting the set of molecules being transported.  The budding and fusion regulations can be represented as matching tables over sets of molecules, i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met.  Given such a graph model of a VTS, then properties, such as $k$-connectedness or steady state condition, can be formally defined as constraints, i.e., first-order logical formulas, over graphs and function types.  Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS.  For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.

\begin{lstlisting}[mathescape,
 breaklines,
  rulecolor=\color{black},
  frame=single,
  caption= \textbf{Steady state specification.},
  moredelim={[is][keywordstyle]{@@}{@@}}
]
# Every edge E is represented by a label; labelE (a bitvector).
# E(x,y): Edge between node x and y. E.source = x, E.target = y    
# labelE(m): mth molecule is present on edge E.
# Edge(m)(x,y): Edge between node x and y with labelE(m).                 
# seq(a1..an): each ak represents a node. len(seq) is |seq|.
# N: total number of nodes, = : Mathematical equality.

@@$\forall$ z $\in$ {Nodes} $\forall$ E $\in$ {Edges}: E.source = z
    $\forall$ m $\in$ {Molecules}: labelE(m) $\supset$
       ($\exists$ a seq(a1..an): (2 $\leq$ |seq| $\leq$ N)  $\wedge$
            ((a1 = z) $\wedge$ (a2 = E.target) $\wedge$
             (($\forall$ k from 1 to |seq| - 1) $\supset$ Edge(m)(ak,ak+1)) $\wedge$
             (Edge(m)(an,a1))) @@

\end{lstlisting}    
%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}

Similarly, one can define fusion and budding rules as constraints over the boolean functions modeling the regulations.  Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.

\begin{lstlisting}[mathescape,
  breaklines,
  rulecolor=\color{black},
  frame=single, 
  caption= \textbf{Maximal Connectedness (LGC) Property.},
  moredelim={[is][keywordstyle]{@@}{@@}}
] 
# C1: Steady state condition.
# C2, C3: Fusion rules.
# C4: Graph is 4-connected.
# G: Graph, f: Constrained function.
# $\supset$: material conditional (if..then), $\wedge$: Logical and.
$\forall$: Universal quantifier, $\exists$: Existential quantifier.
# For every 4-connected graph following conditions must be valid.  
@@VALID ($\forall$ G: C4(G) $\supset$  ($\exists$ f: C1(G) $\wedge$ C2(G,f) $\wedge$ C3(G,f) )) @@

\end{lstlisting}

\subsection{Converting the Graph Problem into Boolean SAT problem}
\label{subsec:satproblem}
To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.

%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2017-07-19 paper/intro_MTedit.tex
sad

%Total two pages

%\begin{itemize}
%\item \mukund{BIO motivation}

The cytoplasm of eukaryotic cells is broken into membrane-bound compartments known as organelles. Cargo is moved between these compartments in small membrane-bound transporters known as vesicles \cite{stenmark2009rab}. This organization resembles a transport logistics network (compartments are nodes, vesicles are directed edges) and is commonly known as the vesicle traffic system (VTS). Vesicle traffic underpins nearly every aspect of eukaryotic cellular physiology, including human cellular physiology. Understanding how this system functions is therefore one of the central challenges of cell biology.

Cell biologists have identified many molecules that drive vesicle traffic~\cite{dacks2007evolution}. The key steps are the creation of vesicles loaded with cargo from source compartments (budding), and the depositing of those vesicles and cargo into target compartments (fusion) \cite{munro2004organelle}. Budding is regulated by proteins known as coats and adaptors that select cargo. Fusion is regulated by proteins known as SNAREs and tethers, that ensure that vesicles fuse to the correct target \cite{mani2016stacking}. Abstractly, we think of SNARE proteins as labels that are collected from the source compartment by vesicles. There is a corresponding set of label molecules on potential target compartments. If the two sets of labels (on vesicles and targets) are compatible, then the vesicle will fuse to the target. Importantly, it is likely that SNARE proteins can be regulated by other molecules, thereby being in active or inactive states. However, SNARE regulation is not well understood.

There has been very little work done on how these molecular processes are integrated across scales to build the entire VTS. We have recently used ideas of graph theory to address this question \cite{mani2016stacking}. We have shown that SNARE regulation places constraints on the structure of the traffic network \cite{shukla}. One informative constraint is graph connectivity. The nature of SNARE regulation determines whether graph topologies of particular levels of connectivity are biologically realizable. For example, if SNAREs are completely unregulated and thus always active, they cannot be used to generate a traffic network. If these SNAREs are regulated by relatively simple rules, then only highly connected traffic networks can be generated using them. In this way, biological inputs (about SNARE regulation) lead to clear testable predictions (about graph topologies).

The analysis of VTSs is a difficult computational problem because of the combinatorial scaling of graph topologies and regulatory rules. Many questions require us to check useful properties over all possible graphs and regulatory rules. Formal verification tools such as model checkers \cite{clarke1996symbolic, biere2003bounded, clarke2008birth, cimatti2000nusmv, holzmann1997model} and SAT solvers \cite{moskewicz2001chaff,een2004extensible} allow us to do this symbolically for graphs of finite size, without enumerating all instances. In a recent work, we employed the model checker CBMC \cite{CKY03, ckl2004} meant to analyze ANSI C programs for studying this problem. VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. Queries about graph connectivity requirements for different variations of SNARE regulations were modeled as logical assertions to be checked by the model checker. CBMC uses its own built-in encodings to reduce the analysis problem to a Boolean satisfiability problem which is solved using SAT solvers. However, the scalability of our recent approach was limited (up to VTSs with 8 nodes) due to the following reasons:

\begin{enumerate}
\item The encoding used to model VTSs was not fine-tuned to the structure of the problem.
\item The queries to be solved involved quantified formulas, i.e., we needed to solve queries of the form ``\emph{for all} graphs does there \emph{exist} SNARE regulation constraints that satisfy cellular steady state conditions.
\end{enumerate}

As CBMC does not directly support solving such quantified formulas, we had to use a technique that combined non-determinism and partial enumeration that is not as efficient.\newline

In this paper, we have developed a novel SAT encoding for searching a VTS that satisfy the given properties. We improved the encoding of some of the conditions for VTSs. In the earlier implementation, reachability was encoded by enumeration of paths. In our current encoding, we have recursively defined the reachability condition such that that we avoid the exponential enumeration. We have also encoded $k$-connectivity in a similar fashion and avoided a blowup in the formula size. Furthermore, our encoding supports several variations of the conditions. We have implemented the encoding using Z3~\cite{z3} python API and searched for VTS satisfying various properties upto size 14-18 nodes as compare earlier tool that could only search graph upto size 8 nodes. Our tool is useful to cell biologists since VTSs of real cells have approximately ten compartments.  \\

%\newline

The following are the contributions of this work:
\begin{itemize}
\item Novel encodings of reachability and 3-4 connectivity
\item Direct encoding into the SAT solver
\item A user friendly and scalable tool based on well known SMT solver Z3
\end{itemize}

%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2017-07-20 paper/bio_MTedit.tex
sad = shiromani_akali_dal

@@
 vesicle and compartment that could drive their fusion.
-\item We verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set; this is the steady state condition.
+\item We verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set; this is the \textbf{stability condition}.
+%steady state condition.
 \end{enumerate}
+
+%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
+\label{subsec:graphmodel}
+Since a VTS are a transport graph, it is but natural to formally model VTS as graphs (as used in computer science) with their nodes denoting compartments and labeled edges denoting transport vesicles with labels denoting the set of molecules being transported.
+The budding and fusion regulations can be represented as matching tables over sets of molecules, i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met.
+Given such a graph model of a VTS, then properties, such as $k$-connectedness or steady state condition, can be formally defined as constraints, i.e., first-order logical formulas, over graphs and function types.
+Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS.
+% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
+
+%\begin{itemize}
+%\item \srivas{Detailed BIO to Graph problem}
+%\end{itemize}
+
+Similarly, one can define fusion and budding rules as constraints over the boolean functions modeling the regulations.
+Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
+the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.
+Here we have defined the property by checking over existence of any fusion/budding rules.
+We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
+
+\subsection{Converting the Graph Problem into Boolean SAT problem}
+\label{subsec:satproblem}
+To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.
+In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.
+We then used the CBMC model checker to convert the graph problem into a SAT problem.
+One of the challenges we had in our earlier work is dealing with quantifiers.
+Note that the connectedness property defined in Listing~1.2 has quantifier alternation.
+Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.
+CBMC supports only a quantifier-free logic n its assertion language.
+In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.
+This enumeration was one source of bottleneck for scaling in our earlier work.
+In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.
+The details of te hnew encding will described in subsequent sections.
 
@@
 \end{example}
-
-\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
-\label{subsec:graphmodel}
-Since a VTS are a transport graph, it is but natural to formally model VTS as graphs (as used in computer science) with their nodes denoting compartments and labeled edges denoting transport vesicles with labels denoting the set of molecules being transported.
-The budding and fusion regulations can be represented as matching tables over sets of molecules, i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met.
-Given such a graph model of a VTS, then properties, such as $k$-connectedness or steady state condition, can be formally defined as constraints, i.e., first-order logical formulas, over graphs and function types.
-Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS.
-For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
-
-\begin{lstlisting}[mathescape,
- breaklines,
-  rulecolor=\color{black},
-  frame=single,
-  caption= \textbf{Steady state specification.},
-  moredelim={[is][keywordstyle]{@@}{@@}}
-]
-# Every edge E is represented by a label; labelE (a bitvector).
-# E(x,y): Edge between node x and y. E.source = x, E.target = y    
-# labelE(m): mth molecule is present on edge E.
-# Edge(m)(x,y): Edge between node x and y with labelE(m).                 
-# seq(a1..an): each ak represents a node. len(seq) is |seq|.
-# N: total number of nodes, = : Mathematical equality.
-
-@@$\forall$ z $\in$ {Nodes} $\forall$ E $\in$ {Edges}: E.source = z
-    $\forall$ m $\in$ {Molecules}: labelE(m) $\supset$
-       ($\exists$ a seq(a1..an): (2 $\leq$ |seq| $\leq$ N)  $\wedge$
-            ((a1 = z) $\wedge$ (a2 = E.target) $\wedge$
-             (($\forall$ k from 1 to |seq| - 1) $\supset$ Edge(m)(ak,ak+1)) $\wedge$
-             (Edge(m)(an,a1))) @@
-
-\end{lstlisting}    
-%\begin{itemize}
-%\item \srivas{Detailed BIO to Graph problem}
-%\end{itemize}
-
-Similarly, one can define fusion and budding rules as constraints over the boolean functions modeling the regulations.
-Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
-the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.
-Here we have defined the property by checking over existence of any fusion/budding rules.
-We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
-
-\begin{lstlisting}[mathescape,
-  breaklines,
-  rulecolor=\color{black},
-  frame=single, 
-  caption= \textbf{Maximal Connectedness (LGC) Property.},
-  moredelim={[is][keywordstyle]{@@}{@@}}
-] 
-# C1: Steady state condition.
-# C2, C3: Fusion rules.
-# C4: Graph is 4-connected.
-# G: Graph, f: Constrained function.
-# $\supset$: material conditional (if..then), $\wedge$: Logical and.
-$\forall$: Universal quantifier, $\exists$: Existential quantifier.
-# For every 4-connected graph following conditions must be valid.  
-@@VALID ($\forall$ G: C4(G) $\supset$  ($\exists$ f: C1(G) $\wedge$ C2(G,f) $\wedge$ C3(G,f) )) @@
-
-\end{lstlisting}
-
-\subsection{Converting the Graph Problem into Boolean SAT problem}
-\label{subsec:satproblem}
-To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.
-In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.
-We then used the CBMC model checker to convert the graph problem into a SAT problem.
-One of the challenges we had in our earlier work is dealing with quantifiers.
-Note that the connectedness property defined in Listing~1.2 has quantifier alternation.
-Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.
-CBMC supports only a quantifier-free logic n its assertion language.
-In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.
-This enumeration was one source of bottleneck for scaling in our earlier work.
-In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.
-The details of te hnew encding will described in subsequent sections.
-
 %--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

### 2017-07-20 paper/intro_MTedit.tex
sad = shiromani_akali_dal

@@
 \item The encoding used to model VTSs was not fine-tuned to the structure of the problem.
-\item The queries to be solved involved quantified formulas, i.e., we needed to solve queries of the form ``\emph{for all} graphs does there \emph{exist} SNARE regulation constraints that satisfy cellular steady state conditions.
+\item The \textbf{specification involved enumeration of all the possible paths in order to satisfy both the graph connectivity and the stability condition (refer section 3).}
+%quantified formulas, i.e., we needed to solve queries of the form ``\emph{for all} graphs does there \emph{exist} SNARE regulation constraints that satisfy cellular steady state conditions.
 \end{enumerate}
 
-As CBMC does not directly support solving such quantified formulas, we had to use a technique that combined non-determinism and partial enumeration that is not as efficient.\newline
+The problem of encoding graph connectivity and stability condition in CBMC was solved combined non-determinism and partial enumeration that is not as efficient.\newline
 
+\todo{REQUIRE A REWRITE FLOW PROBS}
 In this paper, we have developed a novel SAT encoding for searching a VTS that satisfy the given properties.

### 2017-07-20 paper/bio_MTedit.tex
intro-bio-start

@@
 Since a VTS are a transport graph, it is but natural to formally model VTS as graphs (as used in computer science) with their nodes denoting compartments and labeled edges denoting transport vesicles with labels denoting the set of molecules being transported.
-The budding and fusion regulations can be represented as matching tables over sets of molecules, i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met.
-Given such a graph model of a VTS, then properties, such as $k$-connectedness or steady state condition, can be formally defined as constraints, i.e., first-order logical formulas, over graphs and function types.
-Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS.
+The budding and fusion regulations can be represented as matching tables over sets of molecules.
+% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
+Given such a graph model of a VTS, then properties, such as $k$-connectedness or steady state condition, can be formally defined as constraints, 
+%i.e., first-order logical formulas, 
+over graphs and function types.  Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS. 
 % For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
@@
 Similarly, one can define fusion and budding rules as constraints over the boolean functions modeling the regulations.  
-Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
+%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
 the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.
@@
 We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
-
-\subsection{Converting the Graph Problem into Boolean SAT problem}
-\label{subsec:satproblem}
-To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.
+%
+%\subsection{Converting the Graph Problem into Boolean SAT problem}
+%\label{subsec:satproblem}
+%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.
 In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.

### 2017-07-20 paper/intro_MTedit.tex
done

--- 2017-07-19 paper/intro_MTedit.tex
@@
 CBMC uses its own built-in encodings to reduce the analysis problem to a Boolean satisfiability problem which is solved using SAT solvers.
-However, the scalability of our recent approach was limited (up to VTSs with 8 nodes) due to the following reasons:
+%
+However, the scalability of our recent approach was limited (up to
+VTSs with 6 nodes) due to the encoding used to model VTSs was not
+fine-tuned to the structure of the problem.
+%
+In particular, we needed to encode conditional reachability between
+nodes (refer section 3, stability condition), and solved using a
+combination of non-determinism and partial enumeration that is not as
+efficient.
 
-\begin{enumerate}
-\item The encoding used to model VTSs was not fine-tuned to the structure of the problem.
-\item The queries to be solved involved quantified formulas, i.e., we needed to solve queries of the form ``\emph{for all} graphs does there \emph{exist} SNARE regulation constraints that satisfy cellular steady state conditions.
-\end{enumerate}
+% \begin{enumerate}
+% \item 
+% \item The \textbf{specification involved enumeration of all the possible paths in order to satisfy both the graph connectivity and the stability condition (refer section 3).}
+% %quantified formulas, i.e., we needed to solve queries of the form ``\emph{for all} graphs does there \emph{exist} SNARE regulation constraints that satisfy cellular steady state conditions.
+% \end{enumerate}
 
-As CBMC does not directly support solving such quantified formulas, we had to use a technique that combined non-determinism and partial enumeration that is not as efficient.\newline
+% \newline
 
-In this paper, we have developed a novel SAT encoding for searching a VTS that satisfy the given properties.
-We improved the encoding of some of the conditions for VTSs.
-In the earlier implementation, reachability was encoded by enumeration of paths.
-In our current encoding, we have recursively defined the reachability condition such that that we avoid the exponential enumeration.
-We have also encoded $k$-connectivity in a similar fashion and avoided a blowup in the formula size.
-Furthermore, our encoding supports several variations of the conditions.
-We have implemented the encoding using Z3~\cite{z3} python API and searched for VTS satisfying various properties upto size 14-18 nodes as compare earlier tool that could only search graph upto size 8 nodes.
-Our tool is useful to cell biologists since VTSs of real cells have approximately ten compartments.
-\\
+% \todo{REQUIRE A REWRITE FLOW PROBS}
+In this paper, we have developed a novel SAT encoding for
+searching VTSs that satisfy the given properties.
+%
+We have improved the encoding of some of the conditions for VTSs.
+%
+Especially, we have recursively defined the reachability condition
+such that that we avoid the inefficient enumeration.
+%
+% We have also encoded $k$-connectivity in a similar fashion and avoided
+% a blowup in the formula size.
+%
+Furthermore, our encoding supports several variations of the properties.
+%
+We have implemented the encoding using Z3~\cite{z3} python API and
+searched for VTS satisfying various properties upto size 14-18 nodes
+as compare earlier tool that could only search graph upto size 6
+nodes.
+%
+Our tool is useful to cell biologists since VTSs of real cells have
+approximately ten compartments.
+
+  % \\
 

### 2017-07-20 paper/bio_MTedit.tex
intro-bio-related

@@
 Since a VTS are a transport graph, it is but natural to formally model VTS as graphs (as used in computer science) with their nodes denoting compartments and labeled edges denoting transport vesicles with labels denoting the set of molecules being transported.
-The budding and fusion regulations can be represented as matching tables over sets of molecules.
+The pairing mechanism can be represented as matching tables over sets of molecules.
 % i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
-Given such a graph model of a VTS, then properties, such as $k$-connectedness or steady state condition, can be formally defined as constraints, 
+Given such a graph model of a VTS, then properties, such as $k$-connectedness or stability condition, can be formally defined as constraints, 
 %i.e., first-order logical formulas, 
-over graphs and function types.  Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS. 
+over graphs and function types.
+Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS.
+Similarly, one can define fusion rules as constraints over the boolean functions modeling the regulations.
 % For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
@@
 
-Similarly, one can define fusion and budding rules as constraints over the boolean functions modeling the regulations.  
 %Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
@@
 
-If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles.
-In principle the connectivity of a VTS can be determined by cell-biological studies.
-We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity.
+If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
+% We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 
 Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
-We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].
+%We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].
 

### 2017-07-20 paper/related.tex
intro-bio-related

@@
 %\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
-Satisfiability was the first NP-complete problem discovered.
-Stephen cook's in his famous paper \cite{cook1971complexity} (he used the word tautology) shown that every NP-complete problem can be reduced to solving for the satisfiability.
-The fact is that SAT solvers have seen a surge in the handling of millions of variables, hence many general problems are encoded as a SAT problem.
-Due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT solvers.
+Modern day SAT solvers can handle millions of variables and due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT solvers.
 There are many graphs related combinatorial work \cite{gay2013solving,wotzlaw2012generalized} that have used SAT solvers.

### 2017-07-20 paper/encoding.tex
intro-bio-encodingV6

@@
 \end{align}
-\ankit{Without loss of generality, we can fix first half as Q-SNAREs and rest as R-SNAREs},
-we set diagonal blocks in pairing matrix to be 0's.
+We fix first half as Q-SNAREs and rest as R-SNAREs and set diagonal blocks in pairing matrix to be 0's.
 %It reduces the search space.
@@
 The reachability is recursively defined in~\eqref{eq:drop3} and has
-trivial solution by making all $r'$s true.
+trivial solutions by making all $r'$s true.
 %
-However, the trivial solution is disallowed by formula~\eqref{eq:drop4} and we find
+However, the trivial solutions are disallowed by formula~\eqref{eq:drop4} and we find
 only the solutions that captures the evidence of unreachability.
@@
 This is because formula~\eqref{eq:reach2} has only positive
-occurrences of the reachability variables and circular dependencies in
-the recursive definition of $r'$s in ~\eqref{eq:reach1} may result
-in spurious satisfying assignments that do not encode reachability.
+occurrences of the reachability variables and if we had defined
+$r$s in ~\eqref{eq:reach1} without paths,
+the circular dependencies in the recursive definitions of $r$s
+may have resulted in spurious satisfying assignments that
+do not encode reachability.
 %
@@
 formula remains polynomial in size, and satisfying assignments only
-corresponds to correct reachability.
+correspond to correct reachability.
 

### 2017-07-20 paper/intro_MTedit.tex
more in intro

@@
 In particular, we needed to encode conditional reachability between
-nodes (refer section 3, stability condition), and solved using a
-combination of non-determinism and partial enumeration that is not as
-efficient.
+nodes (refer section 3, stability condition), and solved in CBMC using a
+combination of non-determinism and partial enumeration that is
+inefficient.
 
@@
 In this paper, we have developed a novel SAT encoding for
-searching VTSs that satisfy the given properties.
+searching VTSs that satisfy the useful properties.
 %
@@
 %
-Furthermore, our encoding supports several variations of the properties.
+% Furthermore, our encoding supports several variations of the properties.
 %
@@
 searched for VTS satisfying various properties upto size 14-18 nodes
-as compare earlier tool that could only search graph upto size 6
-nodes.
+as compare earlier tool that could only search graph upto
+size~6\footnote{The experiments in~\cite{shukla} scale upto 8.
+However, our experiments only scale upto 6, because
+we are using less powerful machine.} nodes.
 %
 Our tool is useful to cell biologists since VTSs of real cells have
-approximately ten compartments.
+approximately 10 compartments.
 

### 2017-07-20 paper/intro_MTedit.tex
footnote

@@
 as compare earlier tool that could only search graph upto
-size~6\footnote{The experiments in~\cite{shukla} scale upto 8.
-However, our experiments only scale upto 6, because
+size~6\footnote{The original experiments in~\cite{shukla} scaled upto 8.
+However, our current experiments only scale upto 6, because
 we are using less powerful machine.} nodes.

### 2017-07-20 paper/bio_MTedit.tex
asd

@@
 
-If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
+\ankit{If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.}
 % We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 

### 2017-07-20 paper/bio_MTedit.tex
pass

--- 2017-07-20 paper/bio_MTedit.tex
@@
 \label{subsec:graphmodel}
-Since a VTS are a transport graph, it is but natural to formally model VTS as graphs (as used in computer science) with their nodes denoting compartments and labeled edges denoting transport vesicles with labels denoting the set of molecules being transported.
-The pairing mechanism can be represented as matching tables over sets of molecules.
+%
+Since a VTS is a transport graph, it is but natural to formally model
+VTS as graphs (as used in computer science) with their nodes denoting
+compartments and labeled edges denoting transport vesicles with labels
+denoting the set of molecules being transported. The pairing mechanism
+can be represented as matching tables over sets of molecules.
 % i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
-Given such a graph model of a VTS, then properties, such as $k$-connectedness or stability condition, can be formally defined as constraints, 
-%i.e., first-order logical formulas, 
-over graphs and function types.
-Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS.
-Similarly, one can define fusion rules as constraints over the boolean functions modeling the regulations.
+%
+Given such a graph model of VTSs and their properties, such as
+stability condition and fusion rules, can be formally defined as
+constraints over graphs and uninterpreted Boolean functions.
+%
+% Note that the formulas define among other things constraints over
+% paths between nodes in the graph model of VTS. Similarly, one can
+% define fusion rules as constraints over the boolean functions modeling
+% the regulations.  
+\
 % For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
@@
 If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
+\ankit{Why $k$-connected matters?}
 % We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 

### 2017-07-20 paper/bio_MTedit.tex
push

@@
 
-If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
-\ankit{Why $k$-connected matters?}
-% We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 
-Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
-%We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].
+If a VTS is $k$-connected, every pair of compartments remain reachable
+after dropping $k-1$ vesicles.
+%
+This property of VTSs have been considered informative and
+studied~\cite{shukla}.
+%
+Here we have build an \emf{efficient} tool that studies properties of
+VTSs that are not $k$-connected, from some $k$.
 

### 2017-07-20 paper/encoding.tex
minor
pass
push

@@
 Subsequently, we will present the SAT encoding of the search problems
-for the graphs that satisfies the conditions.
+for the graphs that satisfy the conditions.
 
@@
 $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols = \mu|$, and
+$|\nodes| = \nu$, $|\mols| = \mu$, and
 $G$ is not $k$-connected.

### 2017-07-20 paper/experiments.tex
asd
table 1 fixed

@@
 % \def\arraystretch{1.6}
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|}
     \hline
@@
     \multicolumn{2}{c|}{\textbf{Constraints}} & 
-    \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
-   \cline{2-5}
-   &  \textbf{Rest} & \textbf{Activity} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline
+    \textbf{Graph connectivity}
+    % \multicolumn{2}{c|}{\textbf{Graph connectivity}}
+    \\
+   \cline{2-4}
+   &  \textbf{Rest} & \textbf{Activity} & \textbf{\textbf{Least connected}} % & \textbf{Sampling: Guarantee}
+\\ \hline
 
@@
      } 
-& \ref{eq:ann},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
-B. & & \ref{eq:anb},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
-C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected & 3-connected \\  \cline{3-5}
-D. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected & 3-connected \\ \cline{3-5}
-E. & & \ref{eq:ann},\ref{eq:aep} & No graph & No graph \\ \cline{3-5}
-F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected & 4-connected \\ \hline
-%G. & & \ref{eq:anb},\ref{eq:aeb},\ref{eq:ced} & 3-connected & 3-connected \\ \hline
+     & \ref{eq:ann},\ref{eq:aen} & No graph     \\\cline{3-4}
+B. & & \ref{eq:anb},\ref{eq:aen} & No graph     \\\cline{3-4}
+C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected  \\\cline{3-4}
+D. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected  \\\cline{3-4}
+E. & & \ref{eq:ann},\ref{eq:aep} & No graph     \\\cline{3-4}
+F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected  \\\hline
 
@@
 %
-\ankit{
-This additional scalability can provide us leverage to ask for related
-open questions that were not previously possible, for example, what is
-the minimum number of molecules required to satisfy the vesicular
-traffic system in eukaryotes.}
+% \ankit{
+% This additional scalability can provide us leverage to ask for related
+% open questions that were not previously possible, for example, what is
+% the minimum number of molecules required to satisfy the vesicular
+% traffic system in eukaryotes.}
 %

### 2017-07-20 paper/bio_MTedit.tex
table 1 fixed
k connected fix

@@
 
-If a VTS is $k$-connected, every pair of compartments remain reachable
-after dropping $k-1$ vesicles.
+A VTS is {\em $k$-connected} if every pair of compartments remain
+reachable after dropping $k-1$ vesicles.
 %
 This property of VTSs have been considered informative and
-studied~\cite{shukla}.
+studied by~\cite{shukla}.
 %
-Here we have build an \emf{efficient} tool that studies properties of
+Here we have build an {\em efficient} tool that studies properties of
 VTSs that are not $k$-connected, from some $k$.

### 2017-07-20 paper/bio_MTedit.tex
example fixed

@@
 In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
+%
 Molecules are numbered 0-7.
-In the VTS, labels are a string of molecule ids, and an overline over a an id indicates that the molecule is active.
-This VTS is an example of one where every molecule on the node is active, and the activity of the molecules on the edges are controlled by presence of the other molecules.
+%
+In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
+%
+Every molecule on the node is active.
+%
+The activity of the molecules on an edge are controlled
+by presence of the other molecules on the edge.
+%
 On the right side of the figure, we show the pairing matrix.
-An entry 1 represents pairing between molecules; $\times$ represents no pairing.
-Rows are labels on vesicles, columns are labels on compartments.
+%
+An entry 1 represents pairing between molecules.
+%
+$\times$ represents no pairing.
+%
+Rows corresponds to the labels of edges, and
+columns corresponds to the labels of nodes.
+%
 Every molecule flows on a cycle, ensuring steady state.
+%
 This is a 3-connected graph.

### 2017-07-20 paper/encoding.tex
?? fixed
fixed-table0-intro-bio-exper

@@
 %
-In the table~\ref{table1}, we present the constraints involved in each version.
+In the table~\ref{tab:grph}, we present the constraints involved in each version.
 %
@@
 In the case of versions F the activity of the molecules on the edges
-is described by pairing matrix, if all the pairs of the present
-molecule are present on the same edge than all of them inhibit each
-other resulting in making all the molecules inactive, we term this
-process ``pairing inhibition".
+is described by pairing matrix; Aep.
+
+%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
 %

### 2017-07-20 paper/encoding.tex
typo

--- 2017-07-20 paper/encoding.tex
@@
     set of edges with molecule sets as labels
-  \item $\pairs : \mols \times \mols$ is pairing relation
+  \item $\pairs \subseteq \mols \times \mols$ is pairing relation
   \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
@@
 %
-A node $n'$ is {\em reachable} from node $n$ in $G$ if there is a path
+A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
 $n,...,n'$ in $G$.
 %
-A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
-$m$-path $n,...,n'$ in $G$.
+% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
+% $m$-path $n,...,n'$ in $G$.
 %
@@
 and $\pairs(M'')$ are not active in any other node.
-
 %
@@
 \item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\item $r_{i,j,m,p}$ indicates that there is a path from $i$ to $j$ of length less than or equal to $p$
+\item $r_{i,j,m,p}$ indicates that there is a $m$-path from
+  $i$ to $j$ of length less than or equal to $p$
 \end{enumerate}
@@
 \item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped
-\item $r'_{i,j}$ indicates that there is a path from $i$ to $j$ is a modified VTS
+\item $r'_{i,j}$ indicates that there is a path from $i$ to $j$ in the modified VTS
 \end{enumerate}
@@
 \end{align}
-
-The edge labels are subset of the node label of source and target compartments.
-
+The edge labels are subset of the node labels of the source and target compartments.
 \begin{align}

### 2017-07-20 paper/bio_MTedit.tex

@@
 We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales.
-This implies incoming and outgoing fluxes are balanced for each molecular type at each compartment.
+This implies incoming and outgoing fluxes are balanced for each molecular type at each compartment; this is the \textit{stability condition}.
 
@@
 Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle.
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which a two SNAREs that can pair to drive fusion inhibit one another.
+We have also tested \cite{shukla} a particularly simple regulation mechanism in which a two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
 This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
@@
 vesicle and compartment that could drive their fusion.
-\item We verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set; this is the \textbf{stability condition}.
+\item We verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set.
 %steady state condition.

### 2017-07-20 paper/encoding.tex

@@
 \end{align}
-The edge labels are subset of the node labels of the source and target compartments.
+The edge labels are subset of the node labels of the source and target nodes.
 \begin{align}

### 2017-07-20 paper/encoding.tex
merged

@@
 %
-Afterwards, we will present the formulas corresponding to the
+Afterwards, we will present the constraints corresponding to the
 properties.
@@
 \item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
-\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains molecule $m$.
-
-\item Boolean variable $p_{k,k'}$ indicates if $(m,m') \in \pairs$
+\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
+\item Boolean variable $p_{m,m'}$ indicates if $(m,m') \in \pairs$
 \item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
@@
 \item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\item $r_{i,j,m,p}$ indicates that there is a $m$-path from
+\item $r_{i,j,m,p}$ indicates if there is an $m$-path from
   $i$ to $j$ of length less than or equal to $p$
@@
 \item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped
-\item $r'_{i,j}$ indicates that there is a path from $i$ to $j$ in the modified VTS
+\item $r'_{i,j}$ indicates if there is a path from $i$ to $j$ in the modified VTS
 \end{enumerate}
 
-We will describe the Boolean formulas that encode VTSs in several categories.
+We will describe the Boolean constraints that encode VTSs in several categories.
 %
-In the end, we will present in a table the formulas needed for the
+In the end, we will present in a table the constraints needed for the
 model variants.
@@
 To avoid cumbersome notation, we will not explicitly write the ranges of the indexing
-in the formulas.
+in the constraints.
 %
-$i$ and $j$ will be ranged over nodes.
+$i$ and $j$ will range over nodes.
 %
-$m$ will be ranged over molecules.
+$m$ will range over molecules.
 %
-$q$ will be ranged over edges between two nodes.
+$q$ will range over edges between two nodes.
 %
@@
 \subsubsection{Well-fused constraints}
-Boolean constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
+Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
 its destination node.
 %
-Boolean constraint~\eqref{eq:fuse2} encodes that each edge should not
+Constraint~\eqref{eq:fuse2} encodes that each edge should not
 be able to potentially fuse with any node other than its destination node.
@@
 %
-The following formula encodes no conditions on activities on nodes,
+The following constraint encodes no conditions on activities on nodes,
 i.e., all the present molecules on the nodes are active.
@@
 \end{align}
-The following formula encodes that activity of a molecule $m$ on the node is
+The following constraint encodes that activity of a molecule $m$ on the node is
 defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
@@
 \end{align}
-The following formula encodes no conditions on activities on edges,
+The following constraint encodes no conditions on activities on edges,
 i.e., all the present molecules on the edges are active.
@@
 \end{align}
-The following formula encodes that activity of a molecule $m$ on the edge is
+The following constraint encodes that activity of a molecule $m$ on the edge is
 defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
@@
 %
-The following formula encodes that the activity of the molecules on
+The following constraint encodes that the activity of the molecules on
 edges is defined by inhibition by other molecules based on the pairing
@@
 %
-The following formula recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
+The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
 if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
@@
 %
-The following formulas encode that only
+The following constraints encode that only
 existing edges can be dropped and exactly $k-1$ edges are dropped.
@@
 a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
-In the following formula, we encode $r'_{i,j}$ is true if there is an
+In the following constraint, we encode $r'_{i,j}$ is true if there is an
 edge $(i,\_,j)$ and it is not dropped, or there is a node
@@
 Since we are looking for a graph that is not $k$-connected,
-the following formula encodes that there are nodes $i$ and $j$ such that
+the following constraint encodes that there are nodes $i$ and $j$ such that
 there is no path between them in the underlying undirected graph.
@@
 In the current work, we have encoded reachability in two different
-ways in formulas~\eqref{eq:reach1} and~\eqref{eq:drop3}.
+ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
 %
@@
 %
-However, the trivial solutions are disallowed by formula~\eqref{eq:drop4} and we find
+However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
 only the solutions that captures the evidence of unreachability.
@@
 On the other hand,
-we have added length of paths in our reachability encoding in formula~\eqref{eq:reach1},
+we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
 which needs relatively more auxiliary variables.
 %
-This is because formula~\eqref{eq:reach2} has only positive
+This is because constraint~\eqref{eq:reach2} has only positive
 occurrences of the reachability variables and if we had defined
@@
 By adding the path length, we break the circular dependencies, the
-formula remains polynomial in size, and satisfying assignments only
+constraint remains polynomial in size, and satisfying assignments only
 correspond to correct reachability.
@@
 %
-% After creating the formula using different Boolean variables 
+% After creating the constraint using different Boolean variables 
 % we ship them directly to the solver.
@@
 % \subsection{Creating a solver and solving these constraints}
-% We will create a solver and add these build formula using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
+% We will create a solver and add these build constraint using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
 
@@
 % s = Solver()
-% # Add these formulas to it.
+% # Add these constraints to it.
 % s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)

### 2017-07-20 paper/encoding.tex
add

--- 2017-07-20 paper/encoding.tex
@@
     set of edges with molecule sets as labels
-  \item $\pairs \subseteq \mols \times \mols$ is pairing relation
+  \item $\pairs : \mols \times \mols$ is pairing relation
   \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
@@
 %
-A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
+A node $n'$ is {\em reachable} from node $n$ in $G$ if there is a path
 $n,...,n'$ in $G$.
 %
-% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
-% $m$-path $n,...,n'$ in $G$.
+A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
+$m$-path $n,...,n'$ in $G$.
 %
@@
 and $\pairs(M'')$ are not active in any other node.
+
 %
@@
 \item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\item $r_{i,j,m,p}$ indicates that there is a $m$-path from
-  $i$ to $j$ of length less than or equal to $p$
+\item $r_{i,j,m,p}$ indicates that there is a path from $i$ to $j$ of length less than or equal to $p$
 \end{enumerate}
@@
 \item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped
-\item $r'_{i,j}$ indicates that there is a path from $i$ to $j$ in the modified VTS
+\item $r'_{i,j}$ indicates that there is a path from $i$ to $j$ is a modified VTS
 \end{enumerate}
@@
 \end{align}
-The edge labels are subset of the node labels of the source and target nodes.
+
+The edge labels are subset of the node label of source and target compartments.
+
 \begin{align}
@@
 The variants are due to different combinations of constraints on the
-activity on nodes and edges.
+activity of molecules on the nodes and edges.
 %

### 2017-07-20 paper/experiments.tex
fixed-table0-intro-bio-exper
in 12 page
add

@@
     \multicolumn{2}{c|}{\textbf{Constraints}} & 
-    \textbf{Graph connectivity}
+    {\multirow{2}{*}{\textbf{Graph connectivity}}}
     % \multicolumn{2}{c|}{\textbf{Graph connectivity}}
     \\
-   \cline{2-4}
-   &  \textbf{Rest} & \textbf{Activity} & \textbf{\textbf{Least connected}} % & \textbf{Sampling: Guarantee}
+   \cline{2-3}
+   &  \textbf{Rest} & \textbf{Activity} &  % & \textbf{Sampling: Guarantee}
 \\ \hline
@@
 %
-We also visually report the dropped edges to make the graph
-disconnected, which gives information about the connectivity of the
-graph.
+We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
 
@@
 system to a much larger compartmentalized system, especially to
-eukaryotic cells with a total number of ten compartments.
+eukaryotic cells with a total number of 10 compartments. \textbf{Not only we have improved finding a SAT model but this encoding also did better in comparison to cbmc in the
+case of refutation that no model exists. Refer table variant A timing
+comparison and VARIANT D with N =2.}
 %

### 2017-07-20 paper/intro_MTedit.tex
add

@@
 However, the scalability of our recent approach was limited (up to
-VTSs with 6 nodes) due to the encoding used to model VTSs was not
+VTSs with 6 nodes) due to the encoding used to model VTSs was not completely
 fine-tuned to the structure of the problem.

### 2017-07-20 paper/experiments.tex
add

@@
 %
-Hence with the use of this novel encoding, we are able to scale the
-system to a much larger compartmentalized system, especially to
-eukaryotic cells with a total number of 10 compartments. \textbf{Not only we have improved finding a SAT model but this encoding also did better in comparison to cbmc in the
-case of refutation that no model exists. Refer table variant A timing
-comparison and VARIANT D with N =2.}
+ \textbf{Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exists (Table 2 variant A timing comparison and variant D with N =2).}.
+Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
+eukaryotic cells with a total number of 10 compartments.
 %

### 2017-07-20 paper/experiments.tex
add

--- 2017-07-20 paper/experiments.tex
@@
 We have implemented the encodings for each variants
-using the python interface of $\zthree$ in a tool.
+using the python interface of $\zthree$ in a tool (A'tool).
 %
@@
 We have compared our performance with the performance of our earlier 
-CBMC based implementation.
+CBMC based implementation (O'cbmc).
 %
@@
 %
-Hence with the use of this novel encoding, we are able to scale the
-system to a much larger compartmentalized system, especially to
-eukaryotic cells with a total number of 10 compartments. \textbf{Not only we have improved finding a SAT model but this encoding also did better in comparison to cbmc in the
-case of refutation that no model exists. Refer table variant A timing
-comparison and VARIANT D with N =2.}
+ \textbf{Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2).}.
+Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
+eukaryotic cells with a total number of 10 compartments.
 %

### 2017-07-20 paper/experiments.tex
asd

--- 2017-07-20 paper/experiments.tex
@@
 \label{tab:grph}
+\vspace{-5ex}
 \end{table}
@@
 
-In the table~\ref{tab:grph}, we also present the minimum connectedness needed for
-the different variants after applying our tool for sizes from 2 to 10.
+To illustrate usability of our tool 
+in last column of the table~\ref{tab:grph}, we also present the minimum connectedness
+needed for the different variants after applying our tool for sizes from 2 to 10.
 %
-We haven't found any graph for the variant A with constraints Ann and Aen.
+We found no graph for the variant A with constraints Ann and Aen.
 %
-Replacing constraint on the node of Ann with Anb (version B) does not affect the outcome.
+Replacing constraint on the node of Ann with Anb (variant B) does not affect the outcome.
 %
@@
 %
-If we constrain the activity of both the edge and the nodes with the boolean function (Anb and Aeb), 
-the VTS has to be 2-connected.
+% If we constrain the activity of both the edge and the nodes with the boolean function (Anb and Aeb), 
+% the VTS has to be 2-connected.
 %
-Similarly, the results for the other cases are also presented in the table.
+Similarly, the results for the other cases are presented in the table.
 
@@
 
+% \vspace{-3ex}
+
 % \input{cz-comparision}

### 2017-07-20 paper/experiments.tex

@@
 \label{tab:grph}
-\vspace{-5ex}
 \end{table}
@@
 that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.
-
-% \vspace{-3ex}
 

### 2017-07-20 paper/experiments.tex
add

--- 2017-07-20 paper/experiments.tex
@@
 We have implemented the encodings for each variants
-using the python interface of $\zthree$ in a tool (A'tool).
+using the python interface of $\zthree$ in a tool (MAA).
 %
@@
 the different variants after applying our tool for sizes from 2 to 10.
+\textbf{For the comparison between both encodings we have fixed the total number of molecules to be twice as number of the nodes for N > 2 and M = 2N + 1 for N = 2.
+For each version we fix total number of parallel edges to maximum two.
+In the table we have shown comparison for specific connectivity, for example Variant A is checked against any graph with connectivity 2, Variant B with connectivity 3 similarly for the rest of the Variants.
+}
 %
@@
 We have compared our performance with the performance of our earlier 
-CBMC based implementation (O'cbmc).
+CBMC based implementation (old-encoding).
 %
@@
 %
- \textbf{Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2).}.
+ \textbf{Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2)}.
 Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to

### 2017-07-20 paper/encoding.tex

--- 2017-07-20 paper/encoding.tex
@@
 In this section, we will formally define VTSs as a labeled graph
-and the conditions on the graphs that are discussed in the previous
-section.
+and the discussed conditions on the graphs.
 %

### 2017-07-20 paper/experiments.tex

@@
 
-In the table~\ref{tab:grph}, we also present the minimum connectedness needed for
+To illustrate usability of our tool 
+in last column of the table~\ref{tab:grph}, we also present the minimum connectedness needed for
 the different variants after applying our tool for sizes from 2 to 10.
@@
 }
+
 %
-We haven't found any graph for the variant A with constraints Ann and Aen.
+We found no graph for the variant A with constraints Ann and Aen.
 %
-Replacing constraint on the node of Ann with Anb (version B) does not affect the outcome.
+Replacing constraint on the node of Ann with Anb (variant B) does not affect the outcome.
 %

### 2017-07-20 paper/intro_MTedit.tex

@@
 %
-In particular, we needed to encode conditional reachability between
-nodes (refer section 3, stability condition), and solved in CBMC using a
+In particular, we had to encode conditional reachability between
+nodes (refer sec. 3, stability condition), and solved in CBMC using a
 combination of non-determinism and partial enumeration that is

### 2017-07-20 paper/encoding.tex
wd

@@
 %
-Boolean constraints~\ref{eq:drop1}-\ref{eq:drop4}
+Constraints~\ref{eq:drop1}-\ref{eq:drop4}
 encode the relevant constraints for reachability
@@
 \end{align}
-Since we are looking for a graph that is not $k$-connected,
-the following constraint encodes that there are nodes $i$ and $j$ such that
-there is no path between them in the underlying undirected graph.
+Since we search for disconnected modified VTS,
+the following constraint encodes that there are 
+unreachable pair of nodes in the underlying undirected graph.
+% nodes such that
+% there is no path between them .
 \begin{align}

### 2017-07-20 paper/experiments.tex
wd

--- 2017-07-20 paper/experiments.tex
@@
 \label{tab:grph}
+\vspace{-4ex}
 \end{table}
@@
 
-We have implemented the encodings for each variants
+We have implemented~\footnote{\url{https://github.com/arey0pushpa/pyZ3}}
+the encodings for each variants
 using the python interface of $\zthree$ in a tool (A'tool).
@@
 %
- \textbf{Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2).}.
+Using this encoding in comparison to the old one, not only we got
+efficiency improved for finding a SAT model but also did better in the
+case of refutation that no model exist (Table 2 variant A timing
+comparison and variant D with N =2).
+%
 Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to

### 2017-07-20 paper/experiments.tex

@@
 \label{tab:grph}
-\vspace{-4ex}
 \end{table}
@@
 
-We have implemented~\footnote{\url{https://github.com/arey0pushpa/pyZ3}}
-the encodings for each variants
-using the python interface of $\zthree$ in a tool (A'tool).
+We have
+implemented~\footnote{\url{https://github.com/arey0pushpa/pyZ3}} the
+encodings for each variants using the python interface of $\zthree$ in
+a tool (MAA).
 %
@@
 To illustrate usability of our tool 
-in last column of the table~\ref{tab:grph}, we also present the minimum connectedness
-needed for the different variants after applying our tool for sizes from 2 to 10.
+in last column of the table~\ref{tab:grph}, we also present the minimum connectedness needed for
+the different variants after applying our tool for sizes from 2 to 10. 
 %
@@
 %
+For the comparison between both encodings we have fixed the total
+number of molecules to be twice as number of the nodes for N $>$ 2 and M
+= 2N + 1 for N = 2. For each version we fix total number of parallel
+edges to maximum two. In the table we have shown comparison for
+specific connectivity, for example Variant A is checked against any
+graph with connectivity 2, Variant B with connectivity 3 similarly for
+the rest of the Variants.
+%
 The experiments were done on a machine with Intel(R) Core(TM) i3-4030U

### 2017-07-20 paper/experiments.tex
updated table2-description

--- 2017-07-20 paper/experiments.tex
@@
 
-We have implemented~\footnote{\url{https://github.com/arey0pushpa/pyZ3}}
-the encodings for each variants
-using the python interface of $\zthree$ in a tool (A'tool).
+We have implemented the encodings for each variants
+using the python interface of $\zthree$ in a tool (MAA).
 %
@@
 
-To illustrate usability of our tool 
-in last column of the table~\ref{tab:grph}, we also present the minimum connectedness
-needed for the different variants after applying our tool for sizes from 2 to 10.
+To illustrate usability of our tool in last column of the table~\ref{tab:grph}, we also present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10.
+
 %
@@
 If we allow every present molecule to stay active (Ann) but constraint the edge
-by a boolean function (Aeb) the resultant VTS has to be at least 3-connected.
+by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. Similarly, the results for the other cases are presented in the table. 
 %
@@
 %
-Similarly, the results for the other cases are presented in the table.
+We ran experiments varying all parameters for specific N (size).
+For the comparison between both encodings (Table 2) we have fixed the total number of molecules to be twice as number of the nodes for N $>$ 2 and M = 2N + 1 for N = 2.
+For each version we also fix total number of parallel edges to maximum two.
+We have specifically chosen the same connectivity as Table 1 just for illustration purpose; for example in Table~\ref{tab:qf-grabh} Variant A, only check against graph with connectivity 2 is shown, in Variant B with connectivity 3 and similarly for the rest of the Variants.
 
@@
 %
-Using this encoding in comparison to the old one, not only we got
-efficiency improved for finding a SAT model but also did better in the
-case of refutation that no model exist (Table 2 variant A timing
-comparison and variant D with N =2).
-%
+Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2).
 Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to

### 2017-07-20 paper/experiments.tex
updated table2-description

@@
 We have specifically chosen the same connectivity as Table 1 just for illustration purpose; for example in Table~\ref{tab:qf-grabh} Variant A, only check against graph with connectivity 2 is shown, in Variant B with connectivity 3 and similarly for the rest of the Variants.
+Choice of Variants in the table reflects different type of results variations, for example we left out version B and E as it is of same connectivity type as of A \footnote{Complete result is present in our referenced repository}.
 
@@
 %
-Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2).
+Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 Variant A timing comparison and Variant D with N =2).
 Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to

### 2017-07-25 cbmc/1C.c
-m

@@ -1,0 +1,435 @@
+// Arbitary Boolean on edge and nodes.
+#include <stdio.h>
+#include <stdlib.h>
+#include <time.h>
+
+#define M 3      
+#define N 3
+#define snareLength 3
+#define dLen 6  // 2 * M  
+#define bigLen 64 // 2 ^ (2*M) 
+#define len 5
+
+_Bool nondet_bool();
+unsigned int nondet_uint();
+
+typedef unsigned __CPROVER_bitvector[M] bitvector; 
+typedef unsigned __CPROVER_bitvector[snareLength] snareVector; 
+typedef unsigned __CPROVER_bitvector[dLen] dvector;
+typedef unsigned __CPROVER_bitvector[bigLen] bigvector;
+
+
+unsigned int  nondet (){  
+  unsigned int num = nondet_uint();
+  __CPROVER_assume( num>= 0 && num  <= 1);
+   return num;
+};
+
+unsigned int zeroTon(unsigned int n) {
+    unsigned int result = nondet_uint();
+    __CPROVER_assume(result >=0 && result <=n);
+    return result ;
+};
+
+bigvector nondetBV() {
+	     bigvector bee;
+	     __CPROVER_assume(bee >= 0b0 && bee <= 0b1111);  
+	     return bee;  }
+
+
+struct EdgeBag
+ {
+   unsigned int ith;
+   unsigned int jth;
+   unsigned int count;
+   unsigned int count2;
+   bitvector edgeWeight;
+   snareVector  vSnare;
+   snareVector tSnare;
+   snareVector combinedMask; 
+   snareVector combinedMask2; 
+};
+
+
+int  main()
+ {    
+     clock_t start, end;
+     double cpu_time_used;
+    start = clock();
+    unsigned int pos, i, j, k, l, m ,w, x, y , iVal, jVal, g, g0, gl, lastg, ng, nl, nl2 ;
+    unsigned int edgePos = 0, bagNo = 0, colorNode = 0 , minColor, cPos = 0 , tComp, result;
+    unsigned int  ticks, ticks2, valj, vali , calc, edgeCount = 0;
+    _Bool Ck=0, Cl = 0,Cf = 1, C0 = 1, C1 = 1, C2 = 1, C3 = 1, C4, C5, C6 , C7; 
+
+    bigvector b1 = 0b1, b0 = 0b0, vf, vff, edegeInhib[dLen], nodeInhib[dLen];
[…]

### 2017-07-25 cbmc/1E.c

@@ -1,0 +1,369 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+
+#define M 5
+#define N 5
+#define snareLength 5
+#define len 8
+
+
+_Bool nondet_bool();
+unsigned int nondet_uint();
+
+typedef unsigned __CPROVER_bitvector[M] bitvector; 
+typedef unsigned __CPROVER_bitvector[snareLength] snareVector; 
+
+
+unsigned int  nondet (){  
+  unsigned int num = nondet_uint();
+  __CPROVER_assume( num>= 0 && num  <= 1);
+   return num;
+};
+
+unsigned int zeroTon(unsigned int n) {
+  unsigned int result = nondet_uint();
+  __CPROVER_assume(result >=0 && result <=n);
+  return result ;
+};
+
+struct EdgeBag
+ {
+   unsigned int ith;
+   unsigned int jth;
+   unsigned int count;
+   unsigned int count2;
+   bitvector edgeWeight;
+   snareVector  vSnare;
+   snareVector tSnare;
+   snareVector combinedMask; 
+   snareVector combinedMask2; 
+};
+
+
+int  main()
+ 
+ {    
+
+    unsigned int pos, i, j, k, l, m ,w, x, y , iVal, jVal, g, g0, gl, lastg, ng, nl, nl2 ;
+    unsigned int edgePos = 0, bagNo = 0, colorNode = 0 , minColor, cPos = 0 , tComp, result;
+    unsigned int  ticks, ticks2, valj, vali , calc, edgeCount = 0;
+    _Bool Ck=0, Cl = 0,Cf = 1, C0 = 1, C1 = 1, C2 = 1, C3 = 1, C4, C5, C6 , C7; 
+   
+    bitvector Vnodes[N], Tnodes[N];
+    bitvector  fareTotal, inTotal, outTotal , outVSnareTotal , inVSnareTotal , outTSnareTotal , inTSnareTotal ;
+    
+    snareVector total, cond2Total, cond2fareTotal, centTotal, centTotal2, placeHolder;
+    snareVector v, vl, vl2, t, f, h, v2, lastv, lastv2 ,nv, nv2, v0, v02 ;
+    snareVector Tedge[N][N], Vedge[N][N] , Vedge2[N][N] , Tedge2[N][N] , fComp , bComp;    
+    snareVector qrfusionMatrix[snareLength], rqfusionMatrix[snareLength];     
+  
+    unsigned int graph[N][N]; 
+
[…]

### 2017-07-25 cbmc/1F.c

@@ -1,0 +1,415 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+#define M 5
+#define N 5
+#define snareLength 5
+#define dLen 10  // 2 * M  
+#define bigLen 1024 // 2 ^ (2*M) 
+#define len 10
+
+
+_Bool nondet_bool();
+unsigned int nondet_uint();
+
+typedef unsigned __CPROVER_bitvector[M] bitvector; 
+typedef unsigned __CPROVER_bitvector[snareLength] snareVector; 
+typedef unsigned __CPROVER_bitvector[dLen] dvector;
+typedef unsigned __CPROVER_bitvector[bigLen] bigvector;
+
+
+unsigned int  nondet (){  
+  unsigned int num = nondet_uint();
+  __CPROVER_assume( num>= 0 && num  <= 1);
+   return num;
+};
+
+unsigned int zeroTon(unsigned int n) {
+    unsigned int result = nondet_uint();
+    __CPROVER_assume(result >=0 && result <=n);
+    return result ;
+};
+
+bigvector nondetBV() {
+	     bigvector bee;
+	     __CPROVER_assume(bee >= 0b0 && bee <= 0b1111);  
+	     return bee;  }
+
+
+struct EdgeBag
+ {
+   unsigned int ith;
+   unsigned int jth;
+   unsigned int count;
+   unsigned int count2;
+   bitvector edgeWeight;
+   snareVector  vSnare;
+   snareVector tSnare;
+   snareVector combinedMask; 
+   snareVector combinedMask2; 
+};
+
+
+int  main()
+ {    
+	 
+    unsigned int pos, i, j, k, l, m ,w, x, y , iVal, jVal, g, g0, gl, lastg, ng, nl, nl2 ;
+    unsigned int edgePos = 0, bagNo = 0, colorNode = 0 , minColor, cPos = 0 , tComp, result;
+    unsigned int  ticks, ticks2, valj, vali , calc, edgeCount = 0;
+    _Bool Ck=0, Cl = 0,Cf = 1, C0 = 1, C1 = 1, C2 = 1, C3 = 1, C4, C5, C6 , C7; 
+
+    bigvector b1 = 0b1, b0 = 0b0, vf, vff, edegeInhib[dLen], nodeInhib[dLen];
+    dvector bv ,bvv;
+   
+    bitvector Vnodes[N], Tnodes[N];
[…]

### 2017-08-09 paper/bio_MTedit.tex
Review-update

@@
 We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales.
-This implies incoming and outgoing fluxes are balanced for each molecular type at each compartment; this is the \textit{stability condition}.
+Therefore, incoming and outgoing fluxes are balanced for each molecular type at each compartment; it is the \textit{stability condition}.
 
@@
 Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle.
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which a two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
+We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
 This is motivated by the idea that pairing must generate an inactive bi-molecular complex.

### 2017-08-09 paper/related.tex
updated table2-description
Review-update

@@
 
-Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient}.
+Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
 GNR is a complex system driven by many complex rules.
-We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking}.
+We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking,shukla}.
 Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge.

### 2017-08-09 review-sasb-sat/main.tex
Review-update

\documentclass{llncs}
\renewcommand\thesection{\Roman{section}}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[usenames, dvipsnames]{color}

\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
\definecolor{mypink2}{RGB}{219, 48, 122}
\definecolor{mypink3}{cmyk}{0, 0.7808, 0.4429, 0.1412}
\definecolor{mygray}{gray}{0.6}

%\usepackage[dvipsnames]{xcolor}
\usepackage[pdftex,dvipsnames]{xcolor}
\colorlet{LightRubineRed}{RubineRed!70!}
\colorlet{Mycolor1}{green!10!orange!90!}
\definecolor{Mycolor2}{HTML}{00F9DE}
\newcommand\myworries[1]{\textcolor{red}{#1}}
\usepackage{lipsum}                     % Dummytext
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
  % Coloured text etc.
% 
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\begin{document}

\title{Review: SASB SAT Solving for Vesicle Traffic Systems in Cells}

\author{Ashutosh Gupta, Ankit Shukla, Mandayam Srivas and Mukund Thattai}

\institute{TIFR}
\maketitle

\section{Review 1}
\begin{enumerate}
\item {Overall evaluation: Weak accept\\}
\end{enumerate}
\textbf{{\color{black} Evaluation\\}}
{\color{green!20!blue}The paper describes a SAT encoding of the model identification problem for graphical
models of cellular vesicle traffic systems (VTS).
By integrating all the constraints on admissible graphs for VTS, and in particular
regarding stability and reachability constraints, the author obtained an efficient
implementation relying on Z3 which outputs a model (if exists) which satisfy
necessary constraints for VTS and variants of additional constraints on the
topology/functionality of the model.\\}

As far as I understood, the method allows to identify one graph (if any) ; \todo{Discuss with Ashutosh} \textbf{it would be interesting to consider counting the number of solutions as well.}

The paper is very technical and focuses mainly on the SAT encoding of the problem
and \textbf{gives very few examples of application on concrete biological examples.} \todo{Mukund should address this} It will be interesting to discuss the results of the different variants of the model identification on small cases with a biological perspective.\\

\section{Review 2}
\begin{enumerate}
\item {Overall evaluation: Weak accept\\}
\end{enumerate}

\textbf{Evaluation }

{\color{green!20!blue}The paper presents a SAT-based method to study vesicle traffic systems and
specifically, to derive network models for these systems that satisfy some given
properties, specifically, k-connectedness.

The motivation behind the work is very important, i.e. understanding the regulation
of the SNARE protein that is crucial in this system and in particular, in
determining specific network topologies. \todo {We should motivate why k-connected is important? Just reference to old paper i think is not enough. I and Mukund can address this.} \textbf{However biological considerations are only
marginal in this work, and the use of the k-connectedness property} (the only
property considered in this work) \textbf{is not motivated or justified}. \textbf{The authors should
put more effort into explaining why k-connectedness is important here. }}

Discussion of results also reflect this \todo {we should discuss this} \textbf{lack of bio insights}, and is mainly devoted to comparing performance w.r.t. a previous BMC-based version of the approach.

On the other hand, the SAT-based method is adequate, sound and very relevant (for
both this case study and SASB), even though the encoding is quite straightforward.
The paper is generally well written and easy to follow. \\

Please find more detailed comments below:\\
\begin{enumerate}
\item one sentence of the abstract is misleading: "what are all possible networks for
various combinations of those properties?" what you actually do is finding ONE
network (i.e. a model satisfying the SMT problem), not all networks. Consider
rephrasing this.\newline
\todo{We should discuss how to rephrase this or stay as it is.}
{\color{red}{Mukund, Ashutosh}}\\
\item can you better motivate the steady state assumption? have you performed any
dynamic/transient analysis of such derived networks? \newline
{\color{red}{Mukund}}\\
\item Page 3, Line 110: "in which a two SNAREs" --"in which two SNAREs" \newline{\color{red}{Fixed!}}\\

\item  Page 3, "synthesis" paragraph: \todo{Not sure why people are finding too many biology section gaps, happened with last paper also. May be they are too much interested in understanding the biology.} I don't get what you are explaining here, is that a list of analysis performed? I couldn't see any of this in the result section. \newline
{\color{red}{Mukund}}\\

\item Definition 1: shouldn't it be $E \subseteq N \times ... $(not the other way round)? \newline
{\color{red}{Ashutosh}}\\

\item the definition of well-structured network deserves better explanation: what does
"equal partitions" mean? partitions with the same num of elements? the second
condition would be clearer if you added an explanation.\newline
{\color{red}{Ashutosh}}\\

\item - \todo{We should add to the definition. This reviewer have read things in detail} Do you allow self-edges in G? I see that you later add constraints to avoid that, but I've missed this point from definition 1\newline
{\color{red}{Ankit, Ashutosh}}\\

\item Definition of connectedness for G: do you allow any path, or it must exist $m \in M$ such that for all n,n', n' is m-reachable from n? this is not clear at this point
and should be improved. \newline
{\color{red}{Ashutosh}}\\

\item Since you use uninterpreted functions, I guess you can no longer say that you use
SAT, \todo{valid point should be addressed} but you are using SMT (the theory being that of uninterpreted functions).\newline
{\color{red}{Srivas, Ankit, Ashutosh}}\\

\item Eq. V1: I don't get why you use implication and not double implication \newline
{\color{red}{Ashutosh}}\\

\item Related work: some key references are missing about SAT/SMT-based methods for the
synthesis of gene regulatory networks.\newline
\textcolor{red}{Completed !}
\end{enumerate}

\end{document}

### 2017-08-12 paper/bio_MTedit.tex
bio_review_incorporated

@@
 
-In this section, we will describe the model of VTSs and the basic constraints imposed by cell biology.
+In this section, we will describe the basic constraints imposed by cell biology. These are all incorporated into an abstract model of a VTS, whose properties will then be explored using SMT solvers.
 
@@
 
-\textbf{Synthesis:} Given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model, we do the following.
+\textbf{Properties of a VTS that satisfies all cell-biological constraints:} Suppose we are given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model.
+This information is then sufficient to check the following properties, which summarise the cell-biological constraints described above:
+\begin{enumerate}
+\item We can determine which molecules are active on every compartment or vesicle.
+\item For every vesicle fusing to a compartment, we can determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
+\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we can verify that there is no pairing of active molecules on the
+vesicle and compartment that could drive their fusion.
+\item We can verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set.
+This is the steady state condition.
+In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2017}.
+\end{enumerate}
 
-\begin{enumerate}
-\item We determine which molecules are active on every compartment or vesicle.
-\item For every vesicle fusing to a compartment, we determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
-\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we verify that there is no pairing of active molecules on the
-vesicle and compartment that could drive their fusion.
-\item We verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set.
-%steady state condition.
-\end{enumerate}
+The biological problem often boils down to such an analysis.
+A cell biologist might determine which molecules flow between which set of compartments, and biochemical experiments could be used to see how these molecules activate one another.
+We can then ask: is this a complete and consistent description?
+That is, do all the required properties listed above hold, given what the experimentalists have told us?
+It is often the case that biological data is missing.
+For example, only a few of the dozens of molecules involved in real VTSs have been mapped out.
+Therefore, it is extremely likely that the description provided by the cell biologist is incomplete.
+We can use our model to find out which properties have failed to hold, and thus prescribe new experiments in order to fill in the missing information.
+
+Can we find a simple test to see whether any information is missing, given the experimental data?
+We have shown that graph k-connecte furnishes precisely such a test \cite{shukla}.
+If the data provided by cell-biologists, suitably represented as a graph, does not have a certain degree of connectivity, this implies that some biological data has been missed.
+(The converse is not true: even if the required connectivity does hold, there might of course be more information missing.)
+
+Our result about k-connectedness being a useful test of missing information \cite{shukla} was obtained using SAT solvers for graphs up to a certain size, and a certain number of molecules.
+This was due to limitations in how we encoded the problem.
+Here we present a much more natural encoding that allows our result to be extended to graph sizes and molecule numbers that are typical of those found in real cells.
 

### 2017-08-13 paper/bio_MTedit.tex
changes

--- 2017-07-20 paper/bio_MTedit.tex
@@
 %
-This property of VTSs have been considered informative and
+This property of VTSs has been considered informative and
 studied by~\cite{shukla}.

### 2017-08-13 paper/experiments.tex
changes

--- 2017-07-20 paper/experiments.tex
@@
 To illustrate usability of our tool 
-in last column of the table~\ref{tab:grph}, we also present the minimum connectedness needed for
+in the last column of the table~\ref{tab:grph}, we present the minimum connectedness needed for
 the different variants after applying our tool for sizes from 2 to 10. 
@@
 In Table~\ref{tab:qf-grabh}, we present the running times for the search of
-VTSs of sizes 2 to 10 that satisfy the variants.
+VTSs of sizes 2 to 10 that satisfy the variants and compare with our old encoding
+({Old-e}) from~\cite{shukla}.
 %
 For the comparison between both encodings we have fixed the total
-number of molecules to be twice as number of the nodes for N $>$ 2 and M
-= 2N + 1 for N = 2. For each version we fix total number of parallel
-edges to maximum two. In the table we have shown comparison for
-specific connectivity, for example Variant A is checked against any
-graph with connectivity 2, Variant B with connectivity 3 similarly for
-the rest of the Variants.
+number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and
+$|M| = 2|N| + 1$ for $|N| = 2$.
+%
+For each variant, we fix maximum number of parallel
+edges to 2.
+%
+In the table we have shown comparison for specific connectivity, for
+example variant A is checked against any graph with connectivity 2,
+variant B with connectivity 3 similarly for the rest of the Variants.
 %

### 2017-08-13 paper/experiments.tex

--- 2017-07-20 paper/experiments.tex
@@
 
-To illustrate usability of our tool in last column of the table~\ref{tab:grph}, we also present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10.
-
+To illustrate usability of our tool 
+in the last column of the table~\ref{tab:grph}, we present the minimum connectedness needed for
+the different variants after applying our tool for sizes from 2 to 10. 
 %
@@
 In Table~\ref{tab:qf-grabh}, we present the running times for the search of
-VTSs of sizes 2 to 10 that satisfy the variants.
+VTSs of sizes 2 to 10 that satisfy the variants and compare with our old encoding
+({Old-e}) from~\cite{shukla}.
+%
+For the comparison between both encodings we have fixed the total
+number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and
+$|M| = 2|N| + 1$ for $|N| = 2$.
+%
+For each variant, we fix maximum number of parallel
+edges to 2.
+%
+In the table we have shown comparison for specific connectivity, for
+example variant A is checked against any graph with connectivity 2,
+variant B with connectivity 3 similarly for the rest of the Variants.
 %

### 2017-08-13 paper/experiments.tex
fixing bad conflict resolution

--- 2017-07-20 paper/experiments.tex
@@
 
-In Table~\ref{tab:qf-grabh}, we present the running times for the search of
-VTSs of sizes 2 to 10 that satisfy the variants.
+% In Table~\ref{tab:qf-grabh}, we present the running times for the search of
+% VTSs of sizes 2 to 10 that satisfy the variants.
+% and compare with our old encoding
+% ({Old-e}) from~\cite{shukla}.
+% %
+% For the comparison between both encodings we have fixed the total
+% number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and
+% $|M| = 2|N| + 1$ for $|N| = 2$.
+% %
+% For each variant, we fix maximum number of parallel
+% edges to 2.
+% %
+% In the table we have shown comparison for specific connectivity, for
+% example variant A is checked against any graph with connectivity 2,
+% variant B with connectivity 3 similarly for the rest of the Variants.
 %

### 2017-08-16 paper/encoding.tex
changes
sasb-update

@@
 %
-$q$ will range over edges between two nodes.
+$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
 %
 
-% \subsubsection{Constraints on the structure of the edges, nodes and }
 \subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
@@
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,|N|}
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
   \tag{R2}\label{eq:reach2}
@@
 %
-The constraints for the variants can be given to a SAT solver to find
+The constraints for the variants can be given to a SMT solver to find
 VTSs that belong to the variants.

### 2017-08-16 review-sasb-sat/main.tex
sasb-update

@@
 \textbf{{\color{black} Evaluation\\}}
-{\color{green!20!blue}The paper describes a SAT encoding of the model identification problem for graphical
+The paper describes a SAT encoding of the model identification problem for graphical
 models of cellular vesicle traffic systems (VTS).
@@
 necessary constraints for VTS and variants of additional constraints on the
-topology/functionality of the model.\\}
+topology/functionality of the model.\\
 
-As far as I understood, the method allows to identify one graph (if any) ; \todo{Discuss with Ashutosh} \textbf{it would be interesting to consider counting the number of solutions as well.}
+As far as I understood, the method allows to identify one graph (if any) ; \textbf{it would be interesting to consider counting the number of solutions as well.}\newline
+{\color{red}{Ashutosh}}
 
 The paper is very technical and focuses mainly on the SAT encoding of the problem
-and \textbf{gives very few examples of application on concrete biological examples.} \todo{Mukund should address this} It will be interesting to discuss the results of the different variants of the model identification on small cases with a biological perspective.\\
+and \textbf{gives very few examples of application on concrete biological examples.}\\ 
+{\color{red}{Ankit\\}}
+
+It will be interesting to discuss the results of the different variants of the model identification on small cases with a biological perspective.\\
+{\color{red}{Our Comment/Reply:}}
+%The reviewer has highlighted that it would be interesting to connect thedifferent variants of the model to relevant biological cases.
+{\color{blue}{ We agree wholeheartedly. However, there is at the moment very little known about how
+the regulation of SNAREs functions. What we have done here is to study many
+possible variants of SNARE regulation, from simple to complex. It is
+difficult to say which one of these variants is likely to hold in real
+cells, and indeed, different species might use different versions of SNARE
+regulation. Luckily, even given the most general variant of SNARE
+regulation (of which all other models are just special cases) we have still
+managed to find a constraint on graph connectedness. Thus we are confident
+that our results apply to existing cell-biological data. One of the authors
+(MT) is presently assembling a list of known SNARE fluxes in yeast and
+mammalian cells to see whether our predictions hold. This will be published
+as a follow-up manuscript, and we are happy to share a draft of this
+manuscript with the reviewers.}}
 
@@
 
-{\color{green!20!blue}The paper presents a SAT-based method to study vesicle traffic systems and
+The paper presents a SAT-based method to study vesicle traffic systems and
 specifically, to derive network models for these systems that satisfy some given
@@
 of the SNARE protein that is crucial in this system and in particular, in
-determining specific network topologies.
-\todo {We should motivate why k-connected is important?
-Just reference to old paper i think is not enough.
-I and Mukund can address this.} \textbf{However biological considerations are only
+determining specific network topologies. \textbf{However biological considerations are only
 marginal in this work, and the use of the k-connectedness property} (the only
 property considered in this work) \textbf{is not motivated or justified}. \textbf{The authors should
-put more effort into explaining why k-connectedness is important here. }}
+put more effort into explaining why k-connectedness is important here. }
 
-Discussion of results also reflect this \todo {we should discuss this} \textbf{lack of bio insights}, and is mainly devoted to comparing performance w.r.t.
-a previous BMC-based version of the approach.
+{\color{red}{Fixed! refer new updated draft.\\}}
+
+Discussion of results also reflect this \textbf{lack of bio insights}, and is mainly devoted to comparing performance w.r.t. a previous BMC-based version of the approach. \newline 
+{\color{red}{Commented! see first review blue color paragraph\\}}
 
@@
 both this case study and SASB), even though the encoding is quite straightforward.
-The paper is generally well written and easy to follow. \\
+The paper is generally well written and easy to follow. \\ \\
 
@@
 \todo{We should discuss how to rephrase this or stay as it is.}
-{\color{red}{Mukund, Ashutosh}}\\
+{\color{red}{Ashutosh.}}\\
+
 \item can you better motivate the steady state assumption? have you performed any
 dynamic/transient analysis of such derived networks? \newline
-{\color{red}{Mukund}}\\
+{\color{red}{Fixed ! refer updated draft.}}\\
+
 \item Page 3, Line 110: "in which a two SNAREs" --"in which two SNAREs" \newline{\color{red}{Fixed!}}\\
 
-\item  Page 3, "synthesis" paragraph: \todo{Not sure why people are finding too many biology section gaps, happened with last paper also.
-May be they are too much interested in understanding the biology.} I don't get what you are explaining here, is that a list of analysis performed?
-I couldn't see any of this in the result section.
-\newline
-{\color{red}{Mukund}}\\
+\item  Page 3, "synthesis" paragraph: I don't get what you are explaining here, is that a list of analysis performed? I couldn't see any of this in the result section. \newline
+{\color{red}{Fixed! See updated draft}}\\
 

### 2017-08-16 paper/encoding.tex
minor fixed

@@
   \item $\mols$ is the set of molecules flowing in the system, 
-  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes  
-  \item $ \nodes \times (\powerset{\mols}-\emptyset) \times \nodes \subseteq \edges$ is the
-    set of edges with molecule sets as labels
-  \item $\pairs \subseteq \mols \times \mols$ is pairing relation
-  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
-  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges
+  \item $\edges \subseteq \nodes \times (\powerset{\mols}-\emptyset) \times \nodes$ is the
+    set of edges with molecule sets as labels,
+  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes,
+  \item $\pairs \subseteq \mols \times \mols$ is pairing relation,
+  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes, and
+  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges.
   \end{itemize}
@@
 %
-The constraints for the variants can be given to a SMT solver to find
+The constraints for the variants can be given to a SAT solver to find
 VTSs that belong to the variants.

### 2017-08-17 paper/conclusion.tex
?? fixed

@@
 %
-However, there are many further search problems that are of interest.
+However, there are many further search problems or extensions
+that are of interest.
 %
@@
 
+One may be interested in counting the number of graphs that satisfy
+a given property.
+%
+Exact counting of the graphs using SAT solvers may prove to be very difficult.
+%
+We are also planning to employ some methods for approximate counting of solutions.
+
 % \ankit{interpret experiments (3-4 lines)}
 
- \srivas{Future work(quantifier problem etc)}
+ % \srivas{Future work(quantifier problem etc)}
 

### 2017-08-17 paper/encoding.tex

@@
 \begin{df}
-  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$, where
+  A VTS $G$ is a tuple $(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$, where
   \begin{itemize}
@@
 We call $G$ {\em well-structured} if molecules $M$ is divided into
-two equal partitions $M_1$ and $M_2$ such that $P \subseteq M_1 \times M_2$, and
+two equal-sized partitions $M_1$ and $M_2$ such that
+$P \subseteq M_1 \times M_2$, and
 for each $(n,M',n') \in \edges$, $n \neq n'$, 
-$M' \subseteq \nlabel(n)$, and $M' \subseteq \nlabel(n')$.
+$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
 %
+In other words, a well-structured VTS has no self loops, and 
+each edge carry only those molecules that are present in its source
+and destination nodes.
 
@@
 VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
+%
+In the definition, we do not care about the paths to be $m$-connected for some $m$.  
+%
+A variant of the definition may be sensitive to the $m$-connectedness, but
+we are not considering the variation.
 

### 2017-10-01 paper/abstract.tex
added new formula

@@
 such as three connectivity. These properties are consequences of underlying
-biophysical constraints. A natural question for biologists is: what are all
+biophysical constraints. A natural question for biologists is: what are the
 possible networks for various combinations of those properties? In this
-paper, we present novel SAT encodings of the properties over vesicle traffic
+paper, we present novel SMT based encodings of the properties over vesicle traffic
 systems and a tool that searches for the networks that satisfies the
-properties using SAT solvers. In our experiments, we show that our tool
+properties using SMT solvers. In our experiments, we show that our tool
 can search for networks of sizes that are considered to be relevant by

### 2017-10-01 paper/encoding.tex
added new formula

@@
 %
-Subsequently, we will present the SAT encoding of the search problems
+Subsequently, we will present the SMT encoding of the search problems
 for the graphs that satisfy the conditions.
@@
 We translate the search problem into a Boolean satisfiability
-problem and use SAT solvers to find the satisfying VTSs.
+problem and use SMT solvers to find the satisfying VTSs.
 %
@@
 
-\subsection{SAT problems for different variants}
+\subsection{Complete formula}
+The complete QBF looks like the following.
+\begin{align}
+\exists \, e_{i,j,q} \forall \,d_{i,j,q}, r^{\prime}_{i,j,q} \, (D1 \land D2 \land D3 \land D4)  \, \land \notag\\  \forall\, n_{i,k}, a_{i,k}, e_{i,j,k,q}, b_{i,j,k,q}, r_{i,j,k}, p_{k,k^{\prime}} \, \neg (V1 \land V2 \land ...
+V8 \land A_{n} \land A_{e})  \label{eq:final}
+\end{align}
+
+\subsection{SMT problems for different variants}
 %\ankit{Bring model variant table here}

### 2017-10-01 MAA/qbf_old.py

@@ -1,0 +1,898 @@
+#!/usr/bin/python
+
+from z3 import *
+import argparse
+import time
+
+#----------------------------------------------------
+# input parsing
+# input number of nodes and molecules
+parser = argparse.ArgumentParser(description='Auto testing for TARA')
+parser.add_argument("-M","--mols", type=int, default=4, help = "number of molecules")
+parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes")
+parser.add_argument("-Q","--pedges", type=int, default=1, help = "max no.of parallel edges btw two nodes")
+parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
+parser.add_argument("-C","--connected", type=int, default=3, help = "graph connectivity want to check")
+args = parser.parse_args()
+
+M = args.mols
+N = args.nodes
+Q = args.pedges
+V = args.variation
+C = args.connected
+
+bag = []
+bag.append ('1. Boolean function on nodes and Boolean function on the edges.') 
+bag.append ('2. Only Boolean function on the edges.') 
+bag.append ('3. Boolean function on nodes and SNARE-SNARE inhibition on edges.')
+bag.append ('4. Only SNARE-SNARE inhibition on edges.')
+bag.append ('5. Only Boolean function on nodes.')
+bag.append ('6. No regulation at all.')
+
+for i in range(6):
+    if V == i + 1:
+        print ' '
+        print 'Default/choosen vesicular traffic system is regulated by ...',
+        print bag[i]
+        print ' '
+        print 'Use -V option to change the regulated variation.' 
+        for i in bag:
+            print i 
+        print ' '
+        break
+
+#----------------------------------------------------
+# Constraint generation 
+edge = [ [ [ Bool ("e_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+E = [ edge[i][j][q] for i in range(N) for j in range(N) for q in range(Q) if i != j]
+
+#print len(E)
+#print E
+
+# Un_Skolemized dumped edges and reachability.
+dump = [ [ [Bool ("d_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
[…]

### 2017-12-27 sabs-2017/paper/bio_MTedit.tex

--- 2017-08-12 paper/bio_MTedit.tex
@@
 This is the steady state condition.
-In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2017}.
+In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
 \end{enumerate}
@@
 Can we find a simple test to see whether any information is missing, given the experimental data?
-We have shown that graph k-connecte furnishes precisely such a test \cite{shukla}.
+We have shown that graph k-connectedness furnishes precisely such a test \cite{shukla}.
 If the data provided by cell-biologists, suitably represented as a graph, does not have a certain degree of connectivity, this implies that some biological data has been missed.

### 2017-12-27 sabs-2017/paper/experiments.tex

--- 2017-08-13 paper/experiments.tex
@@
 
-We have
-implemented~\footnote{\url{https://github.com/arey0pushpa/pyZ3}} the
-encodings for each variants using the python interface of $\zthree$ in
-a tool (MAA).
+We have implemented the encodings for each variants
+using the python interface of $\zthree$ in a tool (MAA).
 %
@@
 %
-Similarly, the results for the other cases are presented in the table.
+% We ran experiments varying all parameters for specific N (size).
+For the comparison between both encodings (Table 2) we have fixed the total number of molecules to be twice as number of the nodes for N $>$ 2 and M = 2N + 1 for N = 2.
+For each version we also fix total number of parallel edges to maximum two.
+We have specifically chosen the same connectivity as Table 1 just for illustration purpose; for example in Table~\ref{tab:qf-grabh} Variant A, only check against graph with connectivity 2 is shown, in Variant B with connectivity 3 and similarly for the rest of the Variants.
+Choice of Variants in the table reflects different type of results variations, for example we left out version B and E as it is of same connectivity type as of A \footnote{Complete result is present in our referenced repository}.
 
@@
 In Table~\ref{tab:qf-grabh}, we present the running times for the search of
-VTSs of sizes 2 to 10 that satisfy the variants and compare with our old encoding
+VTSs of sizes 2 to 10 that satisfy the variants.
+and compare with our old encoding
 ({Old-e}) from~\cite{shukla}.
@@
 variant B with connectivity 3 similarly for the rest of the Variants.
-%
+
 The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
@@
 %
-Using this encoding in comparison to the old one, not only we got
-efficiency improved for finding a SAT model but also did better in the
-case of refutation that no model exist (Table 2 variant A timing
-comparison and variant D with N =2).
-%
+Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 Variant A timing comparison and Variant D with N =2).
 Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to

### 2018-04-15 papers/sabs-2017/paper/intro_MTedit.tex
moved

--- 2017-07-20 paper/intro_MTedit.tex
@@
 % \todo{REQUIRE A REWRITE FLOW PROBS}
-In this paper, we have developed a novel SAT encoding for
+In this paper, we have developed a novel SMT based encoding for
 searching VTSs that satisfy the useful properties.
@@
 \item Novel encodings of reachability and 3-4 connectivity
-\item Direct encoding into the SAT solver
+\item Direct encoding into the SMT solver
 \item A user friendly and scalable tool based on well known SMT solver Z3

### 2018-04-15 papers/sabs-2017/paper/related.tex
moved

--- 2017-07-20 paper/related.tex
@@
 %\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
-Modern day SAT solvers can handle millions of variables and due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT solvers.
+Modern day SAT/SMT solvers can handle millions of variables and due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT/SMT solvers.
 There are many graphs related combinatorial work \cite{gay2013solving,wotzlaw2012generalized} that have used SAT solvers.
@@
 % Many network questions are being reduced to solving a SAT question.
-Many of these biological system uses model checkers to reason about graphs and networks rules with possible exhaustive search \cite{guerra2012reasoning,chin2008biographe}.
+Many of these biological system uses these tools and techniques to reason about graphs and networks rules with possible exhaustive search \cite{guerra2012reasoning,chin2008biographe}.
 
-Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient}.
+Recently these tools and techniques have found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
 GNR is a complex system driven by many complex rules.
-We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking}.
-Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge.
-In this paper, we have achieved the scalability required for analyzing vesicular transport network for eukaryotic cells, of total ten compartments (N = 10).
+We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking,shukla}, but scaling it to cases which are interesting biologically is still a challenge.
+In this paper, we have achieved the scalability required for analyzing VTS for eukaryotic cells, of total ten compartments (N = 10).
 \\

### 2018-04-15 papers/sabs-2017/paper/bio.tex

--- 2017-07-15 paper/bio.tex
@@
 outgoing fluxes are balanced for each molecular type at each
-compartment.
+compartment; this is the \textit{stability condition}.
 
@@
 We have also tested a particularly simple regulation mechanism in which two
-molecules that can pair to drive fusion inhibit one another.
+molecules that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
 %
@@
 and also that every molecular type entering a set of compartments also
-leaves that set; this is the steady state condition.
+leaves that set.
 %

### 2018-04-15 papers/sabs-2017/review-sasb-sat/main.tex

--- 2017-08-16 review-sasb-sat/main.tex
@@
 As far as I understood, the method allows to identify one graph (if any) ; \textbf{it would be interesting to consider counting the number of solutions as well.}\newline
-{\color{red}{Ashutosh}}
+{\color{red}{done.}}
 
@@
 \todo{We should discuss how to rephrase this or stay as it is.}
-{\color{red}{Ashutosh.}}\\
+{\color{red}{done.}}\\
 
@@
 \item Definition 1: shouldn't it be $E \subseteq N \times ... $(not the other way round)? \newline
-{\color{red}{Ashutosh}}\\
+{\color{red}{done.}}\\
 
@@
 condition would be clearer if you added an explanation.\newline
-{\color{red}{Ashutosh}}\\
+{\color{red}{done.}}\\
 
@@
 I see that you later add constraints to avoid that, but I've missed this point from definition 1\newline
-{\color{red}{Ankit, Ashutosh}}\\
+{\color{red}{it was already written in the definition of well-structured}}\\
 
@@
 and should be improved. \newline
-{\color{red}{Ashutosh}}\\
+{\color{red}{done.}}\\
 
@@
 SAT, \todo{valid point should be addressed} but you are using SMT (the theory being that of uninterpreted functions).\newline
-{\color{red}{Srivas, Ankit, Ashutosh}}\\
+{\color{red}{Ankit will replace everywhere from SAT to SMT}}\\
 
 \item Eq. V1: I don't get why you use implication and not double implication \newline
-{\color{red}{Ashutosh}}\\
+{\color{red}{Ashutosh. needs thinking?? }}\\
 

### 2018-04-15 papers/synth/abstract.tex

Vesicle Traffic Systems are the transport mechanisms inside the cells.
%
Different compartments are viewed as nodes and transport channels are
nodes between the graphs.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-04-15 papers/synth/abstract.tex
abstract in

@@
-Vesicle Traffic Systems are the transport mechanisms inside the cells.
+Vesicle Traffic Systems(VTS) are the material transport mechanisms
+among the compartments inside the cells.
 %
-Different compartments are viewed as nodes and transport channels are
-nodes between the graphs.
+The compartments are viewed nodes that labeled with the containing
+material and the transport channels are labeled edges between the
+graphs.
+%
+Understanding VTS is an ongoing area of research.
+%
+There may be undiscovered edges or nodes.
+%
+The labels may not have been fully observed.
+%
+Furthermore, it is matter of debate what properties
+these systems should have, such as stability, i.e., every
+chemical that is leaving a compartment comes back. 
+%
+In these paper, we present the encoding of the above questions
+into the QBF satisfiability problems.
+%
+We have implemented the encodings in a highly configurable tool
+and  apply to a couple of found-in-nature VTSs and 
+several synthetic graphs.
+%
+Our results demonstrates that our method can scale upto the
+graphs of interest.
+%
 

### 2018-04-19 papers/synth/intro.tex

Vesicle Traffic Systems are the transport mechanisms inside the cells.
%
Different compartments are viewed as nodes and transport channels are
nodes between the graphs.

\ashu{Speculative}
Subsequently, it can be potentially useful in guiding biologists

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-04-19 papers/synth/abstract.tex
ASd

--- 2018-04-15 papers/synth/abstract.tex
@@
-Vesicle Traffic Systems are the transport mechanisms inside the cells.
+Vesicle Traffic Systems(VTS) are the material transport mechanisms
+among the compartments inside the biological cells.
 %
-Different compartments are viewed as nodes and transport channels are
-nodes between the graphs.
+The compartments are viewed as nodes that are labeled with the containing
+chemicals and the transport channels are labeled edges between the
+nodes.
+%
+Understanding VTSs is an ongoing area of research and for many cells
+they are partially known.
+%
+For examples, there may be undiscovered edges, nodes, or their labels
+in a VTS of a cell.
+%
+It has been speculated that there are properties that the VTSs must satisfy.
+%
+For example stability, i.e., every chemical that is leaving a compartment comes back.
+%
+Many synthesis questions may arise in this scenario, where we want
+to complete a partially known VTS under a given property.
+%
+In the paper, we present novel encodings of the above questions
+into the QBF satisfiability problems.
+%
+We have implemented the encodings in a highly configurable tool
+and  apply to a couple of found-in-nature VTSs and 
+several synthetic graphs.
+%
+Our results demonstrates that our method can scale upto the
+graphs of interest.
+%
 

### 2018-04-19 vts-synth/src/main.cpp
xor

@@ -133,7 +133,7 @@ int main(int ac, char* av[])
 
   z3::context c;
 
-  load_vts ld(c,"/home/agupta/tmp/t.vts"); ld.load(); return 0;
+  //load_vts ld(c,"/home/agupta/tmp/t.vts"); ld.load(); return 0;
 
   // vts: v [context, Molecule, Nodes, Edge_arity, Version, Connectivity, Cnf_depth ]
   unsigned int N = 3;

### 2018-04-19 vts-synth/src/pp_vts.cpp

@@ -190,7 +190,6 @@ void vts::print_graph( z3::context& c, std::string filename,
         auto q = std::get<2>( i ); 
         auto k = std::get<3>( i ); 
         
-
         if ( std::find( activeEdgeT.begin(), activeEdgeT.end(), i ) != activeEdgeT.end() ) { 
           continue;
         }else {

### 2018-04-19 vts-synth/src/synth-func.cpp

@@ -217,11 +217,11 @@ void vts::print_denotation_console ( std::map<std::string,int> denotation_map, i
     std::vector < std::vector< std::vector <int> > > vVarStr ( M, std::vector< std::vector <int> > ( M-1, std::vector<int>( typeOfGates ) ) );
     
     for ( auto& dm : denotation_map ) {
-      std::cout << " dm is : [" << dm.first << ", " << dm.second << "]\n";
+      //std::cout << " dm is : [" << dm.first << ", " << dm.second << "]\n";
       std::string val;  
       dm.second >= 0 ? val = "True" : val = "False";
 
-      /* std::cout << dm.first << " = " << val << "\n"; */ 
+      std::cout << dm.first << " = " << val << "\n";  
 
       if ( synthVar == 3 ) {
         if ( dm.first[0] == 't' ) {

### 2018-04-19 vts-synth/src/vts-synthesis.cpp

@@ -2,6 +2,7 @@
 #include<z3-util.h>
 #include<algorithm>
 #include<vector>
+
 /** Synthesis Variations 
  * 1. Add edge to achieve graph stability and k connected. 
  * 2. Add flow of molecules to fix fusion. 
@@ -113,7 +114,6 @@ z3::expr vts::annotate_mukund_graph ( z3::expr_vector& fixN, z3::expr_vector& fi
   fixPresenceE.push_back(e9);
   fixPresenceE.push_back(e10);
 
-
   auto edgel_cons = z3::mk_and ( fixPresenceE );
 
   auto cons = nodes_cons && edge_cons && edgel_cons;
@@ -175,20 +175,26 @@ z3::expr vts::annotate_plos_graph () {
   return cons;
 }
 
+bool equality_check( z3::expr_vector fixZ, z3::expr var ) {
+  for ( unsigned i = 0; i < fixZ.size(); i++ ) {
+    if ( (z3::eq( fixZ[i], var) == true ) ) {
+      return true; 
+    }
+  }
+  return false;
+}
 
 void unassigned_bits ( z3::expr_vector& setZ,
                        z3::expr_vector fixZ,
                        z3::expr_vector& openZ ) {
   for ( unsigned i = 0; i < setZ.size(); i++ ) {
-   // auto var = setZ[i];
-   /*
-    if ( std::find( fixZ.begin(), fixZ.end(), var ) != fixZ.end() ) 
+   auto var = setZ[i];
+   if ( equality_check( fixZ, var ) ) 
       continue;
-    else 
+   else 
       openZ.push_back( var );
   }
-  */
-} }
+}
 
 
 z3::expr vts::vts_synthesis ( unsigned variation ) {
@@ -235,9 +241,9 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     
     //auto nodeC = ! at_least_two ( openN );
     //auto nodeActivityC = ! at_least_two ( openActiveE );
-    auto edgeC = ! at_least_three ( openE );
-    auto edgeActivityC = ! at_least_two ( openActiveE );
-    auto edgePresenceC = ! at_least_two ( openPresenceE );
+    auto edgeC = ! at_least_four ( openE );
+    auto edgeActivityC = ! at_least_three ( openActiveE );
+    auto edgePresenceC = ! at_least_three ( openPresenceE );
     
     // Fix rest of them to zero.
[…]

### 2018-04-19 vts-synth/src/vts.h

@@ -176,7 +176,7 @@ public:
   /** Synthesis constraints**/
   z3::expr vts_synthesis ( unsigned variation );
   z3::expr annotate_plos_graph();
-  z3::expr annotate_mukund_graph();
+ // z3::expr annotate_mukund_graph();
 
   /* */
   z3::expr annotate_mukund_graph ( z3::expr_vector& fixN, z3::expr_vector& fixactiveN, z3::expr_vector& fixE, z3::expr_vector& fixpresenceE, z3::expr_vector& fixactiveE, z3::expr_vector& fixpairingP );
@@ -185,7 +185,8 @@ public:
   // void print_func_node ( std::vector < std::vector< std::vector <int> > >  tVarStr );
   void print_denotation_console ( std::map<std::string,int> denotation_map, int  synthVar );
   void create_map ( z3::context& c, std::map<std::string,int>& denotation_map, std::string& depqbfRun, Tup3Expr& nodeT, Tup3Expr& activeNodeT, Tup3Expr& edgeT, Tup4Expr& presenceEdgeT, Tup4Expr& activeEdgeT, VecsExpr qs  );
-  
+  //bool equality_check( z3::expr_vector fixZ, z3::expr var );
+
   /** Build constraint and model **/
   void use_z3_qbf_solver ( z3::expr cons );
   z3::expr vts_activity_constraint();

### 2018-04-19 papers/synth/intro.tex

@@
+Vesicle Traffic Systems(VTS) are the material transport mechanisms
+among the compartments inside the biological cells.\cite{vtsIntro}
+%
+\ashu{Describe VTS in detail}
+
 Vesicle Traffic Systems are the transport mechanisms inside the cells.
@@
 nodes between the graphs.
+
+%
+The labels may not have been fully observed.
+
+Furthermore, it is a matter of debate what properties
+the VTSs should have, such as stability, i.e., every
+chemical that is leaving a compartment comes back.
 

### 2018-04-19 papers/synth/abstract.tex
asd

@@
-Vesicle Traffic Systems(VTS) are the material transport mechanisms
+Vesicle Traffic Systems(VTSs) are the material transport mechanisms
 among the compartments inside the biological cells.
 %
-The compartments are viewed as nodes that are labeled with the containing
-chemicals and the transport channels are labeled edges between the
-nodes.
+The compartments are viewed as nodes that are labeled with the
+containing chemicals and the transport channels are similarly labeled
+edges between the nodes.
 %
@@
 %
-For examples, there may be undiscovered edges, nodes, or their labels
+For example, there may be undiscovered edges, nodes, or their labels
 in a VTS of a cell.
 %
-It has been speculated that there are properties that the VTSs must satisfy.
+It has been speculated that there are properties that the VTSs must
+satisfy.
 %
-For example stability, i.e., every chemical that is leaving a compartment comes back.
+For example, stability, i.e., every chemical that is leaving a
+compartment comes back.
 %
@@
 In the paper, we present novel encodings of the above questions
-into the QBF satisfiability problems.
+into the QBF(quantified Boolean formula) satisfiability problems.
 %

### 2018-04-19 papers/synth/bio.tex
asd

--- 2017-08-17 paper/encoding.tex
@@
-In this section, we will formally define VTSs as a labeled graph
-and the discussed conditions on the graphs.
+In this section, we will present the model of VTS from~\cite{PloS,SASB}.
 %
-Subsequently, we will present the SAT encoding of the search problems
-for the graphs that satisfy the conditions.
-
-\subsection{Model}
-
-We model VTSs as labeled directed graphs.
-The graph labels both nodes and edges with sets of molecules to denote
-the set of molecules present in them.
-The graph is formally defined as follows.
+We will also present the constrains and properties on the VTSs.   
+%
+We model a VTS as labelled graph along with assisting pairing matrices and
+activating functions.
 
@@
 
-We will also consider several variations of the model.
-%
-For example, unique edge between two nodes, activity of molecules is
-not constrained by $\nodef$ and $\edgef$, etc.
+% We will also consider several variations of the model.
+% %
+% For example, unique edge between two nodes, activity of molecules is
+% not constrained by $\nodef$ and $\edgef$, etc.
 %
@@
 
-\paragraph{Search problem}
-Based upon earlier discussion, we need to answer the following search
-question among VTSs.
-For a given $k$, size $\nu$, and molecule number $\mu$,
-we are searching for well-structured, stable, and well-fused VTS
-$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and
-$G$ is not $k$-connected.
-
-\subsection{Boolean satisfiability of the search problem}
-
-We translate the search problem into a Boolean satisfiability
-problem and use SAT solvers to find the satisfying VTSs.
-%
-We will first present the variables used to encode the
-VTSs and the properties.
-%
-Afterwards, we will present the constraints corresponding to the
-properties.
-
-\subsubsection{Variables for VTS description}
-%
-We assume that size of the graph is $\nu$ and number of molecules is
-$\mu$.
-%
-Furthermore, we also limit the maximum number $\pi$ of edges present
-between two nodes.
-%
-Here, we list the vector of Boolean variables and uninterpreted function symbols
-that encode the VTSs.
-\begin{enumerate}
-
-\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
-\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
-\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
-\item Boolean variable $p_{m,m'}$ indicates if $(m,m') \in \pairs$
-\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
-encoding $\nodef(m)$ map
-\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
-encoding $\edgef(m)$ map
-\end{enumerate}
-We also have auxiliary Boolean variables that will help us encode the well-fused and stability properties 
-\begin{enumerate}
-\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
-  holds
-\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\item $r_{i,j,m,p}$ indicates if there is an $m$-path from
-  $i$ to $j$ of length less than or equal to $p$
-\end{enumerate}
-For $k$-connected property, we also use the following auxiliary Boolean variables
-\begin{enumerate}
-\item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped
-\item $r'_{i,j}$ indicates if there is a path from $i$ to $j$ in the modified VTS
-\end{enumerate}
-
-We will describe the Boolean constraints that encode VTSs in several categories.
-%
-In the end, we will present in a table the constraints needed for the
-model variants.
-%
-To avoid cumbersome notation, we will not explicitly write the ranges of the indexing
-in the constraints.
-%
-$i$ and $j$ will range over nodes.
-%
-$m$ will range over molecules.
-%
-$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
-%
-
-\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
-%
-We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
-to encode the basic structure of VTSs.
-%
-For an edge to exist it should have one molecule present. 
-%
-\begin{align}
-  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
-\end{align}
-If a molecule is active on an edge, it should be present on the edge.
-%
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
-\end{align}
-A molecule should be present to be active on a node.  
-\begin{align}
-  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
-  \tag{V3}\label{eq:c4}
-\end{align}
-The edge labels are subset of the node labels of the source and target nodes.
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
-\end{align}
-Self edges are not allowed. 
-\begin{align}
-   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
-\end{align}
-We fix first half as Q-SNAREs and rest as R-SNAREs and set diagonal blocks in pairing matrix to be 0's.
-%It reduces the search space.
-% Condition on $p_{kk'}$. \ashu{why???} .
-\begin{align}
-  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
-  \tag{V6}\label{eq:c3}
-\end{align}
-
-\subsubsection{Well-fused constraints}
-Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
-its destination node.
-%
-Constraint~\eqref{eq:fuse2} encodes that each edge should not
-be able to potentially fuse with any node other than its destination node.
-\begin{align}
-  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
-  \tag{V7}\label{eq:fuse1}  \\
-\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
-  \tag{V8}\label{eq:fuse2}  
-\end{align}
-
-% Fusion rules consist of two different mechanisms.
-% \begin{enumerate}
-% \item  A \textbf{pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-% \item \textbf{regulatory mechanisms} on the edges and nodes (possibly distinct) which regulates molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
-% \end{enumerate}
-% Boolean constraint~\eqref{eq:fuse1} and~\eqref{eq:fuse2} are used to encode well-fused
-% property.
-
-% F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active and have a non-zero entry in the pairing matrix.
-
-% F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.
-
-\subsubsection{Regulation on nodes and edges}
-We are considering several models that differ in constraints on
-the activity of molecules.
-%
-We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
-the varying constraints.
-%
-The following constraint encodes no conditions on activities on nodes,
-i.e., all the present molecules on the nodes are active.
-\begin{align}
-\bigwedge\limits_{i,m} n_{i,m} = a_{i,m}    \tag{Ann}\label{eq:ann}
-\end{align}
-The following constraint encodes that activity of a molecule $m$ on the node is
-defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
-\begin{align}
-\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
-\tag{Anb}\label{eq:anb}
-\end{align}
-The following constraint encodes no conditions on activities on edges,
-i.e., all the present molecules on the edges are active.
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
-\tag{Aen}\label{eq:aen}
-\end{align}
-The following constraint encodes that activity of a molecule $m$ on the edge is
-defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
-\begin{align}
-   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
-  \tag{Aeb}\label{eq:aeb}
-\end{align}
-%
-The following constraint encodes that the activity of the molecules on
-edges is defined by inhibition by other molecules based on the pairing
-matrix. 
-\begin{align}
-   \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \limplies  \bigwedge_{m' \neq m} (p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv (\neg b_{i,j,q,m} \land\;\;\;\;  \bigwedge_{\mathclap{m' \neq m, p_{m,m'}}} \neg b_{i,j,q,m'})
-  \tag{Aep}\label{eq:aep}
-\end{align}
-%
-\subsubsection{Constraints for stability condition}
-%
-We use $m$-reachability to encode the stability condition in VTSs.
-%
-The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
-if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
-$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
-%
-\begin{align}
-  \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-  \tag{R1}\label{eq:reach1}
-\end{align}
-Now we can encode stability using the reachability variables.
-and say if there is an $m$-edge between $i$ and $j$, there is
-$m$-reachable path from $j$ to $i$.
-\begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-  \tag{R2}\label{eq:reach2}
-\end{align}
-
-% Boolean variable
-% F3 and F2 are used to model these constraints.
-
-% % \textbf {Reachability definition and stability condition.}
-% We have encoded stable condition by using reachability definition. \newline
-
-% F3: Stability condition. For every leaving molecule, the source node is reachable from the target node with that molecule present, in maximum p steps.
-
-% F2: Reachability definition.
-Node j is reachable from node i with kth molecule present in maximum p steps if either there is a direct edge between i-j with that molecule present or there is a direct edge between $i^{\prime \prime}$ $(i \neq i^{\prime \prime})$ and j with kth molecule present on that edge and $i^{\prime \prime}$ are reachable from i in p steps.
-
-\subsubsection{$k$-connectivity constraints}
-To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
-disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
-%
-Constraints~\ref{eq:drop1}-\ref{eq:drop4}
-encode the relevant constraints for reachability
-in the modified VTS. 
-%
-The following constraints encode that only
-existing edges can be dropped and exactly $k-1$ edges are dropped.
-\begin{align}
-  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \tag{D1}\label{eq:drop1}\\
-  \sum_{i,j,q} d_{i,j,q} = k-1
-  \tag{D2}\label{eq:drop2}
-\end{align}
-We need to define reachability in the modified VTS, therefore we use
-a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
-In the following constraint, we encode $r'_{i,j}$ is true if there is an
-edge $(i,\_,j)$ and it is not dropped, or there is a node
-$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
-not dropped and $r'_{i',j}$ is true.
-\begin{align}
-\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}
-  \tag{D3}\label{eq:drop3}
-\end{align}
-Since we search for disconnected modified VTS,
-the following constraint encodes that there are 
-unreachable pair of nodes in the underlying undirected graph.
-% nodes such that
-% there is no path between them .
-\begin{align}
-   \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
-  \tag{D4}\label{eq:drop4}
-\end{align}
-
-The key improvement in our work over the earlier tool is the
-encoding of reachability, which was done using enumeration of paths.
-%
-In the current work, we have encoded reachability in two different
-ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
-%
-The reachability is recursively defined in~\eqref{eq:drop3} and has
-trivial solutions by making all $r'$s true.
-%
-However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
-only the solutions that captures the evidence of unreachability.
-%
-On the other hand,
-we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
-which needs relatively more auxiliary variables.
-%
-This is because constraint~\eqref{eq:reach2} has only positive
-occurrences of the reachability variables and if we had defined
-$r$s in ~\eqref{eq:reach1} without paths,
-the circular dependencies in the recursive definitions of $r$s
-may have resulted in spurious satisfying assignments that
-do not encode reachability.
-%
-By adding the path length, we break the circular dependencies, the
-constraint remains polynomial in size, and satisfying assignments only
-correspond to correct reachability.
-
-% We can go down or up using -C \_ option.  \newline
-
-\subsection{SAT problems for different variants}
-%\ankit{Bring model variant table here}
-
-We have encoded the following variants of VTSs.
-%
-The variants are due to different combinations of constraints on the
-activity of molecules on the nodes and edges.
-%
-\begin{enumerate}[label=\Alph*]
-\item Every present molecule is considered to be active.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
-\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
-\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
-\item Activity of molecules on the edges is driven by pairing inhibition.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
-\end{enumerate}
-%
-% For the version A, every present molecule is in active state.
-%
-In the table~\ref{tab:grph}, we present the constraints involved in each version.
-%
-The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
-for every variant.
-%
-The column three of the table lists the constraints that are different among the variants.
-%
-%
-One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
-%
-For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
-%
-Similarly for the case of the edge in version C and D; Aeb.
-%
-In the case of versions F the activity of the molecules on the edges
-is described by pairing matrix; Aep.
-
-%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
-%
-The constraints for the variants can be given to a SMT solver to find
-VTSs that belong to the variants.
-
-% We have applied the tool for the above variations for searching the
-% VTSs that satisfies their corresponding properties. 
-%
-% After creating the constraint using different Boolean variables 
-% we ship them directly to the solver.
-% %
-% In case of a satisfying (SAT) assignment of the added constraints the
-% Z3 theorem prover gives a model with the variable assignment.
-% %
-% In case no possible satisfying assignment the solver returns UNSAT.
-
-%
-%
-
-% \subsection{Creating a solver and solving these constraints}
-% We will create a solver and add these build constraint using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
-
-% \begin{figure}[ht]
-% %\vspace{-3mm}
-% \begin{verbatim}
-% # Create a solver
-% s = Solver()
-% # Add these constraints to it.
-% s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)
-
-% # Check for the satisfiability assignment.
-% print s.check()   
-% \end{verbatim}
-% \caption{Solving for these constraints.}
-% \label{code:motivate}
-% \end{figure}
-
-%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
-
 %%% Local Variables:

### 2018-04-19 papers/synth/encoding.tex
asd

In this section we will present a list of problems that may arise from
synthesis of VTSs from partial available information.

\subsection{Problem Statements}

Our objective is to find missing parts of a partially known VTSs.
%
We will consider several variations of the problem.
%
\begin{itemize}
\item Learning activity functions
\item Modifying labels of the nodes and edges
\item Adding missing edges
\item Adding
\end{itemize}

\subsection{QBF encodings}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-04-19 papers/synth/intro.tex
asd

--- 2018-04-19 papers/synth/intro.tex
@@
+Vesicle Traffic Systems(VTS) are the material transport mechanisms
+among the compartments inside the biological cells~\cite{vtsIntro}.
+%
+\ashu{Describe VTS in detail}
+%
 Vesicle Traffic Systems are the transport mechanisms inside the cells.
@@
 
-\ashu{Speculative}
-Subsequently, it can be potentially useful in guiding biologists
+\ashu{Make a case for incomplete knowledge of VTSs.}
+%Now we will work on
+Since VTSs are partially known, 
+%
+the labels may not have been fully observed.
+
+\ashu{Make a case for expected properties!!}
+Furthermore, it is a matter of debate what properties the VTSs should
+have, such as stability, i.e., every chemical that is leaving a
+compartment comes back.
+
+\ashu{Speculative: Make a case for completing partial parts of VTSs!!}
+
+We model a VTS as a labelled graph.
+%
+Each compartment of VTS is a node of the graph and and the
+transport channels between the nodes is an edge.
+%
+The set of chemicals present in a compartment is the label of of
+the compartment.
+%
+Similarly, the set of transported chemicals carried by an edge is the label
+on the edge.
+%
+%
+
+There are several constraints that limits
+
+There are several constraints that encode the interaction.
+
+The labels on the nodes
 

### 2018-04-20 papers/synth/intro.tex
asd

@@
 %
-The set of chemicals present in a compartment is the label of of
+The set of molecules present in a compartment is the label of
 the compartment.
 % 
-Similarly, the set of transported chemicals carried by an edge is the label
+Similarly, the set of transported molecules carried by an edge is the label
 on the edge.
 %
+A molecule in a node or edge may be active or inactive. 
 %
+The constraints discussed on the VTSs that allow a VTS to be feasible
+are combinatorial in nature, for example stability or 3-connectedness.
+%
+The problem of synthesizing parts of a VTS that are unobserved such that 
+the modified VTS
+
+It is appropriate that we translate 
+We turn the problem of synthesizing parts of 
+%
+We consider several versions of the synthesis problem involving different
+parts of VTSs that can be synthesized, such as modifying labels,
+adding/deleting edges, learning activity functions, and adding nodes.
+%
+In order to synthesize the parts of a VTS such that it satisfies the constraints, 
+we encode the synthesis problem into a satisfiability of QBF with uninterpreted
+Boolean functions.
+
+Since an available,
+
+on the labels.
 

### 2018-04-20 papers/synth/encoding.tex
vector &

@@
 
+%Types of questions we are trying to solve.
+
+The missing information can be in any of these combinations parts of VTS.
+For example existence of some undiscovered edges or nodes, or insufficient knowledge about the presence of molecules in some part of the VTS (either on the node or on the edge).
+To cover most of the likely variations of this missing information we have encoded the following variants of VTS synthesis.
+%
+%
+\begin{enumerate}[label=\Alph*]
+\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
+\item  Modify the flow of molecules on the nodes and on the edges.
+  \begin{enumerate}
+  	\item use available set of molecules.
+    \item allow new molecule type to be added.     
+  \end{enumerate}        
+\item Learning meaningful activity function. 
+  \begin{enumerate}
+    \item kcnf: low depth circuit.
+    \item Boolean gates: And, Or.
+    \item Boolean gates with linear combination.  
+  % - Function dependence with var occurring once.
+\item  VTS repair. [Allow both delete and add to the system]
+\end{enumerate}
+
+\subsection{Encoding edge addition}
+One of the source of incomplete information in the given VTS system is knowledge of all the edges it contain.
+If this information is missing our tool will suggest a few modification to the given VTS by adding additional edges to fill the missing information that is compatible with the rules of the VTS.
+
+\begin{align}
+  \exists n_{i_k} \, a_{i_k} \, e_{i_j_q_k} \, b_{i_j_q_k} \, p_{k_k^{\dash}} \,  r_{i_j} \, 
+               ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
+  \tag{E1}\label{eq:addedge1}
+\end{align}
+
+The basic_vts_constraints and vts_activity_constraint are same as the previous sections, describing stability of the graph and fusion of the edge into the node and the molecular activity describing the active state of a molecule.
+The given_vts_information is encoded using a front end input language.
+The user provides the information of the VTS with a partial information using this front end.
+Our tool then converts these inputs into the constraints over the given VTS.
+
+We encode the restriction_on_modification by putting the constraints on the unassigned edges and edge labels.
+The constraint of allowing only certain number of addition to the given VTS is encoded as at_most_k() function over the unassigned edges and label.
+
+\begin{align}
+    constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )
+
+    constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
+    constraints of the molecule presence on the edge = at\_most\_k ( unassigned molecule labels in VTS edges )\label{eq:addedge2}
+\end{align}
+
+Put \ref{eq:addedge2} in symbolic form and explain it in a couple of lines.
+
+In order to decrease the search space we do not allow any modification in the node label and activity on the nodes. This constraint can be encoded as the fixing all the unassigned bits to false.
+
+%    // Fix rest of them to zero.
+%    auto fixVar0 = ! z3::mk_or ( openN )  && ! z3::mk_or ( openActiveN );
+
+\begin{align}
+ \exists e_{i_j_q} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
+  \tag{E1}\label{eq:addedge2}
+\end{align}
+
+The connectivity_constraint && self_edge_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
+addedge1 is the constraint of \ref{eq:addedge1}.
+
+%{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+
+    auto addConstraints = edgeC && edgeActivityC && edgePresenceC  && fixVar0;
+
+    auto qvtsCons = exists( setN, 
+                    exists( setActiveN, 
+                    exists( setPresenceE,  
+                    exists( setActiveE, 
+                    exists( setPairingM, 
+                    exists( setReach, 
+                            vtsCons && vtsActivity && inputCons && addConstraints ))))));
+
+\subsection{Encoding molecules presence}
+
+\subsection{Encoding low depth cnf circuits}
+
+\subsection{Encoding boolean gates}
+
+\subsection{Encoding vts repair}
+The repair of the VTS requires both the addition and the deletion of the present molecules, node molecules pairing matrix and activity of the molecules.
+We have encoded the vts repair in our tool using the dummy xor bits.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:
+
 \subsection{QBF encodings}

### 2018-04-20 vts-synth/src/gates-encoding.cpp

@@ -48,7 +48,7 @@ z3::expr create_ast () {
 */
 
 // The expression can take any gates. gth gate.
-z3::expr vts::gates( Vec3Expr u, z3::expr x, z3::expr y, unsigned k, unsigned g ) {
+z3::expr vts::gates( Vec3Expr& u, z3::expr x, z3::expr y, unsigned k, unsigned g ) {
 
   z3::expr_vector g_list(ctx);
   z3::expr_vector c_list (ctx);
@@ -111,7 +111,7 @@ z3::expr vts::var_fml (VecExpr& chooseVar, unsigned i, unsigned k, bool e, unsig
   return cons;
 }
 
-z3::expr_vector vts::reduce_fml ( z3::context& ctx, z3::expr_vector& main_list, unsigned mLen, Vec3Expr u, unsigned k, unsigned& gateVar ) {
+z3::expr_vector vts::reduce_fml ( z3::context& ctx, z3::expr_vector& main_list, unsigned mLen, Vec3Expr& u, unsigned k, unsigned& gateVar ) {
   
   z3::expr_vector cons_list ( ctx ); 
   z3::expr fml( ctx );
@@ -177,15 +177,6 @@ z3::expr vts::build_rhs_fml ( Vec3Expr& chooseVars, Vec3Expr& chooseGates,
       step = 0;
       gateVar += 1;
       
-      /*
-      std::cout << "size is: " << n_list.size() << "\n";
-      std::cout << "gateVar: " << gateVar << "\n";
-      std::cout << "m: " << m << "\n";
-      std::cout << "M: " << M << "\n";
-      std::cout << "Steo: "<< step << "\n";
-      std::cout << "K: " << m1 << "\n";      
-      std::cout << "E: " << isEdge << "\n\n";
-      */
       n_list.resize ( 0 );
     }
       
@@ -219,7 +210,7 @@ z3::expr vts::build_rhs_fml ( Vec3Expr& chooseVars, Vec3Expr& chooseGates,
     */
 }
 
-z3::expr vts::node_gate_fml ( Vec3Expr s, Vec3Expr u ) {
+z3::expr vts::node_gate_fml ( Vec3Expr& s, Vec3Expr& u ) {
   z3::expr_vector n_list(ctx);
   
   for( unsigned i = 0; i < N; i++ ) {
[…]

### 2018-04-20 vts-synth/src/main.cpp

@@ -133,8 +133,9 @@ int main(int ac, char* av[])
 
   z3::context c;
 
-  // load_vts ld(c,"/home/agupta/tmp/t.vts"); ld.load();
- // vts_ptr v1 = ld.get_vts(); return 0;
+   //if ( ) {
+   load_vts ld(c,"/tmp/t.vts"); ld.load();
+   vts_ptr v1 = ld.get_vts(); return 0;
 
   // vts: v [context, Molecule, Nodes, Edge_arity, Version, Connectivity, Cnf_depth ]
   unsigned int N = 3;
@@ -227,7 +228,7 @@ int main(int ac, char* av[])
     //bool timedout = false;
     std::future<int> future = std::async(std::launch::async, [](){ 
         // if ( flagA == false ) {
-        auto retVal  = system ("cd ./build/depqbf/examples;timeout 260s ../depqbf --qdo --no-dynamic-nenofex  /tmp/myfile.qdimacs > /tmp/out.txt");
+        auto retVal  = system ("cd ./build/depqbf/examples;timeout 2s ../depqbf --qdo --no-dynamic-nenofex  /tmp/myfile.qdimacs > /tmp/out.txt");
         // std::cout << retVal << "\n";
         //  } else {
         // auto retVal = system("cd ./build/depqbf/examples; gcc -o depqbf-file depqbf-file.c -L.. -lqdpll; ./depqbf-file" );
@@ -239,7 +240,7 @@ int main(int ac, char* av[])
     //std::cout << "Running depqbf ... " << "\n";
     std::future_status status;
 
-    status = future.wait_for( std::chrono::seconds(260) );
+    status = future.wait_for( std::chrono::seconds(2) );
 
     if ( status == std::future_status::timeout ) { 
       std::cout << "TimeOut! \n";
@@ -252,6 +253,7 @@ int main(int ac, char* av[])
       std::cout << "Program run was sucessful! ";
     }
 
+    
     v.print_graph( c, "/tmp/dep_vts.dot", qs, printModel, displayGraph, synthVar ); 
     if ( displayGraph == true ) { 
       auto retVal = system("xdot /tmp/dep_vts.dot");

### 2018-04-20 vts-synth/src/synth-func.cpp

@@ -291,6 +291,7 @@ void vts::create_map ( z3::context& c, std::map<std::string,int>& denotation_map
         int lit = toDigit ( line.at(6) ); 
         if ( lit == 0 ) {
           depqbfRun = "Formula is UNSAT";
+          exit(0);
           break;
         }else {
           depqbfRun = "Formula is SAT";

### 2018-04-20 vts-synth/src/vts.cpp

@@ -19,10 +19,15 @@
 
 void vts::add_known_edge( unsigned n1, unsigned n2,
                           std::vector<unsigned>& mols, std::vector<bool>& act) {
-
+  
 }
 void vts::add_known_node( unsigned n,
                           std::vector<unsigned>& mols, std::vector<bool>& act) {
+
+  //for ( unsigned i = 0; i < mols.size(); i++ ) {
+  //  nodes[n][mols[i]]
+  //} 
+    
 }
 
 void vts::add_known_pairing( unsigned m1, unsigned m2 ) {

### 2018-04-20 vts-synth/src/vts.h

@@ -165,21 +165,19 @@ public:
   z3::expr edge_cnf ( Vec3Expr& t );
 
   /** Gates constraint **/
-  z3::expr gates( Vec3Expr u, z3::expr x, z3::expr y, unsigned k, unsigned g );
+  z3::expr gates( Vec3Expr& u, z3::expr x, z3::expr y, unsigned k, unsigned g );
   z3::expr build_rhs_fml ( Vec3Expr& s, Vec3Expr& u, unsigned i, unsigned k, bool e, unsigned j, unsigned q );
   //z3::expr var_fml (Vec3Expr s, unsigned i, unsigned k, unsigned g, bool e, unsigned j, unsigned q );
   z3::expr var_fml (VecExpr& s, unsigned i,  unsigned k, bool e, unsigned j, unsigned q );
 
-  z3::expr node_gate_fml ( Vec3Expr s, Vec3Expr u );
-  z3::expr edge_gate_fml ( Vec3Expr t, Vec3Expr v );
-  z3::expr logic_gates ( Vec3Expr s_var, Vec3Expr t_var, Vec3Expr u_var, Vec3Expr v_var );
-  z3::expr_vector reduce_fml ( z3::context& ctx, z3::expr_vector& main_list,  unsigned mLen, Vec3Expr u, unsigned k, unsigned& gateVar );
+  z3::expr node_gate_fml ( Vec3Expr& s, Vec3Expr& u );
+  z3::expr edge_gate_fml ( Vec3Expr& t, Vec3Expr& v );
+  z3::expr logic_gates ( Vec3Expr& s_var, Vec3Expr& t_var, Vec3Expr& u_var, Vec3Expr& v_var );
+  z3::expr_vector reduce_fml ( z3::context& ctx, z3::expr_vector& main_list,  unsigned mLen, Vec3Expr& u, unsigned k, unsigned& gateVar );
+  
   /** Synthesis constraints**/
   z3::expr vts_synthesis ( unsigned variation );
   z3::expr annotate_plos_graph();
- // z3::expr annotate_mukund_graph();
-
-  /* */
   z3::expr annotate_mukund_graph ( z3::expr_vector& fixN, z3::expr_vector& fixactiveN, z3::expr_vector& fixE, z3::expr_vector& fixpresenceE, z3::expr_vector& fixactiveE, z3::expr_vector& fixpairingP );
 
   // Synthesis helper

### 2018-04-21 vts-synth/src/vts-synthesis.cpp
fixing start

@@ -290,11 +290,11 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   z3::expr_vector listReach = reach_list();
   
   
-  unassigned_bits ( listN, v->knownNodes, unknownN ); 
-  unassigned_bits ( listActiveN, v->knownActiveNodes, unknownActiveN ); 
-  unassigned_bits ( listE, v->knownEdges, unknownE ); 
-  unassigned_bits ( listPresenceE, v->knownPresenceEdges, unknownPresenceE ); 
-  unassigned_bits ( listActiveE, v->knownActiveEdges, unknownActiveE  ); 
+  unassigned_bits ( listN, knownNodes, unknownN ); 
+  unassigned_bits ( listActiveN, knownActiveNodes, unknownActiveN ); 
+  unassigned_bits ( listE, knownEdges, unknownE ); 
+  unassigned_bits ( listPresenceE, knownPresenceEdges, unknownPresenceE ); 
+  unassigned_bits ( listActiveE, knownActiveEdges, unknownActiveE  ); 
 
   // 1. Add edge to achieve graph stability and k connected. 
   if ( variation == 1 ) {

### 2018-04-21 vts-synth/src/vts.h

@@ -23,7 +23,11 @@ public:
   vts( z3::context& _ctx,
        unsigned _M, unsigned _N, unsigned _Q, model_version _V, unsigned _C, unsigned _D )
     : ctx(_ctx), M(_M), N(_N), E_arity(_Q),
-      V(_V), C(_C), D(_D)
+      V(_V), C(_C), D(_D), knownEdges(_ctx),
+      knownPresenceEdges( _ctx ),
+      knownActiveEdges( _ctx ),
+      knownNodes( _ctx ),
+      knownPairingMatrix( _ctx )
   {
     init_vts();
   }

### 2018-04-22 papers/synth/encoding.tex
parsing fixed

@@
     \item Boolean gates with linear combination.  
+    \end{enumerate}        
   % - Function dependence with var occurring once.
@@
 
-\subsection{Encoding edge addition}
-One of the source of incomplete information in the given VTS system is knowledge of all the edges it contain.
-If this information is missing our tool will suggest a few modification to the given VTS by adding additional edges to fill the missing information that is compatible with the rules of the VTS.
-
 \begin{align}
-  \exists n_{i_k} \, a_{i_k} \, e_{i_j_q_k} \, b_{i_j_q_k} \, p_{k_k^{\dash}} \,  r_{i_j} \, 
+  \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
                ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
@@
 
-The basic_vts_constraints and vts_activity_constraint are same as the previous sections, describing stability of the graph and fusion of the edge into the node and the molecular activity describing the active state of a molecule.
-The given_vts_information is encoded using a front end input language.
+The basicvtsconstraints and vtsactivityconstraint are same as the previous sections, describing stability of the graph and fusion of the edge into the node and the molecular activity describing the active state of a molecule.
+The givenvtsinformation is encoded using a front end input language.
 The user provides the information of the VTS with a partial information using this front end.
@@
 
-We encode the restriction_on_modification by putting the constraints on the unassigned edges and edge labels.
-The constraint of allowing only certain number of addition to the given VTS is encoded as at_most_k() function over the unassigned edges and label.
+We encode the restriction\_on\_modification by putting the constraints on the unassigned edges and edge labels.
+The constraint of allowing only certain number of addition to the given VTS is encoded as at\_most\_k() function over the unassigned edges and label.
 
@@
     constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )    
-
     constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
@@
 \begin{align}
- \exists e_{i_j_q} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
+ \exists e_{ijq} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
   \tag{E1}\label{eq:addedge2}
@@
 
-The connectivity_constraint && self_edge_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
+The connectivity\_constraint \&\& self\_edge\_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
 addedge1 is the constraint of \ref{eq:addedge1}.
@@
 
-    auto addConstraints = edgeC && edgeActivityC && edgePresenceC  && fixVar0;
+    auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;
 
@@
                     exists( setReach, 
-                            vtsCons && vtsActivity && inputCons && addConstraints ))))));
+                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));
 
@@
 
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "main"
-%%% End:
-
 \subsection{QBF encodings}

### 2018-04-22 papers/synth/intro.tex
fixing start
parsing fixed

@@
-Vesicle Traffic Systems(VTS) are the material transport mechanisms
-among the compartments inside the biological cells~\cite{vtsIntro}.
+%Motivate VTS
+Eukaryotic cells, including human cells, consists of multiple compartments.
 %
-\ashu{Describe VTS in detail}
+Vesicle Traffic Systems(VTSs) are the material transport mechanisms
+among the compartments inside the eukaryotic cells~\cite{vtsIntro}.
 %
-Vesicle Traffic Systems are the transport mechanisms inside the cells.
+Almost all subsystems of eukaryotic cells depend on VTSs.
+%
+Therefore, understanding how VTSs functions is one of the key
+questions of cell biology.
+%
+In this paper, we are looking at the computational questions 
+arise from the VTSs.
+%
+In the following, we use the model of VTSs that has been presented
+in~\cite{VTS}.
+%
+Please look at appendix~\ref{sec:model}
+for the detailed discussion on pros and cons of the model.
+
+% Describe VTS in detail
+While molecules are transported by VTSs, VTSs are also
+regulated by the molecules.
+%
+Each compartment contains a set of molecules.
+%
+The molecules are transported to the other compartments via
+unidirectional channels.  
+%
+The molecules in a compartment may be active or not active.
+%
+Similarly, a molecule can be active along in a channel. 
+%
+The active molecules are the regulators of the channels.
+%
+A channel is enabled by a pair of molecules
+such that one occurs in the channel and the other
+occurs in the destination compartment.
+%
+Both the molecules must be active in the channel
+and compartment respectively.
+%
+The pairs are called {\em fusing} molecules and analogously
+the channel is considered to be {\em fused} with the
+compartment.
+%
+Not all the pairs of molecules can participate in the fusion, it is
+usually determined by wet experiments the potential fusion pairs.
+%
+To ensure effective regulation, the fusing molecule pairs must be
+unique for each fused channel-compartment pair.
+%
+Since a molecule has to be active in order to participate in fusion,
+the molecule may be present in the other places without being active
+and does not interfere with regulation of the other fused
+channel-compartment pairs.
+%
+The activity of molecules is regulated by the other molecules, i.e.,
+the presence and absence of the other molecule in a compartment or
+channel may make the active or inactive.
+%
+We call this regulation {\em activity functions}.
+
+Although the VTSs are very important, our understanding
+
+In the VTS model, we assume that the system is in study state and
+the concentration of molecules does not change over time.
+%
+Therefore, there is no aspect of
+
+%
+They are known
+
+Some of the molecules that are pre
+%
 %

### 2018-04-22 papers/synth/model.tex
parsing fixed

--- 2018-04-19 papers/synth/encoding.tex
@@
-In this section we will present a list of problems that may arise from
-synthesis of VTSs from partial available information.
-
-\subsection{Problem Statements}
-
-Our objective is to find missing parts of a partially known VTSs.
-%
-We will consider several variations of the problem.
-%
-\begin{itemize}
-\item Learning activity functions
-\item Modifying labels of the nodes and edges
-\item Adding missing edges
-\item Adding
-\end{itemize}
-
-\subsection{QBF encodings}
+\ashu{Discuss the model in Biological terms.}
 

### 2018-04-22 vts-synth/src/load-vts.cpp

@@ -21,6 +21,13 @@ char load_vts::peek_skip_space() {
   return in.peek();
 }
 
+bool load_vts::peek_num_or_eol() {
+  char ch = in.peek();
+  if( ch == '\n') return true;
+  if( ch >= '0' && ch <= '9' ) return true;
+  return false;
+}
+
 unsigned load_vts::read_num_line() {
   std::string line;
   std::getline ( in, line);
@@ -83,8 +90,10 @@ void load_vts::get_model_version() {
   }
 }
 
+// activity may conatain dummy expressions
 void load_vts::get_label( std::vector<unsigned>& mols,
                           std::vector<bool>& activity) {
+  z3::expr dummy(c);
   char ch;
   in >> ch;
   if( ch != '|' ) load_error( "no | at start of label!", line_num );
@@ -92,13 +101,17 @@ void load_vts::get_label( std::vector<unsigned>& mols,
     unsigned m_idx;
     in >> m_idx;
     mols.push_back( m_idx );
-    if( peek_skip_space() == '\n') goto ERROR;
-    char act;
-    in >> act;
-    switch( act ) {
-    case '+': activity.push_back(true); break;
-    case '-': activity.push_back(false); break;
-    default: goto ERROR;
+    // if( peek_skip_space() == '\n') goto ERROR;
+    if( peek_num_or_eol() ) {
+      char act;
+      in >> act;
+      switch( act ) {
+      case '+': activity.push_back(true); break;
+      case '-': activity.push_back(false); break;
+      default: goto ERROR;
+      }
+    }else{
+      activity.push_back( dummy );
     }
   }
   return;

### 2018-04-22 vts-synth/src/load-vts.h

@@ -27,6 +27,7 @@ private:
   std::vector< std::string > mol_vars;
 
   char peek_skip_space();
+  bool peek_num_or_eol();
   unsigned read_num_line();
   char read_char_line();
   std::string read_string_line();

### 2018-04-22 vts-synth/src/main.cpp

@@ -155,7 +155,7 @@ int main(int ac, char* av[])
     } else{
     //v = std::shared_ptr<vts>(new vts(c, M, N, Q, MODEL_4, 3, D ));
        std::cout << "Using default file [t.vts] in current folder... \n";
-       load_vts ld(c, "./t.vts" ); ld.load();
+       load_vts ld(c, "./examples/t.vts" ); ld.load();
        v = ld.get_vts(); return 0;
     }
   } else{

### 2018-04-22 vts-synth/src/main.cpp
working-Unsat-example2

@@ -55,13 +55,13 @@ int main(int ac, char* av[])
     options_description variation("Variation options");
     variation.add_options()
       ("func-type", value<int>(), "fix a function type for QBF")
-      ("synth-var", value<int>(), "fix a synthesis variation for vts")
+      ("synth-var,s", value<int>(), "fix a synthesis variation for vts")
       ;
     
     options_description options("Available options");
     options.add_options()
       ("use-z3", "use z3 for QBF solving")
-      ("print-model", "print vts model")
+      ("print-model,p", "print vts model")
       ("display-graph", "display the vts as graph")
       ("input-file,i", value< std::vector<std::string> >(),
      "Specifies input file.");

### 2018-04-22 vts-synth/src/qbf.cpp

@@ -91,6 +91,7 @@ z3::expr vts::create_qbf_formula ( int funcType ) {
 
   }
   else if ( funcType == 2 ) {
+    unsigned noOfGates = 3;
     
     // Populate xtra var node_parameter_var : var for node function
     popl3 ( node_parameter_var, M, M, (2 * M) + 2, "s" );
@@ -99,24 +100,24 @@ z3::expr vts::create_qbf_formula ( int funcType ) {
     popl3 ( edge_parameter_var, M, M, (2 * M) + 2, "t" );
     
     // Populate parameter var
-    popl3 ( u_var, M, M-1, 2, "u" );
+    popl3 ( gate_selector_var_node, M, noOfGates, 2, "u" );
     
     // Populate parameter var
-    popl3 ( v_var, M, M-1, 2, "v" );
+    popl3 ( gate_selector_var_edge, M, noOfGates, 2, "v" );
     
     // [3]: Boolean gates  function 
     /*
      * auto listSvar = flattern3d ( node_parameter_var, M, M - 1, 2*M + 2, false );
     auto listTvar = flattern3d ( edge_parameter_var, M, M - 1, 2*M + 2, false );
-    auto listUvar = flattern2d ( u_var, M, M, false );
-    auto listVvar = flattern2d ( v_var, M, M, false );
+    auto listUvar = flattern2d ( gate_selector_var_node, M, M, false );
+    auto listVvar = flattern2d ( gate_selector_var_edge, M, M, false );
      */
     auto listSvar = flattern3d ( node_parameter_var, M, M, 2*M + 2, false );
     auto listTvar = flattern3d ( edge_parameter_var, M, M, 2*M + 2, false );
-    auto listUvar = flattern3d ( u_var, M, M-1, 2, false );
-    auto listVvar = flattern3d ( v_var, M, M-1, 2, false );
+    auto listUvar = flattern3d ( gate_selector_var_node, M, noOfGates, 2, false );
+    auto listVvar = flattern3d ( gate_selector_var_edge, M, noOfGates, 2, false );
   
-    z3::expr gateCons = logic_gates ( node_parameter_var, edge_parameter_var, u_var, v_var );
+    z3::expr gateCons = logic_gates ( node_parameter_var, edge_parameter_var, gate_selector_var_node, gate_selector_var_edge );
     
     z3::expr funcGate  = forall( listN, 
                          forall( listActiveN, 

### 2018-04-22 vts-synth/src/vts-synthesis.cpp

@@ -255,8 +255,9 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   z3::expr_vector unknownActiveE( ctx );
   
   /** Annotate graph : fix graph known variables **/
-  z3::expr inputCons =  annotate_mukund_graph ( knownNodes, knownActiveNodes, knownEdges, 
-                        knownPresenceEdges, knownActiveEdges, knownPairingMatrix );
+  //z3::expr inputCons =  annotate_mukund_graph ( knownNodes, knownActiveNodes, knownEdges, knownPresenceEdges, knownActiveEdges, knownPairingMatrix );
+
+  z3::expr inputCons (ctx);
 
   z3::expr kConnCons = k_connected_graph_constraint( 3, false ); 
   z3::expr V5 = no_self_edges();
@@ -370,15 +371,16 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   }
   else if ( variation == 4 ) {
     unsigned gateTypes = 2;
+    unsigned noOfgates = 3;
     //Populate xtra var node_parameter_var : var for node function 
     // [Molecules, Total M molecule to pick, Picking options: All molecules + True + False ]
     popl3 ( node_parameter_var, M, M, (2 * M) + 2, "s" );
     // Populate xtra var edge_parameter_var : var for edge function 
     popl3 ( edge_parameter_var, M, M, (2 * M) + 2, "t" );
     // Populate parameter var [ Molecules , No.Of gate to pick ]
-    popl3 ( u_var, M, M-1, gateTypes, "u" );
+    popl3 ( gate_selector_var_node, M, noOfgates, gateTypes, "u" );
     // Populate parameter var
-    popl3 ( v_var, M, M-1, gateTypes, "v" );
+    popl3 ( gate_selector_var_edge, M, noOfgates, gateTypes, "v" );
     
     auto setUnknownVariablesFalse =  !z3::mk_or( unknownN )  
                  && !z3::mk_or( unknownActiveN ) 
@@ -390,10 +392,10 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
 
     auto listSvar = flattern3d ( node_parameter_var, M, M, 2*M + 2, false );
     auto listTvar = flattern3d ( edge_parameter_var, M, M, 2*M + 2, false );
-    auto listUvar = flattern3d ( u_var, M, M-1, gateTypes, false );
-    auto listVvar = flattern3d ( v_var, M, M-1, gateTypes, false ); 
[…]

### 2018-04-22 vts-synth/src/vts.cpp

@@ -47,6 +47,7 @@ void vts::add_known_edge( unsigned n1, unsigned n2, unsigned q,
   }
   std::sort(begin(knownPresenceEdgesTuple), end(knownPresenceEdgesTuple), TupleCompare<0>());
   std::sort(begin(knownEdgesTuple), end(knownEdgesTuple), TupleCompare<0>());
+    std::cout << "\nMama mia ..\n";
 
   for ( auto i& : knownPresenceEdgesTuple ) {
   }

### 2018-04-22 vts-synth/src/vts.h

@@ -52,8 +52,8 @@ private:
 
   Vec3Expr node_parameter_var;
   Vec3Expr edge_parameter_var;
-  Vec3Expr u_var;
-  Vec3Expr v_var;
+  Vec3Expr gate_selector_var_node;
+  Vec3Expr gate_selector_var_edge;
 
   Vec3Expr edges;
   Vec4Expr presence_edge;
@@ -186,7 +186,7 @@ public:
 
   z3::expr node_gate_fml ( Vec3Expr& s, Vec3Expr& u );
   z3::expr edge_gate_fml ( Vec3Expr& t, Vec3Expr& v );
-  z3::expr logic_gates ( Vec3Expr& s_var, Vec3Expr& t_var, Vec3Expr& u_var, Vec3Expr& v_var );
+  z3::expr logic_gates ( Vec3Expr& s_var, Vec3Expr& t_var, Vec3Expr& gate_selector_var_node, Vec3Expr& gate_selector_var_edge );
   z3::expr_vector reduce_fml ( z3::context& ctx, z3::expr_vector& main_list,  unsigned mLen, Vec3Expr& u, unsigned k, unsigned& gateVar );
   
   /** Synthesis constraints**/

### 2018-04-22 papers/synth/intro.tex
intro

@@
 %
-We call this regulation {\em activity functions}.
+We call this regulation as {\em activity functions}.
 
-Although the VTSs are very important, our understanding
+% Defending our model
+%
+In the VTS model, we assume that the system is in study state and
+the concentrations of the molecules do not change over time.
+%
+Therefore, the system only has aspects of a network or a graph.
+%
+We model the system as a labelled graph, where compartments are nodes and
+transport channels are edges.
+%
+The set of molecules present and their activity in a compartment or
+a channel is the label of the respective node or edge.
+%
+The regulation controls are defined by a fusion pairing matrix
+containing Boolean values for each pair of molecules and activity
+Boolean functions.
+%
+Since the system is in study state, we expect that any molecule that
+leaves a compartment must come back via some path on the graph.
+%
+We call this property of VTS as {\em stability}.
 
-In the VTS model, we assume that the system is in study state and
-the concentration of molecules does not change over time.
+% Partial info defence
 %
-Therefore, there is no aspect of
+Although the VTSs are important, our understanding of VTSs are partial.
+%
+It largely means patch work of wet experiments~\cite{model} for
+identifying the compartments, channels, molecules, their activity, and
+regulatory control.
+%
+Often the information is scattered around in several publications.
+%
+Even after with some effort we may collate all the known information about
+a VTS, we may still have unknown pieces of the system.
+%
+The search for the unknown pieces may be {\em assisted} by computation on
+the graph model of VTSs.
+%
+For example, we suspect that some edges are missing from the graph, since
+we expect the must satisfy stability.
+%
+Due the combinatorial nature of graphs, the search space is huge and often
+hard to enumerate naively.
+%
+We need specialized methods to perform the search.
 
 %
-They are known
+We may translate the problem into a synthesis question, in which 
+we have a partial system  and a given property that
+the system needs to satisfy.
+%
+The synthesis method completes the system such that the property
+is satisfied by it.
+%
 
-Some of the molecules that are pre
-%
-%
-Different compartments are viewed as nodes and transport channels are
-nodes between the graphs.
-
-\ashu{Make a case for incomplete knowledge of VTSs.}
-%Now we will work on
-Since VTSs are partially known, 
-%
-the labels may not have been fully observed.
+In synthesis, we may have a partial
 
@@
 
-We model a VTS as a labelled graph.
-%
-Each compartment of VTS is a node of the graph and and the
-transport channels between the nodes is an edge.
-%
-The set of molecules present in a compartment is the label of
-the compartment.
-% 
-Similarly, the set of transported molecules carried by an edge is the label
-on the edge.
-%
-A molecule in a node or edge may be active or inactive. 
-%
 The constraints discussed on the VTSs that allow a VTS to be feasible
@@
 %
-In order to synthesize the parts of a VTS such that it satisfies the constraints, 
-we encode the synthesis problem into a satisfiability of QBF with uninterpreted
-Boolean functions.
+In order to synthesize the parts of a VTS such that it satisfies the
+constraints, we encode the synthesis problem into a satisfiability of
+QBF with uninterpreted Boolean functions.
 

### 2018-04-23 papers/synth/intro.tex
asd

@@
 Vesicle Traffic Systems(VTSs) are the material transport mechanisms
-among the compartments inside the eukaryotic cells~\cite{vtsIntro}.
+among the compartments inside the cells~\cite{vtsIntro}.
 %
-Almost all subsystems of eukaryotic cells depend on VTSs.
+Almost all subsystems of the cells depend on VTSs.
 %
@@
 % Describe VTS in detail
-While molecules are transported by VTSs, VTSs are also
+While VTSs transports molecules, VTSs are also
 regulated by the molecules.
@@
 %
-Similarly, a molecule can be active along in a channel. 
+Similarly, a molecule can be active in a channel. 
 %
@@
 the channel is considered to be {\em fused} with the
-compartment.
+destination compartment.
 %
@@
 %
-Since a molecule has to be active in order to participate in fusion,
-the molecule may be present in the other places without being active
-and does not interfere with regulation of the other fused
-channel-compartment pairs.
+A molecule that have participated in a fusion must not interfere
+with fusion at different compartments or channels.
+%
+Therefore, the molecule must be inactive in appropriate compartments.
 %
@@
 In the VTS model, we assume that the system is in study state and
-the concentrations of the molecules do not change over time.
-%
-Therefore, the system only has aspects of a network or a graph.
+the concentrations of the molecules in the compartments do not change over time.
 %
@@
 %
-It largely means patch work of wet experiments~\cite{model} for
+It largely means the patch work of wet experiments~\cite{model} for
 identifying the compartments, channels, molecules, their activity, and
@@
 %
-The search for the unknown pieces may be {\em assisted} by computation on
+%{Speculative: Make a case for completing partial parts of VTSs!!}
+%
+For example, we may suspect that some edges are missing in a VTS that
+does not satisfy the stability condition.
+%
+The synthesis for the unknown pieces may be {\em assisted} by computation on
 the graph model of VTSs.
 %
-For example, we suspect that some edges are missing from the graph, since
-we expect the must satisfy stability.
+
+In this paper, we consider several versions of the synthesis problem
+involving different parts of VTSs that can be synthesized, such as
+modifying labels, adding/deleting edges, learning activity functions,
+and adding nodes.
 %
-Due the combinatorial nature of graphs, the search space is huge and often
-hard to enumerate naively.
-%
-We need specialized methods to perform the search.
-
-%
-We may translate the problem into a synthesis question, in which 
-we have a partial system  and a given property that
-the system needs to satisfy.
-%
-The synthesis method completes the system such that the property
-is satisfied by it.
-%
-
-In synthesis, we may have a partial
-
-\ashu{Make a case for expected properties!!}
-Furthermore, it is a matter of debate what properties the VTSs should
-have, such as stability, i.e., every chemical that is leaving a
-compartment comes back.
-
-\ashu{Speculative: Make a case for completing partial parts of VTSs!!}
-
-The constraints discussed on the VTSs that allow a VTS to be feasible
-are combinatorial in nature, for example stability or 3-connectedness.
-%
-The problem of synthesizing parts of a VTS that are unobserved such that 
-the modified VTS
-
-It is appropriate that we translate 
-We turn the problem of synthesizing parts of 
-%
-We consider several versions of the synthesis problem involving different
-parts of VTSs that can be synthesized, such as modifying labels,
-adding/deleting edges, learning activity functions, and adding nodes.
+We also consider variation on the properties against which we do synthesis,
+namely stability, and $k$-connectedness that states
+that VTS remains connected after removing any $k-1$ edges.
 %
@@
 constraints, we encode the synthesis problem into a satisfiability of
-QBF with uninterpreted Boolean functions.
+quantified Boolean formulas(QBFs). 
+%
 
-Since an available,
+We have implemented the encoding in a highly flexible tool,
+which can handle a wide range of synthesis query.
+%
+We have applied our tool on two found-in-nature VTSs, namely
+M1~\cite{} and S1~\cite{}.
+%
+We have also applied our tool on various synthetic examples to
+demonstrate that our tool scale upto the graph size ??, which
+is the size of typical VTSs in a eukaryotic cell.
 
-on the labels.
+The following are the contributions of this work:
+\begin{itemize}
+\item We have identified an interesting application of
+  the synthesis technology.
+\item We have developed encoding of the synthesis problem in QBF.
+\item A user friendly and scalable tool based on well known SMT solver Z3
+\end{itemize}
 
-There are several constraints that limits
-
-There are several constraints that encode the interaction.
-
-The labels on the nodes
+The rest of the paper is organized as follows.
+%
+In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
+constraints on VTSs.
+%
+In section~\ref{sec:prelim}, we present the synthesis problems and their
+encoding into QBF satisfiability.
+%
+In section~\ref{sec:experiments}, we present our implementation and experimental results.
+%
+We discuss related work in~\ref{sec:related} and conclude in section~\ref{sec:conclusion}.
 

### 2018-04-23 papers/synth/prelim.tex
asd

--- 2017-08-17 paper/encoding.tex
@@
 VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
+
 %
-In the definition, we do not care about the paths to be $m$-connected for some $m$.  
+% In the definition, we do not care about the paths to be $m$-connected for some $m$.  
+% %
+% A variant of the definition may be sensitive to the $m$-connectedness, but
+% we are not considering the variation.
+
+\subsection{Encoding VTS}
+
+The conditions on the VTSs for a given size can be encoded as a QBF formula
+with uninterpreted functions.
 %
-A variant of the definition may be sensitive to the $m$-connectedness, but
-we are not considering the variation.
-
-\paragraph{Search problem}
-Based upon earlier discussion, we need to answer the following search
-question among VTSs.
-For a given $k$, size $\nu$, and molecule number $\mu$,
-we are searching for well-structured, stable, and well-fused VTS
-$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and
-$G$ is not $k$-connected.
-
-\subsection{Boolean satisfiability of the search problem}
-
-We translate the search problem into a Boolean satisfiability
-problem and use SAT solvers to find the satisfying VTSs.
+To encode the constraints, we need needs variables for each aspect of
+VTS.
 %
-We will first present the variables used to encode the
-VTSs and the properties.
-%
-Afterwards, we will present the constraints corresponding to the
-properties.
-
-\subsubsection{Variables for VTS description}
-%
-We assume that size of the graph is $\nu$ and number of molecules is
-$\mu$.
+Let us suppose that the size of the graph is $\nu$ and number of
+molecules is $\mu$.
 %
@@
 %
-Here, we list the vector of Boolean variables and uninterpreted function symbols
+Here, we list the Boolean variables and uninterpreted function symbols
 that encode the VTSs.
@@
 \end{enumerate}
-We also have auxiliary Boolean variables that will help us encode the well-fused and stability properties 
-\begin{enumerate}
-\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
-  holds
-\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\item $r_{i,j,m,p}$ indicates if there is an $m$-path from
-  $i$ to $j$ of length less than or equal to $p$
-\end{enumerate}
-For $k$-connected property, we also use the following auxiliary Boolean variables
-\begin{enumerate}
-\item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped
-\item $r'_{i,j}$ indicates if there is a path from $i$ to $j$ in the modified VTS
-\end{enumerate}
 
-We will describe the Boolean constraints that encode VTSs in several categories.
+\subsection{Solvers}
+Due the combinatorial nature of the graphs, the search space is huge
+and often hard to enumerate naively.
 %
-In the end, we will present in a table the constraints needed for the
-model variants.
-%
-To avoid cumbersome notation, we will not explicitly write the ranges of the indexing
-in the constraints.
-%
-$i$ and $j$ will range over nodes.
-%
-$m$ will range over molecules.
-%
-$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
-%
-
-\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
-%
-We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
-to encode the basic structure of VTSs.
-%
-For an edge to exist it should have one molecule present. 
-%
-\begin{align}
-  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
-\end{align}
-If a molecule is active on an edge, it should be present on the edge.
-%
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
-\end{align}
-A molecule should be present to be active on a node.  
-\begin{align}
-  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
-  \tag{V3}\label{eq:c4}
-\end{align}
-The edge labels are subset of the node labels of the source and target nodes.
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
-\end{align}
-Self edges are not allowed. 
-\begin{align}
-   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
-\end{align}
-We fix first half as Q-SNAREs and rest as R-SNAREs and set diagonal blocks in pairing matrix to be 0's.
-%It reduces the search space.
-% Condition on $p_{kk'}$. \ashu{why???} .
-\begin{align}
-  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
-  \tag{V6}\label{eq:c3}
-\end{align}
-
-\subsubsection{Well-fused constraints}
-Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
-its destination node.
-%
-Constraint~\eqref{eq:fuse2} encodes that each edge should not
-be able to potentially fuse with any node other than its destination node.
-\begin{align}
-  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
-  \tag{V7}\label{eq:fuse1}  \\
-\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
-  \tag{V8}\label{eq:fuse2}  
-\end{align}
-
-% Fusion rules consist of two different mechanisms.
-% \begin{enumerate}
-% \item  A \textbf{pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
-% \item \textbf{regulatory mechanisms} on the edges and nodes (possibly distinct) which regulates molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
-% \end{enumerate}
-% Boolean constraint~\eqref{eq:fuse1} and~\eqref{eq:fuse2} are used to encode well-fused
-% property.
-
-% F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active and have a non-zero entry in the pairing matrix.
-
-% F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.
-
-\subsubsection{Regulation on nodes and edges}
-We are considering several models that differ in constraints on
-the activity of molecules.
-%
-We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
-the varying constraints.
-%
-The following constraint encodes no conditions on activities on nodes,
-i.e., all the present molecules on the nodes are active.
-\begin{align}
-\bigwedge\limits_{i,m} n_{i,m} = a_{i,m}    \tag{Ann}\label{eq:ann}
-\end{align}
-The following constraint encodes that activity of a molecule $m$ on the node is
-defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
-\begin{align}
-\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
-\tag{Anb}\label{eq:anb}
-\end{align}
-The following constraint encodes no conditions on activities on edges,
-i.e., all the present molecules on the edges are active.
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
-\tag{Aen}\label{eq:aen}
-\end{align}
-The following constraint encodes that activity of a molecule $m$ on the edge is
-defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
-\begin{align}
-   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
-  \tag{Aeb}\label{eq:aeb}
-\end{align}
-%
-The following constraint encodes that the activity of the molecules on
-edges is defined by inhibition by other molecules based on the pairing
-matrix. 
-\begin{align}
-   \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \limplies  \bigwedge_{m' \neq m} (p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv (\neg b_{i,j,q,m} \land\;\;\;\;  \bigwedge_{\mathclap{m' \neq m, p_{m,m'}}} \neg b_{i,j,q,m'})
-  \tag{Aep}\label{eq:aep}
-\end{align}
-%
-\subsubsection{Constraints for stability condition}
-%
-We use $m$-reachability to encode the stability condition in VTSs.
-%
-The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
-if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
-$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
-%
-\begin{align}
-  \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-  \tag{R1}\label{eq:reach1}
-\end{align}
-Now we can encode stability using the reachability variables.
-and say if there is an $m$-edge between $i$ and $j$, there is
-$m$-reachable path from $j$ to $i$.
-\begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-  \tag{R2}\label{eq:reach2}
-\end{align}
-
-% Boolean variable
-% F3 and F2 are used to model these constraints.
-
-% % \textbf {Reachability definition and stability condition.}
-% We have encoded stable condition by using reachability definition. \newline
-
-% F3: Stability condition. For every leaving molecule, the source node is reachable from the target node with that molecule present, in maximum p steps.
-
-% F2: Reachability definition.
-Node j is reachable from node i with kth molecule present in maximum p steps if either there is a direct edge between i-j with that molecule present or there is a direct edge between $i^{\prime \prime}$ $(i \neq i^{\prime \prime})$ and j with kth molecule present on that edge and $i^{\prime \prime}$ are reachable from i in p steps.
-
-\subsubsection{$k$-connectivity constraints}
-To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
-disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
-%
-Constraints~\ref{eq:drop1}-\ref{eq:drop4}
-encode the relevant constraints for reachability
-in the modified VTS. 
-%
-The following constraints encode that only
-existing edges can be dropped and exactly $k-1$ edges are dropped.
-\begin{align}
-  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \tag{D1}\label{eq:drop1}\\
-  \sum_{i,j,q} d_{i,j,q} = k-1
-  \tag{D2}\label{eq:drop2}
-\end{align}
-We need to define reachability in the modified VTS, therefore we use
-a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
-In the following constraint, we encode $r'_{i,j}$ is true if there is an
-edge $(i,\_,j)$ and it is not dropped, or there is a node
-$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
-not dropped and $r'_{i',j}$ is true.
-\begin{align}
-\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}
-  \tag{D3}\label{eq:drop3}
-\end{align}
-Since we search for disconnected modified VTS,
-the following constraint encodes that there are 
-unreachable pair of nodes in the underlying undirected graph.
-% nodes such that
-% there is no path between them .
-\begin{align}
-   \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
-  \tag{D4}\label{eq:drop4}
-\end{align}
-
-The key improvement in our work over the earlier tool is the
-encoding of reachability, which was done using enumeration of paths.
-%
-In the current work, we have encoded reachability in two different
-ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
-%
-The reachability is recursively defined in~\eqref{eq:drop3} and has
-trivial solutions by making all $r'$s true.
-%
-However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
-only the solutions that captures the evidence of unreachability.
-%
-On the other hand,
-we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
-which needs relatively more auxiliary variables.
-%
-This is because constraint~\eqref{eq:reach2} has only positive
-occurrences of the reachability variables and if we had defined
-$r$s in ~\eqref{eq:reach1} without paths,
-the circular dependencies in the recursive definitions of $r$s
-may have resulted in spurious satisfying assignments that
-do not encode reachability.
-%
-By adding the path length, we break the circular dependencies, the
-constraint remains polynomial in size, and satisfying assignments only
-correspond to correct reachability.
-
-% We can go down or up using -C \_ option.  \newline
-
-\subsection{SAT problems for different variants}
-%\ankit{Bring model variant table here}
-
-We have encoded the following variants of VTSs.
-%
-The variants are due to different combinations of constraints on the
-activity of molecules on the nodes and edges.
-%
-\begin{enumerate}[label=\Alph*]
-\item Every present molecule is considered to be active.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
-\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
-\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
-\item Activity of molecules on the edges is driven by pairing inhibition.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
-\end{enumerate}
-%
-% For the version A, every present molecule is in active state.
-%
-In the table~\ref{tab:grph}, we present the constraints involved in each version.
-%
-The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
-for every variant.
-%
-The column three of the table lists the constraints that are different among the variants.
-%
-%
-One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
-%
-For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
-%
-Similarly for the case of the edge in version C and D; Aeb.
-%
-In the case of versions F the activity of the molecules on the edges
-is described by pairing matrix; Aep.
-
-%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
-%
-The constraints for the variants can be given to a SMT solver to find
-VTSs that belong to the variants.
-
-% We have applied the tool for the above variations for searching the
-% VTSs that satisfies their corresponding properties. 
-%
-% After creating the constraint using different Boolean variables 
-% we ship them directly to the solver.
-% %
-% In case of a satisfying (SAT) assignment of the added constraints the
-% Z3 theorem prover gives a model with the variable assignment.
-% %
-% In case no possible satisfying assignment the solver returns UNSAT.
-
-%
-%
-
-% \subsection{Creating a solver and solving these constraints}
-% We will create a solver and add these build constraint using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
-
-% \begin{figure}[ht]
-% %\vspace{-3mm}
-% \begin{verbatim}
-% # Create a solver
-% s = Solver()
-% # Add these constraints to it.
-% s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)
-
-% # Check for the satisfiability assignment.
-% print s.check()   
-% \end{verbatim}
-% \caption{Solving for these constraints.}
-% \label{code:motivate}
-% \end{figure}
-
-%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
+We need sophisticated solvers
 

### 2018-04-23 papers/synth/related.tex
asd

In recent years, there have been a wide range of methods
developed for the similar synthesis problems~\cite{sktech,ceSynth,exampleSynth}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-04-25 papers/synth/encoding.tex
pape

@@
-In this section we will present a list of problems that may arise from
-synthesis of VTSs from partial available information.
+In this section, we will present a list of problems that may arise from
+synthesis of VTSs from partial available information
+and our method for completing the missing parts.
 
@@
 
-Our objective is to find missing parts of a partially known VTSs.
+We will assume that we are given a VTS, whose all components
+are not specified.
 %
-We will consider several variations of the problem.
+Our objective is to find the missing parts.
 %
-\begin{itemize}
-\item Learning activity functions
-\item Modifying labels of the nodes and edges
-\item Adding missing edges
-\item Adding
-\end{itemize}
+The missing information can be in any of these combinations parts of
+VTS. For example existence of some undiscovered edges or nodes, or
+insufficient knowledge about the presence of molecules in some part of
+the VTS (either on the node or on the edge).
+%
+To cover most of the likely variations of this missing information we
+have encoded the following variants of VTS synthesis.
+
+% % We will consider several variations of the problem.
+% %
+% \begin{itemize}
+% \item Learning activity functions
+% \item Modifying labels of the nodes and edges
+% \item Adding missing edges
+% \item Adding 
+% \end{itemize}
 
@@
 
-The missing information can be in any of these combinations parts of VTS.
-For example existence of some undiscovered edges or nodes, or insufficient knowledge about the presence of molecules in some part of the VTS (either on the node or on the edge).
-To cover most of the likely variations of this missing information we have encoded the following variants of VTS synthesis.
 %
@@
   \end{enumerate}        
-\item Learning meaningful activity function. 
+\item Learning meaningful activity functions from a given language of
+  propositional formulas
   \begin{enumerate}
@@
 \begin{align}
-  \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
-               ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
+  \exists n, a, e, b, p, r, p,
+  ( \texttt{Consistancy}\land \texttt{ActiveNode} \land 
+  \texttt{ActiveEdge} \land \texttt{GivenCons} \land
+  \texttt{ModifyCons} )   
   \tag{E1}\label{eq:addedge1}
@@
 
-The basicvtsconstraints and vtsactivityconstraint are same as the previous sections, describing stability of the graph and fusion of the edge into the node and the molecular activity describing the active state of a molecule.
-The givenvtsinformation is encoded using a front end input language.
-The user provides the information of the VTS with a partial information using this front end.
-Our tool then converts these inputs into the constraints over the given VTS.
+% \begin{align}
+%   \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
+%                ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
+%   \tag{E1}\label{eq:addedge1}
+% \end{align}
+
+The basicvtsconstraints and vtsactivityconstraint are same as the
+previous sections, describing stability of the graph and fusion of the
+edge into the node and the molecular activity describing the active
+state of a molecule. The givenvtsinformation is encoded using a front
+end input language. The user provides the information of the VTS with
+a partial information using this front end. Our tool then converts
+these inputs into the constraints over the given VTS.
 

### 2018-04-25 papers/synth/intro.tex
pape

@@
 %
-Not all the pairs of molecules can participate in the fusion, it is
-usually determined by wet experiments the potential fusion pairs.
+Not all the pairs of molecules can participate in the fusion, the
+potential fusion pairs are usually determined by wet experiments.
 %
@@
 %
-The regulation controls are defined by a fusion pairing matrix
-containing Boolean values for each pair of molecules and activity
+The regulation controls are defined by a fusion pairing relation
+containing pairs of molecules and activity
 Boolean functions.
@@
 %
-It largely means the patch work of wet experiments~\cite{model} for
-identifying the compartments, channels, molecules, their activity, and
-regulatory control.
+It largely means that the current knowledge is due to the patch work
+of wet experiments~\cite{model} for identifying the compartments,
+channels, molecules, their activity, and regulatory control.
 %

### 2018-04-26 vts-synth/src/utils.h
brainless coding

@@ -8,6 +8,20 @@
 #include <ostream>
 #include <sstream>
 
+#include <vector>
+// #include <boost/regex.hpp>
+#include <boost/algorithm/string.hpp>
+
+inline std::vector<std::string> get_coordinates ( std::string text, bool splitOnUnder ) {
+  std::vector<std::string> results;
+  if ( splitOnUnder == false ) {
+    boost::split(results, text, [](char c){ return c == '['; });
+  } else {
+    boost::split(results, text, [](char c){ return c == '_'; });
+  }
+  return results;
+}
+
 class vts_exception : public std::runtime_error
 {
 public:

### 2018-04-26 vts-synth/src/vts-synthesis.cpp

@@ -1,7 +1,8 @@
-#include<vts.h>
-#include<z3-util.h>
-#include<algorithm>
-#include<vector>
+#include <vts.h>
+#include <z3-util.h>
+#include <algorithm>
+#include <utils.h>
+
 
 
 /** To do list : 
@@ -140,7 +141,6 @@ z3::expr vts::annotate_plos_graph () {
    * N = 2, M = 6 
    * model 3: Arb on edge, Nothing on node
    */
-
   /** node: n[i][k] : below.  a[i][k] : use Model_3 **/
   // Node 0 : [111 110]  
   z3::expr node_cons = !nodes[0][0] && nodes[0][1] && nodes[0][2] && nodes[0][3] && nodes[0][4] && nodes[0][5]; 
@@ -168,67 +168,125 @@ bool equality_check( z3::expr_vector fixZ, z3::expr var ) {
   return false;
 }
 
+/* /Tuple Version 
+//static z3::expr_vector DEFAULT_VECTOR;
+//static Z3_ast_vector DEFAULT_VECTOR;
 
+static Vec2Expr DEFAULT_2D_XOR;
+static Vec3Expr DEFAULT_3D_XOR;
+static Vec4Expr DEFAULT_4D_XOR;
 
-/*
-void unassigned_2d_bits ( z3::expr_vector& flatternListN,
-                       std::vector < std::tuple <unsigned, unsigned> >& knownTuple,
-                       z3::expr_vector& unassignedVector ) {
-  auto var = knownTuple.begin();
-  for ( unsigned i = 0; i < flatternListN.size(); i++ ) {
-    auto coord = get_coordinates( Z3_ast_to_string(ctx(), flatternListN[i] );
-    if ( var[0] != coord[0] || var[1] != coord[1] ){
-      unassignedVector.push_back( var );
-      // if ( equality_check( fixZ, var ) ) 
-      //  continue;
-    } else 
-      var = std::next(var);
-  }
-}
-
-void unassigned_3d_bits ( z3::expr_vector& flatternListN,
-                       std::vector < std::tuple <unsigned, unsigned, unsigned> >& knownTuple,
-                       z3::expr_vector& unassignedVector ) {
-  auto var = knownTuple.begin();
-  for ( unsigned i = 0; i < flatternListN.size(); i++ ) {
-    auto coord = get_coordinates( Z3_ast_to_string(ctx(), flatternListN[i] );
[…]

### 2018-04-26 vts-synth/src/vts.cpp

@@ -1,7 +1,18 @@
 #include<vts.h>
 #include<z3-util.h>
 #include <tuple>        // std::tuple
+#include <vector>
+#include <algorithm>
 
+
+template<int index> struct TupleCompare
+ {
+    template<typename Tuple>
+    bool operator() (const Tuple& left, const Tuple& right) const
+    {
+        return std::get<index>(left) < std::get<index>(right);
+    }
+};
 // define n dimentional vectors
 //#include "boost/multi_array.hpp"
 //#include <cassert>
@@ -18,6 +29,7 @@ struct TupleCompare
     }
 };
 */
+
 
 void vts::add_known_edge( unsigned n1, unsigned n2, unsigned q,
                           std::vector<unsigned>& mols,
@@ -39,20 +51,27 @@ void vts::add_known_edge( unsigned n1, unsigned n2, unsigned q,
       knownActiveEdges.push_back( active_edge[n1][n2][q][mols[i]] );
     }
   }
+
   
   /*
+  // Tuple version
   for ( unsigned i = 0; i < mols.size(); i++ ) {
-     knownPresenceEdgesTuple.push_back( std::make_tuple (n1, n2, q, i ) );
-     knownEdgesTuple.push_back( std::make_tuple( n1, n2 ) ); 
-  }
+     knownPresenceEdgesTuple.push_back( std::make_tuple (n1, n2, q, mols[i]) );
+     knownEdgesTuple.push_back( std::make_tuple( n1, n2, q ) ); 
+     if ( act[i] == 2 ) {
+       continue;
+     } else if( act[i] == 0 ) {
+       knownActiveEdgesTuple.push_back( std::make_tuple( n1, n2, q, -mols[i] ) );
+     } else {
+       knownActiveEdgesTuple.push_back( std::make_tuple( n1, n2, q, mols[i] ) );
+     }
+
+
   std::sort(begin(knownPresenceEdgesTuple), end(knownPresenceEdgesTuple), TupleCompare<0>());
+  std::sort(begin(knownActiveEdgesTuple), end(knownActiveEdgesTuple), TupleCompare<0>());
   std::sort(begin(knownEdgesTuple), end(knownEdgesTuple), TupleCompare<0>());
-    std::cout << "\nMama mia ..\n";
-
-  for ( auto i& : knownPresenceEdgesTuple ) {
   }
-  **/
-
+  */
 }
 
 void vts::add_known_node( unsigned n,
[…]

### 2018-04-26 vts-synth/src/vts.h

@@ -24,12 +24,22 @@ public:
        unsigned _M, unsigned _N, unsigned _Q, model_version _V, unsigned _C, unsigned _D )
     : ctx(_ctx), M(_M), N(_N), E_arity(_Q),
       V(_V), C(_C), D(_D),
-      knownEdges(_ctx),
+      knownNodes( _ctx ),
       knownActiveNodes( _ctx),
+      knownEdges(_ctx),
       knownPresenceEdges( _ctx ),
       knownActiveEdges( _ctx ),
-      knownNodes( _ctx ),
       knownPairingMatrix( _ctx )
+      
+      /** vector version *
+      knownNodesTuple(),
+      knownActiveNodesTuple(),
+      knownEdgesTuple(),
+      knownPresenceEdgesTuple(),
+      knownActiveEdgesTuple(),
+      knownPairingMatrixTuple()
+      */
+      
   {
     init_vts();
   }
@@ -69,13 +79,23 @@ private:
   Vec3Expr drop2;
   Vec2Expr d_reach2;
 
-  z3::expr_vector knownEdges;
+  /* 
+  // Tuple version
+  Tup2Expr knownNodesTuple;
+  Tup2Expr knownActiveNodesTuple;
+  Tup3Expr knownEdgesTuple;
+  Tup4Expr knownPresenceEdgesTuple;
+  Tup4SignedExpr knownActiveEdgesTuple;
+  Tup2Expr knownPairingMatrixTuple;
+  */
+  
+  z3::expr_vector knownNodes; 
   z3::expr_vector knownActiveNodes;
+  z3::expr_vector knownEdges;
   z3::expr_vector knownPresenceEdges;
   z3::expr_vector knownActiveEdges;
-  z3::expr_vector knownNodes;
   z3::expr_vector knownPairingMatrix;
-
+  
   //flat version of variables
   // VecExpr flat_nodes;
   // VecExpr flat_active_node;
@@ -83,9 +103,6 @@ private:
   // VecExpr flat_edges;
   // VecExpr flat_presence_edge;
   // VecExpr flat_active_edge;
-
-
-
   // Vec3Expr dump2;
 
   //constraints
@@ -200,6 +217,7 @@ public:
   void print_denotation_console ( std::map<std::string,int> denotation_map, int  synthVar );
[…]

### 2018-04-26 papers/synth/prelim.tex

@@
 \end{df}
-$\pairs$ defines which molecules can fuse with which molecules.
+$\nodes$, $\mols$, $\edges$, and $\nlabel$ define a labelled graph.
 %
+Additionally, $\pairs$ defines which molecules can fuse with which molecules,
+and
+$\nodef$ and $\edgef$ are the activity functions for molecules on
+nodes and edges respectively.
+%
+The model captures the study state of a VTS.
+%
+The analysis of the model will inform us the network/graph properties of
+VTSs.
+
 Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
-%
-$\nodef$ and $\edgef$ are used to define activity of molecules on
-nodes and edges respectively.
 %
@@
 and destination nodes. 
+%
+An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
+if there are molecules $m,m' \in \mols$ such that $m$ is active in
+$(n,M',n')$, $m'$ is active in $n'$, and $(m,m') \in \pairs$.
+%
+We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
+with non-empty fusing molecules $M'' \subseteq M'$
+and $\pairs(M'')$ are not active in any other node.
 
@@
 $n$ is $m$-reachable from $n'$.
-%
-An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
-if there are molecules $m,m' \in \mols$ such that $m$ is active in
-$(n,M',n')$, $m'$ is active in $n'$, and $(m,m') \in \pairs$.
-%
-We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
-with non-empty fusing molecules $M'' \subseteq M'$
-and $\pairs(M'')$ are not active in any other node.
 %
@@
 Here, we list the Boolean variables and uninterpreted function symbols
-that encode the VTSs.
+that encode parts of VTSs.
 \begin{enumerate}
@@
 \end{enumerate}
+We also have auxiliary Boolean variables that will help us encode the well-fused property. 
+\begin{enumerate}
+\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
+  holds
+\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
+\end{enumerate}
 
-\subsection{Solvers}
-Due the combinatorial nature of the graphs, the search space is huge
-and often hard to enumerate naively.
+We will describe several constraints that encode VTSs in this section.
 %
-We need sophisticated solvers
+In the next section, we will extend the encoding for the synthesis problem.
+%
+To avoid cumbersome notation, we will not explicitly write the ranges
+of the indexing in the constraints.
+%
+$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
+%
+$m$ will range over molecules, i.e., from $1$ to $\mu$.
+%
+$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
+%
+
+The following constraints encode the basic consistency of VTSs.
+\begin{align}
+  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
+  \land
+  \bigwedge\limits_{i,q} \neg e_{i,i,q}
+  \land
+  % \tag{\texttt{NodeC}}\label{eq:f0}\\
+  \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
+  \tag{\texttt{EdgeC}}\label{eq:c0}\\
+  \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
+  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
+  % \tag{V2}\label{eq:f1}\\
+  \tag{\texttt{ActivityC}}\label{eq:c4}\\
+  \bigwedge\limits_{m} 
+  (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
+  (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
+  \tag{\texttt{PairingC}}\label{eq:c3}\\
+  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
+  \bigvee_{\mathclap{m,m^{\prime}}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
+  \tag{\texttt{Fusion1}}\label{eq:fuse1} \\
+\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies \neg 
+  \bigvee_{\mathclap{j \neq j^{\prime}, m^{\prime\prime}}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
+  \tag{\texttt{Fusion2}}\label{eq:fuse2} \\
+  \texttt{EdgeC} \land
+  \texttt{ActivityC} \land \texttt{PairingC} \land
+  \texttt{Fusion1} \land \texttt{Fusion2} 
+  \tag{\texttt{Consistancy}}\label{eq:c3}
+\end{align}
+\texttt{EdgeC} states that each edge has at least one molecule,
+there are no self loops, and edge labels are consistent with node labels.   
+\texttt{ActivityC} states that active molecule are present.
+\texttt{PairingC} states that a molecule can either participate in fusion
+via nodes or via edges, but not both.
+\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
+\texttt{Consistancy} is the conjunction of all of the above.
+
+\paragraph{Activity functions}
+%
+The following constraints encode that
+the activity of the molecules are controlled by activity functions.
+%
+%
+\begin{align}
+\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
+\tag{\texttt{ActiveNode}}\label{eq:anb}\\
+   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
+  \tag{\texttt{ActiveEdge}}\label{eq:aeb}
+\end{align}
+%
+Later we will be synthesizing missing activity functions and replace the
+above constraints with parameterized constraints.
+
+For synthesis of incomplete systems,
+we need properties properties against which we synthesize the missing parts.
+%
+Here we will discussed two such properties proposed in earlier
+works~\cite{SASBpaper}.
+%
+
+\paragraph{Stability property}
+%
+We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
+$m$-path from $i$ to $j$ of length less than or equal to $p$.
+%
+We use $m$-reachability to encode the stability condition in VTSs.
+%
+The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps.
+%
+Subsequently, we encode stability condition using the reachability variables.
+\begin{align}
+  \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+  \tag{R1}\label{eq:reach1}\\
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
+  \tag{R2}\label{eq:reach2}
+\end{align}
+
+\paragraph{$k$-connected property}
+%
+$k$-connectedness is a robustness property.
+%
+Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is dropped
+and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
+the modified VTS.
+%
+% To check whether $k$-connected is a
+% necessary condition, we remove (drop) $k-1$ edges from the graph and
+% if it disconnects the graph, and we get an assignment.
+% %
+% We have a graph that is not $k$-connected.
+%
+In the following, $\texttt{Drop}(d,k)$  encode that only
+existing edges can be dropped and exactly $k-1$ edges are dropped.
+%
+$\texttt{Reach}(d,r')$ defines reachability in the modified VTS,
+therefore we use a new variable $r'_{i,j}$ to encode reachability from
+$i$ to $j$.
+%
+$\texttt{Connected}(r')$ says that all nodes are reachable from any
+other node.
+% In the following constraint, we encode $r'_{i,j}$ is true if there is an
+% edge $(i,\_,j)$ and it is not dropped, or there is a node
+% $i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
+% not dropped and $r'_{i',j}$ is true.
+\begin{align*}
+  \texttt{Drop}(d,k) = & 
+  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
+  \sum_{i,j,q} d_{i,j,q} = k-1\\
+  \texttt{Reach}(d,r') = &
+  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
+  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
+\end{align*}
+We will be synthesizing for both connected any disconnected graphs.
+%
+We also define the following macros. 
+\begin{align*}
+  \texttt{Connectedness}(k) = & \forall d.\;
+          (\texttt{Drop}(d,k) \limplies \exists r'.\;\texttt{Reach}(d,r')
+                                \land \texttt{Connected}(r'))\\
+  \texttt{Disconnectedness}(k) = & \exists d.\;
+          (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{Reach}(d,r')
+                                \land \lnot \texttt{Connected}(r'))
+\end{align*}
+Since the free variables in $\texttt{Connectedness}(k)$ are universally
+quantified, please note that the connectedness property introduces the two
+quantifier alternations.
+%
+
+% \subsection{Solvers}
+% Due the combinatorial nature of the graphs, the search space is huge
+% and often hard to enumerate naively.
+% %
+% We need sophisticated solvers
 

### 2018-04-26 papers/synth/encoding.tex
encoding formula fix

@@
 \begin{enumerate}[label=\Alph*]
-\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
+\item  Add new edges to the given VTS to achieve k-connectivity, graph stability and fusion. 
 \item  Modify the flow of molecules on the nodes and on the edges.
@@
   % - Function dependence with var occurring once.
-\item  VTS repair. [Allow both delete and add to the system]
+\item  VTS repair. Allow both delete and add to the system.
 \end{enumerate}
@@
 
-The basicvtsconstraints and vtsactivityconstraint are same as the
-previous sections, describing stability of the graph and fusion of the
+%The basicvtsconstraints and vtsactivityconstraint are same as the
+The \texttt{Consistancy} describing stability of the graph and fusion of the
 edge into the node and the molecular activity describing the active
-state of a molecule. The givenvtsinformation is encoded using a front
+state of a molecule. The \texttt{GivenCons} is encoded using a front
 end input language. The user provides the information of the VTS with
@@
 
-We encode the restriction\_on\_modification by putting the constraints on the unassigned edges and edge labels.
-The constraint of allowing only certain number of addition to the given VTS is encoded as at\_most\_k() function over the unassigned edges and label.
+We encode the \texttt{ModifyCons} by putting the constraints on the unassigned edges and edge labels.
+The constraint of allowing only certain number of addition to the given VTS is encoded as \texttt{AtMostK} function over the unassigned edges and label.
+
+%\[Unassigned Edges\]}
+%\[Unassigned Activity Labels\]} 
+%\[Unassigned Molecule Labels\]
+\begin{align}
+   \texttt{EdgeConstraint} = \texttt{AtMostk} \, [ \texttt{unassigned\_edges} ]  
+   \tag{E2}\label{eq:addedge2}
+\end{align}
+\begin{align}
+   \texttt{EdgeActivity} = \texttt{AtMostK} \, [ \texttt{activity\_labels} ]
+   \tag{E3}\label{eq:addedge3}
+\end{align}
 
 \begin{align}
-    constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )    
-    constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
-    constraints of the molecule presence on the edge = at\_most\_k ( unassigned molecule labels in VTS edges )\label{eq:addedge2}
+   \texttt{EdgePresence} = \texttt{AtMostK} \, [ \texttt{unassigned\_molecule\_labels} ]  
+   \tag{E4}\label{eq:addedge4}
 \end{align}
@@
 \begin{align}
- \exists e_{ijq} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
-  \tag{E1}\label{eq:addedge2}
+  \exists i, j, q \,
+  ( \texttt{KConnectivity}  \land \texttt{NoSelfEdge} \land \ref{eq:addedge1} )    
+  \tag{E5}\label{eq:addedge5}
 \end{align}
 
-The connectivity\_constraint \&\& self\_edge\_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
+The \texttt{KConnectivity} and \texttt{NoSelfEdge} are same as the previous section, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
 addedge1 is the constraint of \ref{eq:addedge1}.
@@
 
-    auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;
+ %   auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;
 
-    auto qvtsCons = exists( setN, 
-                    exists( setActiveN, 
-                    exists( setPresenceE,  
-                    exists( setActiveE, 
-                    exists( setPairingM, 
-                    exists( setReach, 
-                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));
+% %   auto qvtsCons = exists( setN, 
+%                    exists( setActiveN, 
+%                    exists( setPresenceE,  
+%                    exists( setActiveE, 
+%                    exists( setPairingM, 
+%                    exists( setReach, 
+%                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));
 

### 2018-04-26 papers/synth/encoding.tex
changes

--- 2018-04-25 papers/synth/encoding.tex
@@
 
+\subsection{Encoding Incomplete VTS}
+
+In our synthesis algorithm, we take a VTS $G =
+(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ as input.
+%
+We allow activity functions not to be specified, i.e., vectors
+$\edgef$ and $\nodef$ may contain uninterpreted Boolean functions.
+%
+We construct the following constraints to encode the available information
+about $G$.
+%
+\begin{align*}
+  \texttt{KnownE} &= \land \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land q \leq q' \land m \in M_q \}\\
+  \texttt{KnownN} &= \land \{n_{i,m}| m \in \nlabel(i) \land i \in \nodes \}\\
+  \texttt{KnownP} &= \land \{p_{i,j}| (i,j) \in \pairs \} \\
+  \texttt{KnownActiveN} &= \land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is defined.} \} \\
+  \texttt{KnownActiveE} &= \land \{ b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
+                   | \edgef_m \text{ is defined.} \} \\
+  \texttt{KnownCons} & = \texttt{KnownE} \land \texttt{KnownN} \land 
+                      \texttt{KnownP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
+\end{align*}
+We will do synthesis against the following property that says the VTS is stable and  3-connected,
+but not 4-connected.
+%
+The property is designed to balance the search space such that the synthesis procedure does not
+succeed with simply adding too many edges. 
+%
+\begin{align*}
+  \texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) \land \texttt{DisConnected}(4)
+\end{align*}
+
+Now we will consider the constraints for synthesis for the above
+listed problems.
+\begin{align*}
+  \texttt{UnknownE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
+                      q' < q \leq \pi \}\\
+  \texttt{SynthE} &= \Sigma \texttt{UnknownE} \leq 3 \\
+\end{align*}
+
 \begin{align}
-  \exists n, a, e, b, p, r, p,
-  ( \texttt{Consistancy}\land \texttt{ActiveNode} \land 
-  \texttt{ActiveEdge} \land \texttt{GivenCons} \land
-  \texttt{ModifyCons} )   
+  \exists n, a, e, b, p
+  ( \texttt{Consistancy}\land \texttt{Property} \land
+  \texttt{KnownCons} \land \texttt{SynthCons} )
   \tag{E1}\label{eq:addedge1}
@@
 
-The basicvtsconstraints and vtsactivityconstraint are same as the
-previous sections, describing stability of the graph and fusion of the
-edge into the node and the molecular activity describing the active
-state of a molecule. The givenvtsinformation is encoded using a front
-end input language. The user provides the information of the VTS with
-a partial information using this front end. Our tool then converts
-these inputs into the constraints over the given VTS.
+% The basicvtsconstraints and vtsactivityconstraint are same as the
+% previous sections, describing stability of the graph and fusion of the
+% edge into the node and the molecular activity describing the active
+% state of a molecule.The givenvtsinformation is encoded using a front
+% end input language. The user provides the information of the VTS with
+% a partial information using this front end. Our tool then converts
+% these inputs into the constraints over the given VTS.
 
-We encode the restriction\_on\_modification by putting the constraints on the unassigned edges and edge labels.
-The constraint of allowing only certain number of addition to the given VTS is encoded as at\_most\_k() function over the unassigned edges and label.
+We encode the restriction\_on\_modification by putting the constraints
+on the unassigned edges and edge labels. The constraint of allowing
+only certain number of addition to the given VTS is encoded as
+at\_most\_k() function over the unassigned edges and label.
 

### 2018-04-26 papers/synth/prelim.tex
changes

@@
 \paragraph{Activity functions}
-%
-The following constraints encode that
+We also need to encode that encode that
 the activity of the molecules are controlled by activity functions.
 %
+However, the encoding functions can be given to us many different ways,
+for example as a lookup table, or  a concise Boolean formula.
+%
+In the following constraints, we assume the appropriate encoding is
+used for the functions.
 %
@@
 \tag{\texttt{ActiveNode}}\label{eq:anb}\\
-   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
+   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
   \tag{\texttt{ActiveEdge}}\label{eq:aeb}
@@
 %
-Later we will be synthesizing missing activity functions and replace the
-above constraints with parameterized constraints.
+Later we will be synthesizing missing activity functions and 
+replace the above constraints with parameterized constraints that
+encode a space of candidate functions.
+
+\subsection{VTS properties}
 
@@
 Subsequently, we encode stability condition using the reachability variables.
-\begin{align}
-  \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-  \tag{R1}\label{eq:reach1}\\
- \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-  \tag{R2}\label{eq:reach2}
-\end{align}
+\begin{align*}
+  \texttt{paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+  \\
+  \texttt{loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
+  \\
+  \texttt{stability} &= \exists r. \; \texttt{paths}(r) \land \texttt{loop}(r)
+\end{align*}
 
@@
   \sum_{i,j,q} d_{i,j,q} = k-1\\
-  \texttt{Reach}(d,r') = &
+  \texttt{ReachAbove}(d,r') = &
   \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
+  \texttt{ReachBelow}(d,r') = &
+   \bigwedge\limits_{i,j}  r^{\prime}_{i,j} \limplies [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
   \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
@@
 \begin{align*}
-  \texttt{Connectedness}(k) = & \forall d.\;
-          (\texttt{Drop}(d,k) \limplies \exists r'.\;\texttt{Reach}(d,r')
+  \texttt{Connected}(k) = & \forall d.\;
+          (\texttt{Drop}(d,k) \limplies \exists r'.\;\texttt{ReachBelow}(d,r')
                                 \land \texttt{Connected}(r'))\\
-  \texttt{Disconnectedness}(k) = & \exists d.\;
-          (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{Reach}(d,r')
+  \texttt{Disconnected}(k) = & \exists d.\;
+          (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
                                 \land \lnot \texttt{Connected}(r'))

### 2018-04-29 papers/synth/encoding.tex

@@
 %
-\begin{enumerate}[label=\Alph*]
-\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
+\begin{enumerate}
+\item  Add new edges 
 \item  Modify the flow of molecules on the nodes and on the edges.
@@
   propositional formulas
-  \begin{enumerate}
-    \item kcnf: low depth circuit.
-    \item Boolean gates: And, Or.
-    \item Boolean gates with linear combination.  
-    \end{enumerate}        
+  % \begin{enumerate}
+  %   \item kcnf: low depth circuit.
+  %   \item Boolean gates: And, Or.
+  %   \item Boolean gates with linear combination.  
+  % \end{enumerate}        
   % - Function dependence with var occurring once.
-\item  VTS repair. [Allow both delete and add to the system]
+\item  VTS repair. Allow both delete and add to the system.
 \end{enumerate}
@@
 \end{align*}
-We will do synthesis against the following property that says the VTS is stable and  3-connected,
-but not 4-connected.
+We also collect the variables that are absent in the VTS.
+\begin{align*}
+  \texttt{UnknownELabel} &=
+  \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
+                          0 < q \leq q' \land m \not\in M_{q} \}\\
+  \texttt{UnknownE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
+                    q' < q \leq \pi \}\\
+  \texttt{UnknownNLabel} &= \{n_{i,m}| m \not\in \nlabel(i) \land i \in \nodes \}\\
+  \texttt{UnknownP} &= \{p_{i,j}| (i,j) \not\in \pairs \} \\
+  \texttt{UnnownActive} &=  \Land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is undefined.} \} \union \\
+   &\quad\quad\quad  \{ b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
+                   | \edgef_m \text{ is undefined.} \}
+\end{align*}
+We have defined $\texttt{UnknownE}$, $\texttt{UnknownN}$, and
+$\texttt{UnknownP}$
+as set and will be converted into formulas depending
+on the different usage in the synthesis problems.
+
+% Since not all the activity functions are defined some of the functions
+% appearing in $\texttt{ActiveE}$ and $\texttt{ActiveN}$ are
+% uninterpreted function symbols.
+
+\subsection{Encoding synthesis property}
+
+We will do synthesis against the following property that says the VTS
+is stable and 3-connected, but not 4-connected.
 %
@@
 
-Now we will consider the constraints for synthesis for the above
-listed problems.
+\subsection{Encoding synthesis constraints}
+
+Now we will consider the encodings for  the above
+listed synthesis problems.
+%
+The variations are presentations are to represent all the encodings supported by our tool.
+%
+However, the combinations of the variation are also possible and our tool easily
+supports them.
+%
+For simplicity of the presentation, we assume that if we are synthesizing an aspect of VTS,
+then all other aspects are fully given.
+
+\subsubsection{Fixing VTS by adding edges}
+%
+Now we will consider the case when we add new edges to VTS to satisfy the properties.
+%
+In the following, the pseudo-Boolean formula $\texttt{AddE}$ encodes
+that at most $slimit$ new undeclared edges may be added in VTS.
+%
 \begin{align*}
-  \texttt{UnknownE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
-                      q' < q \leq \pi \}\\
-  \texttt{SynthE} &= \Sigma \texttt{UnknownE} \leq 3 \\
+  \texttt{AddE}(slimit) &= \Sigma~\texttt{UnknownE} \leq slimit\\
+  \texttt{FixedE} &= \texttt{UnknownActive} \land \lnot \Lor \texttt{UnknownELabel} \;\union\;
+                    \texttt{UnknownNLabel} \;\union\;
+                    \texttt{UnknownP}
 \end{align*}
+We put together the constraints so far and obtain the following formula.
+\begin{align*}
+  & \texttt{SynthE}(slimit) = \\
+  & \quad\quad (  \texttt{Consistancy}\land \texttt{Property} \land
+  \texttt{KnownCons} \land \texttt{FixedE} \land
+  \texttt{AddE}(slimit) )
+  % \tag{SynthE}\label{eq:addedge1}
+\end{align*}
+As we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
+$\texttt{Property}$ encodes the goal, and $\texttt{KnownCons}$ are the constraints
+that are fixed in VTS.
+%
+A satisfying model of $\texttt{SynthE}$ will represent the synthesized VTS.
+%
+In the later synthesis problems, we will construct a similar QBF formula with same
+first three parts and the last one is due the requirements of the synthesis problem.
 
-\begin{align}
-  \exists n, a, e, b, p
+We limit the addition of the edges, since we look for a fix that require minimum number
+of changes in the given VTS.
+%
+We start with $slimit = 1$ and grow one by one until $\texttt{SynthE}(slimit)$
+becomes satisfiable.
+
+\paragraph{\bf Fixing VTS by adding molecules to the labels:}
+The system may also be fixed only by modifying labels on the edges or the nodes instead
+of adding edges.
+%
+In the following, the formula encodes that only $slimit$ edge labels may be added.
+\begin{align*}
+  &\texttt{AddLabelEdge}(slimit) = 
+    \Sigma~\texttt{UnknwonEdgeLabel}  \leq slimit\\
+  & \texttt{FixedForLabel} = \texttt{UnknownActive} \land \lnot \Lor \texttt{UnknownE} \;\union\;
+                    \texttt{UnknownNLabel} \;\union\;
+                    \texttt{UnknownP}\\
+  &\texttt{SynthLabel}(slimit) = \\
+  & \quad\quad
     (  \texttt{Consistancy}\land \texttt{Property} \land
-  \texttt{KnownCons} \land \texttt{SynthCons} )
-  \tag{E1}\label{eq:addedge1}
-\end{align}
+  \texttt{KnownCons} \land \texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
+\end{align*}
+Similar to the previous encoding we solve the satisfiability of the above formula
+to obtain additional molecules that may be added to the edge labels.
+
+% We encode the \texttt{ModifyCons} by putting the constraints on the
+% unassigned edges and edge labels. The constraint of allowing only
+% certain number of addition to the given VTS is encoded as
+% \texttt{AtMostK} function over the unassigned edges and label.
+
+%\[Unassigned Edges\]}
+%\[Unassigned Activity Labels\]} 
+%\[Unassigned Molecule Labels\]
+% \begin{align}
+%    \texttt{EdgeConstraint} = \texttt{AtMostk} \, [ \texttt{unassigned\_edges} ]  
+%    \tag{E2}\label{eq:addedge2}
+% \end{align}
+% \begin{align}
+%    \texttt{EdgeActivity} = \texttt{AtMostK} \, [ \texttt{activity\_labels} ]
+%    \tag{E3}\label{eq:addedge3}
+% \end{align}
 
 % \begin{align}
-%   \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
-%                ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
-%   \tag{E1}\label{eq:addedge1}
+%    \texttt{EdgePresence} = \texttt{AtMostK} \, [ \texttt{unassigned\_molecule\_labels} ]  
+%    \tag{E4}\label{eq:addedge4}
 % \end{align}
 
-% The basicvtsconstraints and vtsactivityconstraint are same as the
-% previous sections, describing stability of the graph and fusion of the
-% edge into the node and the molecular activity describing the active
-% state of a molecule.The givenvtsinformation is encoded using a front
-% end input language. The user provides the information of the VTS with
-% a partial information using this front end. Our tool then converts
-% these inputs into the constraints over the given VTS.
+% Put \ref{eq:addedge2} in symbolic form and explain it in a couple of lines.
 
-We encode the restriction\_on\_modification by putting the constraints
-on the unassigned edges and edge labels. The constraint of allowing
-only certain number of addition to the given VTS is encoded as
-at\_most\_k() function over the unassigned edges and label.
+% In order to decrease the search space we do not allow any modification in the node label and activity on the nodes. This constraint can be encoded as the fixing all the unassigned bits to false.
 
-\begin{align}
-    constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )    
-    constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
-    constraints of the molecule presence on the edge = at\_most\_k ( unassigned molecule labels in VTS edges )\label{eq:addedge2}
-\end{align}
+% %    // Fix rest of them to zero.
+% %    auto fixVar0 = ! z3::mk_or ( openN )  && ! z3::mk_or ( openActiveN );
 
-Put \ref{eq:addedge2} in symbolic form and explain it in a couple of lines.
+% \begin{align}
+%   \exists i, j, q \,
+%   ( \texttt{KConnectivity}  \land \texttt{NoSelfEdge} \land \ref{eq:addedge1} )    
+%   \tag{E5}\label{eq:addedge5}
+% \end{align}
 
-In order to decrease the search space we do not allow any modification in the node label and activity on the nodes. This constraint can be encoded as the fixing all the unassigned bits to false.
-
-%    // Fix rest of them to zero.
-%    auto fixVar0 = ! z3::mk_or ( openN )  && ! z3::mk_or ( openActiveN );
-
-\begin{align}
- \exists e_{ijq} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
-  \tag{E1}\label{eq:addedge2}
-\end{align}
-
-The connectivity\_constraint \&\& self\_edge\_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
+% The \texttt{KConnectivity} and \texttt{NoSelfEdge} are same as the previous section, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
 addedge1 is the constraint of \ref{eq:addedge1}.
@@
 
-    auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;
+ %   auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;
 
-    auto qvtsCons = exists( setN, 
-                    exists( setActiveN, 
-                    exists( setPresenceE,  
-                    exists( setActiveE, 
-                    exists( setPairingM, 
-                    exists( setReach, 
-                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));
+% %   auto qvtsCons = exists( setN, 
+%                    exists( setActiveN, 
+%                    exists( setPresenceE,  
+%                    exists( setActiveE, 
+%                    exists( setPairingM, 
+%                    exists( setReach, 
+%                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));
 
-\subsection{Encoding molecules presence}
+\subsubsection{Fixing VTS by learning activity functions:}
 
-\subsection{Encoding low depth cnf circuits}
+Now we consider a scenario where some of the activity functions for some of the molecules
+are missing.
+%
+The activity functions are $\mu$-input Boolean functions.
+%
+We choose a class of formulas for the candidate functions.
+%
+We encode the candidates in a formula with parameters.
+%
+We choose different candidates by choosing values for the parameters.
 
-\subsection{Encoding boolean gates}
+The formula \texttt{NNFTemplate} encodes a set of negation normal form functions 
+that take $y_1,..,y_\mu$ as input and contain $\lambda$ literals.
+To encode the set, it also has finite-range integer variables
+$z_1,..,z_{2\lambda}$ as parameters to select the functions.
 
-\subsection{Encoding vts repair}
-The repair of the VTS requires both the addition and the deletion of the present molecules, node molecules pairing matrix and activity of the molecules.
-We have encoded the vts repair in our tool using the dummy xor bits.
+% \paragraph{Encoding low depth cnf circuits}
+% \paragraph{Encoding boolean gates}
 
-\subsection{QBF encodings}
+\begin{align*}
+  \texttt{Gate}( z, w_1, w_2 ) = ( z  = 1 \limplies w_1  \land w_2 ) \land  
+  ( z = 2  \limplies w_1  \lor w_2 ) \land
+  ( z = 3  \limplies w_1 )\\
+  \texttt{Leaf}( z, [y_1,..,y_\mu] ) =
+  \Land\limits_{l=1}^{\mu} ( z = 2l-1  \limplies y_{l}) \land ( z = 2l  \limplies \lnot y_{l})\\
+  \texttt{NNFTemplate}([z_1,..,z_{2\lambda}],[y_1,..,y_\mu] ) = \\
+  \exists w_1,..,w_{2\lambda}.\;w_1 \land \Land_{l=1}^{\lambda} w_{\lambda+l} = \texttt{Leaf}( z_{\lambda+l}, [y_1,..,y_\mu] ) \land
+  w_{l} = \texttt{Gate}( z_l, w_{2l},w_{2l+1})
+\end{align*}
+
+Given the above templates
+
+\begin{align*}
+  &\texttt{FindFunctions}(z,\lambda) =\\
+  &\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
+  \texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) |
+  \nodef_m \text{ is undefined}\} \\
+  &\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
+  \texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) | 
+  \edgef_m \text{ is undefined}
+  \}
+\end{align*}
+
+\begin{align*}
+    & \texttt{FixedForLabel} = \lnot \Lor \texttt{UnknownE} \;\union\; \texttt{UnknownN} \;\union\;
+                    \texttt{UnknownNLabel} \;\union\;
+                    \texttt{UnknownP}\\
+  &\texttt{SynthFunction}(z,\lambda) = \\
+  & \quad\quad
+    (  \texttt{Consistancy}\land \texttt{Property} \land
+  \texttt{KnownCons} \land \texttt{FixedForFunctions} \land \texttt{FindFunctions}(slimit) )
+\end{align*}
+
+\subsection{Repairing VTS:}
+%
+Now we will consider the repair of VTS by allowing not only addition but also
+deletion of the molecules, edges, functions, or pairing matrix.
+%
+We illustrate the repairing on one class of variables and rest can be .....
+%
+The repair of the VTS requires both the addition and the deletion of
+the present molecules, node molecules pairing matrix and activity of
+the molecules. We have encoded the vts repair in our tool using the
+dummy xor bits.
 

### 2018-04-29 papers/synth/model.tex
asd
printing

@@
 \ashu{Discuss the model in Biological terms.}
+
+%
+Therefore, the model only has aspects of a network or a graph.\\
+
+\ankit{Discuss the yeast and eukaryotes example graph}
+\begin{enumerate}
+\item Complex form using three Q-SNAREs and one R-SNARE. In order for a vesicle to fuse to it's corresponding target compartment this combination has to be present.
+\item In the graph shown the R-SNAREs are always in active. Every combination is formed by three active Q-SNAREs and one active R-SNARE.
+\item  Qai, Qbi, Qci and Ri are just dummy names, real biological names can be found in the below table. 
+\item In the diagram white circle molecules are always active. Other edge labels are inactive molecules.
+\item Pairing matrix restriction: ith R-SNARE can fuse with only the corresponding ith Q-SNARES and vice-versa. No other combination is allowed.
+\item Concept of v and t-SNAREs is replaced by Q and R-SNAREs. 
+\end{enumerate}
+
+\begin{tabular}{|l|l|}
+\hline
+\multicolumn{2}{|c|}{Team sheet} \\
+\hline
+GK & Paul Robinson \\
+LB & Lucus Radebe \\
+DC & Michael Duberry \\
+DC & Dominic Matteo \\
+\hline
+RB & Didier Domi \\
+MC & David Batty \\
+MC & Eirik Bakke \\
+MC & Jody Morris \\
+FW & Jamie McMaster \\
+ST & Alan Smith \\
+ST & Mark Viduka \\
+\hline
+
+\caption{Run-times for searching for models (in secs).}
+  \label{tab:vts-grabh}
+\end{tabular}
+
+Qa1 Qb1 Qc1 R1
+Stx18 Sec20 Slt1 Sec22b
 

### 2018-04-29 vts-synth/src/kcnf-encoding.cpp

@@ -24,16 +24,18 @@ z3::expr vts::literal_cnf ( Vec2Expr s, unsigned i, unsigned k, bool e, unsigned
     z3::expr_vector cl_list(ctx);
     z3::expr_vector inner_list(ctx);
     
+    //std::cout << "value of k is :" << k << "\n";
     for ( unsigned k1 = 0; k1 < M; k1++ ) {
       if ( k1 == k )  continue;
       
       if ( e == true ) { 
         inner_list.push_back( ( s[d][k1] && presence_edge[i][j][q][k1] ) 
                           || ( s[d][k1+M] && !presence_edge[i][j][q][k1] ) );
-      }
-      else { 
+      } else { 
         inner_list.push_back( ( s[d][k1] && nodes[i][k1] ) 
                            || ( s[d][k1+M] && !nodes[i][k1] ) );
+      //std::cout << "value of k1 is: " << k1 << "\n" ; 
+      //std::cout << "Interested var is: " << s[d][k1] << " and " << s[d][k1+M] << "\n";
       }
       
       cl_list.push_back( s[d][k1] );
@@ -45,6 +47,8 @@ z3::expr vts::literal_cnf ( Vec2Expr s, unsigned i, unsigned k, bool e, unsigned
     // To make compuational challenge easy lets fix at_most_one`
     // auto cConst =  at_least_three ( cl_list) && ! at_least_four( cl_list );
     auto cConst = !at_least_two( cl_list ); 
+    //std::cout << cConst << "\n";
+    //exit(0);
     //auto cConst = !at_least_two( cl_list) && at_least_one( cl_list ); 
     lit_listC.push_back( cConst );
     

### 2018-04-29 vts-synth/src/synth-func.cpp

@@ -23,7 +23,7 @@ void dVar_update ( unsigned m, unsigned M, std::string& depth_var,
     var = "!arg";
     
   //if ( m == M-1 || gateCase == true ) {
-  if ( litCount == noOfLiterals ) {
+  if ( litCount == noOfLiterals || gateCase == true ) {
     depth_var = depth_var + var + std::to_string (m);
   }else { 
     depth_var = depth_var + var + std::to_string (m) + " || ";
@@ -74,8 +74,8 @@ void chosen_var ( unsigned molecule, unsigned leafVar, unsigned candidateVar, un
 }
 
 void chosen_gates ( unsigned m, unsigned gateNumber, 
-                    std::vector < std::vector< std::vector <int> > > wVarStr, 
-                    std::vector<std::string> chosenGates ) {
+                    std::vector < std::vector< std::vector <int> > >& wVarStr, 
+                    std::vector<std::string>& chosenGates ) {
   if ( wVarStr[m][gateNumber][0] == 1 ) 
     chosenGates.push_back( "AND" );
   else 
@@ -108,7 +108,6 @@ void print_learned_function ( std::vector<std::string>& chosenVars,
     std::cout << "a_" << std::to_string(m) << " = "  <<  chosenVars[0] << '\n';
   }
 }
-
 
 void print_func_gates ( unsigned noOfMolecules, unsigned noOfLeaves, unsigned candidateVar, 
                         std::vector < std::vector< std::vector <int> > > func_arg, 

### 2018-04-30 papers/synth/conclusion.tex
intro
encoding finished

--- 2018-04-22 papers/synth/model.tex
@@
-\ashu{Discuss the model in Biological terms.}
+In this paper, we presented the encoding of the synthesis problems
+that may rise from VTSs.
+%
+We demonstrated that our tool scale up to the relevant sizes of the
+VTSs. 
+%
+We will take this tool to the biologists and develop wet experiments 
+that may validate some synthesis results from the tool.
+%
+Our model of VTSs are static graphs.
+%
+In future, we will study the dynamic behaviours of VTSs.
+%
+It will allow us to predict behaviors after the perturbations in the VTSs
+and more ways to test the predicted synthesis results.
 

### 2018-04-30 papers/synth/encoding.tex
encoding finished

@@
 
-% % We will consider several variations of the problem.
-% %
-% \begin{itemize}
-% \item Learning activity functions
-% \item Modifying labels of the nodes and edges
-% \item Adding missing edges
-% \item Adding 
-% \end{itemize}
-
-%Types of questions we are trying to solve.
-
-%
-%
 \begin{enumerate}
@@
 \item  Modify the flow of molecules on the nodes and on the edges.
-  \begin{enumerate}
-  \item use available set of molecules.
-  \item allow new molecule type to be added.     
-  \end{enumerate}        
+  % \begin{enumerate}
+  % \item use available set of molecules.
+  % \item allow new molecule type to be added.     
+  % \end{enumerate}        
 \item Learning meaningful activity functions from a given language of
@@
 
-In our synthesis algorithm, we take a VTS $G =
+In our synthesis method, we take a VTS $G =
 (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ as input.
@@
 \end{align*}
-We also collect the variables that are absent in the VTS.
+We also collect the variables that are not set to true in $\texttt{KnownCons}$.
 \begin{align*}
@@
 %
-The variations are presentations are to represent all the encodings supported by our tool.
+The presented variations represent the encodings
+supported by our tool.
 %
-However, the combinations of the variation are also possible and our tool easily
-supports them.
+Additionally, the combinations of the variation are also possible and
+our tool easily supports them.
 %
-For simplicity of the presentation, we assume that if we are synthesizing an aspect of VTS,
-then all other aspects are fully given.
+For simplicity of the presentation, we assume that if we are
+synthesizing an aspect of VTS, then all other aspects are fully given.
+%
+Therefore, we will describe two kinds of constraints for synthesis
+problems.
+%
+The first will encode the variable part in the synthesis problem and
+the other encodes the fixed parts.
+%
+Subsequently, the two constraints will be put together with 
+$\texttt{Consistancy}$ and 
+$\texttt{Property}$.
 
@@
 In the following, the pseudo-Boolean formula $\texttt{AddE}$ encodes
-that at most $slimit$ new undeclared edges may be added in VTS.
+that at most $slimit$ new undeclared edges may be added in the VTS.
 %
+\texttt{FixedForEdge} encodes the parts of the VTS that do not change.
 \begin{align*}
-  \texttt{AddE}(slimit) &= \Sigma~\texttt{UnknownE} \leq slimit\\
-  \texttt{FixedE} &= \texttt{UnknownActive} \land \lnot \Lor \texttt{UnknownELabel} \;\union\;
+  &\texttt{AddE}(slimit) = \sum~\texttt{UnknownE} \leq slimit\\
+  &\texttt{FixedForEdge} = \texttt{KnownCons} \land \texttt{UnknownActive} \land\\
+   & \quad\quad\quad\quad \lnot \Lor \texttt{UnknownELabel} \;\union\;
                     \texttt{UnknownNLabel} \;\union\;
@@
 \end{align*}
-We put together the constraints so far and obtain the following formula.
+We put together the constraints and obtain the following formula.
 \begin{align*}
-  & \texttt{SynthE}(slimit) = \\
-  & \quad\quad (  \texttt{Consistancy}\land \texttt{Property} \land
-  \texttt{KnownCons} \land \texttt{FixedE} \land
+  & \texttt{SynthE}(slimit) =
+     (  \texttt{Consistancy}\land \texttt{Property} \land
+   \texttt{FixedForEdge} \land
   \texttt{AddE}(slimit) )
@@
 As we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
-$\texttt{Property}$ encodes the goal, and $\texttt{KnownCons}$ are the constraints
-that are fixed in VTS.
+$\texttt{Property}$ encodes the goal, and
+the rest two are just defined constraints.
 %
@@
 %
-In the later synthesis problems, we will construct a similar QBF formula with same
-first three parts and the last one is due the requirements of the synthesis problem.
+In the later synthesis problems, we will construct a similar QBF
+formula with same first two parts and the last two are due the
+requirements of the synthesis problem.
 
@@
   &\texttt{AddLabelEdge}(slimit) = 
-    \Sigma~\texttt{UnknwonEdgeLabel}  \leq slimit\\
-  & \texttt{FixedForLabel} = \texttt{UnknownActive} \land \lnot \Lor \texttt{UnknownE} \;\union\;
+    \sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
+  & \texttt{FixedForLabel} = \texttt{KnownCons} \land \texttt{UnknownActive} \land\\
+  & \quad \quad \lnot \Lor \texttt{UnknownE} \;\union\;
                     \texttt{UnknownNLabel} \;\union\;
@@
     (  \texttt{Consistancy}\land \texttt{Property} \land
-  \texttt{KnownCons} \land \texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
+   \texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
 \end{align*} 
-Similar to the previous encoding we solve the satisfiability of the above formula
-to obtain additional molecules that may be added to the edge labels.
+Similar to the previous encoding we solve the
+satisfiability of the above formula to obtain additional molecules
+that may be added to the node labels.
+
+\subsubsection{Fixing VTS by learning activity functions:}
+
+Now we consider a scenario where some of the activity functions for some of the molecules
+are missing.
+%
+The activity functions are $\mu$-input Boolean functions.
+%
+We choose a class of formulas for the candidate functions.
+%
+We encode the candidates in a formula with parameters.
+%
+We choose different candidates by choosing values for the parameters.
+
+In the following, the formula \texttt{NNFTemplate} encodes a set of
+negation normal form functions that take $y_1,..,y_\mu$ as input and
+contain $\lambda$ literals.
+%
+We use $\texttt{Gate}$ to encode a gate that takes a parameter integer
+$x$ to encode various gates.
+%
+We use $\texttt{Leaf} $ to encode the literal at some position.
+%
+Both are stitched to define \texttt{NNFTemplate}.
+%
+To encode the set of NNF formulas with $\lambda$ literals, it has
+finite-range integer variables
+$z_1,..,z_{2\lambda}$ as parameters.
+
+% \paragraph{Encoding low depth cnf circuits}
+% \paragraph{Encoding boolean gates}
+
+\begin{align*}
+  &\texttt{Gate}( x, w_1, w_2 ) = ( x  = 1 \limplies w_1  \land w_2 ) \land  
+  ( x = 2  \limplies w_1  \lor w_2 ) \land
+  ( x = 3  \limplies w_1 ) \land ...\\
+  &\texttt{Leaf}( x, [y_1,..,y_\mu] ) =
+  \Land\limits_{l=1}^{\mu} ( x = 2l-1  \limplies y_{l}) \land ( x = 2l  \limplies \lnot y_{l})\\
+  &\texttt{NNFTemplate}([z_1,..,z_{2\lambda}],[y_1,..,y_\mu] ) = \\
+  &\exists w_1,..,w_{2\lambda}.\;w_1 \land \Land_{l=1}^{\lambda} w_{\lambda+l} = \texttt{Leaf}( z_{\lambda+l}, [y_1,..,y_\mu] ) \land
+  w_{l} = \texttt{Gate}( z_l, w_{2l},w_{2l+1})
+\end{align*}
+
+Using the template we define the constraints $\texttt{FindFunctions}(z,\lambda)$
+that encodes the candidate functions that satisfy the activity requirements,
+where $z$ is the vectors of parameters for encoding parameters
+for each molecule,
+and $\lambda$ limits the size of the candidate functions. 
+%
+We fix the all other aspect of the VTS to be fixed via constraints
+$\texttt{FixedForFunctions}$.
+%
+\begin{align*}
+  &\texttt{FindFunctions}(z,\lambda) =\\
+  &\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
+  \texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) |
+  \nodef_m \text{ is undefined}\} \\
+  &\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
+  \texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) | 
+  \edgef_m \text{ is undefined}
+  \}\\
+  & \texttt{FixedForFunctions} = \texttt{KnownCons} \land\\
+  & \quad \quad
+\lnot \Lor \texttt{UnknownE} \;\union\; \texttt{UnknownELabel} \;\union\;
+                    \texttt{UnknownNLabel} \;\union\;
+                    \texttt{UnknownP}\\
+  &\texttt{SynthFunction}(z,\lambda) = \\
+  & \quad\quad
+    (  \texttt{Consistancy}\land \texttt{Property} \land
+   \texttt{FixedForFunctions} \land \texttt{FindFunctions}(slimit) )
+\end{align*}
+We construct $\texttt{SynthFunction}(z,\lambda)$ similar to the earlier
+variations.
+%
+By reading of the values of $z$ in a satisfying model of the formula,
+we learn the synthesized function.
+
+\subsection{Repairing VTS:}
+%
+Now we will consider the repair of VTS by allowing not only addition but also
+deletion of the molecules, edges, functions, or pairing matrix.
+%
+We have encoded the vts repair in our tool by introducing flip bits
+for each variable that is modifiable in the VTS.
+%
+We illustrate the repairing on one class of variables and rest can be
+trivially extended.
+%
+Let us consider repairing of node labels.
+%
+For each bit $n_{i,m}$, we create a bit $flip_{i,m}$.
+%
+We add constraints that take xor of VTS assigned values for  $n_{i,m}$
+and $flip_{i,m}$.
+%
+We also limit how many times the $flip_{i,m}$ can be true, therefore
+limiting the number of flips.
+%
+Similar to the earlier variations, we construct
+$\texttt{SynthRepairNode}(slimit)$ for the repair.
+% 
+\begin{align*}
+    &\texttt{FlipN}(slimit) = \Land \{n_{i,m}\lxor flip_{i,m}| m \in \nlabel(i) \land i \in \nodes \} \land \\
+  & \quad \quad \quad
+    \Land \{ \lnot n_{i,m}\lxor flip_{i,m}| m \not \in \nlabel(i) \land i \in \nodes \} \land  \sum\limits_{i,m} flip_{i,m} \leq slimit \\
+% \\  
+    & \texttt{FixedForNodeRepair} =  \texttt{KnownE} \land  
+      \texttt{KnownP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
+      \land \\
+  & \quad \quad \texttt{UnknownActive} \land \lnot 
+    \Lor \texttt{UnknownE} \;\union\; \texttt{UnknownNLabel} \;\union\;
+    \texttt{UnknownP}\\
+  &\texttt{SynthRepairNode}(slimit) = \\
+  & \quad\quad
+    (  \texttt{Consistancy}\land \texttt{Property} \land
+    \texttt{FixedForNodeRepair} \land \texttt{FlipN}(slimit) )
+\end{align*}
 
@@
 
-\subsubsection{Fixing VTS by learning activity functions:}
-
-Now we consider a scenario where some of the activity functions for some of the molecules
-are missing.
-%
-The activity functions are $\mu$-input Boolean functions.
-%
-We choose a class of formulas for the candidate functions.
-%
-We encode the candidates in a formula with parameters.
-%
-We choose different candidates by choosing values for the parameters.
-
-The formula \texttt{NNFTemplate} encodes a set of negation normal form functions 
-that take $y_1,..,y_\mu$ as input and contain $\lambda$ literals.
-To encode the set, it also has finite-range integer variables
-$z_1,..,z_{2\lambda}$ as parameters to select the functions.
-
-% \paragraph{Encoding low depth cnf circuits}
-% \paragraph{Encoding boolean gates}
-
-\begin{align*}
-  \texttt{Gate}( z, w_1, w_2 ) = ( z  = 1 \limplies w_1  \land w_2 ) \land  
-  ( z = 2  \limplies w_1  \lor w_2 ) \land
-  ( z = 3  \limplies w_1 )\\
-  \texttt{Leaf}( z, [y_1,..,y_\mu] ) =
-  \Land\limits_{l=1}^{\mu} ( z = 2l-1  \limplies y_{l}) \land ( z = 2l  \limplies \lnot y_{l})\\
-  \texttt{NNFTemplate}([z_1,..,z_{2\lambda}],[y_1,..,y_\mu] ) = \\
-  \exists w_1,..,w_{2\lambda}.\;w_1 \land \Land_{l=1}^{\lambda} w_{\lambda+l} = \texttt{Leaf}( z_{\lambda+l}, [y_1,..,y_\mu] ) \land
-  w_{l} = \texttt{Gate}( z_l, w_{2l},w_{2l+1})
-\end{align*}
-
-Given the above templates
-
-\begin{align*}
-  &\texttt{FindFunctions}(z,\lambda) =\\
-  &\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
-  \texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) |
-  \nodef_m \text{ is undefined}\} \\
-  &\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
-  \texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) | 
-  \edgef_m \text{ is undefined}
-  \}
-\end{align*}
-
-\begin{align*}
-    & \texttt{FixedForLabel} = \lnot \Lor \texttt{UnknownE} \;\union\; \texttt{UnknownN} \;\union\;
-                    \texttt{UnknownNLabel} \;\union\;
-                    \texttt{UnknownP}\\
-  &\texttt{SynthFunction}(z,\lambda) = \\
-  & \quad\quad
-    (  \texttt{Consistancy}\land \texttt{Property} \land
-  \texttt{KnownCons} \land \texttt{FixedForFunctions} \land \texttt{FindFunctions}(slimit) )
-\end{align*}
-
-\subsection{Repairing VTS:}
-%
-Now we will consider the repair of VTS by allowing not only addition but also
-deletion of the molecules, edges, functions, or pairing matrix.
-%
-We illustrate the repairing on one class of variables and rest can be .....
-%
-The repair of the VTS requires both the addition and the deletion of
-the present molecules, node molecules pairing matrix and activity of
-the molecules. We have encoded the vts repair in our tool using the
-dummy xor bits.
-
 %%% Local Variables:

### 2018-05-01 papers/synth/intro.tex
paper

@@
 %
-Similarly, a molecule can be active in a channel. 
+Similarly, a molecule can be active or inactive in a channel. 
 %
@@
 Not all the pairs of molecules can participate in the fusion, the
-potential fusion pairs are usually determined by wet experiments.
+potential fusion pairs are usually determined by biological experiments.
 %
@@
 %
-A molecule that have participated in a fusion must not interfere
+A molecule that has participated in a fusion must not interfere
 with fusion at different compartments or channels.
@@
 The activity of molecules is regulated by the other molecules, i.e.,
-the presence and absence of the other molecule in a compartment or
-channel may make the active or inactive.
+the presence and absence of the other molecules in a compartment or
+channel may make the molecule active or inactive.
 %
@@
 It largely means that the current knowledge is due to the patch work
-of wet experiments~\cite{model} for identifying the compartments,
-channels, molecules, their activity, and regulatory control.
+of biological experiments~\cite{model} for identifying the compartments,
+channels, molecules, and their activity and regulatory control.
 %
@@
 %
-For example, we may suspect that some edges are missing in a VTS that
-does not satisfy the stability condition.
+For example, we may suspect that some edges may not have been
+discovered in a VTS that does not satisfy the stability condition.
 %
@@
 involving different parts of VTSs that can be synthesized, such as
-modifying labels, adding/deleting edges, learning activity functions,
-and adding nodes.
+modifying labels, adding/deleting edges, and learning activity functions.
 %
@@
 \item We have developed encoding of the synthesis problem in QBF.
-\item A user friendly and scalable tool based on well known SMT solver Z3
+\item A user friendly and scalable tool based on a well known SMT solver Z3
 \end{itemize}
@@
 %
-In section~\ref{sec:prelim}, we present the synthesis problems and their
+In section~\ref{sec:encoding}, we present the synthesis problems and their
 encoding into QBF satisfiability.

### 2018-05-01 papers/synth/prelim.tex
paper

@@
 %
-We will also present the constrains and properties on the VTSs.   
+We will also present the constrains and properties on the VTSs, and their
+encoding as a QBF formula.   
 %
@@
 %
-The analysis of the model will inform us the network/graph properties of
-VTSs.
+The analysis of the model will inform us about the network/graph
+properties of VTSs.
 
@@
 $P \subseteq M_1 \times M_2$, and
-for each $(n,M',n') \in \edges$, $n \neq n'$, 
+for each $(n,M',n') \in \edges$, $n \neq n'$ and
 $M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
 %
-In other words, a well-structured VTS has no self loops, and 
+In other words,
+no molecule can participate in fusion from both channels and
+compartments,
+%
+there are no self loops, and 
 each edge carry only those molecules that are present in its source
@@
 %
-To encode the constraints, we need needs variables for each aspect of
+To encode the constraints, we need variables for each aspect of
 VTS.
@@
 %
-Furthermore, we also limit the maximum number $\pi$ of edges present
-between two nodes.
+To fully finitize the problem, we also limit the maximum number $\pi$
+of edges present between two nodes.
 %
@@
 The following constraints encode the basic consistency of VTSs.
-\begin{align}
-  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
+\begin{align*}
+  \texttt{EdgeC} =\;& \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
   \land
@@
   \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
-  \tag{\texttt{EdgeC}}\label{eq:c0}\\
+  \\
+  \texttt{ActivityC} =\;&
   \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
@@
   % \tag{V2}\label{eq:f1}\\
-  \tag{\texttt{ActivityC}}\label{eq:c4}\\
+  \\
+  \texttt{PairingC} =\;&
   \bigwedge\limits_{m} 
@@
   (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
-  \tag{\texttt{PairingC}}\label{eq:c3}\\
+  \\
+  \texttt{Fusion1} =\;&
   \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
   \bigvee_{\mathclap{m,m^{\prime}}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
-  \tag{\texttt{Fusion1}}\label{eq:fuse1} \\
+  \\
+  \texttt{Fusion2} =\;&
 \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies \neg 
   \bigvee_{\mathclap{j \neq j^{\prime}, m^{\prime\prime}}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
-  \tag{\texttt{Fusion2}}\label{eq:fuse2} \\
-  \texttt{EdgeC} \land
+  \\
+  \texttt{Consistancy} =\;& \texttt{EdgeC} \land
   \texttt{ActivityC} \land \texttt{PairingC} \land
   \texttt{Fusion1} \land \texttt{Fusion2} 
-  \tag{\texttt{Consistancy}}\label{eq:c3}
-\end{align}
+\end{align*}
 \texttt{EdgeC} states that each edge has at least one molecule,
@@
 \paragraph{Activity functions}
-We also need to encode that encode that
+We also need to encode that
 the activity of the molecules are controlled by activity functions.
@@
 %
-In the following constraints, we assume the appropriate encoding is
-used for the functions.
+In the following section, we will assume the appropriate encoding is
+used for the functions and represent them by \texttt{NodeFun}$_m$
+and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
 %
-\begin{align}
-\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
-\tag{\texttt{ActiveNode}}\label{eq:anb}\\
-   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
-  \tag{\texttt{ActiveEdge}}\label{eq:aeb}
-\end{align}
+We will use $\nodef_m$ and $\edgef_m$ to represent functions that
+are not defined in VTS.
+%
+% \begin{align}
+% \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
+% \tag{\texttt{ActiveN}}\label{eq:anb}\\
+%    \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
+%   \tag{\texttt{ActiveE}}\label{eq:aeb}
+% \end{align}
 %
 Later we will be synthesizing missing activity functions and 
-replace the above constraints with parameterized constraints that
+replace $\nodef_m$ and $\edgef_m$ with parameterized constraints that
 encode a space of candidate functions.

### 2018-05-01 papers/synth/abstract.tex

@@
 The compartments are viewed as nodes that are labeled with the
-containing chemicals and the transport channels are similarly labeled
-edges between the nodes.
+containing chemicals and the transport channels
+are similarly viewed as labeled edges between the nodes.
 %

### 2018-05-01 papers/synth/prelim.tex

@@
 We will use $\nodef_m$ and $\edgef_m$ to represent functions that
-are not defined in VTS.
+are not defined in a VTS.
 %
@@
 For synthesis of incomplete systems,
-we need properties properties against which we synthesize the missing parts.
+we need properties  against which we synthesize the missing parts.
 %
 Here we will discussed two such properties proposed in earlier
-works~\cite{SASBpaper}.
+works~\cite{SASBpaper}, namely stability and $k$-connectedness.
 %
@@
 %
-$k$-connectedness is a robustness property.
+$k$-connectedness expresses robustness against failure of few edges.
 %
-Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is dropped
+Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
 and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
@@
 In the following, $\texttt{Drop}(d,k)$  encode that only
-existing edges can be dropped and exactly $k-1$ edges are dropped.
+existing edges can be failed and exactly $k-1$ edges are failed.
 %
-$\texttt{Reach}(d,r')$ defines reachability in the modified VTS,
+Both $\texttt{ReachBelow}(d,r')$ and $\texttt{ReachAbove}(d,r')$ defines
+reachability in the modified VTS,
 therefore we use a new variable $r'_{i,j}$ to encode reachability from
@@
 \end{align*}
-We will be synthesizing for both connected any disconnected graphs.
+We will be synthesizing for both connected and disconnected graphs.
 %
-We also define the following macros. 
+We define the following macros. 
 \begin{align*}
@@
 Since the free variables in $\texttt{Connectedness}(k)$ are universally
-quantified, please note that the connectedness property introduces the two
+quantified, the connectedness property introduces the two
 quantifier alternations.

### 2018-05-02 papers/synth/encoding.tex
paper
clean up pass

@@
-In this section, we will present a list of problems that may arise from
-synthesis of VTSs from partial available information
-and our method for completing the missing parts.
+%
+In this section, we will present a list of synthesis problems that may
+arise from partial available information about a VTS and our solution
+for the problems.
 
@@
 %
-The missing information can be in any of these combinations parts of
-VTS. For example existence of some undiscovered edges or nodes, or
-insufficient knowledge about the presence of molecules in some part of
-the VTS (either on the node or on the edge).
+The missing parts can be in any of the components of VTS. 
 %
-To cover most of the likely variations of this missing information we
-have encoded the following variants of VTS synthesis.
+For example, some undiscovered edges or nodes, or insufficient
+knowledge about the presence of molecules in some part of the VTS.
+%
+To cover most of the likely variations of this missing information,
+we have encoded the following variants of VTS synthesis problem.
 
 \begin{enumerate}
-\item  Add new edges 
-\item  Modify the flow of molecules on the nodes and on the edges.
-  % \begin{enumerate}
-  % \item use available set of molecules.
-  % \item allow new molecule type to be added.     
-  % \end{enumerate}        
-\item Learning meaningful activity functions from a given language of
-  propositional formulas
+\item Fixing VTS by adding edges 
+\item Fixing VTS by adding molecules to the labels
+\item Fixing VTS by learning activity functions
   % \begin{enumerate}
@@
   % - Function dependence with var occurring once.
-\item  VTS repair. Allow both delete and add to the system.
+\item  Fixing VTS by both adding/deleting parts
 \end{enumerate}
@@
 %
-We allow activity functions not to be specified, i.e., vectors
-$\edgef$ and $\nodef$ may contain uninterpreted Boolean functions.
+We allow activity functions not to be specified.
 %
@@
 \begin{align*}
-  \texttt{KnownE} &= \land \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land q \leq q' \land m \in M_q \}\\
-  \texttt{KnownN} &= \land \{n_{i,m}| m \in \nlabel(i) \land i \in \nodes \}\\
-  \texttt{KnownP} &= \land \{p_{i,j}| (i,j) \in \pairs \} \\
-  \texttt{KnownActiveN} &= \land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is defined.} \} \\
-  \texttt{KnownActiveE} &= \land \{ b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
+  \texttt{PresentE} &= \land \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land q \leq q' \land m \in M_q \}\\
+  \texttt{PresentN} &= \land \{n_{i,m}| m \in \nlabel(i) \land i \in \nodes \}\\
+  \texttt{PresentP} &= \land \{p_{i,j}| (i,j) \in \pairs \} \\
+  \texttt{KnownActiveN} &= \land \{ a_{i,m} = \texttt{NodeFun}_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is defined.} \} \\
+  \texttt{KnownActiveE} &= \land \{ b_{i,j,q,m} = \texttt{EdgeFun}_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
                    | \edgef_m \text{ is defined.} \} \\
-  \texttt{KnownCons} & = \texttt{KnownE} \land \texttt{KnownN} \land 
- \texttt{KnownP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
+  \texttt{PresentCons} & = \texttt{PresentE} \land \texttt{PresentN} \land 
+ \texttt{PresentP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
 \end{align*}
-We also collect the variables that are not set to true in $\texttt{KnownCons}$.
+We also collect the variables that are not set to true in $\texttt{PresentCons}$.
 \begin{align*}
-  \texttt{UnknownELabel} &=
+  \texttt{AbsentELabel} &=
   \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
                           0 < q \leq q' \land m \not\in M_{q} \}\\
-  \texttt{UnknownE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
+  \texttt{AbsentE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
                     q' < q \leq \pi \}\\
-  \texttt{UnknownNLabel} &= \{n_{i,m}| m \not\in \nlabel(i) \land i \in \nodes \}\\
-  \texttt{UnknownP} &= \{p_{i,j}| (i,j) \not\in \pairs \} \\
+  \texttt{AbsentNLabel} &= \{n_{i,m}| m \not\in \nlabel(i) \land i \in \nodes \}\\
+  \texttt{AbsentP} &= \{p_{i,j}| (i,j) \not\in \pairs \} \\
   \texttt{UnnownActive} &=  \Land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is undefined.} \} \union \\
@@
 \end{align*}
-We have defined $\texttt{UnknownE}$, $\texttt{UnknownN}$, and
-$\texttt{UnknownP}$
-as set and will be converted into formulas depending
+We have defined $\texttt{AbsentELabel}$, $\texttt{AbsentE}$, $\texttt{AbsentN}$, and
+$\texttt{AbsentP}$
+as sets.
+%
+They will be converted into formulas depending
 on the different usage in the synthesis problems.
@@
 We will do synthesis against the following property that says the VTS
-is stable and 3-connected, but not 4-connected.
+is stable and 3-connected.
 %
-The property is designed to balance the search space such that the synthesis procedure does not
-succeed with simply adding too many edges. 
+% The property is designed to balance the search space such that the synthesis procedure does not
+% succeed with simply adding too many edges. 
 %
 \begin{align*}
-  \texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) \land \texttt{DisConnected}(4)
+  \texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
+  %\land \texttt{DisConnected}(4)
 \end{align*}
+The property was proposed in~\cite{plos}.
+%
+However, the biological relevance of the property is debatable and open for change.
+%
+Our tool is easily modifiable to support any other property that may be deemed 
+interesting by the biologists.
 
@@
 
-Now we will consider the encodings for  the above
+Now we will consider the encodings for the
 listed synthesis problems.
@@
 %
-The first will encode the variable part in the synthesis problem and
+One will encode the variable part in the synthesis problem and
 the other encodes the fixed parts.
@@
 $\texttt{Consistancy}$ and 
-$\texttt{Property}$.
+$\texttt{Property}$ to construct the constraints for synthesis.
 
@@
 %
-\texttt{FixedForEdge} encodes the parts of the VTS that do not change.
+\texttt{FixedForEdge} encodes the parts of the VTS that are not allowed to change.
 \begin{align*}
-  &\texttt{AddE}(slimit) = \sum~\texttt{UnknownE} \leq slimit\\
-  &\texttt{FixedForEdge} = \texttt{KnownCons} \land \texttt{UnknownActive} \land\\
-   & \quad\quad\quad\quad \lnot \Lor \texttt{UnknownELabel} \;\union\;
-                    \texttt{UnknownNLabel} \;\union\;
-                    \texttt{UnknownP}
+  &\texttt{addE}(slimit) = \sum~\texttt{AbsentE} \leq slimit\\
+  &\texttt{fixedForEdge} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
+   & \quad\quad\quad\quad \lnot \Lor \texttt{AbsentELabel} \;\union\;
+                    \texttt{AbsentNLabel} \;\union\;
+                    \texttt{AbsentP}
 \end{align*}
-We put together the constraints and obtain the following formula.
+We put together the constraints and obtain the following formula $\texttt{synthE}(slimit)$.
 \begin{align*}
-  & \texttt{SynthE}(slimit) =
-     (  \texttt{Consistancy}\land \texttt{Property} \land
-   \texttt{FixedForEdge} \land
-  \texttt{AddE}(slimit) )
+  & \texttt{synthE}(slimit) =
+       \texttt{consistancy}\land \texttt{property} \land
+   \texttt{fixedForEdge} \land
+  \texttt{addE}(slimit)
   % \tag{SynthE}\label{eq:addedge1}
 \end{align*}
-As we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
-$\texttt{Property}$ encodes the goal, and
-the rest two are just defined constraints.
+As we have seen $\texttt{consistancy}$ encodes the basic constraints about VTS,
+$\texttt{property}$ encodes the goal, and
+the rest two are defined just above.
 %
-A satisfying model of $\texttt{SynthE}$ will represent the synthesized VTS.
+A satisfying model of $\texttt{synthE}$ will make 
+some of the edges in $\texttt{AbsentE}$ true such that~$\texttt{property}$ is satisfied.
 %
+We limit the addition of the edges, since we look for a fix that require minimum number
+of changes in the given VTS.
+%
+We start with $slimit = 1$ and grow one by one until $\texttt{synthE}(slimit)$
+becomes satisfiable.
+
 In the later synthesis problems, we will construct a similar QBF
@@
 requirements of the synthesis problem.
-
-We limit the addition of the edges, since we look for a fix that require minimum number
-of changes in the given VTS.
-%
-We start with $slimit = 1$ and grow one by one until $\texttt{SynthE}(slimit)$
-becomes satisfiable.
 
@@
 %
+Here let us consider only adding molecules to the labels of edges.
+%
 In the following, the formula encodes that only $slimit$ edge labels may be added.
@@
     \sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
-  & \texttt{FixedForLabel} = \texttt{KnownCons} \land \texttt{UnknownActive} \land\\
-  & \quad \quad \lnot \Lor \texttt{UnknownE} \;\union\;
-                    \texttt{UnknownNLabel} \;\union\;
-                    \texttt{UnknownP}\\
+  & \texttt{FixedForLabel} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
+  & \quad \quad \lnot \Lor \texttt{AbsentE} \;\union\;
+                    \texttt{AbsentNLabel} \;\union\;
+                    \texttt{AbsentP}\\
   &\texttt{SynthLabel}(slimit) = \\
@@
 \end{align*} 
-Similar to the previous encoding we solve the
+Similar to the previous encoding, we solve the
 satisfiability of the above formula to obtain additional molecules
-that may be added to the node labels.
+that may be added to the edge labels to satisfy the properties.
 
@@
 %
-We choose a class of formulas for the candidate functions.
+First, we choose a class of formulas for the candidate functions.
 %
@@
 %
-We choose different candidates by choosing values for the parameters.
+By assigning different values for the parameters, a solver may select
+different candidates for the activity functions.
+%
+We will illustrate only one class of formulas.
+%
+However, we support other classes of formulas for example $k$-CNF.
 
@@
   \}\\
-  & \texttt{FixedForFunctions} = \texttt{KnownCons} \land\\
+  & \texttt{FixedForFunctions} = \texttt{PresentCons} \land\\
   & \quad \quad
-\lnot \Lor \texttt{UnknownE} \;\union\; \texttt{UnknownELabel} \;\union\;
-                    \texttt{UnknownNLabel} \;\union\;
-                    \texttt{UnknownP}\\
+\lnot \Lor \texttt{AbsentE} \;\union\; \texttt{AbsentELabel} \;\union\;
+                    \texttt{AbsentNLabel} \;\union\;
+                    \texttt{AbsentP}\\
   &\texttt{SynthFunction}(z,\lambda) = \\
@@
 
-\subsection{Repairing VTS:}
+\subsection{Fixing VTS by both adding/deleting parts:}
 %
-Now we will consider the repair of VTS by allowing not only addition but also
+Now we will consider repairing of VTS by allowing not only addition but also
 deletion of the molecules, edges, functions, or pairing matrix.
 %
-We have encoded the vts repair in our tool by introducing flip bits
+We have encoded the repairing in our tool by introducing flip bits
 for each variable that is modifiable in the VTS.
@@
 We illustrate the repairing on one class of variables and rest can be
-trivially extended.
+easily extended.
 %
@@
 %
+The above constraints are encoded in $\texttt{FlipN}(slimit)$.
+\begin{align*}
+    &\texttt{FlipN}(slimit,flip) = \Land \{n_{i,m}\lxor flip_{i,m}| m \in \nlabel(i) \land i \in \nodes \} \land \\
+  & \quad \quad \quad
+    \Land \{ \lnot n_{i,m}\lxor flip_{i,m}| m \not \in \nlabel(i) \land i \in \nodes \} \land  \sum\limits_{i,m} flip_{i,m} \leq slimit
+\end{align*}
+%
 Similar to the earlier variations, we construct
@@
 %
+In that, $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
 \begin{align*}
-    &\texttt{FlipN}(slimit) = \Land \{n_{i,m}\lxor flip_{i,m}| m \in \nlabel(i) \land i \in \nodes \} \land \\
-  & \quad \quad \quad
-    \Land \{ \lnot n_{i,m}\lxor flip_{i,m}| m \not \in \nlabel(i) \land i \in \nodes \} \land  \sum\limits_{i,m} flip_{i,m} \leq slimit \\
 % \\ 
-    & \texttt{FixedForNodeRepair} =  \texttt{KnownE} \land  
-      \texttt{KnownP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
+    & \texttt{FixedForNodeRepair} =  \texttt{PresentE} \land  
+      \texttt{PresentP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
       \land \\
   & \quad \quad \texttt{UnknownActive} \land \lnot 
-    \Lor \texttt{UnknownE} \;\union\; \texttt{UnknownNLabel} \;\union\;
-    \texttt{UnknownP}\\
-  &\texttt{SynthRepairNode}(slimit) = \\
+    \Lor \texttt{AbsentE} \;\union\; \texttt{AbsentNLabel} \;\union\;
+    \texttt{AbsentP}\\
+  &\texttt{SynthRepairNode}(slimit,flip) = \\
   & \quad\quad
     (  \texttt{Consistancy}\land \texttt{Property} \land
-    \texttt{FixedForNodeRepair} \land \texttt{FlipN}(slimit) )
+    \texttt{FixedForNodeRepair} \land \texttt{FlipN}(slimit,flip) )
 \end{align*}
-
-% We encode the \texttt{ModifyCons} by putting the constraints on the
-% unassigned edges and edge labels. The constraint of allowing only
-% certain number of addition to the given VTS is encoded as
-% \texttt{AtMostK} function over the unassigned edges and label.
-
-%\[Unassigned Edges\]}
-%\[Unassigned Activity Labels\]} 
-%\[Unassigned Molecule Labels\]
-% \begin{align}
-%    \texttt{EdgeConstraint} = \texttt{AtMostk} \, [ \texttt{unassigned\_edges} ]  
-%    \tag{E2}\label{eq:addedge2}
-% \end{align}
-% \begin{align}
-%    \texttt{EdgeActivity} = \texttt{AtMostK} \, [ \texttt{activity\_labels} ]
-%    \tag{E3}\label{eq:addedge3}
-% \end{align}
-
-% \begin{align}
-%    \texttt{EdgePresence} = \texttt{AtMostK} \, [ \texttt{unassigned\_molecule\_labels} ]  
-%    \tag{E4}\label{eq:addedge4}
-% \end{align}
-
-% Put \ref{eq:addedge2} in symbolic form and explain it in a couple of lines.
-
-% In order to decrease the search space we do not allow any modification in the node label and activity on the nodes. This constraint can be encoded as the fixing all the unassigned bits to false.
-
-% %    // Fix rest of them to zero.
-% %    auto fixVar0 = ! z3::mk_or ( openN )  && ! z3::mk_or ( openActiveN );
-
-% \begin{align}
-%   \exists i, j, q \,
-%   ( \texttt{KConnectivity}  \land \texttt{NoSelfEdge} \land \ref{eq:addedge1} )    
-%   \tag{E5}\label{eq:addedge5}
-% \end{align}
-
-% The \texttt{KConnectivity} and \texttt{NoSelfEdge} are same as the previous section, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS.
-addedge1 is the constraint of \ref{eq:addedge1}.
-
-%{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-
- %   auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;
-
-% %   auto qvtsCons = exists( setN, 
-%                    exists( setActiveN, 
-%                    exists( setPresenceE,  
-%                    exists( setActiveE, 
-%                    exists( setPairingM, 
-%                    exists( setReach, 
-%                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));
+A satisfying model of $\texttt{SynthRepairNode}(slimit,flip)$ will assign some
+$flip$ bits to true.
+We will learn from the assignments the needed modifications in the VTS.
 

### 2018-05-02 papers/synth/prelim.tex
clean up pass

@@
 %
-The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps.
+The following constraint recursively encodes that node $j$ is
+$m$-reachable from node $i$ in less than $p$ steps.
 %
@@
 %
-In the following, $\texttt{Drop}(d,k)$  encode that only
+In the following, $\texttt{Fail}(d,k)$ encodes that only
 existing edges can be failed and exactly $k-1$ edges are failed.
 %
-Both $\texttt{ReachBelow}(d,r')$ and $\texttt{ReachAbove}(d,r')$ defines
-reachability in the modified VTS,
-therefore we use a new variable $r'_{i,j}$ to encode reachability from
-$i$ to $j$.
+$\texttt{FailReach}(d,r')$ defines reachability in the modified VTS.
+%
+We use a new variable $r'_{i,j,p}$ to encode reachability from
+$i$ to $j$ in at most $p$ steps.
 %
@@
 other node.
-% In the following constraint, we encode $r'_{i,j}$ is true if there is an
-% edge $(i,\_,j)$ and it is not dropped, or there is a node
-% $i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
-% not dropped and $r'_{i',j}$ is true.
 \begin{align*}
-  \texttt{Drop}(d,k) = & 
+  \texttt{fail}(d,k) = & 
   \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
   \sum_{i,j,q} d_{i,j,q} = k-1\\
-  \texttt{ReachAbove}(d,r') = &
-  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
-  \texttt{ReachBelow}(d,r') = &
-   \bigwedge\limits_{i,j}  r^{\prime}_{i,j} \limplies [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
-  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
+  % \texttt{ReachAbove}(d,r') = &
+  % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
+  \texttt{failReach}(d,r') = &
+   \bigwedge\limits_{i,j,p}  r^{\prime}_{i,j,p} \limplies [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
+  \texttt{connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
 \end{align*}
-We will be synthesizing for both connected and disconnected graphs.
+We will be synthesizing $k$-connected graphs.
 %
-We define the following macros. 
+We define $\texttt{connected}(k)$ that says for all possible valid failures
+the graph remains reachable. 
 \begin{align*}
-  \texttt{Connected}(k) = & \forall d.\;
-          (\texttt{Drop}(d,k) \limplies \exists r'.\;\texttt{ReachBelow}(d,r')
-                                \land \texttt{Connected}(r'))\\
-  \texttt{Disconnected}(k) = & \exists d.\;
-          (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
-                                \land \lnot \texttt{Connected}(r'))
+  \texttt{connected}(k) = & \forall d.\;
+          (\texttt{fail}(d,k) \limplies \exists r'.\;\texttt{failReach}(d,r')
+                                \land \texttt{connected}(r'))
+% \\
+  % \texttt{Disconnected}(k) = & \exists d.\;
+  %         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
+  %                               \land \lnot \texttt{Connected}(r'))
 \end{align*}
-Since the free variables in $\texttt{Connectedness}(k)$ are universally
-quantified, the connectedness property introduces the two
-quantifier alternations.
+Since $d$ variables in $\texttt{connected}(k)$ are universally
+quantified, $\texttt{connected}(k)$ introduces quantifier alternations.
 %

### 2018-05-02 papers/synth/conclusion.tex
asd

@@
-In this paper, we presented the encoding of the synthesis problems
+In this paper, we presented encodings of the synthesis problems
 that may rise from VTSs.
 %
-We demonstrated that our tool scale up to the relevant sizes of the
-VTSs. 
+We demonstrated that our tool based on the encodings
+scale up to the relevant sizes of the VTSs. 
 %

### 2018-05-02 papers/synth/prelim.tex
as

@@
   \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes,
-  \item $\pairs \subseteq \mols \times \mols$ is pairing relation,
+  \item $\pairs \subseteq 2^{\mols}$ is pairing relation,
   \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes, and
@@
 
-Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
+% Let $\pairs(M')$ denote $\{P\setminus M'|  P \in \pairs \text{ and } P \intersect M' \neq \emptyset \}$.
 %
@@
 We call $G$ {\em well-structured} if molecules $M$ is divided into
-two equal-sized partitions $M_1$ and $M_2$ such that
-$P \subseteq M_1 \times M_2$, and
+two partitions $Q$ and $R$ such that
+for each $P \in \pairs, |P \intersect Q| \leq 3 \land |P \intersect R| = 1 $, and
 for each $(n,M',n') \in \edges$, $n \neq n'$ and
@@
 %
-An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
-if there are molecules $m,m' \in \mols$ such that $m$ is active in
-$(n,M',n')$, $m'$ is active in $n'$, and $(m,m') \in \pairs$.
+An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
+if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
+such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
 %
 We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
-with non-empty fusing molecules $M'' \subseteq M'$
-and $\pairs(M'')$ are not active in any other node.
+with its destination node $n'$
+and can not fuse with any other node.
+
+% $\pairs(M'')$ are not active in any other node.
 
@@
 \item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
-\item Boolean variable $p_{m,m'}$ indicates if $(m,m') \in \pairs$
+\item Boolean variable $p_{m_1,m_2,m_3,m'}$ indicates if $\{m_1,m_2,m_3,m'\} \in \pairs$
 \item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
@@
   \texttt{PairingC} =\;&
-  \bigwedge\limits_{m} 
-  (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
-  (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
+  \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
+                         (p_{m_1,m_2,m_3,m_4} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) \land\\ 
+  & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
+  % \bigwedge\limits_{m} 
+  % (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
+  % (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
   \\
@@
   \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
-  \bigvee_{\mathclap{m,m^{\prime}}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
+  \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
+                        \sum_{l=1}^4 b_{i,j,q,m_l} > 0 \land\\
+  & \qquad \qquad \qquad \qquad \sum_{l=1}^4 a_{j,m_l} > 0 \land p_{m_1,m_2,m_3,m_4})
   \\
   \texttt{Fusion2} =\;&
-\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies \neg 
-  \bigvee_{\mathclap{j \neq j^{\prime}, m^{\prime\prime}}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
+\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \neg 
+  \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
+\land a_{j^{\prime},m_4^{\prime}} \land p_{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4})
   \\

### 2018-05-02 papers/synth/encoding.tex
caps

@@
 \begin{align*}
-  &\texttt{addE}(slimit) = \sum~\texttt{AbsentE} \leq slimit\\
-  &\texttt{fixedForEdge} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
+  &\texttt{AddE}(slimit) = \sum~\texttt{AbsentE} \leq slimit\\
+  &\texttt{FixedForEdge} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
    & \quad\quad\quad\quad \lnot \Lor \texttt{AbsentELabel} \;\union\;
@@
 \end{align*}
-We put together the constraints and obtain the following formula $\texttt{synthE}(slimit)$.
+We put together the constraints and obtain the following formula $\texttt{SynthE}(slimit)$.
 \begin{align*}
-  & \texttt{synthE}(slimit) =
-       \texttt{consistancy}\land \texttt{property} \land
-   \texttt{fixedForEdge} \land
-  \texttt{addE}(slimit)
+  & \texttt{SynthE}(slimit) =
+       \texttt{Consistancy}\land \texttt{Property} \land
+   \texttt{FixedForEdge} \land
+  \texttt{AddE}(slimit)
   % \tag{SynthE}\label{eq:addedge1}
 \end{align*}
-As we have seen $\texttt{consistancy}$ encodes the basic constraints about VTS,
-$\texttt{property}$ encodes the goal, and
+As we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
+$\texttt{Property}$ encodes the goal, and
 the rest two are defined just above.
 %
-A satisfying model of $\texttt{synthE}$ will make 
-some of the edges in $\texttt{AbsentE}$ true such that~$\texttt{property}$ is satisfied.
+A satisfying model of $\texttt{SynthE}$ will make 
+some of the edges in $\texttt{AbsentE}$ true such that~$\texttt{Property}$ is satisfied.
 %
@@
 %
-We start with $slimit = 1$ and grow one by one until $\texttt{synthE}(slimit)$
+We start with $slimit = 1$ and grow one by one until $\texttt{SynthE}(slimit)$
 becomes satisfiable.

### 2018-05-02 papers/synth/prelim.tex
caps

@@
 \item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
-\item Boolean variable $p_{m_1,m_2,m_3,m'}$ indicates if $\{m_1,m_2,m_3,m'\} \in \pairs$
+\item Boolean variable $p_{m_1,m_2,m_3,m_4}$ indicates if $\{m_1,m_2,m_3,m_4\} \in \pairs$
 \item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
@@
 \begin{align*}
-  \texttt{paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+  \texttt{Paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
   \\
-  \texttt{loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
+  \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
   \\
-  \texttt{stability} &= \exists r. \; \texttt{paths}(r) \land \texttt{loop}(r)
+  \texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
 \end{align*}
@@
 \begin{align*}
-  \texttt{fail}(d,k) = & 
+  \texttt{Fail}(d,k) = & 
   \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
@@
   % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
-  \texttt{failReach}(d,r') = &
+  \texttt{FailReach}(d,r') = &
    \bigwedge\limits_{i,j,p}  r^{\prime}_{i,j,p} \limplies [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
-  \texttt{connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
+  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
 \end{align*}
@@
 %
-We define $\texttt{connected}(k)$ that says for all possible valid failures
+We define $\texttt{Connected}(k)$ that says for all possible valid failures
 the graph remains reachable. 
 \begin{align*}
-  \texttt{connected}(k) = & \forall d.\;
-          (\texttt{fail}(d,k) \limplies \exists r'.\;\texttt{failReach}(d,r')
-                                \land \texttt{connected}(r'))
+  \texttt{Connected}(k) = & \forall d.\;
+          (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FailReach}(d,r')
+                                \land \texttt{Connected}(r'))
 % \\
@@
 \end{align*}
-Since $d$ variables in $\texttt{connected}(k)$ are universally
-quantified, $\texttt{connected}(k)$ introduces quantifier alternations.
+Since $d$ variables in $\texttt{Connected}(k)$ are universally
+quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
 %

### 2018-05-02 vts-synth/src/main.cpp
runtime added

@@ -10,6 +10,7 @@
 #include <unistd.h>
 #include <chrono>
 #include <ctime>
+//#include <time.h>
 
 #include <boost/program_options/options_description.hpp>
 #include <boost/program_options/parsers.hpp>
@@ -142,6 +143,9 @@ int main(int ac, char* av[])
     
   z3::context c;
 
+  // Record start time
+  auto start = std::chrono::high_resolution_clock::now();
+  
   //std::cout << useZ3;
   //std::cout << vm["func-model"].as<int>() << "\n";            
   //exit(0);
@@ -284,7 +288,10 @@ int main(int ac, char* av[])
       return 1;
     }
     if ( status == std::future_status::ready ) { 
-      std::cout << "Program run was sucessful! ";
+      std::cout << "Program run was sucessful!\n";
+      auto finish = std::chrono::high_resolution_clock::now();
+      std::chrono::duration<double> elapsed = finish - start;
+      std::cout << "entire run took " << elapsed.count() << " secs\n";
     }
 
     v->print_graph( c, "/tmp/dep_vts.dot", qs, printModel, displayGraph, synthVar ); 
@@ -315,8 +322,7 @@ int main(int ac, char* av[])
 catch (z3::exception & ex) {
 std::cout << "Nuclear Missles are launched ----> " << ex << "\n";
 }
-
-return 0;
+  return 0;
 }
 
 

### 2018-05-02 vts-synth/src/vts.cpp

@@ -467,6 +467,27 @@ z3::expr vts::no_self_edges() {                              //V5
 
 // V6: Only Q R entry has possible non zero entry.
 
+
+
+/*
+unsigned qSnareCount = 23;
+//unsigned rSnareCount = M - 7;
+z3::expr vts::restriction_on_pairing_matrix() {              //V6
+  z3::expr_vector ls(ctx);
+  z3::expr e(ctx);
+  for( unsigned x = 0 ; x < M; x++ ) {
+    for( unsigned y = 0 ; y < M; y++ ) {
+      if ( ((x < qSnareCount) && (y < qSnareCount)) || ((x >= qSnareCount) && (y >= qSnareCount)) ) {
+        e = !pairing_m[x][y];
+        ls.push_back( e );
+      }
+    }
+  }
+  return z3::mk_and( ls );
+}
+
+*/
+
 z3::expr vts::restriction_on_pairing_matrix() {              //V6
   z3::expr_vector ls(ctx);
   z3::expr e(ctx);
@@ -480,7 +501,6 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   }
   return z3::mk_and( ls );
 }
-
 
 // V7 : There should be an active pair corresponding to pairing matrix
 z3::expr vts::edge_must_fuse_with_target() {                 //V7

### 2018-05-03 papers/synth/experiments.tex
running timw

\begin{table}[t]
  \centering
  \begin{tabular}[t]{|c|c|c|c|c|c|c|c|c|c|c}\hline
    {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth Cnf}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline

   \cline{2-9}
    {} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} \\\hline

    plos1-dia[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 0.0492 & 0.0\\\hline
    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & \0.042 \\\hline
%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
    mukund[3/4C] & 0.3809 & 0.0 & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
    node4[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 2.194 & 0.0\\\hline
    yeast-graph & 0.0 & 0.0 & 0.0 & 0.00 & 0.0 & 0.0 & 0.0  & 0.0 & 0.0 & 0.0 \\\hline
    mukund-comp & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs).}
  \label{tab:qf-grabh}
\end{table}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-05-03 vts-synth/src/vts-synthesis.cpp

@@ -367,12 +367,13 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
 
   // 1. Add edge to achieve graph stability and k connected. 
   if ( variation == 1 ) {   
-    auto edgeC = !at_least_four( unknownE );
+    auto edgeC = !at_least_two( unknownE );
     auto edgeActivityC = !at_least_three( unknownActiveE );
     auto edgePresenceC = !at_least_three( unknownPresenceE );
     
     // fix all unknwon bits to false.
-    auto setUnknownVariablesFalse = !z3::mk_or( unknownN )  && !z3::mk_or( unknownActiveN );
+    auto setUnknownVariablesFalse = !z3::mk_or( unknownN )  && !z3::mk_or( unknownActiveN ) 
+                                   && !z3::mk_or( unknownE ) && !z3::mk_or( unknownPresenceE ) && !z3::mk_or( unknownActiveE );
     
     auto addConstraints = edgeC && edgeActivityC && edgePresenceC;
 
@@ -382,10 +383,10 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
                     exists( listActiveE, 
                     exists( listPairingM, 
                     exists( listReach, 
-                            vtsCons && knownVarConstraint ))))));   
+                            vtsCons && knownVarConstraint && setUnknownVariablesFalse ))))));   
 
     auto cons = exists( listE, 
-                        qvtsCons && V5 && kConnCons ); 
+                        qvtsCons && V5 ); 
     return cons;
   }
 
@@ -396,20 +397,23 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     z3::expr edgePresenceC = !at_least_three( unknownPresenceE );
     z3::expr addConstraints = edgeActivityC && edgePresenceC;
 
+
     // fix all unknwon bits to false.
-    z3::expr setUnknownVariablesFalse = !z3::mk_or( unknownActiveN ) && !z3::mk_or( unknownE );
-    
+    //z3::expr setUnknownVariablesFalse = !z3::mk_or( unknownActiveN ) && !z3::mk_or( unknownE );
+    auto setUnknownVariablesFalse = !z3::mk_or( unknownN )  && !z3::mk_or( unknownActiveN ) 
+                                   && !z3::mk_or( unknownE ) && !z3::mk_or( unknownPresenceE ) && !z3::mk_or( unknownActiveE );
+
     z3::expr qvtsCons = exists( listN, 
                         exists( listActiveN, 
[…]

### 2018-05-03 papers/synth/experiments.tex
vts example and conn

@@
     plos1-dia[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 0.0492 & 0.0\\\hline
-    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & \0.042 \\\hline
+    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & 0.042 \\\hline
 %[M=8, N=2, Q=2]    
 % n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
-    mukund[3/4C] & 0.3809 & 0.0 & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
-    node4[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 2.194 & 0.0\\\hline
+    mukund[3/4C] & 0.3809 & 185.06 & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
+    node4[-] & 16.70 & 0.0 & 16.472 & 0.0 & UNSAT & UNSAT & UNSAT & UNSAT & 2.194 & 0.0\\\hline
     yeast-graph & 0.0 & 0.0 & 0.0 & 0.00 & 0.0 & 0.0 & 0.0  & 0.0 & 0.0 & 0.0 \\\hline

### 2018-05-03 vts-synth/src/vts-synthesis.cpp

@@ -368,14 +368,16 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   // 1. Add edge to achieve graph stability and k connected. 
   if ( variation == 1 ) {   
     auto edgeC = !at_least_two( unknownE );
-    auto edgeActivityC = !at_least_three( unknownActiveE );
-    auto edgePresenceC = !at_least_three( unknownPresenceE );
-    
+   // auto edgeActivityC = !at_least_three( unknownActiveE );
+   // auto edgePresenceC = !at_least_three( unknownPresenceE );
+    auto nodeC = !at_least_four( unknownN );    
+    auto nodeActivityC = !at_least_four ( unknownActiveN ); 
+
     // fix all unknwon bits to false.
-    auto setUnknownVariablesFalse = !z3::mk_or( unknownN )  && !z3::mk_or( unknownActiveN ) 
-                                   && !z3::mk_or( unknownE ) && !z3::mk_or( unknownPresenceE ) && !z3::mk_or( unknownActiveE );
+    auto setUnknownVariablesFalse = 
+                                !z3::mk_or( unknownE );
     
-    auto addConstraints = edgeC && edgeActivityC && edgePresenceC;
+    auto addConstraints = edgeC && nodeActivityC;
 
     auto qvtsCons = exists( listN, 
                     exists( listActiveN, 
@@ -383,10 +385,10 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
                     exists( listActiveE, 
                     exists( listPairingM, 
                     exists( listReach, 
-                            vtsCons && knownVarConstraint && setUnknownVariablesFalse ))))));   
+                            vtsCons && knownVarConstraint && setUnknownVariablesFalse && addConstraints ))))));   
 
     auto cons = exists( listE, 
-                        qvtsCons && V5 ); 
+                        qvtsCons ); 
     return cons;
   }
 
@@ -408,7 +410,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
                         exists( listActiveE, 
                         exists( listPairingM, 
                         exists( listReach, 
-                                vtsCons && knownVarConstraint && setUnknownVariablesFalse )))));
+                                vtsCons && knownVarConstraint )))));
 
     auto cons = exists( listPresenceE, 
                 exists( listE, 

### 2018-05-03 papers/synth/experiments.tex
sad

--- 2018-05-03 papers/synth/experiments.tex
@@
     plos1-dia[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 0.0492 & 0.0\\\hline
-    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & \0.042 \\\hline
+    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & \#0.042 \\\hline
 %[M=8, N=2, Q=2]    

### 2018-05-03 vts-synth/src/graph-connectivity.cpp

@@ -1,17 +1,56 @@
 #include<vts.h>
 #include<z3-util.h>
 
+// z3::expr vts::k_connected_graph_constraint ( unsigned K, bool eQuantVar ) {
+
+//   /***** Building [[1]] ****/
+//   VecExpr ee_set = flattern_3d ( edges );
+//   //edgeQuant = ee_set;
+
+//   z3::expr_vector setR1 = flattern2d ( d_reach1, N, N, true );
+//   z3::expr_vector setR2 = flattern2d ( d_reach2, N, N, true );
+  
+//   // Create:  Exists (setR1, reach_d1 && d1_all-conn )
+//   z3::expr is_reach1 = exists( setR1, reachability_under_drop_def( d_reach1 , drop1, 0 ) && remains_connected( d_reach1 )  ); 
+//   z3::expr is_reach2 = exists( setR2, reachability_under_drop_def( d_reach2 , drop2, 1 ) && gets_disconnected( d_reach2 )  );
+  
+//   z3::expr_vector setD1 = flattern3d ( drop1, N, N, E_arity, true );
+//   z3::expr_vector setD2 = flattern3d ( drop2, N, N, E_arity, true );
+  
+//   z3::expr k_min_1_connected = forall ( setD1, implies 
+// 		  (  (exactly_k_drops ( K-1, drop1 ) && only_present_edges_can_be_dropped ( drop1 )), is_reach1 ) );
+ 
+//   z3::expr k_not_connected = exists ( setD2,  
+// 		    (exactly_k_drops ( K, drop2 ) && only_present_edges_can_be_dropped ( drop2 )) && is_reach2 ) ;
+ 
+//   z3::expr at_least_k_edges = at_least_three( ee_set );
+  
+//   // [[1]] : K Connected Graph 
+//   // EXISTS [ setE, kedges && k-1Conn && knotConn ]
+//   z3::expr_vector setE = flattern3d ( edges, N, N, E_arity, true );
+
+//   if ( eQuantVar ) { 
+//     z3::expr cons = exists ( setE, at_least_k_edges && k_min_1_connected && k_not_connected );
+//     return cons;
+//   }else {
+//     z3::expr cons = at_least_k_edges && k_min_1_connected && k_not_connected;
+//     return cons;
+//   }
+
+// }
+
 z3::expr vts::k_connected_graph_constraint ( unsigned K, bool eQuantVar ) {
 
   /***** Building [[1]] ****/
[…]

### 2018-05-03 vts-synth/src/vts.h

@@ -76,7 +76,8 @@ private:
 
   Vec4Expr reach;
   Vec3Expr drop1;
-  Vec2Expr d_reach1;
+  // Vec2Expr d_reach1;
+  Vec3Expr d_reach1;
   Vec3Expr drop2;
   Vec2Expr d_reach2;
 
@@ -182,7 +183,9 @@ public:
   z3::expr atmost_k_drops(unsigned k);          //
   z3::expr exactly_k_drops(unsigned k, Vec3Expr& dump);         //
   z3::expr reachability_under_drop_def(Vec2Expr& r_varas, Vec3Expr& dump1, unsigned conn_or_not);//
-  z3::expr remains_connected( Vec2Expr& r_varas );                 //
+  z3::expr reachability_under_drop_def( Vec3Expr& r_varas, Vec3Expr& dump1 );
+  z3::expr remains_connected( Vec3Expr& r_varas );                 //
+  // z3::expr remains_connected( Vec2Expr& r_varas );                 //
   z3::expr gets_disconnected( Vec2Expr& r_varas );                 //
 
   z3::expr not_k_connected( unsigned k, Vec2Expr& r_varas, Vec3Expr& dump );

### 2018-05-03 papers/synth/experiments.tex

--- 2018-05-03 papers/synth/experiments.tex
@@
     plos1-dia[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 0.0492 & 0.0\\\hline
-    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & 0.042 \\\hline
+    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & \#0.042 \\\hline
 %[M=8, N=2, Q=2]    

### 2018-05-03 papers/synth/example.tex
asd
runtime added
motivating example

--- 2018-04-23 papers/synth/related.tex
@@
-In recent years, there have been a wide range of methods
-developed for the similar synthesis problems~\cite{sktech,ceSynth,exampleSynth}.
+The figure~\ref{fig:mukund} represent mammalian SNARE map created by studying the references []. In this diagram the gray circles represent compartments, the identities of compartments are
+written within: ER=endoplasmic reticulum, ERGIC=ER-Golgi intermediate compartment,
+RE=recycling endosome, EE=early endosome, LE=late endosome, LYS=lysosome, PM=plasma
+membrane. Thin black arrows represent vesicle edges.
+% and hollow arrows represent maturation edges. 
+The set of SNAREs contained in these edges are written alongside each edge. Actual names
+of these SNAREs are mentioned in the key alongside. The red labels represent the paths taken by
+SNARES of the complex Stx-4-SNAP23-VAMP7. Here, the cycles for two SNARE molecules,
+VAMP7 and SNAP23 are complete. The green labels represent the paths taken by SNAREs of the
+complex Stx13-SNAP25-VAMP2. Here the cycle for VAMP2 is complete.The blue labels represent
+the paths taken by SNARES of the complex Stx5-Gs28-Bet1/GS15-Ykt6. Here, cycles for none of
+the SNAREs are complete.
 

### 2018-05-03 vts-synth/src/vts.cpp

@@ -469,6 +469,15 @@ z3::expr vts::no_self_edges() {                              //V5
 // V6: Only Q R entry has possible non zero entry.
 
 
+// pairing restrictions: Only self dependency is disallowed.
+z3::expr vts::restriction_on_pairing_matrix() {              //V6
+  z3::expr_vector ls(ctx);
+  for( unsigned x = 0 ; x < M; x++ ) {
+      ls.push_back( !pairing_m[x][x] );
+  }
+  return z3::mk_and( ls );
+}
+
 
 /*
 unsigned qSnareCount = 23;
@@ -487,7 +496,6 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   return z3::mk_and( ls );
 }
 
-*/
 
 z3::expr vts::restriction_on_pairing_matrix() {              //V6
   z3::expr_vector ls(ctx);
@@ -502,6 +510,7 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   }
   return z3::mk_and( ls );
 }
+*/
 
 // V7 : There should be an active pair corresponding to pairing matrix
 z3::expr vts::edge_must_fuse_with_target() {                 //V7

### 2018-05-03 papers/synth/example.tex
figure in

--- 2018-04-23 papers/synth/related.tex
@@
-In recent years, there have been a wide range of methods
-developed for the similar synthesis problems~\cite{sktech,ceSynth,exampleSynth}.
+\begin{figure}[t]
+  \centering
+  \begin{tikzpicture}[->,>=stealth',auto,node distance=4cm,
+  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+  \node[main node] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
+  \node[main node] (ic) [below right of=ga,yshift=7mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
+  \node[main node] (er) [below of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
+  \node[main node] (ee) [left of=ga] {EE};
+  \node[main node] (le) [below of=ee] {LE};
+  \path (ic) edge[bend right] node [right] {\^{Qc6}} (ga);
+  \path (er) edge[bend left] node [left] {R6} (ga);
+  \path (er) edge[bend right] node [left] {\^{Qc6}} (ga);
+  \path (er) edge[bend right] node [right] {\^{Qc6}} (ic);
+  \path (ga) edge[bend right=80] node [right] {\^{Qc1}} (er);
+  \path (ee) edge[bend left] node [left] {\^{R8},Qa7,Qbc7,R7} (le);
+  \end{tikzpicture}
+  \caption{found-in-nature VTS}
+  \label{fig:mukund-vts}
+\end{figure}
+
+In figure~\ref{fig:mukund-vts}
 

### 2018-05-03 papers/synth/example.tex

--- 2018-05-03 papers/synth/example.tex
@@
+\begin{figure}[t]
+  \centering
+  \begin{tikzpicture}[->,>=stealth',auto,node distance=4cm,
+  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+  \node[main node] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
+  \node[main node] (ic) [below right of=ga,yshift=7mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
+  \node[main node] (er) [below of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
+  \node[main node] (ee) [left of=ga] {EE};
+  \node[main node] (le) [below of=ee] {LE};
+  \path (ic) edge[bend right] node [right] {\^{Qc6}} (ga);
+  \path (er) edge[bend left] node [left] {R6} (ga);
+  \path (er) edge[bend right] node [left] {\^{Qc6}} (ga);
+  \path (er) edge[bend right] node [right] {\^{Qc6}} (ic);
+  \path (ga) edge[bend right=80] node [right] {\^{Qc1}} (er);
+  \path (ee) edge[bend left] node [left] {\^{R8},Qa7,Qbc7,R7} (le);
+  \end{tikzpicture}
+  \caption{found-in-nature VTS}
+  \label{fig:mukund-vts}
+\end{figure}
+
+In figure~\ref{fig:mukund-vts}
+
 The figure~\ref{fig:mukund} represent mammalian SNARE map created by studying the references []. In this diagram the gray circles represent compartments, the identities of compartments are

### 2018-05-03 papers/synth/intro.tex
mychanges

@@
 %Motivate VTS
-Eukaryotic cells, including human cells, consists of multiple compartments.
+
+Eukaryotic cells, including human cells, consist of multiple membrane bound compartments.
+Material is transported among these compartments by the vesicle transport system (VTS) []. Briefly,
+the source compartment produces a membrane bound packet of molecules called a vesicle. After
+release, this vesicle specifically recognizes the correct target compartment within the cell, and fuses
+with it. The molecules that form the machinery of the VTS are known. We also know a lot about the
+specific functions of these molecules and how these molecules interact amongst each other. In spite
+of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the
+road-map of the eukaryotic cell, is far from complete. The current knowledge of the network is put
+together from a patch work of biological experiments. This information is scattered across several
+publications. Even after this information is collected and put together, we find that the network
+obtained is still not complete; new vesicles and new contents in previously known vesicles are
+constantly being discovered. The synthesis for the unknown pieces may be assisted by computation
+on the graph model of VTSs. 
 % 
-Vesicle Traffic Systems(VTSs) are the material transport mechanisms
-among the compartments inside the cells~\cite{vtsIntro}.
+In this work, we use a model described in [] to find out, given a partial
+VTS graph and details about interactions amongst its molecules, what the complete graph of the
+VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
+model.
 %
-Almost all subsystems of the cells depend on VTSs.
+%Eukaryotic cells, including human cells, consists of multiple compartments.
+%
+%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
+%
+%Almost all subsystems of the cells depend on VTSs.
+\ashu{Restructure and connect to next line take the above into consideration}
+
 %

### 2018-05-03 papers/synth/model.tex
model
mychanges

@@
 
-\ankit{Discuss the yeast and eukaryotes example graph}
+\ankit{Write about Q/R SNARES: fill tomorrow}
+The molecules transported by the VTS are themselves its regulators. The molecules in a
+compartment/vesicle may be active or inactive. The molecules that are respnsible for vesicle fusion
+are called SNARE proteins []. Active SNAREs present on vesicles (v-SNAREs) bind with their
+cognate active SNAREs on the target compartment (t-SNAREs) to enable veiscle fusion. A cell
+contains multiple kinds of v- and t- SNAREs. Only specific pairs of v and t SNAREs can bind to
+each other and participate in fusion. Fusion compatible v- and t- SNAREs are determined by
+biological experiments. Different vesicle-compartmetn fusions in the cell are brought about by
+different v- and t-SNARE pairs. A molecule that participates in a given fusion reaction must not
+interfere with fusion at different compartments or vesicles. Therefore, SNAREs must be kept in an
+inactive form in appropriate compartments/vesicles. The activity of molecules is regulated by the
+other molecules, i.e., the presence and absence of the other molecules in a compartment or vesicle
+may make the molecule active or inactive. We call this regulation as activity functions.
+In the VTS model, we assume that the system is in steady state and the concentrations of the
+molecules in the compartments do not change over time. We define SNARE pairing specificity by a
+fusion pairing relation containing pairs of SNAREs and molecular regulation by activity Boolean
+functions. Since the system is in steady state, we expect that any molecule that leaves a
+compartment must come back via some path on the graph. We call this property of VTS as stability.
+
+\ankit{Discuss the yeast and eukaryotes VTS model and assumptions }
+A few assumptions on biological level.
+
 \begin{enumerate}
+\item[1] A cell is a set of compartments exchanging vesicles.
+\item[2] Compartments are neither created nor destroyed.
+\item[3] Each compartment is in steady state, gain and loss balance.
+\item[4] Molecules are neither created nor destroyed.
+\item[5] Molecules move via vesicles of uniform size.
+\item Identical vesicles have identical target compartments.
+\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
+\item The activity of a SNARE can be regulated by other molecules present on the same compartment
+or vesicle.
+\item An active SNARE pair is necessary and sufficient for fusion. \ankit{Change it to consider QR SNARES}
+ \end{enumerate}
+
+\begin{enumerate}
+
 \item Complex form using three Q-SNAREs and one R-SNARE. In order for a vesicle to fuse to it's corresponding target compartment this combination has to be present.
@@
 
-\begin{tabular}{|l|l|}
-\hline
-\multicolumn{2}{|c|}{Team sheet} \\
-\hline
-GK & Paul Robinson \\
-LB & Lucus Radebe \\
-DC & Michael Duberry \\
-DC & Dominic Matteo \\
-\hline
-RB & Didier Domi \\
-MC & David Batty \\
-MC & Eirik Bakke \\
-MC & Jody Morris \\
-FW & Jamie McMaster \\
-ST & Alan Smith \\
-ST & Mark Viduka \\
-\hline
-
-\caption{Run-times for searching for models (in secs).}
-  \label{tab:vts-grabh}
-\end{tabular}
+%%\begin{tabular}{|l|l|}
+%%\hline
+%%\multicolumn{2}{|c|}{Team sheet} \\
+%%\hline
+%%GK & Paul Robinson \\
+%%LB & Lucus Radebe \\
+%%DC & Michael Duberry \\
+%%DC & Dominic Matteo \\
+%%\hline
+%%RB & Didier Domi \\
+%%MC & David Batty \\
+%%MC & Eirik Bakke \\
+%%MC & Jody Morris \\
+%%FW & Jamie McMaster \\
+%%ST & Alan Smith \\
+%%ST & Mark Viduka \\
+%%\hline
+%%
+%%\caption{Run-times for searching for models (in secs).}
+%%  \label{tab:vts-grabh}
+%%\end{tabular}
 

### 2018-05-03 papers/synth/related.tex
mychanges

@@
-In recent years, there have been a wide range of methods
+In recent years, there has been a wide range of methods
 developed for the similar synthesis problems~\cite{sktech,ceSynth,exampleSynth}.
 
+There are a few examples of using synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}.
+A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
+Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
+the~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis.
+The queries contain quantifiers so we have we employ QBF solving for the solving the synthesis problem.
+The paper~\cite{cardelli2017syntax} uses a template-guided approach which is very close to our work.
+To our best knowledge this is the first application of synthesis in VTS.
 %%% Local Variables:

### 2018-05-03 vts-synth/src/vts.cpp

@@ -512,7 +512,38 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
 }
 */
 
+
+z3::expr vts::edge_must_fuse_with_target() {                 //V7
+  z3::expr_vector ls(ctx);
+  z3::expr lhs(ctx);
+  for( unsigned i = 0 ; i < N; i++ ) {
+    for( unsigned j = 0 ; j < N; j++ ) {
+      if (j == i)
+        continue;
+      for ( unsigned q = 0; q < E_arity; q++ ) {
+        lhs = ctx.bool_val(false);
+        for ( unsigned m1 = 0; m1 < M; m1++ ) {
+          for ( unsigned m2 = 0; m2 < M; m2++ ) {
+            for ( unsigned m3 = 0; m3 < M; m3++ ) {
+              for ( unsigned m4 = 0; m4 < M; m4++ ) {
+                z3::expr_vector inner_list(ctx);
+                for ( unsigned l = 0; l < 4; l++ ) {
+                    active_edge[i][j][q][
+                }
+              }
+            }
+          }
+        }
+      z3::expr e =  implies ( edges[i][j][q], lhs );
+      ls.push_back( e );
+      }
+    }
+  }
+  return z3::mk_and( ls );
+}
+
 // V7 : There should be an active pair corresponding to pairing matrix
+/*
 z3::expr vts::edge_must_fuse_with_target() {                 //V7
   z3::expr_vector ls(ctx);
   z3::expr lhs(ctx);
@@ -536,6 +567,7 @@ z3::expr vts::edge_must_fuse_with_target() {                 //V7
   }
   return z3::mk_and( ls );
 }
+*/
 
 //  V8: Edge should not be able to potentially fuse with
 //      any node other than it's target.

### 2018-05-03 papers/synth/example.tex
sad

@@
+% \newenvironment{psmallmatrix}
+%   {\left(\begin{smallmatrix}}
+%   {\end{smallmatrix}\right)}
+
 \begin{figure}[t]
   \centering
-  \begin{tikzpicture}[->,>=stealth',auto,node distance=4cm,
+  \begin{tikzpicture}[->,>=stealth',auto,node distance=5cm,
   thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-  \node[main node] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
-  \node[main node] (ic) [below right of=ga,yshift=7mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
+  \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
+  \node[main node] (ic) [below right of=ga,yshift=8mm,xshift=5mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
   \node[main node] (er) [below of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
-  \node[main node] (ee) [left of=ga] {EE};
-  \node[main node] (le) [below of=ee] {LE};
+  \node[main node,text width=2.5cm] (pm) [right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
+  \node[main node] (ee) [right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
+  \node[main node] (le) [below of=ee] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
+
   \path (ic) edge[bend right] node [right] {\^{Qc6}} (ga);
@@
   \path (ee) edge[bend left] node [left] {\^{R8},Qa7,Qbc7,R7} (le);
+
+  %pm <-> ee
+  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
+  \path (pm) edge[bend left=10] node [above] {{Qb2} Qc2} (ee);
+
+  %ga->pm
+  \path (ga) edge[bend left=10] node [above] {{Qb2} Qc2} (pm);
+  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
+  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
+  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
   \end{tikzpicture}

### 2018-05-03 papers/synth/example.tex
added

@@
   \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
-  \node[main node] (ic) [below right of=ga,yshift=8mm,xshift=5mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
-  \node[main node] (er) [below of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
-  \node[main node,text width=2.5cm] (pm) [right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-  \node[main node] (ee) [right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-  \node[main node] (le) [below of=ee] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
+  \node[main node] (ic) [below right of=ga,yshift=20mm,xshift=20mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
+  \node[main node] (er) [below right of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
+  \node[main node,text width=2.5cm] (pm) [above right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
+  \node[main node] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
+  \node[main node] (le) [above of=ee,yshift=-13mm,xshift=18mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
 
-  \path (ic) edge[bend right] node [right] {\^{Qc6}} (ga);
-  \path (er) edge[bend left] node [left] {R6} (ga);
-  \path (er) edge[bend right] node [left] {\^{Qc6}} (ga);
-  \path (er) edge[bend right] node [right] {\^{Qc6}} (ic);
-  \path (ga) edge[bend right=80] node [right] {\^{Qc1}} (er);
-  \path (ee) edge[bend left] node [left] {\^{R8},Qa7,Qbc7,R7} (le);
+  \path (ic) edge node [below] {\^{Qc6}} (ga);
+  \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);
+
+  %er <> ga
+  \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
+  \path (er) edge[bend left=20] node [left] {R6} (ga);
+  \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);
+
+  %ga <-> ee
+  \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
+  \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
+  \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);
+
+  %le <-> pm
+  \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
+  %ee -> le
+  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);
 
@@
   \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
-  \path (pm) edge[bend left=10] node [above] {{Qb2} Qc2} (ee);
+  \path (pm) edge[bend left=30] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
 
   %ga->pm
-  \path (ga) edge[bend left=10] node [above] {{Qb2} Qc2} (pm);
+  \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
   \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);

### 2018-05-03 papers/synth/intro.tex
intro improve

@@
 %Motivate VTS
+\ashu{Reduce the intro by half page}
 
@@
 release, this vesicle specifically recognizes the correct target compartment within the cell, and fuses
-with it. The molecules that form the machinery of the VTS are known. We also know a lot about the
-specific functions of these molecules and how these molecules interact amongst each other. In spite
-of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the
-road-map of the eukaryotic cell, is far from complete. The current knowledge of the network is put
-together from a patch work of biological experiments. This information is scattered across several
-publications. Even after this information is collected and put together, we find that the network
-obtained is still not complete; new vesicles and new contents in previously known vesicles are
-constantly being discovered. The synthesis for the unknown pieces may be assisted by computation
-on the graph model of VTSs. 
+with it.
+The molecules that form the machinery of the VTS are known.
+\todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other.
+In spite of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the road-map of the eukaryotic cell, is far from complete.
+%The current knowledge of the network is put together from a patch work of biological experiments.
+This information is scattered across several publications.
+Even after this information is collected and put together, we find that the network obtained is still not complete; new vesicles and new contents in previously known vesicles are constantly being discovered.
+The synthesis for the unknown pieces may be assisted by computationon the graph model of VTSs.
 % 
-In this work, we use a model described in [] to find out, given a partial
-VTS graph and details about interactions amongst its molecules, what the complete graph of the
-VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
-model.
+%In this work, we use a model described in [] to find out, given a partial
+%VTS graph and details about interactions amongst its molecules, what the complete graph of the
+%VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
+%model.
 %
@@
 %Almost all subsystems of the cells depend on VTSs.
-\ashu{Restructure and connect to next line take the above into consideration}
-
 %
-Therefore, understanding how VTSs functions is one of the key
-questions of cell biology.
+%Therefore, understanding how VTSs functions is one of the key
+%questions of cell biology.
 %
@@
 Even after with some effort we may collate all the known information about
-a VTS, we may still have unknown pieces of the system.
+a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
 %
@@
 %
-
 In this paper, we consider several versions of the synthesis problem

### 2018-05-03 vts-synth/src/vts.cpp

@@ -469,8 +469,9 @@ z3::expr vts::no_self_edges() {                              //V5
 // V6: Only Q R entry has possible non zero entry.
 
 
+unsigned qSnareCount = 23;
 // pairing restrictions: Only self dependency is disallowed.
-z3::expr vts::restriction_on_pairing_matrix() {              //V6
+z3::expr vts::qr_restriction_on_pairing_matrix() {              //V6
   z3::expr_vector ls(ctx);
   for( unsigned x = 0 ; x < M; x++ ) {
       ls.push_back( !pairing_m[x][x] );
@@ -495,7 +496,7 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   }
   return z3::mk_and( ls );
 }
-
+*/
 
 z3::expr vts::restriction_on_pairing_matrix() {              //V6
   z3::expr_vector ls(ctx);
@@ -510,10 +511,9 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   }
   return z3::mk_and( ls );
 }
-*/
 
 
-z3::expr vts::edge_must_fuse_with_target() {                 //V7
+z3::expr vts::qr_edge_must_fuse_with_target() {                 //V7
   z3::expr_vector ls(ctx);
   z3::expr lhs(ctx);
   for( unsigned i = 0 ; i < N; i++ ) {
@@ -521,21 +521,35 @@ z3::expr vts::edge_must_fuse_with_target() {                 //V7
       if (j == i)
         continue;
       for ( unsigned q = 0; q < E_arity; q++ ) {
-        lhs = ctx.bool_val(false);
-        for ( unsigned m1 = 0; m1 < M; m1++ ) {
-          for ( unsigned m2 = 0; m2 < M; m2++ ) {
-            for ( unsigned m3 = 0; m3 < M; m3++ ) {
-              for ( unsigned m4 = 0; m4 < M; m4++ ) {
-                z3::expr_vector inner_list(ctx);
-                for ( unsigned l = 0; l < 4; l++ ) {
-                    active_edge[i][j][q][
-                }
-              }
-            }
+        //lhs = ctx.bool_val(false);
+        for ( unsigned m = 0; m < M; m++ ) {
+          z3::expr_vector qSnareFml(ctx);
+          z3::expr_vector rSnareFml(ctx);
+          z3::expr_vector candidateFormula(ctx);
+          auto flag = false;
+          if ( m > qSnareCount ) 
+            flag == true;
[…]

### 2018-05-03 vts-synth/src/vts.h

@@ -145,8 +145,11 @@ public:
   z3::expr edge_label_subset_of_node_label();            //V4 
   z3::expr no_self_edges();                              //V5
   z3::expr restriction_on_pairing_matrix();              //V6
+  z3::expr qr_restriction_on_pairing_matrix();              //V6
   z3::expr edge_must_fuse_with_target();                 //V7
+  z3::expr qr_edge_must_fuse_with_target();                //V7
   z3::expr edge_fuse_only_with_target();                 //V8  
+  z3::expr qr_edge_fuse_only_with_target();                 //V8  
 
   // Steady state
   z3::expr reachability_def();           //R1

### 2018-05-04 papers/synth/intro.tex
somya added

@@
 In spite of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the road-map of the eukaryotic cell, is far from complete.
-%The current knowledge of the network is put together from a patch work of biological experiments.
+The current knowledge of the network is put together from a patch work of biological experiments.
 This information is scattered across several publications.
 Even after this information is collected and put together, we find that the network obtained is still not complete; new vesicles and new contents in previously known vesicles are constantly being discovered.
-The synthesis for the unknown pieces may be assisted by computationon the graph model of VTSs.
+The synthesis for the unknown pieces may be assisted by computation on the graph model of VTSs.
 % 

### 2018-05-04 papers/synth/model.tex
somya added

@@
 
-\ankit{Write about Q/R SNARES: fill tomorrow}
 The molecules transported by the VTS are themselves its regulators. The molecules in a
@@
 are called SNARE proteins []. Active SNAREs present on vesicles (v-SNAREs) bind with their
-cognate active SNAREs on the target compartment (t-SNAREs) to enable veiscle fusion. A cell
-contains multiple kinds of v- and t- SNAREs. Only specific pairs of v and t SNAREs can bind to
+cognate active SNAREs on the target compartment (t-SNAREs) to enable vesicle fusion. A cell
+contains multiple kinds of v- and t-SNAREs. Only specific pairs of v and t SNAREs can bind to
 each other and participate in fusion. Fusion compatible v- and t- SNAREs are determined by
-biological experiments. Different vesicle-compartmetn fusions in the cell are brought about by
+biological experiments. Different vesicle-compartment fusions in the cell are brought about by
 different v- and t-SNARE pairs. A molecule that participates in a given fusion reaction must not
@@
 
-\ankit{Discuss the yeast and eukaryotes VTS model and assumptions }
-A few assumptions on biological level.
-
+A few assumptions on modeling level.
 \begin{enumerate}
@@
 or vesicle.
-\item An active SNARE pair is necessary and sufficient for fusion. \ankit{Change it to consider QR SNARES}
+\item An active SNARE pair is necessary and sufficient for fusion. 
 \end{enumerate}
 
+\ankit{Discuss the yeast and eukaryotes VTS model and assumptions }
+
 \begin{enumerate}
-
 \item Complex form using three Q-SNAREs and one R-SNARE. In order for a vesicle to fuse to it's corresponding target compartment this combination has to be present.
@@
 \item Pairing matrix restriction: ith R-SNARE can fuse with only the corresponding ith Q-SNARES and vice-versa. No other combination is allowed.
-\item Concept of v and t-SNAREs is replaced by Q and R-SNAREs. 
 \end{enumerate}

### 2018-05-04 papers/synth/related.tex
somya added

@@
 Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
-the~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis.
-The queries contain quantifiers so we have we employ QBF solving for the solving the synthesis problem.
-The paper~\cite{cardelli2017syntax} uses a template-guided approach which is very close to our work.
+The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis.
+The paper~\cite{cardelli2017syntax} in addition of using SMT over ODE, uses a template-guided approach.
+In our case queries contain quantifiers so we have employed QBF solving with Z3 for the solving the synthesis problem.
 To our best knowledge this is the first application of synthesis in VTS.

### 2018-05-04 vts-synth/src/vts.cpp

@@ -512,12 +512,11 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   return z3::mk_and( ls );
 }
 
-
 z3::expr vts::qr_edge_must_fuse_with_target() {                 //V7
   z3::expr_vector ls(ctx);
   z3::expr lhs(ctx);
-  for( unsigned i = 0 ; i < N; i++ ) {
-    for( unsigned j = 0 ; j < N; j++ ) {
+  for( unsigned i = 0; i < N; i++ ) {
+    for( unsigned j = 0; j < N; j++ ) {
       if (j == i)
         continue;
       for ( unsigned q = 0; q < E_arity; q++ ) {
@@ -529,30 +528,37 @@ z3::expr vts::qr_edge_must_fuse_with_target() {                 //V7
           auto flag = false;
           if ( m > qSnareCount ) 
             flag == true;
-          candidateFormula.push ( active_edge[i][j][q][m] || active_node[j][m] ) ; 
-          for ( unsigned m1 = 0; m1 < M; m1++ ) {
-            if ( m == m1 ) continue;
-            auto fml = (active_edge[i][j][q][m1] || active_node[j][m1]) && pairing_m[m][m1]; 
+            auto ae = active_edge[i][j][q][m];
+            auto an = active_node[j][m]; 
+            //candidateFormula.push( ( ae || an ) && ( !ae || !an ) );
+            candidateFormula.push( ae || an  );
+            z3::expr sideCons( ctx );
+            for ( unsigned m1 = 0; m1 < M; m1++ ) {
+              if ( m == m1 ) continue;
+                auto ae = active_edge[i][j][q][m1];
+                auto an = active_node[j][m1];
+                // todo: if both are present the molecule becomes inactive.
+                auto fml = (ae || ae) && (!ae || !an) && pairing_m[m][m1]; 
+              if ( flag == true ) {
+                qSnareFml.push_back( fml );
+              } else {
+                rSnareFml.push_back( fml );
+              } 
+            }
             if ( flag == true ) {
-              qSnareFml.push_back( fml );
+              auto sideCons1 = !at_least_three(qSnareFml) && at_least_two(qSnareFml);
+              auto sideCons2 = at_least_one(rSnareFml) && at_most_one(rSnareFml);
+              sideCons = sideCons1 && sideCons2;
             } else {
-              rSnareFml.push_back( fml );
-            } 
[…]

### 2018-05-04 vts-synth/src/vts.cpp
somya added

@@ -511,7 +511,7 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   }
   return z3::mk_and( ls );
 }
-
+/*
 z3::expr vts::qr_edge_must_fuse_with_target() {                 //V7
   z3::expr_vector ls(ctx);
   z3::expr lhs(ctx);
@@ -561,7 +561,7 @@ z3::expr vts::qr_edge_must_fuse_with_target() {                 //V7
     }
   return z3::mk_and( ls );
 }
-
+*/
 // V7 : There should be an active pair corresponding to pairing matrix
 z3::expr vts::edge_must_fuse_with_target() {                 //V7
   z3::expr_vector ls(ctx);

### 2018-05-04 papers/synth/experiments.tex
experiments skeletal added

@@
 
+We implemented the encodings in a tool called~\ourtool\footnote{\ashu{\url{http://add-git-hub-url}}}.
+%
+The tool takes a partially defined VTS as input in its custom designed
+input language.
+%
+The tool can not only synthesize the above discussed query, but also their
+combination.
+%
+For example, our tool can modify labels of nodes or edges while
+learning activity functions.
+%
+Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
+processing formulas. Since the formulas are in QBF, we cannot use~\zthree.
+%
+We use~\depqbf~\cite{depqbf} for solving of QBF formulas.
+%
+Our tool includes about ?? lines of code.
+
+We have applied~\ourtool~on six partially defined VTS.
+%
+The results are presented in table~\ref{tab:qf-graph}.
+%
+The experiments were conducted on ... machine,
+with \ashu{?}GB memory and 900s timeout.
+%
+The first four VTSs are synthetic and inspire from literature for typical
+motifs in VTSs. 
+%
+The last two are the VTSs that are from .......\ashu{Describe the source of two examples}.
+
+The table shows timing for various synthesis queries.
+%
+For each synthesis query, we have two columns.
+%
+One column reports the timing and the other reports the minimum changes
+needed to obtain a valid VTS.
+%
+$\infty$ indicates that any number of changes with the synthesis query
+search space can obtain the VTS.
+%
+\ashu{@ankit: please discuss all the synthesis queries in the table.}
+%
+%
+Our experiments suggest that the synthesis problems are solvable by modern
+solvers and the synthesis technology may be useful for biological research.
+%
+
 %%% Local Variables:

### 2018-05-04 papers/synth/intro.tex
experiments skeletal added

@@
 
-Eukaryotic cells, including human cells, consist of multiple membrane bound compartments.
-Material is transported among these compartments by the vesicle transport system (VTS) []. Briefly,
-the source compartment produces a membrane bound packet of molecules called a vesicle. After
-release, this vesicle specifically recognizes the correct target compartment within the cell, and fuses
-with it.
-The molecules that form the machinery of the VTS are known.
-\todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other.
-In spite of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the road-map of the eukaryotic cell, is far from complete.
-The current knowledge of the network is put together from a patch work of biological experiments.
-This information is scattered across several publications.
-Even after this information is collected and put together, we find that the network obtained is still not complete; new vesicles and new contents in previously known vesicles are constantly being discovered.
-The synthesis for the unknown pieces may be assisted by computation on the graph model of VTSs.
+Eukaryotic cells, including human cells, consist of multiple membrane
+bound compartments.
+%
+Material is transported among these compartments by the vesicle
+transport system (VTS) [].
+%
+Briefly, the source compartment produces a membrane bound packet of
+molecules called a vesicle.
+%
+After release, this vesicle specifically recognizes the correct target
+compartment within the cell, and fuses with it.
+%
+A lot of information about the molecules that form the machinery of
+the VTS has been discovered, including their regulatory interaction
+with each other. 
+% %
+% \todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other.
+%
+In spite of this detailed knowledge at the level of the molecules, the
+structure of the VTS network, or the road-map of the eukaryotic cell,
+is far from complete.
+%
+The current knowledge of the network is put together from a patch work
+of biological experiments and is scattered across several publications.
+%
+Even after this information is collected and put together, we find
+that the network obtained is still not complete; new vesicles and new
+contents in previously known vesicles are constantly being discovered.
+%
+The synthesis for the unknown pieces may be assisted by computation on
+the graph model of VTSs.
+%
 % 
@@
 arise from the VTSs.
-%
-In the following, we use the model of VTSs that has been presented
-in~\cite{VTS}.
+
+We use the model of VTSs that has been presented in~\cite{VTS}.
 %
@@
 for the detailed discussion on pros and cons of the model.
-
 % Describe VTS in detail
@@
 %
-A channel is enabled by a pair of molecules
+A channel is enabled by a pair of sets of molecules
 such that one occurs in the channel and the other
@@
 %
-Both the molecules must be active in the channel
+The molecules in both the sets must be active in the channel
 and compartment respectively.
 %
-The pairs are called {\em fusing} molecules and analogously
+The pairs are called {\em fusing} sets and analogously
 the channel is considered to be {\em fused} with the
@@
 %
-Not all the pairs of molecules can participate in the fusion, the
+Not all the pairs of set of molecule can participate in the fusion, the
 potential fusion pairs are usually determined by biological experiments.
 %
-To ensure effective regulation, the fusing molecule pairs must be
+To ensure effective regulation, the fusing pairs must be
 unique for each fused channel-compartment pair.
@@
 %
-In the VTS model, we assume that the system is in study state and
-the concentrations of the molecules in the compartments do not change over time.
+In the VTS model, we assume that the system is in study state and the
+concentrations of the molecules in the compartments do not change over
+time.
 %
@@
 %
-Although the VTSs are important, our understanding of VTSs are partial.
+As we have discussed earlier, our understanding of VTSs are partial.
 %
-It largely means that the current knowledge is due to the patch work
-of biological experiments~\cite{model} for identifying the compartments,
-channels, molecules, and their activity and regulatory control.
-%
-Often the information is scattered around in several publications.
-%
-Even after with some effort we may collate all the known information about
-a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
+% It largely means that the current knowledge is due to the patch work
+% of biological experiments~\cite{model} for identifying the compartments,
+% channels, molecules, and their activity and regulatory control.
+% %
+% Often the information is scattered around in several publications.
+% %
+% Even after with some effort we may collate all the known information about
+% a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
 %
@@
 %
-We also consider variation on the properties against which we do synthesis,
-namely stability, and $k$-connectedness that states
-that VTS remains connected after removing any $k-1$ edges.
+We also consider variation on the properties against which we do
+synthesis, namely stability, and $k$-connectedness that states that
+VTS remains connected after removing any $k-1$ edges.
 %
@@
 
-We have implemented the encoding in a highly flexible tool,
+We have implemented the encoding in a flexible tool,
 which can handle a wide range of synthesis query.
@@
 %
+In section~\ref{sec:example}, we present a motivating example.
+%
 In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several

### 2018-05-04 vts-synth/src/vts-synthesis.cpp
updated fusion

@@ -266,7 +266,8 @@ void xor_bits ( z3::context& c,
 
 z3::expr vts::vts_synthesis ( unsigned variation ) {
   /** Basic Constraints **/
-  z3::expr vtsCons = create_vts_constraint();  
+  //z3::expr vtsCons = create_vts_constraint();  
+  z3::expr vtsCons = create_qr_vts_constraint();  
   //z3::expr nodeActive = always_active_on_node();
   z3::expr vtsActivity = vts_activity_constraint(); 
 

### 2018-05-04 vts-synth/src/vts.cpp

@@ -467,9 +467,6 @@ z3::expr vts::no_self_edges() {                              //V5
 }
 
 // V6: Only Q R entry has possible non zero entry.
-
-
-unsigned qSnareCount = 23;
 // pairing restrictions: Only self dependency is disallowed.
 z3::expr vts::qr_restriction_on_pairing_matrix() {              //V6
   z3::expr_vector ls(ctx);
@@ -478,7 +475,6 @@ z3::expr vts::qr_restriction_on_pairing_matrix() {              //V6
   }
   return z3::mk_and( ls );
 }
-
 
 /*
 unsigned qSnareCount = 23;
@@ -512,60 +508,142 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
   return z3::mk_and( ls );
 }
 
-z3::expr vts::qr_edge_must_fuse_with_target() {                 //V7
-  z3::expr_vector ls(ctx);
-  z3::expr lhs(ctx);
-  for( unsigned i = 0; i < N; i++ ) {
-    for( unsigned j = 0; j < N; j++ ) {
-      if (j == i)
-        continue;
-      for ( unsigned q = 0; q < E_arity; q++ ) {
-        z3::expr_vector moleculeFormula(ctx);
-        //lhs = ctx.bool_val(false);
-        for ( unsigned m = 0; m < M; m++ ) {
+
+// hack: FIXING NUMBER OF QSNARES, QSANRES always starts from 0.
+unsigned qSnareCount = 23;
+
+void vts::create_formula ( z3::expr_vector& qSnareFml, z3::expr_vector& rSnareFml,
+                           z3::expr_vector& molOnEdge, z3::expr_vector& molOnTargetNode,
+                           unsigned i, unsigned j, unsigned q, unsigned m, bool flag )  {
+   for ( unsigned m1 = 0; m1 < M; m1++ ) {
+            if ( m == m1 ) continue;
+              auto ae = active_edge[i][j][q][m1] && pairing_m[m][m1];
+              auto an = active_node[j][m1] && pairing_m[m][m1];
+              molOnEdge.push_back( ae  ); 
+              molOnTargetNode.push_back( an ); 
+              // todo: if both are present the molecule becomes inactive.
+              auto fml = (ae || an) && (!ae || !an); 
+            if ( flag == true ) {
+              qSnareFml.push_back( fml );
+            } else {
+              rSnareFml.push_back( fml );
+            } 
+  }
+}
+
[…]

### 2018-05-04 vts-synth/src/vts.h

@@ -155,12 +155,21 @@ public:
   z3::expr reachability_def();           //R1
   z3::expr steady_state_stability_cond(); //R2
   
+  z3::expr vts_qr_fusion_constraint ();
+  z3::expr create_qr_vts_constraint ();
+
   /** Flattening of the x-d Vectors. **/
   z3::expr_vector flattern2d ( Vec2Expr& dump, unsigned s1, unsigned s2, bool eq );
   z3::expr_vector flattern3d ( Vec3Expr& dump, unsigned s1, unsigned s2, unsigned s3, bool eq );
   z3::expr_vector flattern4d ( Vec4Expr& dump, unsigned s1, unsigned s2, unsigned s3, unsigned s4, bool eq );
   
   VecExpr flattern_3d ( Vec3Expr& dump );
+
+  /** HELPER FOR VTS */
+  void create_formula ( z3::expr_vector& qSnareFml, z3::expr_vector& rSnareFml,
+                        z3::expr_vector& molOnEdge, z3::expr_vector& molOnTargetNode,
+                        unsigned i, unsigned j, unsigned q, unsigned m, bool flag );
+  void fusion_constraint (z3::expr_vector& candidateMoleculeFormula, unsigned i, unsigned j, unsigned q, unsigned m, bool f1Orf2 );
 
   /*** connectivity constraints ***/
   // At least at most

### 2018-05-04 papers/synth/fig-yeast-vts.tex
my fusion added

--- 2018-05-03 papers/synth/example.tex
@@
-% \newenvironment{psmallmatrix}
-%   {\left(\begin{smallmatrix}}
-%   {\end{smallmatrix}\right)}
-
 \begin{figure}[t]
@@
 
-  \path (ic) edge node [below] {\^{Qc6}} (ga);
-  \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);
+  % \path (ic) edge node [below] {\^{Qc6}} (ga);
+  % \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);
 
-  %er <> ga
-  \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
-  \path (er) edge[bend left=20] node [left] {R6} (ga);
-  \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);
+  % %er <> ga
+  % \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
+  % \path (er) edge[bend left=20] node [left] {R6} (ga);
+  % \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);
 
-  %ga <-> ee
-  \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
-  \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
-  \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);
+  % %ga <-> ee
+  % \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
+  % \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
+  % \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);
 
-  %le <-> pm
-  \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
-  %ee -> le
-  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);
+  % %le <-> pm
+  % \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
+  % %ee -> le
+  % \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);
 
-  %pm <-> ee
-  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
-  \path (pm) edge[bend left=30] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
+  % %pm <-> ee
+  % \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
+  % \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
 
-  %ga->pm
-  \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
-  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
-  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
-  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
+  % %ga->pm
+  % \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
+  % \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
+  % \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
+  % \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
   \end{tikzpicture}
@@
 
-In figure~\ref{fig:mukund-vts}
-
-The figure~\ref{fig:mukund} represent mammalian SNARE map created by studying the references []. In this diagram the gray circles represent compartments, the identities of compartments are
-written within: ER=endoplasmic reticulum, ERGIC=ER-Golgi intermediate compartment,
-RE=recycling endosome, EE=early endosome, LE=late endosome, LYS=lysosome, PM=plasma
-membrane. Thin black arrows represent vesicle edges.
-% and hollow arrows represent maturation edges. 
-The set of SNAREs contained in these edges are written alongside each edge. Actual names
-of these SNAREs are mentioned in the key alongside. The red labels represent the paths taken by
-SNARES of the complex Stx-4-SNAP23-VAMP7. Here, the cycles for two SNARE molecules,
-VAMP7 and SNAP23 are complete. The green labels represent the paths taken by SNAREs of the
-complex Stx13-SNAP25-VAMP2. Here the cycle for VAMP2 is complete.The blue labels represent
-the paths taken by SNARES of the complex Stx5-Gs28-Bet1/GS15-Ykt6. Here, cycles for none of
-the SNAREs are complete.
-
 %%% Local Variables:

### 2018-05-04 papers/synth/related.tex
my fusion added

@@
 In recent years, there has been a wide range of methods
-developed for the similar synthesis problems~\cite{sktech,ceSynth,exampleSynth}.
+developed for the similar synthesis problems~\cite{sktech,cegis,exampleSynth}.
+%
+They range from filling gaps an implementation of C programs from the
+pool of template predicates to learn learn an a program from example
+runs of the program.
+%
+In the course of developing such methods,
+the background technology, i.e. solving of quantified
+constraints,~\cite{depQBF,Z3quantifier,markusRabeSolver} has been evolving rapidly.
 

### 2018-05-04 vts-synth/src/vts.cpp

@@ -179,6 +179,7 @@ void vts::init_vts() {
 
 // Populate pairing_m(k,k1)
   popl2 ( pairing_m, M, M, "p" );
+  popl4 ( pairing_m_4d, M, M, M, M, "p" );// todo: more efficent implementation
 /*
 // Populate xtra var s_var : var for node function
   //popl2 ( s_var, 2 * (M-1), J, "s" );
@@ -512,27 +513,125 @@ z3::expr vts::restriction_on_pairing_matrix() {              //V6
 // hack: FIXING NUMBER OF QSNARES, QSANRES always starts from 0.
 unsigned qSnareCount = 23;
 
-void vts::create_formula ( z3::expr_vector& qSnareFml, z3::expr_vector& rSnareFml,
-                           z3::expr_vector& molOnEdge, z3::expr_vector& molOnTargetNode,
-                           unsigned i, unsigned j, unsigned q, unsigned m, bool flag )  {
+void vts::create_formula ( z3::expr_vector& qSnareFml,
+                           z3::expr_vector& rSnareFml,
+                           z3::expr_vector& molOnEdge,
+                           z3::expr_vector& molOnTargetNode,
+                           unsigned i, unsigned j, unsigned q, unsigned m,
+                           bool flag )  {
    for ( unsigned m1 = 0; m1 < M; m1++ ) {
-            if ( m == m1 ) continue;
-              auto ae = active_edge[i][j][q][m1] && pairing_m[m][m1];
-              auto an = active_node[j][m1] && pairing_m[m][m1];
-              molOnEdge.push_back( ae  ); 
-              molOnTargetNode.push_back( an ); 
-              // todo: if both are present the molecule becomes inactive.
-              auto fml = (ae || an) && (!ae || !an); 
-            if ( flag == true ) {
-              qSnareFml.push_back( fml );
-            } else {
-              rSnareFml.push_back( fml );
-            } 
-  }
+     if ( m == m1 ) continue;
+     auto ae = active_edge[i][j][q][m1] && pairing_m[m][m1];
+     auto an = active_node[j][m1] && pairing_m[m][m1];
+     molOnEdge.push_back( ae  );
+     molOnTargetNode.push_back( an );
+     // todo: if both are present the molecule becomes inactive.
+     auto fml = (ae || an) && (!ae || !an);
[…]

### 2018-05-04 vts-synth/src/vts.h

@@ -71,6 +71,7 @@ private:
   Vec4Expr active_edge;
 
   Vec2Expr pairing_m;
+  Vec4Expr pairing_m_4d;
   std::vector<z3::func_decl> node_funcs;
   std::vector<z3::func_decl> edge_funcs;
 
@@ -151,6 +152,13 @@ public:
   z3::expr edge_fuse_only_with_target();                 //V8  
   z3::expr qr_edge_fuse_only_with_target();                 //V8  
 
+  //qr_4d
+  z3::expr is_fuse( VecExpr& edge_vec, VecExpr& node_vec,
+                         std::vector< unsigned >& fuse_mols );
+  z3::expr qr_4d_edge_must_fuse_with_target();                //V7
+  z3::expr qr_4d_edge_fuse_only_with_target();                 //V8  
+  z3::expr vts_qr_4d_fusion_constraint ();
+  
   // Steady state
   z3::expr reachability_def();           //R1
   z3::expr steady_state_stability_cond(); //R2

### 2018-05-04 papers/synth/example.tex
somya added
paper update

@@
   \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
-  \path (pm) edge[bend left=30] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
+  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
 
@@
 
-In figure~\ref{fig:mukund-vts}
+%t snares are labelled within compartmetns, v snares on the edges
+%and snare complexes on the left-hand side
+The figure~\ref{fig:mukund-vts} represent mammalian SNARE map created by studying the references~\cite{somya}. 
+To construct the map, we have assumed that vesicles only contain a single
+active v-SNARE, and we have attributed t-SNAREs and inactive v-SNAREs that
+travel between compartments to one of the known vesicles that go between
+the same source and target compartments.
+In order to identify the active SNARE complex involved in any particular
+vesicle fusion, two criteria were used: 
+\begin{enumerate}
+\item[a.] The SNARE complex is formed \textit{in vivo}. In most papers, this is determined by immunoprecipitation of the SNARE complex from the relevant cell fraction. 
+\item[b.] Blocking SNARE complex formation (for example, using antibodies against these SNAREs, or
+using cytosolic forms of these SNAREs) blocks the specific transport step.
+\end{enumerate}
 
-The figure~\ref{fig:mukund} represent mammalian SNARE map created by studying the references []. In this diagram the gray circles represent compartments, the identities of compartments are
+Note that these vesicles have been collected from multiple cell types, and
+any given cell type is likely to contain only a subset of the vesicles in
+the map.
+
+In this diagram the gray circles represent compartments, the identities of compartments are
 written within: ER=endoplasmic reticulum, ERGIC=ER-Golgi intermediate compartment,
@@
 the paths taken by SNARES of the complex Stx5-Gs28-Bet1/GS15-Ykt6. Here, cycles for none of
-the SNAREs are complete.
+the SNAREs are complete. So, even though most edges known so far are present in the map, paths for molecules (SNAREs) across the cell are still not complete.
+
+We have used our tool to synthesize possible fixes to complete the graph.
+Variation 1 of our tool adds new labelled edges to the graph.
+We have ranked the all possible graph edits with simple rank of minimum updates.
+Our tools was able to complete this graph by adding five new edges and nine new molecules in 210s.
+Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s.
+Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s.
+Variation 4 of our tool synthesis Boolean function based on AND, OR gates.
+The result shows the basic template of 4 leafs and 3 gates we allow user to provide it's own template in our front end language.
+The tool was able to synthesize the Boolean functions in 470s.
 

### 2018-05-04 papers/synth/experiments.tex
paper update

@@
 
-We implemented the encodings in a tool called~\ourtool\footnote{\ashu{\url{http://add-git-hub-url}}}.
+We implemented the encodings in a tool called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
 %
 The tool takes a partially defined VTS as input in its custom designed
-input language.
+input language. The input is then converted to the constraints over VTS. 
 %
@@
 Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
-processing formulas. Since the formulas are in QBF, we cannot use~\zthree.
+processing formulas. 
 %
-We use~\depqbf~\cite{depqbf} for solving of QBF formulas.
+Since, the formulas involve alternation of quantifiers over Boolean variables Z3 is not a suitable choice.
+We translate the formula created by Z3 tool into standard QDIMACS~\cite{qdimacs} format.
+Which can be used as an input for most of the QBF solvers.
+
+%Since the formulas are in QBF, we cannot use~\zthree.
 %
-Our tool includes about ?? lines of code.
+We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
+%
+Our tool includes about 7000 lines of code.
 
@@
 %
-The last two are the VTSs that are from .......\ashu{Describe the source of two examples}.
+%
+The fifth VTS is taken from "A complete set of SNAREs in yeast"
+~\cite{burri2004complete} paper. It has been adapted from the paper by separating the v and the t SNAREs. 
+%The t SNAREs are labelled within compartments and v SNAREs on the edges. %\ashu{Describe the source of two examples}.
+%
+The last VTS represent mammalian SNARE map created by studying the literature references.
 

### 2018-05-04 papers/synth/intro.tex
paper update

@@
 %Motivate VTS
-\ashu{Reduce the intro by half page}
+\ashu{reduce the intro by half page}
 
@@
 Material is transported among these compartments by the vesicle
-transport system (VTS) [].
+transport system (VTS).
 %
@@
 % Describe VTS in detail
-While VTSs transports molecules, VTSs are also
-regulated by the molecules.
+
+VTSs are regulated by the same molecules that they transport. Molecules on compartments and on vesicles can be in either an active or an inactive state.
+% the term vesicle has already been introduced.. using two terms for the same object seems confusing. 
 %
-Each compartment contains a set of molecules.
+% (The molecules are transported to the other compartments via
+%unidirectional channels.) cannot comment on unidirectionality of vesicles. they may be undergoingmultiple cycles of back-fusion for all we %know..  
 %
-The molecules are transported to the other compartments via
-unidirectional channels.  
+The active molecules regulate the vesicle they occur on.
 %
-The molecules in a compartment may be active or not active.
+A vesicle is enabled by a set of molecules
+such that one part of the set occurs in the vesicle and the other part
+occurs in the target compartment.
+% use either target or destination consistantly throughout..i prefer target because that's what the t in t-SNARE stands for.
 %
-Similarly, a molecule can be active or inactive in a channel. 
-%
-The active molecules are the regulators of the channels.
-%
-A channel is enabled by a pair of sets of molecules
-such that one occurs in the channel and the other
-occurs in the destination compartment.
-%
-The molecules in both the sets must be active in the channel
-and compartment respectively.
+These molecules must be active in the vesicle
+and target compartment respectively.
 %
 The pairs are called {\em fusing} sets and analogously
-the channel is considered to be {\em fused} with the
+the vesicle is considered to be {\em fused} with the
 destination compartment.
 %
-Not all the pairs of set of molecule can participate in the fusion, the
+Not all sets molecule can participate in the fusion, the
 potential fusion pairs are usually determined by biological experiments.
 %
-To ensure effective regulation, the fusing pairs must be
-unique for each fused channel-compartment pair.
+Generally, in cells, the fusing pairs are found to be distinct for distinct vesicle-compartment fusions.
 %
-A molecule that has participated in a fusion must not interfere
-with fusion at different compartments or channels.
+In order that a molecule that has participated in a fusion does not interfere
+with fusion at compartments and vesicles, in the model, we require that the molecule is inactive on appropriate compartments.
 %
-Therefore, the molecule must be inactive in appropriate compartments.
 %
@@
 the presence and absence of the other molecules in a compartment or
-channel may make the molecule active or inactive.
+vesicle may make the molecule active or inactive.
 %
@@
 %
-In the VTS model, we assume that the system is in study state and the
+In this VTS model, we assume that the system is in steady state and the
 concentrations of the molecules in the compartments do not change over
@@
 We model the system as a labelled graph, where compartments are nodes and
-transport channels are edges.
+transport vesicles are edges.
 %
 The set of molecules present and their activity in a compartment or
-a channel is the label of the respective node or edge.
+a vesicle is the label of the respective node or edge.
 %
@@
 %
-Since the system is in study state, we expect that any molecule that
+Since our system is in steady state, we expect that any molecule that
 leaves a compartment must come back via some path on the graph.
@@
 %
-As we have discussed earlier, our understanding of VTSs are partial.
+As we have discussed earlier, our understanding of VTSs is partial.
 %
@@
 %
-For example, we may suspect that some edges may not have been
-discovered in a VTS that does not satisfy the stability condition.
+%For example, it is possible that some edges may not have been
+%discovered in a VTS that does not satisfy the stability condition.
+% nature of missing information has already been elaborated upon in the first paragraph
 %
@@
 We have applied our tool on two found-in-nature VTSs, namely
-M1~\cite{} and S1~\cite{}.
+M1~\cite{} and Y1~\cite{burri2004complete}.
 %

### 2018-05-04 papers/synth/model.tex
paper update

@@
 The molecules transported by the VTS are themselves its regulators. The molecules in a
-compartment/vesicle may be active or inactive. The molecules that are respnsible for vesicle fusion
+compartment/vesicle may be active or inactive. The molecules that are responsible for vesicle fusion
 are called SNARE proteins []. Active SNAREs present on vesicles (v-SNAREs) bind with their
@@
 
-A few assumptions on modeling level.
+Our model is inspired by~\cite{shukla2017discovering}.
+On the timescales of minutes, our following assumptions reasonably capture the important aspects of the Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
 \begin{enumerate}
@@
 
-\ankit{Discuss the yeast and eukaryotes VTS model and assumptions }
+SNARE proteins are the agents of vesicle fusion in eukaryotic cells.
+When SNAREs on vesicles (v-SNAREs) encounter their cognate SNAREs on target compartments (t-SNAREs), they form SNARE complexes~\cite{jahn2006snares}, and a single SNARE complex releases enough energy to enable membrane fusion~\cite{van2010one}.
+SNAREs are identified by the presence of a conserved 60-70 stretch of amino acids called the SNARE motif.
+Based on amino acid sequence, SNARE motifs fall into 4 classes: Qa, Qb, Qc, and R~\cite{jahn2006snares}.
+Across all intracellular vesicle fusion reactions, the associated SNARE complexes contain one of each of the four kinds of SNARE motifs; the v-SNARE contributes a single SNARE motif, usually it is an R-SNARE (although, exceptions are known: Sec22b and Ykt6 are both R-SNAREs which form parts of t-SNAREs~\cite{hong}) and the rest of the three SNARE
+motifs are contributed by the t-SNARE. In the cell, different vesicle fusion reactions are associated with distinct v- and t-SNARE pairs.
 
-\begin{enumerate}
-\item Complex form using three Q-SNAREs and one R-SNARE. In order for a vesicle to fuse to it's corresponding target compartment this combination has to be present.
-\item In the graph shown the R-SNAREs are always in active. Every combination is formed by three active Q-SNAREs and one active R-SNARE.
-\item  Qai, Qbi, Qci and Ri are just dummy names, real biological names can be found in the below table. 
-\item In the diagram white circle molecules are always active. Other edge labels are inactive molecules.
-\item Pairing matrix restriction: ith R-SNARE can fuse with only the corresponding ith Q-SNARES and vice-versa. No other combination is allowed.
-\end{enumerate}
+We have extended the model by considering each complex molecule as distinct.
+In the previous paper, we have considered three Q SNARES as a single molecule.
+We also do not assume that SNARE type distribution is even in the whole system.
+The fusion is now driven by the active presence of three Q SNARE and one R SNARE molecule, present in any combination on edge and on the target compartment.
+We have relaxed the pairing matrix constraint to comply with this fact.
+In order for the biological efficiency and optimality reasons we still do not allow self-edges to be present in the VTS.
+%\begin{enumerate} 
+%\item Complex form using three Q-SNAREs and one R-SNARE. In order for a vesicle to fuse to it's corresponding target compartment this combination has to be present.
+%\item In the graph shown the R-SNAREs are always in active. Every combination is formed by three active Q-SNAREs and one active R-SNARE.
+%\item  Qai, Qbi, Qci and Ri are just dummy names, real biological names can be found in the below table. 
+%\item In the diagram white circle molecules are always active. Other edge labels are inactive molecules.
+%\item Pairing matrix restriction: ith R-SNARE can fuse with only the corresponding ith Q-SNARES and vice-versa. No other combination is allowed.
+%\end{enumerate}
 
@@
 
-Qa1 Qb1 Qc1 R1
-Stx18 Sec20 Slt1 Sec22b
-
 %%% Local Variables:

### 2018-05-04 papers/synth/example.tex
paper update

@@
 Variation 1 of our tool adds new labelled edges to the graph.
-We have ranked the all possible graph edits with simple rank of minimum updates.
-Our tools was able to complete this graph by adding five new edges and nine new molecules in 210s.
+We have ranked the all possible graph edits with the simple rank of minimum updates.
+Our tools were able to complete this graph by adding five new edges and nine new molecules in 210s.
 Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s.
@@
 Variation 4 of our tool synthesis Boolean function based on AND, OR gates.
-The result shows the basic template of 4 leafs and 3 gates we allow user to provide it's own template in our front end language.
+The result shows the basic template of 4 leaves and 3 gates we allow the user to provide its own template in our front-end language.
 The tool was able to synthesize the Boolean functions in 470s.

### 2018-05-04 papers/synth/fig-yeast-vts.tex
asd

@@
   thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-  \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
-  \node[main node] (ic) [below right of=ga,yshift=20mm,xshift=20mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
-  \node[main node] (er) [below right of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
-  \node[main node,text width=2.5cm] (pm) [above right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-  \node[main node] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-  \node[main node] (le) [above of=ee,yshift=-13mm,xshift=18mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
+  \node[main node,,text width=2.5cm] (golgi) [] {GOLGI {\small \^{Qa2} \^{Qb2} \^{Qc2} \^{Qa5} \^{Qb5} \^{Qc5}}};
+  \node[main node,text width=2.5cm] (pvac) [right of=golgi] {PRE-VAC {\small \^{Qa3} \^{Qb2} \^{R3} \^{R4}}};
+  \node[main node,text width=2cm] (vac) [right of=pvac] {VAC {\small \^{Qa4} \^{Qb2} \^{R3} \^{R4}}};
+  \node[main node,text width=2.5cm] (pm_up) [above right of=golgi] {PM {\small \^{Qa1} \^{Qbc1}}};
+  \node[main node] (pm_down) [below right of=golgi] {PM {\small \^{Qa6} \^{Qb6} \^{R6} \^{R4}}};
 
-  % \path (ic) edge node [below] {\^{Qc6}} (ga);
-  % \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);
+  \path (golgi) edge[bend right] node [right] {\^{R1}} (pm_up);
+  \path (pm_up) edge[bend right] node [right] {\^{R1}} (golgi);
 
-  % %er <> ga
-  % \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
-  % \path (er) edge[bend left=20] node [left] {R6} (ga);
-  % \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);
+  \path (golgi) edge[bend right] node [right] {\^{Qc6}} (pm_down);
+  \path (pm_down) edge[bend right] node [right] {\^{R1}} (golgi);
 
-  % %ga <-> ee
-  % \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
-  % \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
-  % \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);
+  \path (golgi) edge[] node [below] {\^{Qc3}} (pvac);
+  \path (pvac) edge[bend left=20] node [above] {\^{Qc4}} (vac);
 
-  % %le <-> pm
-  % \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
-  % %ee -> le
-  % \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);
-
-  % %pm <-> ee
-  % \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
-  % \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
-
-  % %ga->pm
-  % \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
-  % \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
-  % \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
-  % \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
   \end{tikzpicture}
-  \caption{found-in-nature VTS}
+  \caption{Yeast VTS}
   \label{fig:mukund-vts}

### 2018-05-04 papers/synth/example.tex

--- 2018-05-04 papers/synth/example.tex
@@
 We have used our tool to synthesize possible fixes to complete the graph.
-Variation 1 of our tool adds new labelled edges to the graph.
-We have ranked the all possible graph edits with simple rank of minimum updates.
-Our tools was able to complete this graph by adding five new edges and nine new molecules in 210s.
-Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s.
-Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s.
-Variation 4 of our tool synthesis Boolean function based on AND, OR gates.
-The result shows the basic template of 4 leafs and 3 gates we allow user to provide it's own template in our front end language.
-The tool was able to synthesize the Boolean functions in 470s.
+Based on the variation we were able to synthesis the this graph within 600s.
+We have created a rank of minimum edits to complete the graph.
+Our experiments suggest that the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
 

### 2018-05-04 papers/synth/experiments.tex

@@
 \ashu{@ankit: please discuss all the synthesis queries in the table.}
+
+Variation 1 of our tool adds new labelled edges to the graph.
+We have ranked the all possible graph edits with the simple rank of minimum updates.
+Our tools were able to complete this graph by adding five new edges and nine new molecules in 210s.
+Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s.
+Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s.
+Variation 4 of our tool synthesis Boolean function based on AND, OR gates.
+The result shows the basic template of 4 leaves and 3 gates we allow the user to provide its own template in our front-end language.
+The tool was able to synthesize the Boolean functions in 470s.
 %
 %
-Our experiments suggest that the synthesis problems are solvable by modern
-solvers and the synthesis technology may be useful for biological research.
+%Our experiments suggest that the synthesis problems are solvable by modern 
+%solvers and the synthesis technology may be useful for biological research.
 %

### 2018-05-04 papers/synth/related.tex
citations added

@@
 In recent years, there has been a wide range of methods
-developed for the similar synthesis problems~\cite{sktech,cegis,exampleSynth}.
+developed for the similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
 %
@@
 the background technology, i.e. solving of quantified
-constraints,~\cite{depQBF,Z3quantifier,markusRabeSolver} has been evolving rapidly.
+constraints,~\cite{lonsing2010depqbf,z3Quant} has been evolving rapidly.
 

### 2018-05-04 papers/synth/experiments.tex
final graph

@@
    \cline{2-9}
-    {} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} & {\textbf{Free}} & {\textbf{Min tweak}} \\\hline
+    {} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} \\\hline
 
-    plos1-dia[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 0.0492 & 0.0\\\hline
-    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & \#0.042 \\\hline
+    plos1-dia[3/4C] & 0.0292 & $\infty$ & 0.0255 & $\infty$ & 0.0843 & $\infty$ & 0.1005 & $\infty$ & 0.0492 & 0.0\\\hline
+    plos2-dia [4C] & 0.0414 & 0 & 0.0407 & 0 & 1.333 & 1 node & 2.327 & 1N 9PE & 0.042 & 0 \\\hline
 %[M=8, N=2, Q=2]    
 % n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
-    mukund[3/4C] & 0.3809 & 185.06 & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
+    mukund[3/4C] & 185.06 &  & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
     node4[-] & 16.70 & 0.0 & 16.472 & 0.0 & UNSAT & UNSAT & UNSAT & UNSAT & 2.194 & 0.0\\\hline
@@
 %
-\ashu{@ankit: please discuss all the synthesis queries in the table.}
+%\ashu{@ankit: please discuss all the synthesis queries in the table.}
 

### 2018-05-04 vts-synth/src/card-constr.cpp

@@ -326,6 +326,10 @@ z3::expr_vector vts::presence_edge_list() {
     return flattern4d ( presence_edge, N, N, E_arity, M, true );
 }
 
+z3::expr_vector vts::pairing_m_4d_list() {
+    return flattern4d ( pairing_m_4d, N, N, E_arity, M, true );
+}
+
 z3::expr_vector vts::active_edge_list() {
     return flattern4d ( active_edge, N, N, E_arity, M, true );
 }

### 2018-05-04 vts-synth/src/load-vts.cpp

@@ -160,6 +160,12 @@ void load_vts::get_pairing() {
   v->add_known_pairing( m1, m2 );
 }
 
+void load_vts::qr_get_pairing() {
+  unsigned m1,m2,m3,m4;
+  in >> m1 >> m2 >> m3 >> m4;
+  v->qr_add_known_pairing( m1, m2, m3, m4 );
+}
+
 void load_vts::get_node_function() {
   unsigned m;
   in >> m;
@@ -197,7 +203,8 @@ void load_vts::load() {
       case 'e': get_edge(); break;
       case 'f': get_node_function(); break;
       case 'g': get_edge_function(); break;
-      case 'p': get_pairing(); break;
+     // case 'p': get_pairing(); break;
+      case 'p': qr_get_pairing(); break;
       default:
         load_error( "expecting a command at line", line_num );
       }

### 2018-05-04 vts-synth/src/load-vts.h

@@ -42,6 +42,7 @@ private:
   void get_node();
   void get_edge();
   void get_pairing();
+  void qr_get_pairing();
   void get_node_function();
   void get_edge_function();
 public:

### 2018-05-04 vts-synth/src/vts-synthesis.cpp

@@ -304,6 +304,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   z3::expr_vector listActiveE = active_edge_list(); 
   z3::expr_vector listPairingM = pairing_m_list(); 
   z3::expr_vector listReach = reach_list();
+  z3::expr_vector listPairing4M  = pairing_m_4d_list();
   
   z3::expr knownVarConstraint( ctx );
 
@@ -340,6 +341,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     unassigned_bits ( listE, knownEdges, unknownE ); 
     unassigned_bits ( listPresenceE, knownPresenceEdges, unknownPresenceE ); 
     unassigned_bits ( listActiveE, knownActiveEdges, unknownActiveE ); 
+    unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
   
     z3::expr_vector list_expr (ctx);
 
@@ -376,7 +378,8 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
 
     // fix all unknwon bits to false.
     auto setUnknownVariablesFalse = 
-                                !z3::mk_or( unknownE );
+                                !z3::mk_or( unknownE ) 
+                                && !z3::mk_or ( unknownPairingM );
     
     auto addConstraints = edgeC && nodeActivityC;
 
@@ -385,8 +388,9 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
                     exists( listPresenceE,  
                     exists( listActiveE, 
                     exists( listPairingM, 
+                    exists( listPairing4M, 
                     exists( listReach, 
-                            vtsCons && knownVarConstraint && setUnknownVariablesFalse && addConstraints ))))));   
+                            vtsCons && knownVarConstraint && setUnknownVariablesFalse )))))));   
 
     auto cons = exists( listE, 
                         qvtsCons ); 
@@ -410,7 +414,8 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
                         exists( listActiveN, 
                         exists( listActiveE, 
                         exists( listPairingM, 
-                        exists( listReach, 
+                        exists( listPairing4M, 
+                     //   exists( listReach, 
                                 vtsCons && knownVarConstraint )))));
 
     auto cons = exists( listPresenceE, 

### 2018-05-04 vts-synth/src/vts.cpp

@@ -106,6 +106,14 @@ void vts::add_known_pairing( unsigned m1, unsigned m2 ) {
   */
 }
 
+void vts::qr_add_known_pairing( unsigned m1, unsigned m2, unsigned m3, unsigned m4 ) {
+    knownPairingMatrix.push_back( pairing_m_4d[m1][m2][m3][m4] );
+  /*
+  std::vector < std::tuple <unsigned, unsigned> > knownPairingTuple;
+  knownPairingTuple.push_back ( std::make_tuple( m1, m2 ) );
+  std::sort(begin(knownPairingTuple), end(knownPairingTuple), TupleCompare<0>()); 
+  */
+}
 void vts::add_known_activity_node_function( unsigned m, z3::expr f ) {
   
 }
@@ -1049,9 +1057,10 @@ z3::expr vts::vts_basic_constraints () {
   z3::expr v2 = active_molecule_is_present_on_edge();         //V2
   z3::expr v3 = active_molecule_is_present_on_node();         //V3
   z3::expr v4 = edge_label_subset_of_node_label();            //V4
-  z3::expr v6 = restriction_on_pairing_matrix();              //V6
+ // z3::expr v6 = restriction_on_pairing_matrix();              //V6
   
-  z3::expr base_cons = v1 && v2 && v3 && v4 && v6;
+//  z3::expr base_cons = v1 && v2 && v3 && v4 && v6;
+  z3::expr base_cons = v1 && v2 && v3 && v4;
   return base_cons;
 }
 
@@ -1075,8 +1084,8 @@ z3::expr vts::vts_fusion_constraint () {
 }
 
 z3::expr vts::vts_qr_fusion_constraint () {
-  z3::expr v7 = qr_edge_must_fuse_with_target();         //V7
-  z3::expr v8 = qr_edge_fuse_only_with_target();         //V8
+  z3::expr v7 = qr_4d_edge_must_fuse_with_target();       //V7
+  z3::expr v8 = qr_4d_edge_fuse_only_with_target();        //V8
   auto cons = v7 && v8;
   return cons;
 }

### 2018-05-04 vts-synth/src/vts.h

@@ -125,7 +125,8 @@ public:
                        std::vector<unsigned>&);
   void add_known_node( unsigned, std::vector<unsigned>&,
                        std::vector<unsigned>&);
-  void add_known_pairing( unsigned, unsigned );
+  void add_known_pairing( unsigned, unsigned);
+  void qr_add_known_pairing( unsigned m1, unsigned m2, unsigned m3, unsigned m4 );
   void add_known_activity_node_function( unsigned, z3::expr );
   void add_known_activity_edge_function( unsigned, z3::expr );
 
@@ -261,6 +262,7 @@ public:
   z3::expr_vector presence_edge_list();
   z3::expr_vector active_edge_list();
   z3::expr_vector pairing_m_list();
+  z3::expr_vector pairing_m_4d_list();
   z3::expr_vector reach_list();
   z3::expr_vector edge_list();
   

### 2018-05-04 papers/synth/intro.tex
results

@@
 %Motivate VTS
-\ashu{reduce the intro by half page}
-
 Eukaryotic cells, including human cells, consist of multiple membrane
@@
 We have applied our tool on two found-in-nature VTSs, namely
-M1~\cite{} and Y1~\cite{burri2004complete}.
+M1~\cite{} and S1~\cite{burri2004complete}.
 %
 We have also applied our tool on various synthetic examples to
-demonstrate that our tool scale upto the graph size ??, which
+demonstrate that our tool scale upto the graph size size nodes, which
 is the size of typical VTSs in a eukaryotic cell.

### 2018-05-04 papers/synth/experiments.tex
update

@@
 % n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
-    mukund[3/4C] & 185.06 &  & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
-    node4[-] & 16.70 & 0.0 & 16.472 & 0.0 & UNSAT & UNSAT & UNSAT & UNSAT & 2.194 & 0.0\\\hline
+    mukund[3/4C] & 185.06 & 4N 8E & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
+    node4[-] & 16.70 & 0.0 & 16.472 & 0.0 &  5.085 & $\infty$ & 7.011 & $\infty$ & 2.194 & 0.0\\\hline
     yeast-graph & 0.0 & 0.0 & 0.0 & 0.00 & 0.0 & 0.0 & 0.0  & 0.0 & 0.0 & 0.0 \\\hline

### 2018-05-04 vts-synth/src/load-vts.cpp

@@ -203,8 +203,8 @@ void load_vts::load() {
       case 'e': get_edge(); break;
       case 'f': get_node_function(); break;
       case 'g': get_edge_function(); break;
-     // case 'p': get_pairing(); break;
-      case 'p': qr_get_pairing(); break;
+      case 'p': get_pairing(); break;
+      //case 'p': qr_get_pairing(); break;
       default:
         load_error( "expecting a command at line", line_num );
       }

### 2018-05-04 vts-synth/src/vts-synthesis.cpp

@@ -266,8 +266,8 @@ void xor_bits ( z3::context& c,
 
 z3::expr vts::vts_synthesis ( unsigned variation ) {
   /** Basic Constraints **/
-  //z3::expr vtsCons = create_vts_constraint();  
-  z3::expr vtsCons = create_qr_vts_constraint();  
+  z3::expr vtsCons = create_vts_constraint();  
+  //z3::expr vtsCons = create_qr_vts_constraint();  
   //z3::expr nodeActive = always_active_on_node();
   z3::expr vtsActivity = vts_activity_constraint(); 
 
@@ -304,7 +304,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   z3::expr_vector listActiveE = active_edge_list(); 
   z3::expr_vector listPairingM = pairing_m_list(); 
   z3::expr_vector listReach = reach_list();
-  z3::expr_vector listPairing4M  = pairing_m_4d_list();
+  //z3::expr_vector listPairing4M  = pairing_m_4d_list();
   
   z3::expr knownVarConstraint( ctx );
 
@@ -341,7 +341,8 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     unassigned_bits ( listE, knownEdges, unknownE ); 
     unassigned_bits ( listPresenceE, knownPresenceEdges, unknownPresenceE ); 
     unassigned_bits ( listActiveE, knownActiveEdges, unknownActiveE ); 
-    unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
+    unassigned_bits ( listPairingM, knownPairingMatrix, unknownPairingM ); 
+    //unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
   
     z3::expr_vector list_expr (ctx);
 
@@ -360,9 +361,10 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     }
   
     knownVarConstraint = z3::mk_and ( list_expr );
+    
     /*
-    for( unsigned i = 0; i < knownActiveEdges.size(); i++  ) {
-      std::cout << "Nodes is " << knownActiveEdges[i] << "\n" ;
+    for( unsigned i = 0; i < unknownPairingM.size(); i++  ) {
+      std::cout << "Nodes is " << unknownPairingM[i] << "\n" ;
     }
     */
 
@@ -370,27 +372,36 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
 
[…]

### 2018-05-04 vts-synth/src/vts.cpp

@@ -1057,9 +1057,21 @@ z3::expr vts::vts_basic_constraints () {
   z3::expr v2 = active_molecule_is_present_on_edge();         //V2
   z3::expr v3 = active_molecule_is_present_on_node();         //V3
   z3::expr v4 = edge_label_subset_of_node_label();            //V4
+  z3::expr v6 = restriction_on_pairing_matrix();              //V6
+  
+  z3::expr base_cons = v1 && v2 && v3 && v4 && v6;
+ // z3::expr base_cons = v1 && v2 && v3 && v4;
+  return base_cons;
+}
+
+z3::expr vts::qr_vts_basic_constraints () {  
+  z3::expr v1 = molecule_presence_require_for_present_edge(); //V1
+  z3::expr v2 = active_molecule_is_present_on_edge();         //V2
+  z3::expr v3 = active_molecule_is_present_on_node();         //V3
+  z3::expr v4 = edge_label_subset_of_node_label();            //V4
  // z3::expr v6 = restriction_on_pairing_matrix();              //V6
   
-//  z3::expr base_cons = v1 && v2 && v3 && v4 && v6;
+ // z3::expr base_cons = v1 && v2 && v3 && v4 && v6;
   z3::expr base_cons = v1 && v2 && v3 && v4;
   return base_cons;
 }
@@ -1099,7 +1111,7 @@ z3::expr vts::create_vts_constraint () {
 
 z3::expr vts::create_qr_vts_constraint () {
 // auto cons = vts_basic_constraints() && vts_self_edges_constraint()
-  auto cons = vts_basic_constraints() 
+  auto cons = qr_vts_basic_constraints () 
               && vts_stability_constraint()
               && vts_qr_fusion_constraint();
   return cons;

### 2018-05-04 vts-synth/src/vts.h

@@ -152,6 +152,7 @@ public:
   z3::expr qr_edge_must_fuse_with_target();                //V7
   z3::expr edge_fuse_only_with_target();                 //V8  
   z3::expr qr_edge_fuse_only_with_target();                 //V8  
+  z3::expr qr_vts_basic_constraints ();  
 
   //qr_4d
   z3::expr is_fuse( VecExpr& edge_vec, VecExpr& node_vec,

### 2018-05-05 papers/synth/experiments.tex
some cleanup

@@
   \centering
-  \begin{tabular}[t]{|c|c|c|c|c|c|c|c|c|c|c}\hline
+  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}}\hline
     {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth Cnf}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline
@@
 
-We implemented the encodings in a tool called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
+We implemented the encodings in a tool
+called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
 %
-The tool takes a partially defined VTS as input in its custom designed
-input language. The input is then converted to the constraints over VTS. 
+The tool takes a partially defined VTS as input in a custom designed
+input language.
 %
-The tool can not only synthesize the above discussed query, but also their
-combination.
+The input is then converted to the constraints over VTS. 
+%
+The tool can not only synthesize the above discussed queries, but also their
+combinations.
 %
@@
 %
-Since, the formulas involve alternation of quantifiers over Boolean variables Z3 is not a suitable choice.
-We translate the formula created by Z3 tool into standard QDIMACS~\cite{qdimacs} format.
-Which can be used as an input for most of the QBF solvers.
-
-%Since the formulas are in QBF, we cannot use~\zthree.
+Since, the formulas involve alternation of quantifiers over Boolean
+variables Z3 is not a suitable choice.
+%
+We translate the formula created by Z3 tool into standard
+QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
 %
@@
 
-We have applied~\ourtool~on six partially defined VTS.
+We have applied~\ourtool~on six partially defined VTSs.
 %
@@
 %
-The experiments were conducted on ... machine,
+The experiments were conducted on ?? machine,
 with \ashu{?}GB memory and 900s timeout.
 %
-The first four VTSs are synthetic and inspire from literature for typical
-motifs in VTSs. 
+The first four VTSs are synthetic, but inspire from literature for
+typical motifs in VTSs. 
 %
@@
 The fifth VTS is taken from "A complete set of SNAREs in yeast"
-~\cite{burri2004complete} paper. It has been adapted from the paper by separating the v and the t SNAREs. 
+~\cite{burri2004complete} paper. It has been adapted from the paper by
+separating the v and the t SNAREs. 
 %The t SNAREs are labelled within compartments and v SNAREs on the edges. %\ashu{Describe the source of two examples}.
@@
 Variation 1 of our tool adds new labelled edges to the graph.
-We have ranked the all possible graph edits with the simple rank of minimum updates.
-Our tools were able to complete this graph by adding five new edges and nine new molecules in 210s.
-Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s.
-Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s.
-Variation 4 of our tool synthesis Boolean function based on AND, OR gates.
-The result shows the basic template of 4 leaves and 3 gates we allow the user to provide its own template in our front-end language.
+%
+We have ranked the all possible graph edits with the simple rank of
+minimum updates.
+%
+Our tools were able to complete this graph by adding five new edges
+and nine new molecules in 210s.
+%
+Variation 2 of our graph adds new labels to the edge and was able to
+fix this graph with eleven new molecule labels in 180s.
+%
+Variation 3 of our tool synthesis low depth CNF functions and was able
+to synthesis the result in 500s.
+%
+Variation 4 of our tool synthesis Boolean function based on AND, OR
+gates.
+%
+The result shows the basic template of 4 leaves and 3 gates we allow
+the user to provide its own template in our front-end language.
+%
 The tool was able to synthesize the Boolean functions in 470s.

### 2018-05-05 papers/synth/intro.tex
some cleanup

@@
 
-We use the model of VTSs that has been presented in~\cite{VTS}.
+We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
 %
@@
 %
-We have applied our tool on two found-in-nature VTSs, namely
-M1~\cite{} and S1~\cite{burri2004complete}.
+We have applied our tool on two found-in-nature
+VTSs~\cite{burri2004complete}.
 %

### 2018-05-05 papers/synth/prelim.tex
caps
some cleanup

@@
-In this section, we will present the model of VTS from~\cite{PloS,SASB}.
+In this section, we will present the model of VTS from~\cite{smtVTS}.
 %
@@
 \item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
-\item Boolean variable $p_{m_1,m_2,m_3,m_4}$ indicates if $\{m_1,m_2,m_3,m_4\} \in \pairs$
+\item Boolean variable $p_{\{m_1,m_2,m_3,m_4\}}$ indicates if $\{m_1,m_2,m_3,m_4\} \in \pairs$
 \item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
@@
   \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
-                         (p_{m_1,m_2,m_3,m_4} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) \land\\ 
-  & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
+                         (p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
+% \land\\ 
+%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
   % \bigwedge\limits_{m} 
@@
   \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
-                        \sum_{l=1}^4 b_{i,j,q,m_l} > 0 \land\\
-  & \qquad \qquad \qquad \qquad \sum_{l=1}^4 a_{j,m_l} > 0 \land p_{m_1,m_2,m_3,m_4})
+                        \Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
+  & \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
   \\
@@
   \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
-\land a_{j^{\prime},m_4^{\prime}} \land p_{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4})
+\land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
   \\
@@
 Here we will discussed two such properties proposed in earlier
-works~\cite{SASBpaper}, namely stability and $k$-connectedness.
+works~\cite{smtVTS}, namely stability and $k$-connectedness.
 %

### 2018-05-05 papers/synth/experiments.tex
still two ref to go
asd

@@
   \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}}\hline
-    {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth Cnf}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline
+    {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth CNF}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline
 
    \cline{2-9}
-    {} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} & {\textbf{Timing}} & {\textbf{Changes}} \\\hline
+    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\\hline
 
@@
   \end{tabular}
-  \caption{Run-times for searching for models (in secs).}
-  \label{tab:qf-grabh}
+  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
+  Time is reported in seconds.}
+  \label{tab:qf-graph}
 \end{table}
@@
 %
-The experiments were conducted on ?? machine,
-with \ashu{?}GB memory and 900s timeout.
+The experiments were conducted on a machine,
+with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
 %

### 2018-05-05 papers/synth/experiments.tex
asd

@@
   \centering
-  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}}\hline
-    {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth CNF}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline
-
+  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
+    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
+    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    \hline   
    \cline{2-9}
@@
 
-    plos1-dia[3/4C] & 0.0292 & $\infty$ & 0.0255 & $\infty$ & 0.0843 & $\infty$ & 0.1005 & $\infty$ & 0.0492 & 0.0\\\hline
-    plos2-dia [4C] & 0.0414 & 0 & 0.0407 & 0 & 1.333 & 1 node & 2.327 & 1N 9PE & 0.042 & 0 \\\hline
-%[M=8, N=2, Q=2]    
-% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
-    mukund[3/4C] & 185.06 & 4N 8E & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
-    node4[-] & 16.70 & 0.0 & 16.472 & 0.0 &  5.085 & $\infty$ & 7.011 & $\infty$ & 2.194 & 0.0\\\hline
+    plos1-dia[3/4C]& 0.0292&$\infty$& 0.0255 &$\infty$& 0.1005      & $\infty$ & 0.0843&$\infty$& 0.0492 & 0.0\\\hline
+    plos2-dia [4C] & 0.0414& 0      & 0.0407 & 0      & 2.327       & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
+    mukund[3/4C]  & 185.06 & 4N 8E  & 0.3773 & 0.0    & !13.92/1.553& 0.0      & 2.062 & 0.0    & 0.230  & 0.0 \\\hline
+    node4[-]      & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
     yeast-graph   & 0.0    & 0.0    & 0.0    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
@@
 \end{table}
+%[M=8, N=2, Q=2]    
+% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
 
@@
 separating the v and the t SNAREs. 
-%The t SNAREs are labelled within compartments and v SNAREs on the edges. %\ashu{Describe the source of two examples}.
 %
@@
 %\ashu{@ankit: please discuss all the synthesis queries in the table.}
-
-Variation 1 of our tool adds new labelled edges to the graph.
+In the table, we are reporting five synthesis queries
+%
+The first one only adds new labelled edges to the graph.
 %
@@
 %
-Our tools were able to complete this graph by adding five new edges
+Our tools were able to complete the graphs by adding five new edges
 and nine new molecules in 210s.
 %
-Variation 2 of our graph adds new labels to the edge and was able to
-fix this graph with eleven new molecule labels in 180s.
+The second query adds new labels to the edge and was able to
+fix the graphs with eleven new molecule labels in 180s.
 %
-Variation 3 of our tool synthesis low depth CNF functions and was able
-to synthesis the result in 500s.
-%
-Variation 4 of our tool synthesis Boolean function based on AND, OR
-gates.
+The third query synthesizes NNF Boolean functions only containing
+$\land$ and $\lor$ gates.
 %
@@
 %
+To illustrated the versatility of our tool,
+the the fourth query synthesizes $3$-CNF functions (encoding not presented) and was able
+to synthesis the results for all graphs in 500s.
+%
+Finally, we report queries that allows both addition and deletion of parts of
+VTS\ashu{which parts}. 
 %

### 2018-05-05 papers/synth/related.tex
still two ref to go
asd

@@
 the background technology, i.e. solving of quantified
-constraints,~\cite{lonsing2010depqbf,z3Quant} has been evolving rapidly.
+constraints has been evolving rapidly~\cite{lonsing2010depqbf,z3Quant}.
+%
 
-There are a few examples of using synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}.
+There has been some work in
+applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}.
 A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.

### 2018-05-05 papers/synth/example.tex
final graph
asd
sad

@@
-% \newenvironment{psmallmatrix}
-%   {\left(\begin{smallmatrix}}
-%   {\end{smallmatrix}\right)}
+\input{fig-mukund-vts}
 
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[->,>=stealth',auto,node distance=5cm,
-  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-  \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
-  \node[main node] (ic) [below right of=ga,yshift=20mm,xshift=20mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
-  \node[main node] (er) [below right of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
-  \node[main node,text width=2.5cm] (pm) [above right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-  \node[main node] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-  \node[main node] (le) [above of=ee,yshift=-13mm,xshift=18mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
+In figure~\ref{fig:mukund-vts}, we present the VTS for mammalian cells
+obtained by studying the literature.
+%
+The
 
-  \path (ic) edge node [below] {\^{Qc6}} (ga);
-  \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);
+% and hollow arrows represent maturation edges.
 
-  %er <> ga
-  \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
-  \path (er) edge[bend left=20] node [left] {R6} (ga);
-  \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);
-
-  %ga <-> ee
-  \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
-  \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
-  \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);
-
-  %le <-> pm
-  \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
-  %ee -> le
-  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);
-
-  %pm <-> ee
-  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
-  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
-
-  %ga->pm
-  \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
-  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
-  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
-  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
-  \end{tikzpicture}
-  \caption{found-in-nature VTS}
-  \label{fig:mukund-vts}
-\end{figure}
-
-%t snares are labelled within compartmetns, v snares on the edges
-%and snare complexes on the left-hand side
-The figure~\ref{fig:mukund-vts} represent mammalian SNARE map created by studying the references~\cite{somya}. 
-To construct the map, we have assumed that vesicles only contain a single
-active v-SNARE, and we have attributed t-SNAREs and inactive v-SNAREs that
-travel between compartments to one of the known vesicles that go between
-the same source and target compartments.
-In order to identify the active SNARE complex involved in any particular
-vesicle fusion, two criteria were used: 
-\begin{enumerate}
-\item[a.] The SNARE complex is formed \textit{in vivo}. In most papers, this is determined by immunoprecipitation of the SNARE complex from the relevant cell fraction. 
-\item[b.] Blocking SNARE complex formation (for example, using antibodies against these SNAREs, or
-using cytosolic forms of these SNAREs) blocks the specific transport step.
-\end{enumerate}
-
-Note that these vesicles have been collected from multiple cell types, and
-any given cell type is likely to contain only a subset of the vesicles in
-the map.
-
-In this diagram the gray circles represent compartments, the identities of compartments are
-written within: ER=endoplasmic reticulum, ERGIC=ER-Golgi intermediate compartment,
-RE=recycling endosome, EE=early endosome, LE=late endosome, LYS=lysosome, PM=plasma
-membrane. Thin black arrows represent vesicle edges.
-% and hollow arrows represent maturation edges. 
-The set of SNAREs contained in these edges are written alongside each edge. Actual names
-of these SNAREs are mentioned in the key alongside. The red labels represent the paths taken by
-SNARES of the complex Stx-4-SNAP23-VAMP7. Here, the cycles for two SNARE molecules,
-VAMP7 and SNAP23 are complete. The green labels represent the paths taken by SNAREs of the
-complex Stx13-SNAP25-VAMP2. Here the cycle for VAMP2 is complete.The blue labels represent
-the paths taken by SNARES of the complex Stx5-Gs28-Bet1/GS15-Ykt6. Here, cycles for none of
-the SNAREs are complete. So, even though most edges known so far are present in the map, paths for molecules (SNAREs) across the cell are still not complete.
-
-We have used our tool to synthesize possible fixes to complete the graph.
-Based on the variation we were able to synthesis the this graph within 600s.
-We have created a rank of minimum edits to complete the graph.
-Our experiments suggest that the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
+We have used our tool to synthesize possible fixes to complete the
+graph. Based on the variation we were able to synthesis the this graph
+within 600s. We have created a rank of minimum edits to complete the
+graph. Our experiments suggest that the synthesis problems are
+solvable by modern solvers and the synthesis technology may be useful
+for biological research.
 

### 2018-05-05 vts-synth/examples/vts-synth-examples/yeastvts.cpp
working with 4pm

@@ -1,0 +1,46 @@
+M 
+ 20
+N 
+ 5
+Q 
+ 2
+n
+ 0 | 5+ 9+ 19+ 18+
+n
+ 1 | 1+ 7+ 11+ 4+ 8+ 14+
+n
+ 2 | 2+ 7+ 17+ 18+
+n
+ 3 | 3+ 7+ 17+ 18+
+n
+ 4 | 0+ 6+ 10+
+e 
+ 0 1 0 | 16+
+e 
+ 1 0 0 | 15+
+e
+ 1 2 0 | 12+
+e 
+ 2 3 0 | 13+
+e 
+ 1 4 0 | 16+
+e 
+ 4 1 0 | 16+
+p
+ 0 6 10 16
+p
+ 1 7 11 16
+p
+ 2 7 12 17
+p
+ 2 7 12 3
+p
+ 3 7 13 17
+p
+ 3 7 13 18
+p
+ 4 8 14 16
+p
+ 5 9 15 18
+p
+ 5 9 15 19

### 2018-05-05 vts-synth/src/load-vts.cpp

@@ -203,8 +203,8 @@ void load_vts::load() {
       case 'e': get_edge(); break;
       case 'f': get_node_function(); break;
       case 'g': get_edge_function(); break;
-      case 'p': get_pairing(); break;
-      //case 'p': qr_get_pairing(); break;
+      //case 'p': get_pairing(); break;
+      case 'p': qr_get_pairing(); break;
       default:
         load_error( "expecting a command at line", line_num );
       }

### 2018-05-05 vts-synth/src/vts-synthesis.cpp

@@ -266,8 +266,8 @@ void xor_bits ( z3::context& c,
 
 z3::expr vts::vts_synthesis ( unsigned variation ) {
   /** Basic Constraints **/
-  z3::expr vtsCons = create_vts_constraint();  
-  //z3::expr vtsCons = create_qr_vts_constraint();  
+ // z3::expr vtsCons = create_vts_constraint();  
+  z3::expr vtsCons = create_qr_vts_constraint();  
   //z3::expr nodeActive = always_active_on_node();
   z3::expr vtsActivity = vts_activity_constraint(); 
 
@@ -303,8 +303,8 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   z3::expr_vector listPresenceE = presence_edge_list();
   z3::expr_vector listActiveE = active_edge_list(); 
   z3::expr_vector listPairingM = pairing_m_list(); 
-  z3::expr_vector listReach = reach_list();
-  //z3::expr_vector listPairing4M  = pairing_m_4d_list();
+ // z3::expr_vector listReach = reach_list();
+  z3::expr_vector listPairing4M  = pairing_m_4d_list();
   
   z3::expr knownVarConstraint( ctx );
 
@@ -341,8 +341,8 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     unassigned_bits ( listE, knownEdges, unknownE ); 
     unassigned_bits ( listPresenceE, knownPresenceEdges, unknownPresenceE ); 
     unassigned_bits ( listActiveE, knownActiveEdges, unknownActiveE ); 
-    unassigned_bits ( listPairingM, knownPairingMatrix, unknownPairingM ); 
-    //unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
+  //  unassigned_bits ( listPairingM, knownPairingMatrix, unknownPairingM ); 
+    unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
   
     z3::expr_vector list_expr (ctx);
 
@@ -388,18 +388,20 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
    //                             !z3::mk_or( unknownE ) 
    //                             && !z3::mk_or ( unknownPairingM );
                                 
-    auto setUnknownVariablesFalse =  
-                                    !z3::mk_or( unknownE );
-                                   
-   auto addConstraints = nodeC;
+//    auto setUnknownVariablesFalse =  
[…]

### 2018-05-05 papers/synth/example.tex

@@
 %
-The
+The VTS has six nodes and 20+ molecules.
+%
+We can easily check that stability condition is not satisfied for
+many molecules for example ???.
+%
+It is clear that there are several unknowns about the VTS.
+%
+Please read appendix~\ref{sec:ex-vts} for more biological details.
 
@@
 We have used our tool to synthesize possible fixes to complete the
-graph. Based on the variation we were able to synthesis the this graph
-within 600s. We have created a rank of minimum edits to complete the
-graph. Our experiments suggest that the synthesis problems are
+graph.
+%
+Based on the variation we were able to synthesis the this graph
+within ??s.
+%
+We added ?? edges to make the graph stable.
+%
+We have created a rank of minimum edits to complete the
+graph.
+%
+Our experiments suggest that the synthesis problems are
 solvable by modern solvers and the synthesis technology may be useful

### 2018-05-05 papers/synth/fig-mukund-vts.tex

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[->,>=stealth',auto,node distance=5cm,
  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
  \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
  \node[main node] (ic) [below right of=ga,yshift=20mm,xshift=20mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
  \node[main node] (er) [below right of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
  \node[main node,text width=2.5cm] (pm) [above right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
  \node[main node] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
  \node[main node] (le) [above of=ee,yshift=-13mm,xshift=18mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};

  \path (ic) edge node [below] {\^{Qc6}} (ga);
  \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);

  %er <> ga
  \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
  \path (er) edge[bend left=20] node [left] {R6} (ga);
  \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);

  %ga <-> ee
  \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
  \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
  \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);

  %le <-> pm
  \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
  %ee -> le
  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  %ga->pm
  \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
  \end{tikzpicture}
  \caption{A found-in-nature VTS. Each node and edges are labelled with a set of molecules. \^{} indicates that the molecule is active.}
  \label{fig:mukund-vts}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-05-05 vts-synth/examples/vts-synth-examples/yeastvts.cpp
fix

@@ -1,46 +1,0 @@
-M 
- 20
-N 
- 5
-Q 
- 2
-n
- 0 | 5+ 9+ 19+ 18+
-n
- 1 | 1+ 7+ 11+ 4+ 8+ 14+
-n
- 2 | 2+ 7+ 17+ 18+
-n
- 3 | 3+ 7+ 17+ 18+
-n
- 4 | 0+ 6+ 10+
-e 
- 0 1 0 | 16+
-e 
- 1 0 0 | 15+
-e
- 1 2 0 | 12+
-e 
- 2 3 0 | 13+
-e 
- 1 4 0 | 16+
-e 
- 4 1 0 | 16+
-p
- 0 6 10 16
-p
- 1 7 11 16
-p
- 2 7 12 17
-p
- 2 7 12 3
-p
- 3 7 13 17
-p
- 3 7 13 18
-p
- 4 8 14 16
-p
- 5 9 15 18
-p
- 5 9 15 19

### 2018-05-05 vts-synth/src/vts-synthesis.cpp
current status

@@ -413,9 +413,9 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   // 2. Add flow of molecules to fix fusion. 
   else if ( variation == 2 )  {
     
-    z3::expr edgeActivityC = !at_least_three( unknownActiveE );
-    z3::expr edgePresenceC = !at_least_three( unknownPresenceE );
-    z3::expr addConstraints = edgeActivityC && edgePresenceC;
+   // z3::expr edgeActivityC = !at_least_three( unknownActiveE );
+   // z3::expr edgePresenceC = !at_least_three( unknownPresenceE );
+   // z3::expr addConstraints = edgeActivityC && edgePresenceC;
 
 
     // fix all unknwon bits to false.
@@ -429,7 +429,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
                       //  exists( listPairingM, 
                         exists( listPairing4M, 
                        exists( listReach, 
-                                vtsCons && knownVarConstraint && setUnknownVariablesFalse )))));
+                                vtsCons && knownVarConstraint )))));
 
     auto cons = exists( listPresenceE, 
                 exists( listE, 

### 2018-05-05 vts-synth/src/vts.cpp
printing

@@ -1096,11 +1096,14 @@ z3::expr vts::vts_fusion_constraint () {
 }
 
 z3::expr vts::vts_qr_fusion_constraint () {
+  std::cout << "Making qr fusion constraints!\n";
   z3::expr v7 = qr_4d_edge_must_fuse_with_target();       //V7
   z3::expr v8 = qr_4d_edge_fuse_only_with_target();        //V8
   auto cons = v7 && v8;
+  std::cout << "Finished qr fusion constraints!\n";
   return cons;
 }
+
 z3::expr vts::create_vts_constraint () {
 // auto cons = vts_basic_constraints() && vts_self_edges_constraint()
   auto cons = vts_basic_constraints() 

### 2018-05-05 papers/synth/example.tex
printing

--- 2018-05-05 papers/synth/example.tex
@@
-\input{fig-mukund-vts}
-
-In figure~\ref{fig:mukund-vts}, we present the VTS for mammalian cells
-obtained by studying the literature.
-%
-The
-
-% and hollow arrows represent maturation edges.
-
-We have used our tool to synthesize possible fixes to complete the
-graph. Based on the variation we were able to synthesis the this graph
-within 600s. We have created a rank of minimum edits to complete the
-graph. Our experiments suggest that the synthesis problems are
-solvable by modern solvers and the synthesis technology may be useful
-for biological research.
+% \input{fig-mukund-vts}
 

### 2018-05-05 papers/synth/intro.tex

@@
 %
+In figure~\ref{fig:mukund-vts}, we present one of the two for
+mammalian cells obtained by studying the
+literature.\footnote{Please read appendix~\ref{sec:ex-vts} for more biological details.}
+%
+The VTS has six nodes and 20+ molecules.
+%
+We can easily check that stability condition is not satisfied for
+many molecules for example ???.
+%
+It is clear that there are several unknowns about the VTS.
+%
+%
+% Our tool 
+% % and hollow arrows represent maturation edges. 
+% We have used our tool to synthesize possible fixes to complete the
+% graph.
+% %
+% Based on the variation we were able to synthesis the this graph
+% within ??s.
+%
+Our synthesis tool reports that minimum ?? edges needs to be added to make
+the VTS stable.
+%
+Our experiments suggest that the synthesis problems are
+solvable by modern solvers and the synthesis technology may be useful
+for biological research.
+%
 We have also applied our tool on various synthetic examples to
@@
 \item We have developed encoding of the synthesis problem in QBF.
-\item A user friendly and scalable tool based on a well known SMT solver Z3
+\item A user friendly and scalable tool based on QBF solvers
 \end{itemize}
@@
 %
-In section~\ref{sec:example}, we present a motivating example.
-%
+% In section~\ref{sec:example}, we present a motivating example.
+% %
 In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
@@
 
+\input{fig-mukund-vts}
+
 %%% Local Variables:

### 2018-05-05 vts-synth/src/main.cpp
z3

@@ -232,6 +232,7 @@ int main(int ac, char* av[])
     /* Run Z3 home made QBF solver or DepQbf */
     if ( useZ3 == true ) { 
       if (synthVar != -1 ) {
+        std::cout << "Using z3...\n";
         v->get_vts_for_synth( f );
       }  else {
         v->use_z3_qbf_solver( f );

### 2018-05-05 vts-synth/src/vts-synthesis.cpp

@@ -393,7 +393,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   //  auto setUnknownVariablesFalse = !z3::mk_or( unknownN )  && !z3::mk_or( unknownActiveN ) 
   //                                 && !z3::mk_or( unknownE ) && !z3::mk_or( unknownPresenceE ) && !z3::mk_or( unknownActiveE );                                  
     //auto addConstraints = nodeC;
-
+/*
     auto qvtsCons = exists( listN, 
                     exists( listActiveN, 
                     exists( listPresenceE,  
@@ -406,7 +406,9 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     //   exists( listPairing4M, 
 
     auto cons = exists( listE, 
-                        qvtsCons ); 
+                qvtsCons ); 
+    */
+    auto cons = vtsCons && knownVarConstraint;
     return cons;
   }
 

### 2018-05-05 papers/synth/experiments.tex

@@
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    \cline{2-11}
+    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
     \hline
-   \cline{2-9}
-    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\\hline
 

### 2018-05-05 papers/synth/encoding.tex
some cleanup
asd

@@
 In this section, we will present a list of synthesis problems that may
-arise from partial available information about a VTS and our solution
+arise from the partial available information about a VTS and our synthesis method
 for the problems.
@@
   \texttt{PresentCons} & = \texttt{PresentE} \land \texttt{PresentN} \land 
- \texttt{PresentP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
+  \texttt{PresentP} \land \texttt{KnownActiveE} \land \\
+  &  \texttt{KnownActiveN}
 \end{align*}
@@
 \end{align*}
-The property was proposed in~\cite{plos}.
+The property was proposed in~\cite{shukla2017discovering}.
 %
@@
   &\texttt{Gate}( x, w_1, w_2 ) = ( x  = 1 \limplies w_1  \land w_2 ) \land  
-  ( x = 2  \limplies w_1  \lor w_2 ) \land
-  ( x = 3  \limplies w_1 ) \land ...\\
+  ( x = 2  \limplies w_1  \lor w_2 ) \\
   &\texttt{Leaf}( x, [y_1,..,y_\mu] ) =
@@
   &\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
-  \texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) |
+  \texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) \\
+  & \hspace{8cm}|
   \nodef_m \text{ is undefined}\} \\
   &\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
-  \texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) | 
-  \edgef_m \text{ is undefined}
+  \texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) \\
+  & \hspace{8cm} | \edgef_m \text{ is undefined}
   \}\\
@@
   &\texttt{SynthFunction}(z,\lambda) = \\
-  & \quad\quad
+  & \quad
     (  \texttt{Consistancy}\land \texttt{Property} \land
@@
     & \texttt{FixedForNodeRepair} =  \texttt{PresentE} \land  
-      \texttt{PresentP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
+      \texttt{PresentP} \land \texttt{KnownActiveE} 
       \land \\
-  & \quad \quad \texttt{UnknownActive} \land \lnot 
+  & \quad \texttt{UnknownActive} \land \texttt{KnownActiveN} \land \lnot 
     \Lor \texttt{AbsentE} \;\union\; \texttt{AbsentNLabel} \;\union\;

### 2018-05-05 papers/synth/intro.tex
asd

@@
 %
-We have applied our tool on two found-in-nature
-VTSs~\cite{burri2004complete}.
+We have applied our tool on several VTSs including two found-in-nature
+VTSs.
 %
@@
 %
-The VTS has six nodes and 20+ molecules.
+The VTS has six nodes and 55 molecules.
 %
@@
 %
-It is clear that there are several unknowns about the VTS.
+On the example, our synthesis tool reports that minimum ?? edges needed
+to be added to make the VTS stable.
 %
-%
-% Our tool 
-% % and hollow arrows represent maturation edges. 
-% We have used our tool to synthesize possible fixes to complete the
-% graph.
-% %
-% Based on the variation we were able to synthesis the this graph
-% within ??s.
-%
-Our synthesis tool reports that minimum ?? edges needs to be added to make
-the VTS stable.
+The dashed edges are the suggested edges from our tool.
 %
@@
 %
-We have also applied our tool on various synthetic examples to
-demonstrate that our tool scale upto the graph size size nodes, which
-is the size of typical VTSs in a eukaryotic cell.
+% We have also applied our tool on various synthetic examples to
+% demonstrate that our tool scale upto the graph size size nodes, which
+% is the size of typical VTSs in a eukaryotic cell.
 

### 2018-05-05 papers/synth/experiments.tex

@@
 \end{table}
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
+    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
+    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    \cline{2-11}
+    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
+    \hline
+
+    plos1-dia[3/4C]& 0.0292&$\infty$& 0.0255 &$\infty$& 0.1005      & $\infty$ & 0.0843&$\infty$& 0.0492 & 0.0\\\hline
+    plos2-dia [4C] & 0.0414& 0      & 0.0407 & 0      & 2.327       & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
+    mukund[3/4C]  & 185.06 & 4N 8E  & 0.3773 & 0.0    & !13.92/1.553& 0.0      & 2.062 & 0.0    & 0.230  & 0.0 \\\hline
+    node4[-]      & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
+    yeast-graph   & 40.8728    & 1 edge  & 0.0    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
+    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+  \end{tabular}
+  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
+  Time is reported in seconds.}
+  \label{tab:z3-qf-graph}
+\end{table}
+
 %[M=8, N=2, Q=2]    

### 2018-05-05 papers/synth/encoding.tex
asd

@@
 \end{align*}
-We put together the constraints and obtain the following formula $\texttt{SynthE}(slimit)$.
+We put together the constraints and obtain the following formula.
 \begin{align*}
@@
 \end{align*}
-As we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
-$\texttt{Property}$ encodes the goal, and
+Similar to what we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
+$\texttt{Property}$\; encodes the goal, and
 the rest two are defined just above.

### 2018-05-05 papers/synth/prelim.tex
asd

@@
 \begin{align*}
-  \texttt{EdgeC} =\;& \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
+  \texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
   \land
@@
   \texttt{Fusion2} =\;&
-\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \neg 
+\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
+  & \hspace{2cm} \neg 
   \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
@@
 \texttt{ActivityC} states that active molecule are present.
-\texttt{PairingC} states that a molecule can either participate in fusion
-via nodes or via edges, but not both.
+\texttt{PairingC} states that all molecules are divided into
+two types and any fusing set of molecules
+must have three molecules involved from one type and one molecule from the other.
 \texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
@@
 %
-$\texttt{FailReach}(d,r')$ defines reachability in the modified VTS.
+$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
 %
@@
   % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
-  \texttt{FailReach}(d,r') = &
-   \bigwedge\limits_{i,j,p}  r^{\prime}_{i,j,p} \limplies [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
+  \texttt{FReach}(d,r') = &\hspace{-1ex}
+   \bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
   \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
@@
   \texttt{Connected}(k) = & \forall d.\;
-          (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FailReach}(d,r')
+          (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
                                 \land \texttt{Connected}(r'))

### 2018-05-05 papers/synth/intro.tex
asd

@@
 %
-Our experiments suggest that the synthesis problems are
+Our experiments suggest that some of the synthesis problems are
 solvable by modern solvers and the synthesis technology may be useful

### 2018-05-06 papers/synth/experiments.tex
z3 tabbel

--- 2018-05-05 papers/synth/experiments.tex
@@
 \end{table}
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
+    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
+    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    \cline{2-11}
+    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
+    \hline
+
+    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & del: . 1 edge, 1 edge bit 1 node, 1 act each add: 1 edge bit 1 node bit\\\hline
+    plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
+    mukund  & 3.483 & 1 edge  & 4.379 & 5 edge bits  & 6.340[-] / 29.980 & 2 edge, 10 edge bits  & 10.4052[-] & [-] & 3.650  &  del : 1 edge, 2 edge bit, 1 active node.
+add:1 edge 4 edge bit 4 node bit, 2 act \\\hline
+    node4  & 4.1502  & 1 edge  & 10.562  & 12 mol & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & del: 2 edge, 2 act, 1 node and 1 act. add: 12 node, 8 edge, 1 edge bits \\\hline
+    yeast-graph & 40.8728  & 1 edge  &   timeout  & N/A   & 1313.91  & 1 edge  & 517.619   & 1 edge    & 380.43  &  del: 1 edge, 2 node, 2 act bits each. add: 2 edge, 12 mol, 7 node bits \\\hline
+    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+  \end{tabular}
+  \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
+  Time is reported in seconds.}
+  \label{tab:z3-qf-graph}
+\end{table}
+
 %[M=8, N=2, Q=2]    

### 2018-05-06 vts-synth/src/card-constr.cpp

@@ -17,6 +17,16 @@ VecExpr vts::flattern_3d ( Vec3Expr& dump ) {
   return d1;
 }
 
+z3::expr vts::cardC (z3::expr_vector d1, unsigned drop_count) {
+   z3::expr expr = ctx.int_val(0);
+        auto tt = ctx.bool_val(true);
+        for (unsigned i=0; i < d1.size(); i++ ) {
+         expr = expr + z3::ite( d1[i], ctx.int_val(1), ctx.int_val(0) ) ;
+       }
+     // std::cout << "The total count is : " << expr;  
+      return (tt && (expr == ctx.int_val(drop_count)) );
+}
+
 
 // Use PbEq for exactly k.
 z3::expr vts::exactly_k_drops( unsigned drop_count, Vec3Expr& dump ) { //

### 2018-05-06 vts-synth/src/load-vts.cpp

@@ -203,8 +203,8 @@ void load_vts::load() {
       case 'e': get_edge(); break;
       case 'f': get_node_function(); break;
       case 'g': get_edge_function(); break;
-    //  case 'p': get_pairing(); break;
-      case 'p': qr_get_pairing(); break;
+      case 'p': get_pairing(); break;
+     // case 'p': qr_get_pairing(); break;
       default:
         load_error( "expecting a command at line", line_num );
       }

### 2018-05-06 vts-synth/src/vts-synthesis.cpp

@@ -266,8 +266,8 @@ void xor_bits ( z3::context& c,
 
 z3::expr vts::vts_synthesis ( unsigned variation ) {
   /** Basic Constraints **/
- // z3::expr vtsCons = create_vts_constraint();  
-  z3::expr vtsCons = create_qr_vts_constraint();  
+  z3::expr vtsCons = create_vts_constraint();  
+  //z3::expr vtsCons = create_qr_vts_constraint();  
   //z3::expr nodeActive = always_active_on_node();
  // z3::expr vtsActivity = vts_activity_constraint(); 
 
@@ -302,9 +302,9 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   z3::expr_vector listE = edge_list(); 
   z3::expr_vector listPresenceE = presence_edge_list();
   z3::expr_vector listActiveE = active_edge_list(); 
-//  z3::expr_vector listPairingM = pairing_m_list(); 
+  z3::expr_vector listPairingM = pairing_m_list(); 
   z3::expr_vector listReach = reach_list();
-  z3::expr_vector listPairing4M  = pairing_m_4d_list();
+//  z3::expr_vector listPairing4M  = pairing_m_4d_list();
   
   z3::expr knownVarConstraint( ctx );
 
@@ -341,8 +341,8 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     unassigned_bits ( listE, knownEdges, unknownE ); 
     unassigned_bits ( listPresenceE, knownPresenceEdges, unknownPresenceE ); 
     unassigned_bits ( listActiveE, knownActiveEdges, unknownActiveE ); 
-  //  unassigned_bits ( listPairingM, knownPairingMatrix, unknownPairingM ); 
-    unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
+    unassigned_bits ( listPairingM, knownPairingMatrix, unknownPairingM ); 
+  //  unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
   
     z3::expr_vector list_expr (ctx);
 
@@ -372,12 +372,13 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
 
   // 1. Add edge to achieve graph stability and k connected. 
   if ( variation == 1 ) {
-     
+   // auto nodeC = cardC( unknownN, 4 );
+   // auto edgeC = cardC( unknownE, 1);
[…]

### 2018-05-06 vts-synth/src/vts.h

@@ -197,7 +197,7 @@ public:
 
   z3::expr at_most_one ( z3::expr_vector dump );
 
-  
+  z3::expr cardC (z3::expr_vector d1, unsigned drop_count);
   /** connectivity costraints **/
   // todo: variables are needed to be parametrized
   z3::expr only_present_edges_can_be_dropped( Vec3Expr& dump ); //

### 2018-05-06 papers/synth/experiments.tex
as

@@
+\begin{landscape}
 \begin{table}[t]
@@
 \end{table}
+\end{landscape}
 
@@
 minimum updates.
+% %
+% Our tools were able to complete the graphs by adding five new edges
+% and nine new molecules in 210s.
 %
-Our tools were able to complete the graphs by adding five new edges
-and nine new molecules in 210s.
-%
-The second query adds new labels to the edge and was able to
-fix the graphs with eleven new molecule labels in 180s.
+The second query adds new labels to the edge.
+%  and was able to
+% fix the graphs with eleven new molecule labels in 180s.
 %
 The third query synthesizes NNF Boolean functions only containing
-$\land$ and $\lor$ gates.
+$\land$ and $\lor$ gates for activity functions, while allowing
+more edges to be added.
 %
-The result shows the basic template of 4 leaves and 3 gates we allow
-the user to provide its own template in our front-end language.
+The result shows the basic template of 4 leaves and 3 gates.
 %
-The tool was able to synthesize the Boolean functions in 470s.
+% The tool was able to synthesize the Boolean functions in 470s.
 %
-To illustrated the versatility of our tool,
-the the fourth query synthesizes $3$-CNF functions (encoding not presented) and was able
-to synthesis the results for all graphs in 500s.
+To illustrated the versatility of our tool, the the fourth query
+synthesizes $3$-CNF functions (encoding not presented).
+%  and was able to
+% synthesis the results for all graphs in 500s.
 %

### 2018-05-06 papers/synth/experiments.tex
as

@@
   \end{tabular}
-  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
+  \caption{Run-times for synthesis queries with~\depqbf (in secs). \#C  stands for minimum changes.
   Time is reported in seconds.}
@@
   \centering
-  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
+  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
@@
   \end{tabular}
-  \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
+  \caption{Run-times for synthesis queries with~\depqbf (in secs). \#C  stands for minimum changes.
   Time is reported in seconds.}

### 2018-05-06 papers/synth/experiments.tex
asd

--- 2018-05-06 papers/synth/experiments.tex
@@
-\begin{landscape}
-\begin{table}[t]
+% \begin{landscape}
+\begin{sidewaysfigure}[t]
   \centering
@@
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    {\multirow{2}{*} \textbf{Table (a)}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
     \cline{2-11}
@@
   \end{tabular}
-  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
-  Time is reported in seconds.}
-  \label{tab:qf-graph}
-\end{table}
-
-\begin{table}[t]
+  \mbox{}\\\mbox{}\\
+  % \caption{Run-times for synthesis queries with~\depqbf (in secs). \#C  stands for minimum changes.
+  % Time is reported in seconds.}
+  % \label{tab:qf-graph}
+% \end{table}
+% \begin{table}[t]
   \centering
-  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
+  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    {\multirow{2}{*} \textbf{Table (b)}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
     \cline{2-11}
@@
   \end{tabular}
-  \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
-  Time is reported in seconds.}
-  \label{tab:z3-qf-graph}
-\end{table}
-\end{landscape}
+  \caption{Run-times for synthesis queries. \#C  stands for minimum changes. Time is reported
+    in seconds. (a) solver used~\depqbf (b) solver used~\zthree}
+  \label{tab:qf-graph}
+\end{sidewaysfigure}
+% \end{landscape}
 
@@
 %
-Since, the formulas involve alternation of quantifiers over Boolean
-variables Z3 is not a suitable choice.
+Since, some of the formulas involve alternation of quantifiers over
+Boolean variables Z3 is not a suitable choice for those examples.
 %
-We translate the formula created by Z3 tool into standard
+We translate the formulas created by Z3 tool into standard
 QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
@@
 %
-The results are presented in table~\ref{tab:qf-graph}.
+The results are presented in table~\ref{tab:qf-graph} for both the solvers
+\depqbf and \zthree.
 %
-The experiments were conducted on a machine,
-with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
+% The experiments were conducted on a machine,
+% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
+%
+The experiments were conducted with 1 hour timeout.
 %
@@
 %
-The fifth VTS is taken from "A complete set of SNAREs in yeast"
-~\cite{burri2004complete} paper. It has been adapted from the paper by
-separating the v and the t SNAREs. 
+The fifth VTS is taken from~\cite{burri2004complete}.
 %
@@
 %
-Finally, we report queries that allows both addition and deletion of parts of
-VTS\ashu{which parts}. 
+Finally, we report queries that allows both addition and deletion of edges, and labels
+of node and labels. 
 %

### 2018-05-06 papers/synth/intro.tex
asd

@@
 %
-In figure~\ref{fig:mukund-vts}, we present one of the two for
-mammalian cells obtained by studying the
-literature.\footnote{Please read appendix~\ref{sec:ex-vts} for more biological details.}
-%
-The VTS has six nodes and 55 molecules.
-%
-We can easily check that stability condition is not satisfied for
-many molecules for example ???.
-%
-On the example, our synthesis tool reports that minimum ?? edges needed
-to be added to make the VTS stable.
-%
-The dashed edges are the suggested edges from our tool.
-%
+
+% \input{fig-mukund-vts}
+% %
+% In figure~\ref{fig:mukund-vts}, we present one of the two for
+% mammalian cells obtained by studying the
+% literature.\footnote{Please read appendix~\ref{sec:ex-vts} for more biological details.}
+% %
+% The VTS has six nodes and 55 molecules.
+% %
+% We can easily check that stability condition is not satisfied for
+% many molecules for example ???.
+% %
+% On the example, our synthesis tool reports that minimum ?? edges needed
+% to be added to make the VTS stable.
+% %
+% The dashed edges are the suggested edges from our tool.
+% %
+
 Our experiments suggest that some of the synthesis problems are
@@
 
-\input{fig-mukund-vts}
-
 %%% Local Variables:

### 2018-05-06 papers/synth/experiments.tex
running qbf

--- 2018-05-06 papers/synth/experiments.tex
@@
-\begin{landscape}
 \begin{table}[t]
@@
 
-    plos1-dia[3/4C]& 0.0292&$\infty$& 0.0255 &$\infty$& 0.1005      & $\infty$ & 0.0843&$\infty$& 0.0492 & 0.0\\\hline
-    plos2-dia [4C] & 0.0414& 0      & 0.0407 & 0      & 2.327       & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
+    plos1-dia[3C/4C]& 0.326 &$\infty$& 0.312 &$\in0.224fty$& 0.669 & $\infty$ & 0.966 &$\infty$& !0.985/ & add: 1 edge bit, del: 2 edge bit, 1 actv E, 1 act node\\\hline
+    plos2-dia[4C] & 0.266 & 0   & 0.248 & 0  & 2.327  & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
     mukund[3/4C]  & 185.06 & 4N 8E  & 0.3773 & 0.0    & !13.92/1.553& 0.0      & 2.062 & 0.0    & 0.230  & 0.0 \\\hline
@@
 \end{table}
-\end{landscape}
 
@@
 minimum updates.
-% %
-% Our tools were able to complete the graphs by adding five new edges
-% and nine new molecules in 210s.
 %
-The second query adds new labels to the edge.
-%  and was able to
-% fix the graphs with eleven new molecule labels in 180s.
+Our tools were able to complete the graphs by adding five new edges
+and nine new molecules in 210s.
+%
+The second query adds new labels to the edge and was able to
+fix the graphs with eleven new molecule labels in 180s.
 %
 The third query synthesizes NNF Boolean functions only containing
-$\land$ and $\lor$ gates for activity functions, while allowing
-more edges to be added.
+$\land$ and $\lor$ gates.
 %
-The result shows the basic template of 4 leaves and 3 gates.
+The result shows the basic template of 4 leaves and 3 gates we allow
+the user to provide its own template in our front-end language.
 %
-% The tool was able to synthesize the Boolean functions in 470s.
+The tool was able to synthesize the Boolean functions in 470s.
 %
-To illustrated the versatility of our tool, the the fourth query
-synthesizes $3$-CNF functions (encoding not presented).
-%  and was able to
-% synthesis the results for all graphs in 500s.
+To illustrated the versatility of our tool,
+the the fourth query synthesizes $3$-CNF functions (encoding not presented) and was able
+to synthesis the results for all graphs in 500s.
 %

### 2018-05-06 vts-synth/src/vts-synthesis.cpp

@@ -272,7 +272,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
  // z3::expr vtsActivity = vts_activity_constraint(); 
 
   /** Connectedness Constraints */
-  //z3::expr kConnCons = k_connected_graph_constraint( 3, false ); 
+  z3::expr kConnCons = k_connected_graph_constraint( 4, false ); 
  // z3::expr V5 = no_self_edges();
   
   //z3::expr inputCons = ctx.bool_val(true);
@@ -376,7 +376,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
    // auto edgeC = cardC( unknownE, 1);
     // auto edgeC =  pbeq(unknownE , 1, int 1);
     // auto edgeC =  atmost(unknownE, 1);
-    // auto edgeC = !at_least_two( unknownE );
+//     auto edgeC = !at_least_two( unknownE );
     // auto edgeC = !at_least_three( unknownE );
   // auto edgeC = mk_le_k_bits( unknownE, 0);
     // auto edgeActivityC = !at_least_three( unknownActiveE );
@@ -400,13 +400,13 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
      ;
 
    //auto addConstraints = nodeC;
-/*
+
     auto qvtsCons = exists( listN, 
                     exists( listActiveN, 
                     exists( listPresenceE,  
                     exists( listActiveE, 
-               //     exists( listPairingM, 
-                    exists( listPairing4M,
+                    exists( listPairingM, 
+                //    exists( listPairing4M,
                     exists( listReach, 
                             vtsCons && knownVarConstraint ))))));   
 
@@ -414,11 +414,11 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
 
 
     auto cons = exists( listE, 
-                qvtsCons ); 
-    */
+                 qvtsCons && kConnCons ); 
+    
 
 
-    auto cons = vtsCons && knownVarConstraint && setUnknownVariablesFalse;
+  //  auto cons = vtsCons && knownVarConstraint && setUnknownVariablesFalse;
     return cons;
   }
 
@@ -430,7 +430,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
    // z3::expr addConstraints = edgeActivityC && edgePresenceC;
     auto edgeC = mk_le_k_bits( unknownPresenceE, 0);
      
-     /* 
+      
     // fix all unknwon bits to false.
[…]

### 2018-05-06 papers/synth/experiments.tex
experiment update

@@
 
-    plos1-dia[3C/4C]& 0.326 &$\infty$& 0.312 &$\in0.224fty$& 0.669 & $\infty$ & 0.966 &$\infty$& !0.985/ & add: 1 edge bit, del: 2 edge bit, 1 actv E, 1 act node\\\hline
-    plos2-dia[4C] & 0.266 & 0   & 0.248 & 0  & 2.327  & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
-    mukund[3/4C]  & 185.06 & 4N 8E  & 0.3773 & 0.0    & !13.92/1.553& 0.0      & 2.062 & 0.0    & 0.230  & 0.0 \\\hline
+    plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\in0.224fty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & add: 1 edge bit, 1 node bit, del: 1 E, 1 AE, 1 AN\\\hline
+    plos2-dia[4C] & 0.266 & 0   & 0.3229 & 0  & 1.409  & 0 & 2.114 & 0 &  0.3378 & 0 \\\hline
+    mukund[3/4C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
     node4[-]  & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
-    yeast-graph   & 0.0    & 0.0    & 0.0    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
+    yeast-graph[3C]   & 95.0162    & 1 edge   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
     mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
@@
 
-    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & del: . 1 edge, 1 edge bit 1 node, 1 act each add: 1 edge bit 1 node bit\\\hline
+    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PN, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
     plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
-    mukund  & 3.483 & 1 edge  & 4.379 & 5 edge bits  & 6.340[-] / 29.980 & 2 edge, 10 edge bits  & 10.4052[-] & [-] & 3.650  &  del : 1 edge, 2 edge bit, 1 active node.
-add:1 edge 4 edge bit 4 node bit, 2 act \\\hline
-    node4  & 4.1502  & 1 edge  & 10.562  & 12 mol & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & del: 2 edge, 2 act, 1 node and 1 act. add: 12 node, 8 edge, 1 edge bits \\\hline
-    yeast-graph & 40.8728  & 1 edge  &   timeout  & N/A   & 1313.91  & 1 edge  & 517.619   & 1 edge    & 380.43  &  del: 1 edge, 2 node, 2 act bits each. add: 2 edge, 12 mol, 7 node bits \\\hline
-    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+    mukund  & 3.483 & 1 E  & 4.379 & 5 PE  & 6.340[-] / 29.980 & 2 E, 10 PE  & 10.4052[-] & [-] & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
+    node4  & 4.1502  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
+    yeast-graph & 40.8728  & 1 E  &   timeout  & N/A   & 1313.91  & 1 E  & 517.619   & 1 E & 380.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
+    mammal-graph   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
   \end{tabular}

### 2018-05-06 vts-synth/src/vts-synthesis.cpp

@@ -272,7 +272,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
  // z3::expr vtsActivity = vts_activity_constraint(); 
 
   /** Connectedness Constraints */
-  z3::expr kConnCons = k_connected_graph_constraint( 4, false ); 
+  z3::expr kConnCons = k_connected_graph_constraint( 3, false ); 
  // z3::expr V5 = no_self_edges();
   
   //z3::expr inputCons = ctx.bool_val(true);
@@ -378,7 +378,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     // auto edgeC =  atmost(unknownE, 1);
 //     auto edgeC = !at_least_two( unknownE );
     // auto edgeC = !at_least_three( unknownE );
-  // auto edgeC = mk_le_k_bits( unknownE, 0);
+  auto edgeC = mk_le_k_bits( unknownE, 1);
     // auto edgeActivityC = !at_least_three( unknownActiveE );
     //auto edgePresenceC = !at_least_four( unknownPresenceE );
     // auto nodeC = !at_least_four( unknownN );    
@@ -428,7 +428,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
    // z3::expr edgeActivityC = !at_least_three( unknownActiveE );
    // z3::expr edgePresenceC = !at_least_three( unknownPresenceE );
    // z3::expr addConstraints = edgeActivityC && edgePresenceC;
-    auto edgeC = mk_le_k_bits( unknownPresenceE, 0);
+    auto edgeC = mk_le_k_bits( unknownPresenceE, 4);
      
       
     // fix all unknwon bits to false.
@@ -604,16 +604,16 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     Vec4Expr xorPresenceEdges;
     Vec4Expr xorActiveEdges;
     Vec2Expr xorPairingMatrix;
-    //Vec4Expr xorReach;
+    Vec4Expr xorReach;
     
     popl2 ( xorNodes, N, M, "xn" );
     popl2 ( xorActiveNodes, N, M, "xa" );
     popl3( xorEdges, N, N, E_arity, "xz" ); 
     popl4 ( xorPresenceEdges, N, N, E_arity, M, "xe" );
     popl4 ( xorActiveEdges, N, N, E_arity, M, "xb" );
[…]

### 2018-05-06 papers/synth/ex-vts.tex
asd

Here we will present the two VTS collected from the literature.

\subsection{Mammalian VTS}
\input{fig-mukund-vts}

The figure~\ref{fig:mukund-vts} represent mammalian SNARE map
created by studying the wide array of literature.
% 
To construct the map, we have assumed that vesicles only contain a
single active v-SNARE, and we have attributed t-SNAREs and inactive
v-SNAREs that travel between compartments to one of the known vesicles
that go between the same source and target compartments.
%
In order to identify the active SNARE complex involved in any
particular vesicle fusion, we used two criteria.
%
The SNARE complex is formed \textit{in vivo}. In most papers, this is
determined by immunoprecipitation of the SNARE complex from the
relevant cell fraction.
%
Blocking SNARE complex formation (for example, using antibodies
against these SNAREs, or using cytosolic forms of these SNAREs) blocks
the specific transport step.
%
Note that these vesicles have been collected from multiple cell types, and
any given cell type is likely to contain only a subset of the vesicles in
the map.

In this figure the rectangles represent compartments, the identities
of compartments are written within: ER=endoplasmic reticulum,
ERGIC=ER-Golgi intermediate compartment, RE=recycling endosome,
EE=early endosome, LE=late endosome, LYS=lysosome, PM=plasma
membrane. The arrows represent vesicle edges.

% \ashu{Adopt }
% The set of SNAREs contained in these edges are written alongside each
% edge.
% %
% Actual names of these SNAREs are mentioned in the key
% alongside.
% %
% The red labels represent the paths taken by SNARES of the
% complex Stx-4-SNAP23-VAMP7.
% %
% Here, the cycles for two SNARE molecules,
% VAMP7 and SNAP23 are complete.
% %
% The green labels represent the paths
% taken by SNAREs of the complex Stx13-SNAP25-VAMP2.
% %
% Here the cycle for
% VAMP2 is complete.The blue labels represent the paths taken by SNARES
% of the complex Stx5-Gs28-Bet1/GS15-Ykt6.
% %
% Here, cycles for none of the
% SNAREs are complete.
% %
% So, even though most edges known so far are
% present in the map, paths for molecules (SNAREs) across the cell are
% still not complete.

\subsection{Yeast VTS}

\input{fig-yeast-vts}

In figure~\ref{fig:yeast-vts}, we present the yeast VTS.
%
We have borrowed the VTS from~\cite{burri2004complete}.
%
It has been adapted from the paper by
separating the v and the t SNAREs. 
%
It is clear that it is an incomplete description of the VTS.
%
For example, the inactive molecules were not reported in the reference.
%
We are currently searching for more literature that can help us complete
all known information about the VTS.
%

% It is important to note that it is not trivial collect all the information
% about such systems.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-05-06 papers/synth/experiments.tex
asd

--- 2018-05-06 papers/synth/experiments.tex
@@
-% \begin{landscape}
 \begin{sidewaysfigure}[t]
   \centering
-  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
+  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Table (a)}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
     \cline{2-11}
@@
   \end{tabular}
-  \mbox{}\\\mbox{}\\
-  % \caption{Run-times for synthesis queries with~\depqbf (in secs). \#C  stands for minimum changes.
+%   \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
 %   Time is reported in seconds.}
@@
 % \end{table}
+
 % \begin{table}[t]
@@
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Table (b)}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
     \cline{2-11}

### 2018-05-06 papers/synth/experiments.tex
updated table

--- 2018-05-06 papers/synth/experiments.tex
@@
     mukund[3/4C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-    node4[-]  & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
-    yeast-graph[3C]   & 95.0162    & 1 edge   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
+    node4[-]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
+    yeast-graph[3C]   & 95.0162    & 1 E   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
     mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline

### 2018-05-06 vts-synth/src/vts-synthesis.cpp

@@ -272,7 +272,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
  // z3::expr vtsActivity = vts_activity_constraint(); 
 
   /** Connectedness Constraints */
-  z3::expr kConnCons = k_connected_graph_constraint( 3, false ); 
+  z3::expr kConnCons = k_connected_graph_constraint( 4, false ); 
  // z3::expr V5 = no_self_edges();
   
   //z3::expr inputCons = ctx.bool_val(true);
@@ -428,7 +428,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
    // z3::expr edgeActivityC = !at_least_three( unknownActiveE );
    // z3::expr edgePresenceC = !at_least_three( unknownPresenceE );
    // z3::expr addConstraints = edgeActivityC && edgePresenceC;
-    auto edgeC = mk_le_k_bits( unknownPresenceE, 4);
+    auto edgeC = mk_le_k_bits( unknownPresenceE, 12);
      
       
     // fix all unknwon bits to false.
@@ -672,22 +672,22 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     auto xadd_a_edge_C = !at_least_two( xorActiveNVec );
 */
 
-    auto xadd_node_C = mk_le_k_bits( xorNVec, 1 );
-    auto xadd_active_node_C =  mk_le_k_bits( xorActiveNVec, 1 );
-    auto xadd_edge_C =  mk_le_k_bits( xorEVec, 1 );
+    auto xadd_node_C = mk_le_k_bits( xorNVec, 2);
+    auto xadd_active_node_C =  mk_le_k_bits( xorActiveNVec, 2 );
+    auto xadd_edge_C =  mk_le_k_bits( xorEVec, 2 );
     auto xadd_p_edge_C = mk_le_k_bits( xorPresenceEVec, 2);
-    auto xadd_a_edge_C = mk_le_k_bits( xorActiveEVec, 1);
+    auto xadd_a_edge_C = mk_le_k_bits( xorActiveEVec, 2);
     
     auto edgeC = 
-      mk_le_k_bits( unknownE, 1);
+      mk_le_k_bits( unknownE, 2);
     auto edgePresenceC =
-      mk_le_k_bits( unknownPresenceE, 4);
+      mk_le_k_bits( unknownPresenceE, 12);
     auto nodeC = 
[…]

### 2018-05-06 papers/synth/model.tex
asd

@@
-\ashu{Discuss the model in Biological terms.}
-
-%
-Therefore, the model only has aspects of a network or a graph.\\
-
 The molecules transported by the VTS are themselves its regulators. The molecules in a
 compartment/vesicle may be active or inactive. The molecules that are responsible for vesicle fusion
-are called SNARE proteins []. Active SNAREs present on vesicles (v-SNAREs) bind with their
+are called SNARE proteins~\cite{jahn2006snares, wickner2008membrane}. Active SNAREs present on vesicles (v-SNAREs) bind with their
 cognate active SNAREs on the target compartment (t-SNAREs) to enable vesicle fusion. A cell
@@
 Based on amino acid sequence, SNARE motifs fall into 4 classes: Qa, Qb, Qc, and R~\cite{jahn2006snares}.
-Across all intracellular vesicle fusion reactions, the associated SNARE complexes contain one of each of the four kinds of SNARE motifs; the v-SNARE contributes a single SNARE motif, usually it is an R-SNARE (although, exceptions are known: Sec22b and Ykt6 are both R-SNAREs which form parts of t-SNAREs~\cite{hong}) and the rest of the three SNARE
+Across all intracellular vesicle fusion reactions, the associated SNARE complexes contain one of each of the four kinds of SNARE motifs; the v-SNARE contributes a single SNARE motif, usually it is an R-SNARE (although, exceptions are known: Sec22b and Ykt6 are both R-SNAREs which form parts of t-SNAREs~\cite{hong2005snares}) and the rest of the three SNARE
 motifs are contributed by the t-SNARE. In the cell, different vesicle fusion reactions are associated with distinct v- and t-SNARE pairs.

### 2018-05-06 papers/synth/experiments.tex
asd
push

@@
     plos2-dia[4C] & 0.266 & 0   & 0.3229 & 0  & 1.409  & 0 & 2.114 & 0 &  0.3378 & 0 \\\hline
-    mukund[3/4C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-    node4[-]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-    yeast-graph[3C]   & 95.0162    & 1 E   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
-    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+    mammal-vts[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
+    node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
+    yeast-graph[3C]   & 95.016    & 1 E   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
+       & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
   \end{tabular}

### 2018-05-06 papers/synth/experiments.tex
asd

--- 2018-05-06 papers/synth/experiments.tex
@@
   \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
+% \begin{table}[t]
+%   \centering
+%   \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    {\multirow{2}{*} \textbf{Table a}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
     \cline{2-11}
@@
     plos2-dia[4C] & 0.266 & 0   & 0.3229 & 0  & 1.409  & 0 & 2.114 & 0 &  0.3378 & 0 \\\hline
-    mukund[3/4C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-    node4[-]  & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
-    yeast-graph[3C]   & 95.0162    & 1 edge   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
-    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+    mammal-vts[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
+    node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
+    yeast-graph[3C]   & 95.016    & 1 E   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
+       & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
   \end{tabular}
@@
 % \end{table}
-
-% \begin{table}[t]
-  \centering
   \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
     {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Benchmark}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
+    {\multirow{2}{*} \textbf{Table b}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
     \cline{2-11}
@@
     in seconds. (a) solver used~\depqbf (b) solver used~\zthree}
-  \label{tab:qf-graph}
+  % \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
+  % Time is reported in seconds.}
+  \label{tab:z3-qf-graph}
 \end{sidewaysfigure}
-% \end{landscape}
 
@@
 \depqbf and \zthree.
+%
+To use~\zthree, we remove \texttt{Connected} constraints, such the query becomes
+quantifier free.
 %

### 2018-05-06 papers/synth/prelim.tex
minor edits

@@
 two partitions $Q$ and $R$ such that
-for each $P \in \pairs, |P \intersect Q| \leq 3 \land |P \intersect R| = 1 $, and
+for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $, and
 for each $(n,M',n') \in \edges$, $n \neq n'$ and

### 2018-05-06 papers/synth/experiments.tex
graph labelling fixed
final version

@@
 
-    plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\in0.224fty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & add: 1 edge bit, 1 node bit, del: 1 E, 1 AE, 1 AN\\\hline
-    plos2-dia[4C] & 0.266 & 0   & 0.3229 & 0  & 1.409  & 0 & 2.114 & 0 &  0.3378 & 0 \\\hline
-    mammal-vts[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & - & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-    node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-    yeast-graph[3C]   & 95.016    & 1 E   & 94.5206    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
-       & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+    plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\infty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & -1 E, -1 AE, -1 AN. +1 E, +1 N. \\\hline
+    plos2-dia[4C] & 0.266 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
+    small-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline
+    node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE.\\\hline
+    yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
+   %    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
   \end{tabular}
@@
 
-    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PN, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
+    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PE, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
     plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
-    mukund  & 3.483 & 1 E  & 4.379 & 5 PE  & 6.340[-] / 29.980 & 2 E, 10 PE  & 10.4052[-] & [-] & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-    node4  & 4.1502  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-    yeast-graph & 40.8728  & 1 E  &   timeout  & N/A   & 1313.91  & 1 E  & 517.619   & 1 E & 380.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-    mammal-graph   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+    small-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
+    node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
+    yeast-graph & 40.872  & 1 E  &   timeout  & N/A   & 131.91  & 1 E  & 97.619   & 1 E & 70.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
+   % mammal-graph   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
   \end{tabular}
   \caption{Run-times for synthesis queries. \#C  stands for minimum changes. Time is reported
-    in seconds. (a) solver used~\depqbf (b) solver used~\zthree}
+    in seconds. (a) solver used~\depqbf (b) solver used~\zthree. The small-mammal is a subgraph of the complete mammalian graph. In the Add/Delete parts column, '+'n sign is used to show
+    addition of n number of the molecule and '-'n is used to show the removal of n number of molecules. 
+    In the table N represents node label, AN represent active node molecules, E represents edges, PE as the presence of molecules on the edge and AE as active molecules on the edge. 
+      }
   % \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
@@
 of node and labels.
+
 %

### 2018-05-06 papers/synth/conclusion.tex

@@
 We demonstrated that our tool based on the encodings
-scale up to the relevant sizes of the VTSs. 
+scale up to the relevant sizes of the VTSs for some synthesis queries.
+%
+Our tool timedout on larger examples.
+%
+We are working to improve the performance of our tool.
 %

### 2018-05-06 papers/synth/experiments.tex
add
type
experminent fix

@@
   \caption{Run-times for synthesis queries. \#C  stands for minimum changes. Time is reported
-    in seconds. (a) solver used~\depqbf (b) solver used~\zthree. The small-mammal is a subgraph of the complete mammalian graph. In the Add/Delete parts column, '+'n sign is used to show
-    addition of n number of the molecule and '-'n is used to show the removal of n number of molecules. 
-    In the table N represents node label, AN represent active node molecules, E represents edges, PE as the presence of molecules on the edge and AE as active molecules on the edge. 
+    in seconds. (a) solver used~\depqbf (b) solver used~\zthree. The small-mammal is a subgraph of the complete mammalian graph. In the Add/Delete parts column, `+'n sign is used to show
+    addition of n number of the molecules, similarly `-'n is used to show the removal of n number of molecules. 
+  In the table N represents node labels, AN represents active node molecules, E represents edges, PE represents the presence of molecules on the edge and AE represents active molecules on the edge. 
+    The C stands for graph connectedness which is part of only DepQBF experiments.
       }
@@
   % Time is reported in seconds.}
-  \label{tab:z3-qf-graph}
+  \label{tab:qf-graph}
 \end{sidewaysfigure}
@@
 %
-To use~\zthree, we remove \texttt{Connected} constraints, such the query becomes
+To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
 quantifier free.
@@
 %
-The experiments were conducted with 1 hour timeout.
+The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
+CPU @ 1.90GHz processor and 4GB RAM with 900s timeout.
+%The experiments were conducted with 900s timeout.
 %

### 2018-05-06 papers/synth/model.tex
appendix fix

@@
 
-We have extended the model by considering each complex molecule as distinct.
 In the previous paper, we have considered three Q SNARES as a single molecule.
-We also do not assume that SNARE type distribution is even in the whole system.
-The fusion is now driven by the active presence of three Q SNARE and one R SNARE molecule, present in any combination on edge and on the target compartment.
+We have extended this model by considering each complex molecule as distinct.
+In contrast to the previous model we allow SNARE type distribution across the whole system to be uneven.
+The fusion is now driven by the active combination of three Q SNARE and one R SNARE molecule.
 We have relaxed the pairing matrix constraint to comply with this fact.
-In order for the biological efficiency and optimality reasons we still do not allow self-edges to be present in the VTS.
+For biological efficiency and optimality reasons we do not allow self-edges to be present in the VTS.
 %\begin{enumerate} 

### 2018-05-06 papers/synth/model.tex
appendix fix

@@
 \begin{enumerate}
-\item[1] A cell is a set of compartments exchanging vesicles.
-\item[2] Compartments are neither created nor destroyed.
-\item[3] Each compartment is in steady state, gain and loss balance.
-\item[4] Molecules are neither created nor destroyed.
-\item[5] Molecules move via vesicles of uniform size.
+\item A cell is a set of compartments exchanging vesicles.
+\item Compartments are neither created nor destroyed.
+\item Each compartment is in steady state, gain and loss balance.
+\item Molecules are neither created nor destroyed.
+\item Molecules move via vesicles of uniform size.
 \item Identical vesicles have identical target compartments.
@@
 We have extended this model by considering each complex molecule as distinct.
-In contrast to the previous model we allow SNARE type distribution across the whole system to be uneven.
+In contrast to the previous model, we allow SNARE type distribution across the whole system to be uneven.
 The fusion is now driven by the active combination of three Q SNARE and one R SNARE molecule.
 We have relaxed the pairing matrix constraint to comply with this fact.
-For biological efficiency and optimality reasons we do not allow self-edges to be present in the VTS.
+For biological efficiency and optimality reasons, we do not allow self-edges to be present in the VTS.
 %\begin{enumerate} 

### 2018-05-10 papers/synth/model.tex
initial version

@@
 
-In the previous paper, we have considered three Q SNARES as a single molecule.
-We have extended this model by considering each complex molecule as distinct.
-In contrast to the previous model, we allow SNARE type distribution across the whole system to be uneven.
-The fusion is now driven by the active combination of three Q SNARE and one R SNARE molecule.
+The paper~\cite{shukla2017discovering} consider three Q SNARES as a single molecule,  we have extended this model by considering each complex molecule as distinct.
+In contrast to the~\cite{shukla2017discovering}, we allow Q and R-SNARE type distribution across the whole system to be uneven.
+In our model fusion is driven by an active combination of three Q SNARE and one R SNARE molecule.
 We have relaxed the pairing matrix constraint to comply with this fact.

### 2018-05-10 vts-synth/src/load-vts.cpp
updated

@@ -203,8 +203,8 @@ void load_vts::load() {
       case 'e': get_edge(); break;
       case 'f': get_node_function(); break;
       case 'g': get_edge_function(); break;
-      case 'p': get_pairing(); break;
-     // case 'p': qr_get_pairing(); break;
+   //   case 'p': get_pairing(); break;
+      case 'p': qr_get_pairing(); break;
       default:
         load_error( "expecting a command at line", line_num );
       }

### 2018-05-10 vts-synth/src/main.cpp

@@ -216,7 +216,9 @@ int main(int ac, char* av[])
            } else {
               v->dump_dot("/tmp/vts.dot", m);
            }
-           auto retVal = system("xdot /tmp/vts.dot");
+           auto retVal = system("dot -Tpng /tmp/vts.dot -o vts.png; open vts.png");
+
+           //auto retVal = system("xdot /tmp/vts.dot");
            if(retVal == -1) 
                std::cout << "SYTEM ERROR !!!\n";
         }
@@ -261,7 +263,7 @@ int main(int ac, char* av[])
     //bool timedout = false;
     std::future<int> future = std::async(std::launch::async, [](){ 
         // if ( flagA == false ) {
-        auto retVal  = system ("cd ./build/depqbf/examples;timeout 600s ../depqbf --qdo --no-dynamic-nenofex  /tmp/myfile.qdimacs > /tmp/out.txt");
+        auto retVal  = system ("cd ./build/depqbf/examples;gtimeout 6000s ../depqbf --qdo --no-dynamic-nenofex  /tmp/myfile.qdimacs > /tmp/out.txt");
         // std::cout << retVal << "\n";
         //  } else {
         // auto retVal = system("cd ./build/depqbf/examples; gcc -o depqbf-file depqbf-file.c -L.. -lqdpll; ./depqbf-file" );
@@ -273,7 +275,7 @@ int main(int ac, char* av[])
     //std::cout << "Running depqbf ... " << "\n";
     std::future_status status;
 
-    status = future.wait_for( std::chrono::seconds(600) );
+    status = future.wait_for( std::chrono::seconds(6000) );
 
     if ( status == std::future_status::timeout ) { 
       std::cout << "TimeOut! \n";
@@ -291,7 +293,8 @@ int main(int ac, char* av[])
 
     v->print_graph( c, "/tmp/dep_vts.dot", qs, printModel, displayGraph, synthVar ); 
     if ( displayGraph == true ) { 
-      auto retVal = system("xdot /tmp/dep_vts.dot");
+      auto retVal = system("dot -Tpng /tmp/vts.dot -o vts.png; open vts.png");
+     // auto retVal = system("xdot /tmp/dep_vts.dot");
       if(retVal == -1) 
         std::cout << "SYTEM ERROR !!!\n"; 
     }

### 2018-05-10 vts-synth/src/vts-synthesis.cpp

@@ -266,13 +266,13 @@ void xor_bits ( z3::context& c,
 
 z3::expr vts::vts_synthesis ( unsigned variation ) {
   /** Basic Constraints **/
-  z3::expr vtsCons = create_vts_constraint();  
-  //z3::expr vtsCons = create_qr_vts_constraint();  
+  //z3::expr vtsCons = create_vts_constraint();  
+  z3::expr vtsCons = create_qr_vts_constraint();  
   //z3::expr nodeActive = always_active_on_node();
  // z3::expr vtsActivity = vts_activity_constraint(); 
 
   /** Connectedness Constraints */
-  z3::expr kConnCons = k_connected_graph_constraint( 4, false ); 
+  z3::expr kConnCons = k_connected_graph_constraint( 3, false ); 
  // z3::expr V5 = no_self_edges();
   
   //z3::expr inputCons = ctx.bool_val(true);
@@ -302,9 +302,9 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   z3::expr_vector listE = edge_list(); 
   z3::expr_vector listPresenceE = presence_edge_list();
   z3::expr_vector listActiveE = active_edge_list(); 
-  z3::expr_vector listPairingM = pairing_m_list(); 
+  //z3::expr_vector listPairingM = pairing_m_list(); 
   z3::expr_vector listReach = reach_list();
-//  z3::expr_vector listPairing4M  = pairing_m_4d_list();
+  z3::expr_vector listPairing4M  = pairing_m_4d_list();
   
   z3::expr knownVarConstraint( ctx );
 
@@ -341,8 +341,8 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     unassigned_bits ( listE, knownEdges, unknownE ); 
     unassigned_bits ( listPresenceE, knownPresenceEdges, unknownPresenceE ); 
     unassigned_bits ( listActiveE, knownActiveEdges, unknownActiveE ); 
-    unassigned_bits ( listPairingM, knownPairingMatrix, unknownPairingM ); 
-  //  unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
+   // unassigned_bits ( listPairingM, knownPairingMatrix, unknownPairingM ); 
+     unassigned_bits ( listPairing4M, knownPairingMatrix, unknownPairingM ); 
   
     z3::expr_vector list_expr (ctx);
 
[…]

### 2018-05-10 vts-synth/src/vts.cpp

@@ -1098,8 +1098,9 @@ z3::expr vts::vts_fusion_constraint () {
 z3::expr vts::vts_qr_fusion_constraint () {
   std::cout << "Making qr fusion constraints!\n";
   z3::expr v7 = qr_4d_edge_must_fuse_with_target();       //V7
-  z3::expr v8 = qr_4d_edge_fuse_only_with_target();        //V8
+   z3::expr v8 = qr_4d_edge_fuse_only_with_target();        //V8
   auto cons = v7 && v8;
+  //auto cons = v7;
   std::cout << "Finished qr fusion constraints!\n";
   // auto cons = ctx.bool_val(true);
   return cons;

### 2018-06-07 papers/synth/experiments.tex
initial version
journal repo

@@
     plos2-dia[4C] & 0.266 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
-    small-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline
+    sub-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline
     node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE.\\\hline
-    yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
+ %   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
+    yeast-graph[3C]   & 95.016    & 1 E  &   timeout  & N/A   & 1393.84  & 1 E  & 468.161   & 1 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
+
+mammal-graph[3C]  &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A    &  timeout     & N/A\\\hline
    %    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
@@
     plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
-    small-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
+    sub-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
     node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-    yeast-graph & 40.872  & 1 E  &   timeout  & N/A   & 131.91  & 1 E  & 97.619   & 1 E & 70.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-   % mammal-graph   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+    yeast-graph & 40.225  & 1 E  &   timeout  & N/A   & 1393.84  & 1 E  & 468.161   & 1 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
+    mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
   \end{tabular}
   \caption{Run-times for synthesis queries. \#C  stands for minimum changes. Time is reported
-    in seconds. (a) solver used~\depqbf (b) solver used~\zthree. The small-mammal is a subgraph of the complete mammalian graph. In the Add/Delete parts column, `+'n sign is used to show
+    in seconds. (a) solver used~\depqbf (b) solver used~\zthree. The sub-mammal is a subgraph of the complete mammalian graph. In the Add/Delete parts column, `+'n sign is used to show
     addition of n number of the molecules, similarly `-'n is used to show the removal of n number of molecules. 
@@
 The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
-CPU @ 1.90GHz processor and 4GB RAM with 900s timeout.
+CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
 %The experiments were conducted with 900s timeout.
@@
 The first four VTSs are synthetic, but inspire from literature for
-typical motifs in VTSs. 
+typical motifs in VTSs. The third VTS is a subgraph of~\ref{fig:mukund-vts}.
 %

### 2018-06-13 papers/synth/intro.tex
asd
fixed typos

@@
 In this paper, we are looking at the computational questions 
-arise from the VTSs.
+arising from the VTSs.
 
@@
 Please look at appendix~\ref{sec:model}
-for the detailed discussion on pros and cons of the model.
+for a detailed discussion on pros and cons of the model.
 % Describe VTS in detail
@@
 %
-Not all sets molecule can participate in the fusion, the
+Not all molecule sets can participate in the fusion, the
 potential fusion pairs are usually determined by biological experiments.
@@
 We also consider variation on the properties against which we do
-synthesis, namely stability, and $k$-connectedness that states that
-VTS remains connected after removing any $k-1$ edges.
+synthesis, namely stability, and $k$-connectedness that states that the VTS remains connected after removing any $k-1$ edges.
 %
 In order to synthesize the parts of a VTS such that it satisfies the
-constraints, we encode the synthesis problem into a satisfiability of
+constraints, we encode the synthesis problem into one of satisfiability of
 quantified Boolean formulas(QBFs). 
@@
 We have implemented the encoding in a flexible tool,
-which can handle a wide range of synthesis query.
+which can handle a wide range of synthesis queries.
 %
@@
 %
-
 % \input{fig-mukund-vts}

### 2018-06-13 papers/synth/prelim.tex
add
fixed typos

@@
 %
-The model captures the study state of a VTS.
+The model captures the steady state of a VTS.
 %
@@
 
-The following constraints encode the basic consistency of VTSs.
+The following constraints encode the basic consistancy of VTSs.
 \begin{align*}
@@
 %
-Here we will discussed two such properties proposed in earlier
+Here we will discuss two such properties proposed in earlier
 works~\cite{smtVTS}, namely stability and $k$-connectedness.

### 2018-06-13 vts/bio.py

@@ -12,7 +12,7 @@ set_option(max_args=10000000, max_lines=1000000, max_depth=10000000, max_visited
 # input parsing
 # input number of nodes and molecules
 parser = argparse.ArgumentParser(description='Auto testing for TARA')
-parser.add_argument("-M","--mols", type=int, default=4, help = "number of molecules")
+parser.add_argument("-i","--file", type=file, default=examples/qbflib.qdimacs, help = "number of molecules")
 parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes")
 parser.add_argument("-Q","--pedges", type=int, default=2, help = "max no.of parallel edges btw two nodes")
 parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")

### 2018-06-13 papers/synth/encoding.tex
asd
fixed typos
fixed Killos of typos

@@
 In this section, we will present a list of synthesis problems that may
-arise from the partial available information about a VTS and our synthesis method
+arise from the partially available information about a VTS and our synthesis method
 for the problems.
@@
   \texttt{PresentN} &= \land \{n_{i,m}| m \in \nlabel(i) \land i \in \nodes \}\\
-  \texttt{PresentP} &= \land \{p_{i,j}| (i,j) \in \pairs \} \\
+  \texttt{PresentP} &= \land \{p_{\{m_1,m_2,m_3,m_4\}}| \{m_1,m_2,m_3,m_4\} \in \pairs \} \\
   \texttt{KnownActiveN} &= \land \{ a_{i,m} = \texttt{NodeFun}_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is defined.} \} \\
@@
   \texttt{AbsentNLabel} &= \{n_{i,m}| m \not\in \nlabel(i) \land i \in \nodes \}\\
-  \texttt{AbsentP} &= \{p_{i,j}| (i,j) \not\in \pairs \} \\
-  \texttt{UnnownActive} &=  \Land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is undefined.} \} \union \\
+  \texttt{AbsentP} &= \{p_{\{m_1,m_2,m_3,m_4\}}| {\{m_1,m_2,m_3,m_4\}} \not\in \pairs \} \\
+  \texttt{UnknownActive} &=  \Land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is undefined.} \} \union \\
    &\quad\quad\quad  \{ b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
@@
 %
-However, we support other classes of formulas for example $k$-CNF.
+However, we support other classes of formulas, for example, $k$-CNF.
 
@@
 %
-We fix the all other aspect of the VTS to be fixed via constraints
+We fix the all other aspects of the VTS to be fixed via constraints
 $\texttt{FixedForFunctions}$.
@@
 %
-We also limit how many times the $flip_{i,m}$ can be true, therefore
+We also limit the number of $flip_{i,m}$ that can be true, therefore
 limiting the number of flips.

### 2018-06-13 papers/synth/ex-vts.tex
fixed Killos of typos

@@
 
-In this figure the rectangles represent compartments, the identities
-of compartments are written within: ER=endoplasmic reticulum,
+In this figure, the rectangles represent compartments, the identities
+of compartments are written within ER=endoplasmic reticulum,
 ERGIC=ER-Golgi intermediate compartment, RE=recycling endosome,
@@
 % Here the cycle for
-% VAMP2 is complete.The blue labels represent the paths taken by SNARES
+% VAMP2 is complete. The blue labels represent the paths taken by SNARES
 % of the complex Stx5-Gs28-Bet1/GS15-Ykt6.

### 2018-06-13 papers/synth/experiments.tex
fixed Killos of typos

@@
   \caption{Run-times for synthesis queries. \#C  stands for minimum changes. Time is reported
-    in seconds. (a) solver used~\depqbf (b) solver used~\zthree. The sub-mammal is a subgraph of the complete mammalian graph. In the Add/Delete parts column, `+'n sign is used to show
-    addition of n number of the molecules, similarly `-'n is used to show the removal of n number of molecules. 
+    in seconds.
+(a) solver used~\depqbf (b) solver used~\zthree.
+The sub-mammal is a subgraph of the complete mammalian graph.
+In the Add/Delete parts column, `+'n sign is used to show the addition of n number of the molecules, similarly `-'n is used to show the removal of n number of molecules.
   In the table N represents node labels, AN represents active node molecules, E represents edges, PE represents the presence of molecules on the edge and AE represents active molecules on the edge. 
@@
 %
-The tool can not only synthesize the above discussed queries, but also their
+The tool can not only synthesize the above-discussed queries, but also their
 combinations.
@@
 %
-Since, some of the formulas involve alternation of quantifiers over
+Since some of the formulas involve alternation of quantifiers over
 Boolean variables Z3 is not a suitable choice for those examples.
 %
-We translate the formulas created by Z3 tool into standard
+We translate the formulas created by Z3 tool into a standard
 QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
@@
 To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
-quantifier free.
+quantifier-free.
 %
@@
 CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
-%The experiments were conducted with 900s timeout.
+%The experiments were conducted with a 900s timeout.
 %
-The first four VTSs are synthetic, but inspire from literature for
+The first four VTSs are synthetic but inspire from literature for
 typical motifs in VTSs. The third VTS is a subgraph of~\ref{fig:mukund-vts}.
@@
 %
-To illustrated the versatility of our tool, the the fourth query
+To illustrate the versatility of our tool, the fourth query
 synthesizes $3$-CNF functions (encoding not presented).

### 2018-06-13 papers/synth/intro.tex
fixed Killos of typos

@@
 %Motivate VTS
-Eukaryotic cells, including human cells, consist of multiple membrane
-bound compartments.
+Eukaryotic cells, including human cells, consist of multiple membrane-bound compartments.
 %
@@
 %
-Briefly, the source compartment produces a membrane bound packet of
+Briefly, the source compartment produces a membrane-bound packet of
 molecules called a vesicle.
@@
 %
-The current knowledge of the network is put together from a patch work
+The current knowledge of the network is put together from a patchwork
 of biological experiments and is scattered across several publications.
@@
 %VTS graph and details about interactions amongst its molecules, what the complete graph of the
-%VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
+%VTS could look like. (Please look at Appendix A for the detailed discussion on pros and cons of the
 %model.
@@
 %
-Please look at appendix~\ref{sec:model}
+Please look at appendix~\ref{sec: model}
 for a detailed discussion on pros and cons of the model.
@@
 % (The molecules are transported to the other compartments via
-%unidirectional channels.) cannot comment on unidirectionality of vesicles. they may be undergoingmultiple cycles of back-fusion for all we %know..  
+%unidirectional channels.) cannot comment on unidirectionality of vesicles. they may be undergoing multiple cycles of back-fusion for all we %know.  
 %
@@
 occurs in the target compartment.
-% use either target or destination consistantly throughout..i prefer target because that's what the t in t-SNARE stands for.
+% use either target or destination consistently throughout..i prefer target because that's what the t in t-SNARE stands for.
 %
@@
 %
-% It largely means that the current knowledge is due to the patch work
+% It largely means that the current knowledge is due to the patchwork
 % of biological experiments~\cite{model} for identifying the compartments,
@@
 % We have also applied our tool on various synthetic examples to
-% demonstrate that our tool scale upto the graph size size nodes, which
+% demonstrate that our tool scale up to the graph size nodes, which
 % is the size of typical VTSs in a eukaryotic cell.
@@
 \item We have developed encoding of the synthesis problem in QBF.
-\item A user friendly and scalable tool based on QBF solvers
+\item A user-friendly and scalable tool based on QBF solvers
 \end{itemize}

### 2018-06-13 papers/synth/prelim.tex
fixed Killos of typos

@@
 %
-We will also present the constrains and properties on the VTSs, and their
+We will also present the constraints and properties on the VTSs, and their
 encoding as a QBF formula.   
 %
-We model a VTS as labelled graph along with assisting pairing matrices and
+We model a VTS as a labelled graph along with assisting pairing matrices and
 activating functions.
@@
 % %
-% For example, unique edge between two nodes, activity of molecules is
+% For example, the unique edge between two nodes, the activity of molecules is
 % not constrained by $\nodef$ and $\edgef$, etc.
@@
 %
-Let us suppose that the size of the graph is $\nu$ and number of
-molecules is $\mu$.
+Let us suppose that the size of the graph is $\nu$ and a number of
+molecules are $\mu$.
 %
@@
 
-For synthesis of incomplete systems,
+For the synthesis of incomplete systems,
 we need properties against which we synthesize the missing parts.
@@
 % \subsection{Solvers}
-% Due the combinatorial nature of the graphs, the search space is huge
+% Due to the combinatorial nature of the graphs, the search space is huge
 % and often hard to enumerate naively.

### 2018-06-14 papers/synth/prelim.tex
minor issues fixed

@@
   \begin{itemize}
-  \item $\nodes$ is a set of nodes representing compartments in the VTS,
-  \item $\mols$ is the set of molecules flowing in the system, 
+  \item $\nodes$ is a finite set of nodes representing compartments in the VTS,
+  \item $\mols$ is the finite set of molecules flowing in the system, 
   \item $\edges \subseteq \nodes \times (\powerset{\mols}-\emptyset) \times \nodes$ is the
@@
 compartments,
+%
+pairing relations have sets of four molecules such that three
+are of one type and one is of another type
+(motivated by the biochemistry of the fusion),
 %
@@
 \texttt{ActivityC} states that active molecule are present.
-\texttt{PairingC} states that all molecules are divided into
-two types and any fusing set of molecules
-must have three molecules involved from one type and one molecule from the other.
+\texttt{PairingC} states that all molecules are divided into two types
+using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
+and any fusing set of molecules must have three molecules involved
+from one type and one molecule from the other.
 \texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
@@
 \paragraph{Activity functions}
-We also need to encode that
-the activity of the molecules are controlled by activity functions.
 %
-However, the encoding functions can be given to us many different ways,
+We also need to encode that the activity of the molecules are
+controlled by activity functions.
+%
+The input VTS may include concrete activity functions for some molecules,
+and for the others the functions may be unknown and to be synthesized. 
+%
+The concrete functions can be given to us in many different ways,
 for example as a lookup table, or a concise Boolean formula.
@@
 In the following section, we will assume the appropriate encoding is
-used for the functions and represent them by \texttt{NodeFun}$_m$
+used for the concrete functions and represent them by \texttt{NodeFun}$_m$
 and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
@@
 We will use $\nodef_m$ and $\edgef_m$ to represent functions that
-are not defined in a VTS.
+are unknown in a VTS.
 %
@@
 %
-Later we will be synthesizing missing activity functions and 
+Later we will be synthesizing the unknown activity functions and 
 replace $\nodef_m$ and $\edgef_m$ with parameterized constraints that
@@
 %
+Therefore, synthesis against this property will require QBF reasoning.
+%
+We may make the formula quantifier free  by considering all possible failures
+separately and introducing a vector of reachability variables for each
+failure.
+%
+However, this will blow up the size of the formula and may not be
+solvable by a SAT solver.
+%
 

### 2018-06-14 papers/journal/abstract.tex

--- 2018-04-19 papers/synth/abstract.tex
@@
-Vesicle Traffic Systems(VTSs) are the material transport mechanisms
-among the compartments inside the biological cells.
-%
-The compartments are viewed as nodes that are labeled with the
-containing chemicals and the transport channels are similarly labeled
-edges between the nodes.
-%
-Understanding VTSs is an ongoing area of research and for many cells
-they are partially known.
-%
-For example, there may be undiscovered edges, nodes, or their labels
-in a VTS of a cell.
-%
-It has been speculated that there are properties that the VTSs must
-satisfy.
-%
-For example, stability, i.e., every chemical that is leaving a
-compartment comes back.
-%
-Many synthesis questions may arise in this scenario, where we want
-to complete a partially known VTS under a given property.
-%
-In the paper, we present novel encodings of the above questions
-into the QBF(quantified Boolean formula) satisfiability problems.
-%
-We have implemented the encodings in a highly configurable tool
-and  apply to a couple of found-in-nature VTSs and 
-several synthetic graphs.
-%
-Our results demonstrates that our method can scale upto the
-graphs of interest.
-%
+Vesicle Traffic Systems(VTSs) are the material transport 
+mechanisms among the compartments inside the biological cells.
 

### 2018-06-14 papers/synth/abstract.tex
appendix fix

@@
-Vesicle Traffic Systems(VTSs) are the material transport mechanisms
-among the compartments inside the biological cells.
+Vesicle Traffic Systems (VTSs) are the material transport 
+mechanisms among the compartments inside the biological cells.
 %
@@
 In the paper, we present novel encodings of the above questions
-into the QBF(quantified Boolean formula) satisfiability problems.
+into the QBF (quantified Boolean formula) satisfiability problems.
 %
 We have implemented the encodings in a highly configurable tool
-and apply to a couple of found-in-nature VTSs and 
+and applied to a couple of found-in-nature VTSs and 
 several synthetic graphs.
 %
-Our results demonstrates that our method can scale upto the
-graphs of interest.
+Our results demonstrate that our method can scale up to the graphs of interest.
+%
+%Our results demonstrates that our method can scale upto the graphs of interest.
 %

### 2018-06-14 papers/synth/experiments.tex

@@
   \end{tabular}
-  \caption{Run-times for synthesis queries. \#C  stands for minimum changes. Time is reported
+  \caption{Run-times for synthesis queries. \#C  stands for minimum changes in the synthesised VTS in comparision to the given VTS. Time is reported
     in seconds.
@@
 In the Add/Delete parts column, `+'n sign is used to show the addition of n number of the molecules, similarly `-'n is used to show the removal of n number of molecules.
-  In the table N represents node labels, AN represents active node molecules, E represents edges, PE represents the presence of molecules on the edge and AE represents active molecules on the edge. 
-    The C stands for graph connectedness which is part of only DepQBF experiments.
+In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge. 
+    The [kC] stands for k graph connectedness which is part of only DepQBF experiments.
       }

### 2018-06-14 papers/synth/related.tex

@@
 %
-They range from filling gaps an implementation of C programs from the
-pool of template predicates to learn learn an a program from example
+They range from filling gaps an implementation of C programs from the pool of template predicates to learn a program from example
 runs of the program.
@@
 The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis.
-The paper~\cite{cardelli2017syntax} in addition of using SMT over ODE, uses a template-guided approach.
+The paper~\cite{cardelli2017syntax} in addition to using SMT over ODE, uses a template-guided approach.
 In our case queries contain quantifiers so we have employed QBF solving with Z3 for the solving the synthesis problem.
-To our best knowledge this is the first application of synthesis in VTS.
+To our best knowledge, this is the first application of synthesis in VTS.
 %%% Local Variables:

### 2018-06-14 papers/synth/intro.tex
reference fix
intro fixed

@@
 After release, this vesicle specifically recognizes the correct target
-compartment within the cell, and fuses with it.
+compartment within the cell, and fuses with it~\cite{alberts2013essential}.
 %
@@
 the VTS has been discovered, including their regulatory interaction
-with each other. 
+with each other~\cite{bonifacino2004mechanisms}. 
 % %
@@
 %
+For example, although thee localization of various SNAREs in the cell is known, and also their site of action~\cite{hong2014tethering}, for most SNAREs, how they first reached the compartments they reside in is not known.
+%
 The current knowledge of the network is put together from a patchwork
@@
 that the network obtained is still not complete; new vesicles and new
-contents in previously known vesicles are constantly being discovered.
+contents in previously known vesicles are constantly being discovered(some new discoveries include~\cite{chanaday2017you, d2017tethering, rodepeter2017indication, zhao2017conserved}).
 %
@@
 
+%
+In particular, the VTS molecules to keep in mind for the purpose of this paper are SNARE proteins.
+SNAREs drive the recognition of the target compartment by vesicles and their subsequent fusion.
+Functionally, SNAREs can be divided into v-SNAREs (which are present on vesicles) and t-SNAREs (which are present on compartments).
+A vesicle fuses with a compartment if its v-SNARE can form a complex with the t-SNARE present on that compartment.
+Not all v- and t- SNARE combinations can form complexes; this constraint forms part of the basis for the specificity of vesicle traffic~\cite{jahn2006snares}.
+The activity of SNARE proteins is further regulated by their interaction with other traffic molecules, such as SM proteins~\cite{sudhof2009membrane} and proteins of tethering complexes~\cite{hong2014tethering}.
+%
 We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
 %
-Please look at appendix~\ref{sec: model}
+Please look at appendix~\ref{sec:model}
 for a detailed discussion on pros and cons of the model.
@@
 %
+We have assumed that the given partial VTS is always well-fused whereas properties like stability and k-connectedness may not hold in the partial VTS.
+%
 In order to synthesize the parts of a VTS such that it satisfies the

### 2018-06-14 papers/synth/experiments.tex
fixed table

@@
  %   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-    yeast-graph[3C]   & 95.016    & 1 E  &   timeout  & N/A   & 1393.84  & 1 E  & 468.161   & 1 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
+    yeast-graph[3C]   & 95.016    & 1 E  &   timeout  & N/A   & 1571.42  & 1 E  & 530.211   & 1 E & 110.206  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
 
@@
   \end{tabular}
-  \caption{Run-times for synthesis queries. \#C  stands for minimum changes in the synthesised VTS in comparision to the given VTS. Time is reported
-    in seconds.
-(a) solver used~\depqbf (b) solver used~\zthree.
-The sub-mammal is a subgraph of the complete mammalian graph.
-In the Add/Delete parts column, `+'n sign is used to show the addition of n number of the molecules, similarly `-'n is used to show the removal of n number of molecules.
+    \caption{Run-times for synthesis queries.
+\#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS.
+Time is reported in seconds.
+(a) The solver used is DepQBF (b) The solver used is Z3.
+The sub-mammal is a subgraph of the complete mammal-graph.
+In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules.
 In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge.
-    The [kC] stands for k graph connectedness which is part of only DepQBF experiments.
-      }
+The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}
+
   % \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
@@
 
-We implemented the encodings in a tool
+We have implemented the encodings in a tool
 called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
@@
 The first four VTSs are synthetic but inspire from literature for
-typical motifs in VTSs. The third VTS is a subgraph of~\ref{fig:mukund-vts}.
+typical motifs in VTSs. 
+The third VTS is a subgraph of the last VTS.
 %

### 2018-06-15 papers/synth/intro.tex
intro done

@@
 that the network obtained is still not complete; new vesicles and new
-contents in previously known vesicles are constantly being discovered(some new discoveries include~\cite{chanaday2017you, d2017tethering, rodepeter2017indication, zhao2017conserved}).
+contents in previously known vesicles are constantly being discovered (some new discoveries include~\cite{chanaday2017you, d2017tethering, rodepeter2017indication, zhao2017conserved}).
 %
@@
 %
-In particular, the VTS molecules to keep in mind for the purpose of this paper are SNARE proteins.
+VTSs are regulated by the same molecules that they transport. 
+For the purpose of this paper, the VTS molecules we focus on are the transmembrane SNARE proteins.
+%which form an essential part of the cellular addressing system.
+%
+%In particular, the VTS molecules to keep in mind for the purpose of this paper are SNARE proteins. 
+%
 SNAREs drive the recognition of the target compartment by vesicles and their subsequent fusion.
@@
 %
+
 We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
 %
-Please look at appendix~\ref{sec:model}
+Please look at Appendix~\ref{sec:model}
 for a detailed discussion on pros and cons of the model.
+%
+We model the system as a labeled graph, where compartments are nodes and transport vesicles are edges.
+Molecular compositions of the compartments and vesicles are given by node and edge labels respectively.
+These molecules can be active or inactive on any given compartment or vesicle.
+The activity state of molecules is also included in the node and edge labels.
+Consistently with the SNARE picture, a vesicle is enabled by a set of molecules such that one part of the set occurs in the vesicle and the other part occurs in the target compartment.
 % Describe VTS in detail
-
-VTSs are regulated by the same molecules that they transport. Molecules on compartments and on vesicles can be in either an active or an inactive state.
+%Molecules on compartments and on vesicles can be in either an active or an inactive state.
 % the term vesicle has already been introduced.. using two terms for the same object seems confusing. 
@@
 %
-The active molecules regulate the vesicle they occur on.
+%The active molecules regulate the vesicle they occur on.
 %
-A vesicle is enabled by a set of molecules
-such that one part of the set occurs in the vesicle and the other part
-occurs in the target compartment.
+%A vesicle is enabled by a set of molecules such that one part of the set occurs in the vesicle and the other part occurs in the target compartment.
 % use either target or destination consistently throughout..i prefer target because that's what the t in t-SNARE stands for.
@@
 %
-Not all molecule sets can participate in the fusion, the
-potential fusion pairs are usually determined by biological experiments.
+Not all sets of molecules can participate in the fusion; in real biological cells, fusogenic SNARE complexes are discovered through experiments. 
+%Not all molecule sets can participate in the fusion, the
+%potential fusion pairs are usually determined by biological experiments.
 %
@@
 We call this regulation as {\em activity functions}.
-
 % Defending our model
 %
-In this VTS model, we assume that the system is in steady state and the
-concentrations of the molecules in the compartments do not change over
-time.
+%In this VTS model, we assume that the system is in steady state and the
+%concentrations of the molecules in the compartments do not change over
+%time.
 %
-We model the system as a labelled graph, where compartments are nodes and
-transport vesicles are edges.
+%We model the system as a labelled graph, where compartments are nodes and
+%transport vesicles are edges.
 %
-The set of molecules present and their activity in a compartment or
-a vesicle is the label of the respective node or edge.
+%The set of molecules present and their activity in a compartment or
+%a vesicle is the label of the respective node or edge.
 %
@@
 Boolean functions.
+
+%
+In the model, we assume that the system is in steady state and the concentrations of the molecules in compartments do not change over time.
 %

### 2018-06-15 papers/synth/intro.tex
intro pass

@@
 %
-For example, although thee localization of various SNAREs in the cell is known, and also their site of action~\cite{hong2014tethering}, for most SNAREs, how they first reached the compartments they reside in is not known.
+For example, although the localization of various SNAREs --a class of
+molecules that participate in the control of VTS-- in the cell is
+known, and also their site of action~\cite{hong2014tethering}, for
+most SNAREs, how they first reached the compartments they reside in is
+not known.
 %
@@
 that the network obtained is still not complete; new vesicles and new
-contents in previously known vesicles are constantly being discovered (some new discoveries include~\cite{chanaday2017you, d2017tethering, rodepeter2017indication, zhao2017conserved}).
+contents in previously known vesicles are constantly being discovered
+(some new discoveries include~\cite{chanaday2017you, d2017tethering,
+rodepeter2017indication, zhao2017conserved}).
 %
@@
 VTSs are regulated by the same molecules that they transport.
+%
 For the purpose of this paper, the VTS molecules we focus on are the transmembrane SNARE proteins.
-%which form an essential part of the cellular addressing system.
 %
-%In particular, the VTS molecules to keep in mind for the purpose of this paper are SNARE proteins. 
+SNAREs drive the recognition of the target compartment by vesicles and
+their subsequent fusion.
 %
-SNAREs drive the recognition of the target compartment by vesicles and their subsequent fusion.
-Functionally, SNAREs can be divided into v-SNAREs (which are present on vesicles) and t-SNAREs (which are present on compartments).
-A vesicle fuses with a compartment if its v-SNARE can form a complex with the t-SNARE present on that compartment.
-Not all v- and t- SNARE combinations can form complexes; this constraint forms part of the basis for the specificity of vesicle traffic~\cite{jahn2006snares}.
-The activity of SNARE proteins is further regulated by their interaction with other traffic molecules, such as SM proteins~\cite{sudhof2009membrane} and proteins of tethering complexes~\cite{hong2014tethering}.
+The SNAREs can be divided into v-SNAREs (which are present
+on vesicles) and t-SNAREs (which are present on compartments). A
+vesicle fuses with a compartment if its v-SNARE can form a complex
+with the t-SNARE present on that compartment.
+%
+Not all v- and t- SNARE combinations can form complexes; this
+constraint forms part of the basis for the specificity of vesicle
+traffic~\cite{jahn2006snares}.
+%
+The activity of SNARE proteins is further regulated by their
+interaction with other traffic molecules \ashu{ [do we need the following], such as SM
+proteins~\cite{sudhof2009membrane} and proteins of tethering
+complexes~\cite{hong2014tethering}.}
 %
 
-We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
+We use the model of VTSs that has been presented
+in~\cite{shukla2017discovering}.
 %
-Please look at Appendix~\ref{sec:model}
-for a detailed discussion on pros and cons of the model.
+Please look at Appendix~\ref{sec:model} for a detailed discussion on
+pros and cons of the model.
 %
-We model the system as a labeled graph, where compartments are nodes and transport vesicles are edges.
-Molecular compositions of the compartments and vesicles are given by node and edge labels respectively.
-These molecules can be active or inactive on any given compartment or vesicle.
-The activity state of molecules is also included in the node and edge labels.
-Consistently with the SNARE picture, a vesicle is enabled by a set of molecules such that one part of the set occurs in the vesicle and the other part occurs in the target compartment.
+We model the system as a labeled graph, where compartments are nodes
+and transport vesicles are edges.
+%
+The molecular compositions of the compartments and vesicles are the
+node and edge labels respectively.
+%
+The molecules can be active or inactive on any a compartment or
+vesicle.
+%
+The activity states of molecules are also included in the labels.
+%
+Due to the biology of SNAREs of the VTSs our interest, a vesicle is enabled
+by a set of {\em four} molecules such that one part of the set occurs in the
+vesicle and the other part occurs in the target of the vesicle compartment.
+%
+The partition is always three and one molecules.
+%
 % Describe VTS in detail
@@
 %
-These molecules must be active in the vesicle
+The enabling molecules must be active in the vesicle
 and target compartment respectively.
@@
 %
-Not all sets of molecules can participate in the fusion; in real biological cells, fusogenic SNARE complexes are discovered through experiments. 
+Not all sets of molecules can participate in the fusion; in the
+biological cells, fusogenic SNARE complexes are discovered through
+experiments.
+%
 %Not all molecule sets can participate in the fusion, the
@@
 %
-Generally, in cells, the fusing pairs are found to be distinct for distinct vesicle-compartment fusions.
+Generally, the fusing pairs are found to be distinct for distinct vesicle-compartment fusions.
 %
-In order that a molecule that has participated in a fusion does not interfere
-with fusion at compartments and vesicles, in the model, we require that the molecule is inactive on appropriate compartments.
-%
+To ensure that a molecule that has participated in a fusion does not
+interfere with fusion at compartments and vesicles, in the model, we
+require that the molecule is inactive on appropriate compartments.
 %
@@
 %
-In the model, we assume that the system is in steady state and the concentrations of the molecules in compartments do not change over time.
+In the model, we assume that the system is in steady state and the
+concentrations of the molecules in compartments do not change over
+time.
 %
@@
 
-The following are the contributions of this work:
-\begin{itemize}
-\item We have identified an interesting application of
-  the synthesis technology.
-\item We have developed encoding of the synthesis problem in QBF.
-\item A user-friendly and scalable tool based on QBF solvers
-\end{itemize}
+% The following are the contributions of this work:
+% \begin{itemize}
+% \item We have identified an interesting application of
+%   the synthesis technology.
+% \item We have developed encoding of the synthesis problem in QBF.
+% \item A user-friendly and scalable tool based on QBF solvers
+% \end{itemize}
 

### 2018-06-15 papers/synth/intro.tex
qwe
reply

@@
 proteins~\cite{sudhof2009membrane} and proteins of tethering
-complexes~\cite{hong2014tethering}.}
+complexes~\cite{hong2014tethering}. }
+\ankit{From our papers prospective NO.
+But Biologically Yes.
+Mukund have written this earlier then stated that "In this paper we focus only on SNARE's ...
+But somya has did this in reverse.
+Similar was the case many places, a few of which I fixed.
+I can give one more try."}
 %

### 2018-06-15 papers/synth/intro.tex
intro line delete

--- 2018-06-15 papers/synth/intro.tex
@@
 %
-The activity of SNARE proteins is further regulated by their
-interaction with other traffic molecules \ashu{ [do we need the following], such as SM
-proteins~\cite{sudhof2009membrane} and proteins of tethering
-complexes~\cite{hong2014tethering}.}
+%The activity of SNARE proteins is further regulated by their interaction with other traffic molecules.
+
+%\ashu{ [do we need the following], such as SMproteins~\cite{sudhof2009membrane} and proteins of tethering complexes~\cite{hong2014tethering}. }
 %
@@
 %
-The partition is always three and one molecules.
+The partition always divides the set in the set of three and one molecules.
 %

### 2018-06-15 papers/synth/intro.tex
fixed more typos

@@
 
-% Partial info defence
+% Partial info defense
 %
@@
 % %
-% Even after with some effort we may collate all the known information about
+% Even after with some effort, we may collate all the known information about
 % a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
@@
 %
-The synthesis for the unknown pieces may be {\em assisted} by computation on
+The synthesis of the unknown pieces may be {\em assisted} by computation on
 the graph model of VTSs.
@@
 involving different parts of VTSs that can be synthesized, such as
-modifying labels, adding/deleting edges, and learning activity functions.
+modifying labels, adding/deleting edges, and learning activity function.
 %
-We also consider variation on the properties against which we do
+We also consider a variation on the properties against which we do
 synthesis, namely stability, and $k$-connectedness that states that the VTS remains connected after removing any $k-1$ edges.

### 2018-06-15 papers/synth/intro.tex
one more

@@
 %
-We also consider a variation on the properties against which we do
+We also consider variations on the properties against which we do
 synthesis, namely stability, and $k$-connectedness that states that the VTS remains connected after removing any $k-1$ edges.

### 2018-10-02 papers/journal/abstract.tex
added prelim and abstract

--- 2018-05-01 papers/synth/abstract.tex
@@
 In the paper, we present novel encodings of the above questions
-into the QBF(quantified Boolean formula) satisfiability problems.
+into the QBF (quantified Boolean formula) satisfiability problems.
 %
 We have implemented the encodings in a highly configurable tool
-and apply to a couple of found-in-nature VTSs and 
+and applied to a couple of found-in-nature VTSs and 
 several synthetic graphs.
 %
-Our results demonstrates that our method can scale upto the
-graphs of interest.
-%
+Our results demonstrate that our method can scale up to the graphs of interest.
+
+% Vesicle Traffic Systems(VTSs) are the material transport 
+% mechanisms among the compartments inside the biological cells.
 

### 2018-10-03 papers/journal/model.tex
prelim and model added

--- 2018-06-13 papers/synth/prelim.tex
@@
-In this section, we will present the model of VTS from~\cite{smtVTS}.
+In this section, we will present our formal model of VTS.
 %
-We will also present the constraints and properties on the VTSs, and their
-encoding as a QBF formula.   
+Our model attempts to capture only the relevant aspects of the
+system to develop understanding the flow structure of VTSs.
 %
-We model a VTS as a labelled graph along with assisting pairing matrices and
-activating functions.
+The model assumes that a cell consists of clearly defined compartments
+that are well stirred within themselves.
+%
+The model assumes that all chemical reactions get sufficient time to complete.
+%
+The model describes stable flow of molecules and does not
+capture the transient nature of VTSs.
+%
+The model also does not capture concentrations of the molecules and
+only captures their presence or absence.
+%
+
+In the model, the compartments are nodes of a graph
+and vesicles are the edges between the nodes.
+%
+There is a set of relevant molecules that participate in
+management of the VTS.
+%
+Both nodes and edges are labelled with subsets of the molecules.
+%
+The molecules are activity and their control is defined using
+activity functions and a pairing matrix.
+%
 
@@
 %
-The model captures the steady state of a VTS.
-%
-The analysis of the model will inform us about the network/graph
-properties of VTSs.
+% The model captures the steady state of a VTS.
+% %
+% The analysis of the model will inform us about the network/graph
+% properties of VTSs.
 
@@
 %
-We call $G$ {\em well-structured} if molecules $M$ is divided into
+We say $G$ is {\em fuse compatible} if molecules $M$ is divided into
 two partitions $Q$ and $R$ such that
-for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $, and
+for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $.
+%
+In other words,
+molecules are of two types $Q$ and $R$,
+%
+pairing relations have sets of four molecules such that three
+are of one type (??) and one is of another type (??).
+%
+% This distinction of molecules is due to section~\ref{mol-types}.
+%
+We call $G$ {\em well-structured} if it is pair compatible, and
 for each $(n,M',n') \in \edges$, $n \neq n'$ and
@@
 %
-In other words,
-no molecule can participate in fusion from both channels and
-compartments,
-%
-there are no self loops, and 
+In addition to fuse compatibility, the well-structured property requires that
+here are no self loops, and 
 each edge carry only those molecules that are present in its source
@@
 and can not fuse with any other node.
+%
+$\pairs$ models biological possible quadruple of molecules that participate in fusion.
+%
+Each edge must be uniquely supported by such a quadruple of molecules.
+%
+We also require three of them to be on the node or edge, and the forth one
+to be on the other side of the fusion.
 
@@
 %
+The definition of stability implies that if a molecule leaves a
+compartment then there must be a path for it to come back.
+%
+It ensures that the flow of molecules does not deplete a
+compartment.
+%
+Such a property is often expected in several physical systems
+such that electromagnetic fields, fluid dynamics, etc.
+
+%
 We call $G$ {\em connected} if for each $n,n' \in \nodes$,
@@
 %
-We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
-VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
+We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and
+$|\edges'| < k$, VTS
+$(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
+%
+We will check if a VTS $G$ is $k$-connected or not.
+%
+The property of $k$-connectedness is a robustness property that one
+expects from a biological systems.
+%
+The property says even after failure of a few edges the system will continue to work.
 
@@
 
-\subsection{Encoding VTS}
-
-The conditions on the VTSs for a given size can be encoded as a QBF formula
-with uninterpreted functions.
+Let us discuss rough sizes of the system and expected behaviors.
 %
-To encode the constraints, we need variables for each aspect of
-VTS.
+A typical VTS may have about 10 compartments.
 %
-Let us suppose that the size of the graph is $\nu$ and a number of
-molecules are $\mu$.
+The VTS may transport a large number of molecules but the molecules that
+are relevant of the control of VTS are about 50~\cite{doWeKnowThis}.
 %
-To fully finitize the problem, we also limit the maximum number $\pi$
-of edges present between two nodes.
+According to the definition the activity of molecules can be controlled by
+the presence of all other molecules.
 %
-Here, we list the Boolean variables and uninterpreted function symbols
-that encode parts of VTSs.
-\begin{enumerate}
-
-\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
-\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
-\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
-\item Boolean variable $p_{\{m_1,m_2,m_3,m_4\}}$ indicates if $\{m_1,m_2,m_3,m_4\} \in \pairs$
-\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
-encoding $\nodef(m)$ map
-\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
-encoding $\edgef(m)$ map
-\end{enumerate}
-We also have auxiliary Boolean variables that will help us encode the well-fused property. 
-\begin{enumerate}
-\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
-  holds
-\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\end{enumerate}
-
-We will describe several constraints that encode VTSs in this section.
-%
-In the next section, we will extend the encoding for the synthesis problem.
-%
-To avoid cumbersome notation, we will not explicitly write the ranges
-of the indexing in the constraints.
-%
-$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
-%
-$m$ will range over molecules, i.e., from $1$ to $\mu$.
-%
-$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
-%
-
-The following constraints encode the basic consistancy of VTSs.
-\begin{align*}
-  \texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
-  \land
-  \bigwedge\limits_{i,q} \neg e_{i,i,q}
-  \land
-  % \tag{\texttt{NodeC}}\label{eq:f0}\\
-  \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
-  \\
-  \texttt{ActivityC} =\;&
-  \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
-  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
-  % \tag{V2}\label{eq:f1}\\
-  \\
-  \texttt{PairingC} =\;&
-  \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
-                         (p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
-% \land\\ 
-%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
-  % \bigwedge\limits_{m} 
-  % (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
-  % (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
-  \\
-  \texttt{Fusion1} =\;&
-  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
-  \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
-                        \Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
-  & \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
-  \\
-  \texttt{Fusion2} =\;&
-\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
-  & \hspace{2cm} \neg 
-  \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
-\land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
-  \\
-  \texttt{Consistancy} =\;& \texttt{EdgeC} \land
-  \texttt{ActivityC} \land \texttt{PairingC} \land
-  \texttt{Fusion1} \land \texttt{Fusion2} 
-\end{align*}
-\texttt{EdgeC} states that each edge has at least one molecule,
-there are no self loops, and edge labels are consistent with node labels.   
-\texttt{ActivityC} states that active molecule are present.
-\texttt{PairingC} states that all molecules are divided into
-two types and any fusing set of molecules
-must have three molecules involved from one type and one molecule from the other.
-\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
-\texttt{Consistancy} is the conjunction of all of the above.
-
-\paragraph{Activity functions}
-We also need to encode that
-the activity of the molecules are controlled by activity functions.
-%
-However, the encoding functions can be given to us many different ways,
-for example as a lookup table, or a concise Boolean formula.
-%
-In the following section, we will assume the appropriate encoding is
-used for the functions and represent them by \texttt{NodeFun}$_m$
-and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
-%
-We will use $\nodef_m$ and $\edgef_m$ to represent functions that
-are not defined in a VTS.
-%
-% \begin{align}
-% \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
-% \tag{\texttt{ActiveN}}\label{eq:anb}\\
-%    \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
-%   \tag{\texttt{ActiveE}}\label{eq:aeb}
-% \end{align}
-%
-Later we will be synthesizing missing activity functions and 
-replace $\nodef_m$ and $\edgef_m$ with parameterized constraints that
-encode a space of candidate functions.
-
-\subsection{VTS properties}
-
-For the synthesis of incomplete systems,
-we need properties against which we synthesize the missing parts.
-%
-Here we will discuss two such properties proposed in earlier
-works~\cite{smtVTS}, namely stability and $k$-connectedness.
-%
-
-\paragraph{Stability property}
-%
-We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
-$m$-path from $i$ to $j$ of length less than or equal to $p$.
-%
-We use $m$-reachability to encode the stability condition in VTSs.
-%
-The following constraint recursively encodes that node $j$ is
-$m$-reachable from node $i$ in less than $p$ steps.
-%
-Subsequently, we encode stability condition using the reachability variables.
-\begin{align*}
-  \texttt{Paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-  \\
-  \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-  \\
-  \texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
-\end{align*}
-
-\paragraph{$k$-connected property}
-%
-$k$-connectedness expresses robustness against failure of few edges.
-%
-Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
-and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
-the modified VTS.
-%
-% To check whether $k$-connected is a
-% necessary condition, we remove (drop) $k-1$ edges from the graph and
-% if it disconnects the graph, and we get an assignment.
-% %
-% We have a graph that is not $k$-connected.
-%
-In the following, $\texttt{Fail}(d,k)$ encodes that only
-existing edges can be failed and exactly $k-1$ edges are failed.
-%
-$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
-%
-We use a new variable $r'_{i,j,p}$ to encode reachability from
-$i$ to $j$ in at most $p$ steps.
-%
-$\texttt{Connected}(r')$ says that all nodes are reachable from any
-other node.
-\begin{align*}
-  \texttt{Fail}(d,k) = & 
-  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
-  \sum_{i,j,q} d_{i,j,q} = k-1\\
-  % \texttt{ReachAbove}(d,r') = &
-  % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
-  \texttt{FReach}(d,r') = &\hspace{-1ex}
-   \bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
-  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
-\end{align*}
-We will be synthesizing $k$-connected graphs.
-%
-We define $\texttt{Connected}(k)$ that says for all possible valid failures
-the graph remains reachable. 
-\begin{align*}
-  \texttt{Connected}(k) = & \forall d.\;
-          (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
-                                \land \texttt{Connected}(r'))
-% \\
-  % \texttt{Disconnected}(k) = & \exists d.\;
-  %         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
-  %                               \land \lnot \texttt{Connected}(r'))
-\end{align*}
-Since $d$ variables in $\texttt{Connected}(k)$ are universally
-quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
-%
-
-% \subsection{Solvers}
-% Due to the combinatorial nature of the graphs, the search space is huge
-% and often hard to enumerate naively.
-% %
-% We need sophisticated solvers
+However, in practice the activity of a molecule is controlled by
+the presence of ~2-3 other molecules.
 

### 2018-10-03 papers/journal/prelim.tex
added prelim and abstract
prelim and model added

--- 2018-06-13 papers/synth/prelim.tex
@@
-In this section, we will present the model of VTS from~\cite{smtVTS}.
+% \subsection{VTS properties}
+
+% For the synthesis of incomplete systems,
+% we need properties against which we synthesize the missing parts.
+% %
+% Here we will discuss two such properties proposed in earlier
+% works~\cite{smtVTS}, namely stability and $k$-connectedness.
+% %
+
+% \paragraph{Stability property}
+% %
+% We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
+% $m$-path from $i$ to $j$ of length less than or equal to $p$.
+% %
+% We use $m$-reachability to encode the stability condition in VTSs.
+% %
+% The following constraint recursively encodes that node $j$ is
+% $m$-reachable from node $i$ in less than $p$ steps.
+% %
+% Subsequently, we encode stability condition using the reachability variables.
+% \begin{align*}
+%   \texttt{Paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+%   \\
+%   \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
+%   \\
+%   \texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
+% \end{align*}
+
+% \paragraph{$k$-connected property}
+% %
+% $k$-connectedness expresses robustness against failure of few edges.
+% %
+% Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
+% and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
+% the modified VTS.
+% %
+% % To check whether $k$-connected is a
+% % necessary condition, we remove (drop) $k-1$ edges from the graph and
+% % if it disconnects the graph, and we get an assignment.
+% % %
+% % We have a graph that is not $k$-connected.
+% %
+% In the following, $\texttt{Fail}(d,k)$ encodes that only
+% existing edges can be failed and exactly $k-1$ edges are failed.
+% %
+% $\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
+% %
+% We use a new variable $r'_{i,j,p}$ to encode reachability from
+% $i$ to $j$ in at most $p$ steps.
+% %
+% $\texttt{Connected}(r')$ says that all nodes are reachable from any
+% other node.
+% \begin{align*}
+%   \texttt{Fail}(d,k) = & 
+%   \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
+%   \sum_{i,j,q} d_{i,j,q} = k-1\\
+%   % \texttt{ReachAbove}(d,r') = &
+%   % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
+%   \texttt{FReach}(d,r') = &\hspace{-1ex}
+%    \bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
+%   \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
+% \end{align*}
+% We will be synthesizing $k$-connected graphs.
+% %
+% We define $\texttt{Connected}(k)$ that says for all possible valid failures
+% the graph remains reachable. 
+% \begin{align*}
+%   \texttt{Connected}(k) = & \forall d.\;
+%           (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
+%                                 \land \texttt{Connected}(r'))
+% % \\
+%   % \texttt{Disconnected}(k) = & \exists d.\;
+%   %         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
+%   %                               \land \lnot \texttt{Connected}(r'))
+% \end{align*}
+% Since $d$ variables in $\texttt{Connected}(k)$ are universally
+% quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
+% %
+% Therefore, synthesis against this property will require QBF reasoning.
+% %
+% We may make the formula quantifier free  by considering all possible failures
+% separately and introducing a vector of reachability variables for each
+% failure.
+% %
+% However, this will blow up the size of the formula and may not be
+% solvable by a SAT solver.
+% %
+
+\subsection{Solvers}
+Due to the combinatorial nature of the graphs, the search space is huge
+and often hard to enumerate naively.
 %
-We will also present the constrains and properties on the VTSs, and their
-encoding as a QBF formula.   
-%
-We model a VTS as labelled graph along with assisting pairing matrices and
-activating functions.
-
-\begin{df}
-  A VTS $G$ is a tuple $(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$, where
-  \begin{itemize}
-  \item $\nodes$ is a set of nodes representing compartments in the VTS,
-  \item $\mols$ is the set of molecules flowing in the system, 
-  \item $\edges \subseteq \nodes \times (\powerset{\mols}-\emptyset) \times \nodes$ is the
-    set of edges with molecule sets as labels,
-  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes,
-  \item $\pairs \subseteq 2^{\mols}$ is pairing relation,
-  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes, and
-  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges.
-  \end{itemize}
-\end{df}
-$\nodes$, $\mols$, $\edges$, and $\nlabel$ define a labelled graph.
-%
-Additionally, $\pairs$ defines which molecules can fuse with which molecules,
-and
-$\nodef$ and $\edgef$ are the activity functions for molecules on
-nodes and edges respectively.
-%
-The model captures the steady state of a VTS.
-%
-The analysis of the model will inform us about the network/graph
-properties of VTSs.
-
-% Let $\pairs(M')$ denote $\{P\setminus M'|  P \in \pairs \text{ and } P \intersect M' \neq \emptyset \}$.
-%
-A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
-$\nodef(k,\nlabel(n))$ is true.
-%
-A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
-$\edgef(k,M')$ is true.
-%
-We call $G$ {\em well-structured} if molecules $M$ is divided into
-two partitions $Q$ and $R$ such that
-for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $, and
-for each $(n,M',n') \in \edges$, $n \neq n'$ and
-$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
-%
-In other words,
-no molecule can participate in fusion from both channels and
-compartments,
-%
-there are no self loops, and 
-each edge carry only those molecules that are present in its source
-and destination nodes. 
-%
-An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
-if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
-such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
-%
-We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
-with its destination node $n'$
-and can not fuse with any other node.
-
-% $\pairs(M'')$ are not active in any other node.
-
-% We will also consider several variations of the model.
-% %
-% For example, unique edge between two nodes, activity of molecules is
-% not constrained by $\nodef$ and $\edgef$, etc.
-%
-
-A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
-such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
-%
-For a molecule $m \in M$,
-an {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
-such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
-each $ 0 < i < \ell$.
-%
-A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
-$n,...,n'$ in $G$.
-%
-% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
-% $m$-path $n,...,n'$ in $G$.
-%
-We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
-$n$ is $m$-reachable from $n'$.
-%
-We call $G$ {\em connected} if for each $n,n' \in \nodes$,
-$n'$ is reachable from $n$ in $G$.
-%
-We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
-VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
-
-%
-% In the definition, we do not care about the paths to be $m$-connected for some $m$.  
-% %
-% A variant of the definition may be sensitive to the $m$-connectedness, but
-% we are not considering the variation.
-
-\subsection{Encoding VTS}
-
-The conditions on the VTSs for a given size can be encoded as a QBF formula
-with uninterpreted functions.
-%
-To encode the constraints, we need variables for each aspect of
-VTS.
-%
-Let us suppose that the size of the graph is $\nu$ and number of
-molecules is $\mu$.
-%
-To fully finitize the problem, we also limit the maximum number $\pi$
-of edges present between two nodes.
-%
-Here, we list the Boolean variables and uninterpreted function symbols
-that encode parts of VTSs.
-\begin{enumerate}
-
-\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
-\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
-\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
-\item Boolean variable $p_{\{m_1,m_2,m_3,m_4\}}$ indicates if $\{m_1,m_2,m_3,m_4\} \in \pairs$
-\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
-encoding $\nodef(m)$ map
-\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
-encoding $\edgef(m)$ map
-\end{enumerate}
-We also have auxiliary Boolean variables that will help us encode the well-fused property. 
-\begin{enumerate}
-\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
-  holds
-\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
-\end{enumerate}
-
-We will describe several constraints that encode VTSs in this section.
-%
-In the next section, we will extend the encoding for the synthesis problem.
-%
-To avoid cumbersome notation, we will not explicitly write the ranges
-of the indexing in the constraints.
-%
-$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
-%
-$m$ will range over molecules, i.e., from $1$ to $\mu$.
-%
-$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
-%
-
-The following constraints encode the basic consistancy of VTSs.
-\begin{align*}
-  \texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
-  \land
-  \bigwedge\limits_{i,q} \neg e_{i,i,q}
-  \land
-  % \tag{\texttt{NodeC}}\label{eq:f0}\\
-  \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
-  \\
-  \texttt{ActivityC} =\;&
-  \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
-  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
-  % \tag{V2}\label{eq:f1}\\
-  \\
-  \texttt{PairingC} =\;&
-  \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
-                         (p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
-% \land\\ 
-%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
-  % \bigwedge\limits_{m} 
-  % (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
-  % (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
-  \\
-  \texttt{Fusion1} =\;&
-  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
-  \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
-                        \Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
-  & \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
-  \\
-  \texttt{Fusion2} =\;&
-\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
-  & \hspace{2cm} \neg 
-  \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
-\land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
-  \\
-  \texttt{Consistancy} =\;& \texttt{EdgeC} \land
-  \texttt{ActivityC} \land \texttt{PairingC} \land
-  \texttt{Fusion1} \land \texttt{Fusion2} 
-\end{align*}
-\texttt{EdgeC} states that each edge has at least one molecule,
-there are no self loops, and edge labels are consistent with node labels.   
-\texttt{ActivityC} states that active molecule are present.
-\texttt{PairingC} states that all molecules are divided into
-two types and any fusing set of molecules
-must have three molecules involved from one type and one molecule from the other.
-\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
-\texttt{Consistancy} is the conjunction of all of the above.
-
-\paragraph{Activity functions}
-We also need to encode that
-the activity of the molecules are controlled by activity functions.
-%
-However, the encoding functions can be given to us many different ways,
-for example as a lookup table, or a concise Boolean formula.
-%
-In the following section, we will assume the appropriate encoding is
-used for the functions and represent them by \texttt{NodeFun}$_m$
-and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
-%
-We will use $\nodef_m$ and $\edgef_m$ to represent functions that
-are not defined in a VTS.
-%
-% \begin{align}
-% \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
-% \tag{\texttt{ActiveN}}\label{eq:anb}\\
-%    \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
-%   \tag{\texttt{ActiveE}}\label{eq:aeb}
-% \end{align}
-%
-Later we will be synthesizing missing activity functions and 
-replace $\nodef_m$ and $\edgef_m$ with parameterized constraints that
-encode a space of candidate functions.
-
-\subsection{VTS properties}
-
-For synthesis of incomplete systems,
-we need properties  against which we synthesize the missing parts.
-%
-Here we will discuss two such properties proposed in earlier
-works~\cite{smtVTS}, namely stability and $k$-connectedness.
-%
-
-\paragraph{Stability property}
-%
-We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
-$m$-path from $i$ to $j$ of length less than or equal to $p$.
-%
-We use $m$-reachability to encode the stability condition in VTSs.
-%
-The following constraint recursively encodes that node $j$ is
-$m$-reachable from node $i$ in less than $p$ steps.
-%
-Subsequently, we encode stability condition using the reachability variables.
-\begin{align*}
-  \texttt{Paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-  \\
-  \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-  \\
-  \texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
-\end{align*}
-
-\paragraph{$k$-connected property}
-%
-$k$-connectedness expresses robustness against failure of few edges.
-%
-Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
-and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
-the modified VTS.
-%
-% To check whether $k$-connected is a
-% necessary condition, we remove (drop) $k-1$ edges from the graph and
-% if it disconnects the graph, and we get an assignment.
-% %
-% We have a graph that is not $k$-connected.
-%
-In the following, $\texttt{Fail}(d,k)$ encodes that only
-existing edges can be failed and exactly $k-1$ edges are failed.
-%
-$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
-%
-We use a new variable $r'_{i,j,p}$ to encode reachability from
-$i$ to $j$ in at most $p$ steps.
-%
-$\texttt{Connected}(r')$ says that all nodes are reachable from any
-other node.
-\begin{align*}
-  \texttt{Fail}(d,k) = & 
-  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
-  \sum_{i,j,q} d_{i,j,q} = k-1\\
-  % \texttt{ReachAbove}(d,r') = &
-  % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
-  \texttt{FReach}(d,r') = &\hspace{-1ex}
-   \bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
-  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
-\end{align*}
-We will be synthesizing $k$-connected graphs.
-%
-We define $\texttt{Connected}(k)$ that says for all possible valid failures
-the graph remains reachable. 
-\begin{align*}
-  \texttt{Connected}(k) = & \forall d.\;
-          (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
-                                \land \texttt{Connected}(r'))
-% \\
-  % \texttt{Disconnected}(k) = & \exists d.\;
-  %         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
-  %                               \land \lnot \texttt{Connected}(r'))
-\end{align*}
-Since $d$ variables in $\texttt{Connected}(k)$ are universally
-quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
-%
-
-% \subsection{Solvers}
-% Due the combinatorial nature of the graphs, the search space is huge
-% and often hard to enumerate naively.
-% %
-% We need sophisticated solvers
+We need sophisticated solvers
 

### 2018-10-03 papers/journal/prelim.tex
model and prelim

@@
-% \subsection{VTS properties}
+We will use lower case variables like $e,r,s$ etc to represent vectors of Boolean variables
+possibly indexed with multiple dimensions.
+%
+For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
+%
+%
+A Boolean variable may take Boolean values $1$ or $0$.
+%
+The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
+%
+$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
+collection of formulas.
+%
+We will use the variables and the operators to construct Boolean formulas to
+encode our problems.
+%
+An assignment is a map from variables in the formula to Boolean values.
+%
+An assignment may satisfy a formula if the interpretation of Boolean operators
+reduce the whole Formula into 1.
+%
+The problem of finding a satisfying assignment for a Boolean formula is
+hard.
+%
 
-% For the synthesis of incomplete systems,
-% we need properties against which we synthesize the missing parts.
-% %
-% Here we will discuss two such properties proposed in earlier
-% works~\cite{smtVTS}, namely stability and $k$-connectedness.
-% %
-
-% \paragraph{Stability property}
-% %
-% We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
-% $m$-path from $i$ to $j$ of length less than or equal to $p$.
-% %
-% We use $m$-reachability to encode the stability condition in VTSs.
-% %
-% The following constraint recursively encodes that node $j$ is
-% $m$-reachable from node $i$ in less than $p$ steps.
-% %
-% Subsequently, we encode stability condition using the reachability variables.
-% \begin{align*}
-%   \texttt{Paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-%   \\
-%   \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-%   \\
-%   \texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
-% \end{align*}
-
-% \paragraph{$k$-connected property}
-% %
-% $k$-connectedness expresses robustness against failure of few edges.
-% %
-% Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
-% and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
-% the modified VTS.
-% %
-% % To check whether $k$-connected is a
-% % necessary condition, we remove (drop) $k-1$ edges from the graph and
-% % if it disconnects the graph, and we get an assignment.
-% % %
-% % We have a graph that is not $k$-connected.
-% %
-% In the following, $\texttt{Fail}(d,k)$ encodes that only
-% existing edges can be failed and exactly $k-1$ edges are failed.
-% %
-% $\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
-% %
-% We use a new variable $r'_{i,j,p}$ to encode reachability from
-% $i$ to $j$ in at most $p$ steps.
-% %
-% $\texttt{Connected}(r')$ says that all nodes are reachable from any
-% other node.
-% \begin{align*}
-%   \texttt{Fail}(d,k) = & 
-%   \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
-%   \sum_{i,j,q} d_{i,j,q} = k-1\\
-%   % \texttt{ReachAbove}(d,r') = &
-%   % \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
-%   \texttt{FReach}(d,r') = &\hspace{-1ex}
-%    \bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
-%   \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
-% \end{align*}
-% We will be synthesizing $k$-connected graphs.
-% %
-% We define $\texttt{Connected}(k)$ that says for all possible valid failures
-% the graph remains reachable. 
-% \begin{align*}
-%   \texttt{Connected}(k) = & \forall d.\;
-%           (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
-%                                 \land \texttt{Connected}(r'))
-% % \\
-%   % \texttt{Disconnected}(k) = & \exists d.\;
-%   %         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
-%   %                               \land \lnot \texttt{Connected}(r'))
-% \end{align*}
-% Since $d$ variables in $\texttt{Connected}(k)$ are universally
-% quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
-% %
-% Therefore, synthesis against this property will require QBF reasoning.
-% %
-% We may make the formula quantifier free  by considering all possible failures
-% separately and introducing a vector of reachability variables for each
-% failure.
-% %
-% However, this will blow up the size of the formula and may not be
-% solvable by a SAT solver.
-% %
+Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
+%
+For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
+%
+The formula says that for both the values of $x$ there is a value of $y$
+such that $x \lor y$ is 1.
+%
+The problem of finding satisfying assignment for QBFs is even harder problem.
+%
 
 \subsection{Solvers}
-Due to the combinatorial nature of the graphs, the search space is huge
-and often hard to enumerate naively.
+In this paper, we will encode several problems into finding satisfying
+solutions of a Boolean formula or QBFs.
 %
-We need sophisticated solvers
+We will use SAT/SMT/QBF solvers to get the satisfying assignments.
+%
+The modern solvers are result of several decades of research
+and implement sophisticated algorithms.
+%
+A SAT solver typically implements conflict-driven clause learning(CDCL).
+%
+The QBF solver add support of quantifiers by adding more rules for
+quantifiers.
+
+%
+% Due to the combinatorial nature of the graphs, the search space is huge
+% and often hard to enumerate naively.
+%
+% We need sophisticated solvers
 

### 2018-10-04 papers/journal/related.tex
Related results

--- 2018-04-15 papers/sabs-2017/paper/related.tex
@@
-%\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
 Modern day SAT/SMT solvers can handle millions of variables and due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT/SMT solvers.
@@
 
-%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
+In recent years, there has been a wide range of methods
+developed for the similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
+%
+They range from filling gaps an implementation of C programs from the pool of template predicates to learn a program from example
+runs of the program.
+%
+In the course of developing such methods,
+the background technology, i.e. solving of quantified
+constraints has been evolving rapidly~\cite{lonsing2010depqbf,z3Quant}.
+%
+
+There has been some work in
+applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}.
+A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
+Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
+The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis.
+The paper~\cite{cardelli2017syntax} in addition to using SMT over ODE, uses a template-guided approach.
+In our case queries contain quantifiers so we have employed QBF solving with Z3 for the solving the synthesis problem.
+To our best knowledge, this is the first application of synthesis in VTS.
 
@@
 %%% End:
+~

### 2018-10-05 papers/journal/related.tex
Related section SAT/SMT part rewrite

@@
-Modern day SAT/SMT solvers can handle millions of variables and due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT/SMT solvers.
-There are many graphs related combinatorial work \cite{gay2013solving,wotzlaw2012generalized} that have used SAT solvers.
-Thanks to the improvement in SAT solver and formal techniques, tools like model checkers and theorem provers scalability and combinatorial solving capability are now being used to model complex biological systems \cite{heule2010exact,yordanov2013smt,mangla2010timing}.
-% Many network questions are being reduced to solving a SAT question.
-Many of these biological system uses these tools and techniques to reason about graphs and networks rules with possible exhaustive search \cite{guerra2012reasoning,chin2008biographe}.
-
-Recently these tools and techniques have found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
-GNR is a complex system driven by many complex rules.
-We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking,shukla}, but scaling it to cases which are interesting biologically is still a challenge.
-In this paper, we have achieved the scalability required for analyzing VTS for eukaryotic cells, of total ten compartments (N = 10).
-\\
+SAT and SMT solvers are a perfect fit for solving combinatorial problems due to their exhaustive nature of searching. 
+%
+Improvement in SAT and SMT solvers in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
+%
+Many of which involve reasoning about graphs and networks rules with possible exhaustive search and hence can be reduced to solving a SAT/SMT question. 
+%
+Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example.
+%
+We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS) \cite{mani2016stacking,shukla}.
 

### 2018-10-06 papers/journal/experiments.tex
added experiments section: a basic cut paste

--- 2018-06-14 papers/synth/experiments.tex
@@
  %   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-    yeast-graph[3C]   & 95.016    & 1 E  &   timeout  & N/A   & 1571.42  & 1 E  & 530.211   & 1 E & 110.206  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
+    yeast-graph[3C]   & 95.016    & 2 E  &   timeout  & N/A   & 1571.42  & 2 E  & 530.210   & 2 E & 72.316  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
 
@@
     node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-    yeast-graph & 40.225  & 1 E  &   timeout  & N/A   & 1393.84  & 1 E  & 468.161   & 1 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
+    yeast-graph & 40.225  & 2 E  &   timeout  & N/A   & 1393.84  & 2 E  & 468.161   & 2 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
     mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline

### 2018-10-06 papers/journal/experiments.tex
added experiments section: small improvement in cbmc section

@@
-\begin{sidewaysfigure}[t]
-  \centering
-  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
-% \begin{table}[t]
-%   \centering
-%   \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
-    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Table a}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
-    \cline{2-11}
-    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
-    \hline
+\begin{enumerate}
+  \item CBMC: \\
+The first tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
+%
+Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
+%
+CBMC allows the depth of model to be incrementally increased to any desired value.
 
-    plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\infty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & -1 E, -1 AE, -1 AN. +1 E, +1 N. \\\hline
-    plos2-dia[4C] & 0.266 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
-    sub-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline
-    node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE.\\\hline
- %   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-    yeast-graph[3C]   & 95.016    & 2 E  &   timeout  & N/A   & 1571.42  & 2 E  & 530.210   & 2 E & 72.316  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
+CBMC consists of a C-language front-end (CFE) and SAT Solver back-end (SAT).
+%
+CBMC accepts ANSI-C programs interspersed with special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
+%		
+In our experiments, the vesicle transport network was modeled as a non-deterministic C-program manipulating a graph with labeled edges with the fusion rules and steady state properties expressed as constraints
+using assumes. 
+%		
+The correspondence relationship between connectedness conditions
+and guarantees for steady state were expressed as assertions to be checked. 
+%		
+Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, CBMC verifies the properties by executing the following steps:
+	\begin{itemize}
+	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
+depth iff the Boolean formula is valid.
+	\item Check (using a SAT solver) validity of the verification condition. CBMC reports successful verification if the formula is found to be valid. If not, then CBMC produces a counterexample,
+an assignment to the variables of the model, that is a witness to the violation of the property.
+	\end{itemize}
 
-mammal-graph[3C]  &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A    &  timeout     & N/A\\\hline
-   %    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
-  \end{tabular}
-  % \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
-  % Time is reported in seconds.}
-  % \label{tab:qf-graph}
-% \end{table}
-  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
-    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-    {\multirow{2}{*} \textbf{Table b}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
-    \cline{2-11}
-    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
-    \hline
+CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification.
+Besides using MiniSat as a default SAT solver for our model,
+		we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}. 
+%		
+MiniSat performed satisfactorily in comparison to other SAT solvers.
+\item Z3: \\
+	We have implemented the encodings for each variants using the python interface of Z3 in a tool (MAA). 
+%
+Our tool allows the user to choose a model and the size
+of the network besides other parameters like connectivity and number of parallel edges. 
+%		
+It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model ( a satisfying assignment that respects the constraints). 
+%
+This tool also translates the satisfying model found by Z3 into
+a VTS and presents a visual output to the user in form of annotated graph. 
+%
+We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
 
-    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PE, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
-    plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
-    sub-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-    node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-    yeast-graph & 40.225  & 2 E  &   timeout  & N/A   & 1393.84  & 2 E  & 468.161   & 2 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
-    mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
-  \end{tabular}
-    \caption{Run-times for synthesis queries.
-\#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS.
-Time is reported in seconds.
-(a) The solver used is DepQBF (b) The solver used is Z3.
-The sub-mammal is a subgraph of the complete mammal-graph.
-In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules.
-In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge.
-The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}
-
-  % \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
-  % Time is reported in seconds.}
-  \label{tab:qf-graph}
-\end{sidewaysfigure}
-
-%[M=8, N=2, Q=2]    
-% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
-
+\item DEPQBF: \\
 We have implemented the encodings in a tool
@@
 
+\end{enumerate}
+
 %

### 2018-10-06 papers/journal/related.tex
added experiments section: small improvement in cbmc section

@@
 %
-Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example.
+Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example.
 %
-We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS) \cite{mani2016stacking,shukla}.
+We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS)~\cite{mani2016stacking,shukla}.
 

### 2018-10-09 papers/journal/experiments.tex
restructure experiments

@@
-\begin{enumerate}
-  \item CBMC: \\
+We have developed three different tools (satVTS, smtVTS, synthVTS) for implementation of proposed encodings.
+All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
+\subsection{SATVTS (Bounded model checker based tool)} 
 The first tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
@@
 CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification.
-Besides using MiniSat as a default SAT solver for our model,
-		we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}. 
+Besides using MiniSat as a default SAT solver for our model, we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}.
 %		
 MiniSat performed satisfactorily in comparison to other SAT solvers.
-\item Z3: \\
+
+\subsection{SMTVTS/pyVTS (SMT based tool)}
 	We have implemented the encodings for each variants using the python interface of Z3 in a tool (MAA). 
@@
 
-\item DEPQBF: \\
+\subsection{SynthVTS (QBF based synthesis tool)} 
 We have implemented the encodings in a tool
@@
 %
-The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
-CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
 %The experiments were conducted with a 900s timeout.
@@
 
-\end{enumerate}
-
 %

### 2018-10-09 vts-synth/src/main.cpp

@@ -6,7 +6,6 @@
 
 #include <iostream>
 #include <fstream>
-
 #include <unistd.h>
 #include <chrono>
 #include <ctime>

### 2018-10-09 papers/journal/experiments.tex
added pyVTS text in experimentation section to the paper

@@
 We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
+%
+To illustrate usability of our tool in the last column of the table 1, we present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10. 
+%
+We found no graph for the variant A with constraints Ann and Aen. 
+%
+Replacing constraint on the node of Ann with Anb (variant B)
+does not affect the outcome. 
+%
+If we allow every present molecule to stay active
+(Ann) but constraint the edge by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. 
+%
+Similarly, the results for the other cases are presented in the table.
+
+In Table~\ref{tab:qf-grabh}, we present the running times for the sear
+ch of
+VTSs of sizes 2 to 10 that satisfy the variants.
+and compare with our old encoding
+({Old-e}) from~\cite{shukla}.
+%
+For the comparison between both encodings we have fixed the total
+number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and
+$|M| = 2|N| + 1$ for $|N| = 2$.
+%
+For each variant, we fix maximum number of parallel
+edges to 2.
+%
+In the table we have shown comparison for specific connectivity, for
+example variant A is checked against any graph with connectivity 2,
+variant B with connectivity 3 similarly for the rest of the Variants.
+%
+
+We have compared our performance with the performance of our earlier
+CBMC based implementation (old-encoding).
+%
+For example, the formula for variation F, the total number of
+compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 s
+ecs)
+with a SAT result.
+%
+In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
+%
+``!'' indicate that the constraints were unsatisfiable.
+%
+Using this encoding in comparison to the old one, not only we got effi
+ciency improved for finding a SAT model but also did better in the cas
+e of refutation that no model exist (Table 2 Variant A timing comparis
+on and Variant D with N =2). 
+%
+Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
+eukaryotic cells with a total number of 10 compartments.
+%
+Furthermore, we experimented with limits of our tools and found
+that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ n
+odes.
 

### 2018-10-09 papers/journal/conclusion.tex
added synthesis conclusion text as it is

--- 2018-05-06 papers/synth/conclusion.tex
@@
 In this paper, we presented encodings of the synthesis problems
-that may rise from VTSs.
+that may arise from VTSs.
 %
@@
 %
-Our tool timedout on larger examples.
+Our tool timed out on larger examples.
 %
@@
 %
-We will take this tool to the biologists and develop wet experiments 
-that may validate some synthesis results from the tool.
+We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
 %
-Our model of VTSs are static graphs.
+Our model of VTSs is static graphs.
 %
-In future, we will study the dynamic behaviours of VTSs.
+In future, we will study the dynamic behaviors of VTSs.
 %

### 2018-10-11 papers/journal/experiments.tex
Added all three result tables and rewritten CBMC first paragraph

@@
 All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
+
+\input{result-table}
+
 \subsection{SATVTS (Bounded model checker based tool)} 
@@
 %
+CBMC is a Bounded Model Checker for C and C++ programs. 
+%
 Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
 %
-CBMC allows the depth of model to be incrementally increased to any desired value.
+The depth of model is specified by the user and can be  incrementally increased to a desired value.
 
-CBMC consists of a C-language front-end (CFE) and SAT Solver back-end (SAT).
+The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
 %
-CBMC accepts ANSI-C programs interspersed with special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
+CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
 %		
-In our experiments, the vesicle transport network was modeled as a non-deterministic C-program manipulating a graph with labeled edges with the fusion rules and steady state properties expressed as constraints
-using assumes. 
+In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes.
 %		

### 2018-10-11 papers/journal/result-table.tex
Added all three result tables and rewritten CBMC first paragraph

--- 2018-06-14 papers/synth/experiments.tex
@@
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\def\arraystretch{1.6}
+\caption{
+{\bf SNARE regulation and graph connectedness.}}
+\begin{tabular}{|c|l|l|c|}
+\hline
+\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness}\\ \thickhline
+1. & Boolean function & Boolean function & N = 2C S = 3C \\ \hline
+2. & None & Boolean function & N \& S = 3C\\ \hline
+3. & Boolean function & SNARE-SNARE inhibition & N \& S = 4C\\ \hline
+4. & None & SNARE-SNARE inhibition & No graphs found\\ \hline
+5. & Boolean function & None & No graphs found\\ \hline
+6. &  None & None & No graphs found\\ \hline
+
+%6. & Arbitrary Boolean & Specificity matrix and every edge is distinct & N \& S = 3C\\ \hline
+
+\end{tabular}
+\label{tab:smt-grph}
+%\end{adjustwidth}
+\end{table}
+
+\begin{table}[t]
+	\centering
+	% \def\arraystretch{1.6}
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		{\multirow{2}{*}{\textbf{Variant}}}  &
+		\multicolumn{2}{c|}{\textbf{Constraints}} &
+		{\multirow{2}{*}{\textbf{Graph connectivity}}}
+		% \multicolumn{2}{c|}{\textbf{Graph connectivity}}
+		\\
+		\cline{2-3}
+		&  \textbf{Rest} & \textbf{Activity} &  % & \textbf{Sampling: Guarantee}
+	\\ \hline
+
+	A. & \multirow{5}{*}{
+		\makecell{ \ref{eq:f0}--\ref{eq:fuse2},\\
+			\ref{eq:reach1},\ref{eq:reach2},\\
+			\ref{eq:drop1}--\ref{eq:drop4}}
+	}
+	& \ref{eq:ann},\ref{eq:aen} & No graph     \\\cline{3-4}
+	B. & & \ref{eq:anb},\ref{eq:aen} & No graph     \\\cline{3-4}
+	C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected  \\\cline{3-4}
+	D. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected  \\\cline{3-4}
+	E. & & \ref{eq:ann},\ref{eq:aep} & No graph     \\\cline{3-4}
+	F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected  \\\hline
+
+	% C_es :Self edges are allowed
+	% C_ed : Every edge is distinct 
+\end{tabular}
+\caption{{\bf Activity regulation of molecules vs. graph connectivity.
+}}
+\label{tab:smt-grph}
+\end{table}
+
 \begin{sidewaysfigure}[t]
@@
 		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-    yeast-graph[3C]   & 95.016    & 1 E  &   timeout  & N/A   & 1571.42  & 1 E  & 530.211   & 1 E & 110.206  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
+		yeast-graph[3C]   & 95.016    & 2 E  &   timeout  & N/A   & 1571.42  & 2 E  & 530.210   & 2 E & 72.316  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
 
@@
 		node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-    yeast-graph & 40.225  & 1 E  &   timeout  & N/A   & 1393.84  & 1 E  & 468.161   & 1 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +1 E, 7 PE, 8 N. \\\hline
+		yeast-graph & 40.225  & 2 E  &   timeout  & N/A   & 1393.84  & 2 E  & 468.161   & 2 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
 		mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
@@
 	% Time is reported in seconds.}
-  \label{tab:qf-graph}
+	\label{tab:qbf-graph}
 \end{sidewaysfigure}
-
-%[M=8, N=2, Q=2]    
-% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
-
-We have implemented the encodings in a tool
-called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
-%
-The tool takes a partially defined VTS as input in a custom designed
-input language.
-%
-The input is then converted to the constraints over VTS. 
-%
-The tool can not only synthesize the above-discussed queries, but also their
-combinations.
-%
-For example, our tool can modify labels of nodes or edges while
-learning activity functions.
-%
-Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
-processing formulas. 
-%
-Since some of the formulas involve alternation of quantifiers over
-Boolean variables Z3 is not a suitable choice for those examples.
-%
-We translate the formulas created by Z3 tool into a standard
-QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
-%
-We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
-%
-Our tool includes about 7000 lines of code.
-
-We have applied~\ourtool~on six partially defined VTSs.
-%
-The results are presented in table~\ref{tab:qf-graph} for both the solvers
-\depqbf and \zthree.
-%
-To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
-quantifier-free.
-%
-% The experiments were conducted on a machine,
-% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
-%
-The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
-CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
-%The experiments were conducted with a 900s timeout.
-%
-The first four VTSs are synthetic but inspire from literature for
-typical motifs in VTSs. 
-The third VTS is a subgraph of the last VTS.
-%
-%
-The fifth VTS is taken from~\cite{burri2004complete}.
-%
-The last VTS represent mammalian SNARE map created by studying the literature references.
-
-The table shows timing for various synthesis queries.
-%
-For each synthesis query, we have two columns.
-%
-One column reports the timing and the other reports the minimum changes
-needed to obtain a valid VTS.
-%
-$\infty$ indicates that any number of changes with the synthesis query
-search space can obtain the VTS.
-%
-%\ashu{@ankit: please discuss all the synthesis queries in the table.}
-In the table, we are reporting five synthesis queries
-%
-The first one only adds new labelled edges to the graph.
-%
-We have ranked the all possible graph edits with the simple rank of
-minimum updates.
-% %
-% Our tools were able to complete the graphs by adding five new edges
-% and nine new molecules in 210s.
-%
-The second query adds new labels to the edge.
-%  and was able to
-% fix the graphs with eleven new molecule labels in 180s.
-%
-The third query synthesizes NNF Boolean functions only containing
-$\land$ and $\lor$ gates for activity functions, while allowing
-more edges to be added.
-%
-The result shows the basic template of 4 leaves and 3 gates.
-%
-% The tool was able to synthesize the Boolean functions in 470s.
-%
-To illustrate the versatility of our tool, the fourth query
-synthesizes $3$-CNF functions (encoding not presented).
-%  and was able to
-% synthesis the results for all graphs in 500s.
-%
-Finally, we report queries that allows both addition and deletion of edges, and labels
-of node and labels.
-
-%
-%Our experiments suggest that the synthesis problems are solvable by modern 
-%solvers and the synthesis technology may be useful for biological research.
-%
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "main"
-%%% End:

### 2018-10-14 papers/journal/experiments.tex
Improved Experimentation and Previous work

@@
-We have developed three different tools (satVTS, smtVTS, synthVTS) for implementation of proposed encodings.
+We have developed three different tools (\sattool, \smttool, \ourtool) for implementation of proposed encodings.
+{\sattool} is based on the architecture of a Bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
+{\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem.
+The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS.
+It is based on the QBF encoding and uses {\depqbf} solver to solve the generated QBF.
 All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.

### 2018-10-14 papers/journal/related.tex
Improved Experimentation and Previous work

@@
-SAT and SMT solvers are a perfect fit for solving combinatorial problems due to their exhaustive nature of searching. 
+\begin{table}[!ht]
+	%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline 
+		\textbf{N} & \textbf{Total Number of graphs} \\ \hline
+		1.         & 0                               \\ \hline
+		2.         & 0                               \\ \hline
+		3.         & 0                               \\ \hline
+		4.         & 1                               \\ \hline
+		5.         & 2                               \\ \hline
+		6.         & 15                              \\ \hline
+		7.         & 121                             \\ \hline
+		8.         & 2159                            \\ \hline
+		9.         & 68715                           \\ \hline
+		10.        & 3952378                         \\ \hline
+	\end{tabular}
+	\label{tab-graphs}
+     \caption{Number of simple 3-edge-connected unlabeled N-node graphs.}
+	%\end{adjustwidth}
+\end{table}
+
+The analysis of vesicle traffic systems is a difficult problem
+because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
 %
+For example, we might want to check some conjecture of interest for all 3-connected graphs and
+all possible variations of SNARE regulation rules. 
+%
+The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab-graphs} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
+%
+
+Previous analyses of VTS have mostly been based on sampling approach~\cite{mani2016wine, mani2016stacking}. 
+%
+In these analyses, vesicle traffic is
+modeled as a dynamical system. 
+%
+The traffic rule specifies how the system transitions from one
+time point to the next. 
+%
+Given a traffic rule and an initial condition, the system is evolved over time until a steady state is reached. By studying a large sample of randomly generated traffic
+rules, such analyses can make statistical claims about vesicle traffic.
+%
+Hence making precise general prediction about the properties of vesicle traffic networks over all possible traffic rules, not just for a sampled subset is not possible.
+%
+SAT and SMT solvers are a perfect fit for this situation, solving combinatorial problems with their exhaustive nature of searching. 
+%
+These tools check a specified logical property
+on every possible state of a model constructed using variables ranging over Boolean or any
+finite discrete type.
+
 Improvement in SAT and SMT solvers in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 

### 2018-10-14 papers/journal/result-table.tex
Improved Experimentation and Previous work

@@
 {\bf SNARE regulation and graph connectedness.}}
-\begin{tabular}{|c|l|l|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness}\\ \thickhline
-1. & Boolean function & Boolean function & N = 2C S = 3C \\ \hline
-2. & None & Boolean function & N \& S = 3C\\ \hline
-3. & Boolean function & SNARE-SNARE inhibition & N \& S = 4C\\ \hline
-4. & None & SNARE-SNARE inhibition & No graphs found\\ \hline
-5. & Boolean function & None & No graphs found\\ \hline
-6. &  None & None & No graphs found\\ \hline
+\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness} & \bf{Timing} \\  \thickhline
+1. & Boolean function & Boolean function & 2C & \\ \hline
+2. & None & Boolean function & 3C & \\ \hline
+3. & Boolean function & SNARE-SNARE inhibition & 4C & \\ \hline
+4. & None & SNARE-SNARE inhibition & No graphs found & \\ \hline
+5. & Boolean function & None & No graphs found & \\ \hline
+6. &  None & None & No graphs found & \\ \hline
 

### 2018-11-09 papers/journal/abstract.tex
Updated the directory from the Overleaf directory, added encodings from CBMC paper/ PLOS paper

--- 2018-06-14 papers/journal/abstract.tex
@@
-Vesicle Traffic Systems(VTSs) are the material transport 
+Vesicle Traffic Systems (VTSs) are the material transport
 mechanisms among the compartments inside the biological cells.
+%
+The compartments are viewed as nodes that are labeled with the
+containing chemicals and the transport channels
+are similarly viewed as labeled edges between the nodes.
+%
+Several interesting questions about VTS translates to combinatorial
+search and synthesis problem. 
+%
+We present novel SAT, SMT and QBF based encodings of the properties
+over vesicle traffic systems and a tool that searches for the networks
+that satisfies the properties using these solvers. 
+%
+Understanding VTSs is an ongoing area of research and for many cells
+they are partially known...
+%
+In our experiments, we show that our tool can search for network of sizes that are considered
+to be relevant by biologists.
+
+% Vesicle Traffic Systems(VTSs) are the material transport 
+% mechanisms among the compartments inside the biological cells.
 

### 2018-11-09 papers/journal/encoding.tex
Updated the directory from the Overleaf directory, added encodings from CBMC paper/ PLOS paper

--- 2017-08-16 paper/encoding.tex
@@
-In this section, we will formally define VTSs as a labeled graph
-and the discussed conditions on the graphs.
-%
-Subsequently, we will present the SAT encoding of the search problems
-for the graphs that satisfy the conditions.
+In this section we will present the SAT, SMT and QBF based encoding of both the search and the synthesis problem.
+We will start with the SMT based encoding and later present the contrast with the BMC encoding.
 
-\subsection{Model}
-
-We model VTSs as labeled directed graphs.
-The graph labels both nodes and edges with sets of molecules to denote
-the set of molecules present in them.
-The graph is formally defined as follows.
-
-\begin{df}
-  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$, where
-  \begin{itemize}
-  \item $\nodes$ is a set of nodes representing compartments in the VTS,
-  \item $\mols$ is the set of molecules flowing in the system, 
-  \item $\edges \subseteq \nodes \times (\powerset{\mols}-\emptyset) \times \nodes$ is the
-    set of edges with molecule sets as labels,
-  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes,
-  \item $\pairs \subseteq \mols \times \mols$ is pairing relation,
-  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes, and
-  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges.
-  \end{itemize}
-\end{df}
-$\pairs$ defines which molecules can fuse with which molecules.
-%
-Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
-%
-$\nodef$ and $\edgef$ are used to define activity of molecules on
-nodes and edges respectively.
-%
-A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
-$\nodef(k,\nlabel(n))$ is true.
-%
-A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
-$\edgef(k,M')$ is true.
-%
-We call $G$ {\em well-structured} if molecules $M$ is divided into
-two equal partitions $M_1$ and $M_2$ such that $P \subseteq M_1 \times M_2$, and
-for each $(n,M',n') \in \edges$, $n \neq n'$, 
-$M' \subseteq \nlabel(n)$, and $M' \subseteq \nlabel(n')$.
-%
-
-We will also consider several variations of the model.
-%
-For example, unique edge between two nodes, activity of molecules is
-not constrained by $\nodef$ and $\edgef$, etc.
-%
-
-A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
-such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
-%
-For a molecule $m \in M$,
-an {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
-such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
-each $ 0 < i < \ell$.
-%
-A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
-$n,...,n'$ in $G$.
-%
-% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
-% $m$-path $n,...,n'$ in $G$.
-%
-We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
-$n$ is $m$-reachable from $n'$.
-%
-An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
-if there are molecules $m,m' \in \mols$ such that $m$ is active in
-$(n,M',n')$, $m'$ is active in $n'$, and $(m,m') \in \pairs$.
-%
-We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
-with non-empty fusing molecules $M'' \subseteq M'$
-and $\pairs(M'')$ are not active in any other node.
-%
-We call $G$ {\em connected} if for each $n,n' \in \nodes$,
-$n'$ is reachable from $n$ in $G$.
-%
-We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
-VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
-
-\paragraph{Search problem}
-Based upon earlier discussion, we need to answer the following search
-question among VTSs.
-For a given $k$, size $\nu$, and molecule number $\mu$,
-we are searching for well-structured, stable, and well-fused VTS
-$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and
-$G$ is not $k$-connected.
+\subsection{SMT based encoding}
 
@@
 
+% We can go down or up using -C \_ option.  \newline
+
+\subsection{BMC based encoding}
+
+The BMC encoding differs with presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
+%
+Variables are not Boolean indexed with multiple dimensions but multidimensional arrays. 
+%
+For clarity, we will only present the stability encoding.
+
+We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
+%
+We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
+%\begin{align*}
+%graph [i] [j] = x.
+%\end{align*}
+
+%
+The nodes are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
+%
+The index of the bitvector implicitly determines the corresponding molecule we are referring to.
+%
+
+The molecule set is divided into Q and R-SNAREs. 
+%
+For clarity, we consider both in the same amount and represent the first half of the bitvector as  Q-SNAREs and rest as R-SNAREs.
+%
+A node in the system with M = 4 molecules is interpreted as a tag [M1, M2, M3, M4]. 
+%
+Where M1, M2 are Q-SNAREs and M3, M4 are R-SNAREs.
+%
+Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the molecule i.
+%
+Similarly, an edge in the graph is also tagged as a bitvector of length M.   
+%
+We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected.
+
+In order to specify the stability condition, we use a combination of enumeration and nondeterminism.
+%
+Nondeterminism can be considered as an oracle that guesses a correct $m$-path for a specific m if it exists. 
+%
+We then use this path as a witness to ensures that stability is maintained for each outgoing molecule m on every edge E.
+
+\subsubsection{Constraints for stability condition}
+%
+We use NOracle to guess the required path to encode the stability condition in VTS.
+%
+The following constraint encodes that there is a $m$-path from node $i$ to node $j$ of maximum $w$ length.
+%there is a edge between $i^{\prime \prime}$ and
+%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
+%
+% \begin{align}
+%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
+%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
+%   \tag{S1}\label{eq:reach1}
+% \end{align}
+%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
+%
+The NOracle perform enumeration of $m$-${paths}_i^j$ of at most w length. 
+%
+Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length w-1.
+%by performing series of node hops till final node destination j is reached.
+%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.
+
+%|m-path| = 1 \lor  |m-path| = 2 \lor ...  |m-path| = w.     \\
+%\bigvee\limits_{l = 1}^{|path| - 1} |m-path| = l
+
+\begin{align}
+NOracle (m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} | {m-path}_i^j | = l
+  \tag{S1}\label{eq:reachbmc1}
+\end{align}
+
+Now we can encode stability using the NOracle and say if there is an $m$-edge between $i$ and $j$, there is a $m$-path from $j$ to $i$ of length max w.
+\begin{align}
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} e[i][j][q][m]) \limplies NOracle(m, j, i, w)
+  \tag{S2}\label{eq:reachbmc2}
+\end{align}
+
+%A variant of the definition may be sensitive to the $m$-connectedness, but
+%we are not considering the variation.
+
+\subsection{The key improvement}
 The key improvement in our work over the earlier tool is the
@@
 
-% We can go down or up using -C \_ option.  \newline
-
-\subsection{SAT problems for different variants}
+\subsection{SMT problems for different variants}
 %\ankit{Bring model variant table here}
@@
 %
-\begin{enumerate}[label=\Alph*]
+\begin{enumerate}
 \item Every present molecule is considered to be active.
@@
 %
-The constraints for the variants can be given to a SAT solver to find
+The constraints for the variants can be given to a SMT solver to find
 VTSs that belong to the variants.
 
-% We have applied the tool for the above variations for searching the
-% VTSs that satisfies their corresponding properties. 
-%
-% After creating the constraint using different Boolean variables 
-% we ship them directly to the solver.
-% %
-% In case of a satisfying (SAT) assignment of the added constraints the
-% Z3 theorem prover gives a model with the variable assignment.
-% %
-% In case no possible satisfying assignment the solver returns UNSAT.
-
-%
-%
-
-% \subsection{Creating a solver and solving these constraints}
-% We will create a solver and add these build constraint using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.
-
-% \begin{figure}[ht]
-% %\vspace{-3mm}
-% \begin{verbatim}
-% # Create a solver
-% s = Solver()
-% # Add these constraints to it.
-% s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)
-
-% # Check for the satisfiability assignment.
-% print s.check()   
-% \end{verbatim}
-% \caption{Solving for these constraints.}
-% \label{code:motivate}
-% \end{figure}
-
-%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
+\subsection{Universal condition}
 

### 2018-11-09 papers/journal/intro.tex
Updated the directory from the Overleaf directory, added encodings from CBMC paper/ PLOS paper

A characteristic feature of eukaryotic cells is the presence of multiple internal membrane bound organelles. 
%
These organelles exchange molecules amongst themselves in small membrane bound packets called vesicles. 
%
The recognition of cargo molecules to be loaded onto these vesicles and the recognition of the correct target organelles for each vesicle is performed by an intricate network of molecules called the vesicle transport system []. 
%
We call the set of internal organelles, together with the molecular routes that connect them through vesicle exchange, the vesicle transport network. 
%
Although vesicle mediated traffic was discovered decades ago [17], the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year [1, 3].

Completing the vesicle traffic network is a difficult task for many reasons: (1) the core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms [6, 12, 14], and even in different cell types within an organism can be different [10, 11], (2) although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different [15, 16], (3) behaviour of traffic molecules in vitro is different from their behaviour inside cells [9], (4) molecules can have redundant routes within the cell [7,8], and (5) it can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules [2, 13].

Nonetheless, completing the vesicle traffic network for different organisms is very useful. Many diseases are caused by the malfunction of the vesicle traffic network. Knowledge of the complete network would be helpful in identifying the root causes.[4,5]. At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic [14].

In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs and output various completed versions which can then be tested experimentally.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-11-09 papers/journal/model.tex
Updated the directory from the Overleaf directory, added encodings from CBMC paper/ PLOS paper

@@
   \item $\pairs \subseteq 2^{\mols}$ is pairing relation,
-  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes, and
-  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges.
+  \item $\nodef : \mols \maps \powerset{\mols} \maps B$ is activity maps for nodes, and
+ \item $\edgef : \mols \maps \powerset{\mols} \maps B$ is activity maps for edges.
   \end{itemize}
@@
 % Let $\pairs(M')$ denote $\{P\setminus M'|  P \in \pairs \text{ and } P \intersect M' \neq \emptyset \}$.
+
+\subsection{BMC and SMT}
+$\pairs$ defines which molecules can fuse with which molecules.
+%
+Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
+%
+$\nodef$ and $\edgef$ are used to define activity of molecules on
+nodes and edges respectively.
+%
+A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
+$\nodef(k,\nlabel(n))$ is true.
+%
+A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
+$\edgef(k,M')$ is true.
+%
+We call $G$ {\em well-structured} if molecules $M$ is divided into
+two equal-sized partitions $M_1$ and $M_2$ such that
+$P \subseteq M_1 \times M_2$, and
+for each $(n,M',n') \in \edges$, $n \neq n'$, 
+$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
+%
+In other words, a well-structured VTS has no self loops, and 
+each edge carry only those molecules that are present in its source
+and destination nodes.
+
+We will also consider several variations of the model.
+%
+For example, unique edge between two nodes, activity of molecules is
+not constrained by $\nodef$ and $\edgef$, etc.
+%
+
+\subsection{QBF and synthesis}
 %
@@
 
+\subsection{Uniform}
 A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
@@
 
-%
-% In the definition, we do not care about the paths to be $m$-connected for some $m$.  
-% %
-% A variant of the definition may be sensitive to the $m$-connectedness, but
-% we are not considering the variation.
-
 Let us discuss rough sizes of the system and expected behaviors.

### 2018-11-09 papers/journal/problem.tex
Updated the directory from the Overleaf directory, added encodings from CBMC paper/ PLOS paper

This section will present the different search problems of VTS.

\subsection{SMT}

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.

\subsection{BMC}
The notion of stability and connectivity varies slightly for BMC encoding.

%
We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
there exists a $m$-path in G with $n_1 = n'$ and $n_\ell = n$.
%

%
We call $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ there is a path from $n$ to $n'$ in G.
%
We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
%

We use $m$-${path}_i^j$ to denote an $m$-path between source node i and target node is j.

For the experimentation, we will restrict ourselves to the cycles of length one. 
%
This restriction puts an upper limit of N on the length of each searched path. 
%
Creating a formula to search a path of length N for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
%
Even if there exist shorter paths we have to create the formula of maximum size N. 
% 
To resolve the these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
%
This specified depth is called unwinding in the technical terms.
%and can be specified for each path separately.

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth w,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w length of unwinding.

\subsection{QBF and synthesis}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-11-09 papers/journal/property.tex
Updated the directory from the Overleaf directory, added encodings from CBMC paper/ PLOS paper

The conjecture relates graph-connectedness to a particular variation of SNARE pairing and regulation rules of the VTS.
%
We are interested in the following two type of properties of the transport graph:

\begin{enumerate}
\item Existential condition:
%the structural connectedness of the transport graph required for the system driven by a particular set of rules. 
structural connectedness of a transport graph which satisfies the stated set of rules.

%there is a transport graph with the structural connectedness which satisfies the stated set of rules.

%that a transport graph satisfies driven by a particular set of rules. 
%And we are interested in the least one.

\item Universal condition: 
%every graph with the structural connectedness satisfies the stated set of rules. 
the structural connectedness that ensures every transport graph with that fundamental structure satisfies the stated set of rules. 
%The goal is to find the minimum graph connectivity that satisfies sufficient condition.
\end{enumerate}

The goal is to find the minimum graph connectivity that satisfies each of these condition.

%We express both these conditions as assertions in our program.

\subsubsection{Checking existential conditions} 
In our program, the rules VTS needs to follow 
%
%are we represent the stability, fusion, SNARE pairing and regulation rules, and the connectedness property that the system needs to follow, as 
%
are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
%
Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
%
We use these functions to define the assertion that characterizes the existential condition to be checked. 
%
We will show in later sections how we encode these Boolean functions.

To ensure that k-connectedness is an existential condition, we have to find a k-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also have to ensure that the particular k is the least one. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a k-connected graph (G) we specify our property as a query for the existence of a model for a conjunction of the formula representing stability, fusion and specific graph connectivity constraint. 
%

\begin{align*}
  &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)} 
\end{align*}

We will start with the value of k = 1 and check for the satisfiability of the above formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of k. 
%
If the formula is not satisfiable we increment the k by 1 and perform the same procedure. 
%
In this way, we ensure that the reported k is the minimum connectivity of the VTS that satisfies the existential condition.  
% Used E as edge and L_e L_n as label for node and the edge,

\subsubsection{Checking universal conditions}

Similarly, for the conjecture that k-connectedness is a universal condition for the VTS, we have to ensure that every graph of k-connected structure satisfies all the rules (and constraints) of the system. 
%
We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system.

\begin{align*}
  & \forall G \, \texttt{Connectivity(k)} \implies  \exists
                        f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
\end{align*}

Note that the specification of this requires quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas. 
%
%To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.
We will use the same procedure as the existential condition to ensure the k to be the least one.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-11-09 papers/journal/result-table.tex
removed some spaces

--- 2018-10-11 papers/journal/result-table.tex
@@
 {\bf SNARE regulation and graph connectedness.}}
-\begin{tabular}{|c|l|l|c|}
+\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline
-\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness}\\ \thickhline
-1. & Boolean function & Boolean function & N = 2C S = 3C \\ \hline
-2. & None & Boolean function & N \& S = 3C\\ \hline
-3. & Boolean function & SNARE-SNARE inhibition & N \& S = 4C\\ \hline
-4. & None & SNARE-SNARE inhibition & No graphs found\\ \hline
-5. & Boolean function & None & No graphs found\\ \hline
-6. &  None & None & No graphs found\\ \hline
+\bf{Sr.No} & 	{\multirow{2}{*}{\textbf{Regulation}}} & 
+  {\multirow{2}{*}{\textbf{Existential}}} &
+{\multirow{2}{*}{\textbf{Universal}}}  \\ 
+%	\cline{2-3} &  \cline{Connect & Timing & \\ \hline
+%\thickhline
+
+1. & Boolean function & Boolean function & 2C \\ \hline
+2. & None & Boolean function & 3C \\ \hline
+3. & Boolean function & SNARE-SNARE inhibition & 4C \\ \hline
+4. & None & SNARE-SNARE inhibition & No graphs found \\ \hline
+5. & Boolean function & None & No graphs found \\ \hline
+6. &  None & None & No graphs found \\ \hline
 

### 2018-11-12 papers/journal/intro.tex
Updated introduction section: Biological part is still in early writing stage. Incomplete update.

@@
+\textbf{Components of the vesicle transport network}:
+The vesicle transport network is used by cells to transport molecules across compartments.
+% 
+The mechanism of vesicle transport can roughly be broken down into two steps: budding of vesicles from the source compartment and their fusion with the target compartment.
+%
+Vesicle budding involves three steps:
+\begin{enumerate}
+	\item  \textbf{Sorting of cargo molecules by cytosolic adaptor molecules}. 
+	 Cargo adaptors bind to short linear stretches of amino acids in the cargo molecules called sorting signals and thereby sequester them for packaging. 
+	 %
+	 Different adaptor proteins act at different compartments, for eg., sec23/24 is required
+	for packaging vesicles that form at the ER, the AP2 adaptor is used for packaging vesicles at the plasma membrane, etc. 
+	%
+	Adaptors are recruited to the source compartments through interactions with
+	the lipids that form the source compartment's membrane, and interactions with Arf/Sar GTPases which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
+
+	\item \textbf{Membrane deformation, which involves cytosolic coat proteins}.
+	   Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
+	   %
+	   These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
+	   %
+	   A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
+	   %
+	   Clathrin, COP2 and COP1 are the three major kinds of coat proteins
+	   in eukaryotic cells. 
+	   %
+	   The clathrin coat operates at multiple compartments, and can interact with
+	   multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}
+
+	 \item \textbf{Pinching of vesicles from the source compartment by dynamin}.
+	 The final step in vesicle formation is its piching off from the source compartment.
+	 %
+	 This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}
+\end{enumerate}
+
+Vesicle fusion involves two steps:
+\begin{enumerate}
+	\item \textbf{Recognition of the correct target compartment}. 
+	      This is a complex process involving Rab
+	      GTPases and tethering complexes:
+
+	    \begin{enumerate}[label=(\roman*)]
+	    	\item \textbf{Rab GTPases}  are small proteins which occur in two forms: the membrane associated and active
+	    	GTP bound form, and the cytosolic and inactive GDP bound forms. 
+	    	%
+	    	Different compartments of the
+	    	cell are associated with a different type of Rab protein. In their active form, Rabs recruit many
+	    	downstream proteins, including tethering complexes, fusion regulators, motor proteins, sorting
+	    	adaptors, etc, to the membrane they are associated with. 
+	    	%
+	    	The proteins that are recruited by active
+	    	Rabs are called Rab effectors.
+	    	%
+	    	Rab activity is controlled by two proteins: GEFs turn Rabs on and
+	    	GAPs turn them off. 
+	    	%
+	    	Each Rab has its own specific GEF and GAP. In some cases, GEFs and GAPs
+	    	themselves can be Rab effectors, thus generating feed-forward and feedback loops. 
+	    	%
+	    	In their cytosolic, inactive form, Rabs are complexed with GDI proteins, and it is in this form that Rabs are presented to membrane bound GEFs for activation~\cite{muller2018molecular}
+
+	    	\item \textbf{Tethering complexes} sequester vesicles to their target compartments and regulate SNARE
+	    	proteins, which enable vesicle fusion. 
+	    	%
+	    	Tethers are believed to bind to SNAREs and function as
+	    	chaperones for SNARE complex assembly which is the ultimate step in membrane fusion. 
+	    	%
+	    	There are two types of tethering complexes: multi subunit tethers and long coiled-coil tethers:
+
+	    	\begin{enumerate}[label=(\alph*)]
+	    		\item \textbf{Coiled coil} tethers are long, single subunit proteins. 
+	    		%
+	    		These tethers are believed to bind the
+	    		vesicle on one end and the target compartment on the other end, thereby bridging the two before
+	    		fusion.
+	    		%
+	    		A clear mechanism for action of these tethers is missing, but based on their interactions with
+	    		other proteins of the traffic machinery, some hypotheses as to their mechanism of action have been
+	    		put forth. 
+	    		%
+	    		Golgins, coiled coil tethers that are anchored at the Golgi by a transmembrane domain, contain a large number of binding sites for Rab GTPases. 
+	    		%
+	    		Thus, golgins might capture vesicles by
+	    		binding vesicle-associated Rab proteins. 
+	    		%
+	    		Golgins also contain domains which can sense membrane
+	    		curvature, which they could be using to recognize vesicles. 
+	    		%
+	    		They might also be interacting directly
+	    		with vesicle SNAREs~\cite{baker2016chaperoning}.
+
+	    		\item \textbf{Multi-subunit tethering complexes (MTCs)} are composed of three or more different
+	    		subunits.
+	    		%
+	    		MTCs are known to interact with vesicle coat proteins, Rab GTPases, SNAREs and SM proteins.
+	    		%
+	    		For example, the HOPS complex, which is required for homotypic (fusion of two identical
+	    		membranes) and heterotypic fusion in the endo-lysosomal system, was shown to tether membranes
+	    		through its interactions with the membrane-associated Rab GTPase Ypt7, acidic phospholipids and
+	    		SNAREs. 
+	    		%
+	    		The HOPS complex binds both individual SNAREs and SNARE complexes. It also
+	    		seems to protect assembling trans-SNARE complexes from premature disassembly. 
+	    		%
+	    		Another example is given by the Dsl1 complex, which is anchored to the ER membrane through interactions
+	    		with t-SNAREs. 
+	    		%
+	    		At the other end, the Dsl1 complex contains multiple binding sites for COPI
+	    		(vesicle coat that is present on vesicles produced by the Golgi). 
+	    		%
+	    		This structure suggests that the Dsl1
+	    		complex functions as a tether connecting COPI-coated vesicles to their target organelle, the ER~\cite{baker2016chaperoning}.
+
+	    	\end{enumerate}
+
+      \end{enumerate}
+
+	  \item \textbf{Fusion of vesicle with the target compartment} is brought about by SNARE proteins. 
+	  %
+	  SNAREs
+	  are defined by a 60- to 70-residue SNARE motif. Most SNAREs are anchored to the membrane by
+	  their C-terminal transmembrane helices. 
+	  %
+	  The formation of a productive SNARE complex requires
+	  the formation of a four-helix bundle containing four different SNARE motifs. Usually, one of these
+	  motifs is contributed by the SNARE on the vesicle membrane (v-SNAREs), and the other three
+	  motifs by SNAREs on the membrane of the tartget compartment (t-SNAREs). 
+	  %
+	  Alternatively, they
+	  can be defined by their amino acid sequences as R-, Qa-, Qb-, and Qc-SNAREs. A few SNARE
+	  proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs.
+	  %
+	  Most v-SNAREs are RSNAREs, and most t-SNAREs are Q-SNAREs~\cite{yoon2018snare}.
+
+\end{enumerate}
+
+Many SNAREs also have N-terminal domains that regulate SNARE complex assembly and/or
+interact with other parts of the vesicle fusion machinery. 
+%
+Qa-SNAREs have an amino terminal
+domain called the Habc domain, which can fold back on the SNARE domain and hold the QaSNARE
+in an inactive state. 
+%
+This inactivated state is stabilized by interactions with SM proteins~\cite{yoon2018snare}.
+
+A subset of R-SNAREs (the longin SNAREs) possess an amino-terminal domain called the longin domain. 
+%
+In addition to regulation of SNARE activity as in the case of the Qa-SNARE Habcdomains,
+these longin domains also regulate the localization of longin SNAREs through their
+interaction with adaptor proteins~\cite{daste2015structure}.
+
+Different vesicle-target compartment pairs in the cell are associated with unique SNARE
+complexes.
+%
+Membrane fusion converts the trans-SNARE complex (v- and t- SNAREs on opposite
+membranes) into a cis-SNARE complex (both v- and t- SNAREs on the same membrane).
+Disassembly of cis-SNARE complexes requires Sec17 and Sec18 (the yeast SNAP and NSF
+protein, respectively). 
+%
+This process requires energy which is released by the hydrolysis of ATP.
+
+\textbf{SNAREs are regulated by SM proteins}, which have three modes of action: SM proteins can hold
+the Qa-SNAREs in an autoinhibited state and prevent or postpone their assembly into SNARE
+complexes.
+%
+ Secondly, some SM proteins have been seen to act as a template upon which a halfzippered
+complex between the Qa- and R-SNAREs (an early SNARE complex intermediate) can
+form. 
+%
+In this mode, by choosing an R-SNARE located on the opposite membrane, SM proteins
+could be imposing a filter inhibiting the formation of futile cis-SNARE complexes and promoting
+trans-SNARE complexes.
+%
+Finally, SM proteins bind the four-helix bundles formed by assembled
+SNARE complexes.
+%
+ This mode of binding of SM proteins might protect assembled SNARE
+complexes from premature disassembly by NSF and SNAPs and/or might stimulate fusion directly~\cite{baker2016chaperoning}.
+%
+SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
+
+\textbf{Major paths in the vesicle transport network}:
+Molecules traverse the cell in a series of vesicles, and there are two major such routes of transport in all eukaryotic cells:
+\begin{enumerate}
+	\item the secretory route, which takes proteins from the ER, their site of production, to the plasma
+	membrane, from where they are secreted out of the cell.
+	\item the endocytic route, which takes proteins from the outside of the cell through the plasma
+	membrane to the endocytic compartments, where they are digested.
+\end{enumerate}
+
+Other paths are used for cross talk between the secretory and the endocytic routes.
+%
+There are also cyclic paths for recycle of proteins which are necessarily dislodged during the process of vesicle traffic back to their original compartments.
+
+\textbf{Biological Model of VTS}
+%
 A characteristic feature of eukaryotic cells is the presence of multiple internal membrane bound organelles. 

### 2018-11-12 papers/journal/problem.tex
removed some spaces
Updated introduction section: Biological part is still in early writing stage. Incomplete update

@@
 \subsection{SMT}
-
 \paragraph{Search problem}
@@
 \subsection{BMC}
-The notion of stability and connectivity varies slightly for BMC encoding.
+%The notion of stability and connectivity varies slightly for BMC encoding. 
+In this subsection, we will present the concept of stability and connectivity for BMC encoding.
 
 %
-We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
+We call a graph $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
 there exists a $m$-path in G with $n_1 = n'$ and $n_\ell = n$.
@@
 %
-We call $G$ {\em connected} if for each $n,n' \in \nodes$,
+We call a graph $G$ {\em connected} if for each $n,n' \in \nodes$,
 $n'$ there is a path from $n$ to $n'$ in G.
 %
-We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
+We call a graph $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
 VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
@@
 
-For the experimentation, we will restrict ourselves to the cycles of length one. 
+For the experimentation, we will restrict ourselves to the elementary cycles (cycles of length one). 
 %
-This restriction puts an upper limit of N on the length of each searched path. 
+This restriction puts an upper limit of N-1 on the length of each searched path. 
 %
-Creating a formula to search a path of length N for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
+Creating a formula to search a path of length N-1 for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
 %
-Even if there exist shorter paths we have to create the formula of maximum size N. 
+Even if there exist shorter paths we have to create the formula of maximum size N-1. 
 % 
-To resolve the these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
+To resolve these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
 %
@@
 $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w length of unwinding.
+$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w depth of unwinding.
 

### 2018-11-13 papers/journal/encoding.tex
Updated introduction section: Biological part is still in early writing stage. Incomplete update
Added encodings for recahabilty for BMC implementation

@@
-In this section we will present the SAT, SMT and QBF based encoding of both the search and the synthesis problem.
+\externaldocument{sat-table}
+\externaldocument{smt-table}
+
+In this section we will present the BMC, SMT and QBF based encoding of both the search and the synthesis problem.
 We will start with the SMT based encoding and later present the contrast with the BMC encoding.
@@
 
-The BMC encoding differs with presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
+The BMC encoding differs with the presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
 %
-Variables are not Boolean indexed with multiple dimensions but multidimensional arrays. 
+Variables are not Boolean indexed with multiple dimensions but arrays of bitvectors of size $\mu$. 
 %
-For clarity, we will only present the stability encoding.
-
-We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
-%
-We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
+%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
+%%
+%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
 %\begin{align*}
@@
 %\end{align*}
-
 %
-The nodes are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
+For example the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
 %
 The index of the bitvector implicitly determines the corresponding molecule we are referring to.
+
+\begin{enumerate}
+	\item Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between $i$ and $j$.
+\end{enumerate}
+
 %
@@
 %
-A node in the system with M = 4 molecules is interpreted as a tag [M1, M2, M3, M4]. 
+An edge in the system with M = 4 molecules is interpreted as a tag [M1, M2, M3, M4]. 
 %
@@
 %
-Similarly, an edge in the graph is also tagged as a bitvector of length M.   
+
+\textbf{Example 1} The variable bv\_e[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule M1 and M4 present.
+
+Similarly, a node in the graph is also tagged as a bitvector of length M.   
 %
 We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
+%
+For clarity, we will only present the stability encoding.
 
@@
 We then use this path as a witness to ensures that stability is maintained for each outgoing molecule m on every edge E.
+%
 
@@
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} e[i][j][q][m]) \limplies NOracle(m, j, i, w)
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] >> m) > 0) \limplies NOracle(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}
@@
 
-\subsection{SMT problems for different variants}
+\subsection{BMC and SMT problems for different variants}
 %\ankit{Bring model variant table here}

### 2018-11-13 papers/journal/model.tex
Added encodings for recahabilty for BMC implementation

@@
 
-\subsection{BMC and SMT}
+\textbf{Fusion condition in BMC and SMT:}
 $\pairs$ defines which molecules can fuse with which molecules.
@@
 
-\subsection{QBF and synthesis}
+\textbf{Fusion condition in QBF and synthesis:}
 %
@@
 to be on the other side of the fusion.
-
 % $\pairs(M'')$ are not active in any other node.
@@
 
-\subsection{Uniform}
+\vspace{0.2cm}
+%\subsection{Uniform}
+\noindent
 A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
@@
 %
+%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
+%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
+
 The VTS may transport a large number of molecules but the molecules that
-are relevant of the control of VTS are about 50~\cite{doWeKnowThis}.
+are \todo{SA: commented line above} relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
 %

### 2018-11-13 papers/journal/problem.tex
Added encodings for recahabilty for BMC implementation

@@
 
-\subsection{SMT}
-\paragraph{Search problem}
+\subsection{Existential condition}
+
 Based upon earlier discussion, we need to answer the following search
 question among VTSs.
+%
+Here, we will present both BMC and SMT search problem.
+
+\textbf{SMT Search problem:}
 For a given $k$, size $\nu$, and molecule number $\mu$,
@@
 
-\subsection{BMC}
-%The notion of stability and connectivity varies slightly for BMC encoding. 
-In this subsection, we will present the concept of stability and connectivity for BMC encoding.
-
+\noindent
+The notion of stability and connectivity varies slightly for BMC encoding. 
+%In this subsection, we will present the concept of stability and connectivity for BMC encoding. 
 %
@@
 %
-
 %
@@
 %	
-
 We use $m$-${path}_i^j$ to denote an $m$-path between source node i and target node is j.
@@
 This specified depth is called unwinding in the technical terms.
-%and can be specified for each path separately.
 
-\paragraph{Search problem}
-Based upon earlier discussion, we need to answer the following search
-question among VTSs.
+\textbf{BMC Search problem:}
 For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth w,
@@
 \subsection{QBF and synthesis}
+Here we will present the QBF and Synthesis search problem.
 

### 2018-11-13 papers/journal/property.tex
Added encodings for recahabilty for BMC implementation

@@
 
-\subsubsection{Checking existential conditions} 
 In our program, the rules VTS needs to follow 
@@
 %
-We use these functions to define the assertion that characterizes the existential condition to be checked. 
+We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
 %
 We will show in later sections how we encode these Boolean functions.
+
+\subsubsection{Checking existential conditions}
 

### 2018-11-14 papers/journal/qbf-table.tex
added tables for sat smt and qbf

--- 2018-10-11 papers/journal/result-table.tex
@@
-\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\def\arraystretch{1.6}
-\caption{
-{\bf SNARE regulation and graph connectedness.}}
-\begin{tabular}{|c|l|l|c|}
-\hline
-\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness}\\ \thickhline
-1. & Boolean function & Boolean function & N = 2C S = 3C \\ \hline
-2. & None & Boolean function & N \& S = 3C\\ \hline
-3. & Boolean function & SNARE-SNARE inhibition & N \& S = 4C\\ \hline
-4. & None & SNARE-SNARE inhibition & No graphs found\\ \hline
-5. & Boolean function & None & No graphs found\\ \hline
-6. &  None & None & No graphs found\\ \hline
-
-%6. & Arbitrary Boolean & Specificity matrix and every edge is distinct & N \& S = 3C\\ \hline
-
-\end{tabular}
-\label{tab:smt-grph}
-%\end{adjustwidth}
-\end{table}
-
-\begin{table}[t]
-	\centering
-	% \def\arraystretch{1.6}
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		{\multirow{2}{*}{\textbf{Variant}}}  &
-		\multicolumn{2}{c|}{\textbf{Constraints}} &
-		{\multirow{2}{*}{\textbf{Graph connectivity}}}
-		% \multicolumn{2}{c|}{\textbf{Graph connectivity}}
-		\\
-		\cline{2-3}
-		&  \textbf{Rest} & \textbf{Activity} &  % & \textbf{Sampling: Guarantee}
-	\\ \hline
-
-	A. & \multirow{5}{*}{
-		\makecell{ \ref{eq:f0}--\ref{eq:fuse2},\\
-			\ref{eq:reach1},\ref{eq:reach2},\\
-			\ref{eq:drop1}--\ref{eq:drop4}}
-	}
-	& \ref{eq:ann},\ref{eq:aen} & No graph     \\\cline{3-4}
-	B. & & \ref{eq:anb},\ref{eq:aen} & No graph     \\\cline{3-4}
-	C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected  \\\cline{3-4}
-	D. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected  \\\cline{3-4}
-	E. & & \ref{eq:ann},\ref{eq:aep} & No graph     \\\cline{3-4}
-	F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected  \\\hline
-
-	% C_es :Self edges are allowed
-	% C_ed : Every edge is distinct 
-\end{tabular}
-\caption{{\bf Activity regulation of molecules vs. graph connectivity.
-}}
-\label{tab:smt-grph}
-\end{table}
-
 \begin{sidewaysfigure}[t]

### 2018-11-15 papers/journal/encoding.tex
added QBF section and attached Synthesis encodings to it

@@
-\externaldocument{sat-table}
-\externaldocument{smt-table}
+%\externaldocument{sat-table}
+%\externaldocument{smt-table}
+%\externaldocument{qbf-table}
 
@@
 
-\subsection{Boolean satisfiability of the search problem}
+%\subsection{Boolean satisfiability of the search problem}
 
@@
 \begin{enumerate}
-	\item Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between $i$ and $j$.
+	\item Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
 \end{enumerate}
@@
 %
-Nondeterminism can be considered as an oracle that guesses a correct $m$-path for a specific m if it exists. 
+Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific m if it exists. 
 %
@@
 %
-The following constraint encodes that there is a $m$-path from node $i$ to node $j$ of maximum $w$ length.
+A naive implementation of NOracle is shown in~\ref{eq:reachbmc1}.
+%
+The constraint encodes that there is a $m$-path from node $i$ to node $j$ of maximum $w$ length.
 %there is a edge between $i^{\prime \prime}$ and
@@
 %
-The NOracle perform enumeration of $m$-${paths}_i^j$ of at most w length. 
+It performs enumeration of $m$-${paths}_i^j$ of at most w length. 
 %
@@
 Now we can encode stability using the NOracle and say if there is an $m$-edge between $i$ and $j$, there is a $m$-path from $j$ to $i$ of length max w.
+%
+We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] >> m) > 0) \limplies NOracle(m, j, i, w)
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}
@@
 \subsection{Universal condition}
+Recall that the specification for universal condition~\ref{eq:univcond} requires quantifier alternation. 
+%
+Most SAT solvers can not efficiently handle the quantifier in the formulas. 
+% 
+\todo{SA: Rewrite completely}But it is still possible to encode the universal condition~\ref{eq:univcond} as a SAT or SMT problem.
+% 
+We have implemented a SAT version with the current encoding of the same.
+%
+The basic idea is to conjunct the formula for each combination value of the quantified variable. 
+%
+This may blow up the formula size for the solver to solve.
+
+\input{qbf-table}
+%
+In the table~\ref{tab:satqbf-graph}, you can see that SAT version was not able to scale it to the desired results.
+%
+This is due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.
+
+\textbf{QBF encoding of universal condition:}
+We will describe several constraints that encode VTSs in this section.
+%
+To avoid cumbersome notation, we will not explicitly write the ranges
+of the indexing in the constraints.
+%
+$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
+%
+$m$ will range over molecules, i.e., from $1$ to $\mu$.
+%
+$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
+%
+
+The following constraints encode the basic consistency of VTSs. 
+%
+Recall that now the molecule set is divided into 3:1 Q and R pairs (or partition).
+\begin{align*}
+\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
+\land
+\bigwedge\limits_{i,q} \neg e_{i,i,q}
+\land
+% \tag{\texttt{NodeC}}\label{eq:f0}\\
+\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
+\\
+\texttt{ActivityC} =\;&
+\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
+\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
+% \tag{V2}\label{eq:f1}\\
+\\
+\texttt{PairingC} =\;&
+\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
+(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
+% \land\\ 
+%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
+% \bigwedge\limits_{m} 
+% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
+% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
+\\
+\texttt{Fusion1} =\;&
+\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
+\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
+\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
+& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
+\\
+\texttt{Fusion2} =\;&
+\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
+& \hspace{2cm} \neg 
+\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
+\land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
+\\
+\texttt{Consistancy} =\;& \texttt{EdgeC} \land
+\texttt{ActivityC} \land \texttt{PairingC} \land
+\texttt{Fusion1} \land \texttt{Fusion2} 
+\end{align*}
+\texttt{EdgeC} states that each edge has at least one molecule,
+there are no self loops, and edge labels are consistent with node labels.   
+\texttt{ActivityC} states that active molecule are present.
+\texttt{PairingC} states that all molecules are divided into two types
+using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
+and any fusing set of molecules must have three molecules involved
+from one type and one molecule from the other.
+\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
+\texttt{Consistancy} is the conjunction of all of the above.
+
+\paragraph{Activity functions}
+%
+We also need to encode that the activity of the molecules are
+controlled by activity functions.
+%
+The input VTS may include concrete activity functions for some molecules,
+and for the others the functions may be unknown and to be synthesized. 
+%
+The concrete functions can be given to us in many different ways,
+for example as a lookup table, or a concise Boolean formula.
+%
+In the following section, we will assume the appropriate encoding is
+used for the concrete functions and represent them by \texttt{NodeFun}$_m$
+and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
+%
+%We will use $\nodef_m$ and $\edgef_m$ to represent functions that
+%are unknown in a VTS.
+%
+% \begin{align}
+% \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
+% \tag{\texttt{ActiveN}}\label{eq:anb}\\
+%    \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
+%   \tag{\texttt{ActiveE}}\label{eq:aeb}
+% \end{align}
+%
+%Later we will be synthesizing the unknown activity functions and 
+%replace $\nodef_m$ and $\edgef_m$ with parameterized constraints that
+%encode a space of candidate functions.
+%\subsubsection{VTS properties}
+%For the synthesis of incomplete systems,
+%we need properties against which we synthesize the missing parts.
+%
+Next, we will discuss stability and $k$-connectedness.
+%
+
+\paragraph{Stability property}
+%
+We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
+$m$-path from $i$ to $j$ of length less than or equal to $p$.
+%
+We use $m$-reachability to encode the stability condition in VTSs.
+%
+The following constraint recursively encodes that node $j$ is
+$m$-reachable from node $i$ in less than $p$ steps.
+%
+Subsequently, we encode stability condition using the reachability variables.
+\begin{align*}
+\texttt{Paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+\\
+\texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
+\\
+\texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
+\end{align*}
+
+\paragraph{$k$-connected property}
+%
+$k$-connectedness expresses robustness against failure of few edges.
+%
+Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
+and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
+the modified VTS.
+%
+% To check whether $k$-connected is a
+% necessary condition, we remove (drop) $k-1$ edges from the graph and
+% if it disconnects the graph, and we get an assignment.
+% %
+% We have a graph that is not $k$-connected.
+%
+In the following, $\texttt{Fail}(d,k)$ encodes that only
+existing edges can be failed and exactly $k-1$ edges are failed.
+%
+$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
+%
+We use a new variable $r'_{i,j,p}$ to encode reachability from
+$i$ to $j$ in at most $p$ steps.
+%
+$\texttt{Connected}(r')$ says that all nodes are reachable from any
+other node.
+\begin{align*}
+\texttt{Fail}(d,k) = & 
+\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
+\sum_{i,j,q} d_{i,j,q} = k-1\\
+% \texttt{ReachAbove}(d,r') = &
+% \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
+\texttt{FReach}(d,r') = &\hspace{-1ex}
+\bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
+\texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
+\end{align*}
+%We will be synthesizing $k$-connected graphs.
+%
+We define $\texttt{Connected}(k)$ that says for all possible valid failures
+the graph remains reachable. 
+\begin{align*}
+\texttt{Connected}(k) = & \forall d.\;
+(\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
+\land \texttt{Connected}(r'))
+% \\
+% \texttt{Disconnected}(k) = & \exists d.\;
+%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
+%                               \land \lnot \texttt{Connected}(r'))
+\end{align*}
+Since $d$ variables in $\texttt{Connected}(k)$ are universally
+quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
+%
+Therefore, synthesis against this property will require QBF reasoning.
+%
+We may make the formula quantifier free  by considering all possible failures
+separately and introducing a vector of reachability variables for each
+failure.
+%
+However, this will blow up the size of the formula and may not be
+solvable by a SAT solver.
+%
+
+\subsection{Synthesis of VTS}
+%In this section, we will present our synthesis method for
+%the synthesis problems.
+
+\subsubsection{Encoding Incomplete VTS}
+
+In our synthesis method, we take a VTS $G =
+(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ as input.
+%
+We allow activity functions not to be specified.
+%
+We will use the same encoding for the VTS as discussed in the QBF subsection.
+%
+We construct the following constraints to encode the available information
+about $G$.
+%
+We encode both the present and the absent components in $G$.
+%
+Later, the constraints will help us encode the synthesis problems.
+%
+\begin{align*}
+\texttt{PresentE} &= \land \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land q \leq q' \land m \in M_q \}\\
+\texttt{PresentN} &= \land \{n_{i,m}| m \in \nlabel(i) \land i \in \nodes \}\\
+\texttt{PresentP} &= \land \{p_{\{m_1,m_2,m_3,m_4\}}| \{m_1,m_2,m_3,m_4\} \in \pairs \} \\
+\texttt{KnownActiveN} &= \land \{ a_{i,m} = \texttt{NodeFun}_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is defined.} \} \\
+\texttt{KnownActiveE} &= \land \{ b_{i,j,q,m} = \texttt{EdgeFun}_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
+| \edgef_m \text{ is defined.} \} \\
+\texttt{PresentCons} & = \texttt{PresentE} \land \texttt{PresentN} \land 
+\texttt{PresentP} \land \texttt{KnownActiveE} \land \\
+&  \texttt{KnownActiveN}
+\end{align*}
+We also collect the variables that are not set to true in $\texttt{PresentCons}$.
+\begin{align*}
+\texttt{AbsentELabel} &=
+\{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
+0 < q \leq q' \land m \not\in M_{q} \}\\
+\texttt{AbsentE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
+q' < q \leq \pi \}\\
+\texttt{AbsentNLabel} &= \{n_{i,m}| m \not\in \nlabel(i) \land i \in \nodes \}\\
+\texttt{AbsentP} &= \{p_{\{m_1,m_2,m_3,m_4\}}| {\{m_1,m_2,m_3,m_4\}} \not\in \pairs \} \\
+\texttt{UnknownActive} &=  \Land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is undefined.} \} \union \\
+&\quad\quad\quad  \{ b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
+| \edgef_m \text{ is undefined.} \}
+\end{align*}
+We have defined $\texttt{AbsentELabel}$, $\texttt{AbsentE}$, $\texttt{AbsentN}$, and
+$\texttt{AbsentP}$
+as sets.
+%
+They will be converted into formulas depending
+on the different usage in the synthesis problems.
+
+% Since not all the activity functions are defined some of the functions
+% appearing in $\texttt{ActiveE}$ and $\texttt{ActiveN}$ are
+% uninterpreted function symbols.
+
+\subsubsection{Encoding synthesis constraints}
+
+Now we will consider the encodings for the
+listed synthesis problems.
+%
+The presented variations represent the encodings
+supported by our tool.
+%
+Additionally, the combinations of the variation are also possible and
+our tool easily supports them.
+%
+For simplicity of the presentation, we assume that if we are
+synthesizing an aspect of VTS, then all other aspects are fully given.
+%
+Therefore, we will describe two kinds of constraints for synthesis
+problems.
+%
+One will encode the variable part in the synthesis problem and
+the other encodes the fixed parts.
+%
+Subsequently, the two constraints will be put together with 
+$\texttt{Consistancy}$ and 
+$\texttt{Property}$ to construct the constraints for synthesis.
+
+\subsubsection{Fixing VTS by adding edges}
+%
+Now we will consider the case when we add new edges to VTS to satisfy the properties.
+%
+In the following, the pseudo-Boolean formula $\texttt{AddE}$ encodes
+that at most $slimit$ new undeclared edges may be added in the VTS.
+%
+\texttt{FixedForEdge} encodes the parts of the VTS that are not allowed to change.
+\begin{align*}
+&\texttt{AddE}(slimit) = \sum~\texttt{AbsentE} \leq slimit\\
+&\texttt{FixedForEdge} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
+& \quad\quad\quad\quad \lnot \Lor \texttt{AbsentELabel} \;\union\;
+\texttt{AbsentNLabel} \;\union\;
+\texttt{AbsentP}
+\end{align*}
+We put together the constraints and obtain the following formula.
+\begin{align*}
+& \texttt{SynthE}(slimit) =
+\texttt{Consistancy}\land \texttt{Property} \land
+\texttt{FixedForEdge} \land
+\texttt{AddE}(slimit)
+% \tag{SynthE}\label{eq:addedge1}
+\end{align*}
+Similar to what we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
+$\texttt{Property}$\; encodes the goal, and
+the rest two are defined just above.
+%
+A satisfying model of $\texttt{SynthE}$ will make 
+some of the edges in $\texttt{AbsentE}$ true such that~$\texttt{Property}$ is satisfied.
+%
+We limit the addition of the edges, since we look for a fix that require minimum number
+of changes in the given VTS.
+%
+We start with $slimit = 1$ and grow one by one until $\texttt{SynthE}(slimit)$
+becomes satisfiable.
+
+In the later synthesis problems, we will construct a similar QBF
+formula with same first two parts and the last two are due the
+requirements of the synthesis problem.
+
+\paragraph{\bf Fixing VTS by adding molecules to the labels:}
+The system may also be fixed only by modifying labels on the edges or the nodes instead
+of adding edges.
+%
+Here let us consider only adding molecules to the labels of edges.
+%
+In the following, the formula encodes that only $slimit$ edge labels may be added.
+\begin{align*}
+&\texttt{AddLabelEdge}(slimit) = 
+\sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
+& \texttt{FixedForLabel} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
+& \quad \quad \lnot \Lor \texttt{AbsentE} \;\union\;
+\texttt{AbsentNLabel} \;\union\;
+\texttt{AbsentP}\\
+&\texttt{SynthLabel}(slimit) = \\
+& \quad\quad
+(  \texttt{Consistancy}\land \texttt{Property} \land
+\texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
+\end{align*} 
+Similar to the previous encoding, we solve the
+satisfiability of the above formula to obtain additional molecules
+that may be added to the edge labels to satisfy the properties.
+
+\subsubsection{Fixing VTS by learning activity functions:}
+
+Now we consider a scenario where some of the activity functions for
+some of the molecules are missing.
+%
+The activity functions are $\mu$-input Boolean functions.
+%
+First, we choose a class of formulas for the candidate functions.
+%
+We encode the candidates in a formula with parameters.
+%
+By assigning different values for the parameters, a solver may select
+different candidates for the activity functions.
+%
+We will illustrate only one class of formulas.
+%
+However, we support other classes of formulas, for example, $k$-CNF.
+
+In the following, the formula \texttt{NNFTemplate} encodes a set of
+negation normal form functions that take $y_1,..,y_\mu$ as input and
+contain $\lambda$ literals.
+%
+We use $\texttt{Gate}$ to encode a gate that takes a parameter integer
+$x$ to encode various gates.
+%
+We use $\texttt{Leaf} $ to encode the literal at some position.
+%
+Both are stitched to define \texttt{NNFTemplate}.
+%
+To encode the set of NNF formulas with $\lambda$ literals, it has
+finite-range integer variables
+$z_1,..,z_{2\lambda}$ as parameters.
+
+% \paragraph{Encoding low depth cnf circuits}
+% \paragraph{Encoding boolean gates}
+
+\begin{align*}
+&\texttt{Gate}( x, w_1, w_2 ) = ( x  = 1 \limplies w_1  \land w_2 ) \land  
+( x = 2  \limplies w_1  \lor w_2 ) \\
+&\texttt{Leaf}( x, [y_1,..,y_\mu] ) =
+\Land\limits_{l=1}^{\mu} ( x = 2l-1  \limplies y_{l}) \land ( x = 2l  \limplies \lnot y_{l})\\
+&\texttt{NNFTemplate}([z_1,..,z_{2\lambda}],[y_1,..,y_\mu] ) = \\
+&\exists w_1,..,w_{2\lambda}.\;w_1 \land \Land_{l=1}^{\lambda} w_{\lambda+l} = \texttt{Leaf}( z_{\lambda+l}, [y_1,..,y_\mu] ) \land
+w_{l} = \texttt{Gate}( z_l, w_{2l},w_{2l+1})
+\end{align*}
+
+Using the template we define the constraints $\texttt{FindFunctions}(z,\lambda)$
+that encodes the candidate functions that satisfy the activity requirements,
+where $z$ is the vectors of parameters for encoding parameters
+for each molecule,
+and $\lambda$ limits the size of the candidate functions. 
+%
+We fix the all other aspects of the VTS to be fixed via constraints
+$\texttt{FixedForFunctions}$.
+%
+\begin{align*}
+&\texttt{FindFunctions}(z,\lambda) =\\
+&\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
+\texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) \\
+& \hspace{8cm}|
+\nodef_m \text{ is undefined}\} \\
+&\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
+\texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) \\
+& \hspace{8cm} | \edgef_m \text{ is undefined}
+\}\\
+& \texttt{FixedForFunctions} = \texttt{PresentCons} \land\\
+& \quad \quad
+\lnot \Lor \texttt{AbsentE} \;\union\; \texttt{AbsentELabel} \;\union\;
+\texttt{AbsentNLabel} \;\union\;
+\texttt{AbsentP}\\
+&\texttt{SynthFunction}(z,\lambda) = \\
+& \quad
+(  \texttt{Consistancy}\land \texttt{Property} \land
+\texttt{FixedForFunctions} \land \texttt{FindFunctions}(slimit) )
+\end{align*}
+We construct $\texttt{SynthFunction}(z,\lambda)$ similar to the earlier
+variations.
+%
+By reading of the values of $z$ in a satisfying model of the formula,
+we learn the synthesized function.
+
+\subsubsection{Fixing VTS by both adding/deleting parts:}
+%
+Now we will consider repairing of VTS by allowing not only addition but also
+deletion of the molecules, edges, functions, or pairing matrix.
+%
+We have encoded the repairing in our tool by introducing flip bits
+for each variable that is modifiable in the VTS.
+%
+We illustrate the repairing on one class of variables and rest can be
+easily extended.
+%
+Let us consider repairing of node labels.
+%
+For each bit $n_{i,m}$, we create a bit $flip_{i,m}$.
+%
+We add constraints that take xor of VTS assigned values for  $n_{i,m}$
+and $flip_{i,m}$.
+%
+We also limit the number of $flip_{i,m}$ that can be true, therefore
+limiting the number of flips.
+%
+The above constraints are encoded in $\texttt{FlipN}(slimit)$.
+\begin{align*}
+&\texttt{FlipN}(slimit,flip) = \Land \{n_{i,m}\lxor flip_{i,m}| m \in \nlabel(i) \land i \in \nodes \} \land \\
+& \quad \quad \quad
+\Land \{ \lnot n_{i,m}\lxor flip_{i,m}| m \not \in \nlabel(i) \land i \in \nodes \} \land  \sum\limits_{i,m} flip_{i,m} \leq slimit
+\end{align*}
+%
+Similar to the earlier variations, we construct
+$\texttt{SynthRepairNode}(slimit)$ for the repair.
+%
+In that, $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
+\begin{align*}
+% \\ 
+& \texttt{FixedForNodeRepair} =  \texttt{PresentE} \land  
+\texttt{PresentP} \land \texttt{KnownActiveE} 
+\land \\
+& \quad \texttt{UnknownActive} \land \texttt{KnownActiveN} \land \lnot 
+\Lor \texttt{AbsentE} \;\union\; \texttt{AbsentNLabel} \;\union\;
+\texttt{AbsentP}\\
+&\texttt{SynthRepairNode}(slimit,flip) = \\
+& \quad\quad
+(  \texttt{Consistancy}\land \texttt{Property} \land
+\texttt{FixedForNodeRepair} \land \texttt{FlipN}(slimit,flip) )
+\end{align*}
+A satisfying model of $\texttt{SynthRepairNode}(slimit,flip)$ will assign some
+$flip$ bits to true.
+We will learn from the assignments the needed modifications in the VTS.
 

### 2018-11-15 papers/journal/problem.tex
added QBF section and attached Synthesis encodings to it

@@
 
+ \todo{A dummy template} \textbf{QBF search problem:}
+For a given $k$, size $\nu$, and molecule number $\mu$,
+we are searching for well-structured, stable, and well-fused VTS
+$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
+$|\nodes| = \nu$, $|\mols| = \mu$,and
+$G$ is not $k$-connected.
+
+%
+%In this section, we will present a list of synthesis problems that may
+%arise from the partially available information about a VTS and our synthesis method
+%for the problems.
+
+%\subsection{Problem Statements}
+\textbf{Synthesis problem statement:}
+We will assume that we are given a VTS, whose all components
+are not specified.
+%
+Our objective is to find the missing parts.
+%
+The missing parts can be in any of the components of VTS. 
+%
+For example, some undiscovered edges or nodes, or insufficient
+knowledge about the presence of molecules in some part of the VTS.
+%
+To cover most of the likely variations of this missing information,
+we have encoded the following variants of VTS synthesis problem.
+
+\begin{enumerate}
+	\item Fixing VTS by adding edges 
+	\item Fixing VTS by adding molecules to the labels
+	\item Fixing VTS by learning activity functions
+	% \begin{enumerate}
+	%   \item kcnf: low depth circuit.
+	%   \item Boolean gates: And, Or.
+	%   \item Boolean gates with linear combination.  
+	% \end{enumerate}        
+	% - Function dependence with var occurring once.
+	\item  Fixing VTS by both adding/deleting parts
+\end{enumerate}
+
+\subsubsection{Encoding synthesis property}
+
+We will do synthesis against the following property that says the VTS
+is stable and 3-connected.
+%
+% The property is designed to balance the search space such that the synthesis procedure does not
+% succeed with simply adding too many edges. 
+%
+\begin{align*}
+\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
+%\land \texttt{DisConnected}(4)
+\end{align*}
+The property was proposed in~\cite{shukla2017discovering}.
+%
+However, the biological relevance of the property is debatable and open for change.
+%
+Our tool is easily modifiable to support any other property that may be deemed 
+interesting by the biologists.
+
 %%% Local Variables:

### 2018-11-15 papers/journal/qbf-table.tex
added QBF section and attached Synthesis encodings to it

@@
-\begin{sidewaysfigure}[t]
+\begin{table}[t]
 	\centering
-	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
-		% \begin{table}[t]
-		%   \centering
-		%   \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
-		{\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-		{\multirow{2}{*} \textbf{Table a}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
-		\cline{2-11}
-		{} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
-		\hline
+	    \def\arraystretch{1.1}
+%	\caption{{\bf SAT and QBF implementation comparison.}}
+%	\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
+%		max width=\textwidth}{
+		\begin{tabular}[t]{|c|c|c|c|c|c|}\hline
 
-		plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\infty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & -1 E, -1 AE, -1 AN. +1 E, +1 N. \\\hline
-		plos2-dia[4C] & 0.266 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
-		sub-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline
-		node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE.\\\hline
-		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-		yeast-graph[3C]   & 95.016    & 2 E  &   timeout  & N/A   & 1571.42  & 2 E  & 530.210   & 2 E & 72.316  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
+			{\multirow{2}{*} {Sr.No}}  & \multicolumn{2}{c|}{Regulation} & \multicolumn{3}{c|}{Universal condition}
 
-		mammal-graph[3C]  &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A    &  timeout     & N/A\\\hline
-		%    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
+		%	\\\cline{2-7}
+
+%			{} & \multicolumn{2}{c|}{\textbf{2-connected} } & \multicolumn{2}{c|}{\textbf{3-connected} } & \multicolumn{2}{c|}{\textbf{2-connected}}  &  \multicolumn{2}{c|}{\textbf{4-connected}}
+
+			%{} & \multicolumn{2}{c|}{2-connected} & \multicolumn{2}{c|}{3-connected} & \multicolumn{2}{c|}{2-connected}  &  \multicolumn{2}{c|}{4-connected}
+
+			\\\cline{2-6}
+			{} & {Node} & {Edge} & {Connectivity} & {SAT-time} & {QBF-time}
+
+			\\\hline
+			1. & Bf & Bf & 3C & 2.12 & 1.89  \\\hline
+			2. & None & Bf  & 3C & 7.12 & 4.89  \\\hline
+			3. & Bf & SNARE inhib & 4C  & M/O & 7.66 \\\hline
+			4. & None & SNARE inhib  & No graph & M/O & 48.35 \\\hline
+			5. & Bf & None  & No graphs & M/O & 890.84 \\\hline
+			6. &  None & None  & No graphs & M/O & M/O \\\hline
+
 	\end{tabular}
-	% \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
-	% Time is reported in seconds.}
-	% \label{tab:qf-graph}
-	% \end{table}
-	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
-		{\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
-		{\multirow{2}{*} \textbf{Table b}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
-		\cline{2-11}
-		{} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
-		\hline
-
-		plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PE, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
-		plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
-		sub-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-		node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-		yeast-graph & 40.225  & 2 E  &   timeout  & N/A   & 1393.84  & 2 E  & 468.161   & 2 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
-		mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
-	\end{tabular}
-	\caption{Run-times for synthesis queries.
-\#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS.
-Time is reported in seconds.
-(a) The solver used is DepQBF (b) The solver used is Z3.
-The sub-mammal is a subgraph of the complete mammal-graph.
-In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules.
-In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge.
-The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}
-
-	% \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
-	% Time is reported in seconds.}
-	\label{tab:qbf-graph}
-\end{sidewaysfigure}
+%}
+	\caption{ SAT and QBF implementation comparison (in secs.)}
+	\label{tab:satqbf-graph}
+\end{table}

### 2018-11-22 papers/journal/encoding.tex
Improvements in the reachability section edited slightly

@@
 \subsection{The key improvement}
-The key improvement in our work over the earlier tool is the
-encoding of reachability, which was done using enumeration of paths.
+The key improvement of SMT tool over the BMC is the
+encoding of reachability, which was done using an enumeration of paths. 
 %
-In the current work, we have encoded reachability in two different
+In SMT tool, reachability is encoded in two different
 ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
@@
 %
-Therefore, synthesis against this property will require QBF reasoning.
-%
-We may make the formula quantifier free  by considering all possible failures
-separately and introducing a vector of reachability variables for each
-failure.
-%
-However, this will blow up the size of the formula and may not be
-solvable by a SAT solver.
+%Therefore, synthesis against this property will require QBF reasoning.
+%%
+%We may make the formula quantifier free  by considering all possible failures
+%separately and introducing a vector of reachability variables for each
+%failure.
+%%
+%However, this will blow up the size of the formula and may not be
+%solvable by a SAT solver.
 %

### 2018-12-23 papers/journal/experiments.tex
Added encodings for recahabilty for BMC implementation
added QBF section and attached Synthesis encodings to it
restructure introduction and started experiments section. Added references to the bio part of the intro section.

--- 2018-10-11 papers/journal/experiments.tex
@@
-We have developed three different tools (satVTS, smtVTS, synthVTS) for implementation of proposed encodings.
-All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.
+%\externaldocument{sat-table}
 
-\input{result-table}
+%We have developed four different tools (\sattool, \smttool, \qbftool, \ourtool) for implementation of proposed encodings.
+%
+We have developed the {\vtstool} tool to conjecture the properties of the VTS. 
+%
+The toolchain is divided into three different blocks. 
+%
+Checking existential condition, checking the universal condition and performing synthesis on the incomplete VTS. 
+%
+The existential condition is subdivided into two sub-block, using bounded model checking and using constraint solving. 
+%
+We will refer to existential subblocks as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
 
-\subsection{SATVTS (Bounded model checker based tool)} 
-The first tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
+\subsection{Implementation}
+{\sattool} is based on the architecture of a Bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
+%
+{\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. 
+%
+{\qbftool} is based on the QBF encoding of the universal condition and uses {\depqbf} solver to solve the generated QBF. 
+%
+The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS.
+%
+All the experiments were done on a machine with  Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM with 30 min (1800 sec) timeout.
+
+%\input{sat-table}
+
+%\input{tab:satqbf-grabh}
+%\ExecuteMetaData[result-table.tex]{tab:satqbf-grabh}
+
+\textbf{{\sattool} (Bounded model checker based tool)}:
+The {\sattool} tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
 %
@@
 
-\subsection{SMTVTS/pyVTS (SMT based tool)}
-	We have implemented the encodings for each variants using the python interface of Z3 in a tool (MAA). 
+\textbf{{\smttool} (SMT based tool)}:
+	We have implemented the encodings for each variants using the python interface of Z3 in a tool {\smttool}. 
 %
@@
 
-In Table~\ref{tab:qf-grabh}, we present the running times for the sear
+\input{smt-table}
+
+In Table~\ref{tab:smt-grph}, we present the running times for the sear
 ch of
@@
 
-\subsection{SynthVTS (QBF based synthesis tool)} 
+\textbf{{\qbftool} (QBF based synthesis tool):}
+
+\input{synth-table}
 We have implemented the encodings in a tool

### 2018-12-23 papers/journal/intro.tex
removed first subsection of intro
restructure introduction and started experiments section. Added references to the bio part of the intro section.

@@
+%\textbf{Components of the vesicle transport network}:
+A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bound organelles. 
+These organelles exchange molecules amongst themselves in small membrane-bound packets called vesicles. 
+%
+The recognition of cargo molecules to be loaded onto these vesicles and the recognition of the correct target organelles for each vesicle is performed by an intricate network of molecules called the vesicle transport system~\cite{alberts2002molecular}.
+%
+We call the set of internal organelles, together with the molecular routes that connect them through vesicle exchange, the vesicle transport network. 
+%
+Vesicle traffic underpins nearly every aspect of eukaryotic cellular physiology, including
+human cellular physiology.
+%
+Understanding how this system function is, therefore,
+one of the central challenges of cell biology.
+
+\vspace{0.5cm}
+
 \textbf{Components of the vesicle transport network}:
@@
 \begin{enumerate}
-	\item the secretory route, which takes proteins from the ER, their site of production, to the plasma
-	membrane, from where they are secreted out of the cell.
-	\item the endocytic route, which takes proteins from the outside of the cell through the plasma
-	membrane to the endocytic compartments, where they are digested.
+	\item The secretory route takes proteins from the ER, their site of production, to the plasma membrane, from where they are secreted out of the cell.
+Cargo proteins leave the ER in COP2 coated vesicles which fuse with the Golgi apparatus.
+The golgi apparatus is where proteins get modified, for example by the addition of carbohydrate side-chains.
+Subsequently, proteins destined for secretion are packaged into clathrin coated vesicles which fuse with the plasma membrane, thus releasing their contents to the outside of the cell\cite{alberts2002molecular}.
+	\item the endocytic routetakes proteins from the outside of the cell through the plasma membrane to the endocytic compartments, where they are digested.
+Cargo from the outside of the cell is taken in in the form of clathrin coated vesicles which form at the plasma membrane.
+These vesicles fuse amongst themselves in a process called homotypic fusion to generate the early endosomal compartments.
+Early endosomes undergo changes in their composition due to ongoing vesicle traffic and maturee into late endosomes.
+This maturation is concomitant with a switch the Rab protein they are associated with; the Rab5 associated early endosomes mature into Rab7 associated late endosomes\cite{rink2005rab}.
+Late endosomes then fuse with lysosomes, where all its contents get digested\cite{pryor2009delivery}.
 \end{enumerate}
 
+\textbf{Existential and universal condition:}
 Other paths are used for cross talk between the secretory and the endocytic routes.
+For example, vesicles are sent from the TGN (Trans-Golgi network) to the early and the late endosomes to transport enzymes, and vesicles are sent back from the endocytic compartments to the TGN to recycle sorting receptors\cite{progida2016bidirectional}.
+Also recently, evidence for unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi.
+The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.
 %
-There are also cyclic paths for recycle of proteins which are necessarily dislodged during the process of vesicle traffic back to their original compartments.
 
-\textbf{Biological Model of VTS}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+			\hline
+			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
+			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
+			\hline
+		\end{tabular}
+		\label{tab:threec}
+		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
+	\end{center}	
+\end{table}
+
+\textbf{Difficulty of the problem:}
+The analysis of vesicle traffic systems is a difficult problem
+because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
 %
-A characteristic feature of eukaryotic cells is the presence of multiple internal membrane bound organelles. 
+For example, we might want to check some conjecture of interest for all 3-connected graphs and
+all possible variations of SNARE regulation rules. 
 %
-These organelles exchange molecules amongst themselves in small membrane bound packets called vesicles. 
-%
-The recognition of cargo molecules to be loaded onto these vesicles and the recognition of the correct target organelles for each vesicle is performed by an intricate network of molecules called the vesicle transport system [].
-%
-We call the set of internal organelles, together with the molecular routes that connect them through vesicle exchange, the vesicle transport network. 
-%
-Although vesicle mediated traffic was discovered decades ago [17], the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year [1, 3].
+The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
 
-Completing the vesicle traffic network is a difficult task for many reasons: (1) the core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms [6, 12, 14], and even in different cell types within an organism can be different [10, 11], (2) although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different [15, 16], (3) behaviour of traffic molecules in vitro is different from their behaviour inside cells [9], (4) molecules can have redundant routes within the cell [7,8], and (5) it can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules [2, 13].
+\textbf{Synthesis of VTS:}
+Although vesicle-mediated traffic was discovered decades ago~\cite{wells2005discovery}, the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
+
+Completing the vesicle traffic network is a difficult task for many reasons: (1) the core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different \cite{stoops2014trafficking,zhou2015arp2}, (2) although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different \cite{davletov2007regulation,di2010calcium}, (3) behaviour of traffic molecules in vitro is different from their behaviour inside cells \cite{furukawa2014multiple}, (4) molecules can have redundant routes within the cell \cite{shimizu2014compensatory,nakatsukasa2014nutrient}, and (5) it can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
 
@@
 Many diseases are caused by the malfunction of the vesicle traffic network.
-Knowledge of the complete network would be helpful in identifying the root causes.[4,5].
-At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic [14].
+Knowledge of the complete network would be helpful in identifying the root causes\cite{bexiga2013human,gissen2007cargos}.
+At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
 
 In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs and output various completed versions which can then be tested experimentally.
+%
+
+%Previous analyses of VTS have mostly been based on sampling approach~\cite{mani2016wine, mani2016stacking}. 
+%%
+%In these analyses, vesicle traffic is
+%modeled as a dynamical system. 
+%%
+%The traffic rule specifies how the system transitions from one
+%time point to the next. 
+%%
+%Given a traffic rule and an initial condition, the system is evolved over time until a steady state is reached. By studying a large sample of randomly generated traffic
+%rules, such analyses can make statistical claims about vesicle traffic.
+%%
+%Hence making precise general prediction about the properties of vesicle traffic networks over all possible traffic rules, not just for a sampled subset is not possible.
+%%
+%SAT and SMT solvers are a perfect fit for this situation, solving combinatorial problems with their exhaustive nature of searching. 
+%%
+%These tools check a specified logical property
+%on every possible state of a model constructed using variables ranging over Boolean or any
+%finite discrete type.
 

### 2018-12-27 papers/journal/encoding.tex
Improvements in the reachability section edited slightly
intro addition

@@
 The key improvement of SMT tool over the BMC is the
-encoding of reachability, which was done using an enumeration of paths. 
+encoding of reachability.
+% which was done using an enumeration of paths. 
 %
@@
 
+\input{variation-table}
+
 \subsection{BMC and SMT problems for different variants}
@@
 %
-In the table~\ref{tab:grph}, we present the constraints involved in each version.
+
+In the table~\ref{tab:var-grph}, we present the constraints involved in each version.
 %
@@
 
-\input{qbf-table}
+\input{satqbf-table}
 %
@@
 %
-This is due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.
+This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.
 

### 2018-12-27 papers/journal/experiments.tex
intro addition

@@
 %
-We have developed the {\vtstool} tool to conjecture the properties of the VTS. 
+We have developed the {\vtstool} tool to conjecture the properties of the VTS (explained in Section 6). 
 %
-The toolchain is divided into three different blocks. 
 %
-Checking existential condition, checking the universal condition and performing synthesis on the incomplete VTS. 
+The {\vtstool} tool includes about 10,000 lines of code.
+%
+The tool is divided into three different blocks,
+%
+checking existential condition, checking the universal condition and performing synthesis on the incomplete VTS. 
 %
@@
 We will refer to existential subblocks as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
+%
 
@@
 %
-The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS.
+The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS using {\qbftool}.
 %
@@
 %
+
 In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes.
@@
 %		
-It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model ( a satisfying assignment that respects the constraints). 
+It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that respects the constraints). 
 %
@@
 %
-To illustrate usability of our tool in the last column of the table 1, we present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10. 
+
+\textbf{{\qbftool} (QBF based universal condition):}
+{\qbftool} is developed in C++ and uses~\zthree~\cite{z3} infrastructure and implement the encodings of the VTS in QBF form (presented in section 6.5). 
+%
+Since some of the formulas involve alternation of quantifiers over
+Boolean variables Z3 is not a suitable choice for those examples.
+%
+We translate the formulas created by Z3 tool into a standard
+QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
+%
+We use~\depqbf~\cite{lonsing2010depqbf} for solving the QBF formulas.
+
+\textbf{{\ourtool} (QBF based synthesis tool):}
+
+\input{synth-table}
+We have implemented the synthesis  encodings in a tool
+called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
+%
+The tool takes a partially defined VTS as input in a custom designed
+input language.
+%
+The input is then converted to the constraints over VTS using the {\qbftool} interface. 
+%
+The tool can not only synthesize the above-discussed queries, but also their
+combinations.
+%
+For example, our tool can modify labels of nodes or edges while
+learning activity functions.
+
+\subsection{Results}
+
+To illustrate usability of our tool in the last column of the Table~\ref{tab:smt-grph}, we present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10.
 %
@@
 %
-Similarly, the results for the other cases are presented in the table.
+Similarly, the results for other cases are presented in the table.
 
@@
 
-In Table~\ref{tab:smt-grph}, we present the running times for the sear
-ch of
+In Table~\ref{tab:smt-grph}, we present the running times for the search of
 VTSs of sizes 2 to 10 that satisfy the variants.
-and compare with our old encoding
-({Old-e}) from~\cite{shukla}.
+and compare with the {\sattool}.
 %
@@
 
-\textbf{{\qbftool} (QBF based synthesis tool):}
+\input{qbf-table}
+%\textbf{Universal Condition:}
+Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
 
-\input{synth-table}
-We have implemented the encodings in a tool
-called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
-%
-The tool takes a partially defined VTS as input in a custom designed
-input language.
-%
-The input is then converted to the constraints over VTS. 
-%
-The tool can not only synthesize the above-discussed queries, but also their
-combinations.
-%
-For example, our tool can modify labels of nodes or edges while
-learning activity functions.
-%
-Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
-processing formulas. 
-%
-Since some of the formulas involve alternation of quantifiers over
-Boolean variables Z3 is not a suitable choice for those examples.
-%
-We translate the formulas created by Z3 tool into a standard
-QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
-%
-We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
-%
-Our tool includes about 7000 lines of code.
+%\textbf{Synthesis}:
 
@@
 %
-The results are presented in table~\ref{tab:qf-graph} for both the solvers
+The results are presented in Fig~\ref{tab:synth-graph} for both the solvers
 \depqbf and \zthree.

### 2018-12-27 papers/journal/intro.tex
intro addition

@@
 %\textbf{Components of the vesicle transport network}:
-A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bound organelles. 
-These organelles exchange molecules amongst themselves in small membrane-bound packets called vesicles. 
+A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bound organelles called compartments.
 % 
-The recognition of cargo molecules to be loaded onto these vesicles and the recognition of the correct target organelles for each vesicle is performed by an intricate network of molecules called the vesicle transport system~\cite{alberts2002molecular}.
+These compartments exchange molecules amongst themselves in small membrane-bound packets called vesicles. 
 %
-We call the set of internal organelles, together with the molecular routes that connect them through vesicle exchange, the vesicle transport network. 
+The recognition of cargo molecules to be loaded onto these vesicles and the recognition of the correct target compartments for each vesicle is performed by an intricate network of molecules called the vesicle transport system~\cite{alberts2002molecular}.
+%
+We call the set of internal compartments, together with the molecular routes that connect them through vesicle exchange, the vesicle transport network. 
 %
@@
 one of the central challenges of cell biology.
+%
+The high complexity of the problems~\cite{mani2016wine, mani2016stacking} in VTS restricts the use of traditional methods like simulation and statistical reasoning. 
+%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
+The requirement of precise analysis makes formal methods ideal candidate in this case.
 
-\vspace{0.5cm}
-
-\textbf{Components of the vesicle transport network}:
+First, we will give an overview of the VTS mechanism and then will sketch out a few interesting problems that are key to the understanding of the VTS.
+%
+%\textbf{Components of the vesicle transport network}:
 The vesicle transport network is used by cells to transport molecules across compartments.

### 2018-12-27 papers/journal/synth-table.tex
intro addition

--- 2018-10-11 papers/journal/result-table.tex
@@
 	% Time is reported in seconds.}
-	\label{tab:qbf-graph}
+	\label{tab:synth-graph}
 \end{sidewaysfigure}

### 2018-12-28 papers/journal/experiments.tex
Imroved introduction section and Experiments section

@@
 \textbf{{\sattool} (Bounded model checker based tool)}:
-The {\sattool} tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
+	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
 %
-CBMC is a Bounded Model Checker for C and C++ programs. 
+%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
 %
-Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
+The tool verify property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
 %
 The depth of model is specified by the user and can be  incrementally increased to a desired value.
-
+%
 The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
@@
 %	
-
+\todo{SA: CBMC Diagram}	
 In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes.
@@
 %		
-Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, CBMC verifies the properties by executing the following steps:
+Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
 	\begin{itemize}
@@
 depth iff the Boolean formula is valid.
-	\item Check (using a SAT solver) validity of the verification condition. CBMC reports successful verification if the formula is found to be valid. If not, then CBMC produces a counterexample,
+	\item Check (using a SAT solver) validity of the verification condition.
+{\sattool} reports successful verification if the formula is found to be valid.
+If not, then {\sattool} produces a counterexample,
 an assignment to the variables of the model, that is a witness to the violation of the property.
 	\end{itemize}
+For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.
 
-CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification.
+%CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification.
 Besides using MiniSat as a default SAT solver for our model, we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}.
-%		
-MiniSat performed satisfactorily in comparison to other SAT solvers.
+%		MiniSat performed satisfactorily in comparison to other SAT solvers.
 
 \textbf{{\smttool} (SMT based tool)}:
-	We have implemented the encodings for each variants using the python interface of Z3 in a tool {\smttool}. 
+	We have implemented the encodings for each variants (presented in section 6.1) using the python interface of Z3 in a tool {\smttool}. 
 %
-Our tool allows the user to choose a model and the size
+The tool allows the user to choose a model and the size
 of the network besides other parameters like connectivity and number of parallel edges. 
@@
 This tool also translates the satisfying model found by Z3 into
-a VTS and presents a visual output to the user in form of annotated graph. 
+a VTS and represent a visual output to the user in form of coloured annotated graph. 
 %
-We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
+%We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
 %
@@
 We translate the formulas created by Z3 tool into a standard
-QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
+QDIMACS~\cite{qdimacs} format and use it as an input for QBF solvers. 
 %
-We use~\depqbf~\cite{lonsing2010depqbf} for solving the QBF formulas.
+We have used~\depqbf~\cite{lonsing2010depqbf} for solving the QBF formulas.
 
@@
 \input{synth-table}
-We have implemented the synthesis  encodings in a tool
+We have implemented the synthesis encodings (presented in section 6.6) in a tool
 called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
@@
 %
-The tool can not only synthesize the above-discussed queries, but also their
+The tool can not only synthesize the discussed queries, but also their
 combinations.
@@
 \subsection{Results}
+The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
 
-To illustrate usability of our tool in the last column of the Table~\ref{tab:smt-grph}, we present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10.
-%
-We found no graph for the variant A with constraints Ann and Aen. 
-%
-Replacing constraint on the node of Ann with Anb (variant B)
-does not affect the outcome. 
-%
-If we allow every present molecule to stay active
-(Ann) but constraint the edge by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. 
-%
-Similarly, the results for other cases are presented in the table.
+%To illustrate usability of our tool in the last column of the Table~\ref{tab:smt-grph}, we present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10.
+%%
+%We found no graph for the variant A with constraints Ann and Aen. 
+%%
+%Replacing constraint on the node of Ann with Anb (variant B)
+%does not affect the outcome. 
+%%
+%If we allow every present molecule to stay active
+%(Ann) but constraint the edge by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. 
+%%
+%Similarly, the results for other cases are presented in the table.
 
@@
 In Table~\ref{tab:smt-grph}, we present the running times for the search of
-VTSs of sizes 2 to 10 that satisfy the variants.
-and compare with the {\sattool}.
+VTSs for {\smttool} of sizes 2 to 10 that satisfy the variants and compare with the {\sattool}.
 %
 For the comparison between both encodings we have fixed the total
-number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and
-$|M| = 2|N| + 1$ for $|N| = 2$.
+number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and $|M| = 2|N| + 1$ for $|N| = 2$.
 %
@@
 
-We have compared our performance with the performance of our earlier
-CBMC based implementation (old-encoding).
+%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
 %

### 2018-12-28 papers/journal/intro.tex
Imroved introduction section and Experiments section

@@
 First, we will give an overview of the VTS mechanism and then will sketch out a few interesting problems that are key to the understanding of the VTS.
+
+\todo{SA:One para of BIO BACKGROUND related to VTS. Why they are Important history etc.}
 %
@@
 % 
-The mechanism of vesicle transport can roughly be broken down into two steps: budding of vesicles from the source compartment and their fusion with the target compartment.
+The mechanism of vesicle transport can roughly be broken down into two big steps:
+% budding of vesicles from the source compartment and their fusion with the target compartment.
 %
-Vesicle budding involves three steps:
-\begin{enumerate}
-	\item  \textbf{Sorting of cargo molecules by cytosolic adaptor molecules}. 
+the process of formation of a vesicle by budding from the membrane called as vesicle budding and the fusion of these transport vesicle with its target compartment called as vesicle fusion.
+
+\todo{SA:Need a Diagram}Vesicle budding process involves series of steps, sorting and packaging of the molecules, membrane deformation and budding out from the compartment.
+%
+First the sorting of cargo molecules takes place by cytosolic adaptor molecules. 
+%
 Cargo adaptors bind to short linear stretches of amino acids in the cargo molecules called sorting signals and thereby sequester them for packaging. 
 %
-	Different adaptor proteins act at different compartments, for eg., sec23/24 is required
-	for packaging vesicles that form at the ER, the AP2 adaptor is used for packaging vesicles at the plasma membrane, etc. 
+Then the different adaptor proteins act at different compartments, for eg., sec23/24 is required for packaging vesicles that form at the ER, the AP2 adaptor is used for packaging vesicles at the plasma membrane, etc.
 %
-	Adaptors are recruited to the source compartments through interactions with
-	the lipids that form the source compartment's membrane, and interactions with Arf/Sar GTPases which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
+Thereafter, adaptors are recruited to the source compartments through interactions with the lipids that form the source compartment's membrane, and interactions with Arf/Sar GTPases which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
 
-	\item \textbf{Membrane deformation, which involves cytosolic coat proteins}.
+The next step is membrane deformation, which involves cytosolic coat proteins.
 Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
@@
 %
-	Clathrin, COP2 and COP1 are the three major kinds of coat proteins
-	in eukaryotic cells. 
+Clathrin, COP2 and COP1 are the three major kinds of coat proteins in eukaryotic cells. 
 %
-	The clathrin coat operates at multiple compartments, and can interact with
-	multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}
+The clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
 
-	\item \textbf{Pinching of vesicles from the source compartment by dynamin}.
-	The final step in vesicle formation is its piching off from the source compartment.
+The final step is budding of the vesicles from the source compartment.
+% by dynamin.
+%	The final step in vesicle formation is its pinching off from the source compartment.
 	%
-	This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}
-\end{enumerate}
+This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}.
+%
+The transport vesicle is now ready for the transportation.
 
-Vesicle fusion involves two steps:
-\begin{enumerate}
-	\item \textbf{Recognition of the correct target compartment}. 
-	This is a complex process involving Rab
-	GTPases and tethering complexes:
+Vesicle fusion involves two types of events, recognition of the correct target compartment and fusion of the transport vesicle with it's target compartment.
 
-	\begin{enumerate}[label=(\roman*)]
-		\item \textbf{Rab GTPases}  are small proteins which occur in two forms: the membrane associated and active
+	 \textbf{Recognition of the correct target compartment} is a complex process involving Rab
+	GTPases and tethering complexes.
+	% 
+	 Rab GTPases are small proteins which occur in two forms: the membrane associated and active
 		GTP bound form, and the cytosolic and inactive GDP bound forms. 
@@
 
-		\item \textbf{Tethering complexes} sequester vesicles to their target compartments and regulate SNARE
+	 \textbf{Tethering complexes} sequester vesicles to their target compartments and regulate SNARE
 		proteins, which enable vesicle fusion. 
@@
 		There are two types of tethering complexes: multi subunit tethers and long coiled-coil tethers:
-
-		\begin{enumerate}[label=(\alph*)]
-			\item \textbf{Coiled coil} tethers are long, single subunit proteins. 
+%		
+ Coiled coil tethers are long, single subunit proteins. 
 			%
@@
 			with vesicle SNAREs~\cite{baker2016chaperoning}.
-
-			\item \textbf{Multi-subunit tethering complexes (MTCs)} are composed of three or more different
+		%	
+			Multi-subunit tethering complexes (MTCs) are composed of three or more different
 			subunits.
@@
 
-		\end{enumerate}
-
-	\end{enumerate}
-
-	\item \textbf{Fusion of vesicle with the target compartment} is brought about by SNARE proteins. 
+	 \textbf{Fusion of vesicle with the target compartment} is brought about by SNARE proteins. 
 	%
@@
 	Most v-SNAREs are RSNAREs, and most t-SNAREs are Q-SNAREs~\cite{yoon2018snare}.
-
-\end{enumerate}
 
@@
 \textbf{Major paths in the vesicle transport network}:
-Molecules traverse the cell in a series of vesicles, and there are two major such routes of transport in all eukaryotic cells:
-\begin{enumerate}
-	\item The secretory route takes proteins from the ER, their site of production, to the plasma membrane, from where they are secreted out of the cell.
+Molecules traverse the cell in a series of vesicles, and there are two major such routes of transport in all eukaryotic cells.
+%
+	The secretory route takes proteins from the ER, their site of production, to the plasma membrane, from where they are secreted out of the cell.
+	%
 	 Cargo proteins leave the ER in COP2 coated vesicles which fuse with the Golgi apparatus.
+	 %
 	  The golgi apparatus is where proteins get modified, for example by the addition of carbohydrate side-chains. 
+	  %
 	  Subsequently, proteins destined for secretion are packaged into clathrin coated vesicles which fuse with the plasma membrane, thus releasing their contents to the outside of the cell\cite{alberts2002molecular}.
-	\item the endocytic routetakes proteins from the outside of the cell through the plasma membrane to the endocytic compartments, where they are digested.
+	  %
+ The endocytic routetakes proteins from the outside of the cell through the plasma membrane to the endocytic compartments, where they are digested. 
+ %
  Cargo from the outside of the cell is taken in in the form of clathrin coated vesicles which form at the plasma membrane. 
+ %
  These vesicles fuse amongst themselves in a process called homotypic fusion to generate the early endosomal compartments. 
+ %
  Early endosomes undergo changes in their composition due to ongoing vesicle traffic and maturee into late endosomes. 
+ %
  This maturation is concomitant with a switch the Rab protein they are associated with; the Rab5 associated early endosomes mature into Rab7 associated late endosomes\cite{rink2005rab}.
 Late endosomes then fuse with lysosomes, where all its contents get digested\cite{pryor2009delivery}.
-\end{enumerate}
-
-\textbf{Existential and universal condition:}
+%
 Other paths are used for cross talk between the secretory and the endocytic routes.
@@
 
+\todo{SA: Describe the model in graph terms and connect it to the topology question. ONE PAGE !}
 \textbf{Difficulty of the problem:}
@@
 Although vesicle-mediated traffic was discovered decades ago~\cite{wells2005discovery}, the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
-
+%
 Completing the vesicle traffic network is a difficult task for many reasons: (1) the core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different \cite{stoops2014trafficking,zhou2015arp2}, (2) although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different \cite{davletov2007regulation,di2010calcium}, (3) behaviour of traffic molecules in vitro is different from their behaviour inside cells \cite{furukawa2014multiple}, (4) molecules can have redundant routes within the cell \cite{shimizu2014compensatory,nakatsukasa2014nutrient}, and (5) it can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.

### 2018-12-28 papers/journal/intro.tex
Added comparision table for SAT and SMT tool's timing.

@@
 %
-Completing the vesicle traffic network is a difficult task for many reasons: (1) the core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different \cite{stoops2014trafficking,zhou2015arp2}, (2) although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different \cite{davletov2007regulation,di2010calcium}, (3) behaviour of traffic molecules in vitro is different from their behaviour inside cells \cite{furukawa2014multiple}, (4) molecules can have redundant routes within the cell \cite{shimizu2014compensatory,nakatsukasa2014nutrient}, and (5) it can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
+Completing the vesicle traffic network is a difficult task for the following reasons: 
+\begin{enumerate}
+	\item The core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.
+
+	\item Although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
+
+	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.
+
+	\item Molecules can have redundant routes within the cell ~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
+
+	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
+\end{enumerate}
 

### 2018-12-29 papers/journal/experiments.tex
Added comparision table for SAT and SMT tool's timing.
Experiments section update

@@
 %
+\todo{SA: CBMC Diagram}	
 The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
@@
 %
-\todo{SA: CBMC Diagram}	
+
 In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes.
@@
 \subsection{Results}
-The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
+The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
 
@@
 
-In Table~\ref{tab:smt-grph}, we present the running times for the search of
-VTSs for {\smttool} of sizes 2 to 10 that satisfy the variants and compare with the {\sattool}.
+In table~\ref{tab:smt-grph} we present the minimal connectivity results for each variation of the existential condition. 
 %
-For the comparison between both encodings we have fixed the total
-number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and $|M| = 2|N| + 1$ for $|N| = 2$.
+Table~\ref{tab:satsmt-graph} present the comparision of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
 %
-For each variant, we fix maximum number of parallel
-edges to 2.
+For this comparison we fixed the total number of molecules ($|M|$) to be $2|N|$ 
+%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
 %
-In the table we have shown comparison for specific connectivity, for
-example variant A is checked against any graph with connectivity 2,
-variant B with connectivity 3 similarly for the rest of the Variants.
+%For each variant, we fix 1
+and maximum number of parallel
+edges to be 2.
 %
-
+%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
+%
 %We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
 %
-For example, the formula for variation F, the total number of
-compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 s
-ecs)
-with a SAT result.
+As an example, the result of verifying the formula for variation F, of 2-connected 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
 %
-In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
+In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
 %
-``!'' indicate that the constraints were unsatisfiable.
+In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
+% for $|N|$ greater than 5.
 %
-Using this encoding in comparison to the old one, not only we got effi
-ciency improved for finding a SAT model but also did better in the cas
-e of refutation that no model exist (Table 2 Variant A timing comparis
-on and Variant D with N =2). 
 % 
-Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
-eukaryotic cells with a total number of 10 compartments.
+The recursive encoding also performed better for the cases where instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
+%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
 %
-Furthermore, we experimented with limits of our tools and found
-that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ n
-odes.
+Hence with the use of improved encoding of reachability, we were able to scale the system to the biologicly relevant compartment size, the
+%a much larger compartmentalized system, especially to interesting 
+case of eukaryotic cells with a total number of 10 compartments.
+%
+Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.
 
@@
 %\textbf{Universal Condition:}
+\todo{SA: Will add after experimentations.}
 Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
@@
 The last VTS represent mammalian SNARE map created by studying the literature references.  
-
-The table shows timing for various synthesis queries.
+%
+The fig shows timing for various synthesis queries.
 %
@@
 %
-One column reports the timing and the other reports the minimum changes
-needed to obtain a valid VTS.
+One column reports the timing and the other reports the minimum changes needed to obtain a valid VTS.
 %
@@
 %\ashu{@ankit: please discuss all the synthesis queries in the table.}
-In the table, we are reporting five synthesis queries
+
+In the Fig~\ref{tab:synth-graph}, we report five synthesis queries.
 %

### 2018-12-29 papers/journal/experiments.tex
Experiments section update-2

@@
 \subsection{Implementation}
-{\sattool} is based on the architecture of a Bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
+{\sattool} is based on the architecture of a bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
 %
@@
 
-\textbf{{\sattool} (Bounded model checker based tool)}:
+\textbf{{\sattool} (bounded model checker based tool)}:
 	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
@@
 %
-\todo{SA: CBMC Diagram}	
-The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
+\todo{SA: Do we need a diagram}	
+%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
 %
-CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
+%CBMC front end accepts
+
+We encode the problem using CBMC C-language front-end (CFE) interface 
+%ANSI-C programs 
+with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
 %	
-
 In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes.
@@
 and guarantees for steady state were expressed as assertions to be checked.
-%		
+
 Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
@@
 learning activity functions.
+%
+The tool returns a complete VTS with visual graph representation as an output to the user.
 
@@
 %
+%
+In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
 %In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
@@
 %
-As an example, the result of verifying the formula for variation F, of 2-connected 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
+As an example, the result of verifying the formula for variation F of 2-connected, 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
 %
 In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
-%
-In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
 % for $|N|$ greater than 5.
@@
 % 
-The recursive encoding also performed better for the cases where instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
+The recursive encoding also performed better for the cases where the instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
 %instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
 %
-Hence with the use of improved encoding of reachability, we were able to scale the system to the biologicly relevant compartment size, the
+Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
 %a much larger compartmentalized system, especially to interesting 
-case of eukaryotic cells with a total number of 10 compartments.
+the case of eukaryotic cells with a total number of 10 compartments.
 %
@@
 %\textbf{Universal Condition:}
-\todo{SA: Will add after experimentations.}
+\todo{SA: will improve after experimentation.}
 Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
+%
+The table represents the result of the graph connectivity for each variation of the VTS.  
+%
+For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
+%
+Note that for this variation existential condition result was the 2-connected graph. 
+%
+For every other version, the results remained the same.
+% 
+The experimentations were done using two QBF solvers: \depqbf and \rarqbf.
 
+%(there is a satisfying assignments to satisfy constraints of VTS) is valid VTS.   
 %\textbf{Synthesis}:

### 2018-12-29 papers/journal/experiments.tex
update of exper

@@
 \subsection{Implementation}
+%The existential condition is implemented with two different encodings. First, with a bounded model checker that uses an enumeration of paths for encoding the reachability problem: {\sattool}.
+%which is based on the architecture of a
+%
+%The other with an SMT solver Z3 that uses the efficient encoding of finding a least fixed point to solve it: {\smttool}.
 {\sattool} is based on the architecture of a bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.

### 2018-12-30 papers/journal/intro.tex
Rewritten Introduction Section

@@
 
+\subsection{Vesicle traffic system}
 \todo{SA:One para of BIO BACKGROUND related to VTS. Why they are Important history etc.}
@@
 
-\begin{table}
-	\begin{center}
-		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-			\hline
-			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
-			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
-			\hline
-		\end{tabular}
-		\label{tab:threec}
-		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
-	\end{center}	
-\end{table}
+%\begin{table}
+%	\begin{center}
+%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%			\hline
+%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
+%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
+%			\hline
+%		\end{tabular}
+%		\label{tab:threec}
+%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
+%	\end{center}	
+%\end{table}
+\subsection{Abstraction of VTS as a graph problem}
 
-\todo{SA: Describe the model in graph terms and connect it to the topology question. ONE PAGE !}
-\textbf{Difficulty of the problem:}
+%In this section, we will describe the basic constraints imposed by cell biology. These are all incorporated into an abstract model of a VTS, whose properties will then be explored using SMT solvers.
+
+In this section, we will abstract from the biological description of a VTS and represent the whole network as an annotated transport graph. 
+%
+The constraints imposed by cell biology is incorporated in the  annotations of the graph.
+
+\textbf{The cell as a transport graph:} 
+%We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph.
+Every compartment or vesicle has a set of molecular labels, such as SNARE proteins, associated with it.
+The cell can be abstractly represented as an annotated graph. 
+Every compartment in the cell can be represented as a node in the graph. 
+%
+The set of molecules present in the compartment, for example SNARE proteins associated with it, are represented as a label to the corresponding nodes.
+%
+The label of each node will be unique molecules present on the compartment, i.e we abstract over the quantity of the molecule present in a compartment.
+%This represent the flux of the molecule type present at that compartment.
+%
+The target vesicle flowing from source compartment to the target compartment is represented by an labelled directed edge. 
+% 
+The label represent the associated flux of all molecular types carried by the corresponding vesicle.
+%
+
+\textbf{Steady state:} 
+The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
+%
+In our abstracted model we will assume that cell is in a steady state. 
+%
+The compartment's composition does not evolve over the short times scales.
+%
+Therefore, the incoming and outgoing flux are balanced for each of the molecular type at each compartment.
+%
+This abstraction is supported by the cell biology as on the scale of seconds and minutes the molecular composition actually remains the same. 
+%
+In this paper we refer to the steady state of the cell as stability condition over the annotated graph.
+
+%Each edge is associated with a flux of all the molecular types carried by the corresponding vesicle.
+The total amount of each molecular type on each compartment can therefore increase or decrease.
+We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales.
+Therefore, incoming and outgoing fluxes are balanced for each molecular type at each compartment; it is the \textit{stability cond1ition}.
+
+\textbf{Vesicle fusion:}
+Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
+%
+Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
+% 
+%The molecular composition and hence the properties of the transfer vesicle 
+is the crucial factor to which target compartment the vesicle will fuse to.
+%
+%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
+%  
+%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
+%
+%Once a vesicle has budded out of the source, the molecules it carries determine its properties.
+In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment.
+Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
+%
+SNAREs are of two types (known as Q and R in the cell biology literature) and vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE between transfer vesicle and target compartment. 
+%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
+%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
+%
+%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
+%
+Only particular pair of Q ad R SNAREs are allowed to fuse with each other.
+%
+Without loss of generality we assume equal numbers of Q and R SNARE types.
+%
+Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with an equal number of Q and R SNAREs. 
+% equal number of Q and R SNAREs as a part of node and edge label.
+%
+%
+Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (edge between two compartments) based on the above condition.
+
+\textbf{Molecular regulation:} 
+Fusion takes place only if the SNARE types involved on the vesicle and compartment must both be in an active state.
+%We assume that for fusion to occur, the pair of 
+%
+The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
+%
+In our abstract model we create a set of variations of different kind of molecular regulations.
+%
+Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
+%
+We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}. 
+%
+This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
+%
+
+%We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state.
+Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively.
+We test many different versions of this kind of molecular regulation.
+Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle.
+We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
+This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
+
+\textbf{Difficulty of the analysis:}
 The analysis of vesicle traffic systems is a difficult problem
@@
 
-\textbf{Synthesis of VTS:}
+\subsection{Interesting properties of VTS}
+%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
+Suppose we are given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model.
+This information is then sufficient to check the following properties, which summarise the cell-biological constraints described above:
+\begin{enumerate}
+	\item We can determine which molecules are active on every compartment or vesicle.
+	\item For every vesicle fusing to a compartment, we can determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
+	\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we can verify that there is no pairing of active molecules on the
+	vesicle and compartment that could drive their fusion.
+	\item We can verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set.
+This is the steady state condition.
+In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
+\end{enumerate}
+
+The biological problem often boils down to such an analysis.
+A cell biologist might determine which molecules flow between which set of compartments, and biochemical experiments could be used to see how these molecules activate one another.
+We can then ask: is this a complete and consistent description?
+That is, do all the required properties listed above hold, given what the experimentalists have told us?
+It is often the case that biological data is missing.
+For example, only a few of the dozens of molecules involved in real VTSs have been mapped out.
+Therefore, it is extremely likely that the description provided by the cell biologist is incomplete.
+We can use our model to find out which properties have failed to hold, and thus prescribe new experiments in order to fill in the missing information.
+
+Can we find a simple test to see whether any information is missing, given the experimental data?
+We have shown that graph k-connectedness furnishes precisely such a test \cite{shukla}.
+If the data provided by cell-biologists, suitably represented as a graph, does not have a certain degree of connectivity, this implies that some biological data has been missed.
+(The converse is not true: even if the required connectivity does hold, there might of course be more information missing.)
+
+Our result about k-connectedness being a useful test of missing information \cite{shukla} was obtained using SAT solvers for graphs up to a certain size, and a certain number of molecules.
+This was due to limitations in how we encoded the problem.
+Here we present a much more natural encoding that allows our result to be extended to graph sizes and molecule numbers that are typical of those found in real cells.
+
+%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
+\label{subsec:graphmodel}
+%
+Since a VTS is a transport graph, it is but natural to formally model
+VTS as graphs (as used in computer science) with their nodes denoting
+compartments and labeled edges denoting transport vesicles with labels
+denoting the set of molecules being transported. The pairing mechanism
+can be represented as matching tables over sets of molecules.
+% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
+%
+Given such a graph model of VTSs and their properties, such as
+stability condition and fusion rules, can be formally defined as
+constraints over graphs and uninterpreted Boolean functions.
+%
+% Note that the formulas define among other things constraints over
+% paths between nodes in the graph model of VTS. Similarly, one can
+% define fusion rules as constraints over the boolean functions modeling
+% the regulations.  
+\
+% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
+
+%\begin{itemize}
+%\item \srivas{Detailed BIO to Graph problem}
+%\end{itemize}
+
+%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
+the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.
+Here we have defined the property by checking over existence of any fusion/budding rules.
+We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
+%
+%\subsection{Converting the Graph Problem into Boolean SAT problem}
+%\label{subsec:satproblem}
+%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.
+In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.
+We then used the CBMC model checker to convert the graph problem into a SAT problem.
+One of the challenges we had in our earlier work is dealing with quantifiers.
+Note that the connectedness property defined in Listing~1.2 has quantifier alternation.
+Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.
+CBMC supports only a quantifier-free logic n its assertion language.
+In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.
+This enumeration was one source of bottleneck for scaling in our earlier work.
+In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.
+The details of te hnew encding will described in subsequent sections.
+
+A VTS is {\em $k$-connected} if every pair of compartments remain
+reachable after dropping $k-1$ vesicles.
+%
+This property of VTSs has been considered informative and
+studied by~\cite{shukla}.
+%
+Here we have build an {\em efficient} tool that studies properties of
+VTSs that are not $k$-connected, from some $k$.
+
+\subsection{Synthesis of VTS:}
 Although vesicle-mediated traffic was discovered decades ago~\cite{wells2005discovery}, the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.

### 2018-12-30 papers/journal/intro.tex
Improvement and bug fixes in writing

@@
 %
-The set of molecules present in the compartment, for example SNARE proteins associated with it, are represented as a label to the corresponding nodes.
+The set of molecules present in the compartment, for example, SNARE proteins associated with it, are represented as a label to the corresponding nodes.
 %
 The label of each node will be unique molecules present on the compartment, i.e we abstract over the quantity of the molecule present in a compartment.
-%This represent the flux of the molecule type present at that compartment.
+%This represents the flux of the molecule type present at that compartment.
 %
-The target vesicle flowing from source compartment to the target compartment is represented by an labelled directed edge. 
+The target vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
 % 
-The label represent the associated flux of all molecular types carried by the corresponding vesicle.
+The label represents the associated flux of all molecular types carried by the corresponding vesicle.
+%
 %
@@
 %
-In our abstracted model we will assume that cell is in a steady state. 
+In our abstracted model, we will assume that cell is in a steady state. 
 %
-The compartment's composition does not evolve over the short times scales.
+The compartment's composition does not evolve over the short times' scales.
 %
-Therefore, the incoming and outgoing flux are balanced for each of the molecular type at each compartment.
+Therefore, the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
 %
@@
 %
-In this paper we refer to the steady state of the cell as stability condition over the annotated graph.
+In this paper, we refer to the steady state of the cell as stability condition over the annotated graph.
 
@@
 \textbf{Vesicle fusion:}
-Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
+%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
 %
-Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
+%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
 % 
 %The molecular composition and hence the properties of the transfer vesicle 
-is the crucial factor to which target compartment the vesicle will fuse to.
+%is the crucial factor to which target compartment the vesicle will fuse to.
 %
@@
 %
-SNAREs are of two types (known as Q and R in the cell biology literature) and vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE between transfer vesicle and target compartment. 
+%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
+Vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE between transfer vesicle and target compartment. 
 %For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
@@
 %
-Only particular pair of Q ad R SNAREs are allowed to fuse with each other.
+Only a particular pair of Q and R SNAREs are allowed to fuse with each other.
 %
-Without loss of generality we assume equal numbers of Q and R SNARE types.
+Without loss of generality, we assume equal numbers of Q and R SNARE types.
 %
@@
 %
-Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (edge between two compartments) based on the above condition.
+Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.
 
 \textbf{Molecular regulation:} 
-Fusion takes place only if the SNARE types involved on the vesicle and compartment must both be in an active state.
+Fusion takes place only if the SNARE types involved in the vesicle and compartment must both be in an active state.
 %We assume that for fusion to occur, the pair of 
@@
 %
-In our abstract model we create a set of variations of different kind of molecular regulations.
+In our abstract model, we create a set of variations of different kind of molecular regulations.
 %
@@
 %
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}. 
+We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
 %

### 2018-12-30 papers/journal/intro.tex
Introduction 0.1 version

@@
 %
-For example, we might want to check some conjecture of interest for all 3-connected graphs and
-all possible variations of SNARE regulation rules. 
+For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
 %
-The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
+The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
+%
+Precise analysis of the properties of the VTS would be hindered by the same reason. 
+%
+Properties of the VTS would be hindered by the same reason. 
+%3-connected graphs and all possible variations of SNARE regulation rules. 
+%
+%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
 
@@
 Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
+%
 Many diseases are caused by the malfunction of the vesicle traffic network. 
-Knowledge of the complete network would be helpful in identifying the root causes\cite{bexiga2013human,gissen2007cargos}.
+%
+Knowledge of the complete network would be helpful in identifying the root causes~\cite{bexiga2013human,gissen2007cargos}. 
+%
 At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
 
-In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs and output various completed versions which can then be tested experimentally.
 %
+The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
+%
+In order to even attempt to complete a given partial VTS we have to agree on the properties that every complete VTS should follow in spite of basic constraints. 
+%
+We can use our stability and k-connectivity constraints as a basis for this investigation.   
+%
+The incomplete VTS might not respect these constraints. 
+%
+In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
+%
+We output various completed versions of VTS against these properties which can then be tested experimentally.
+%
+
+We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
+%
+We have applied our tool on several VTSs including
+two found-in-nature VTSs.
+%
+Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
+%
+
+The rest of the paper is organized as follows. 
+%
+In Sect.~\ref{sec:prelim}, we present the notations we use in this paper. 
+%
+In Sect.~\ref{sec:model}, we present graph model of VTSs.
+%
+%encoding of several constraints on VTSs. 
+%
+In Sect.~\ref{sec:property}, we present the properties of interest.
+%
+In Sect.~\ref{sec:problem}, we present formal problem statement of the verification properties.
+%
+In Sect.~\ref{sec:encoding}, we present the encoding of BMC, SMT, QBF and Synthesis into SAT, SMT and QBF satisfiability. 
+%
+In Sect.~\ref{sec:experiments}, we present our implementation and experimental results. 
+%
+In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.
 

### 2019-01-01 papers/journal/experiments.tex
Experimentation 0.1 version

--- 2018-12-29 papers/journal/experiments.tex
@@
 %
-The existential condition is subdivided into two sub-block, using bounded model checking and using constraint solving. 
+The existential condition is subdivided into two sub-block, bounded model checking and constraint solving. 
 %
@@
 \subsection{Implementation}
-{\sattool} is based on the architecture of a bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
+%The existential condition problem is implemented with two separate encodings.
+We have implemented two separate encodings to determine the existential condition of the VTS. 
+%To solve the existential condition we have implemented two separate encodings. 
 %
-{\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. 
+The first encoding is implemented in {\sattool}
+%One 
+%with a successful bounded model checker, CBMC, 
+and perform path enumeration to encode the reachability. 
 %
-{\qbftool} is based on the QBF encoding of the universal condition and uses {\depqbf} solver to solve the generated QBF. 
+%This encoding is implemented in {\sattool}.
+% and uses a successful bounded model checker, CBMC.
+%which is based on the architecture of a
 %
-The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS using {\qbftool}.
+%The second encoding is implemented in {\smttool} and uses a
+%is based on 
+%industrial strength SMT solver, Z3, that uses a 
+%recursive encoding of finding a least fixed point to encode the same. 
+The second encoding is implemented in {\smttool} and employs a recursive encoding of finding a least fixed point for the reachability.
+
 %
-All the experiments were done on a machine with  Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM with 30 min (1800 sec) timeout.
+%The encoding is implemented in {\smttool}.
+% and uses industrial strength SMT solver, Z3.
+%The {\sattool} is based on the architecture of a bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
+%
+%The {\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. 
+%
+%The {\qbftool} is based on the QBF encoding of the universal condition and uses {\depqbf} solver to solve the generated QBF. 
+The QBF encoding of the universal condition is implemented in {\qbftool}.
+%
+The tool uses {\depqbf} solver to solve the generated QBF formula. 
+%
+The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS using {\qbftool} interface.
+%
+
+All the experiments were done
+%Each test was run 
+on a machine with Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM.
+%
+A 30 min (1800 sec) timeout was used for the tool.
 
@@
 \textbf{{\sattool} (bounded model checker based tool)}:
-	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
+The enumeration encoding (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
+	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
+The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
 %
@@
 %
-The tool verify property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
+It verify property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
 %
@@
 %
-\todo{SA: Do we need a diagram}	
 %The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
@@
 
-We encode the problem using CBMC C-language front-end (CFE) interface 
-%ANSI-C programs 
-with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
+%We encode the problem using CBMC C-language front-end (CFE) interface with some special annotations called \textit{assumes} and \textit{assertions}.
 %
-In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes.
+%These annotations express constraints on the model and properties to be checked. 
 %	
-The correspondence relationship between connectedness conditions
-and guarantees for steady state were expressed as assertions to be checked.
-
-Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
-	\begin{itemize}
-	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
-depth iff the Boolean formula is valid.
-	\item Check (using a SAT solver) validity of the verification condition.
+The vesicle transport network was modelled as a non-deterministic C-program manipulating an annotated graph. 
+%
+The special annotations \textit{assumes} and \textit{assertions} of CBMC's front end were used to express constraints on the model and properties to be checked. 
+%
+%The fusion rules and steady state properties were expressed as constraints using special annotations \textit{assumes}. 
+%		
+%The correspondence relationship between connectedness conditions and steady state were expressed as annotations \textit{assertions} to be checked. 
+Using the tool's interface user can select the variation of the VTS, connectivity of the graph and other required parameters like an exploration depth.
+%
+The {\sattool} verifies the properties by first converting the constraints and properties into a Boolean formula and determine the satisfiability of the formula with the help of a SAT solver backend.
+%
+The satisfying model is translated into a readable format and in case of a violation, the tool produces a readable counterexample.
+%  following steps:
+%	\begin{itemize}
+%	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
+%depth iff the Boolean formula is valid.
+%	\item Check (using a SAT solver) validity of the verification condition.
 {\sattool} reports successful verification if the formula is found to be valid.
 If not, then {\sattool} produces a counterexample,
-an assignment to the variables of the model, that is a witness to the violation of the property.
-	\end{itemize}
+%an assignment to the variables of the model, that is a witness to the violation of the property.
+%	\end{itemize}
 For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.
@@
 \textbf{{\smttool} (SMT based tool)}:
-	We have implemented the encodings for each variants (presented in section 6.1) using the python interface of Z3 in a tool {\smttool}. 
+The recursive encoding (presented in section 6.1)  
+%We have implemented the encodings 
+for each variant is implemented in {\smttool}.
+%
+It used python interface of industrial strength SMT solver, Z3. 
 %
@@
 \textbf{{\qbftool} (QBF based universal condition):}
-{\qbftool} is developed in C++ and uses~\zthree~\cite{z3} infrastructure and implement the encodings of the VTS in QBF form (presented in section 6.5). 
+We have implemented the encodings of the VTS in QBF form (presented in section 6.5) in
+{\qbftool}. 
 %
-Since some of the formulas involve alternation of quantifiers over
-Boolean variables Z3 is not a suitable choice for those examples.
+The tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure to encode the constraints.
+%
+Since some of the formulas involve alternation of quantifiers over Boolean variables Z3 is not a suitable choice for those examples.
 %
@@
 \textbf{{\ourtool} (QBF based synthesis tool):}
-
 \input{synth-table}
-We have implemented the synthesis encodings (presented in section 6.6) in a tool
+We have implemented the synthesis encodings (presented in section 6.6) in
 called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.

### 2019-01-01 papers/journal/intro.tex
Experimentation 0.1 version

@@
 %
-Properties of the VTS would be hindered by the same reason. 
+%Properties of the VTS would be hindered by the same reason. 
 %3-connected graphs and all possible variations of SNARE regulation rules. 
@@
 
-A VTS is {\em $k$-connected} if every pair of compartments remain
-reachable after dropping $k-1$ vesicles.
+%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
 %
-This property of VTSs has been considered informative and
-studied by~\cite{shukla}.
+%This property of VTSs has been considered informative and studied by~\cite{shukla}.
 %
-Here we have build an {\em efficient} tool that studies properties of
-VTSs that are not $k$-connected, from some $k$.
+%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$.
 

### 2019-01-01 papers/journal/experiments.tex
small fixes

@@
 
-In table~\ref{tab:smt-grph} we present the minimal connectivity results for each variation of the existential condition. 
+The minimal connectivity results for each variation of the existential condition is presented in table~\ref{tab:smt-grph}.
 %
-Table~\ref{tab:satsmt-graph} present the comparision of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
+Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
 %
-For this comparison we fixed the total number of molecules ($|M|$) to be $2|N|$ 
+For this comparison we have fixed the total number of molecules ($|M|$) to be $2|N|$ 
 %for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$

### 2019-01-01 papers/journal/intro.tex
small fixes

@@
 
-In this section, we will abstract from the biological description of a VTS and represent the whole network as an annotated transport graph. 
+In this section, we will abstract from the biological description of the VTS and represent the whole network as an annotated transport graph. 
 %
@@
 %
-In Sect.~\ref{sec:model}, we present graph model of VTSs.
+In Sect.~\ref{sec:model}, we present graph model of VTSs and  properties of interest in Sect.~\ref{sec:property}.
 %
@@
 %
-In Sect.~\ref{sec:property}, we present the properties of interest.
+%In , we present the
 %
-In Sect.~\ref{sec:problem}, we present formal problem statement of the verification properties.
+In Sect.~\ref{sec:problem}, we present the complete formal problem statement of the verification properties.
 %

### 2019-01-04 papers/journal/experiments.tex
added results for existential case

@@
 %
+No matter what the rules of molecular
+interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
+%
+Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is necessary and sufficient for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
+%
+For more constrained regulation models
+(including the case where SNAREs are always active) we did not find any possible graphs
+representing steady state vesicle transport networks. 
+%
+This strongly suggests (but does not
+prove, since we only checked graphs of finite size) that no such graphs exist.
+%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
+%%
+%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
+%%  
+%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
+%%
+%Variants C has 3-connectedness as
+
+\todo{SA: Explain the results in details and Add biological interpretation of results.}
+%
 Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.

### 2019-01-04 papers/journal/experiments.tex
minor edit

@@
 %
-No matter what the rules of molecular
-interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
+%No matter what the rules of molecular interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
+The steady-state constraint requires that structure of the graph is at least 2-connected. 
 %
-Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is necessary and sufficient for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
+We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
+%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
 %

### 2019-01-08 vts/bio.py
Changed the python code for Neccessary condition Experimentations

@@ -12,7 +12,8 @@ set_option(max_args=10000000, max_lines=1000000, max_depth=10000000, max_visited
 # input parsing
 # input number of nodes and molecules
 parser = argparse.ArgumentParser(description='Auto testing for TARA')
-parser.add_argument("-i","--file", type=file, default=examples/qbflib.qdimacs, help = "number of molecules")
+#parser.add_argument("-M","--file", type=file, default=4, help = "number of molecules")
+parser.add_argument("-M","--mols", type=int, default=4, help = "number of molecules")
 parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes")
 parser.add_argument("-Q","--pedges", type=int, default=2, help = "max no.of parallel edges btw two nodes")
 parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
@@ -39,7 +40,7 @@ bag.append ('6. No regulation at all.')
 #    if V == i + 1:
 #        print ' '
 #        print 'Default/choosen vesicular traffic system is regulated by ...',
-#        print bag[i]
+#        print bag[i]No graph
 #        print ' '
 #        print 'Use -V option to change the regulated variation.' 
 #        for i in bag:
@@ -209,9 +210,10 @@ if V == 1:
     #print Activity_node
     #print Activity_edge
     #exit(0)
+#Boolean on Edge
 elif V == 2:
     Activity_node = f_nn()
-    #Activity_edge = f_be()
+    Activity_edge = True
     #print Activity_node
     #print Activity_edge
 elif V == 3:
@@ -223,7 +225,7 @@ elif V == 4:
     Activity_node = f_nn()
     Activity_edge = f_se()
 elif V == 5:
-    #Activity_node = f_bn()
+    Activity_node = True
     Activity_edge = f_ne()
 else:
     Activity_node = f_nn()
@@ -550,7 +552,6 @@ for i in range(N):
             #rhs = And( rhs, r1[l][j])
             kbc = Or ( kbc, And (rhs, r1[i][j])) 
         w = Implies( r1[i][j], Or (bhs , kbc) )
-        #w = Implies( Or(bhs , kbc), r1[i][j] )
         A_list.append(w)
 D3_1_reachability = And(A_list)
 
@@ -639,10 +640,11 @@ for i in range(N):
     for j in range(i+1, N):
         if i == j:
             continue
[…]

### 2019-01-08 vts/vts.py
Version for the experimentation. vts.py

@@ -1,0 +1,565 @@
+#!/usr/bin/python
+
+from z3 import *
+#print z3.__file__
+import argparse
+import itertools
+import time
+
+set_option(max_args=10000000, max_lines=1000000, max_depth=10000000, max_visited=1000000)
+
+#----------------------------------------------------
+# input parsing
+# input number of nodes and molecules
+parser = argparse.ArgumentParser(description='Auto testing for TARA')
+#parser.add_argument("-M","--file", type=file, default=4, help = "number of molecules")
+parser.add_argument("-M","--mols", type=int, default=4, help = "number of molecules")
+parser.add_argument("-N","--nodes", type=int, default=2, help = "number of nodes")
+parser.add_argument("-Q","--pedges", type=int, default=2, help = "max no.of parallel edges btw two nodes")
+parser.add_argument("-V","--variation", type=int, default=1, help = "model of the biological system")
+parser.add_argument("-C","--connected", type=int, default=3, help = "graph connectivity want to check")
+#parser.add_argument("-E","--edges", type=int, default=3, help = "graph connectivity want to check")
+
+args = parser.parse_args()
+
+M = args.mols
+N = args.nodes
+Q = args.pedges
+V = args.variation
+C = args.connected
+
+bag = []
+bag.append ('1. Boolean function on nodes and Boolean function on the edges.') 
+bag.append ('2. Only Boolean function on the edges.') 
+bag.append ('3. Boolean function on nodes and SNARE-SNARE inhibition on edges.')
+bag.append ('4. Only SNARE-SNARE inhibition on edges.')
+bag.append ('5. Only Boolean function on nodes.')
+bag.append ('6. No regulation at all.')
+
+#----------------------------------------------------
+# Constraint generation 
+edge = [ [ [ Bool ("e_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+setE = [ edge[i][j][q] for i in range(N) for j in range(N) for q in range(Q) if i != j]
+
+lenE = len(setE)
+
+dump1 = [ [ [Bool ("d1_{}_{}_{}".format(i,j,q)) for q in range(Q)] for j in range(N)] for i in range(N)]
+
+setDump1 =  [ dump1[i][j][q] for i in range(N) for j in range(N) for q in range(Q) if i != j]
+
[…]

### 2019-01-11 papers/journal/experiments.tex
Version 0.2 Experimentation section

@@
 %
-A 30 min (1800 sec) timeout was used for the tool.
+A 90 min (5400 sec) timeout was used for the tool.
 
@@
 %	\end{itemize}
-For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.
+For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}.
+% the winner of SAT 2015 Competition~\cite{balyo2016sat}.
 
@@
 %
-It used python interface of industrial strength SMT solver, Z3. 
+The tool is based on industrial strength SMT solver, Z3. 
 %
@@
 We translate the formulas created by Z3 tool into a standard
-QDIMACS~\cite{qdimacs} format and use it as an input for QBF solvers. 
+QDIMACS~\cite{qdimacs} format and use QBF solvers to solve the formula. 
 %
-We have used~\depqbf~\cite{lonsing2010depqbf} for solving the QBF formulas.
+We have used~\depqbf~\cite{lonsing2010depqbf} for solving QBF formulas with alternation of quantifiers.
 
@@
 \input{synth-table}
-We have implemented the synthesis encodings (presented in section 6.6) in
-called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
+We have implemented the synthesis encodings (presented in section 6.6) in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
 %

### 2019-01-13 papers/journal/related.tex
restructure introduction and started experiments section. Added references to the bio part of the intro section.
Table update

--- 2018-10-06 papers/journal/related.tex
@@
-SAT and SMT solvers are a perfect fit for solving combinatorial problems due to their exhaustive nature of searching. 
+Previous analysis of vesicle traffic system has used simulation and statistical reasoning~\cite{mani2016stacking}. 
 %
-Improvement in SAT and SMT solvers in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
+Such analysis is far from complete and can only make statistical claims based on a subset of samples. 
 %
-Many of which involve reasoning about graphs and networks rules with possible exhaustive search and hence can be reduced to solving a SAT/SMT question. 
+The properties of VTS required precise analysis for all possible rules and variations that make formal methods a suitable choice.
+
+The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
 %
-Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example.
+software and hardware verification, equivalence checking, automatic test generation,
+AI planning, scheduling and program synthesis. 
 %
-We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS)~\cite{mani2016stacking,shukla}.
+The enormous progress in the performance of SAT and SMT solvers
+%Improvement in SAT and SMT solvers
+in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
+%
+Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
+% and hence can be reduced to solving a SAT/SMT question. 
+%
+
+One of the prominent areas of application of SAt/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
+%
+We have extended the application of SAT and SMT solvers to the most complex Biological transport network (VTS)~\cite{mani2016stacking,shukla}.
 

### 2019-01-13 vts/vts.py

@@ -403,7 +403,9 @@ for i in range(N):
                 rhs = Or( Or (And( edge[i][l][q], Not (dump1[i][l][q]) ), And (edge[l][i][q], Not ( dump1[l][i][q]) ) ) , rhs)
             #rhs = And( rhs, r1[l][j])
             kbc = Or ( kbc, And (rhs, r1[i][j])) 
-        w = Implies( r1[i][j], Or (bhs , kbc) )
+        # THIS WAS A BUG :)
+        #w = Implies( r1[i][j], Or (bhs , kbc) )
+        w = Implies( Or (bhs , kbc), r1[i][j] )
         A_list.append(w)
 D3_reachability = And(A_list)
 

### 2019-01-13 papers/journal/experiments.tex
small changes

@@
 %
-The satisfying model is translated into a readable format and in case of a violation, the tool produces a readable counterexample.
+The satisfying model is translated into a human readable format and in case of a violation, the tool produces a readable counterexample.
 %  following steps:
@@
 %		
-It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that respects the constraints). 
+It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that follows the constraints). 
 %
@@
 %
-The tool can not only synthesize the discussed queries, but also their
-combinations.
+The tool can synthesize the queries discussed earlier and also their combinations.
+%The tool can not only synthesize the discussed queries, but also their combinations.
 %
@@
 \subsection{Results}
-The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
+The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\qbftool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
 
@@
 
-The minimal connectivity results for each variation of the existential condition is presented in table~\ref{tab:smt-grph}.
+The minimal connectivity results for each variation of the existential condition are presented in table~\ref{tab:smt-grph}.
 %
@@
 %
-For more constrained regulation models
-(including the case where SNAREs are always active) we did not find any possible graphs
-representing steady state vesicle transport networks. 
+For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the vesicle transport networks in the stable state.
+%(including the case where SNAREs are always active) we did not find any possible graphs representing stable vesicle transport networks. 
 %
-This strongly suggests (but does not
-prove, since we only checked graphs of finite size) that no such graphs exist.
+This hints that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof. 
+%This strongly suggests (but does not prove, since we only checked graphs of finite size) that no such graphs exist.
 %We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.

### 2019-01-13 papers/journal/related.tex
small changes

@@
 
+\todo{Add references}
 The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
@@
 
-One of the prominent areas of application of SAt/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
+One of the prominent areas of application of SAT/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
 %
-We have extended the application of SAT and SMT solvers to the most complex Biological transport network (VTS)~\cite{mani2016stacking,shukla}.
+The gene regulatory network question is encoded into a Boolean satisfiability problem and then with the help of a SAT and SMT solvers solve the generated formula. 
+% 
+We have extended the application of SAT and SMT solvers to a more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system.
 

### 2019-01-13 vts/vts.py

@@ -352,6 +352,7 @@ for i in range(N):
         for q in range(Q):
             D1_list.append( Implies (dump1[i][j][q], edge[i][j][q]) )
 D1_only_present_e_dropped = And (D1_list)
+d1_1_0_0 = False
 
 # Make sure that the summation of edges present is greater than k-1
 oneList = []

### 2019-01-13 papers/journal/related.tex
SAT SMT table update

@@
 % 
-We have extended the application of SAT and SMT solvers to a more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system.
+We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system.
 

### 2019-01-13 papers/journal/experiments.tex
SAT SMT table update
Added Biological Interpretation to the REsult section

@@
 %
-A 90 min (5400 sec) timeout was used for the tool.
+A 120 min (7200 sec) timeout was used for the tool.
 
@@
 %
-This hints that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof. 
+This strongly suggests that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof.
+
+For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
+%
+On top of this, for the case where traffic molecules are regulated in some form, every pair of compartments with a vesicle going between them, have two additional vesicle paths connecting them; where these two paths go in opposite directions.
+%
+Finally, when we take into account the exact manner in which SNAREs interact in real cells, we find that the biological VTS must conform to a very specific structure; any two compartments that are connected by a vesicle, must be connected by 4 vesicle paths, two of them going in the same direction, and the other two in the opposite direction.
+%
+No graph results suggests that a functional VTS necessarily needs some form of regulation, where the molecules of the VTS are kept inactive in places where they might disrupt other interactions
+
 %This strongly suggests (but does not prove, since we only checked graphs of finite size) that no such graphs exist.
@@
 %\textbf{Universal Condition:}
-\todo{SA: will improve after experimentation.}
+
 Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
@@
 For every other version, the results remained the same.
+This implies that for every 3-connected graph, a valid VTS that satisfies all constraints \todo{ elaborate a bit on the constraints} exists.
 % 
-The experimentations were done using two QBF solvers: \depqbf and \rarqbf.
+For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration
+%
+%The experimentations were done using two QBF solvers: \depqbf and \rarqbf.
 

### 2019-01-13 papers/journal/encoding.tex
Fancy lookign table

@@
 %
-In the table~\ref{tab:satqbf-graph}, you can see that SAT version was not able to scale it to the desired results.
+The table~\ref{tab:satqbf-graph}, shows results of search result of universal condition for N = 5, 3-connected graphs.
+The SAT version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
 %

### 2019-01-13 papers/journal/qbf-table.tex
Experimentation 0.1 version
Added Biological Interpretation to the REsult section
Universal condition table restructure
Fancy table everywhere

@@
 	\centering
-	    \def\arraystretch{1.1}
-%	\caption{{\bf SAT and QBF implementation comparison.}}
-%	\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
-%		max width=\textwidth}{
-		\begin{tabular}[t]{|c|c|c|c|c|c|}\hline
+	\def\arraystretch{1.2}
+%	\begin{tabular}{ c|c|c|c }
+%		\hline
+%		{\multirow{2}{*}{Variant}}  &
+%		\multicolumn{2}{c|} {Constraints} & 
+%		%	{\multirow{2}{*}{\textbf{Results}}}
+%		{\multirow{2}{*}{Graph connectivity }} 
+%		\\
+%		\cline{2-3}
+%		&  Rest & Activity & 
+%		\\ \hline
+%		
+%		A. & \multirow{5}{*}{
+%			\makecell{ \texttt{Consistancy}, \\  \texttt{Stability}, \\
+%				 \texttt{Connected(k)}  }
+%		}
+%		& \ref{eq:ann},\ref{eq:aen} & No graph   \\
+%		B. & & \ref{eq:anb},\ref{eq:aen} & No graph \\
+%		C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected \\
+%		D. & & \ref{eq:anb},\ref{eq:aeb} & 3-connected \\
+%		E. & & \ref{eq:ann},\ref{eq:aep} & No graph    \\
+%		F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected \\\hline
+%		
+%		% C_es :Self edges are allowed
+%		% C_ed : Every edge is distinct 
+%	\end{tabular}
+	\begin{tabular}{ c|c c c|c }
+	\hline
+	{\multirow{3}{*}{Variant}}  &
+	\multicolumn{3}{c|} {Constraints} & 
+	%	{\multirow{2}{*}{\textbf{Results}}}
+	{\multirow{3}{*}{Graph connectivity} } 
+	\\
+	\cline{2-4}
+	& 	{\multirow{2}{*}{Rest} }  & 	\multicolumn{2}{c|} {Activity} & 
+	\\ 
+	\cline{3-4}
+	&  & Node  & Edge & 
+	\\\hline
 
-			{\multirow{2}{*} {Sr.No}}  & \multicolumn{2}{c|}{Regulation} & \multicolumn{3}{c|}{Universal condition}
+	A. & \multirow{5}{*}{
+					\makecell{ \texttt{Consistancy}, \\  \texttt{Stability}, \\
+						 \texttt{Connected(k)}  }
+	}
+	& \ref{eq:ann} & \ref{eq:aen} & No graph  \\
+	B. & & \ref{eq:anb} & \ref{eq:aen} & No graph \\
+	C. & & \ref{eq:ann} &  \ref{eq:aeb} &  3-connected \\
+	D. & & \ref{eq:anb} & \ref{eq:aeb} & 3-connected \\
+	E. & & \ref{eq:ann} & \ref{eq:aep} & No graph  \\
+	F. & & \ref{eq:anb} &  \ref{eq:aep} & 4-connected \\\hline
 
-		%	\\\cline{2-7}
-
-%			{} & \multicolumn{2}{c|}{\textbf{2-connected} } & \multicolumn{2}{c|}{\textbf{3-connected} } & \multicolumn{2}{c|}{\textbf{2-connected}}  &  \multicolumn{2}{c|}{\textbf{4-connected}}
-
-			%{} & \multicolumn{2}{c|}{2-connected} & \multicolumn{2}{c|}{3-connected} & \multicolumn{2}{c|}{2-connected}  &  \multicolumn{2}{c|}{4-connected}
-
-			\\\cline{2-6}
-			{} & {Node} & {Edge} & {Connectivity} & {SAT-time} & {QBF-time}
-
-			\\\hline
-			1. & Bf & Bf & 3C & 2.12 & 1.89  \\\hline
-			2. & None & Bf  & 3C & 7.12 & 4.89  \\\hline
-			3. & Bf & SNARE inhib & 4C  & M/O & 7.66 \\\hline
-			4. & None & SNARE inhib  & No graph & M/O & 48.35 \\\hline
-			5. & Bf & None  & No graphs & M/O & 890.84 \\\hline
-			6. &  None & None  & No graphs & M/O & M/O \\\hline
-
+	% C_es :Self edges are allowed
+	% C_ed : Every edge is distinct 
 \end{tabular}
-%}
-	\caption{ SAT and QBF implementation comparison (in secs.)}
-	\label{tab:satqbf-graph}
+	\caption{ QBF result for graph connectivity}
+	\label{tab:qbf-graph}
 \end{table}

### 2019-01-13 papers/journal/experiments.tex
Universal condition table restructure
results section improvement V1

@@
 
-\todo{SA: Explain the results in details and Add biological interpretation of results.}
 %
@@
 %
-For this comparison we have fixed the total number of molecules ($|M|$) to be $2|N|$ 
+For this comparison we have fixed the total number of molecules minimum twice the node count 
 %for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
@@
 %
-In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
+In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
 %In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
@@
 %
-As an example, the result of verifying the formula for variation F of 2-connected, 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
+As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs. with a satisfying result.
 %
-In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
+In comparison, {\sattool} was unable to solve the instance and ran out of memory.
 % for $|N|$ greater than 5.
@@
 % 
-The recursive encoding also performed better for the cases where the instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
+The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
 %instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).

### 2019-01-13 papers/journal/experiments.tex
Results section is completed

@@
 %
-As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs. with a satisfying result.
+As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
 %
@@
 %
-Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.
+Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.
 
@@
 For every other version, the results remained the same.
-This implies that for every 3-connected graph, a valid VTS that satisfies all constraints \todo{ elaborate a bit on the constraints} exists.
+%
+This implies that for every 3-connected graph there is a valid VTS that satisfies all the constraints of the system.
 % 

### 2019-01-13 papers/journal/related.tex
Addded references to the related work

@@
 
-\todo{Add references}
 The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
 %
-software and hardware verification, equivalence checking, automatic test generation,
-AI planning, scheduling and program synthesis. 
+software and hardware verification~\cite{biere1999symbolic1, biere1999symbolic2, bjesse2001finding, velev2003effective}, equivalence checking~\cite{goldberg2001using} automatic test case generation~\cite{stephan1996combinational},
+AI planning~\cite{kautz1996pushing} and scheduling~\cite{gomes1998randomization}. 
 %

### 2019-01-13 papers/journal/related.tex
Related work section completed

@@
 %
-Such analysis is far from complete and can only make statistical claims based on a subset of samples. 
+Such analysis is far from complete and can only make statistical claims about VTS based on a subset of samples. 
 %
-The properties of VTS required precise analysis for all possible rules and variations that make formal methods a suitable choice.
+The properties of VTS discussed in this paper require precise analysis for all possible rules and variations, that make formal methods a suitable alternative.
 
@@
 %
-software and hardware verification~\cite{biere1999symbolic1, biere1999symbolic2, bjesse2001finding, velev2003effective}, equivalence checking~\cite{goldberg2001using} automatic test case generation~\cite{stephan1996combinational},
+software and hardware verification~\cite{biere1999symbolic1, biere1999symbolic2, bjesse2001finding, velev2003effective}, equivalence checking~\cite{goldberg2001using}, automatic test case generation~\cite{stephan1996combinational},
 AI planning~\cite{kautz1996pushing} and scheduling~\cite{gomes1998randomization}. 
@@
 
-One of the prominent areas of application of SAT/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
+One of the prominent areas of application of SAT/SMT solvers is modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
 %
-The gene regulatory network question is encoded into a Boolean satisfiability problem and then with the help of a SAT and SMT solvers solve the generated formula. 
+The gene regulatory network question is encoded into a Boolean satisfiability problem and then SAT and SMT solvers are used to solve the generated formula. 
+%
+The~\cite{rosenblueth2014inference, batt2010efficient, dunn2014defining} use symbolic SAT solving approach whereas~\cite{giacobbe2015model, yordanov2016method} present an SMT based encoding of the problem.
 % 
 We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system. 
+%
+To our best knowledge this series of work is the first application
+of formal methods to vesicle traffic networks.
 

### 2019-01-13 papers/journal/conclusion.tex
Added Bio interpretation of the Synthesis and rough conclusion

@@
 
+\todo{SA: Rough outline of the answers needed in the future work section}
+1. why this tool was biologically helpful?
+\begin{itemize}
+	\item we do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries.
+	\item With this tool, we make multiple new easily testable predictions. So it is very likely to hasten discoveries in this field.
+\end{itemize}
+
+2.  What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
+\\
+\textbf{Encode Dynamic behaviour of the VTS:} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation.
+Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.
+Maturation  is  evident  in  the  Golgi  apparatus  and  in  the  endocytic system. 
+Including this behaviour of the compartments in the model would allow it to make more accurate predictions.
 %%% Local Variables:

### 2019-01-13 papers/journal/experiments.tex
Added Bio interpretation of the Synthesis and rough conclusion

@@
 
+%Each completed graph is a prediction of our model.
+For every single incomplete graph, there are multiple ways to complete it, although, in this paper, we output the minimum number of changes required to complete the input graph.
+%%
+%These results are intended to be used as guides for further discoveries, where the predicted new vesicles and molecular components of existing vesicles and compartments can be tested experimentally.
+The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
+%%
+These queries represent different levels of changes that we can make in order to complete these graphs.
+%
+Each completed graph is a prediction of our model. 
+%
+For every single incomplete graph, there are multiple ways to complete it, although, in this paper, we output the minimum number of changes required to complete the input graph. 
+%
+These results are intended to be used as guides for further discoveries, where the predicted new vesicles and molecular components of existing vesicles and compartments can be tested experimentally.
 %

### 2019-01-14 papers/journal/intro.tex
Added new introduction to the paper

@@
-%\textbf{Components of the vesicle transport network}:
-A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bound organelles called compartments.
+A characteristic feature of eukaryotic cells is the presence of multiple internal membrane bound compartments.
+These compartments exchange molecules amongst themselves in small membrane bound packets called vesicles ~\cite{alberts2002molecular}.
+The molecular interaction network that controls the vesicle transport system involves tens of kinds of molecules which regulate each others activities and modes of action.
+Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
 %
-These compartments exchange molecules amongst themselves in small membrane-bound packets called vesicles. 
-%
-The recognition of cargo molecules to be loaded onto these vesicles and the recognition of the correct target compartments for each vesicle is performed by an intricate network of molecules called the vesicle transport system~\cite{alberts2002molecular}.
-%
-We call the set of internal compartments, together with the molecular routes that connect them through vesicle exchange, the vesicle transport network. 
-%
-Vesicle traffic underpins nearly every aspect of eukaryotic cellular physiology, including
-human cellular physiology.
-%
-Understanding how this system function is, therefore,
-one of the central challenges of cell biology.
-%
-The high complexity of the problems~\cite{mani2016wine, mani2016stacking} in VTS restricts the use of traditional methods like simulation and statistical reasoning. 
+The high complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
 %The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
-The requirement of precise analysis makes formal methods ideal candidate in this case.
+In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the aptitude of such methods.
 
-First, we will give an overview of the VTS mechanism and then will sketch out a few interesting problems that are key to the understanding of the VTS.
+First, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
 
 \subsection{Vesicle traffic system}
-\todo{SA:One para of BIO BACKGROUND related to VTS. Why they are Important history etc.}
+Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}.
+These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
+Below, we give a brief description of the sequence of steps involved in the vesicle transport process.
+Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.
+\begin{figure}
+	\includegraphics[width=\textwidth]{ankitspaper_schem1.png}
+	\label{schematic}
+	\caption{Schematic of the vesicle transport system.
+Steps involved in vesicle transport between two compartments; a source and a target compartment are shown.
+The symbols used for different molecules involved in vesicle traffic are explained in the key.
+At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins.
+Here, the different colours indicate different types of cargo and adaptor proteins.
+Coat proteins are recruited to the forming vesicle by adaptor proteins.
+Note here that a single type of coat protein can interact with multiple types of adaptor proteins.
+Subsequently, the vesicle is pinched off at its neck by dynamin.
+Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment.
+At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.
+}
+\end{figure}
+
+\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{schematic}.
 %
-%\textbf{Components of the vesicle transport network}:
-The vesicle transport network is used by cells to transport molecules across compartments.
+Cargo sorting is performed by cytosolic adaptor proteins. 
+Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
+Then these adaptors bind to cargo molecules and thereby sequester them for packaging.
 %
-The mechanism of vesicle transport can roughly be broken down into two big steps:
-% budding of vesicles from the source compartment and their fusion with the target compartment.
+Different adaptor proteins act at different compartments, for eg., vesicle formation at the ER requires the adaptor sec23/24, and AP2 adaptor is used for packaging vesicles at the plasma membrane.
 %
-the process of formation of a vesicle by budding from the membrane called as vesicle budding and the fusion of these transport vesicle with its target compartment called as vesicle fusion.
-
-\todo{SA:Need a Diagram}Vesicle budding process involves series of steps, sorting and packaging of the molecules, membrane deformation and budding out from the compartment.
-%
-First the sorting of cargo molecules takes place by cytosolic adaptor molecules. 
-%
-Cargo adaptors bind to short linear stretches of amino acids in the cargo molecules called sorting signals and thereby sequester them for packaging. 
-%
-Then the different adaptor proteins act at different compartments, for eg., sec23/24 is required for packaging vesicles that form at the ER, the AP2 adaptor is used for packaging vesicles at the plasma membrane, etc.
-%
-Thereafter, adaptors are recruited to the source compartments through interactions with the lipids that form the source compartment's membrane, and interactions with Arf/Sar GTPases which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
 
@@
 Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins.
-%
 These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
-%
 A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
 %
-Clathrin, COP2 and COP1 are the three major kinds of coat proteins in eukaryotic cells. 
-%
-The clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
+There are three major types of coat proteins; Clathrin, COP2 and COP1.
+These act on different compartments; the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
 
-The final step is budding of the vesicles from the source compartment.
-% by dynamin.
-%	The final step in vesicle formation is its pinching off from the source compartment.
-	%
+Finally, transport vesicles bud out from the source compartment.
 This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}.
 %
-The transport vesicle is now ready for the transportation.
+The vesicle is now ready for transport and subsequent fusion with a target compartment.
 
-Vesicle fusion involves two types of events, recognition of the correct target compartment and fusion of the transport vesicle with it's target compartment.
+\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\cite{schematic}.
 
-	 \textbf{Recognition of the correct target compartment} is a complex process involving Rab
-	GTPases and tethering complexes.
+Target compartment recognition involves molecular switches called Rabs and  tethering complexes.
+Distinct compartments of the cell are associated with distinct Rabs.
+For example, Rab5 is associated early endosomes and  Rab7 with late endosomes\cite{rink2005rab}.
+Rabs are master regulators; in their active form Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment.
+~\cite{muller2018molecular}
+
+Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion.
+They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion.
+A clear mechanism for action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle associated Rabs, SNAREs and SNARE regulators.
+They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.
+
+The final step in vesicle transport is fusion of vesicle with the target compartment.This is brought about by SNARE proteins. 
+There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type.
+In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment (A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs)~\cite{yoon2018snare}.
+
+\todo{schematic of snare regulatory network}
+In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
 %
-	 Rab GTPases are small proteins which occur in two forms: the membrane associated and active
-		GTP bound form, and the cytosolic and inactive GDP bound forms. 
-		%
-		Different compartments of the
-		cell are associated with a different type of Rab protein. In their active form, Rabs recruit many
-		downstream proteins, including tethering complexes, fusion regulators, motor proteins, sorting
-		adaptors, etc, to the membrane they are associated with. 
-		%
-		The proteins that are recruited by active
-		Rabs are called Rab effectors.
-		%
-		Rab activity is controlled by two proteins: GEFs turn Rabs on and
-		GAPs turn them off. 
-		%
-		Each Rab has its own specific GEF and GAP. In some cases, GEFs and GAPs
-		themselves can be Rab effectors, thus generating feed-forward and feedback loops. 
-		%
-		In their cytosolic, inactive form, Rabs are complexed with GDI proteins, and it is in this form that Rabs are presented to membrane bound GEFs for activation~\cite{muller2018molecular}
-
-	 \textbf{Tethering complexes} sequester vesicles to their target compartments and regulate SNARE
-		proteins, which enable vesicle fusion. 
-		%
-		Tethers are believed to bind to SNAREs and function as
-		chaperones for SNARE complex assembly which is the ultimate step in membrane fusion. 
-		%
-		There are two types of tethering complexes: multi subunit tethers and long coiled-coil tethers:
-%		
- Coiled coil tethers are long, single subunit proteins. 
-			%
-			These tethers are believed to bind the
-			vesicle on one end and the target compartment on the other end, thereby bridging the two before
-			fusion.
-			%
-			A clear mechanism for action of these tethers is missing, but based on their interactions with
-			other proteins of the traffic machinery, some hypotheses as to their mechanism of action have been
-			put forth. 
-			%
-			Golgins, coiled coil tethers that are anchored at the Golgi by a transmembrane domain, contain a large number of binding sites for Rab GTPases. 
-			%
-			Thus, golgins might capture vesicles by
-			binding vesicle-associated Rab proteins. 
-			%
-			Golgins also contain domains which can sense membrane
-			curvature, which they could be using to recognize vesicles. 
-			%
-			They might also be interacting directly
-			with vesicle SNAREs~\cite{baker2016chaperoning}.
-		%	
-			Multi-subunit tethering complexes (MTCs) are composed of three or more different
-			subunits.
-			%
-			MTCs are known to interact with vesicle coat proteins, Rab GTPases, SNAREs and SM proteins.
-			%
-			For example, the HOPS complex, which is required for homotypic (fusion of two identical
-			membranes) and heterotypic fusion in the endo-lysosomal system, was shown to tether membranes
-			through its interactions with the membrane-associated Rab GTPase Ypt7, acidic phospholipids and
-			SNAREs. 
-			%
-			The HOPS complex binds both individual SNAREs and SNARE complexes. It also
-			seems to protect assembling trans-SNARE complexes from premature disassembly. 
-			%
-			Another example is given by the Dsl1 complex, which is anchored to the ER membrane through interactions
-			with t-SNAREs. 
-			%
-			At the other end, the Dsl1 complex contains multiple binding sites for COPI
-			(vesicle coat that is present on vesicles produced by the Golgi). 
-			%
-			This structure suggests that the Dsl1
-			complex functions as a tether connecting COPI-coated vesicles to their target organelle, the ER~\cite{baker2016chaperoning}.
-
-	 \textbf{Fusion of vesicle with the target compartment} is brought about by SNARE proteins. 
-	%
-	SNAREs
-	are defined by a 60- to 70-residue SNARE motif. Most SNAREs are anchored to the membrane by
-	their C-terminal transmembrane helices. 
-	%
-	The formation of a productive SNARE complex requires
-	the formation of a four-helix bundle containing four different SNARE motifs. Usually, one of these
-	motifs is contributed by the SNARE on the vesicle membrane (v-SNAREs), and the other three
-	motifs by SNAREs on the membrane of the tartget compartment (t-SNAREs). 
-	%
-	Alternatively, they
-	can be defined by their amino acid sequences as R-, Qa-, Qb-, and Qc-SNAREs. A few SNARE
-	proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs.
-	%
-	Most v-SNAREs are RSNAREs, and most t-SNAREs are Q-SNAREs~\cite{yoon2018snare}.
-
-Many SNAREs also have N-terminal domains that regulate SNARE complex assembly and/or
-interact with other parts of the vesicle fusion machinery. 
-%
-Qa-SNAREs have an amino terminal
-domain called the Habc domain, which can fold back on the SNARE domain and hold the QaSNARE
-in an inactive state. 
-%
-This inactivated state is stabilized by interactions with SM proteins~\cite{yoon2018snare}.
-
-A subset of R-SNAREs (the longin SNAREs) possess an amino-terminal domain called the longin domain. 
-%
-In addition to regulation of SNARE activity as in the case of the Qa-SNARE Habcdomains,
-these longin domains also regulate the localization of longin SNAREs through their
-interaction with adaptor proteins~\cite{daste2015structure}.
-
-Different vesicle-target compartment pairs in the cell are associated with unique SNARE
+\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
+\newline SM proteins have multiple modes of SNARE regulation: 
+\begin{itemize}
+	\item SM proteins can hold
+	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
 	complexes.
 	%
-Membrane fusion converts the trans-SNARE complex (v- and t- SNAREs on opposite
-membranes) into a cis-SNARE complex (both v- and t- SNAREs on the same membrane).
-Disassembly of cis-SNARE complexes requires Sec17 and Sec18 (the yeast SNAP and NSF
-protein, respectively). 
-%
-This process requires energy which is released by the hydrolysis of ATP.
-
-\textbf{SNAREs are regulated by SM proteins}, which have three modes of action: SM proteins can hold
-the Qa-SNAREs in an autoinhibited state and prevent or postpone their assembly into SNARE
-complexes.
-%
-Secondly, some SM proteins have been seen to act as a template upon which a halfzippered
-complex between the Qa- and R-SNAREs (an early SNARE complex intermediate) can
+	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
 	form.
 	%
-In this mode, by choosing an R-SNARE located on the opposite membrane, SM proteins
-could be imposing a filter inhibiting the formation of futile cis-SNARE complexes and promoting
-trans-SNARE complexes.
+	\item Finally, SM proteins bind the fully assembled
+	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
 	%
-Finally, SM proteins bind the four-helix bundles formed by assembled
-SNARE complexes.
-%
-This mode of binding of SM proteins might protect assembled SNARE
-complexes from premature disassembly by NSF and SNAPs and/or might stimulate fusion directly~\cite{baker2016chaperoning}.
-%
-SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
+	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
+\end{itemize}
 
 \textbf{Major paths in the vesicle transport network}:
-Molecules traverse the cell in a series of vesicles, and there are two major such routes of transport in all eukaryotic cells.
+\todo{schematic of intracellular compartments and  major routes}
+Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
 %
-	The secretory route takes proteins from the ER, their site of production, to the plasma membrane, from where they are secreted out of the cell.
+\begin{itemize}
+	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
 	%
-	 Cargo proteins leave the ER in COP2 coated vesicles which fuse with the Golgi apparatus.
-	 %
-	  The golgi apparatus is where proteins get modified, for example by the addition of carbohydrate side-chains. 
-	  %
-	  Subsequently, proteins destined for secretion are packaged into clathrin coated vesicles which fuse with the plasma membrane, thus releasing their contents to the outside of the cell\cite{alberts2002molecular}.
-	  %
- The endocytic routetakes proteins from the outside of the cell through the plasma membrane to the endocytic compartments, where they are digested. 
- %
- Cargo from the outside of the cell is taken in in the form of clathrin coated vesicles which form at the plasma membrane. 
- %
- These vesicles fuse amongst themselves in a process called homotypic fusion to generate the early endosomal compartments. 
- %
- Early endosomes undergo changes in their composition due to ongoing vesicle traffic and maturee into late endosomes. 
- %
- This maturation is concomitant with a switch the Rab protein they are associated with; the Rab5 associated early endosomes mature into Rab7 associated late endosomes\cite{rink2005rab}.
-Late endosomes then fuse with lysosomes, where all its contents get digested\cite{pryor2009delivery}.
-%
+	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
+\end{itemize}
 Other paths are used for cross talk between the secretory and the endocytic routes.
-For example, vesicles are sent from the TGN (Trans-Golgi network) to the early and the late endosomes to transport enzymes, and vesicles are sent back from the endocytic compartments to the TGN to recycle sorting receptors\cite{progida2016bidirectional}.
-Also recently, evidence for unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi.
+For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}.
+Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus.
 The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.
+
 %
@@
 %
-The constraints imposed by cell biology is incorporated in the  annotations of the graph.
+The constraints imposed by cell biology are incorporated in the  annotations of the graph.
 
@@
 %
-The target vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
+The transport vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
 % 
@@
 %
-In our abstracted model, we will assume that cell is in a steady state. 
+In our model, we assume that the cell is in steady state.
+As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
+Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
 %
-The compartment's composition does not evolve over the short times' scales.
-%
-Therefore, the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
-%
-This abstraction is supported by the cell biology as on the scale of seconds and minutes the molecular composition actually remains the same. 
-%
-In this paper, we refer to the steady state of the cell as stability condition over the annotated graph.
+In this paper, we refer to the steady state of the cell (refered as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.
 
@@
 %SNAREs are of two types (known as Q and R in the cell biology iterature) and 
-Vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE between transfer vesicle and target compartment. 
+Vesicle fusion requires a pairing of 3 Qsnares and 1 Rsnare that are distributed between the transfer vesicle and the target compartment. 
 %For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
@@
 %
-Only a particular pair of Q and R SNAREs are allowed to fuse with each other.
+Not all sets of Q and R SNAREs are allowed to fuse with each other.
 %
-Without loss of generality, we assume equal numbers of Q and R SNARE types.
+In the model, we assume that the cell has an equal number of Q and R SNARE types.
 %
@@
 \textbf{Molecular regulation:} 
-Fusion takes place only if the SNARE types involved in the vesicle and compartment must both be in an active state.
+Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
 %We assume that for fusion to occur, the pair of 
@@
 %
-In our abstract model, we create a set of variations of different kind of molecular regulations.
+In our abstract model, 
+we create a hierarchy of models for varying degrees of regulation of SNARE activity.
+%we create a set of variations of different kind of molecular regulations.
 %
@@
 
-\subsection{Interesting properties of VTS}
+\subsection{Graph connectivity is an interesting and accessible property of the VTS}
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
-Suppose we are given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model.
-This information is then sufficient to check the following properties, which summarise the cell-biological constraints described above:
-\begin{enumerate}
-	\item We can determine which molecules are active on every compartment or vesicle.
-	\item For every vesicle fusing to a compartment, we can determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
-	\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we can verify that there is no pairing of active molecules on the
-	vesicle and compartment that could drive their fusion.
-	\item We can verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set.
-This is the steady state condition.
-In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
-\end{enumerate}
+Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
+The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments.
+But we do not know if this information is complete.
+In order to assess how completely we know the VTS, we need easily readable benchmarks.
 
-The biological problem often boils down to such an analysis.
-A cell biologist might determine which molecules flow between which set of compartments, and biochemical experiments could be used to see how these molecules activate one another.
-We can then ask: is this a complete and consistent description?
-That is, do all the required properties listed above hold, given what the experimentalists have told us?
-It is often the case that biological data is missing.
-For example, only a few of the dozens of molecules involved in real VTSs have been mapped out.
-Therefore, it is extremely likely that the description provided by the cell biologist is incomplete.
-We can use our model to find out which properties have failed to hold, and thus prescribe new experiments in order to fill in the missing information.
+\todo{SA: Need more text on the importance and relevance of PROPRTY OF CONNECTIVITY}
+One such benchmark is provided by our result about connectivity of the VTS graph.
+Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected.
+For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph.
+Therefore the underlying undirected graph is 2-connected.
+From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity.
+When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected.
+And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].
 
-Can we find a simple test to see whether any information is missing, given the experimental data?
-We have shown that graph k-connectedness furnishes precisely such a test \cite{shukla}.
-If the data provided by cell-biologists, suitably represented as a graph, does not have a certain degree of connectivity, this implies that some biological data has been missed.
-(The converse is not true: even if the required connectivity does hold, there might of course be more information missing.)
-
-Our result about k-connectedness being a useful test of missing information \cite{shukla} was obtained using SAT solvers for graphs up to a certain size, and a certain number of molecules.
-This was due to limitations in how we encoded the problem.
-Here we present a much more natural encoding that allows our result to be extended to graph sizes and molecule numbers that are typical of those found in real cells.
+\todo{SA: We need not specify Synthesis here. Only connectivity use next subsection to build this. SM: but this is the para where we explain why connectivity is interesting an biological property}
+The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
+%
+In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
+%
+These predictions are intended to be used as guides for future experiments. 
+%
+A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
+%
+Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.
 
@@
 %
-Since a VTS is a transport graph, it is but natural to formally model
-VTS as graphs (as used in computer science) with their nodes denoting
-compartments and labeled edges denoting transport vesicles with labels
-denoting the set of molecules being transported. The pairing mechanism
-can be represented as matching tables over sets of molecules.
+
 % i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
 %
-Given such a graph model of VTSs and their properties, such as
-stability condition and fusion rules, can be formally defined as
-constraints over graphs and uninterpreted Boolean functions.
+
 %
@@
 %Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
+\subsection{Synthesis of VTS }
+The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
+%
+Completing the vesicle traffic network is a difficult task for the many important reasons: 
+\begin{enumerate}
+	\item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.
 
-\subsection{Synthesis of VTS:}
-Although vesicle-mediated traffic was discovered decades ago~\cite{wells2005discovery}, the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
-%
-Completing the vesicle traffic network is a difficult task for the following reasons: 
-\begin{enumerate}
-	\item The core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.
-
-	\item Although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
-
-	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.
+	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
 
 	\item Molecules can have redundant routes within the cell ~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
+	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.
 
@@
 %
-At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
+At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
 
+%\subsection{Synthesis of VTS:}
 %
@@
 %
-In order to even attempt to complete a given partial VTS we have to agree on the properties that every complete VTS should follow in spite of basic constraints. 
+In order to attempt to complete a given partial VTS we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
 %
@@
 
-%Previous analyses of VTS have mostly been based on sampling approach~\cite{mani2016wine, mani2016stacking}. 
-%%
-%In these analyses, vesicle traffic is
-%modeled as a dynamical system. 
-%%
-%The traffic rule specifies how the system transitions from one
-%time point to the next. 
-%%
-%Given a traffic rule and an initial condition, the system is evolved over time until a steady state is reached. By studying a large sample of randomly generated traffic
-%rules, such analyses can make statistical claims about vesicle traffic.
-%%
-%Hence making precise general prediction about the properties of vesicle traffic networks over all possible traffic rules, not just for a sampled subset is not possible.
-%%
-%SAT and SMT solvers are a perfect fit for this situation, solving combinatorial problems with their exhaustive nature of searching. 
-%%
-%These tools check a specified logical property
-%on every possible state of a model constructed using variables ranging over Boolean or any
-%finite discrete type.
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "main"
-%%% End:
+%\textbf{Biological Model of VTS}
+%

### 2019-01-16 vts-synth/src/main.cpp
Working version for PLOS2 graph Edge Synthesis

@@ -74,7 +74,7 @@ int main(int ac, char* av[])
 
     // Declare an options description instance which will be shown
     // to the user
-    options_description visible("VTS-Synth [version 0.0.1]. (C) Copyright 2017-2018 TIFR Mumbai. \nUsage: ./vts-synth [--options] [--variation arg] \n\nFunction types:\n  0. Arbitrary Boolean func: ackermannization. [default] \n  1. K-cnf with depth D. \n  2. Logic-gates AND OR. \n  3. Logic gate with unique arguments. \n\nSynthesis variation:\n  0. Default. \n  1. Edge synthesis.\n  2. Molecule synthesis.\n  3. K-Cnf.\n  4. Logic gates.\n  5. VTS repair.\n 6. Activate-deactivate");
+    options_description visible("VTS-Synth [version 0.0.1]. (C) Copyright 2017-2018 TIFR Mumbai. \nUsage: ./vts-synth [--options] [--variation arg] \n\nFunction types:\n  0. Arbitrary Boolean func: ackermannization. [default] \n  1. K-cnf with depth D. \n  2. Logic-gates AND OR. \n  3. Logic gate with unique arguments. \n\nSynthesis variation:\n  0. Default. \n  1. Edge synthesis.\n  2. Molecule synthesis.\n  3. K-Cnf.\n  4. Logic gates.\n  5. VTS repair.\n  6. Activate-deactivate");
     visible.add(general).add(variation).add(options);
 
 
@@ -229,8 +229,11 @@ int main(int ac, char* av[])
         v->use_z3_qbf_solver( f );
       }
     }
+
     VecsExpr qs;
+		std::cout << "Creating Prenexing of the Formula\n";
     auto prenex_f = prenex( f, qs );
+		std::cout << "Done Prenexing the Formula\n";
 
     /* Print the formaula in pcnf  Avoid printing now ! */
     //std::cout << "Prenexed f : " << prenex_f << "\n";
@@ -262,7 +265,7 @@ int main(int ac, char* av[])
     //bool timedout = false;
     std::future<int> future = std::async(std::launch::async, [](){ 
         // if ( flagA == false ) {
-        auto retVal  = system ("cd ./build/depqbf/examples;gtimeout 6000s ../depqbf --qdo --no-dynamic-nenofex  /tmp/myfile.qdimacs > /tmp/out.txt");
[…]

### 2019-01-16 vts-synth/src/vts-synthesis.cpp

@@ -277,14 +277,13 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
   
   //z3::expr inputCons = ctx.bool_val(true);
 
-  /** Known and Unknown Bit variables 
+  /** Known and Unknown Bit variables */
   z3::expr_vector knownNodes( ctx );
   z3::expr_vector knownActiveNodes( ctx );
   z3::expr_vector knownEdges( ctx );
   z3::expr_vector knownPresenceEdges ( ctx );
   z3::expr_vector knownActiveEdges( ctx );
   z3::expr_vector knownPairingMatrix( ctx );
-  */
   
   z3::expr_vector unknownN( ctx );
   z3::expr_vector unknownActiveN( ctx );
@@ -378,7 +377,7 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
     // auto edgeC =  atmost(unknownE, 1);
 //     auto edgeC = !at_least_two( unknownE );
     // auto edgeC = !at_least_three( unknownE );
-    auto edgeC = mk_le_k_bits( unknownE, 1);
+    auto edgeC = mk_le_k_bits( unknownE, 3);
     /*
     for ( unsigned i = 0; i < knownEdges.size(); i++ ) {
       std::cout << "known edge: " << knownEdges[i] << "\n";
@@ -414,9 +413,6 @@ z3::expr vts::vts_synthesis ( unsigned variation ) {
                     exists( listPairing4M,
                     exists( listReach, 
                             vtsCons && knownVarConstraint ))))));   
-
-    //   exists( listPairing4M, 
-
 
     auto cons = exists( listE, 
                  qvtsCons && kConnCons && edgeC ); 

### 2019-01-17 papers/journal/synth-table.tex
qbf mentioned in the related work section

@@
 
-		plos1-dia[3C]& 0.326 &$\infty$& 0.312 &$\infty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & -1 E, -1 AE, -1 AN. +1 E, +1 N. \\\hline
-		plos2-dia[4C] & 0.266 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
+		plos1-dia[3C]& 0.012 &$\infty$& 0.312 &$\infty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & -1 E, -1 AE, -1 AN. +1 E, +1 N. \\\hline
+		plos2-dia[4C] & 0.014 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
 		sub-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline

### 2019-02-27 papers/journal/prelim.tex
Added encodings for recahabilty for BMC implementation
asd

@@
-We will use lower case variables like $e,r,s$ etc to represent vectors of Boolean variables
-possibly indexed with multiple dimensions.
+We will use lower case variables like $e,r,s$ etc to represent vectors of
+Boolean variables, possibly indexed, with multiple dimensions.
 %
@@
 $\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
-collection of formulas.
+collection of formulas respectively.
 %
-We will use the variables and the operators to construct Boolean formulas to
+We will use the variables and operators to construct Boolean formulas to
 encode our problems.
 %
-An assignment is a map from variables in the formula to Boolean values.
+An assignment is a map from the variables in the formula to the Boolean values.
 %
@@
 The problem of finding a satisfying assignment for a Boolean formula is
-hard.
+known to be hard~\cite{sat-hard}.
 %
@@
 %
-The problem of finding satisfying assignment for QBFs is even harder problem.
+The problem of finding satisfying assignment for QBFs is even harder problem~\cite{qbf-hard}.
 %
@@
 %
-We will use SAT/SMT/QBF solvers to get the satisfying assignments.
+We will use BMC/SMT/QBF solvers to get the satisfying assignments.
 %
@@
 %
-A SAT solver typically implements conflict-driven clause learning(CDCL).
+A SAT solver typically implements conflict-driven clause learning(CDCL)~\cite{cdcl}.
 %
 The QBF solver add support of quantifiers by adding more rules for
-quantifiers.
+quantifiers~\cite{qbf}.
 

### 2019-02-27 papers/journal/encoding.tex
Partial encoding added

@@
 \subsection{SMT based encoding}
+\label{enc:smt}
 
@@
 \end{align}
-We fix first half as Q-SNAREs and rest as R-SNAREs and set diagonal blocks in pairing matrix to be 0's.
+We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs (and similarly R-SNAREs to R-SNAREs) in the pairing matrix to be 0's.
 %It reduces the search space.
 % Condition on $p_{kk'}$. \ashu{why???} .
+%\begin{align}
+%  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
+%  \tag{V6}\label{eq:c3}
+%\end{align}
+
 \begin{align}
-  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
+  \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \land y >= 3M/4)} \neg p(x,y)
   \tag{V6}\label{eq:c3}
@@
 %
-For example the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
+For examplei, the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
 %
 The index of the bitvector implicitly determines the corresponding molecule we are referring to.
-
-\begin{enumerate}
-	\item Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
-\end{enumerate}
-
+%
+Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
 %
@@
 %
-
-\textbf{Example 1} The variable bv\_e[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule M1 and M4 present.
+For example, the variable bv\_e[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule M1 and M4 present.
 
@@
 %
-For clarity, we will only present the stability encoding.
+Here, we will only present the stability encoding.  
+%
+Rest of the encoding are similar to that of the presented in~\ref{enc:smt}.
 
@@
 
-Now we can encode stability using the NOracle and say if there is an $m$-edge between $i$ and $j$, there is a $m$-path from $j$ to $i$ of length max w.
+We encode stability using NOracle and if there is an $m$-edge between node $i$ and $j$, there has to be a $m$-path from $j$ to $i$ of length maximum w.
 %
-We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
+%We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} bv\_e[i][j][q] \limplies NOracle(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}
 \end{align}
+
+%\begin{align}
+% \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
+ % \tag{S2}\label{eq:reachbmc2}
+%\end{align}
 

### 2019-02-27 papers/journal/model.tex

@@
 
-\textbf{Fusion condition in BMC and SMT:}
-$\pairs$ defines which molecules can fuse with which molecules.
-%
-Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
-%
-$\nodef$ and $\edgef$ are used to define activity of molecules on
-nodes and edges respectively.
-%
-A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
-$\nodef(k,\nlabel(n))$ is true.
-%
-A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
-$\edgef(k,M')$ is true.
-%
-We call $G$ {\em well-structured} if molecules $M$ is divided into
-two equal-sized partitions $M_1$ and $M_2$ such that
-$P \subseteq M_1 \times M_2$, and
-for each $(n,M',n') \in \edges$, $n \neq n'$, 
-$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
-%
-In other words, a well-structured VTS has no self loops, and 
-each edge carry only those molecules that are present in its source
-and destination nodes.
+% \textbf{Fusion condition in BMC and SMT:}
+% $\pairs$ defines which molecules can fuse with which molecules.
+% %
+% Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
+% %
+% $\nodef$ and $\edgef$ are used to define activity of molecules on
+% nodes and edges respectively.
+% %
+% A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
+% $\nodef(k,\nlabel(n))$ is true.
+% %
+% A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
+% $\edgef(k,M')$ is true.
+% %
+% We call $G$ {\em well-structured} if molecules $M$ is divided into
+% two equal-sized partitions $M_1$ and $M_2$ such that
+% $P \subseteq M_1 \times M_2$, and
+% for each $(n,M',n') \in \edges$, $n \neq n'$, 
+% $M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
+% %
+% In other words, a well-structured VTS has no self loops, and 
+% each edge carry only those molecules that are present in its source
+% and destination nodes.
 
-We will also consider several variations of the model.
-%
-For example, unique edge between two nodes, activity of molecules is
-not constrained by $\nodef$ and $\edgef$, etc.
-%
+% We will also consider several variations of the model.
+% %
+% For example, unique edge between two nodes, activity of molecules is
+% not constrained by $\nodef$ and $\edgef$, etc.
+% %
 
-\textbf{Fusion condition in QBF and synthesis:}
+% \textbf{Fusion condition in QBF and synthesis:}
 %
@@
 pairing relations have sets of four molecules such that three
-are of one type (??) and one is of another type (??).
+are of type $Q$ and one of type $R$ or vice versa.
 %
@@
 
+\ashu{Should be written bio people}
 Let us discuss rough sizes of the system and expected behaviors.
@@
 %contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
-
+%
 The VTS may transport a large number of molecules but the molecules that

### 2019-02-27 papers/journal/encoding.tex
Updated Fusion encoding for SMT
Fusion 2 encoding
Update on BMC

@@
 \begin{align}
-  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
-  \tag{V7}\label{eq:fuse1}  \\
-\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
+  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies 
+\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land
+\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land
+  \notag\\	
+	\Lor\limits_{l=1}^4 a_{j,m_l} \land p_{\{m_1,m_2,m_3,m_4\}})
+  \tag{V7}\label{eq:fuse1}  
+\end{align}
+
+\begin{align}
+	\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies
+\mspace{250mu}
+  \notag\\
+	\neg
+\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
+\land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
   \tag{V8}\label{eq:fuse2}  
@@
 %
-For examplei, the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
+For example, the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
 %
@@
 %
-%We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
+We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv.
+
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} bv\_e[i][j][q] \limplies NOracle(m, j, i, w)
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) == 1) \limplies NOracle(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}
 \end{align}
-
-%\begin{align}
-% \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
- % \tag{S2}\label{eq:reachbmc2}
-%\end{align}
 

### 2019-02-27 papers/journal/prelim.tex
Small fix

@@
 %
-We will use BMC/SMT/QBF solvers to get the satisfying assignments.
+We will use BMC,SMT and QBF solvers to get the satisfying assignments.
 %
@@
 %
-A SAT solver typically implements conflict-driven clause learning(CDCL)~\cite{cdcl}.
+A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{cdcl}.
 %

### 2019-02-28 papers/journal/encoding.tex
Activity ecoding update for SMT
Minor fixes
Fusion 2 encoding
Small fix

@@
 \begin{align}
-  \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \land y >= 3M/4)} \neg p(x,y)
+  \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
   \tag{V6}\label{eq:c3}
@@
 \Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land
-  \notag\\	
+  \notag \\
+	\qquad \qquad \qquad \qquad
 	\Lor\limits_{l=1}^4 a_{j,m_l} \land p_{\{m_1,m_2,m_3,m_4\}})
@@
 	\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies
-\mspace{250mu}
-  \notag\\
+\mspace{300mu}
+  \notag \\
+	\qquad \qquad \qquad \qquad
 	\neg
@@
 \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
+\mspace{50mu}
   \tag{V8}\label{eq:fuse2}  
@@
 \begin{align}
-   \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \limplies  \bigwedge_{m' \neq m} (p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv (\neg b_{i,j,q,m} \land\;\;\;\;  \bigwedge_{\mathclap{m' \neq m, p_{m,m'}}} \neg b_{i,j,q,m'})
+	\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies 
+	\notag \\
+	  \qquad \qquad \qquad \qquad
+	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})
   \tag{Aep}\label{eq:aep}
@@
 %
-Variables are not Boolean indexed with multiple dimensions but arrays of bitvectors of size $\mu$. 
+In the BMC encoding, variables are represented as an array of bit vectors of size $M$. 
 %
@@
 %
-For example, the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
+For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
 %
-The index of the bitvector implicitly determines the corresponding molecule we are referring to.
+Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
 %
-Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
+The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
 %
@@
 %
-For clarity, we consider both in the same amount and represent the first half of the bitvector as  Q-SNAREs and rest as R-SNAREs.
+For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
 %
-An edge in the system with M = 4 molecules is interpreted as a tag [M1, M2, M3, M4]. 
+An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
 %
-Where M1, M2 are Q-SNAREs and M3, M4 are R-SNAREs.
+Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
 %
-Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the molecule i.
+Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
 %
-For example, the variable bv\_e[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule M1 and M4 present.
+For example, the variable \texttt{bvEdge}[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present.
 
-Similarly, a node in the graph is also tagged as a bitvector of length M.   
+Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
 %
@@
 %
-Rest of the encoding are similar to that of the presented in~\ref{enc:smt}.
+Rest of the encoding are similar to the one presented in the Section~\ref{enc:smt}.
 
@@
 %
-Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific m if it exists. 
+Nondeterminism can be viewed as an oracle that encodes a correct $m$-path for a specific $m$ if it exists. 
 %
-We then use this path as a witness to ensures that stability is maintained for each outgoing molecule m on every edge E.
+We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
 %
@@
 %
-We use NOracle to guess the required path to encode the stability condition in VTS.
+We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
 %
-A naive implementation of NOracle is shown in~\ref{eq:reachbmc1}.
-%
-The constraint encodes that there is a $m$-path from node $i$ to node $j$ of maximum $w$ length.
-%there is a edge between $i^{\prime \prime}$ and
+A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m-path$ from node $i$ to node $j$ of maximum $w$ length.
+%there is a edge between $i^{\prime \prime}$ and01
 %$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
@@
 %
-It performs enumeration of $m$-${paths}_i^j$ of at most w length. 
+It performs enumeration of every $m-path$, $m$-${paths}_i^j$, of at most $w$ length. 
 %
-Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length w-1.
+Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length $w-1$.
 %by performing series of node hops till final node destination j is reached.
@@
 \begin{align}
-NOracle (m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} | {m-path}_i^j | = l
+\texttt{NOracle}(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} | {m-path}_i^j | = l
   \tag{S1}\label{eq:reachbmc1}
@@
 
-We encode stability using NOracle and if there is an $m$-edge between node $i$ and $j$, there has to be a $m$-path from $j$ to $i$ of length maximum w.
+We encode stability using \texttt{NOracle} and if there is an $m$-edge between node $i$ and $j$, there has to be a $m$-path from $j$ to $i$ of length maximum w.
 %
@@
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) == 1) \limplies NOracle(m, j, i, w)
+ \bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies NOracle(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}

### 2019-02-28 papers/journal/encoding.tex
Small fix

@@
 %
-A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m-path$ from node $i$ to node $j$ of maximum $w$ length.
+A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m$-$path$ from node $i$ to node $j$ of maximum $w$ length.
 %there is a edge between $i^{\prime \prime}$ and01
@@
 %
-It performs enumeration of every $m-path$, $m$-${paths}_i^j$, of at most $w$ length. 
+It performs enumeration of every $m$-$path$, $m$-${paths}_i^j$, of at most $w$ length. 
 %

### 2019-02-28 papers/journal/encoding.tex
Updated 6.3

@@
 %
-Nondeterminism can be viewed as an oracle that encodes a correct $m$-path for a specific $m$ if it exists. 
+Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
 %
@@
 %
-
 \subsubsection{Constraints for stability condition}
 %
-We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
+We use \texttt{NOracle} to guess the required path to encode the stability condition in VTS.
 %
@@
 %
-Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length $w-1$.
+Starting with exploring $m$-${paths}_i^j$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_i^j$ of length $w-1$ is explored.
 %by performing series of node hops till final node destination j is reached.
@@
 
-We encode stability using \texttt{NOracle} and if there is an $m$-edge between node $i$ and $j$, there has to be a $m$-path from $j$ to $i$ of length maximum w.
+We encode stability using \texttt{NOracle}. If there is an $m$-edge between node $i$ and $j$, there has to be a $m$-$path_i^j$ from $j$ to $i$ of maximum $w$ length.
 %
-We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv.
+The expression (\texttt{bv} $\unrhd$ $m$) extracts the $m^{th}$ bit of the bitvector \texttt{bv}.
 
 \begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies NOracle(m, j, i, w)
+	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies \texttt{NOracle}(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}
@@
 
-\subsection{The key improvement}
-The key improvement of SMT tool over the BMC is the
+\subsection{The key difference in the reachability encoding}
+The key improvement of the SMT tool over the BMC is the
 encoding of reachability.
@@
 %
-In SMT tool, reachability is encoded in two different
+In the BMC tool, reachability is encoded by enumerating all the possible paths using nondeterminism.
+%
+This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
+%
+Whereas in the SMT tool, reachability is encoded in two different
 ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.

### 2019-02-28 papers/journal/encoding.tex
Fixed the wrong sequence of the BMC and SMT encoding
Minor Fixes, Final push

@@
 
-In this section we will present the BMC, SMT and QBF based encoding of both the search and the synthesis problem.
+In this section we will present the SMT, BMC and QBF based encoding of both the search and the synthesis problem.
 We will start with the SMT based encoding and later present the contrast with the BMC encoding.
@@
 %
-We use \texttt{NOracle} to guess the required path to encode the stability condition in VTS.
+We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
 %

### 2019-03-02 papers/journal/experiments.tex
Fixed references and other latex LOG's, Fig and other issues continues

@@
 
-\textbf{{\sattool} (bounded model checker based tool)}:
+{\sattool} \textbf{(bounded model checker based tool)}:
 The enumeration encoding (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.

### 2019-03-02 papers/journal/intro.tex
Working version for PLOS2 graph Edge Synthesis
Fixed references and other latex LOG's, Fig and other issues continues

@@
 Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.
+
 \begin{figure}
-	\includegraphics[width=\textwidth]{ankitspaper_schem1.png}
-	\label{schematic}
+	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
 	\caption{Schematic of the vesicle transport system.
@@
 Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment.
-At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.
-}
+At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
+    \label{fig:vts}
 \end{figure}
 
-\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{schematic}.
+\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
 %
@@
 
-\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\cite{schematic}.
+\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
 

### 2019-03-02 papers/journal/prelim.tex
Fixed references and other latex LOG's, Fig and other issues continues

--- 2019-02-27 papers/journal/prelim.tex
@@
 %
-The problem of finding a satisfying assignment for a Boolean formula is
-known to be hard~\cite{sat-hard}.
+The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
 %
@@
 %
-The problem of finding satisfying assignment for QBFs is even harder problem~\cite{qbf-hard}.
+The problem of finding satisfying assignment for QBFs is even harder problem~\cite{arora2009computational}.
 %
@@
 %
-We will use BMC/SMT/QBF solvers to get the satisfying assignments.
+We will use BMC, SMT and QBF solvers to get the satisfying assignments.
 %
@@
 %
-A SAT solver typically implements conflict-driven clause learning(CDCL)~\cite{cdcl}.
-%
-The QBF solver add support of quantifiers by adding more rules for
-quantifiers~\cite{qbf}.
+A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
+%1
+The QBF solver add support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
 

### 2019-03-10 papers/journal/encoding.tex
removed the recahability disccusion as a seperate subsection
moved section 6.3 and 6.4 to subsection of the 6.2

@@
 
-\subsection{The key difference in the reachability encoding}
+\subsubsection{The key difference in the reachability encoding}:
 The key improvement of the SMT tool over the BMC is the
@@
 
-\subsection{BMC and SMT problems for different variants}
+\subsubsection{BMC and SMT problems for different variants}
 %\ankit{Bring model variant table here}

### 2019-03-10 papers/journal/encoding.tex
Improvement in Univ conddition section 6.3

@@
 %
-\subsubsection{Constraints for stability condition}
+
+\textbf{Constraints for stability condition}
 %
@@
 \subsection{Universal condition}
+%
 Recall that the specification for universal condition~\ref{eq:univcond} requires quantifier alternation. 
@@
 % 
-\todo{SA: Rewrite completely}But it is still possible to encode the universal condition~\ref{eq:univcond} as a SAT or SMT problem.
+Although, it is possible to encode the universal condition~\ref{eq:univcond} as a SAT or SMT problem.
 %
-We have implemented a SAT version with the current encoding of the same.
+There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
+%Which may blow up the formula size for the solver to solve.
+% 
+As an experiment we have implemented a trivial SMT version of the universal problem extending the current SMT encodings.
 %
@@
 %
-This may blow up the formula size for the solver to solve.
 
@@
 %
-The table~\ref{tab:satqbf-graph}, shows results of search result of universal condition for N = 5, 3-connected graphs.
+The table~\ref{tab:satqbf-graph}, shows results of search result of universal condition for N = 4, 3-connected graphs.
 The SAT version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).

### 2019-03-10 papers/journal/encoding.tex
Improvement in Univ condition section 6.3

@@
 
-\textbf{Constraints for stability condition}
+\subsubsection{Constraints for stability condition}
 %
@@
 \subsection{Universal condition}
+\label{enc:univ-cond}
 %
@@
 % 
-As an experiment we have implemented a trivial SMT version of the universal problem extending the current SMT encodings.
+As an experiment, we have implemented a direct SMT version of the universal problem extending the current SMT encodings.
 %
@@
 %
-The table~\ref{tab:satqbf-graph}, shows results of search result of universal condition for N = 4, 3-connected graphs.
-The SAT version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
+The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
+%
+The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
 %
@@
 %
-We will use the same encoding for the VTS as discussed in the QBF subsection.
+We will re-use the QBF encodings for the input VTS as described in the Section~\ref{enc:univ-cond}.
 %

### 2019-03-10 papers/journal/model.tex
Improvement in Univ condition section 6.3

@@
 The VTS may transport a large number of molecules but the molecules that
-are \todo{SA: commented line above} relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
+are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
 %

### 2019-03-10 papers/journal/conclusion.tex
Improvement in the Related work section and changed the TODO to the respective work

@@
 It will allow us to predict behaviors after the perturbations in the VTSs
-and more ways to test the predicted synthesis results.
+and more ways to test the predicted synthesis results.\\
 
-\todo{SA: Rough outline of the answers needed in the future work section}
-1. why this tool was biologically helpful?
+\ankit{A rough outline of the answers needed in the future work section}
+\begin{enumerate}
+  \item why this tool was biologically helpful?
         \begin{itemize}
@@
         \end{itemize}
+  \item What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
+\end{enumerate}
 
-2.  What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
-\\
 \textbf{Encode Dynamic behaviour of the VTS:} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation.

### 2019-03-10 papers/journal/intro.tex
Improvement in the Related work section and changed the TODO to the respective work

@@
 
-\todo{schematic of snare regulatory network}
+\somya{schematic of snare regulatory network}
 In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
@@
 
+\somya{schematic of intracellular compartments and  major routes}
 \textbf{Major paths in the vesicle transport network}:
-\todo{schematic of intracellular compartments and  major routes}
 Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
@@
 \subsection{Graph connectivity is an interesting and accessible property of the VTS}
+\ankit{This section requires serious work and best written by Mukund.}
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
@@
 
-\todo{SA: Need more text on the importance and relevance of PROPRTY OF CONNECTIVITY}
+\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
 One such benchmark is provided by our result about connectivity of the VTS graph.
@@
 
-\todo{SA: We need not specify Synthesis here. Only connectivity use next subsection to build this. SM: but this is the para where we explain why connectivity is interesting an biological property}
+\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
+\somya{But this is the para where we explain why connectivity is interesting an biological property}
 The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 

### 2019-03-10 papers/journal/problem.tex
Fixed references and other latex LOG's, Fig and other issues continues
Improvement in the Related work section and changed the TODO to the respective work

@@
 
- \todo{A dummy template} \textbf{QBF search problem:}
+\ankit{This is a dummy template. need a rewrite.} \textbf{QBF search problem:}
 For a given $k$, size $\nu$, and molecule number $\mu$,

### 2019-03-10 papers/journal/related.tex
qbf mentioned in the related work section
Improvement in the Related work section and changed the TODO to the respective work

@@
 
-One of the prominent areas of application of SAT/SMT solvers is modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
+One of the prominent areas of application of SAT and SMT solvers is modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
 %
-The gene regulatory network question is encoded into a Boolean satisfiability problem and then SAT and SMT solvers are used to solve the generated formula. 
+The gene regulatory network question is encoded either directly as a Boolean satisfiability problem or in addition with the combinations of background theories.
 %
-The~\cite{rosenblueth2014inference, batt2010efficient, dunn2014defining} use symbolic SAT solving approach whereas~\cite{giacobbe2015model, yordanov2016method} present an SMT based encoding of the problem.
+The generated formula is then solved with the help of a SAT solver. 
 %
-We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system. 
+The~\cite{rosenblueth2014inference} uses symbolic model checking approach on the qualitative
+models of regulatory networks.
 %
-To our best knowledge this series of work is the first application
-of formal methods to vesicle traffic networks.
+Whereas,~\cite{dunn2014defining}  uses symbolic, SAT-based approach on the Boolean network model. 
+%
+The~\cite{giacobbe2015model, yordanov2016method} presents an SMT based encoding of the problem based on the presented Boolean model.
+%
+
+We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system (VTS). 
+%
+%Unlike the GNR, not many  VTS
+We have presented both SAT and SMT based encoding for our Boolean model of the VTS.
+%
+We have also introduced the use of QBF solvers and it's encoding in this context.
+% 
+To our best knowledge our work is the first application
+of formal methods to the vesicle traffic networks.
 

### 2019-03-10 papers/journal/intro.tex
added a VTS fig: will improve this soon

@@
 	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
-	\caption{Schematic of the vesicle transport system.
-Steps involved in vesicle transport between two compartments; a source and a target compartment are shown.
-The symbols used for different molecules involved in vesicle traffic are explained in the key.
-At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins.
-Here, the different colours indicate different types of cargo and adaptor proteins.
-Coat proteins are recruited to the forming vesicle by adaptor proteins.
-Note here that a single type of coat protein can interact with multiple types of adaptor proteins.
-Subsequently, the vesicle is pinched off at its neck by dynamin.
+	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
+	%
+	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
+	%
+	Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
+	%
+	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. 
+	%
 	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment.
@@
 
-\subsection{Graph connectivity is an interesting and accessible property of the VTS}
+\subsubsection{Graph connectivity is an interesting and accessible property of the VTS}
 \ankit{This section requires serious work and best written by Mukund.}
@@
 %
-Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.
+Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
 
+\ankit{Added this as a template. Will change it soon.}
+\begin{example}
+%
+In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
+%
+Molecules are numbered 0-7.
+%
+In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
+%
+Every molecule on the node is active.
+%
+The activity of the molecules on an edge are controlled
+by presence of the other molecules on the edge.
+%
+On the right side of the figure, we show the pairing matrix.
+%
+An entry 1 represents pairing between molecules.
+%
+$\times$ represents no pairing.
+%
+Rows corresponds to the labels of edges, and
+columns corresponds to the labels of nodes.
+%
+Every molecule flows on a cycle, ensuring steady state.
+%
+This is a 3-connected graph.
+\end{example}
+
+\input{pm-1-matrix}
 %\subsection{Modeling and Symbolic Analysis of VTS: An Overview}

### 2019-03-10 papers/journal/encoding.tex
added the synthesis text for 6.3 Synthesis encoding

@@
 \subsection{Synthesis of VTS}
-%In this section, we will present our synthesis method for
-%the synthesis problems.
+In this section, we will present our synthesis method for
+the synthesis problems.
+%
+We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
+%
+Whereas properties like stability and connectivity discussed in the previous sections may not.
+%
+Here, we use these two properties against which we perform our synthesis. 
+%
+The encoding can be easily extended to accommodate other interesting properties.
 

### 2019-03-11 papers/journal/synth-dia.tex
Added synthesis dia (just template)

\begin{figure}[t]
	\centering
	%\begin{minipage}{0.45\linewidth

\begin{tikzpicture}[->,>=stealth',auto,node distance=4cm,
  thick,main node/.style={rectangle,draw}]
  	\begin{scope}[]
  \node[main node] (pm) {PM { \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
  \node[main node] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
  \node[main node] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};

  %le <-> pm
  \path (le) edge[bend right=30] node [above] {Qb7 Qc7} (pm);
  %ee -> le
  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7, Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=30] node [above] {\^{R3}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  \end{scope}

  \begin{scope}[xshift=2cm,yshift=-1.0cm]
  \node[main node,text width=2.0cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2 ... } \^{Qbc7}}};
  \node[main node, text width=2.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
  \node[main node] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8} ...}};

  %le <-> pm
  \path (le) edge[bend right=30] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

  %le <-> ee
  {\color{red} { \path (le) edge[bend right] node [below,rotate=70] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
  }}
  %ee -> le
  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7, Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=30] node [above] {\^{R3, {\color{blue} { \textbf{\^{Qa2,}, \^{Qa7}, \^{R2}}}}}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  \end{scope}
 \end{tikzpicture}
  \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}
\end{figure}

### 2019-03-11 papers/journal/synth-dia.tex
use subcaption to put fig along side

@@
 \begin{figure}[t]
-	\centering
+%	\centering
 	%\begin{minipage}{0.45\linewidth
+ \begin{subfigure}[b]{0.49\linewidth}
 
-\begin{tikzpicture}[->,>=stealth',auto,node distance=4cm,
+	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.0cm,
 	  thick,main node/.style={rectangle,draw}]
-  	\begin{scope}[]
-  \node[main node] (pm) {PM { \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-  \node[main node] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-  \node[main node] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};
+	 % 	\begin{scope}[]
+	  \node[main node, text width=1.5cm] (pm) {PM { \^{Qa5} 
+	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
+	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
+	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};
 
@@
 	  %ee -> le
-  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7, Qbc7,R7} (le);
+	  \path (ee) edge[bend right, text width=3.0cm] node [below,rotate=65] {\^{R8},Qa7, Qbc7,R7} (le);
 
@@
 	  \path (ee) edge[bend left=30] node [above] {\^{R3}} (pm);
-  \path (pm) edge[bend left=30] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
-
-  \end{scope}
-
-  \begin{scope}[xshift=2cm,yshift=-1.0cm]
-  \node[main node,text width=2.0cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2 ... } \^{Qbc7}}};
-  \node[main node, text width=2.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
-  \node[main node] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8} ...}};
+	  \path (pm) edge[bend left=30, text width=2.5cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
+	\end{tikzpicture}
+  \end{subfigure}%
+ % \end{scope}
+%  \vspace{1.2cm}
+  \begin{subfigure}[b]{0.49\linewidth}
+	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.0cm,
+	  thick,main node/.style={rectangle,draw}]
+	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
+	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
+	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
+	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
 
@@
 	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
-
-  \end{scope}
+	 % \end{scope}
 	 \end{tikzpicture}
+  \end{subfigure}%
   \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}

### 2019-03-11 papers/journal/synth-dia.tex
Improved image for synthesis

@@
 
-	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.0cm,
+	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
 	  thick,main node/.style={rectangle,draw}]
@@
 	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};
+	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};
 
 	  %le <-> pm
-	  \path (le) edge[bend right=30] node [above] {Qb7 Qc7} (pm);
+	  \path (le) edge[bend right=55] node [above] {Qb7 Qc7} (pm);
 	  %ee -> le
-	  \path (ee) edge[bend right, text width=3.0cm] node [below,rotate=65] {\^{R8},Qa7, Qbc7,R7} (le);
+	  \path (ee) edge[bend right=32, text width=2.0cm] node [below,rotate=55] {\^{R8},Qa7, Qbc7,R7} (le);
 
 	  %pm <-> ee
-	  \path (ee) edge[bend left=30] node [above] {\^{R3}} (pm);
-	  \path (pm) edge[bend left=30, text width=2.5cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
+	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
+	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
 	\end{tikzpicture}
@@
   \begin{subfigure}[b]{0.49\linewidth}
-	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.0cm,
+	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
 	  thick,main node/.style={rectangle,draw}]
 	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
-	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
+	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
 	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
-	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
+	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};
 
 	  %le <-> pm
-	  \path (le) edge[bend right=30] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
+	  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
 
 	  %le <-> ee
-	  {\color{red} { \path (le) edge[bend right] node [below,rotate=70] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
+	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
 	  }}
 	  %ee -> le
-	  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7, Qbc7,R7} (le);
+	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8},Qa7, Qbc7,R7} (le);
 
 	  %pm <-> ee
-	  \path (ee) edge[bend left=30] node [above] {\^{R3, {\color{blue} { \textbf{\^{Qa2,}, \^{Qa7}, \^{R2}}}}}} (pm);
+	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {\^{R3, {\color{blue} { \textbf{\^{Qa2}, \^{Qa7}, \^{R2}}}}}} (pm);
 	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    

### 2019-03-12 papers/journal/property.tex
added QBF section and attached Synthesis encodings to it
ads

--- 2018-11-09 papers/journal/property.tex
@@
-The conjecture relates graph-connectedness to a particular variation of SNARE pairing and regulation rules of the VTS.
+We analyze the model against our desired properties.
 %
-We are interested in the following two type of properties of the transport graph:
+Since in biology there are are no declared specifications or properties,
+we conjecture some properties that appear to be true in all known
+biological systems.
+%
+In this paper, we choose graph connectedness to be a key property.
+%
+We will also seek two kinds of questions give the property.
+
+% %
+% In this paper,
+% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
+% regulation rules of the VTS.
+% %
+% We are interested in the following two type of properties of the transport graph:
 
 \begin{enumerate}
-\item Existential condition:
-%the structural connectedness of the transport graph required for the system driven by a particular set of rules. 
-structural connectedness of a transport graph which satisfies the stated set of rules.
+\item {\em Existential condition:}
+if there is a VTS that satisfies the connectedness property.
 
-%there is a transport graph with the structural connectedness which satisfies the stated set of rules.
-
-%that a transport graph satisfies driven by a particular set of rules. 
-%And we are interested in the least one.
-
-\item Universal condition: 
-%every graph with the structural connectedness satisfies the stated set of rules. 
-the structural connectedness that ensures every transport graph with that fundamental structure satisfies the stated set of rules. 
-%The goal is to find the minimum graph connectivity that satisfies sufficient condition.
+\item {\em Universal condition:}
+  if there is a connectedness property that is satisfied by each valid VTS.
 \end{enumerate}
 
-The goal is to find the minimum graph connectivity that satisfies each of these condition.
+The goal is to find the minimum graph connectivity properties that for each of the condition.
 
-%We express both these conditions as assertions in our program.
+% In our program, the rules VTS needs to follow 
+% %
+% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
+% %
+% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
+% %
+% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
+% %
+% We will show in later sections how we encode these Boolean functions.
 
-\subsubsection{Checking existential conditions} 
-In our program, the rules VTS needs to follow 
+\subsubsection{Search for existential condition} 
 %
-%are we represent the stability, fusion, SNARE pairing and regulation rules, and the connectedness property that the system needs to follow, as 
+% To ensure that k-connectedness is an existential condition,
 %
-are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
+We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
 %
-Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
-%
-We use these functions to define the assertion that characterizes the existential condition to be checked. 
-%
-We will show in later sections how we encode these Boolean functions.
-
-To ensure that k-connectedness is an existential condition, we have to find a k-connected graph that satisfies all the rules (and constraints) of the system. 
-%
-We also have to ensure that the particular k is the least one. 
+We also aim to find the minimum $k$. 
 %
@@
 %
-To find a k-connected graph (G) we specify our property as a query for the existence of a model for a conjunction of the formula representing stability, fusion and specific graph connectivity constraint.
+To find a k-connected graph we specify our property as a query for the existence
+of a model for a conjunction of the formula representing stability, fusion and specific
+graph connectivity constraint. 
 %
-
-\begin{align*}
-  &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)} 
-\end{align*}
-
-We will start with the value of k = 1 and check for the satisfiability of the above formula.
+% \begin{align*}
+%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
+%  \tag{E}\label{eq:existcond}
+% \end{align*}
 %
-In case the formula is satisfiable the procedure terminates and we report the value of k. 
+We will start with the value of $k = 1$ and check for the satisfiability of the formula.
 %
-If the formula is not satisfiable we increment the k by 1 and perform the same procedure. 
+In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
 %
-In this way, we ensure that the reported k is the minimum connectivity of the VTS that satisfies the existential condition.  
+If the formula is not satisfiable we increment the $k$ by $1$ and perform the same procedure. 
+%
+In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
+satisfies the existential condition.
+%
 % Used E as edge and L_e L_n as label for node and the edge,
 
-\subsubsection{Checking universal conditions}
-
-Similarly, for the conjecture that k-connectedness is a universal condition for the VTS, we have to ensure that every graph of k-connected structure satisfies all the rules (and constraints) of the system.
+\subsubsection{Search for universal problem}
 %
-We also have to ensure that the particular k is the least one. 
+% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
+For some $k>0$,
+we have to ensure that every graph of $k$-connected structure satisfies all
+the rules of the system.
+%
+We also aim to find the minimum $k$. 
+% We also have to ensure that the particular k is the least one. 
 %
 This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
-
-\begin{align*}
-  & \forall G \, \texttt{Connectivity(k)} \implies  \exists
-                        f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
-\end{align*}
-
-Note that the specification of this requires quantifier alternation. 
+%
+% \begin{align*}
+%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
+%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
+%   \tag{U}\label{eq:univcond}
+% \end{align*}
+%
+We will use the same procedure as the existential condition to ensure the k to be the least one.
+%
+The formula for the problem has quantifier alternation. 
 %
@@
 %
+We need a QBF solvers for such queries.
+%
 %To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.
-We will use the same procedure as the existential condition to ensure the k to be the least one.
 

### 2019-03-12 papers/journal/synth-dia.tex
Minor update on dia

@@
 	 % 	\begin{scope}[]
-	  \node[main node, text width=1.5cm] (pm) {PM { \^{Qa5} 
+	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { \^{Qa5} 
 	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};
+	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
+	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { \^{Qa8} \^{Qb8} \^{Qc8}}};
 
@@
 	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
-	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
-	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};
+	  \node[main node,text width=1.5cm] (pm) {\textbf{PM:} {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
+	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
+	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {\textbf{LE:} {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};
 

### 2019-03-12 papers/journal/problem.tex
SMt and BMC

@@
 This section will present the different search problems of VTS.
+%
+We categorize the search problems into three different categories, search problem to solve the existential condition, search problem for universal condition and performing synthesis on the incomplete VTS.
 
 \subsection{Existential condition}
+We employ two techniques to investigate the existential condition. 
+%
+First, using bounded model checking (BMC).
+%
+%The Bounded model checking technique
+It performs a search for violation of the property in the program executions whose length is bounded by some fixed integer value, a \textit{depth}. 
+%
+In the case of no violation for a particular depth, one can iteratively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached.
+%
+For our case, the depth (called as \textit{unwinding} in the technical terms) is the length of the path in the underline graph.
+%
+%
+For the experimentation, we will restrict ourselves to the elementary cycles (cycles of length one). 
+%
+This restriction puts an upper limit of $N$ on the length of each searched path. 
+%
+%
+%and the upper bound is the number of nodes $N$.
 
-Based upon earlier discussion, we need to answer the following search
-question among VTSs.
+Second, using constraint solving, where the rules are represented as a constraint over the variables defined in the system.
 %
-Here, we will present both BMC and SMT search problem.
+The search problem is to find an assignment of variables that satisfies all the generated constraints.
+%
+We have used a form of this technique called satisfiability modulo theories (SMT).
+%
+The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning. 
+%
+It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
+% is satisfiability of formulas with respect to some background theory.
+%
+Throughout the paper we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
+%The existential condition search problem is represented as a bounded model checking and constraint solving. 
+%
+%Based upon earlier discussion, we need to answer the following search question among VTSs.
+%
+Here, we will present both $\fbmc$ and $\fsmt$ search problem for the existential condition.
 
-\textbf{SMT Search problem:}
+\subsubsection{$\fbmc$ Search problem:}
+For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth w,
+we are searching for well-structured, stable, and well-fused VTS
+$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
+$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w depth of unwinding.
+
+\subsubsection{$\fsmt$ Search problem:}
 For a given $k$, size $\nu$, and molecule number $\mu$,
@@
 
-\noindent
-The notion of stability and connectivity varies slightly for BMC encoding. 
-%In this subsection, we will present the concept of stability and connectivity for BMC encoding. 
+%\noindent
+%The notion of stability and connectivity varies slightly for BMC encoding. 
+%%In this subsection, we will present the concept of stability and connectivity for BMC encoding. 
+%%
+%We call a graph $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
+%there exists a $m$-path in G with $n_1 = n'$ and $n_\ell = n$.
+%%
+%%
+%We call a graph $G$ {\em connected} if for each $n,n' \in \nodes$,
+%$n'$ there is a path from $n$ to $n'$ in G.
 %
-We call a graph $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
-there exists a $m$-path in G with $n_1 = n'$ and $n_\ell = n$.
+%We call a graph $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
+%VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
+%%	
+%We use $m$-${path}_i^j$ to denote an $m$-path between source node i and target node is j. 
 %
 %
-We call a graph $G$ {\em connected} if for each $n,n' \in \nodes$,
-$n'$ there is a path from $n$ to $n'$ in G.
+%Creating a formula to search a path of length N-1 for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
+%%
+%Even if there exist shorter paths we have to create the formula of maximum size N-1. 
+%% 
+%To resolve these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
 %
-We call a graph $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
-VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
-%	
-We use $m$-${path}_i^j$ to denote an $m$-path between source node i and target node is j.
 
-For the experimentation, we will restrict ourselves to the elementary cycles (cycles of length one). 
-%
-This restriction puts an upper limit of N-1 on the length of each searched path. 
-%
-Creating a formula to search a path of length N-1 for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
-%
-Even if there exist shorter paths we have to create the formula of maximum size N-1. 
-% 
-To resolve these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
-%
-This specified depth is called unwinding in the technical terms.
-
-\textbf{BMC Search problem:}
-For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth w,
-we are searching for well-structured, stable, and well-fused VTS
-$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w depth of unwinding.
-
-\subsection{QBF and synthesis}
-Here we will present the QBF and Synthesis search problem.
+\subsection{Universal condition:}
+Here we will present the QBF.
 
@@
 %\subsection{Problem Statements}
-\textbf{Synthesis problem statement:}
+\subsection{Synthesis:}
 We will assume that we are given a VTS, whose all components
@@
 
-We will do synthesis against the following property that says the VTS
+We will do synthesis against the property that the VTS
 is stable and 3-connected.
@@
 %
-\begin{align*}
-\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
-%\land \texttt{DisConnected}(4)
-\end{align*}
-The property was proposed in~\cite{shukla2017discovering}.
+%\begin{align*}
+%\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
+%%\land \texttt{DisConnected}(4)
+%\end{align*}
+This property was proposed in~\cite{shukla2017discovering}.
 %

### 2019-03-12 papers/journal/problem.tex
SMt and BMC : update 01

@@
 %
-The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning. 
+The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors etc.
 %
-It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
+%It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
 % is satisfiability of formulas with respect to some background theory.
@@
 \subsubsection{$\fbmc$ Search problem:}
-For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth w,
+For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
 we are searching for well-structured, stable, and well-fused VTS

### 2019-03-12 papers/journal/problem.tex
QBF

@@
 
-\subsubsection{$\fbmc$ Search problem:}
+\subsubsection{$\fbmc$ Search problem.}
 For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
@@
 
-\subsubsection{$\fsmt$ Search problem:}
+\subsubsection{$\fsmt$ Search problem.}
 For a given $k$, size $\nu$, and molecule number $\mu$,
@@
 
-\subsection{Universal condition:}
-Here we will present the QBF.
+\subsection{Universal condition}
+%Here we will present the QBF.
+We will model the search problem for the universal condition as a quantified Boolean formula, and resultant formula will be solved with the help of a QBF solver.
+%
+The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifiers.
+%
+The QBFs enables potentially more succinct encodings than propositional logic.
 
-\ankit{This is a dummy template. need a rewrite.} \textbf{QBF search problem:}
-For a given $k$, size $\nu$, and molecule number $\mu$,
-we are searching for well-structured, stable, and well-fused VTS
-$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$,and
-$G$ is not $k$-connected.
+%\ankit{This is a dummy template. need a rewrite.} 
+\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment for well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
 
@@
 %\subsection{Problem Statements}
-\subsection{Synthesis:}
+\subsection{Synthesis of VTS}
 We will assume that we are given a VTS, whose all components

### 2019-03-12 papers/journal/encoding.tex
removed duplicate text from 6.4 intro
updated univ encoding ref

--- 2019-03-10 papers/journal/encoding.tex
@@
 %
-Recall that the specification for universal condition~\ref{eq:univcond} requires quantifier alternation. 
+Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
 %
@@
 % 
-Although, it is possible to encode the universal condition~\ref{eq:univcond} as a SAT or SMT problem.
+Although, it is possible to encode the universal condition as a SAT or SMT problem.
 %
@@
 \subsection{Synthesis of VTS}
-%In this section, we will present our synthesis method for
-%the synthesis problems.
+In this section, we will present our synthesis method for
+the synthesis problems.
+%
+%We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
+%
+%Whereas properties like stability and connectivity discussed in the previous sections may not.
+%
+Here, we use these two properties stability and connectivity against which we perform our synthesis. 
+%
+The encoding can be easily extended to accommodate other interesting properties.
 

### 2019-03-12 papers/journal/encoding.tex
made ambiguou claim

@@
 %
-This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.
+This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
 

### 2019-03-12 papers/journal/problem.tex
Minor corrections

@@
 %
-We categorize the search problems into three different categories, search problem to solve the existential condition, search problem for universal condition and performing synthesis on the incomplete VTS.
+We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition and performing synthesis on the incomplete VTS.
 
@@
 %
-The search problem is to find an assignment of variables that satisfies all the generated constraints.
+The search problem is to find an assignment of variables that satisfies all the specified constraints.
 %

### 2019-03-12 papers/journal/problem.tex
Minor corrections: 01

@@
 $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with w depth of unwinding.
+$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with $w$ depth of unwinding.
 
@@
 %\ankit{This is a dummy template. need a rewrite.} 
-\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment for well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
+\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment to make it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
 

### 2019-03-12 papers/journal/problem.tex
BMC and SMT Section 5.1 Done

@@
 \subsection{Existential condition}
-We employ two techniques to investigate the existential condition. 
+We employ two techniques to examine the existential condition. 
 %
-First, using bounded model checking (BMC).
+First, using the bounded model checking (BMC) technique~\cite{biere1999symbolic1, biere2003bounded}.
+%
+%It  represents the executions of a program symbolically and 
 %
 %The Bounded model checking technique
-It performs a search for violation of the property in the program executions whose length is bounded by some fixed integer value, a \textit{depth}. 
+BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed integer value $w$ (\textit{unwinding depth}). 
 %
-In the case of no violation for a particular depth, one can iteratively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached.
+The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
+% is used to check the satisfiability of the resultant propositional formula.
 %
-For our case, the depth (called as \textit{unwinding} in the technical terms) is the length of the path in the underline graph.
+In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
+%
+For our case, the unwinding depth is the length of the path of the underline graph.
 %
 %
-For the experimentation, we will restrict ourselves to the elementary cycles (cycles of length one). 
+For the experimentation, we restrict the check only to the elementary cycles, cycles of length one. 
 %
-This restriction puts an upper limit of $N$ on the length of each searched path. 
+This restriction puts an upper limit of number of node, $N$ on the length of the searched path. 
 %

### 2019-03-12 papers/journal/problem.tex
Minor corrections: 02

@@
 $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected with $w$ depth of unwinding.
+$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected, within $w$ depth of unwinding.
 

### 2019-03-12 papers/journal/problem.tex
qbf Section 5.1 Done

@@
 %
-We have used a form of this technique called satisfiability modulo theories (SMT).
+We have used a form of this technique called satisfiability modulo theories (SMT)~\cite{nieuwenhuis2006solving, barrett2018satisfiability}.
 %
@@
 %Here we will present the QBF.
-We will model the search problem for the universal condition as a quantified Boolean formula, and resultant formula will be solved with the help of a QBF solver.
+We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
 %
@@
 %
-The QBFs enables potentially more succinct encodings than propositional logic.
+The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.
 
 %\ankit{This is a dummy template. need a rewrite.} 
-\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment to make it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
+\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
 

### 2019-03-12 papers/journal/intro.tex
Added synthesis dia (just template)
Improved image for synthesis
added image folder

--- 2019-03-02 papers/journal/intro.tex
@@
 
-First, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
+\ankit{Put parts of Bio back to this section and be best written by mukund: for Bio and Ashutosh: for CS.}
 
-\subsection{Vesicle traffic system}
-Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}.
-These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
-Below, we give a brief description of the sequence of steps involved in the vesicle transport process.
-Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.
+\mukund{Bio} ..... \\ ... \\
 
-\begin{figure}
-	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
-	\caption{Schematic of the vesicle transport system.
-Steps involved in vesicle transport between two compartments; a source and a target compartment are shown.
-The symbols used for different molecules involved in vesicle traffic are explained in the key.
-At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins.
-Here, the different colours indicate different types of cargo and adaptor proteins.
-Coat proteins are recruited to the forming vesicle by adaptor proteins.
-Note here that a single type of coat protein can interact with multiple types of adaptor proteins.
-Subsequently, the vesicle is pinched off at its neck by dynamin.
-Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment.
-At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
-    \label{fig:vts}
-\end{figure}
+\ashu{CS} ... \\ ... \\
 
-\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
-%
-Cargo sorting is performed by cytosolic adaptor proteins. 
-Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
-Then these adaptors bind to cargo molecules and thereby sequester them for packaging.
-%
-Different adaptor proteins act at different compartments, for eg., vesicle formation at the ER requires the adaptor sec23/24, and AP2 adaptor is used for packaging vesicles at the plasma membrane.
-%
+\ankit{A template}
+The following are the contributions of this work:
 
-The next step is membrane deformation, which involves cytosolic coat proteins.
-Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins.
-These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
-A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
-%
-There are three major types of coat proteins; Clathrin, COP2 and COP1.
-These act on different compartments; the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
-
-Finally, transport vesicles bud out from the source compartment.
-This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}.
-%
-The vesicle is now ready for transport and subsequent fusion with a target compartment.
-
-\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
-
-Target compartment recognition involves molecular switches called Rabs and  tethering complexes.
-Distinct compartments of the cell are associated with distinct Rabs.
-For example, Rab5 is associated early endosomes and  Rab7 with late endosomes\cite{rink2005rab}.
-Rabs are master regulators; in their active form Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment.
-~\cite{muller2018molecular}
-
-Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion.
-They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion.
-A clear mechanism for action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle associated Rabs, SNAREs and SNARE regulators.
-They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.
-
-The final step in vesicle transport is fusion of vesicle with the target compartment.This is brought about by SNARE proteins. 
-There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type.
-In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment (A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs)~\cite{yoon2018snare}.
-
-\todo{schematic of snare regulatory network}
-In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
-%
-\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
-\newline SM proteins have multiple modes of SNARE regulation: 
-\begin{itemize}
-	\item SM proteins can hold
-	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
-	complexes.
-	%
-	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
-	form.
-	%
-	\item Finally, SM proteins bind the fully assembled
-	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
-	%
-	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
-\end{itemize}
-
-\textbf{Major paths in the vesicle transport network}:
-\todo{schematic of intracellular compartments and  major routes}
-Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
-%
-\begin{itemize}
-	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
-	%
-	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
-\end{itemize}
-Other paths are used for cross talk between the secretory and the endocytic routes.
-For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}.
-Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus.
-The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.
-
-%
-
-%\begin{table}
-%	\begin{center}
-%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-%			\hline
-%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
-%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
-%			\hline
-%		\end{tabular}
-%		\label{tab:threec}
-%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
-%	\end{center}	
-%\end{table}
-\subsection{Abstraction of VTS as a graph problem}
-
-%In this section, we will describe the basic constraints imposed by cell biology. These are all incorporated into an abstract model of a VTS, whose properties will then be explored using SMT solvers.
-
-In this section, we will abstract from the biological description of the VTS and represent the whole network as an annotated transport graph. 
-%
-The constraints imposed by cell biology are incorporated in the  annotations of the graph.
-
-\textbf{The cell as a transport graph:} 
-%We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph.
-Every compartment or vesicle has a set of molecular labels, such as SNARE proteins, associated with it.
-The cell can be abstractly represented as an annotated graph. 
-Every compartment in the cell can be represented as a node in the graph. 
-%
-The set of molecules present in the compartment, for example, SNARE proteins associated with it, are represented as a label to the corresponding nodes.
-%
-The label of each node will be unique molecules present on the compartment, i.e we abstract over the quantity of the molecule present in a compartment.
-%This represents the flux of the molecule type present at that compartment.
-%
-The transport vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
-% 
-The label represents the associated flux of all molecular types carried by the corresponding vesicle.
-%
-%
-
-\textbf{Steady state:} 
-The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
-%
-In our model, we assume that the cell is in steady state.
-As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
-Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
-%
-In this paper, we refer to the steady state of the cell (refered as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.
-
-%Each edge is associated with a flux of all the molecular types carried by the corresponding vesicle.
-The total amount of each molecular type on each compartment can therefore increase or decrease.
-We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales.
-Therefore, incoming and outgoing fluxes are balanced for each molecular type at each compartment; it is the \textit{stability cond1ition}.
-
-\textbf{Vesicle fusion:}
-%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
-%
-%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
-% 
-%The molecular composition and hence the properties of the transfer vesicle 
-%is the crucial factor to which target compartment the vesicle will fuse to.
-%
-%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
-%  
-%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
-%
-%Once a vesicle has budded out of the source, the molecules it carries determine its properties.
-In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment.
-Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
-%
-%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
-Vesicle fusion requires a pairing of 3 Qsnares and 1 Rsnare that are distributed between the transfer vesicle and the target compartment. 
-%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
-%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
-%
-%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
-%
-Not all sets of Q and R SNAREs are allowed to fuse with each other.
-%
-In the model, we assume that the cell has an equal number of Q and R SNARE types.
-%
-Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with an equal number of Q and R SNAREs. 
-% equal number of Q and R SNAREs as a part of node and edge label.
-%
-%
-Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.
-
-\textbf{Molecular regulation:} 
-Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
-%We assume that for fusion to occur, the pair of 
-%
-The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
-%
-In our abstract model, 
-we create a hierarchy of models for varying degrees of regulation of SNARE activity.
-%we create a set of variations of different kind of molecular regulations.
-%
-Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
-%
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
-%
-This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
-%
-
-%We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state.
-Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively.
-We test many different versions of this kind of molecular regulation.
-Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle.
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
-This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
-
-\textbf{Difficulty of the analysis:}
-The analysis of vesicle traffic systems is a difficult problem
-because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
-%
-For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
-%
-The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
-%
-Precise analysis of the properties of the VTS would be hindered by the same reason. 
-%
-%Properties of the VTS would be hindered by the same reason. 
-%3-connected graphs and all possible variations of SNARE regulation rules. 
-%
-%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
-
-\subsection{Graph connectivity is an interesting and accessible property of the VTS}
-%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
-Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
-The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments.
-But we do not know if this information is complete.
-In order to assess how completely we know the VTS, we need easily readable benchmarks.
-
-\todo{SA: Need more text on the importance and relevance of PROPRTY OF CONNECTIVITY}
-One such benchmark is provided by our result about connectivity of the VTS graph.
-Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected.
-For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph.
-Therefore the underlying undirected graph is 2-connected.
-From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity.
-When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected.
-And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].
-
-\todo{SA: We need not specify Synthesis here. Only connectivity use next subsection to build this. SM: but this is the para where we explain why connectivity is interesting an biological property}
-The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
-%
-In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
-%
-These predictions are intended to be used as guides for future experiments. 
-%
-A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
-%
-Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.
-
-%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
-\label{subsec:graphmodel}
-%
-
-% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
-%
-
-%
-% Note that the formulas define among other things constraints over
-% paths between nodes in the graph model of VTS. Similarly, one can
-% define fusion rules as constraints over the boolean functions modeling
-% the regulations.  
-\
-% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
-
-%\begin{itemize}
-%\item \srivas{Detailed BIO to Graph problem}
-%\end{itemize}
-
-%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
-the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.
-Here we have defined the property by checking over existence of any fusion/budding rules.
-We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
-%
-%\subsection{Converting the Graph Problem into Boolean SAT problem}
-%\label{subsec:satproblem}
-%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.
-In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.
-We then used the CBMC model checker to convert the graph problem into a SAT problem.
-One of the challenges we had in our earlier work is dealing with quantifiers.
-Note that the connectedness property defined in Listing~1.2 has quantifier alternation.
-Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.
-CBMC supports only a quantifier-free logic n its assertion language.
-In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.
-This enumeration was one source of bottleneck for scaling in our earlier work.
-In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.
-The details of te hnew encding will described in subsequent sections.
-
-%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
-%
-%This property of VTSs has been considered informative and studied by~\cite{shukla}.
-%
-%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
-\subsection{Synthesis of VTS }
-The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
-%
-Completing the vesicle traffic network is a difficult task for the many important reasons: 
-\begin{enumerate}
-	\item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.
-
-	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
-
-	\item Molecules can have redundant routes within the cell ~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
-	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.
-
-	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
-\end{enumerate}
-
-Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
-%
-Many diseases are caused by the malfunction of the vesicle traffic network. 
-%
-Knowledge of the complete network would be helpful in identifying the root causes~\cite{bexiga2013human,gissen2007cargos}. 
-%
-At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
-
-%\subsection{Synthesis of VTS:}
-%
-The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
-%
-In order to attempt to complete a given partial VTS we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
-%
-We can use our stability and k-connectivity constraints as a basis for this investigation.   
-%
-The incomplete VTS might not respect these constraints. 
-%
-In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
-%
-We output various completed versions of VTS against these properties which can then be tested experimentally.
-%
-
-We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
-%
-We have applied our tool on several VTSs including
-two found-in-nature VTSs.
-%
-Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
-%
-
-The rest of the paper is organized as follows. 
-%
-In Sect.~\ref{sec:prelim}, we present the notations we use in this paper. 
-%
-In Sect.~\ref{sec:model}, we present graph model of VTSs and  properties of interest in Sect.~\ref{sec:property}.
-%
-%encoding of several constraints on VTSs. 
-%
-%In , we present the
-%
-In Sect.~\ref{sec:problem}, we present the complete formal problem statement of the verification properties.
-%
-In Sect.~\ref{sec:encoding}, we present the encoding of BMC, SMT, QBF and Synthesis into SAT, SMT and QBF satisfiability. 
-%
-In Sect.~\ref{sec:experiments}, we present our implementation and experimental results. 
-%
-In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.
-
-%\textbf{Biological Model of VTS}
-%
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:
+~

### 2019-03-12 papers/journal/property.tex
Minor corrections
added image folder

@@
+\ankit{This section requires a revision}
 We analyze the model against our desired properties.
@@
 %
-If the formula is not satisfiable we increment the $k$ by $1$ and perform the same procedure. 
+If the formula is not satisfiable we increment the $k$ by $1$ and repeat the same procedure. 
 %
@@
 
-\subsubsection{Search for universal problem}
+\subsubsection{Search for universal condition}
 %
@@
 %
-We need a QBF solvers for such queries.
+We need a QBF solver for such queries.
 %

### 2019-03-12 papers/journal/bio.tex
added bio.tex

First, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.

\subsection{Vesicle traffic system}
Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}. These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments. Below, we give a brief description of the sequence of steps involved in the vesicle transport process. Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.

%\includegraphics{akbar}

\begin{figure}
	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
	%
	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
	%
	Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
	%
	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. 
	%
	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment. At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
    \label{fig:vts}
\end{figure}

\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for eg., vesicle formation at the ER requires the adaptor sec23/24, and AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

The next step is membrane deformation, which involves cytosolic coat proteins. Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
%
There are three major types of coat proteins; Clathrin, COP2 and COP1. These act on different compartments; the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.

Finally, transport vesicles bud out from the source compartment. This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}.
%
The vesicle is now ready for transport and subsequent fusion with a target compartment.

\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.

Target compartment recognition involves molecular switches called Rabs and  tethering complexes. Distinct compartments of the cell are associated with distinct Rabs. For example, Rab5 is associated early endosomes and  Rab7 with late endosomes\cite{rink2005rab}.  Rabs are master regulators; in their active form Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment. ~\cite{muller2018molecular}

Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion. They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion. 
A clear mechanism for action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle associated Rabs, SNAREs and SNARE regulators. They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.

The final step in vesicle transport is fusion of vesicle with the target compartment.This is brought about by SNARE proteins. 
There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type. In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment (A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs)~\cite{yoon2018snare}.

\somya{schematic of snare regulatory network}
In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
%
\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
\newline SM proteins have multiple modes of SNARE regulation: 
\begin{itemize}
	\item SM proteins can hold
	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
	complexes.
	%
	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
	form.
	%
	\item Finally, SM proteins bind the fully assembled
	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
	%
	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
\end{itemize}

\somya{schematic of intracellular compartments and  major routes}
\textbf{Major paths in the vesicle transport network}:
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.

%

%\begin{table}
%	\begin{center}
%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
%			\hline
%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
%			\hline
%		\end{tabular}
%		\label{tab:threec}
%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
%	\end{center}	
%\end{table}
\subsection{Abstraction of VTS as a graph problem}

%In this section, we will describe the basic constraints imposed by cell biology. These are all incorporated into an abstract model of a VTS, whose properties will then be explored using SMT solvers.

In this section, we will abstract from the biological description of the VTS and represent the whole network as an annotated transport graph. 
%
The constraints imposed by cell biology are incorporated in the  annotations of the graph.

\textbf{The cell as a transport graph:} 
%We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph. Every compartment or vesicle has a set of molecular labels, such as SNARE proteins, associated with it.
The cell can be abstractly represented as an annotated graph. 
Every compartment in the cell can be represented as a node in the graph. 
%
The set of molecules present in the compartment, for example, SNARE proteins associated with it, are represented as a label to the corresponding nodes.
%
The label of each node will be unique molecules present on the compartment, i.e we abstract over the quantity of the molecule present in a compartment.
%This represents the flux of the molecule type present at that compartment.
%
The transport vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
% 
The label represents the associated flux of all molecular types carried by the corresponding vesicle.
%
%

\textbf{Steady state:} 
The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
%
In our model, we assume that the cell is in steady state. As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment. 
Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
%
In this paper, we refer to the steady state of the cell (refered as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.

%Each edge is associated with a flux of all the molecular types carried by the corresponding vesicle. The total amount of each molecular type on each compartment can therefore increase or decrease. We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales. Therefore, incoming and outgoing fluxes are balanced for each molecular type at each compartment; it is the \textit{stability cond1ition}.

\textbf{Vesicle fusion:}
%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
%
%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
% 
%The molecular composition and hence the properties of the transfer vesicle 
%is the crucial factor to which target compartment the vesicle will fuse to.
%
%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%  
%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
%
%Once a vesicle has budded out of the source, the molecules it carries determine its properties. In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment. Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment. 
%
%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
Vesicle fusion requires a pairing of 3 Qsnares and 1 Rsnare that are distributed between the transfer vesicle and the target compartment. 
%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%
%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
%
Not all sets of Q and R SNAREs are allowed to fuse with each other.
%
In the model, we assume that the cell has an equal number of Q and R SNARE types.
%
Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with an equal number of Q and R SNAREs. 
% equal number of Q and R SNAREs as a part of node and edge label.
%
%
Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.

\textbf{Molecular regulation:} 
Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
%We assume that for fusion to occur, the pair of 
%
The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
%
In our abstract model, 
we create a hierarchy of models for varying degrees of regulation of SNARE activity.
%we create a set of variations of different kind of molecular regulations.
%
Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
%
We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
%
This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
%

%We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state. Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively. We test many different versions of this kind of molecular regulation. Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}. This is motivated by the idea that pairing must generate an inactive bi-molecular complex.

\textbf{Difficulty of the analysis:}
The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered by the same reason. 
%
%Properties of the VTS would be hindered by the same reason. 
%3-connected graphs and all possible variations of SNARE regulation rules. 
%
%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.

\subsubsection{Graph connectivity is an interesting and accessible property of the VTS}
\ankit{This section requires serious work and best written by Mukund.}
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths. The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments. But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.

\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
One such benchmark is provided by our result about connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].

\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
\somya{But this is the para where we explain why connectivity is interesting an biological property}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\

\ankit{Added this as a template. Will change it soon.}
\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
%
Molecules are numbered 0-7.
%
In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
%
Every molecule on the node is active.
%
The activity of the molecules on an edge are controlled
by presence of the other molecules on the edge.
%
On the right side of the figure, we show the pairing matrix.
%
An entry 1 represents pairing between molecules.
%
$\times$ represents no pairing.
%
Rows corresponds to the labels of edges, and
columns corresponds to the labels of nodes.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 3-connected graph.
\end{example}

\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%

% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
%

%
% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
\
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.

%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}

%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
%
%\subsection{Converting the Graph Problem into Boolean SAT problem}
%\label{subsec:satproblem}
%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.

%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
%
%This property of VTSs has been considered informative and studied by~\cite{shukla}.
%
%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
\subsection{Synthesis of VTS }
The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the vesicle traffic network is a difficult task for the many important reasons: 
\begin{enumerate}
	\item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.

	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.

	\item Molecules can have redundant routes within the cell ~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.

	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
%
Many diseases are caused by the malfunction of the vesicle traffic network. 
%
Knowledge of the complete network would be helpful in identifying the root causes~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research. \\
%

\ankit{Added this as a template. Will change it soon.}
\begin{example}
	%
	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool.

\end{example}
\input{synth-dia}

The rest of the paper is organized as follows. 
%
In Sect.~\ref{sec:prelim}, we present the notations we use in this paper. 
%
In Sect.~\ref{sec:model}, we present graph model of VTSs and  properties of interest in Sect.~\ref{sec:property}.
%
%encoding of several constraints on VTSs. 
%
%In , we present the
%
In Sect.~\ref{sec:problem}, we present the complete formal problem statement of the verification properties.
%
In Sect.~\ref{sec:encoding}, we present the encoding of BMC, SMT, QBF and Synthesis into SAT, SMT and QBF satisfiability. 
%
In Sect.~\ref{sec:experiments}, we present our implementation and experimental results. 
%
In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.

%\textbf{Biological Model of VTS}
%

### 2019-03-12 papers/journal/encoding.tex
fixed wide space problem

@@
 \subsubsection{Fixing VTS by learning activity functions:}
-
 Now we consider a scenario where some of the activity functions for
@@
 $z_1,..,z_{2\lambda}$ as parameters.
-
 % \paragraph{Encoding low depth cnf circuits}
 % \paragraph{Encoding boolean gates}
-
+%
 \begin{align*}
@@
 \end{align*}
-
+%
 Using the template we define the constraints $\texttt{FindFunctions}(z,\lambda)$

### 2019-03-12 papers/journal/experiments.tex
Minor corrections: 03

@@
 
-{\sattool} \textbf{(bounded model checker based tool)}:
+\textbf{{\sattool (bounded model checker based tool)}}:
 The enumeration encoding (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.

### 2019-03-13 papers/journal/problem.tex
Minor updates on synthesis code

@@
 %The Bounded model checking technique
-BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed integer value $w$ (\textit{unwinding depth}). 
+BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
 %
@@
 %
-For the experimentation, we restrict the check only to the elementary cycles, cycles of length one. 
+For the experimentation, we restrict the check only to the elementary cycles; cycles of length one. 
 %
-This restriction puts an upper limit of number of node, $N$ on the length of the searched path. 
+This restriction puts an upper limit of number of nodes, $N$ on the length of the searched path. 
 %

### 2019-03-13 vts-synth/src/main.cpp

@@ -1,33 +1,32 @@
 #include <stdio.h>
-#include <z3++.h>
-#include <vector>
 #include <stdlib.h>
+#include <z3++.h>
 #include <future>
+#include <vector>
 
-#include <iostream>
-#include <fstream>
 #include <unistd.h>
 #include <chrono>
 #include <ctime>
+#include <fstream>
+#include <iostream>
 //#include <time.h>
 
 #include <boost/program_options/options_description.hpp>
 #include <boost/program_options/parsers.hpp>
 #include <boost/program_options/variables_map.hpp>
-#include <boost/tokenizer.hpp>
 #include <boost/token_functions.hpp>
+#include <boost/tokenizer.hpp>
 
 using namespace boost;
 using namespace boost::program_options;
 
 #include <exception>
 
-#include "z3-util.h"
-#include <vts.h>
 #include <load-vts.h>
+#include <vts.h>
+#include "z3-util.h"
 
-int main(int ac, char* av[])
-{
+int main(int ac, char* av[]) {
   try {
     int funcType = -1;
     int synthVar = -1;
@@ -36,14 +35,13 @@ int main(int ac, char* av[])
     bool printModel = false;
     bool inputFile = false;
     std::vector<std::string> inputFilename;
-    
+
     options_description general("General options");
-    general.add_options()
-      ("help", "produce a help message")
-    //  ("help-module", value<std::string>(),
-    //   "produce a help for a given module")
-    //  ("version", "output the version number")
-      ;
+    general.add_options()("help", "produce a help message")
+        //  ("help-module", value<std::string>(),
+        //   "produce a help for a given module")
+        //  ("version", "output the version number")
+        ;
 
     /*
     options_description gui("GUI options");
@@ -51,56 +49,59 @@ int main(int ac, char* av[])
       ("display", value<std::string>(), "display to use")
       ;
    */
-   
+
     options_description variation("Variation options");
-    variation.add_options()
-      ("func-type,f", value<int>(), "fix a function type for QBF")
-      ("synth-var,s", value<int>(), "fix a synthesis variation for vts")
-      ;
-    
+    variation.add_options()("func-type,f", value<int>(),
+                            "fix a function type for QBF")(
+        "synth-var,s", value<int>(), "fix a synthesis variation for vts");
+
[…]

### 2019-03-13 vts-synth/src/vts-synthesis.cpp

@@ -1,23 +1,21 @@
+#include <utils.h>
 #include <vts.h>
 #include <z3-util.h>
 #include <algorithm>
-#include <utils.h>
 
-
-
-/** To do list : 
+/** To do list :
  * 1. Take Care of at_least_k and at_most_k with asserts() or false adds
  *
  */
 
-/** Synthesis Variations 
- * 1. Add edge to achieve graph stability and k connected. 
- * 2. Add flow of molecules to fix fusion. 
+/** Synthesis Variations
+ * 1. Add edge to achieve graph stability and k connected.
+ * 2. Add flow of molecules to fix fusion.
  *   - use available molecules.
  *   - allow other type of molecule.
  * 3. KCnf
  *   - Low depth circuit
- * 4. Gates: And Or  
+ * 4. Gates: And Or
  *   - Function dependence with var occuring once
  * 5. VTS repair.
  * 6. Biological Operations
@@ -25,18 +23,19 @@
  *  - Deactivate
  */
 
-
-z3::expr vts::annotate_mukund_graph ( z3::expr_vector& fixN, z3::expr_vector& fixActiveN, 
-                                      z3::expr_vector& fixE, z3::expr_vector& fixPresenceE,
-                                      z3::expr_vector& fixActiveE, z3::expr_vector& fixPairingP )  {
-
+z3::expr vts::annotate_mukund_graph(z3::expr_vector& fixN,
+                                    z3::expr_vector& fixActiveN,
+                                    z3::expr_vector& fixE,
+                                    z3::expr_vector& fixPresenceE,
+                                    z3::expr_vector& fixActiveE,
+                                    z3::expr_vector& fixPairingP) {
   /* M = 14, Molecules subgraph of Mukunds VTS`
    * [ Qa2, Qa5, Qa7, Qa8 ] ::> [ M0, M1, M2, M3 ]
    * [ Qb8 ] ::> [ M4 ]
    * [ Qc7, Qc8 ] ::> [ M5, M6 ]
    * [ Qbc2, Qbc2/3, Qbc7 ] ::> [ M7, M8, M9 ]
    * [ R2, R3, R7, R8 ] ::> [ M10, M11, M12, R13 ]
-   * 
+   *
    * Nodes: N = 3
    *        EE :: 0
    *        LE :: 1
[…]

### 2019-03-13 vts-synth/src/vts.cpp

@@ -1,17 +1,15 @@
-#include<vts.h>
-#include<z3-util.h>
-#include <tuple>        // std::tuple
-#include <vector>
+#include <vts.h>
+#include <z3-util.h>
 #include <algorithm>
+#include <tuple>  // std::tuple
+#include <vector>
 
-
-template<int index> struct TupleCompare
- {
-    template<typename Tuple>
-    bool operator() (const Tuple& left, const Tuple& right) const
-    {
-        return std::get<index>(left) < std::get<index>(right);
-    }
+template <int index>
+struct TupleCompare {
+  template <typename Tuple>
+  bool operator()(const Tuple& left, const Tuple& right) const {
+    return std::get<index>(left) < std::get<index>(right);
+  }
 };
 // define n dimentional vectors
 //#include "boost/multi_array.hpp"
@@ -25,30 +23,31 @@ struct TupleCompare
     template<typename T>
     bool operator()(T const &t1, T const &t2)
     {
-        return F<typename tuple_element<M, T>::type>()(std::get<M>(t1), std::get<M>(t2));
+        return F<typename tuple_element<M, T>::type>()(std::get<M>(t1),
+std::get<M>(t2));
     }
 };
 */
 
+void vts::add_known_edge(unsigned n1, unsigned n2, unsigned q,
+                         std::vector<unsigned>& mols,
+                         std::vector<unsigned>& act) {
+  // std::vector < std::tuple <unsigned, unsigned> > knownEdgesTuple;
+  // std::vector < std::tuple <unsigned, unsigned, unsigned, unsigned> >
+  // knownPresenceEdgesTuple; std::vector < std::tuple <unsigned, unsigned,
+  // unsigned, unsigned> > knownActiveEdgesTuple;
+  assert(n1 < N);
+  assert(n2 < N);
+  assert(q < E_arity);
 
-void vts::add_known_edge( unsigned n1, unsigned n2, unsigned q,
-                          std::vector<unsigned>& mols,
-                          std::vector<unsigned>& act ) {
-  //std::vector < std::tuple <unsigned, unsigned> > knownEdgesTuple;
-  //std::vector < std::tuple <unsigned, unsigned, unsigned, unsigned> > knownPresenceEdgesTuple;
[…]

### 2019-03-14 papers/journal/bio.tex
fixed image prob
image problem: skipped
image working across the platforms
Updated the lang

@@
 \begin{figure}
-	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
+	\includegraphics[height=10cm,width=12cm]{diavts.eps}
 	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
@@
 \subsubsection{Graph connectivity is an interesting and accessible property of the VTS}
-\ankit{This section requires serious work and best written by Mukund.}
+\ankit{This section requires some rewrite and best written by Mukund.}
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
@@
 \somya{But this is the para where we explain why connectivity is interesting an biological property}
+\ankit{Yes; Both of our remark looks correct!}
 The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 

### 2019-03-14 papers/journal/encoding.tex
made uniform use of SMTBMCQBF

@@
 
-In this section we will present the SMT, BMC and QBF based encoding of both the search and the synthesis problem.
-We will start with the SMT based encoding and later present the contrast with the BMC encoding.
+In this section we will present the $\fsmt$, $\fbmc$ and $\fqbf$ search encodings with the encoding for synthesis problem.
+We will start with the $\fsmt$ search encoding and later present the contrast with the $\fbmc$ encoding.
 
-\subsection{SMT based encoding}
+\subsection{$\fsmt$ search encoding}
 \label{enc:smt}
@@
 
-\subsection{BMC based encoding}
+\subsection{$\fbmc$ search encoding}
 
-The BMC encoding differs with the presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
+The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding slightly in the way variables are represented and how we encode reachability.  
 %
-In the BMC encoding, variables are represented as an array of bit vectors of size $M$. 
+In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
 %
@@
 \subsubsection{The key difference in the reachability encoding}:
-The key improvement of the SMT tool over the BMC is the
+The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
 encoding of reachability.
@@
 %
-In the BMC tool, reachability is encoded by enumerating all the possible paths using nondeterminism.
+In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using non-determinism.
 %
@@
 %
-Whereas in the SMT tool, reachability is encoded in two different
+Whereas in the $\fsmt$ encoding, reachability is encoded in two different
 ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
@@
 However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
-only the solutions that captures the evidence of unreachability.
+only the solutions that captures the evidence of non-reachability.
 %
-On the other hand,
-we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
-which needs relatively more auxiliary variables.
+On the other hand, we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1}, which needs relatively more auxiliary variables.
 %
@@
 
-\subsubsection{BMC and SMT problems for different variants}
+\subsubsection{$\fbmc$ and $\fsmt$ search problems for different variants}
 %\ankit{Bring model variant table here}
@@
 %
-The constraints for the variants can be given to a SMT solver to find
+The constraints for the variants can be given to a SAT or a SMT solver to find
 VTSs that belong to the variants.
@@
 % 
-As an experiment, we have implemented a direct SMT version of the universal problem extending the current SMT encodings.
+As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
 %
@@
 
-\textbf{QBF encoding of universal condition:}
+\textbf{$\fqbf$ encoding of the universal condition:}
 We will describe several constraints that encode VTSs in this section.
@@
 %
-We will re-use the QBF encodings for the input VTS as described in the Section~\ref{enc:univ-cond}.
+We will re-use the $\fqbf$ encodings for the input VTS as described in the Section~\ref{enc:univ-cond}.
 %

### 2019-03-14 papers/journal/experiments.tex
made uniform use of SMTBMCQBF

@@
 \textbf{{\sattool (bounded model checker based tool)}}:
-The enumeration encoding (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
+The $\fbmc$ encoding based on enumeration of paths (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
 	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
@@
 \textbf{{\smttool} (SMT based tool)}:
-The recursive encoding (presented in section 6.1)  
+The $\fsmt$ encoding based on recursive reachability definition (presented in section 6.1)  
 %We have implemented the encodings 
@@
 \textbf{{\qbftool} (QBF based universal condition):}
-We have implemented the encodings of the VTS in QBF form (presented in section 6.5) in
-{\qbftool}. 
+The $\fqbf$ encoding (presented in section 6.5) is implemented in the {\qbftool}. 
 %
@@
 
-\textbf{{\ourtool} (QBF based synthesis tool):}
+\textbf{{\ourtool} (SMT and QBF based synthesis tool):}
 \input{synth-table}
-We have implemented the synthesis encodings (presented in section 6.6) in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
+The synthesis encodings (presented in section 6.6) is implemented  in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
 %

### 2019-03-14 papers/journal/problem.tex
minor update

@@
 
-\subsubsection{$\fbmc$ Search problem.}
+\subsubsection{$\fbmc$ search problem.}
 For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
@@
 
-\subsubsection{$\fsmt$ Search problem.}
+\subsubsection{$\fsmt$ search problem.}
 For a given $k$, size $\nu$, and molecule number $\mu$,

### 2019-03-15 papers/journal/experiments.tex
Vts dia update

@@
 
-\textbf{{\sattool (bounded model checker based tool)}}:
+\textbf{{\sattool (Bounded model checker based tool)}}:
 The $\fbmc$ encoding based on enumeration of paths (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
@@
 
-\textbf{{\ourtool} (SMT and QBF based synthesis tool):}
+\textbf{{\ourtool} (QBF based synthesis tool):}
 \input{synth-table}

### 2019-03-15 papers/journal/intro.tex
Minor corrections: 03
Updated the lang
Vts dia update

--- 2019-03-10 papers/journal/intro.tex
@@
 
+%\includegraphics{akbar}
+
 \begin{figure}
-	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
+	\includegraphics[height=10cm,width=12cm]{diavts.eps}
 	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
@@
 
-\somya{schematic of snare regulatory network}
-In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
+%\somya{schematic of snare regulatory network}
+In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
 %
-\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
-\newline SM proteins have multiple modes of SNARE regulation: 
+Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
+%
+Whereas, SM proteins have following multiple modes of SNARE regulation: 
 \begin{itemize}
@@
 
-\somya{schematic of intracellular compartments and  major routes}
+%\somya{schematic of intracellular compartments and  major routes}
 \textbf{Major paths in the vesicle transport network}:
@@
 
-\subsubsection{Graph connectivity is an interesting and accessible property of the VTS}
-\ankit{This section requires serious work and best written by Mukund.}
+\subsubsection{Graph connectivity is an interesting and accessible property of the VTS.} 
+%\ankit{This section requires some rewrite and best written by Mukund.}
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:}
+
 Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
@@
 
-\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
+%\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
 One such benchmark is provided by our result about connectivity of the VTS graph.
@@
 
-\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
-\somya{But this is the para where we explain why connectivity is interesting an biological property}
+%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
+%\somya{But this is the para where we explain why connectivity is interesting an biological property}
+%\ankit{Yes; Both of our remark looks correct!}
 The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
@@
 Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
-
-\ankit{Added this as a template. Will change it soon.}
+%
+%\ankit{Added this as a template. Will change it soon.}
 \begin{example}
@@
 \end{example}
-
+%
 \input{pm-1-matrix}
@@
 %
-Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
+Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research. \\
 %
+%
+%ankit{Added this as a template. Will change it soon.}
+\begin{example}
+	%
+	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool.
+The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.
+
+\end{example}
+\input{synth-dia}
 
@@
 
-%\textbf{Biological Model of VTS}
-%
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:
+~

### 2019-03-15 vts-synth/src/graph-connectivity.cpp

@@ -62,6 +62,7 @@ z3::expr vts::k_connected_graph_constraint ( unsigned K, bool eQuantVar ) {
   z3::expr k_not_connected = exists ( setD2,  
 		    (exactly_k_drops ( K, drop2 ) && only_present_edges_can_be_dropped ( drop2 )) && is_reach2 ) ;
  
+	// TODO: Implement a linear encoding
   z3::expr at_least_k_edges = at_least_three( ee_set );
   
   // [[1]] : K Connected Graph 

### 2019-03-15 vts-synth/src/vts-synthesis.cpp

@@ -308,31 +308,7 @@ z3::expr vts::vts_synthesis(unsigned variation) {
 
   z3::expr knownVarConstraint(ctx);
 
-  /*
-  if ( variation != 5 ) {
-    unassigned_2d_bits( knownNodesTuple, knownNodes, unknownN, nodes, N, M,
-  false ); unassigned_2d_bits( knownActiveNodesTuple, knownActiveNodes,
-                        unknownActiveN, active_node, N, M, false );
-    unassigned_2d_bits( knownPairingMatrixTuple, knownPairingMatrix,
-                        unknownPairingM, pairing_m, M, M, true );
-
-    unassigned_3d_bits( knownEdgesTuple, knownEdges, unknownE,
-                        edges, N, N, E_arity, true );
-
-    unassigned_4d_bits( knownPresenceEdgesTuple, knownPresenceEdges,
-                        unknownPresenceE, presence_edge, N, N, E_arity, M, true
-  ); unassigned_4d_bits( knownActiveEdgesTuple, knownActiveEdges,
-                        unknownActiveE, active_edge, N, N, E_arity, M, true );
-
-    knownVarConstraint =  z3::mk_and( knownEdges )
-                              && z3::mk_and( knownActiveNodes )
-                              && z3::mk_and( knownPresenceEdges )
-                              && z3::mk_and( knownActiveEdges )
-                              && z3::mk_and( knownNodes )
-                              && z3::mk_and( knownPairingMatrix );
-  }
-  */
-
+  // TODO: Check how the knownbits are fixed
   if (variation != 5) {
     unassigned_bits(listN, knownNodes, unknownN);
     unassigned_bits(listActiveN, knownActiveNodes, unknownActiveN);
@@ -381,7 +357,6 @@ z3::expr vts::vts_synthesis(unsigned variation) {
       std::cout << "known edge: " << knownEdges[i] << "\n";
     }
     */
-    //
     // auto edgeActivityC = !at_least_three( unknownActiveE );
     // auto edgePresenceC = !at_least_four( unknownPresenceE );
     // auto nodeC = !at_least_four( unknownN );

### 2019-03-15 papers/journal/intro.tex
added the discussion about the example used and the model Rothman and Batman

@@
 %\end{table}
+
+\subsection{The model}
+\ankit{Requires rewriting and some explanation}
+Our model is inspired by~\cite{shukla2017discovering}.
+On the timescales of minutes, our following assumptions reasonably capture the important aspects of the Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
+\begin{enumerate}
+\item A cell is a set of compartments exchanging vesicles.
+\item Compartments are neither created nor destroyed.
+\item Each compartment is in steady state, gain and loss balance.
+\item Molecules are neither created nor destroyed.
+\item Molecules move via vesicles of uniform size.
+\item Identical vesicles have identical target compartments.
+\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
+\item The activity of a SNARE can be regulated by other molecules present on the same compartment
+or vesicle.
+\item An active SNARE pair is necessary and sufficient for fusion. 
+\end{enumerate}
+
 \subsection{Abstraction of VTS as a graph problem}
@@
 %The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
-
 \subsubsection{Graph connectivity is an interesting and accessible property of the VTS.} 
-%\ankit{This section requires some rewrite and best written by Mukund.}
+\ankit{Requires rewriting and better explanation}
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
-
 Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
+%
 The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments. 
-But we do not know if this information is complete.
-In order to assess how completely we know the VTS, we need easily readable benchmarks.
+%
+But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.
 

### 2019-03-15 papers/journal/intro.tex
added the combi. problem subsection

@@
 \subsection{The model}
-\ankit{Requires rewriting and some explanation}
+\ankit{A template: Requires rewriting and some explanation}
 Our model is inspired by~\cite{shukla2017discovering}.
@@
 
-\textbf{Difficulty of the analysis:}
-The analysis of vesicle traffic systems is a difficult problem
-because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
-%
-For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
-%
-The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
-%
-Precise analysis of the properties of the VTS would be hindered by the same reason. 
+%\textbf{Difficulty of the analysis:}
+
 %
@@
 %The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
-\subsubsection{Graph connectivity is an interesting and accessible property of the VTS.} 
+\subsection{Graph connectivity is an interesting and accessible property of the VTS.} 
 \ankit{Requires rewriting and better explanation}
@@
 \label{subsec:graphmodel}
+
+\subsection{Combinatorial problem and use of Formal methods}
+%
+\ankit{A template: Requires complete rewriting}
+The analysis of vesicle traffic systems is a difficult problem
+because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
+%
+For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
+%
+The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
+%
+Precise analysis of the properties of the VTS would be hindered by the same reason.
+
+Previous analyses of vesicle traffic networks dealt with this combinatorial
+explosion by using a sampling approach~\cite{mani2016stacking}. 
+%
+In these analyses, vesicle traffic is
+modelled as a dynamical system. 
+%
+The traffic rule specifies how the system transitions from one
+time point to the next. 
+%
+Given a traffic rule and an initial condition, the system is evolved over
+time until a steady state is reached. 
+%
+By studying a large sample of randomly generated traffic
+rules, such analyses can make statistical claims about vesicle traffic. 
+%
+
+In contrast, here we seek understand properties of vesicle traffic networks over all possible traffic rules, not just for a sampled subset. 
+%
+We would also like to directly make statements about steady state properties, rather
+than using transition dynamics to first search for steady states. 
+%
+Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
+%
+The tools model the computation symbolically for the graphs of finite size and can verify the and hence make prediction about the hypothesis for all possible states of the system. 
 %

### 2019-03-15 papers/journal/intro.tex
added the combi. problem subsection

@@
 %
-In these analyses, vesicle traffic is
-modelled as a dynamical system. 
+In these analyses, vesicle traffic is modelled as an update system. 
 %
-The traffic rule specifies how the system transitions from one
-time point to the next. 
+%The traffic rule specifies how the system transitions from one
+%time point to the next. 
 %
-Given a traffic rule and an initial condition, the system is evolved over
-time until a steady state is reached. 
+Given a traffic rule and an initial condition, the system is updates one step a time, updating molecular flux of the compartments, until a steady state is reached. 
 %
-By studying a large sample of randomly generated traffic
-rules, such analyses can make statistical claims about vesicle traffic. 
+The update rule defines the flux transition for the next step. 
+%
+By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
 %
 
-In contrast, here we seek understand properties of vesicle traffic networks over all possible traffic rules, not just for a sampled subset. 
+In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
 %

### 2019-03-16 papers/journal/intro.tex
added missing file

@@
 %
-Given a traffic rule and an initial condition, the system is updates one step a time, updating molecular flux of the compartments, until a steady state is reached. 
+Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
 %
 The update rule defines the flux transition for the next step. 
+%
+This process is performed until a steady state is reached. 
+%
 %

### 2019-03-16 papers/journal/model.tex
Minor update on dia
cleaning of comment
added the number of mole and dependency text

@@
 
-\ashu{Should be written bio people}
 Let us discuss rough sizes of the system and expected behaviors.
+%%
+%A typical VTS may have about 10 compartments.
+%%
+%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
+%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
+%%
+%The VTS may transport a large number of molecules but the molecules that
+%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
+%%
+%According to the definition the activity of molecules can be controlled by
+%the presence of all other molecules.
+%%
+%However, in practice the activity of a molecule is controlled by
+%the presence of ~2-3 other molecules.
+A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
 %
-A typical VTS may have about 10 compartments.
+The organellar content of cells vary across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhopteries and micronemes~\cite{gubbels2012evolution}.
 %
-%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
-%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
+The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
 %
-The VTS may transport a large number of molecules but the molecules that
-are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
+Also, across different cell-types, these organelles may be more or less differentiated, for example, number of stacks in the Golgi vary across different cells~\cite{polishchuk2004structural}. 
 %
-According to the definition the activity of molecules can be controlled by
-the presence of all other molecules.
+Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
 %
-However, in practice the activity of a molecule is controlled by
-the presence of ~2-3 other molecules.
+The VTS transports a large number of molecules but the molecules that actively control the system are in their tens [MBOC]. 
+%
+By definition the activity of any VTS molecules can be controlled by all other molecules.
+%
+However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}.
+%
+Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
+%
+But most VTS molecules have more localized influence.
 

### 2019-03-17 papers/journal/encoding.tex
minor update
added the combi. problem subsection
update in BMC section

@@
 %
+Here, we will only present the stability encoding.  
+%
+Rest of the encoding are similar to the one presented in the previous section, Section~\ref{enc:smt}.
+
 In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
@@
 For example, the variable \texttt{bvEdge}[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
-
+%
 Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
@@
 %
-Here, we will only present the stability encoding.  
-%
-Rest of the encoding are similar to the one presented in the Section~\ref{enc:smt}.
 
@@
 %
-
+%
 \input{satqbf-table}
@@
 This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
+%
 
-\textbf{$\fqbf$ encoding of the universal condition:}
+\textbf{$\fqbf$ search encoding of the universal condition:}
 We will describe several constraints that encode VTSs in this section.

### 2019-03-17 papers/journal/encoding.tex
update in BMC section> 01

@@
 %
-For example, the variable \texttt{bvEdge}[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
+For example, the variable \texttt{bvEdge}[1][2][1] = 1001, represents the first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
 %

### 2019-03-17 papers/journal/intro.tex
update in intro

--- 2019-03-15 papers/journal/intro.tex
@@
 \end{enumerate}
+
+A cell is a set of compartments exchanging molecules via vesicles of uniform size.
+%
+On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
+%
+The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
+%
+Fusion of vesicles to compartments is driven by specific SNARE pairing, and a single active SNARE complex is necessary and sufficient for fusion.
+%
+The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
 
@@
 %
-\ankit{A template: Requires complete rewriting}
 The analysis of vesicle traffic systems is a difficult problem
@@
 
-Previous analyses of vesicle traffic networks dealt with this combinatorial
-explosion by using a sampling approach~\cite{mani2016stacking}. 
+In previous work, a sampling approach was undertaken. 
 %
-In these analyses, vesicle traffic is modelled as an update system. 
+The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached.
+%
+With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
+%
+Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
+%
+It is possible that a different scheme for the dynamics could lead to a different set of solution
+
+%Previous analyses of vesicle traffic networks dealt with this combinatorial
+%explosion by using a sampling approach~\cite{mani2016stacking}. 
+%
+%In these analyses, vesicle traffic is modelled as an update system. 
 %
@@
 %
-Given a traffic rule and an initial condition, the system is updates one step a time, updating molecular flux of the compartments, until a steady state is reached. 
+%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
 %
-The update rule defines the flux transition for the next step. 
+%The update rule defines the flux transition for the next step. 
 %
-By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
+%This process is performed until a steady state is reached. 
+%
+%
+%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
 %

### 2019-03-18 papers/journal/intro.tex
Update to intro

@@
 \ankit{A template: Requires rewriting and some explanation}
-Our model is inspired by~\cite{shukla2017discovering}.
-On the timescales of minutes, our following assumptions reasonably capture the important aspects of the Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
+%
+\todo{Ankit: The Rothman model has no intuition; Add couple of lines relating it to VTS; Also, relate it to previous subsection.
+The connect is lacking.} The VTS model for this paper is inspired by~\cite{shukla2017discovering}.
+%
+On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
+%
+The following are the basic component and assumptions of our model. 
 \begin{enumerate}
-\item A cell is a set of compartments exchanging vesicles.
-\item Compartments are neither created nor destroyed.
-\item Each compartment is in steady state, gain and loss balance.
-\item Molecules are neither created nor destroyed.
+\item A cell is a set of compartments exchanging molecules via vesicles of uniform size.
+\item On the timescale of minutes, compartments are neither created nor destroyed.
+\item Each compartment is in steady state, gain and loss of the molecules is balance\todo{Ankit: Need intuition and also reasoning why this is okay to add this as an assumption}.
+\item We assume that molecules are neither created nor destroyed.
 \item Molecules move via vesicles of uniform size.
@@
 \item Fusion of vesicles to compartments is driven by specific SNARE pairing.
+\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
 \item The activity of a SNARE can be regulated by other molecules present on the same compartment
@@
 
-A cell is a set of compartments exchanging molecules via vesicles of uniform size.
-%
-On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
-%
-The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
-%
-Fusion of vesicles to compartments is driven by specific SNARE pairing, and a single active SNARE complex is necessary and sufficient for fusion.
-%
-The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
+\todo{Ankit: Need some additional discussion;4 lines max about the legitamecy of the assumptions.}
+%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
+%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
 
@@
 %
-%\ankit{Added this as a template. Will change it soon.}
+\ankit{Added this as a template. Will change it soon.}
 \begin{example}
@@
 \subsection{Combinatorial problem and use of Formal methods}
-%
+\ankit{Needs revision; overlapping writing.}
 The analysis of vesicle traffic systems is a difficult problem
@@
 %
-For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
+%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
 %
-The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
+%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
+If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
 %
@@
 %
-It is possible that a different scheme for the dynamics could lead to a different set of solution
+It is possible that a different scheme for the dynamics could lead to a different set of solutions.
 
@@
 %
-The tools model the computation symbolically for the graphs of finite size and can verify the and hence make prediction about the hypothesis for all possible states of the system. 
+The tools model the computation symbolically for the graphs of finite size and can make prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
 %
@@
 %
-%ankit{Added this as a template. Will change it soon.}
+\ankit{Added this as a template. Will change it soon.}
 \begin{example}

### 2019-03-18 papers/journal/encoding.tex
update in BMC section> 02
Update to bmc

--- 2019-03-17 papers/journal/encoding.tex
@@
 
-The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding slightly in the way variables are represented and how we encode reachability.  
+Our first attempt was to encode the existential condition check as a $\fbmc$ search problem.
 %
-Here, we will only present the stability encoding.  
+%In this section we will present the $\fbmc$ encoding of the same.
 %
-Rest of the encoding are similar to the one presented in the previous section, Section~\ref{enc:smt}.
+Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is very similar.
+% 
+The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding slightly in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
+%
+Hence, we will only present the stability encoding.  
+%
+Rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.
 
-In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
+In the $\fbmc$ encoding, the label of edges and nodes are represented as an array of bit vector of size $M$. 
+%
+For example, the bit vector \texttt{bvEdge}$[i][j][q]$ is the label is the $q$th edge between node $i$ and $j$.
+% with each bit corresponding to the presence or absence of the molecule. 
+%
+%In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
 %
@@
 %
-For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
+%For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
 %
-Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
+%Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
 %
-The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
+%The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
 %
 
-The molecule set is divided into Q and R-SNAREs. 
+%The molecule set is divided into Q and R-SNAREs. 
+%
+%For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
+%
+%An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
+%
+%Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
+%
+%Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
+%
+%For example, the variable \texttt{bvEdge}[1][2][1] = 1001, represents the first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
+%
+%Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
+%
+%We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
+%
+
+The value of the bit vector describes the presence of corresponding molecules at the particular location. 
 %
@@
 %
-An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
-%
-Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
-%
-Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
-%
-For example, the variable \texttt{bvEdge}[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
-%
-Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
-%
-We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
-%
+For example, the variable \texttt{bvEdge}[0][2][1] = 1001, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 1 and node 2.
 

### 2019-03-18 papers/journal/encoding.tex
Update to bmc

@@
 For example, the bit vector \texttt{bvEdge}$[i][j][q]$ is the label is the $q$th edge between node $i$ and $j$.
+
 % with each bit corresponding to the presence or absence of the molecule. 
@@
 % 
-
 %The molecule set is divided into Q and R-SNAREs. 
@@
 %
-
-The value of the bit vector describes the presence of corresponding molecules at the particular location. 
+%
+The value of the bit vector describe the presence of the corresponding molecules at that particular location. 
 %
@@
 %
-For example, the variable \texttt{bvEdge}[0][2][1] = 1001, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 1 and node 2.
+For example, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 1 and node 2.
 
-In order to specify the stability condition, we use a combination of enumeration and nondeterminism.
+To specify the stability condition, we use a combination of enumeration and nondeterminism.
 %
-Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
+The encoding here presents a simpler version of the implementation. 
+%Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
 %
-We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
+%We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
 %
@@
 %
-We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
+A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if there exists a path with molecule $m$ present on edges along the path between node $i$ and $j$.
 %
-A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m$-$path$ from node $i$ to node $j$ of maximum $w$ length.
+%We use {\npath} to represent the required path to encode the stability condition in VTS.
+%
+%A naive implementation is shown in~\ref{eq:reachbmc1} where 
+We use {\npath}$(m, i, j, w)$ to represent the presence of a $m$-$path_{ij}$ of maximum $w$ length.
 %there is a edge between $i^{\prime \prime}$ and01
@@
 %
-It performs enumeration of every $m$-$path$, $m$-${paths}_i^j$, of at most $w$ length. 
+The~\ref{eq:reachbmc1} performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
 %
-Starting with exploring $m$-${paths}_i^j$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_i^j$ of length $w-1$ is explored.
+Starting with exploring $m$-${paths}_{ij}$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
 %by performing series of node hops till final node destination j is reached.
@@
 \begin{align}
-\texttt{NOracle}(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} | {m-path}_i^j | = l
+\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
   \tag{S1}\label{eq:reachbmc1}
@@
 
-We encode stability using \texttt{NOracle}. If there is an $m$-edge between node $i$ and $j$, there has to be a $m$-$path_i^j$ from $j$ to $i$ of maximum $w$ length.
+We encode stability using \npath. For every edge with $m^{th}$ molecule present between node $i$ and $j$ then there exists a $m$-$path_{ji}$ of maximum $w$ length.
 %
@@
 \begin{align}
-	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies \texttt{NOracle}(m, j, i, w)
+	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies \npath(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}

### 2019-03-18 papers/journal/encoding.tex
Update to bmc:01

@@
 %
-Starting with exploring $m$-${paths}_{ij}$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
+Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
 %by performing series of node hops till final node destination j is reached.

### 2019-03-18 papers/journal/encoding.tex
Update to bmc:02

@@
 %
-Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is very similar.
+Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
 % 
-The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding slightly in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
+The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
 %
@@
 
-In the $\fbmc$ encoding, the label of edges and nodes are represented as an array of bit vector of size $M$. 
+In the $\fbmc$ encoding, the label of the edges and nodes are represented by variables of type arrays of bit vector of size $M$. 
 %
-For example, the bit vector \texttt{bvEdge}$[i][j][q]$ is the label is the $q$th edge between node $i$ and $j$.
+For example, the variable \texttt{bvEdge}$[i][j][q]$, represent the label of the $q$th edge between node $i$ and $j$.
 
@@
 %
-The value of the bit vector describe the presence of the corresponding molecules at that particular location. 
+The value of the bit vector variable describe the presence of the corresponding molecules at that particular location. 
 %
@@
 %
-For example, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 1 and node 2.
+For example, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 2 and node 1.
 

### 2019-03-18 papers/journal/encoding.tex
Update to bmc:03

@@
 %
-For example, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 2 and node 1.
+For an edge in the system with $M$ = 4 molecules, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 2 and node 1.
 
@@
 %
-The encoding here presents a simpler version of the implementation. 
-%Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
+%Nondeterminism can be viewed as an oracle that guesses a correct path for a specific $m$ if it exists. 
 %
@@
 %
+The encoding here presents a simpler version of the implementation.
 

### 2019-03-18 papers/journal/encoding.tex
Update to bmc:04
Update to bmc:06
update in bmc

@@
 
-To specify the stability condition, we use a combination of enumeration and nondeterminism.
+To specify the stability condition, we use nondeterminism to perform enumeration.
 %
@@
 The encoding here presents a simpler version of the implementation. 
-
+%
+Note that the enumeration is done only for an unwinding depth $w$.
 \subsubsection{Constraints for stability condition}
 %
-A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if there exists a path with molecule $m$ present on edges along the path between node $i$ and $j$.
+A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if molecule $m$ is present on edges along the that path.
 %
@@
 \begin{align}
-	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies \npath(m, j, i, w)
+	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) == 1) \limplies \npath(m, j, i, w)
   \tag{S2}\label{eq:reachbmc2}

### 2019-03-18 papers/journal/encoding.tex
update in bmc:08

@@
 %
-The encoding here presents a simpler version of the implementation. 
 %
 Note that the enumeration is done only for an unwinding depth $w$.
+%
+The encoding presented below is a simpler version of the implementation. 
 \subsubsection{Constraints for stability condition}
 %
-A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if molecule $m$ is present on edges along the that path.
+A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if molecule $m$ is present on edges along that path.
 %

### 2019-03-18 papers/journal/encoding.tex
update in bmc:09

@@
 %
-Hence, we will only present the stability encoding.  
-%
-Rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.
+Here, we will only present the stability encoding.
+%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.
 
-In the $\fbmc$ encoding, the label of the edges and nodes are represented by variables of type arrays of bit vector of size $M$. 
+In the $\fbmc$ encoding, the label of the edges and nodes are represented by variables of type, \textit{array of bit vector} of size $M$. 
 %

### 2019-03-18 papers/journal/encoding.tex
sd

@@
 
-In this section we will present the $\fsmt$, $\fbmc$ and $\fqbf$ search encodings with the encoding for synthesis problem.
-We will start with the $\fsmt$ search encoding and later present the contrast with the $\fbmc$ encoding.
+In the previous section, we have discussed four problems.
+%
+In this section we will present encodings fof the
+$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
+%
+We will start with the $\fsmt$ search encoding and later present the
+contrast with the $\fbmc$ encoding.
 
-\subsection{$\fsmt$ search encoding}
+\subsection{Encoding for $\fsmt$ search problem}
 \label{enc:smt}
@@
 
-\subsection{$\fbmc$ search encoding}
+\subsection{Encoding for $\fbmc$ search problem}
 
-Our first attempt was to encode the existential condition check as a $\fbmc$ search problem.
+Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{plospaper}.
 %
@@
 
-\subsection{Universal condition}
+\subsection{Encoding for $\fqbf$ search problem}
 \label{enc:univ-cond}
@@
 
-\subsection{Synthesis of VTS}
+\subsection{Encoding for the synthesis problem}
 In this section, we will present our synthesis method for

### 2019-03-18 papers/journal/problem.tex
sd

@@
 %
-We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition and performing synthesis on the incomplete VTS.
+We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition,
+and performing synthesis on the incomplete VTS.
 
@@
 \subsection{Synthesis of VTS}
+%
+We also consider another variant of analysis of VTSs.
+%
 We will assume that we are given a VTS, whose all components
@@
 
-\subsubsection{Encoding synthesis property}
+\subsubsection{Synthesis problem}
 
@@
 %
-Our tool is easily modifiable to support any other property that may be deemed 
-interesting by the biologists.
+% Our tool is easily modifiable to support any other property that may be deemed 
+% interesting by the biologists.
 

### 2019-03-18 papers/journal/property.tex
Minor updates on synthesis code
Vts dia update
sd

@@
-\ankit{This section requires a revision}
+%\ankit{This section needs a revision}
 We analyze the model against our desired properties.
 %
-Since in biology there are are no declared specifications or properties,
-we conjecture some properties that appear to be true in all known
+Since in biology there are no declared specifications or properties,
+we conjecture some properties that appear to be true in all the known
 biological systems.
@@
 
-The goal is to find the minimum graph connectivity properties that for each of the condition.
+The goal is to find the minimum graph connectivity properties for each of the condition.
 

### 2019-03-19 papers/journal/encoding.tex
exmaple update

@@
 
-Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{plospaper}.
+Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
 %
@@
 %
-Recall that now the molecule set is divided into 3:1 Q and R pairs (or partition).
+Recall that the molecule set is divided into 3:1 Q and R pairs (or partition).
 \begin{align*}

### 2019-03-19 papers/journal/experiments.tex
exmaple update

@@
 %
-A 120 min (7200 sec) timeout was used for the tool.
+A 45 min (2700 sec) timeout was used for the tool.
 
@@
 %
-For this comparison we have fixed the total number of molecules minimum twice the node count 
+For this comparison we have fixed the total number of molecules minimum four times the node count 
 %for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
@@
 %
+For our analysis we relax the 3:1 requirement for the Q and R-SNARES and treat a Q-SNARE triple helix as a single complex as modelled in~\cite{shukla2017discovering}.
+%
+The 
 %
@@
 
-We have applied~\ourtool~on six partially defined VTSs.
+We have applied~\ourtool~on seven partially defined VTSs.
 %
@@
 %
-The first four VTSs are synthetic but inspire from literature for
+The first four and the sixth VTSs are synthetic but inspire from literature for
 typical motifs in VTSs. 
+%
 The third VTS is a subgraph of the last VTS.

### 2019-03-19 papers/journal/synth-table.tex
exmaple update

@@
 
-		plos1-dia[3C]& 0.012 &$\infty$& 0.312 &$\infty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & -1 E, -1 AE, -1 AN. +1 E, +1 N. \\\hline
-		plos2-dia[4C] & 0.014 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
-		sub-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline
-		node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE.\\\hline
+		plos1-dia[3C]& 0.02 &$\infty$& 0.37 &$\infty$& 0.46 & $\infty$ & 0.63 &$\infty$& 0.21 & -1 E, -1AE, -1AN. +1E, +1N. \\\hline
+		plos2-dia[4C] & 2.02 & 0   & 2.38 & 0  & 4.27  & 0 & 5.94 & 0 &  3.30 & 0 \\\hline
+		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 5 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -1AN. +1E, +4PE, +4N, +2AN, +2AE. \\\hline
+		node4[3C]  & 5.93  & 1 E   &  13.72 & 12 PE  &  5.09  & $\infty$ & 4.30 &$\infty$& 7.21  & -2 E, -2PE, -1 N, -1AN, -1 AE. +12 N, +8E, +1PE.\\\hline
 		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
-		yeast-graph[3C]   & 95.016    & 2 E  &   timeout  & N/A   & 1571.42  & 2 E  & 530.210   & 2 E & 72.316  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
-
-		mammal-graph[3C]  &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A    &  timeout     & N/A\\\hline
+		yeast-graph[3C]   & 105.15    & 2 E  &   247.04  & 15 PE   & 1381.24  & 2 E  & 541.66   & 2 E & 326.09  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
+	   	node6[3C]  &  454.98  & 2 E  &  1209.30    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
+		mammal-graph[3C]  &  T/O     & N/A  &  T/O     & N/A    &  T/O         & N/A      &  T/O    &  N/A    &  T/O     & N/A\\\hline
 		%    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
@@
 
-		plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PE, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
-		plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
-		sub-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
-		node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
-		yeast-graph & 40.225  & 2 E  &   timeout  & N/A   & 1393.84  & 2 E  & 468.161   & 2 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
-		mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
+		plos1-dia & 0.04&$\infty$& 0.31 &$\infty$& 0.20 & $\infty$ & 0.27&$\infty$& 3.47 & -1E, -1PE, - 1N, -1PE. +1AE, +1PE, +1N\\\hline
+		plos2-dia & 3.97 & 0 &  2.26 & 0  & 5.46 & 0 & 5.35 & 0 & 3.24 & 0 \\\hline
+		sub-mammal & 3.22 & 1 E  & 4.18 & 5 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -1AN. +1 E, +4PE, +4N, +2AN, +2AE \\\hline
+		node4  & 4.01  & 1 E  & 10.19  & 12 PE & 4.26  & $\infty$ & 4.13 &$\infty$&  6.89  & -2 E, -2PE, -1N, -1AN, -1AE. +12N, +8E, +1PE \\\hline
+		yeast-graph & 38.68  & 2 E  &   127.45  & 15 PE   & 1002.41  & 2 E  & 434.08   & 2 E & 197.82  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
+		node6  &  235.97  & 2 E  &  549.25    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
+		mammal-graph   &  T/O     & N/A  &  T/O    & N/A    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A\\\hline
 	\end{tabular}

### 2019-03-19 papers/journal/experiments.tex
exmaple update

@@
 %These results are intended to be used as guides for further discoveries, where the predicted new vesicles and molecular components of existing vesicles and compartments can be tested experimentally.
-The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
+%The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
 %%
-These queries represent different levels of changes that we can make in order to complete these graphs.
+Biologically, these queries represent different levels of changes that we can make in order to complete these graphs.
 %

### 2019-03-19 papers/journal/encoding.tex
results update

@@
 %
-The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
+\todo{Fix the table; the entries of constraint is incorrect}The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs.
 %
@@
 %
+%\begin{align*}
+%  & \forall G \, \texttt{Connectivity(k)} \limplies  \exists
+%                        f,p: \texttt{Stability} \, \land \, \texttt{Consistancy}  
+%  \tag{U}\label{eq:univcond}
+%\end{align*}
 

### 2019-03-20 papers/journal/abstract.tex
Improvement in the Related work section and changed the TODO to the respective work
Vts dia update
added the combi. problem subsection
Abstract Update

--- 2018-06-14 papers/journal/abstract.tex
@@
-Vesicle Traffic Systems(VTSs) are the material transport 
-mechanisms among the compartments inside the biological cells.
+Vesicle Traffic Systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
+%
+The compartments are viewed as nodes that are labeled by their chemical identity and the transport vesicles are similarly viewed as labeled edges between the nodes.
+%
+Several interesting questions about VTSs translate to combinatorial search and synthesis problems. 
+%
+We present novel SAT, SMT and QBF based encodings of the properties over vesicle traffic systems and a tool that searches for the networks that satisfy properties that are related to transport consistency conditions using these solvers.
+%
+In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.
+
+% Vesicle Traffic Systems(VTSs) are the material transport 
+% mechanisms among the compartments inside the biological cells.
 

### 2019-03-20 papers/journal/intro.tex
Abstract Update

@@
-A characteristic feature of eukaryotic cells is the presence of multiple internal membrane bound compartments.
-These compartments exchange molecules amongst themselves in small membrane bound packets called vesicles ~\cite{alberts2002molecular}.
+A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bound compartments.
+These compartments exchange molecules amongst themselves in small membrane-bound packets called vesicles ~\cite{alberts2002molecular}.
 The molecular interaction network that controls the vesicle transport system involves tens of kinds of molecules which regulate each others activities and modes of action.
@@
 %
-The high complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
+High complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
 %The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 

### 2019-03-20 papers/journal/intro.tex
Intro: part1

@@
-A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bound compartments.
-These compartments exchange molecules amongst themselves in small membrane-bound packets called vesicles ~\cite{alberts2002molecular}.
-The molecular interaction network that controls the vesicle transport system involves tens of kinds of molecules which regulate each others activities and modes of action.
+A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
+%
+These compartments exchange molecules amongst themselves in small membrane-bounded packets called vesicles ~\cite{alberts2002molecular}. 
+%
+The molecular interaction network that controls the vesicle transport system involves dozens of varieties of molecules that regulate flow of cargo. 
+%
 Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
 %
-High complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
+Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
+%
+However, high complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
 %The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
-In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the aptitude of such methods.
+In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
 
-First, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
+The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
+%
+Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
 
@@
 Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}. 
+%
 These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
+%
 Below, we give a brief description of the sequence of steps involved in the vesicle transport process. 
+%
 Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.
-
 %\includegraphics{akbar}

### 2019-03-20 papers/journal/intro.tex
Dia: text update

@@
 \subsection{Vesicle traffic system}
-Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}. 
-%
-These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
+%Vesicles were discovered decades ago, in the early 1950s, and
+
+The major molecules involved in the vesicle traffic system~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
 %
@@
 Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.
-%\includegraphics{akbar}
 
@@
 	\includegraphics[height=10cm,width=12cm]{diavts.eps}
-	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
+	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
 	%
@@
 	%
-	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. 
+	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin. 
 	%
-	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment.
-At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
+	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex which is linked to the target compartment. 
+	%
+	At the target compartment the tethered vesicle undergoes fusion, thereby releasing its contents.}
     \label{fig:vts}
@@
 Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
+%
 Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
 %
-Different adaptor proteins act at different compartments, for eg., vesicle formation at the ER requires the adaptor sec23/24, and AP2 adaptor is used for packaging vesicles at the plasma membrane.
+Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
 %
@@
 The next step is membrane deformation, which involves cytosolic coat proteins. 
+%
 Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
+%
 These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
+%
 A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
 %
-There are three major types of coat proteins; Clathrin, COP2 and COP1.
-These act on different compartments; the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
+There are three major types of coat proteins: Clathrin, COP2 and COP1.
+These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
 

### 2019-03-20 papers/journal/intro.tex
Intro: Additon complete: All Mukund's suggestions incorporated

@@
 There are three major types of coat proteins: Clathrin, COP2 and COP1.
-These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
-
-Finally, transport vesicles bud out from the source compartment.
-This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}.
+These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
+%
+Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
 %
@@
 For example, Rab5 is associated early endosomes and  Rab7 with late endosomes\cite{rink2005rab}.
-Rabs are master regulators; in their active form Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment.
-~\cite{muller2018molecular}
+%
+Rabs are master regulators; in their active form Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment ~\cite{muller2018molecular}.
 
 Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion. 
+%
 They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion. 
-A clear mechanism for action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle associated Rabs, SNAREs and SNARE regulators.
+%
+A clear mechanism for action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle, associated Rabs, SNAREs and SNARE regulators.
+%
 They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.
 
-The final step in vesicle transport is fusion of vesicle with the target compartment.This is brought about by SNARE proteins. 
+The final step in vesicle transport is fusion of vesicle with the target compartment is brought about by SNARE proteins. 
+%
 There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type. 
-In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment (A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs)~\cite{yoon2018snare}.
+%
+In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment. 
+%
+A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs~\cite{yoon2018snare}.
 
 %\somya{schematic of snare regulatory network}
+\textbf{Schematic of snare regulatory network:}
 In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
@@
 \subsection{The model}
-\ankit{A template: Requires rewriting and some explanation}
-%
 \todo{Ankit: The Rothman model has no intuition; Add couple of lines relating it to VTS; Also, relate it to previous subsection.
@@
 %
-In this paper, we refer to the steady state of the cell (refered as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.
+In this paper, we refer to the steady state of the cell (referred to as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.
 
@@
 \subsection{Graph connectivity is an interesting and accessible property of the VTS.} 
-\ankit{Requires rewriting and better explanation}
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
@@
 %
-\ankit{Added this as a template. Will change it soon.}
+
 \begin{example}
@@
 \subsection{Combinatorial problem and use of Formal methods}
-\ankit{Needs revision; overlapping writing.}
 The analysis of vesicle traffic systems is a difficult problem
@@
 %
-
 % i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
@@
 % the regulations.  
-\
 % For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
-
 %\begin{itemize}
@@
 %\end{itemize}
-
 %Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
@@
 The details of te hnew encding will described in subsequent sections.
-
 %A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
@@
 %
-Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research. \\
+Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
 %
-%
-\ankit{Added this as a template. Will change it soon.}
 \begin{example}

### 2019-03-20 papers/journal/encoding.tex
First push for SMT QBF overlap

@@
 %
-We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
-to encode the basic structure of VTSs.
+We need the following constraints \texttt{EdgeC},
+\texttt{ActivityC} and \texttt{PairingC} to encode the basic structure of VTSs.
 %
@@
 %
-\begin{align}
-  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
-\end{align}
+\begin{align*}
+  \texttt{PresentEdge} = \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
+\end{align*}
+The edge labels are subset of the node labels of the source and target nodes.
+\begin{align*}
+  \texttt{LabelEdge} = \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
+\end{align*}
+Self edges are not allowed. 
+\begin{align*}
+  \texttt{SelfEdge} = \bigwedge\limits_{i,q} \neg e_{i,i,q}
+\end{align*}
+
+We use \texttt{EdgeC} to collect all the edge related constraints. 
+%
+\texttt{EdgeC} states that each edge has at least one molecule,
+ edge labels are consistent with node labels and there are no self loops.    
+\begin{align*}
+  \texttt{EdgeC} = \texttt{PresentEdge} \land \texttt{SelfEdge} \land \texttt{LabelEdge} 
+\end{align*}
+
 If a molecule is active on an edge, it should be present on the edge.
 %
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
-\end{align}
+\begin{align*}
+  \texttt{ActivityMol} = \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\label{eq:f1}
+\end{align*}
 A molecule should be present to be active on a node.  
-\begin{align}
-  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
-  \tag{V3}\label{eq:c4}
-\end{align}
-The edge labels are subset of the node labels of the source and target nodes.
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
-\end{align}
-Self edges are not allowed. 
-\begin{align}
-   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
-\end{align}
+\begin{align*}
+    \texttt{PresentMol} = \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
+\end{align*}
+
+We use \texttt{ActivityC} to collect all the molecule activity related constraints. 
+\texttt{ActivityC} states that active molecule are present.
+\begin{align*}
+  \texttt{ActivityC} = \texttt{ActivityMol} \land \texttt{PresentMol} 
+\end{align*}
+
 We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs (and similarly R-SNAREs to R-SNAREs) in the pairing matrix to be 0's.
@@
 
-\begin{align}
-  \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
-  \tag{V6}\label{eq:c3}
-\end{align}
+\begin{align*}
+ \texttt{PairingC} =\;& \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
+\end{align*}
 
 \subsubsection{Well-fused constraints}
-Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
+Constraint \texttt{Fusion1} encodes that each edge must fuse with
 its destination node.
 %
-Constraint~\eqref{eq:fuse2} encodes that each edge should not
+Constraint \texttt{Fusion2} encodes that each edge should not
 be able to potentially fuse with any node other than its destination node.
-\begin{align}
+\begin{align*}
+\texttt{Fusion1} =\;&
 \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
 \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
-\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land
-  \notag \\
-	\qquad \qquad \qquad \qquad
-	\Lor\limits_{l=1}^4 a_{j,m_l} \land p_{\{m_1,m_2,m_3,m_4\}})
-  \tag{V7}\label{eq:fuse1}  
-\end{align}
-
-\begin{align}
-	\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies
-\mspace{300mu}
-  \notag \\
-	\qquad \qquad \qquad \qquad
-	\neg
+\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
+& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
+\\
+\texttt{Fusion2} =\;&
+\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
+& \hspace{2cm} \neg 
 \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
 \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
-\mspace{50mu}
-  \tag{V8}\label{eq:fuse2}  
-\end{align}
+\\
+\end{align*}
 
@@
 
-\subsubsection{Regulation on nodes and edges}
+\subsubsection{Regulation on nodes and edges (Activity function)}
 We are considering several models that differ in constraints on
@@
 %
-We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
-the varying constraints.
+%We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
+%the varying constraints.
 %
+The activity of the molecules are controlled by activity functions.
+%
+We will have encoded five variation of the boolean functions based on the biological discussion.
+%
+The concrete functions encoding is presented below.
+%
+We will use \texttt{NodeFun}$_m$ and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
+
 The following constraint encodes no conditions on activities on nodes,
 i.e., all the present molecules on the nodes are active.
-\begin{align}
-\bigwedge\limits_{i,m} n_{i,m} = a_{i,m}    \tag{Ann}\label{eq:ann}
-\end{align}
+\begin{align*}
+\texttt{NodeFunOn} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
+\end{align*}
 The following constraint encodes that activity of a molecule $m$ on the node is
 defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
-\begin{align}
-\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
-\tag{Anb}\label{eq:anb}
-\end{align}
+\begin{align*}
+\texttt{NodeFunBf} =& \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
+\end{align*}
 The following constraint encodes no conditions on activities on edges,
 i.e., all the present molecules on the edges are active.
-\begin{align}
-  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
-\tag{Aen}\label{eq:aen}
-\end{align}
+\begin{align*}
+ \texttt{EdgeFunOn} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
+\end{align*}
 The following constraint encodes that activity of a molecule $m$ on the edge is
 defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
-\begin{align}
-   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
-  \tag{Aeb}\label{eq:aeb}
-\end{align}
+\begin{align*}
+ \texttt{EdgeFunBf} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
+\end{align*}
 %
@@
 matrix. 
-\begin{align}
-	\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies 
-	\notag \\
-	  \qquad \qquad \qquad \qquad
+\begin{align*}
+\texttt{EdgeFunPairing} =&	
+\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land   \\
+      \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies 
 	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})
-  \tag{Aep}\label{eq:aep}
-\end{align}
+\end{align*}
 %
@@
 %
-\begin{align}
-  \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
-  \tag{R1}\label{eq:reach1}
-\end{align}
+\begin{align*}
+  \texttt{Paths}(r) &= \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
+\end{align*}
 Now we can encode stability using the reachability variables.
@@
 $m$-reachable path from $j$ to $i$.
-\begin{align}
- \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-  \tag{R2}\label{eq:reach2}
-\end{align}
+\begin{align*}
+ \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
+\end{align*}
 
@@
 %
-Constraints~\ref{eq:drop1}-\ref{eq:drop4}
+Constraints \texttt{Fail}(d,k), \texttt{FReach}(d,r') and \texttt{Connected}(r')
 encode the relevant constraints for reachability
@@
 existing edges can be dropped and exactly $k-1$ edges are dropped.
-\begin{align}
-  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \tag{D1}\label{eq:drop1}\\
-  \sum_{i,j,q} d_{i,j,q} = k-1
-  \tag{D2}\label{eq:drop2}
-\end{align}
+\begin{align*}
+\texttt{Fail}(d,k) = & 
+\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
+\sum_{i,j,q} d_{i,j,q} = k-1\\
+\end{align*}
 We need to define reachability in the modified VTS, therefore we use
@@
 not dropped and $r'_{i',j}$ is true.
-\begin{align}
-\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}
-  \tag{D3}\label{eq:drop3}
-\end{align}
+\begin{align*}
+\texttt{FReach}(d,r') = &  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}
+\end{align*}
 Since we search for disconnected modified VTS,
@@
 % there is no path between them .
-\begin{align}
-   \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
-  \tag{D4}\label{eq:drop4}
-\end{align}
+\begin{align*}
+   \texttt{Connected}(r')  = & \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
+\end{align*}
 
@@
 %
-The~\ref{eq:reachbmc1} performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
+$\npath(m, i, j, w)$ performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
 %
@@
 
-\begin{align}
+\begin{align*}
 \npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
-  \tag{S1}\label{eq:reachbmc1}
-\end{align}
+\end{align*}
 
@@
 
-\begin{align}
+\begin{align*}
 	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) == 1) \limplies \npath(m, j, i, w)
-  \tag{S2}\label{eq:reachbmc2}
-\end{align}
+\end{align*}
 

### 2019-03-20 papers/journal/property.tex
First push for SMT QBF overlap

@@
-%\ankit{This section needs a revision}
+\todo{This section needs a revision}
 We analyze the model against our desired properties.
 %
-Since in biology there are no declared specifications or properties,
+\ankit{Not completely correct}Since in biology there are no declared specifications or properties,
 we conjecture some properties that appear to be true in all the known

### 2019-04-02 papers/journal/encoding.tex
SMT encoding with Constraints Tag

@@
 \begin{align*}
-  \texttt{PresentEdge} = \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
+  \texttt{PresentE} = \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
 \end{align*}
@@
 \begin{align*}
-  \texttt{LabelEdge} = \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
+  \texttt{LabelE} = \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
 \end{align*}
@@
 \begin{align*}
-  \texttt{SelfEdge} = \bigwedge\limits_{i,q} \neg e_{i,i,q}
+  \texttt{SelfE} = \bigwedge\limits_{i,q} \neg e_{i,i,q}
 \end{align*}
-
-We use \texttt{EdgeC} to collect all the edge related constraints. 
+\noindent We define \texttt{EdgeC} to collect all the edge related constraints. 
 %
@@
 \begin{align*}
-  \texttt{EdgeC} = \texttt{PresentEdge} \land \texttt{SelfEdge} \land \texttt{LabelEdge} 
+  \texttt{EdgeC} = \texttt{PresentE} \land \texttt{LabelE}  \land \texttt{SelfE} 
 \end{align*}
-
-If a molecule is active on an edge, it should be present on the edge.
+\noindent If a molecule is active on an edge, it should be present on the edge.
 %
 \begin{align*}
-  \texttt{ActivityMol} = \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\label{eq:f1}
+  \texttt{ActiveMolE} = \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\label{eq:f1}
 \end{align*}
@@
 \begin{align*}
-    \texttt{PresentMol} = \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
+    \texttt{ActiveMolN} = \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
 \end{align*}
-
-We use \texttt{ActivityC} to collect all the molecule activity related constraints. 
-\texttt{ActivityC} states that active molecule are present.
+\noindent We define \texttt{ActivityC} to collect all the molecule activity related constraints. 
+\texttt{ActivityC} states that all active molecules are present.
 \begin{align*}
-  \texttt{ActivityC} = \texttt{ActivityMol} \land \texttt{PresentMol} 
+  \texttt{ActivityC} = \texttt{ActiveMolE} \land \texttt{ActiveMolN} 
 \end{align*}
-
-We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs (and similarly R-SNAREs to R-SNAREs) in the pairing matrix to be 0's.
+\noindent We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs and R-SNAREs to R-SNAREs in the pairing matrix to be all 0's.
 %It reduces the search space.
@@
 \end{align*}
-
+We define \texttt{FusionC} to collect all the fusion related constraints.
+% 
+\texttt{FusionC} states that every edge in the graph is well-fused.
+\begin{align*}
+\texttt{FusionC} = \texttt{Fusion1} \land \texttt{Fusion2} 
+\end{align*}
 % Fusion rules consist of two different mechanisms.
@@
 \subsubsection{Regulation on nodes and edges (Activity function)}
-We are considering several models that differ in constraints on
-the activity of molecules.
+We are considering several models of VTS that differ in types of regulations on the molecule both on the node and on the edge.  
+%constraints on the activity of molecules.
 %
@@
 %
-We will have encoded five variation of the boolean functions based on the biological discussion.
+We will have encoded five variation of the Boolean functions based on the biological discussion.
 %
@@
 We will use \texttt{NodeFun}$_m$ and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
+%
 
@@
 \begin{align*}
-\texttt{EdgeFunPairing} =&	
-\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land   \\
-      \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies 
-	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})
+\texttt{EdgeFunPairing} =&	\begin{aligned}[t]
+\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies\\
+	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})\end{aligned}\\
 \end{align*}
 %
+We denote the particular choice of node and edge function combined by \texttt{ActivityFun}.
+\begin{align*}
+\texttt{ActivityFun} = \texttt{NodeFun}_m \land \texttt{EdgeFun}_m
+\end{align*}
 \subsubsection{Constraints for stability condition}
@@
 \end{align*}
-
+We define \texttt{StabilityC} to collect all the stability related constraints.
+% 
+\texttt{StabilityC} states that every molecule is moving in a cycle.
+\begin{align*}
+\texttt{StabilityC} = \texttt{Paths}(r) \land \texttt{Loop}(r) 
+\end{align*}
 % Boolean variable
@@
 \end{align*}
-
+We define $\texttt{Connected}(k)$ that says graph is not k-connected.
+\begin{align*}
+\texttt{Connected}(k) = \texttt{Fail}(d,k) \land \texttt{FReach}(d,r') \land \texttt{Connected}(r') 
+% \\
+% \texttt{Disconnected}(k) = & \exists d.\;
+%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
+%                               \land \lnot \texttt{Connected}(r'))
+\end{align*}
 % We can go down or up using -C \_ option.  \newline

### 2019-04-02 papers/journal/intro.tex
SMT encoding with Constraints Tag

@@
 \begin{enumerate}
-\item A cell is a set of compartments exchanging molecules via vesicles of uniform size.
-\item On the timescale of minutes, compartments are neither created nor destroyed.
+\item A cell is a set of compartments exchanging vesicles.
+\item Compartments are neither created nor destroyed.
 \item Each compartment is in steady state, gain and loss of the molecules is balance\todo{Ankit: Need intuition and also reasoning why this is okay to add this as an assumption}.
-\item We assume that molecules are neither created nor destroyed.
+\item Molecules are neither created nor destroyed.
 \item Molecules move via vesicles of uniform size.
@@
 \item Fusion of vesicles to compartments is driven by specific SNARE pairing.
-\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
-\item The activity of a SNARE can be regulated by other molecules present on the same compartment
-or vesicle.
+%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
+\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
 \item An active SNARE pair is necessary and sufficient for fusion. 

### 2019-04-02 papers/journal/encoding.tex
Key difference in encoding section fixed

@@
 Whereas in the $\fsmt$ encoding, reachability is encoded in two different
-ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
+ways in constraints $\texttt{Paths}(r)$ and $\texttt{FReach}(d,r')$.
 %
-The reachability is recursively defined in~\eqref{eq:drop3} and has
+The reachability is recursively defined in~$\texttt{FReach}(d,r')$ and has
 trivial solutions by making all $r'$s true.
 %
-However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
+However, the trivial solutions are disallowed by constraint~$\texttt{Connected}(r')$ and we find
 only the solutions that captures the evidence of non-reachability.
 %
-On the other hand, we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1}, which needs relatively more auxiliary variables.
+On the other hand, we have added length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
 %
-This is because constraint~\eqref{eq:reach2} has only positive
+This is because constraint~$\texttt{Loop}(r)$ has only positive
 occurrences of the reachability variables and if we had defined
-$r$s in ~\eqref{eq:reach1} without paths,
+$r$s in~$\texttt{Paths}(r)$ without paths,
 the circular dependencies in the recursive definitions of $r$s

### 2019-04-02 papers/journal/property.tex
Key difference in encoding section fixed

@@
-\todo{This section needs a revision}
 We analyze the model against our desired properties.
@@
 We will also seek two kinds of questions give the property.
-
 % %
@@
 % We are interested in the following two type of properties of the transport graph:
-
 \begin{enumerate}
@@
 \end{enumerate}
-
 The goal is to find the minimum graph connectivity properties for each of the condition.
-
 % In our program, the rules VTS needs to follow 
@@
 % We will show in later sections how we encode these Boolean functions. 
-
 \subsubsection{Search for existential condition} 

### 2019-04-02 papers/journal/encoding.tex
table update with tags of constraints

@@
 \begin{align*}
-\texttt{NodeFunOn} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
+\texttt{FunOnN} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
 \end{align*}
@@
 \begin{align*}
-\texttt{NodeFunBf} =& \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
+\texttt{FunBfN} =& \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
 \end{align*}
@@
 \begin{align*}
- \texttt{EdgeFunOn} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
+ \texttt{FunOnE} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
 \end{align*}
@@
 \begin{align*}
- \texttt{EdgeFunBf} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
+ \texttt{FunBfE} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
 \end{align*}
@@
 \begin{align*}
-\texttt{EdgeFunPairing} =&	\begin{aligned}[t]
+\texttt{FunPairE} =&	\begin{aligned}[t]
 \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies\\
@@
 %
-The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
-for every variant.
+The column two of the table shows that the constraints $\texttt{EdgeC}$, $\texttt{ActivityC}$, $\texttt{PairingC}$, $\texttt{FusionC}$, $\texttt{StabilityC}$ and $\texttt{Connected}(k)$ are present for every variant.
 %
-The column three of the table lists the constraints that are different among the variants.
+The last two columns of the table lists the activity constraints that are different among the variants.
 %
 %
-One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
+%One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
 %
-For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
+%For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
 %
-Similarly for the case of the edge in version C and D; Aeb.
+%Similarly for the case of the edge in version C and D; Aeb.
 %
-In the case of versions F the activity of the molecules on the edges
-is described by pairing matrix; Aep.
+%In the case of versions F the activity of the molecules on the edges
+%is described by pairing matrix; Aep.
 

### 2019-04-02 papers/journal/encoding.tex
QBF encoding updated

@@
 %\subsection{Boolean satisfiability of the search problem}
-
 We translate the search problem into a Boolean satisfiability
@@
 VTSs that belong to the variants.
-
-\subsection{Encoding for $\fqbf$ search problem}
-\label{enc:univ-cond}
+\subsection{Encoding for $\fqbf$ search problem}\label{enc:univ-cond}
 %
+\input{satqbf-table}
 Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
@@
 % 
-As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
+As an experiment, we have implemented a direct SMT version (encoding not presented) of the universal problem extending the current $\fsmt$ search encodings.
 %
@@
 %
+The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
 %
-\input{satqbf-table}
-%
-\todo{Fix the table; the entries of constraint is incorrect}The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs.
+The connectivity constraint and connectedness constraints are tagged with subscript $U$, $\texttt{StabilityC}_{U}$, $\texttt{Connected}(k)_{U}$,  to distinguish from earlier presented encodings of existential condition.
 %
@@
 %
-
-\textbf{$\fqbf$ search encoding of the universal condition:}
-We will describe several constraints that encode VTSs in this section.
+%
+\subsubsection{$\fqbf$ search encoding of the universal condition:}
+We will describe several constraints that encode universal condition based on QBF formulation in this section.
 %
@@
 
-The following constraints encode the basic consistency of VTSs. 
+Using constraints for VTS from Section~\ref{enc:smt}, we encode the basic consistency of VTSs. 
 %
-Recall that the molecule set is divided into 3:1 Q and R pairs (or partition).
+%Recall that the molecule set is divided into 3:1 Q and R pairs (or partition).
 \begin{align*}
-\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
-\land
-\bigwedge\limits_{i,q} \neg e_{i,i,q}
-\land
-% \tag{\texttt{NodeC}}\label{eq:f0}\\
-\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
-\\
-\texttt{ActivityC} =\;&
-\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
-\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
-% \tag{V2}\label{eq:f1}\\
-\\
-\texttt{PairingC} =\;&
-\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
-(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
-% \land\\ 
-%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
-% \bigwedge\limits_{m} 
-% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
-% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
-\\
-\texttt{Fusion1} =\;&
-\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
-\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
-\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
-& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
-\\
-\texttt{Fusion2} =\;&
-\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
-& \hspace{2cm} \neg 
-\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
+%\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
+%\land
+%\bigwedge\limits_{i,q} \neg e_{i,i,q}
+%\land
+%% \tag{\texttt{NodeC}}\label{eq:f0}\\
+%\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
+%\\
+%\texttt{ActivityC} =\;&
+%\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
+%\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
+%% \tag{V2}\label{eq:f1}\\
+%\\
+%\texttt{PairingC} =\;&
+%\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
+%(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
+%% \land\\ 
+%%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
+%% \bigwedge\limits_{m} 
+%% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
+%% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
+%\\
+%\texttt{Fusion1} =\;&
+%\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
+%\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
+%\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
+%& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
+%\\
+%\texttt{Fusion2} =\;&
+%\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
+%& \hspace{2cm} \neg 
+%\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land ..
 \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
-\\
 \texttt{Consistancy} =\;& \texttt{EdgeC} \land
 \texttt{ActivityC} \land \texttt{PairingC} \land
-\texttt{Fusion1} \land \texttt{Fusion2} 
+\texttt{Fusion} 
 \end{align*}
-\texttt{EdgeC} states that each edge has at least one molecule,
-there are no self loops, and edge labels are consistent with node labels.   
-\texttt{ActivityC} states that active molecule are present.
-\texttt{PairingC} states that all molecules are divided into two types
-using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
-and any fusing set of molecules must have three molecules involved
-from one type and one molecule from the other.
-\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
-\texttt{Consistancy} is the conjunction of all of the above.
+%\texttt{EdgeC} states that each edge has at least one molecule,
+%there are no self loops, and edge labels are consistent with node labels.   
+%\texttt{ActivityC} states that active molecule are present.
+%\texttt{PairingC} states that all molecules are divided into two types
+%using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
+%and any fusing set of molecules must have three molecules involved
+%from one type and one molecule from the other.
+%\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
+%\texttt{Consistancy} is the conjunction of all of the above.
 
@@
 %
-We also need to encode that the activity of the molecules are
-controlled by activity functions.
+Activity functions are encoded as presented in the Section~\ref{enc:smt}.
+%We also need to encode that the activity of the molecules are
+%controlled by activity functions.
 %
-The input VTS may include concrete activity functions for some molecules,
-and for the others the functions may be unknown and to be synthesized. 
+%The input VTS may include concrete activity functions for some molecules,
+%and for the others the functions may be unknown and to be synthesized. 
 %
-The concrete functions can be given to us in many different ways,
-for example as a lookup table, or a concise Boolean formula.
+%The concrete functions can be given to us in many different ways,
+%for example as a lookup table, or a concise Boolean formula.
 %
-In the following section, we will assume the appropriate encoding is
-used for the concrete functions and represent them by \texttt{NodeFun}$_m$
-and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
+%In the following section, we will assume the appropriate encoding is
+%used for the concrete functions and represent them by \texttt{NodeFun}$_m$
+%and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
 %
@@
 %
-We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
-$m$-path from $i$ to $j$ of length less than or equal to $p$.
+%We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
+%$m$-path from $i$ to $j$ of length less than or equal to $p$.
 %
-We use $m$-reachability to encode the stability condition in VTSs.
+%We use $m$-reachability to encode the stability condition in VTSs.
+%%
+%The following constraint recursively encodes that node $j$ is
+%$m$-reachable from node $i$ in less than $p$ steps.
+%%
+We encode stability condition using the reachability variables like presented in Section~\ref{enc:smt}. 
 %
-The following constraint recursively encodes that node $j$ is
-$m$-reachable from node $i$ in less than $p$ steps.
+Recall the definition of $\texttt{Paths}(r)$ and $\texttt{Loop}(r)$ constraint from Section~\ref{enc:smt}.
 %  
-Subsequently, we encode stability condition using the reachability variables.
 \begin{align*}
@@
 \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
-\\
-\texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
 \end{align*}
-
+We encode stability, \texttt{QStability} using quantifiers as existence of reachability bits such that constraints $\texttt{Paths}(r)$ and $\texttt{Loop}(r)$ are satisfied.
+\begin{align*}
+\texttt{QStability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
+\end{align*}
 \paragraph{$k$-connected property}
 %
-$k$-connectedness expresses robustness against failure of few edges.
+The $k$-connectedness expresses robustness against failure of few edges.
 %
-Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
-and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
-the modified VTS.
+%Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
+%and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
+%the modified VTS.
 %
@@
 %
-In the following, $\texttt{Fail}(d,k)$ encodes that only
-existing edges can be failed and exactly $k-1$ edges are failed.
-%
-$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
-%
-We use a new variable $r'_{i,j,p}$ to encode reachability from
-$i$ to $j$ in at most $p$ steps.
-%
-$\texttt{Connected}(r')$ says that all nodes are reachable from any
-other node.
+Recall the definition of $\texttt{Fail}(d,k)$, $\texttt{FReach}(d,r')$ and $\texttt{Connected}(r')$ constraint from Section~\ref{enc:smt}.
+%In the following,  encodes that only
+%existing edges can be failed and exactly $k-1$ edges are failed.
+%%
+% defines reachability in the modified VTS.
+%%
+%We use a new variable $r'_{i,j,p}$ to encode reachability from
+%$i$ to $j$ in at most $p$ steps.
+%%
+%$\texttt{Connected}(r')$ says that all nodes are reachable from any
+%other node.
 \begin{align*}
@@
 %
-We define $\texttt{Connected}(k)$ that says for all possible valid failures
+We define $\texttt{QConnected}(k)$ that says for all possible valid failures
 the graph remains reachable. 
 \begin{align*}
-\texttt{Connected}(k) = & \forall d.\;
+\texttt{QConnected}(k) = & \forall d.\;
 (\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
@@
 \end{align*}
-Since $d$ variables in $\texttt{Connected}(k)$ are universally
-quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
+Since $d$ variables in $\texttt{QConnected}(k)$ are universally
+quantified, $\texttt{QConnected}(k)$ introduces quantifier alternations.
 %
@@
 on the different usage in the synthesis problems. 
-
 % Since not all the activity functions are defined some of the functions
@@
 % uninterpreted function symbols.
+%
+\subsubsection{Encoding synthesis property}
+%
+We will do synthesis against the following property that says the VTS
+is stable and $k$-connected.
+%
+Where $k$ is the minimum connectivity constraint for the corresponding variant in the result of existential condition.
+% The property is designed to balance the search space such that the synthesis procedure does not
+% succeed with simply adding too many edges. 
+%
+\begin{align*}
+\texttt{Property} =  \texttt{QStability} \land \texttt{QConnected}(k) 
+%\land \texttt{DisConnected}(4)
+\end{align*}
+The property was proposed in~\cite{shukla2017discovering}.
+%
+However, the biological relevance of the property is debatable and open for change.
+%
+Our tool is easily modifiable to support any other property that may be deemed 
+interesting by the biologists.
 

### 2019-04-02 papers/journal/encoding.tex
QBF encoding updated
added pairing matrix constraint in qbf

@@
 
+We will rewrite \texttt{PairingC} constraint using quantifiers.
+%
+The \texttt{QPairingC} states that all molecules are divided into two types
+using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
+and any fusing set of molecules must have three molecules involved
+%
+We encode this constraint as a QBF.
+\begin{align*}
+ \texttt{QPairingC} =\;&
+\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
+(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3)
+\end{align*}
 Using constraints for VTS from Section~\ref{enc:smt}, we encode the basic consistency of VTSs. 
@@
 \texttt{Consistancy} =\;& \texttt{EdgeC} \land
-\texttt{ActivityC} \land \texttt{PairingC} \land
+\texttt{ActivityC} \land \texttt{QPairingC} \land
 \texttt{Fusion} 
@@
 %
-Where $k$ is the minimum connectivity constraint for the corresponding variant in the result of existential condition.
+Where $k$ is the minimum connectivity solution of the corresponding variant in the existential condition.
+%
+%Where $k$ is the connectivity of the solution of the existential condition of the corresponding variant.
 % The property is designed to balance the search space such that the synthesis procedure does not

### 2019-04-02 papers/journal/intro.tex
Removed todo from 1.2

@@
 
-\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
+\subsubsection{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
 %
@@
 
-\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
+\subsubsection{Vesicle fusion involves two steps} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
 
@@
 %\somya{schematic of snare regulatory network}
-\textbf{Schematic of snare regulatory network:}
+\subsubsection{Schematic of snare regulatory network}
 In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
@@
 %\somya{schematic of intracellular compartments and  major routes}
-\textbf{Major paths in the vesicle transport network}:
+\subsubsection{Major paths in the vesicle transport network}
 Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
@@
 The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.
-
 %
-
 %\begin{table}
@@
 \subsection{The model}
-\todo{Ankit: The Rothman model has no intuition; Add couple of lines relating it to VTS; Also, relate it to previous subsection.
-The connect is lacking.} The VTS model for this paper is inspired by~\cite{shukla2017discovering}.
+The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
 %
@@
 \item Compartments are neither created nor destroyed.
-\item Each compartment is in steady state, gain and loss of the molecules is balance\todo{Ankit: Need intuition and also reasoning why this is okay to add this as an assumption}.
+\item Each compartment is in steady state, gain and loss of the molecules is balance.
 \item Molecules are neither created nor destroyed.
@@
 \end{enumerate}
-
-\todo{Ankit: Need some additional discussion;4 lines max about the legitamecy of the assumptions.}
 %On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
@@
 
-\textbf{The cell as a transport graph:} 
+\subsubsection{The cell as a transport graph} 
 %We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph.
@@
 
-\textbf{Steady state:} 
+\subsubsection{Steady state} 
 The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
@@
 
-\textbf{Vesicle fusion:}
+\subsubsection{Vesicle fusion}
 %Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
@@
 
-\textbf{Molecular regulation:} 
+\subsubsection{Molecular regulation} 
 Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
@@
 %
+
+\subsubsection{Size of the system}
+Let us discuss rough sizes of the system and expected behaviors.
+%%
+%A typical VTS may have about 10 compartments.
+%%
+%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
+%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
+%%
+%The VTS may transport a large number of molecules but the molecules that
+%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
+%%
+%According to the definition the activity of molecules can be controlled by
+%the presence of all other molecules.
+%%
+%However, in practice the activity of a molecule is controlled by
+%the presence of ~2-3 other molecules.
+A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
+%
+The organellar content of cells vary across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhopteries and micronemes~\cite{gubbels2012evolution}.
+%
+The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
+%
+Also, across different cell-types, these organelles may be more or less differentiated, for example, number of stacks in the Golgi vary across different cells~\cite{polishchuk2004structural}. 
+%
+
+Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
+%
+The VTS transports a large number of molecules but the molecules that actively control the system are in their tens [MBOC]. 
+%
+By definition the activity of any VTS molecules can be controlled by all other molecules.
+%
+However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}.
+%
+Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
+%
+But most VTS molecules have more localized influence.
+%
+We use the above information during the encoding of all search problems presented later.
+
 % i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 

### 2019-04-02 papers/journal/conclusion.tex
Uniform use of the title without :

@@
-In this paper, we presented encodings of the synthesis problems
+\noindent In this paper, we presented encodings of the synthesis problems
 that may arise from VTSs.
@@
 
-\textbf{Encode Dynamic behaviour of the VTS:} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation.
+\textbf{Encode Dynamic behaviour of the VTS} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation.
 Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.

### 2019-04-02 papers/journal/encoding.tex
added pairing matrix constraint in qbf
Uniform use of the title without :

@@
 %\externaldocument{qbf-table}
-
-In the previous section, we have discussed four problems.
+\noindent In the previous section, we have discussed four problems.
 %
@@
 %\subsection{Boolean satisfiability of the search problem}
-We translate the search problem into a Boolean satisfiability
+\noindent We translate the search problem into a Boolean satisfiability
 problem and use SMT solvers to find the satisfying VTSs.
@@
 
-Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
+\noindent Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
 %
@@
 
-\subsubsection{The key difference in the reachability encoding}:
+\subsubsection{The key difference in the reachability encoding}
 The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
@@
 \input{satqbf-table}
-Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
+\noindent The specification for universal condition~\ref{sec:property} requires quantifier alternation. 
 %
@@
 %
-\subsubsection{$\fqbf$ search encoding of the universal condition:}
+\subsubsection{$\fqbf$ search encoding of the universal condition}
 We will describe several constraints that encode universal condition based on QBF formulation in this section.
@@
 
-We will rewrite \texttt{PairingC} constraint using quantifiers.
+We rewrite \texttt{PairingC} constraint using quantifiers.
 %
@@
 \subsection{Encoding for the synthesis problem}
-In this section, we will present our synthesis method for
+\noindent In this section, we will present our synthesis method for
 the synthesis problems.
@@
 requirements of the synthesis problem.
-
-\paragraph{\bf Fixing VTS by adding molecules to the labels:}
+%
+\subsubsection{Fixing VTS by adding molecules to the labels}
 The system may also be fixed only by modifying labels on the edges or the nodes instead
@@
 
-\subsubsection{Fixing VTS by learning activity functions:}
+\subsubsection{Fixing VTS by learning activity functions}
 Now we consider a scenario where some of the activity functions for
@@
 
-\subsubsection{Fixing VTS by both adding/deleting parts:}
+\subsubsection{Fixing VTS by both adding/deleting parts}
 %

### 2019-04-02 papers/journal/experiments.tex
results update
Uniform use of the title without :

@@
 %\externaldocument{sat-table}
-
 %We have developed four different tools (\sattool, \smttool, \qbftool, \ourtool) for implementation of proposed encodings.
 %
-We have developed the {\vtstool} tool to conjecture the properties of the VTS (explained in Section 6). 
+\noindent We have developed the {\vtstool} tool to conjecture the properties of the VTS (explained in Section 6). 
 %
@@
 %The existential condition problem is implemented with two separate encodings.
-We have implemented two separate encodings to determine the existential condition of the VTS. 
+\noindent We have implemented two separate encodings to determine the existential condition of the VTS. 
 %To solve the existential condition we have implemented two separate encodings. 
@@
 
-\textbf{{\sattool (Bounded model checker based tool)}}:
+\textbf{{\sattool (Bounded model checker based tool)}}
 The $\fbmc$ encoding based on enumeration of paths (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
@@
 
-\textbf{{\smttool} (SMT based tool)}:
+\textbf{{\smttool} (SMT based tool)}
 The $\fsmt$ encoding based on recursive reachability definition (presented in section 6.1)  
@@
 
-\textbf{{\qbftool} (QBF based universal condition):}
+\textbf{{\qbftool} (QBF based universal condition)}
 The $\fqbf$ encoding (presented in section 6.5) is implemented in the {\qbftool}. 
@@
 
-\textbf{{\ourtool} (QBF based synthesis tool):}
+\textbf{{\ourtool} (QBF based synthesis tool)}
 \input{synth-table}
@@
 \subsection{Results}
-The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\qbftool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
+\noindent The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\qbftool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
 
@@
 %%
-Biologically, these queries represent different levels of changes that we can make in order to complete these graphs.
+For biological cells, these queries represent different levels of changes that we can make in order to complete the missing information.
 %

### 2019-04-02 papers/journal/intro.tex
Updated macro to disallow verticle watage of space by subsubparagraph
Uniform use of the title without :

@@
-A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
+\noindent A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
 %
@@
 \subsection{Vesicle traffic system}
-%Vesicles were discovered decades ago, in the early 1950s, and
-
-The major molecules involved in the vesicle traffic system~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
+%Vesicles were discovered decades ago, in the early 1950s, and s
+\noindent The major molecules involved in the vesicle traffic system~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
 %
@@
 
-\subsubsection{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
+\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
 %
@@
 
-\subsubsection{Vesicle fusion involves two steps} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
+\subsubsection{Vesicle fusion} The vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
 
@@
 \subsection{The model}
-The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
+\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
 %
@@
 \end{enumerate}
+
 %On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
@@
 
-In this section, we will abstract from the biological description of the VTS and represent the whole network as an annotated transport graph. 
+\noindent In this section, we will abstract from the biological description of the VTS and represent the whole network as an annotated transport graph. 
 %
@@
 %The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
-\subsection{Graph connectivity is an interesting and accessible property of the VTS.} 
+\subsection{Graph connectivity is an interesting and accessible property of the VTS} 
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
-Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
+\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
 %
@@
 \subsection{Combinatorial problem and use of Formal methods}
-The analysis of vesicle traffic systems is a difficult problem
+\noindent The analysis of vesicle traffic systems is a difficult problem
 because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
@@
 
-\subsubsection{Size of the system}
+\subsubsection{Size of the VTS system}
 Let us discuss rough sizes of the system and expected behaviors.
@@
 \subsection{Synthesis of VTS }
-The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
+\noindent The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
 %
@@
 In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.
-
+%
 %%% Local Variables:

### 2019-04-02 papers/journal/model.tex
Update to bmc:05
Uniform use of the title without :

--- 2019-03-10 papers/journal/model.tex
@@
-In this section, we will present our formal model of VTS.
+\noindent In this section, we will present our formal model of VTS.
 %
@@
 
-\ashu{Should be written bio people}
-Let us discuss rough sizes of the system and expected behaviors.
+%Let us discuss rough sizes of the system and expected behaviors.
+%%
+%A typical VTS may have about 10 compartments.
+%%
+%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
+%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
+%%
+%The VTS may transport a large number of molecules but the molecules that
+%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
+%%
+%According to the definition the activity of molecules can be controlled by
+%the presence of all other molecules.
+%%
+%However, in practice the activity of a molecule is controlled by
+%the presence of ~2-3 other molecules.
+%A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
+%%
+%The organellar content of cells vary across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhopteries and micronemes~\cite{gubbels2012evolution}.
+%%
+%The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
+%%
+%Also, across different cell-types, these organelles may be more or less differentiated, for example, number of stacks in the Golgi vary across different cells~\cite{polishchuk2004structural}. 
+%%
 %
-A typical VTS may have about 10 compartments.
-%
-%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
-%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
-%
-The VTS may transport a large number of molecules but the molecules that
-are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
-%
-According to the definition the activity of molecules can be controlled by
-the presence of all other molecules.
-%
-However, in practice the activity of a molecule is controlled by
-the presence of ~2-3 other molecules.
+%Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
+%%
+%The VTS transports a large number of molecules but the molecules that actively control the system are in their tens [MBOC]. 
+%%
+%By definition the activity of any VTS molecules can be controlled by all other molecules.
+%%
+%However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}.
+%%
+%Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
+%%
+%But most VTS molecules have more localized influence.
+%%
+%We use the above information during the encoding of all search problems presented later.
 

### 2019-04-02 papers/journal/prelim.tex
Uniform use of the title without :

@@
-We will use lower case variables like $e,r,s$ etc to represent vectors of
+\noindent We will use lower case variables like $e,r,s$ etc to represent vectors of
 Boolean variables, possibly indexed, with multiple dimensions.
@@
 \subsection{Solvers}
-In this paper, we will encode several problems into finding satisfying
+\noindent In this paper, we will encode several problems into finding satisfying
 solutions of a Boolean formula or QBFs.

### 2019-04-02 papers/journal/problem.tex
Uniform use of the title without :

@@
-This section will present the different search problems of VTS.
+\noindent This section will present the different search problems of VTS.
 %
@@
 \subsection{Existential condition}
-We employ two techniques to examine the existential condition. 
+\noindent We employ two techniques to examine the existential condition. 
 %
@@
 %Here we will present the QBF.
-We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
+\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
 %
@@
 %
-We also consider another variant of analysis of VTSs.
+\noindent We also consider another variant of analysis of VTSs.
 %
@@
 
-\subsubsection{Synthesis problem}
+\subsubsection{Synthesis problem.}
 

### 2019-04-02 papers/journal/intro.tex
Moved the discussion about the size of the system upfront

--- 2019-04-02 papers/journal/intro.tex
@@
 
-\subsubsection{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
+\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
 %
@@
 
-\subsubsection{Vesicle fusion involves two steps} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
+\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
 
@@
 %\somya{schematic of snare regulatory network}
-\subsubsection{Schematic of snare regulatory network}
+\textbf{Schematic of snare regulatory network:}
 In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
@@
 %\somya{schematic of intracellular compartments and  major routes}
-\subsubsection{Major paths in the vesicle transport network}
+\textbf{Major paths in the vesicle transport network}:
 Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
@@
 The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.
+
 %
+
 %\begin{table}
@@
 \subsection{The model}
-The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
+\todo{Ankit: The Rothman model has no intuition; Add couple of lines relating it to VTS; Also, relate it to previous subsection.
+The connect is lacking.} The VTS model for this paper is inspired by~\cite{shukla2017discovering}.
 %
@@
 \item Compartments are neither created nor destroyed.
-\item Each compartment is in steady state, gain and loss of the molecules is balance.
+\item Each compartment is in steady state, gain and loss of the molecules is balance\todo{Ankit: Need intuition and also reasoning why this is okay to add this as an assumption}.
 \item Molecules are neither created nor destroyed.
@@
 \end{enumerate}
+
+\todo{Ankit: Need some additional discussion;4 lines max about the legitamecy of the assumptions.}
 %On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
@@
 
-\subsubsection{The cell as a transport graph} 
+\textbf{The cell as a transport graph:} 
 %We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph.
@@
 
-\subsubsection{Steady state} 
+\textbf{Steady state:} 
 The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
@@
 
-\subsubsection{Vesicle fusion}
+\textbf{Vesicle fusion:}
 %Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
@@
 
-\subsubsection{Molecular regulation} 
+\textbf{Molecular regulation:} 
 Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.

### 2019-04-03 papers/journal/encoding.tex
Updated the 1.2

@@
 In the following, the formula encodes that only $slimit$ edge labels may be added.
+%
 \begin{align*}
@@
 \end{align*} 
+%
 Similar to the previous encoding, we solve the
@@
 that may be added to the edge labels to satisfy the properties.
-
+%
 \subsubsection{Fixing VTS by learning activity functions}

### 2019-04-03 papers/journal/intro.tex
Updated the 1.2

--- 2019-04-02 papers/journal/intro.tex
@@
 \item A cell is a set of compartments exchanging vesicles.
-\item Compartments are neither created nor destroyed.
-\item Each compartment is in steady state, gain and loss of the molecules is balance.
-\item Molecules are neither created nor destroyed.
+\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
+\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
+\item Molecules are neither created nor destroyed~\cite{he2009differential}.
 \item Molecules move via vesicles of uniform size.
-\item Identical vesicles have identical target compartments.
-\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
+\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
+\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
 %\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
-\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
-\item An active SNARE pair is necessary and sufficient for fusion. 
+\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
+\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
+. 
 \end{enumerate}
-
+%
+All our assumptions, except assumption 5, are held up by cell biological results.
+%
+Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence, for the sake of simplicity, we assume a uniform size for intracellular vesicles.
+%The assumptions 
 %On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
@@
 %
-\begin{example}
+%\begin{example}
+%	%
+%	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool.
+The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.
 %	
-	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool.
-The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.
-
-\end{example}
-\input{synth-dia}
+%\end{example}
+%\input{synth-dia}
 

### 2019-04-03 papers/journal/prelim.tex
Updated the 1.2

@@
 %
-The problem of finding satisfying assignment for QBFs is even harder problem~\cite{arora2009computational}.
+The problem of finding satisfying assignment for QBFs is even harder problem~\cite{arora2009computational}.\\
 %
 
-\subsection{Solvers}
-\noindent In this paper, we will encode several problems into finding satisfying
+\subsubsection{Solvers}
+In this paper, we will encode several problems into finding satisfying
 solutions of a Boolean formula or QBFs.

### 2019-04-03 papers/journal/synth-dia.tex
Vts dia update
Updated the 1.2

--- 2019-03-11 papers/journal/synth-dia.tex
@@
 \begin{figure}[t]
-%	\centering
+	\centering
 	%\begin{minipage}{0.45\linewidth
  \begin{subfigure}[b]{0.49\linewidth}
+%\begin{tikzpicture}[node distance = 30mm]
 
-	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.0cm,
-	  thick,main node/.style={rectangle,draw}]
-	 % 	\begin{scope}[]
-	  \node[main node, text width=1.5cm] (pm) {PM { \^{Qa5} 
-	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};
+\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
+thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
+\begin{scope}[]
 
-	  %le <-> pm
-	  \path (le) edge[bend right=30] node [above] {Qb7 Qc7} (pm);
-	  %ee -> le
-	  \path (ee) edge[bend right, text width=3.0cm] node [below,rotate=65] {\^{R8},Qa7, Qbc7,R7} (le);
+\node[main node] (1) {$s_{1}$};
+\node[main node] (2) [below left of=1] {$s_{2}$};
+\node[main node] (3) [below right of=1] {$s_{3}$};
 
-	  %pm <-> ee
-	  \path (ee) edge[bend left=30] node [above] {\^{R3}} (pm);
-	  \path (pm) edge[bend left=30, text width=2.5cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
+\path[every node/.style={font=\sffamily\small}]
+(3) edge node [left] {} (1)
+(1) edge [loop above] node {} ()
+(2) edge [loop above] node {} ()
+(1) edge node [right] {} (2)
+(2) edge node[right] {} (3)
+(3) edge[bend left, below] node{} (2);
+%(3) edge [bend right] node[right] {} (2)
+\end{scope}
+%	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
+%	  thick,main node/.style={rectangle,draw}]
+%	 % 	\begin{scope}[]
+%	  \node[main node] (pm) {08};
+%	  \node[main node] (ee) [below right of=pm] {346};
+%	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {1 2 7 9};
+%	
+%	  %le <-> pm
+%	  \path (le) edge[bend right=55] node [above] {Qb7 Qc7} (pm);
+%	  %ee -> le
+%	  \path (ee) edge[bend right=32, text width=2.0cm] node [below,rotate=55] {\^{R8},Qa7, Qbc7,R7} (le);
+%	
+%	  %pm <-> ee
+%	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
+%	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
 	\end{tikzpicture}
+	\caption{Input partial VTS} 
+		 \label{fig:synth-vts1}
   \end{subfigure}%
@@
   \begin{subfigure}[b]{0.49\linewidth}
-	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.0cm,
-	  thick,main node/.style={rectangle,draw}]
-	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
-	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
-	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};
+%	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
+%	  thick,main node/.style={rectangle,draw}]
+%	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
+%	  \node[main node,text width=1.5cm] (pm) {\textbf{PM:} {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
+%	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
+%	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {\textbf{LE:} {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};
+%	  
+%	  %le <-> pm
+%	  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
+%	  
+%	  %le <-> ee
+%	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
+%	  }}
+%	  %ee -> le
+%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8},Qa7, Qbc7,R7} (le);	  
+%	  
+%	  %pm <-> ee
+%	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {\^{R3, {\color{blue} { \textbf{\^{Qa2}, \^{Qa7}, \^{R2}}}}}} (pm);
+%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
+%	 % \end{scope}
+\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
+thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
+\begin{scope}[]
 
-	  %le <-> pm
-	  \path (le) edge[bend right=30] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
+\node[main node] (1) {$s_{1}$};
+\node[main node] (2) [below left of=1] {$s_{2}$};
+\node[main node] (3) [below right of=1] {$s_{3}$};
 
-	  %le <-> ee
-	  {\color{red} { \path (le) edge[bend right] node [below,rotate=70] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
-	  }}
-	  %ee -> le
-	  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7, Qbc7,R7} (le);
-
-	  %pm <-> ee
-	  \path (ee) edge[bend left=30] node [above] {\^{R3, {\color{blue} { \textbf{\^{Qa2,}, \^{Qa7}, \^{R2}}}}}} (pm);
-	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
-	 % \end{scope}
+\path[every node/.style={font=\sffamily\small}]
+(3) edge node [left] {} (1)
+(1) edge [loop above] node {} ()
+(2) edge [loop above] node {} ()
+(1) edge node [right] {} (2)
+(2) edge node[right] {} (3)
+(3) edge[bend left, below] node{} (2);
+%(3) edge [bend right] node[right] {} (2)
+\end{scope}
 	 \end{tikzpicture}
+	 \caption{Output complete VTS} 
+	 \label{fig:synth-vts2}
   \end{subfigure}%
-  \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}
+  \caption{An example of synthesis of edge and molecules in the partial VTS.} \label{fig:synth-vts}
 \end{figure}

### 2019-04-03 papers/journal/abstract.tex
Updated dia and results fix

--- 2018-10-02 papers/journal/abstract.tex
@@
-Vesicle Traffic Systems (VTSs) are the material transport 
-mechanisms among the compartments inside the biological cells.
+Vesicle Traffic Systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
 %
-The compartments are viewed as nodes that are labeled with the
-containing chemicals and the transport channels
-are similarly viewed as labeled edges between the nodes.
+The compartments are viewed as nodes that are labeled by their chemical identity and the transport vesicles are similarly viewed as labeled edges between the nodes.
 %
-Understanding VTSs is an ongoing area of research and for many cells
-they are partially known.
+Several interesting questions about VTSs translate to combinatorial search and synthesis problems. 
 %
-For example, there may be undiscovered edges, nodes, or their labels
-in a VTS of a cell.
+We present novel SAT, SMT and QBF based encodings of the properties over vesicle traffic systems.
 %
-It has been speculated that there are properties that the VTSs must
-satisfy.
+We have implemented the presented encoding in a tool that searches for the networks that satisfy properties related to transport consistency conditions using these solvers. 
 %
-For example, stability, i.e., every chemical that is leaving a
-compartment comes back.
+In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.
 %
-Many synthesis questions may arise in this scenario, where we want
-to complete a partially known VTS under a given property.
+Understanding VTSs is an ongoing area of
+research and for many cells they are partially known. 
 %
-In the paper, we present novel encodings of the above questions
-into the QBF (quantified Boolean formula) satisfiability problems.
+For example, there
+may be undiscovered edges, nodes, or their labels in a VTS of a cell. 
 %
-We have implemented the encodings in a highly configurable tool
-and applied to a couple of found-in-nature VTSs and 
-several synthetic graphs.
+It has been speculated that there are properties that the VTSs must satisfy.
+For example, stability, i.e., every chemical that is leaving a compartment
+comes back. 
+%
+Many synthesis questions may arise in this scenario, where
+we want to complete a partially known VTS under a given property.
+%
+In the paper, we present novel encodings of the above questions into
+the QBF (quantified Boolean formula) satisfiability problems. 
+%
+We have implemented the encodings in a highly configurable tool and applied to a
+couple of found-in-nature VTSs and several synthetic graphs.
 %
 Our results demonstrate that our method can scale up to the graphs of interest.
-
 % Vesicle Traffic Systems(VTSs) are the material transport 

### 2019-04-03 papers/journal/synth-table.tex
results update
Updated dia and results fix

@@
 		plos2-dia[4C] & 2.02 & 0   & 2.38 & 0  & 4.27  & 0 & 5.94 & 0 &  3.30 & 0 \\\hline
-		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 5 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -1AN. +1E, +4PE, +4N, +2AN, +2AE. \\\hline
-		node4[3C]  & 5.93  & 1 E   &  13.72 & 12 PE  &  5.09  & $\infty$ & 4.30 &$\infty$& 7.21  & -2 E, -2PE, -1 N, -1AN, -1 AE. +12 N, +8E, +1PE.\\\hline
+		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 7 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -4AN. +1 E, +5PE, +4N, +3AN, +3AE. \\\hline
+		node4[3C]  & 5.93  & 1 E   &  13.72 & 12 PE  &  5.09  & $\infty$ & 4.30 &$\infty$& 7.21  & -2 E, -2PE, -1 N, -1AN, -1 AE. +18N, +8E, +1PE.\\\hline
 		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
@@
 		plos2-dia & 3.97 & 0 &  2.26 & 0  & 5.46 & 0 & 5.35 & 0 & 3.24 & 0 \\\hline
-		sub-mammal & 3.22 & 1 E  & 4.18 & 5 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -1AN. +1 E, +4PE, +4N, +2AN, +2AE \\\hline
-		node4  & 4.01  & 1 E  & 10.19  & 12 PE & 4.26  & $\infty$ & 4.13 &$\infty$&  6.89  & -2 E, -2PE, -1N, -1AN, -1AE. +12N, +8E, +1PE \\\hline
+		sub-mammal & 3.22 & 1 E  & 4.18 & 7 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -4AN. +1 E, +5PE, +4N, +3AN, +3AE \\\hline
+		node4  & 4.01  & 1 E  & 10.19  & 12 PE & 4.26  & $\infty$ & 4.13 &$\infty$&  6.89  & -2 E, -2PE, -1N, -1AN, -1AE. +18N, +8E, +1PE \\\hline
 		yeast-graph & 38.68  & 2 E  &   127.45  & 15 PE   & 1002.41  & 2 E  & 434.08   & 2 E & 197.82  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline

### 2019-04-03 papers/journal/abstract.tex
Updated abstarct

--- 2019-03-20 papers/journal/abstract.tex
@@
 %
-We present novel SAT, SMT and QBF based encodings of the properties over vesicle traffic systems and a tool that searches for the networks that satisfy properties that are related to transport consistency conditions using these solvers.
+We present novel encoding based on Boolean satisfiability (SAT), satisfiability modulo theories (SMT) and quantified Boolean formula (QBF) of the properties over vesicle traffic systems.
+%
+We have implemented the presented encoding in a tool that searches for the networks that satisfy properties related to transport consistency conditions using these solvers. 
 %
 In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.
-
+%
+%Understanding VTSs is an ongoing area of research and for many cells they are partially known. 
+%
+%We do not have a complete picture of the VTS graph, and in many cases we know only partial information known.
+%
+The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
+%Complete picture of VTSs are not clear and only partial 
+%For example, there may be undiscovered edges, nodes, or their labels in a VTS of a cell. 
+%
+%In this sense the picture of the VTS graphs is only partially complete. 
+%
+It has been speculated that there are properties that the VTSs must satisfy.
+For example, stability, i.e., every chemical that is leaving a compartment
+comes back. 
+%
+\todo{Text below this is just a copy of last paper}Many synthesis questions may arise in this scenario, where we want to complete a partially known VTS under a given property.
+%
+In the paper, we present novel encodings of the above questions into
+the QBF satisfiability problems. 
+%
+We have implemented the encodings in a highly configurable tool and applied to a couple of VTSs found in the literature and to several synthetic graphs.
+%
+Our results demonstrate that our method can scale up to the graphs of interest.
 % Vesicle Traffic Systems(VTSs) are the material transport 

### 2019-04-03 papers/journal/property.tex
Uniform use of the title without :
Updated abstarct

@@
-We analyze the model against our desired properties.
+\noindent We analyze the model against our desired properties.
 %
-\ankit{Not completely correct}Since in biology there are no declared specifications or properties,
-we conjecture some properties that appear to be true in all the known
+Since in biology there are no declared specifications or properties,
+we conjecture some properties that appear to be 
+%true in 
+relevant in
+all the known
 biological systems.
@@
 %To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.
-
+%
 %%% Local Variables:

### 2019-04-03 papers/journal/conclusion.tex
Updated abstarct

--- 2019-03-10 papers/journal/conclusion.tex
@@
+\noindent 
+%
+We do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries.
+%
 In this paper, we presented encodings of the synthesis problems
 that may arise from VTSs.
+%
 %
@@
 %
+%
+With this tool, we made an attempt to present multiple new testable predictions. 
+%
 We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
 %
+These predictions may very likely increase to hasten discoveries in this field alongside pushing forward the use of formal methods in the biological field.
+
 Our model of VTSs is static graphs.
@@
 
-\ankit{A rough outline of the answers needed in the future work section}
-\begin{enumerate}
-  \item why this tool was biologically helpful?
-        \begin{itemize}
-        	\item we do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries.
-        	\item With this tool, we make multiple new easily testable predictions. So it is very likely to hasten discoveries in this field.
-        \end{itemize}
-  \item What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
-\end{enumerate}
-
-\textbf{Encode Dynamic behaviour of the VTS:} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation.
+However, there are a few aspects in the modeling that we have relaxed.
+%  \item What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
+%\end{enumerate}
+%\textbf{Encode Dynamic behaviour of the VTS}
+A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation.
 Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.

### 2019-04-03 papers/journal/conclusion.tex
Updated conclusion

@@
 %
-In this paper, we presented encodings of the synthesis problems
+\todo{Copied! Need revision}In this paper, we presented encodings of the synthesis problems
 that may arise from VTSs.
@@
 
-Our model of VTSs is static graphs.
+%Our model of VTSs is static graphs.
 %
-In future, we will study the dynamic behaviors of VTSs.
-%
-It will allow us to predict behaviors after the perturbations in the VTSs
-and more ways to test the predicted synthesis results.\\
-
 However, there are a few aspects in the modeling that we have relaxed.
@@
 A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation. 
+%
+We have only analyzed the VTS as a static graphs.
+%
 Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.
+%
 Maturation  is  evident  in  the  Golgi  apparatus  and  in  the  endocytic system. 
+%
 Including this behaviour of the compartments in the model would allow it to make more accurate predictions.

### 2019-04-03 papers/journal/conclusion.tex
Updated conclusion

@@
 %
+\todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the
+value of careful encoding of the problems into SMT queries. 
+%
+We manage to scale the tool upto the size that makes tool biologically relevant. However, there are many further search problems or extensions that are of interest. 
+%
+For example, are there any k-connected graphs that can not be annotated into a VTS? 
+%
+This problem induces a quantifier alternation in an encoding. Therefore, a simple call to SAT solver will not work. 
+%
+We are planning to use QBF(quantified Boolean
+formulas) solvers or develop iterative search algorithm for such queries.
+%
+One may be interested in counting the number of graphs that satisfy a given
+property. 
+%
+Exact counting of the graphs using SAT solvers may prove to be very
+difficult. 
+%
+We are also planning to employ some methods for approximate counting
+of solutions.
+
 We do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries.
 %
-\todo{Copied! Need revision}In this paper, we presented encodings of the synthesis problems
+\todo{Copied till para end! Need revision}In this paper, we presented encodings of the synthesis problems
 that may arise from VTSs.

### 2019-04-03 papers/journal/conclusion.tex
Updated conclusion

@@
 %
+\todo{Copid just to create a template}
+We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
+%
+Our results contain many predictions which can in
+principle be tested through cell-biological experiments. 
+%
+However, our current knowledge of the actual vesicle transport graph of a cell is very poor: it is likely that there are many vesicle transport routes that are still uncharacterized.
+Even in those instances where vesicles are known to exist, the precise molecular drivers of their creation and fusion are often unknown.
+%
+Therefore, a direct verification of our predictions based on graph connectedness alone is not likely. 
+%
+However, more indirect predictions based on how SNAREs are regulated can be
+explored. 
+%
+In this context, the Sec/MUNC proteins or SNARE longin domains are interesting
+targets of study~\cite{van2010one,rossi2004longins}.
+
 \todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the

### 2019-04-03 papers/journal/encoding.tex
Updated Pairing encoding for the SMT

@@
 \end{align*}
-\noindent We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs and R-SNAREs to R-SNAREs in the pairing matrix to be all 0's.
+\noindent We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of R-SNAREs to R-SNAREs in the pairing matrix to be all 0's.
 %It reduces the search space.
@@
 \begin{align*}
- \texttt{PairingC} =\;& \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
+ \texttt{PairingC} =\;& \bigwedge\limits_{(x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
 \end{align*}

### 2019-04-04 papers/journal/conclusion.tex
Updated Pairing encoding for the SMT

@@
 %
-\todo{Copid just to create a template}
+\todo{Just a template}
 We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
@@
 
-\todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the
+%\todo{Copid just to create a template}
+In the experiments, we have demonstrated the power of SMT solvers and the
 value of careful encoding of the problems into SMT queries. 
@@
 %
-\todo{Copied till para end! Need revision}In this paper, we presented encodings of the synthesis problems
+%\todo{Copied till para end! Need revision}
+In this paper, we presented encodings of the synthesis problems
 that may arise from VTSs.

### 2019-04-04 papers/journal/intro.tex
Updated Pairing encoding for the SMT

@@
 When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
-And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].
+And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected.
 

### 2019-04-04 papers/journal/conclusion.tex
Todo added again in abstract and conclusion

--- 2019-04-03 papers/journal/conclusion.tex
@@
 %
-\todo{Copid just to create a template}
+\todo{copied frm the PLOS paper to Just a template}
 We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
@@
 
-\todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the
+\todo{Copid just to create a template}
+In the experiments, we have demonstrated the power of SMT solvers and the
 value of careful encoding of the problems into SMT queries. 
@@
 %
-\todo{Copied till para end! Need revision}In this paper, we presented encodings of the synthesis problems
+\todo{Copied till para end! Need revision}
+In this paper, we presented encodings of the synthesis problems
 that may arise from VTSs.

### 2019-04-04 papers/journal/encoding.tex
added clarification for the 3 problems and 4 envodings

@@
 %\externaldocument{qbf-table}
-\noindent In the previous section, we have discussed four problems.
-%
-In this section we will present encodings fof the
-$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
-%
-We will start with the $\fsmt$ search encoding and later present the
-contrast with the $\fbmc$ encoding.
+\noindent In the previous section, we have discussed four problems, $\fbmc$ search, $\fsmt$ search, $\fqbf$ search and synthesis problem.
+%
+In this section we will present encodings for each of them.
+%
+Although the underlying technique for $\fbmc$ and $\fsmt$ search varies, the encoding is very similar. 
+%
+So, instead of presenting both 
+%$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
+%
+we will start with the complete $\fsmt$ search encoding and present only the relevant part of the the $\fbmc$ encoding to show a contrast.
+%contrast with the $\fbmc$ encoding.
 

### 2019-04-04 papers/journal/intro.tex
VTS dia update: first attempt
Synthesis dia added back
Updated the VTS Examples

@@
 %
+%\begin{table}[!t]
+%	\caption{Table Caption}
+%	\label{tab1}
+%	\centering
+%	{\setlength\tabcolsep{0.1pt}%
+%		\begin{tabular}{ccccccccccccccc}
+%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
+%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
+%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
+%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
+%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
+%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
+%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
+%	\end{tabular}}
+%\end{table}
 
@@
 %
-In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
+In figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 16 molecules, and a corresponding pairing matrix.
 %
-Molecules are numbered 0-7.
+Molecules are represented as $Q_{i}$ or $R_{i}$.
 %
-In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
+In the VTS, labels are a string of molecule, and red color text indicates that the molecule is active.
 %
-Every molecule on the node is active.
+The activity of the molecules are controlled
+by presence of the other molecules. 
+%Every molecule on the node is active.
 %
-The activity of the molecules on an edge are controlled
-by presence of the other molecules on the edge.
+The activity of the molecules on an edge is determined by the corresponding pairing matrix on the edge.
 %
-On the right side of the figure, we show the pairing matrix.
+Below of the figure, we show the pairing matrix.
 %
@@
 %
-This is a 3-connected graph.
+This is a 4-connected graph.
 \end{example}
@@
 %
+\begin{example}
+	%
+	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS.
+The synthesis is performed on the basis of steady state property and the  3-connectivity of the graph.
+PM, EE, LE are the tags representing the node.
+Edge in the red colour represent the added edge and molecules in blue represent added molecules on the corresponding edge by synthesis.
+For the sake of clarity we have not presented the activity, pairing matrix and rest of the molecules on the nodes.
+
+\end{example}
+\input{synth-dia}
 
@@
 %
-%\begin{example}
-%	%
-%	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool.
-The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.
-%	
-%\end{example}
-%\input{synth-dia}
 

### 2019-04-04 papers/journal/synth-dia.tex
Synthesis dia added back
Updated the VTS Examples

--- 2019-03-12 papers/journal/synth-dia.tex
@@
 \begin{figure}[t]
-%	\centering
+	\centering
 	%\begin{minipage}{0.45\linewidth
  \begin{subfigure}[b]{0.49\linewidth}
+%\begin{tikzpicture}[node distance = 30mm]
 
+%\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
+%thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
+%\begin{scope}[]
+%
+%\node[main node] (1) {$s_{1}$};
+%\node[main node] (2) [below left of=1] {$s_{2}$};
+%\node[main node] (3) [below right of=1] {$s_{3}$};
+%
+%\path[every node/.style={font=\sffamily\small}]
+%(3) edge node [left] {} (1)
+%(1) edge [loop above] node {} ()
+%(2) edge [loop above] node {} ()
+%(1) edge node [right] {} (2)
+%(2) edge node[right] {} (3)
+%(3) edge[bend left, below] node{} (2);
+%%(3) edge [bend right] node[right] {} (2)
+%\end{scope}
  \begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
@@
 	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
-	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
+	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2}, {Qa7} Qbc7, R7, Qc7, Qa2,} (ee);
 	\end{tikzpicture}
+	\caption{Input partial VTS} 
+		 \label{fig:synth-vts1}
   \end{subfigure}%
@@
 	  %ee -> le
-	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8},Qa7, Qbc7,R7} (le);
+	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8}, Qa7, Qbc7,R7} (le);
 
@@
 	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {\^{R3, {\color{blue} { \textbf{\^{Qa2}, \^{Qa7}, \^{R2}}}}}} (pm);
-	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
+	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
 	 % \end{scope}
+
 	 \end{tikzpicture}
+	 \caption{Output complete VTS} 
+	 \label{fig:synth-vts2}
   \end{subfigure}%
-  \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}
+  \caption{An example of synthesis of edge and molecules in the partial VTS.} \label{fig:synth-vts}
 \end{figure}

### 2019-04-05 papers/journal/intro.tex
Added complete discusision of the example

@@
 %\end{table}
-
+%
 \begin{example}
@@
 %
-Molecules are represented as $Q_{i}$ or $R_{i}$.
+Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
 %
-In the VTS, labels are a string of molecule, and red color text indicates that the molecule is active.
+In the VTS, labels are a string of molecule, and red colored molecules are active.
 %
-The activity of the molecules are controlled
-by presence of the other molecules. 
+On the node, the activity of molecules is controlled
+by the presence of the other molecules (exact Boolean function is not shown). 
 %Every molecule on the node is active.
@@
 %
-$\times$ represents no pairing.
+0 represents no pairing.
 %
@@
 \label{subsec:graphmodel}
-
+%
 \subsection{Combinatorial problem and use of Formal methods}
@@
 	%
-	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS.
-The synthesis is performed on the basis of steady state property and the  3-connectivity of the graph.
-PM, EE, LE are the tags representing the node.
-Edge in the red colour represent the added edge and molecules in blue represent added molecules on the corresponding edge by synthesis.
-For the sake of clarity we have not presented the activity, pairing matrix and rest of the molecules on the nodes.
+	In figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
+	%
+	The synthesis is performed against the steady state property and 3-connectivity.
+The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for proper discussion about the nodes and molecules).
+	%
+	Synthesized edge is in red color and synthesized molecules are represented with blue.
+	 %
+	For clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
 

### 2019-04-05 papers/journal/intro.tex
Added complete discusision of the example

@@
 	The synthesis is performed against the steady state property and 3-connectivity.
-The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for proper discussion about the nodes and molecules).
+The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for proper discussion about the nodes and molecules depicted in the diagram).
 	%

### 2019-04-05 papers/journal/synth-dia.tex
Dia is complete

@@
 	 % 	\begin{scope}[]
-	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { \^{Qa5} 
-	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
-	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { \^{Qa8} \^{Qb8} \^{Qc8}}};
+	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
+	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}};
+	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}};
+	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}};
 
 	  %le <-> pm
-	  \path (le) edge[bend right=55] node [above] {Qb7 Qc7} (pm);
-	  %ee -> le
-	  \path (ee) edge[bend right=32, text width=2.0cm] node [below,rotate=55] {\^{R8},Qa7, Qbc7,R7} (le);
+	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$ $Q_{c7}$} (pm);
+	   \path (ee) edge[bend right=32, text width=2.0cm] node [below,right=0.1] {{$R_{8}$},$Q_{a7}$, $Q_{b7}$,$R_{7}$} (le);
 
 	  %pm <-> ee
-	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
-	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2}, {Qa7} Qbc7, R7, Qc7, Qa2,} (ee);
+	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
+	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
 	\end{tikzpicture}
@@
 	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
-	  \node[main node,text width=1.5cm] (pm) {\textbf{PM:} {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
-	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {\textbf{LE:} {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};
+	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
+	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$} ...}};
+	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $} ...}};
+	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$} ...}};
 
 	  %le <-> pm
-	  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
+	  	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$ $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
+	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
 
 	  %le <-> ee
-	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
+	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {{\color{blue} { {\textbf{{$R_{8}$}}}}}{\color{black},} {\color{blue} {$Q_{a7}$}}} (ee);
 	  }}
 	  %ee -> le
-	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8}, Qa7, Qbc7,R7} (le);
+	   \path (ee) edge[bend right=32, text width=2.0cm] node [below,right=0.1] {{$R_{8}$},$Q_{a7}$, $Q_{b7}$,$R_{7}$} (le);
+%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);
 
 	  %pm <-> ee
-	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {\^{R3, {\color{blue} { \textbf{\^{Qa2}, \^{Qa7}, \^{R2}}}}}} (pm);
-	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
+	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
+	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below] {\color{blue} { \textbf{$R_{3}$}}} (ee);
+%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
 	 % \end{scope}

### 2019-04-05 papers/journal/synth-dia.tex
Dia is complete

@@
 	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
-	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below] {\color{blue} { \textbf{$R_{3}$}}} (ee);
+	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{$R_{3}$}}} (ee);
 %	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    

### 2019-04-05 papers/journal/synth-dia.tex
Dia is complete
Dia is complet

@@
  \begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
-	  thick,main node/.style={rectangle,draw}]
+	  thick,main node/.style={rectangle,draw,rounded corners}]
 	 % 	\begin{scope}[]
@@
 	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
-	  thick,main node/.style={rectangle,draw}]
+	  thick,main node/.style={rectangle,draw,rounded corners}]
 	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
@@
 	  %le <-> pm
-	  	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$ $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
+	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$ $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
 	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

### 2019-04-05 papers/journal/synth-dia.tex
Dia is complet

@@
 	  %le <-> pm
-	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$ $Q_{c7}$} (pm);
-	   \path (ee) edge[bend right=32, text width=2.0cm] node [below,right=0.1] {{$R_{8}$},$Q_{a7}$, $Q_{b7}$,$R_{7}$} (le);
+	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$, $Q_{c7}$} (pm);
+	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
 
@@
 	  %le <-> pm
-	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$ $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
+	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$, $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
 	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
@@
 	  %ee -> le
-	   \path (ee) edge[bend right=32, text width=2.0cm] node [below,right=0.1] {{$R_{8}$},$Q_{a7}$, $Q_{b7}$,$R_{7}$} (le);
+	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
 %	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);

### 2019-04-05 papers/journal/synth-dia.tex
Dia is complet

@@
 	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
-	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{$R_{3}$}}} (ee);
+	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{    $R_{3}$}}} (ee);
 %	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    

### 2019-04-05 papers/journal/synth-dia.tex
Dia is complet

--- 2019-04-05 papers/journal/synth-dia.tex
@@
 	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
-	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
+	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
 	\end{tikzpicture}
@@
 	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
-	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{$R_{3}$}}} (ee);
+	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{    $R_{3}$}}} (ee);
 %	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    

### 2019-04-05 papers/journal/problem.tex
added clarification for the 3 problems and 4 envodings
Added additional diagram to fix the problem statement confusion

@@
 %
-We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition,
-and performing synthesis on the incomplete VTS.
+We categorize the search problem, Figure~\ref{fig:vts-search} into three different categories, search problem for existential condition, search problem for universal condition, and performing synthesis on the incomplete VTS.
+%
+We will present two encodings for existential condition and one each for universal condition condition and synthesis.
+
+\begin {figure}[!h]
+\centering
+\begin{adjustbox}{width=\columnwidth}
+{\Large
+%{	\scalefont{1.0}
+%\forestset{parent color/.style args={#1}{
+%		{fill=#1},
+%		for tree={fill/.wrap pgfmath arg={#1!##1}{1/level()*80},draw=#1!80!darkgray}},
+%	root color/.style args={#1}{fill={{#1!60!gray!25},draw=#1!80!darkgray}}
+%}
+
+\begin{forest}
+ /tikz/every node/.append style={font=\sffamily,minimum size=1.0cm},
+	for tree={
+		edge+={->,thick},% uncomment for arrows
+		draw,
+		rounded corners,
+		node options={align=center,},
+		text width=1.7cm,
+		calign=fixed edge angles, calign primary angle=-84,calign secondary angle=85,
+	%	anchor=center,	
+    %	calign=center,
+	},
+	where level=0{%
+		parent anchor=children,
+	}{%
+		folder,
+		grow'=0,
+		if level=1{% this changes the edges from level 0 to nodes at level 1
+			before typesetting nodes={child anchor=north},
+			edge path'={(!u.parent anchor) -- ++(0,-5pt) -| (.child anchor)},
+		}{},
+	}
+    [\textbf{VTS Search \\ Problems}, fill=white!20, parent, s sep=1mm,
+	[\textbf{Existential Condition}, for tree={fill=fv, child}, 
+	[BMC, for tree={fill=ai, child}]
+	[SMT \\, for tree={fill=ai, child}]
+	]
+	[\textbf{Universal Condition}, for tree={fill=fv, child},
+	[QBF, for tree={fill=ai, child}]
+	]
+	[\textbf{VTS Synthesis}, for tree={fill=fv,child}, 
+	[Synthesis, for tree={fill=ai, child}]
+	]
+	]
+\end{forest}
+}
+\end{adjustbox}
+\vspace{0.01cm}
+
+\begin{tikzpicture}
+\begin{customlegend}[legend columns=-1,legend style={draw=none,column sep=1ex},legend entries={ \small Problem Statement, \small Encodings}]
+\addlegendimage{fill=fv,area legend} 
+\addlegendimage{fill=ai,area legend} 
+%\addlegendimage{fill=ar,area legend}
+%\addlegendimage{red,fill=black!50!red,ybar,ybar legend}
+\end{customlegend}
+\end{tikzpicture}
+
+\caption{Overview of the VTS search problems with respective encodings}
+\label{fig:vts-search}
+\end{figure}
 

### 2019-04-05 papers/journal/problem.tex
Added additional diagram to fix the problem statement confusion

@@
 	[\textbf{Existential Condition}, for tree={fill=fv, child}, 
-	[BMC, for tree={fill=ai, child}]
-	[SMT \\, for tree={fill=ai, child}]
+	[BMC Sec.6.2, for tree={fill=ai, child}]
+	[SMT Sec.6.1\\, for tree={fill=ai, child}]
 	]
 	[\textbf{Universal Condition}, for tree={fill=fv, child},
-	[QBF, for tree={fill=ai, child}]
+	[QBF \\ Sec.6.3, for tree={fill=ai, child}]
 	]
 	[\textbf{VTS Synthesis}, for tree={fill=fv,child}, 
-	[Synthesis, for tree={fill=ai, child}]
+	[Synthesis Sec.6.4, for tree={fill=ai, child}]
 	]

### 2019-04-05 papers/journal/problem.tex
Added additional diagram to fix the problem statement confusion

--- 2019-04-05 papers/journal/problem.tex
@@
 %
-We will present two encodings for existential condition and one each for universal condition condition and synthesis.
+We will present Figure~\ref{fig:vts-search}, two encodings for existential condition and one each for universal condition condition and synthesis.
 
@@
     [\textbf{VTS Search \\ Problems}, fill=white!20, parent, s sep=1mm,
-	[\textbf{Existential Condition}, for tree={fill=fv, child}, 
-	[BMC, for tree={fill=ai, child}]
-	[SMT \\, for tree={fill=ai, child}]
+	[\textbf{1.Existential Condition}, for tree={fill=fv, child}, 
+	[BMC Sec.6.2, for tree={fill=ai, child}]
+	[SMT Sec.6.1\\, for tree={fill=ai, child}]
 	]
-	[\textbf{Universal Condition}, for tree={fill=fv, child},
-	[QBF, for tree={fill=ai, child}]
+	[\textbf{2.Universal Condition}, for tree={fill=fv, child},
+	[QBF \\ Sec.6.3, for tree={fill=ai, child}]
 	]
-	[\textbf{VTS Synthesis}, for tree={fill=fv,child}, 
-	[Synthesis, for tree={fill=ai, child}]
+	[\textbf{3.VTS Synthesis}, for tree={fill=fv,child}, 
+	[Synthesis Sec.6.4, for tree={fill=ai, child}]
 	]

### 2019-04-05 papers/journal/problem.tex
removed unwanted refernce

@@
 %
-We will present Figure~\ref{fig:vts-search}, two encodings for existential condition and one each for universal condition condition and synthesis.
+We will present two encodings for existential condition and one each for universal condition condition and synthesis.
 
@@
 \begin{tikzpicture}
-\begin{customlegend}[legend columns=-1,legend style={draw=none,column sep=1ex},legend entries={ \small Problem Statement, \small Encodings}]
+\begin{customlegend}[legend columns=-1,legend style={draw=none,column sep=1ex},legend entries={ \small Search Problems, \small Encodings}]
 \addlegendimage{fill=fv,area legend} 
@@
 We will do synthesis against the property that the VTS
-is stable and 3-connected.
+is stable and k-connected (k=3,4).
 %

### 2019-04-05 papers/journal/encoding.tex
removed unwanted refernce

@@
 %
-So, instead of presenting both 
+So, instead of presenting serially the complete encoding of both, 
 %$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
@@
 %
-Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
-% 
-The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
-%
+%Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are 
+%In $\fbmc$ we only partially unroll the program to check for the solutions within that subset. 
+%in the case of $\fbmc$, the encoding is not considerably different.
+% 
+In comparison to $\fsmt$, the $\fbmc$ search encodes reachability (both for the stability and connectivity) differently.  
+%]
 Here, we will only present the stability encoding.

### 2019-04-05 papers/journal/encoding.tex
BMC update

@@
 
-\noindent Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
+\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search problem~\cite{shukla2017discovering}.
 %
@@
 % 
-In comparison to $\fsmt$, the $\fbmc$ search encodes reachability (both for the stability and connectivity) differently.  
+The main difference between $\fsmt$ and $\fbmc$ is the encoding of 
+%I n comparison to $\fsmt$, the $\fbmc$ search encodes 
+reachability (both for the stability and connectivity).  
 %]

### 2019-04-07 papers/journal/intro.tex
Dia is complete
Added additional diagram to fix the problem statement confusion
Font problems fixed
First Read complete and Intro Fix errors checked grammar and todo listed typos fixed

@@
 %
-These compartments exchange molecules amongst themselves in small membrane-bounded packets called vesicles ~\cite{alberts2002molecular}. 
+These compartments exchange molecules amongst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
 %
-The molecular interaction network that controls the vesicle transport system involves dozens of varieties of molecules that regulate flow of cargo. 
+The molecular interaction network that controls the \unsure{Transport/Traffic}vesicle transport system involves dozens of varieties of molecules that regulate the flow of cargo. 
 %
@@
 %
-However, high complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
+However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}\change{Should only cite 3?}. 
 %The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
 In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
-
+%
 The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
@@
 Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
-
+%
 \subsection{Vesicle traffic system}
@@
 	%
-	Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
+	Here, different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
 	%
@@
 	%
-	At the target compartment the tethered vesicle undergoes fusion, thereby releasing its contents.}
+	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents.}
     \label{fig:vts}
@@
 
-\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
+\subsubsection{Vesicle budding} \unsure{Somya should we say it involve three mojor steps?
+This line is not optimal.
+Use of "see" okay?}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment, see Figure~\ref{fig:vts}.
 %
-Cargo sorting is performed by cytosolic adaptor proteins. 
+\unsure{new line start or this is ok?}Cargo sorting is performed by cytosolic adaptor proteins. 
 Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
@@
 %
-There are three major types of coat proteins: Clathrin, COP2 and COP1.
+There are three major types of coat proteins: Clathrin, COP2, and COP1.
 These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
@@
 
-\subsubsection{Vesicle fusion} The vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
+\subsubsection{Vesicle fusion} \info{Calling them process okay?}The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.
 
@@
 Distinct compartments of the cell are associated with distinct Rabs.
-For example, Rab5 is associated early endosomes and  Rab7 with late endosomes\cite{rink2005rab}.
+For example, Rab5 is associated with early endosomes and Rab7 with late endosomes~\cite{rink2005rab}.
 %
-Rabs are master regulators; in their active form Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment ~\cite{muller2018molecular}.
+Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment~\cite{muller2018molecular}.
 
@@
 %
-A clear mechanism for action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle, associated Rabs, SNAREs and SNARE regulators.
+A clear mechanism for the action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle, associated Rabs, SNAREs and SNARE regulators.
 %
@@
 
-The final step in vesicle transport is fusion of vesicle with the target compartment is brought about by SNARE proteins. 
+The final step in vesicle transport is the fusion of the vesicle with the target compartment is brought about by SNARE proteins. 
 %
@@
 	%
-	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
-	form.
+	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can form.
 	%
@@
 \begin{itemize}
-	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
+	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus~\cite{alberts2002molecular}.
 	%
@@
 Other paths are used for cross talk between the secretory and the endocytic routes.
-For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}.
+For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes (endocytic route)~\cite{progida2016bidirectional}.
 Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus.
-The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.
+The molecules involved in these routes are as yet unknown~\cite{nickel2018unconventional}.
 %
@@
 \subsection{The model}
-\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
+\noindent \info{Ashutosh. Should we say this. We have done this uniformally.}The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
 %
@@
 %
-Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence, for the sake of simplicity, we assume a uniform size for intracellular vesicles.
+Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the \unsure{Is it a simplification or simplification to suite our Boolean Model.
+Should we say Boolean model?
+Or this looks fine?}sake of simplicity, we assume a uniform size for intracellular vesicles.
 %The assumptions 
@@
 %
-In our model, we assume that the cell is in steady state.
+In our model, we assume that the cell is in a steady state.
 As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
@@
 %SNAREs are of two types (known as Q and R in the cell biology iterature) and 
-Vesicle fusion requires a pairing of 3 Qsnares and 1 Rsnare that are distributed between the transfer vesicle and the target compartment. 
+Vesicle fusion requires a pairing of 3 Q-SNAREs and 1 R-SNARE that are distributed between the transfer vesicle and the target compartment. 
 %For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
@@
 %
-Not all sets of Q and R SNAREs are allowed to fuse with each other.
+Not all sets of \unsure{R-SNARE? or R SNARE is Okay?}Q and R SNAREs are allowed to fuse with each other.
 %
-In the model, we assume that the cell has an equal number of Q and R SNARE types.
+%In the model, we assume that the cell has an equal number of Q and R SNARE types.
 %
-Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with an equal number of Q and R SNAREs. 
+Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R SNAREs. 
 % equal number of Q and R SNAREs as a part of node and edge label.
@@
 In our abstract model, 
-we create a hierarchy of models for varying degrees of regulation of SNARE activity.
+we create a hierarchy of variants for varying degrees of regulation of SNARE activity.
 %we create a set of variations of different kind of molecular regulations.
@@
 %
-The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments. 
+The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
 %
@@
 
-%\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
-One such benchmark is provided by our result about connectivity of the VTS graph.
+One such benchmark is provided by our result about the connectivity of the VTS graph.
 Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected.
@@
 Therefore the underlying undirected graph is 2-connected.
-From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity.
+From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity.
 When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
-And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected.
+And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be \change{We have used 4 connected in results!
+2 strongly or 4 what to put?}2-strongly connected.
 
@@
 %
-Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
+Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is \unsure{shld we say something about example in one line before the start?}complete.\\
 %
@@
 %
+\vspace{-0.5cm}
 \begin{example}
 %
-In figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 16 molecules, and a corresponding pairing matrix.
+In Figure~\ref{fig:M1}, \improve{require improvement in the description of this example}we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
 %
-Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
+%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
 %
-In the VTS, labels are a string of molecule, and red colored molecules are active.
+In the VTS, labels are a string of molecule, where we show active molecules in red color.
 %
-On the node, the activity of molecules is controlled
+The activity of the molecules on the node is controlled
 by the presence of the other molecules (exact Boolean function is not shown). 
-%Every molecule on the node is active.
 %
-The activity of the molecules on an edge is determined by the corresponding pairing matrix on the edge.
+The activity of the molecules on an edge is determined by the corresponding pairing matrix.
 %
-Below of the figure, we show the pairing matrix.
+Below the VTS, we show the pairing matrix.
 %
-An entry 1 represents pairing between molecules.
+Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
 %
-0 represents no pairing.
-%
-Rows corresponds to the labels of edges, and
-columns corresponds to the labels of nodes.
+An entry 1 represents pairing between molecules and 0 represents no pairing.
 %
@@
 We would also like to directly make statements about steady state properties, rather
-than using transition dynamics to first search for steady states. 
+than using transition dynamics to the first search for steady states. 
 %
@@
 %
-The tools model the computation symbolically for the graphs of finite size and can make prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
+The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
 %
@@
 	%
+	The synthesis added one edge and 7 molecules to complete the partial VTS.
+	%
 	For clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.

### 2019-04-07 papers/journal/model.tex
Moved the discussion about the size of the system upfront
Section 3 is completed

@@
 Our model attempts to capture only the relevant aspects of the
-system to develop understanding the flow structure of VTSs.
+system to develop an understanding of the flow structure of VTSs.
 %
@@
 %
-The model describes stable flow of molecules and does not
+The model describes the stable flow of molecules and does not
 capture the transient nature of VTSs.
@@
 %
-There is a set of relevant molecules that participate in
-management of the VTS.
+There is a set of relevant molecules that participate in the management of the VTS.
 %
-Both nodes and edges are labelled with subsets of the molecules.
+Both nodes and edges are labeled with subsets of the molecules.
 %
-The molecules are activity and their control is defined using
+The molecules activity and their control is defined using
 activity functions and a pairing matrix.
@@
 In addition to fuse compatibility, the well-structured property requires that
-here are no self loops, and 
+here are no self-loops, and 
 each edge carry only those molecules that are present in its source
@@
 %
-
+%
 \vspace{0.2cm}

### 2019-04-07 papers/journal/problem.tex
removed unwanted refernce
Section 5 completed

@@
 %
-We categorize the search problem, Figure~\ref{fig:vts-search} into three different categories, search problem for existential condition, search problem for universal condition, and performing synthesis on the incomplete VTS.
+We categorize the search problem (Figure~\ref{fig:vts-search}) into three different categories, search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
 %
-We will present two encodings for existential condition and one each for universal condition condition and synthesis.
+We will present two encodings for existential condition and one each for universal condition and synthesis.
 
@@
 	[\textbf{1.Existential Condition}, for tree={fill=fv, child}, 
-	[BMC Sec.6.2, for tree={fill=ai, child}]
-	[SMT Sec.6.1\\, for tree={fill=ai, child}]
+	[BMC Section 6.2, for tree={fill=ai, child}]
+	[SMT Section 6.1\\, for tree={fill=ai, child}]
 	]
 	[\textbf{2.Universal Condition}, for tree={fill=fv, child},
-	[QBF \\ Sec.6.3, for tree={fill=ai, child}]
+	[QBF \\ Section 6.3, for tree={fill=ai, child}]
 	]
 	[\textbf{3.VTS Synthesis}, for tree={fill=fv,child}, 
-	[Synthesis Sec.6.4, for tree={fill=ai, child}]
+	[Synthesis Section 6.4, for tree={fill=ai, child}]
 	]
@@
 %The Bounded model checking technique
-BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
+\improve{The violation connect to search for the VTS; what about counterexamples?}BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
 %
 The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
-% is used to check the satisfiability of the resultant propositional formula.
 %
@@
 %
-This restriction puts an upper limit of number of nodes, $N$ on the length of the searched path. 
+This restriction puts an upper limit of the number of nodes on the length of the searched path. 
 %
@@
 %
-The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors etc.
+The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors, etc.
 %
@@
 %
-Throughout the paper we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
+Throughout the paper, we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
 %The existential condition search problem is represented as a bounded model checking and constraint solving. 
@@
 %
-Here, we will present both $\fbmc$ and $\fsmt$ search problem for the existential condition.
+Here, we present both the $\fbmc$ and $\fsmt$ search problem for the existential condition.
 
@@
 To cover most of the likely variations of this missing information,
-we have encoded the following variants of VTS synthesis problem.
+we have encoded the following variants of the VTS synthesis problem.
 
@@
 We will do synthesis against the property that the VTS
-is stable and k-connected (k=3,4).
+is stable and 3-connected.
 %

### 2019-04-07 papers/journal/problem.tex
Section 5 completed

@@
 %Here we will present the QBF.
-\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
+\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
 %
-The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifiers.
+The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
 %

### 2019-04-07 papers/journal/encoding.tex
Font problems fixed
Section 6 completed

@@
 %\externaldocument{qbf-table}
-\noindent In the previous section, we have discussed four problems, $\fbmc$ search, $\fsmt$ search, $\fqbf$ search and synthesis problem.
-%
-In this section we will present encodings for each of them.
+\noindent In the previous section, we have discussed in total four problems, $\fbmc$ search, $\fsmt$ search, $\fqbf$ search and synthesis problem.
+%
+In this section, we will present encodings for each of them.
 %
@@
 %
-So, instead of presenting serially the complete encoding of both, 
-%$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
-%
-we will start with the complete $\fsmt$ search encoding and present only the relevant part of the the $\fbmc$ encoding to show a contrast.
+So, instead of presenting serially the complete encoding of both, we will start with the complete $\fsmt$ search encoding and present only the relevant part of the $\fbmc$ encoding to show a contrast.
 %contrast with the $\fbmc$ encoding.
@@
 %
-Afterwards, we will present the constraints corresponding to the
+Afterward, we will present the constraints corresponding to the
 properties.
@@
 %
-We assume that size of the graph is $\nu$ and number of molecules is
+We assume that the size of the graph is $\nu$ and number of molecules is
 $\mu$.
 %
-Furthermore, we also limit the maximum number $\pi$ of edges present
+Furthermore, we also limit the maximum number of $\pi$ of edges present
 between two nodes.
 %
-Here, we list the vector of Boolean variables and uninterpreted function symbols
-that encode the VTSs.
+Here, we list the vector of Boolean variables and uninterpreted function symbols that encode the VTSs.
 \begin{enumerate}
@@
 \texttt{EdgeC} states that each edge has at least one molecule,
- edge labels are consistent with node labels and there are no self loops.    
+ edge labels are consistent with node labels and there are no self-loops.    
 \begin{align*}
@@
 \end{align*}
-We define \texttt{FusionC} to collect all the fusion related constraints.
+We define \texttt{FusionC} \change{Use of the word collect looks weird! change it.}to collect all the fusion related constraints.
 % 
@@
 %
-The activity of the molecules are controlled by activity functions.
-%
-We will have encoded five variation of the Boolean functions based on the biological discussion.
+The activity of the molecules is controlled by activity functions.
+%
+We will have encoded five variations of the Boolean functions based on the biological discussion.
 %
@@
 \begin{align*}
-\texttt{FunOnN} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
+\texttt{FunNoN} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
 \end{align*}
@@
 \begin{align*}
- \texttt{FunOnE} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
-\end{align*}
-The following constraint encodes that activity of a molecule $m$ on the edge is
-defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
+ \texttt{FunNoE} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
+\end{align*}
+The following constraint encodes that activity of a molecule $m$ on the edge is defined by a Boolean function $\edgef_m$ of the presence of molecules present on that edge.
 \begin{align*}
@@
 
-\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search problem~\cite{shukla2017discovering}.
+\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search \unsure{Should we cite it here or not?}problem~\cite{shukla2017discovering}.
 %
 %In this section we will present the $\fbmc$ encoding of the same.
-%
+%The basic idea is to search the solution only upto a certain depth $w$. 
+%
+%\begin{align*}
+%\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
+%\end{align*}
+%
+%
+%\begin{align*}
+%\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) == 1) \limplies \npath(m, j, i, w)
+%\end{align*}
 %Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are 
@@
 % 
-The main difference between $\fsmt$ and $\fbmc$ is the encoding of 
+The main differences between $\fsmt$ and $\fbmc$ are the representation of variables and the encoding of 
 %I n comparison to $\fsmt$, the $\fbmc$ search encodes 
@@
 %
-The value of the bit vector variable describe the presence of the corresponding molecules at that particular location. 
+The value of the bit vector variable describes the presence of the corresponding molecules at that particular location. 
 %
@@
 %
-For an edge in the system with $M$ = 4 molecules, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 2 and node 1.
-
-To specify the stability condition, we use nondeterminism to perform enumeration.
+For an edge in the system with $M$ = 4 molecules, the variable \texttt{bvEdge}[2][1][0] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 2 and node 1.
+
+To specify the stability condition, we use \improve{Nondet usage is not clear in the encoding. improve.}nondeterminism to perform enumeration.
 %
@@
 %
-Note that the enumeration is done only for an unwinding depth $w$.
+Note that the enumeration is done only for an unwinding depth of $w$.
 %
@@
 %
-A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if molecule $m$ is present on edges along that path.
+A path between node $i$ and $j$ in the graph is an $m$-$path_{ij}$ if molecule $m$ is present on edges along that path.
 %
@@
 %
-Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
+Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.\change{m-path looks - sign in the align}
 %by performing series of node hops till final node destination j is reached.
@@
 %
-In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using non-determinism.
+In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using \improve{Do not show up in the encoding}nondeterminism.
 %
@@
 However, the trivial solutions are disallowed by constraint~$\texttt{Connected}(r')$ and we find
-only the solutions that captures the evidence of non-reachability.
-%
-On the other hand, we have added length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
+only the solutions that capture the evidence of non-reachability.
+%
+On the other hand, we have added the length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
 %
@@
 \item Every present molecule is considered to be active.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
-\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
-\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
+\item Activity of molecules on the nodes is based on Boolean function of the presence of other molecules. 
+\item Activity of molecules on the edges is based on Boolean function of the presence of other molecules
+\item Activity of molecules both on the edges and nodes is based on Boolean function of the presence of other molecules.
 \item Activity of molecules on the edges is driven by pairing inhibition.
-\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
+\item Activity of molecules on the nodes is based on Boolean function of the presence of other molecules and on edge by pairing inhibition.
 \end{enumerate}
@@
 
-In the table~\ref{tab:var-grph}, we present the constraints involved in each version.
+In the Table~\ref{tab:var-grph}, we present the constraints involved in each version.
 %
@@
 %
-The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
+The Table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
 %
@@
 %
-This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
+This can be due to the fact that directly translating a quantified formula into a quantifier-free by introducing a vector of variables for each boolean possibility \change{Increase the formula size exponentially..
+the current statement is a repeat of the forth line.
+Improve.}will blow up the size of the formula and may not be solvable by a solver.
 %
@@
 %
-Our tool is easily modifiable to support any other property that may be deemed 
-interesting by the biologists.
+Our tool is easily modifiable to support any other property that may be deemed interesting by the biologists.
 
@@
 %
-We limit the addition of the edges, since we look for a fix that require minimum number
+We limit the addition of the edges since we look for a fix that requires a minimum number
 of changes in the given VTS.
@@
 %
-We fix the all other aspects of the VTS to be fixed via constraints
+We fix all other aspects of the VTS to be fixed via constraints
 $\texttt{FixedForFunctions}$.

### 2019-04-07 papers/journal/experiments.tex
Minor update
Dia is complet
Section 7.1 completed

@@
 %
-The existential condition is subdivided into two sub-block, bounded model checking and constraint solving. 
+The existential condition is subdivided into two sub-blocks, bounded model checking and constraint solving. 
 %
-We will refer to existential subblocks as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
+We will refer to existential subblocks \unsure{The fonts of toolset looks different make them uniform.
+The reason is valid although.}as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
 %
@@
 %recursive encoding of finding a least fixed point to encode the same. 
-The second encoding is implemented in {\smttool} and employs a recursive encoding of finding a least fixed point for the reachability.
-
+The second encoding is implemented in {\smttool} and employs a recursive encoding
+% of finding a least fixed point 
+for the reachability. 
 %
@@
 
-\textbf{{\sattool (Bounded model checker based tool)}}
-The $\fbmc$ encoding based on enumeration of paths (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
+%\textbf{{
+\subsubsection{{\sattool} (Bounded model checker based tool)}
+%}}
+The $\fbmc$ encoding based on enumeration of paths (Section~\ref{enc:bmc}) for each variants of VTS is implemented in {\sattool}.
 	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
@@
 %
-It verify property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
+It verifies property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
 %
-The depth of model is specified by the user and can be  incrementally increased to a desired value.
+The depth of the model is specified by the user and can be incrementally increased to the desired value.
 %
@@
 %	
-The vesicle transport network was modelled as a non-deterministic C-program manipulating an annotated graph. 
+The vesicle transport network was modeled as a non-deterministic C-program manipulating an annotated graph. 
 %
@@
 %	\end{itemize}
-For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}.
+For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat} and CryptoMiniSat~\cite{soos2016cryptominisat}.
 % the winner of SAT 2015 Competition~\cite{balyo2016sat}.
@@
 
-\textbf{{\smttool} (SMT based tool)}
-The $\fsmt$ encoding based on recursive reachability definition (presented in section 6.1)  
-%We have implemented the encodings 
-for each variant is implemented in {\smttool}.
+\subsubsection{{\smttool} (SMT based tool)}
+The $\fsmt$ encoding based on recursive reachability definition (Section~\ref{enc:smt})  for each variant is implemented in {\smttool}.
 %
@@
 %        
-It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that follows the constraints). 
+It uses the Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that follows the constraints). 
 %
 This tool also translates the satisfying model found by Z3 into
-a VTS and represent a visual output to the user in form of coloured annotated graph. 
+a VTS and represent a visual output to the user in the form of a colored annotated graph. 
 %
@@
 
-\textbf{{\qbftool} (QBF based universal condition)}
-The $\fqbf$ encoding (presented in section 6.5) is implemented in the {\qbftool}. 
+\subsubsection{{\qbftool} (QBF based universal condition)}
+The $\fqbf$ encoding (Section~\ref{enc:univ-cond}) is implemented in the {\qbftool}. 
 %
@@
 
-\textbf{{\ourtool} (QBF based synthesis tool)}
+\subsubsection{{\ourtool} (QBF based synthesis tool)}
 \input{synth-table}
-The synthesis encodings (presented in section 6.6) is implemented  in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
+The synthesis encodings (Section~\ref{enc:synth}) is implemented  in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
 %
@@
 %
-For our analysis we relax the 3:1 requirement for the Q and R-SNARES and treat a Q-SNARE triple helix as a single complex as modelled in~\cite{shukla2017discovering}.
+%For our analysis we relax the 3:1 requirement for the Q and R-SNARES and treat a Q-SNARE triple helix as a single complex as modelled in~\cite{shukla2017discovering}.
 %
-The 
+%The 
 %

### 2019-04-07 papers/journal/experiments.tex
Section 7 completed

@@
 \subsection{Results}
-\noindent The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\qbftool} and in table~\ref{tab:synth-graph} for~{\ourtool}.
+\noindent The results and timings of {\sattool} and {\smttool} is presented in the Table~\ref{tab:smt-grph} and Table~\ref{tab:satsmt-graph} respectively.
+The Table~\ref{tab:qbf-graph} present the results for {\qbftool} and Table~\ref{tab:synth-graph} for~{\ourtool}.
 
@@
 
-The minimal connectivity results for each variation of the existential condition are presented in table~\ref{tab:smt-grph}.
+The minimal connectivity results for each variation of the existential condition are presented in Table~\ref{tab:smt-grph}.
 %
-%No matter what the rules of molecular interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
-The steady-state constraint requires that structure of the graph is at least 2-connected. 
+The steady-state constraint requires that the structure of the graph is at least 2-connected. 
 %
@@
 For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the vesicle transport networks in the stable state.
-%(including the case where SNAREs are always active) we did not find any possible graphs representing stable vesicle transport networks. 
 %
@@
 
-For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
+\unsure{The bio discussion looks pale and irrelevant!}For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
 %
@@
 %
-No graph results suggests that a functional VTS necessarily needs some form of regulation, where the molecules of the VTS are kept inactive in places where they might disrupt other interactions
+No graph results suggest that a functional VTS necessarily needs some form of regulation, where the molecules of the VTS are kept inactive in places where they might disrupt other interactions
 
@@
 %
-Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
+The Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
 %
-For this comparison we have fixed the total number of molecules minimum four times the node count 
-%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
+For this comparison, we have fixed the total number of molecules minimum four times for each SNARE type of the node count. 
 %
-%For each variant, we fix 1
-and maximum number of parallel
-edges to be 2.
+The maximum number of parallel edges is 2.
 %
@@
 In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
-%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
 %
-%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
-%
-As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
+As an example, the result of verifying the formula for variation C of 3-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
 %
 In comparison, {\sattool} was unable to solve the instance and ran out of memory.
-% for $|N|$ greater than 5.
-%
 %
 The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
-%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
 %
-Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
-%a much larger compartmentalized system, especially to interesting 
-the case of eukaryotic cells with a total number of 10 compartments.
+Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the case of eukaryotic cells with a total number of 10 compartments.
 %
-Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.
+Furthermore, we experimented with the limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.
 
@@
 
-Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
+The Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
 %
-The table represents the result of the graph connectivity for each variation of the VTS.  
+The result of the graph connectivity for each variation of the VTS is shown.  
 %
@@
 % 
-For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration
+For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration.
 %
@@
 %
-The results are presented in Fig~\ref{tab:synth-graph} for both the solvers
+The results are presented in Figure~\ref{tab:synth-graph} for both the solvers
 \depqbf and \zthree.
@@
 quantifier-free.
-%
-% The experiments were conducted on a machine,
-% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
-%
-%The experiments were conducted with a 900s timeout.
 %
@@
 %
-The fig shows timing for various synthesis queries.
+The figure shows timing for various synthesis queries.
 %
@@
 search space can obtain the VTS.
+
+In the Figure~\ref{tab:synth-graph}, we report five synthesis queries.
 %
-%\ashu{@ankit: please discuss all the synthesis queries in the table.}
-
-In the Fig~\ref{tab:synth-graph}, we report five synthesis queries.
-%
-The first one only adds new labelled edges to the graph.
+The first one only adds new labeled edges to the graph.
 %
@@
 The second query adds new labels to the edge.
-%  and was able to
-% fix the graphs with eleven new molecule labels in 180s.
 %
@@
 %
-% The tool was able to synthesize the Boolean functions in 470s.
-%
 To illustrate the versatility of our tool, the fourth query
 synthesizes $3$-CNF functions (encoding not presented).
-%  and was able to
-% synthesis the results for all graphs in 500s.
 %
-Finally, we report queries that allows both addition and deletion of edges, and labels
-of node and labels.
+Finally, we report queries that allow both addition and deletion of edges and labels of node and labels.
 
@@
 %
-
 %%% Local Variables:

### 2019-04-07 papers/journal/related.tex
Uniform use of the title without :
Section 8 completed

@@
-Previous analysis of vesicle traffic system has used simulation and statistical reasoning~\cite{mani2016stacking}. 
+\noindent \improve{Not upto the mark}The previous analysis of vesicle traffic system used simulation and statistical reasoning~\cite{mani2016stacking}. 
 %
@@
 
-The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
+The Boolean satisfiability (SAT) solvers are used to solve a wide range of problems including
 %
@@
 %
-%Unlike the GNR, not many  VTS
 We have presented both SAT and SMT based encoding for our Boolean model of the VTS.
@@
 % 
-To our best knowledge our work is the first application
+To our best knowledge, this series of work is the first application
 of formal methods to the vesicle traffic networks.
@@
 In recent years, there has been a wide range of methods
-developed for the similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
+developed for similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
 %
-They range from filling gaps an implementation of C programs from the pool of template predicates to learn a program from example
+They range from filling gaps an implementation of C programs from the pool of template predicates to learn a program from the example
 runs of the program.
@@
 
-There has been some work in
-applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}.
+There has been some work in applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}.
 A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
@@
 The paper~\cite{cardelli2017syntax} in addition to using SMT over ODE, uses a template-guided approach.
-In our case queries contain quantifiers so we have employed QBF solving with Z3 for the solving the synthesis problem.
+In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem.
 To our best knowledge, this is the first application of synthesis in VTS.
-
 %%% Local Variables:

### 2019-04-07 papers/journal/abstract.tex
Updated Pairing encoding for the SMT
Todo added again in abstract and conclusion
asd

--- 2019-03-20 papers/journal/abstract.tex
@@
 %
-We present novel SAT, SMT and QBF based encodings of the properties over vesicle traffic systems and a tool that searches for the networks that satisfy properties that are related to transport consistency conditions using these solvers.
+We present novel encodings for the problems
+based on Boolean satisfiability (SAT), satisfiability modulo theories (SMT) and
+quantified Boolean formula (QBF) of the properties over vesicle traffic systems.
+%
+We have implemented the presented encodings in a tool that searches for the networks that satisfy properties related to transport consistency conditions using these solvers. 
 %
 In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.
+%
+Our work illustrates the potential of novel biological applications of
+SAT soling technology.
 
-% Vesicle Traffic Systems(VTSs) are the material transport 
-% mechanisms among the compartments inside the biological cells.
+%
+%Understanding VTSs is an ongoing area of research and for many cells they are partially known. 
+%
+%We do not have a complete picture of the VTS graph, and in many cases we know only partial information known.
+%
+% The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
+% %Complete picture of VTSs are not clear and only partial 
+% %For example, there may be undiscovered edges, nodes, or their labels in a VTS of a cell. 
+% %
+% %In this sense the picture of the VTS graphs is only partially complete. 
+% %
+% It has been speculated that there are properties that the VTSs must satisfy.
+% For example, stability, i.e., every chemical that is leaving a compartment
+% comes back. 
+% %
+% \todo{Text below this is just a copy of last paper}Many synthesis questions may arise in this scenario, where we want to complete a partially known VTS under a given property.
+% %
+% In the paper, we present novel encodings of the above questions into
+% the QBF satisfiability problems. 
+% %
+% We have implemented the encodings in a highly configurable tool and applied to a couple of VTSs found in the literature and to several synthetic graphs.
+% %
+% Our results demonstrate that our method can scale up to the graphs of interest.
+% % Vesicle Traffic Systems(VTSs) are the material transport 
+% % mechanisms among the compartments inside the biological cells.
 

### 2019-04-08 papers/journal/intro.tex
Intro Dia fixed

@@
 %
-However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}\change{Should only cite 3?}. 
+However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
 %The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
@@
 \subsubsection{Vesicle budding} \unsure{Somya should we say it involve three mojor steps?
-This line is not optimal.
-Use of "see" okay?}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment, see Figure~\ref{fig:vts}.
+This line is not optimal.}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
 %
-\unsure{new line start or this is ok?}Cargo sorting is performed by cytosolic adaptor proteins. 
+Cargo sorting is performed by cytosolic adaptor proteins. 
 Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
@@
 
-\subsubsection{Vesicle fusion} \info{Calling them process okay?}The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.
+\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.
 
@@
 \subsection{The model}
-\noindent \info{Ashutosh. Should we say this. We have done this uniformally.}The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
+\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
 %
@@
 %
-Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the \unsure{Is it a simplification or simplification to suite our Boolean Model.
-Should we say Boolean model?
-Or this looks fine?}sake of simplicity, we assume a uniform size for intracellular vesicles.
+Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the sake of simplicity, we assume a uniform size for intracellular vesicles.
 %The assumptions 
@@
 %
-Not all sets of \unsure{R-SNARE? or R SNARE is Okay?}Q and R SNAREs are allowed to fuse with each other.
+Not all sets of Q and R-SNAREs are allowed to fuse with each other.
 %
@@
 %
-Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R SNAREs. 
+Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R-SNAREs. 
 % equal number of Q and R SNAREs as a part of node and edge label.
@@
 %
-Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is \unsure{shld we say something about example in one line before the start?}complete.\\
+Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
 %
@@
 %
-In Figure~\ref{fig:M1}, \improve{require improvement in the description of this example}we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
+In Figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
 %
@@
 The activity of the molecules on an edge is determined by the corresponding pairing matrix.
+%
+Note that molecules $X$ and $Y$ do not take part in the fusion but play a part in determining activity at the corresponding nodes.
 %
@@
 \subsubsection{Size of the VTS system}
-Let us discuss rough sizes of the system and expected behaviors.
+Let us discuss the rough sizes of the system and expected behaviors.
 %%
@@
 %
-The organellar content of cells vary across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhopteries and micronemes~\cite{gubbels2012evolution}.
+The organellar content of cells varies across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhoptries and micronemes~\cite{gubbels2012evolution}.
 %
@@
 %
-Also, across different cell-types, these organelles may be more or less differentiated, for example, number of stacks in the Golgi vary across different cells~\cite{polishchuk2004structural}. 
+Also, across different cell-types, these organelles may be more or less differentiated, for example, the number of stacks in the Golgi varies across different cells~\cite{polishchuk2004structural}. 
 %
@@
 %
-The VTS transports a large number of molecules but the molecules that actively control the system are in their tens [MBOC]. 
+The VTS transports a large number of molecules but the molecules that actively control the system are in their tens~\cite{lodish2008molecular}. 
 %
-By definition the activity of any VTS molecules can be controlled by all other molecules.
+By definition, the activity of any VTS molecules can be controlled by all other molecules.
 %
@@
 \subsection{Synthesis of VTS }
-\noindent The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
+\noindent The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
 %
@@
 \begin{enumerate}
-	\item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.
+    \item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms~\cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
 
@@
 
-	\item Molecules can have redundant routes within the cell ~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
-	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.
+    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
+    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}.
 
-	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
+    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
 \end{enumerate}
@@
 %
-Knowledge of the complete network would be helpful in identifying the root causes~\cite{bexiga2013human,gissen2007cargos}. 
+Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
 %
-At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
+At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
+%
+This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
 
@@
 %
-In order to attempt to complete a given partial VTS we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
+In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
 %
@@
     The synthesis is performed against the steady state property and 3-connectivity. 
-The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for proper discussion about the nodes and molecules depicted in the diagram).
+    %The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for a proper discussion about the nodes and molecules depicted in the diagram). 
     %
-	Synthesized edge is in red color and synthesized molecules are represented with blue.
+    Synthesized edge is in red color and synthesized molecules are presented in blue.
     %
-	The synthesis added one edge and 7 molecules to complete the partial VTS.
+    The synthesis adds one edge and 7 molecules to complete the partial VTS.
     %
-	For clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
+    For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
 
@@
 
+%
 The rest of the paper is organized as follows. 
 %
-In Sect.~\ref{sec:prelim}, we present the notations we use in this paper. 
+In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
 %
-In Sect.~\ref{sec:model}, we present graph model of VTSs and  properties of interest in Sect.~\ref{sec:property}.
+In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
 %
-%encoding of several constraints on VTSs. 
+In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
 %
-%In , we present the
+In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
 %
-In Sect.~\ref{sec:problem}, we present the complete formal problem statement of the verification properties.
+In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
 %
-In Sect.~\ref{sec:encoding}, we present the encoding of BMC, SMT, QBF and Synthesis into SAT, SMT and QBF satisfiability. 
-%
-In Sect.~\ref{sec:experiments}, we present our implementation and experimental results. 
-%
-In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.
+In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
 %

### 2019-04-08 papers/journal/synth-dia.tex
Intro Dia fixed

--- 2019-04-05 papers/journal/synth-dia.tex
@@
 	 % 	\begin{scope}[]
-	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
+	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
 	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}};
-	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}};
+	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}};
+	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}};
 
 	  %le <-> pm
-	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$, $Q_{c7}$} (pm);
-	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
+	  \path (le) edge[bend right=55] node [above] {$Q_{bc7}$} (pm);
+	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);
 
@@
 	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
-	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
+	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{a2}$} (ee);
 	\end{tikzpicture}
@@
 	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
-	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
-	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$} ...}};
-	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $} ...}};
-	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$} ...}};
+	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
+	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}...};
+	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}...};
+	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}...};
 
 	  %le <-> pm
-	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$, $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
+	  	  \path (le) edge[bend right=45] node [above] {$Q_{bc7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
 	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
@@
 	  %ee -> le
-	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
+	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);
 %	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);
@@
 	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
-	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{$R_{3}$}}} (ee);
+	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{a2}$, \color{blue} {$R_{3}$}} (ee);
 %	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    

### 2019-04-08 papers/journal/encoding.tex
encoding todos completed

@@
 \end{align*}
-\noindent We define \texttt{ActivityC} to collect all the molecule activity related constraints. 
+\noindent We define \texttt{ActivityC} to group all the molecule activity related constraints. 
 \texttt{ActivityC} states that all active molecules are present.
@@
 \end{align*}
-We define \texttt{FusionC} \change{Use of the word collect looks weird! change it.}to collect all the fusion related constraints.
+We define \texttt{FusionC} to group all the fusion related constraints.
 % 
@@
 \subsection{Encoding for $\fbmc$ search problem}
-
-\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search \unsure{Should we cite it here or not?}problem~\cite{shukla2017discovering}.
+\label{enc:bmc}
+\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search problem~\cite{shukla2017discovering}.
 %
@@
 \subsection{Encoding for the synthesis problem}
+\label{enc:synth}
 \noindent In this section, we will present our synthesis method for

### 2019-04-08 papers/journal/problem.tex
encoding todos completed

@@
 %The Bounded model checking technique
-\improve{The violation connect to search for the VTS; what about counterexamples?}BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
+BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
 %

### 2019-04-08 papers/journal/encoding.tex
Todos till experiments done

@@
 %
-This can be due to the fact that directly translating a quantified formula into a quantifier-free by introducing a vector of variables for each boolean possibility \change{Increase the formula size exponentially..
-the current statement is a repeat of the forth line.
-Improve.}will blow up the size of the formula and may not be solvable by a solver.
+This can be due to the fact that directly translating a quantified formula into a quantifier-free by introducing a vector of variables for each boolean possibility can lead to exponential increase in the formula size.
 %

### 2019-04-08 papers/journal/experiments.tex
Todos till experiments done

@@
 %
-The existential condition is subdivided into two sub-blocks, bounded model checking and constraint solving. 
+The existential condition is subdivided into two subblocks, bounded model checking and constraint solving. 
 %
-We will refer to existential subblocks \unsure{The fonts of toolset looks different make them uniform.
-The reason is valid although.}as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
+We will refer to existential subblocks as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
 %
@@
 
-\unsure{The bio discussion looks pale and irrelevant!}For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
+For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
 %

### 2019-04-08 papers/journal/problem.tex
Todos till experiments done

@@
 %
-The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.
+The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{savitch1970relationships, stockmeyer1973word}.
 

### 2019-04-08 papers/journal/property.tex
Intro Dia fixed
Todos till experiments done

@@
-\noindent We analyze the model against our desired properties.
+\noindent %\improve{The weakest part of the paper; Need a serious rewrite!}
+We analyze the model against our desired properties.
 %
@@
 \begin{enumerate}
-\item {\em Existential condition:}
+\item {\em Existential condition}:
 if there is a VTS that satisfies the connectedness property.
 
-\item {\em Universal condition:}
+\item {\em Universal condition}:
   if there is a connectedness property that is satisfied by each valid VTS.

### 2019-04-08 papers/journal/ex-vts.tex
Minor Fixes

--- 2018-06-13 papers/synth/ex-vts.tex
@@
 
-The figure~\ref{fig:mukund-vts} represent mammalian SNARE map
+The Figure~\ref{fig:mukund-vts} represent mammalian SNARE map
 created by studying the wide array of literature.
@@
 
-In figure~\ref{fig:yeast-vts}, we present the yeast VTS.
+In Figure~\ref{fig:yeast-vts}, we present the yeast VTS.
 %

### 2019-04-08 papers/journal/intro.tex
Minor Fixes

@@
 
-\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.
+\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Figure~\ref{fig:vts}).
 
@@
 	%
-    In figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
+    In Figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
     %

### 2019-04-08 papers/journal/encoding.tex
Todos done
Minor Fixes

@@
 \end{align*}
-We define \texttt{StabilityC} to collect all the stability related constraints.
+We define \texttt{StabilityC} to group all the stability related constraints.
 % 
@@
 
-To specify the stability condition, we use \improve{Nondet usage is not clear in the encoding. improve.}nondeterminism to perform enumeration.
+To specify the stability condition, we use nondeterminism to perform enumeration.
 %
@@
 %
-Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.\change{m-path looks - sign in the align}
+Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
 %by performing series of node hops till final node destination j is reached.
 %Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.
-
+%
 %|m-path| = 1 \lor  |m-path| = 2 \lor ...  |m-path| = w.     \\
 %\bigvee\limits_{l = 1}^{|path| - 1} |m-path| = l
-
+%
 \begin{align*}

### 2019-04-08 papers/journal/intro.tex
Minor Fixes

@@
 
-\subsubsection{Vesicle budding} \unsure{Somya should we say it involve three mojor steps?
-This line is not optimal.}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
+\subsubsection{Vesicle budding} The process of vesicle budding involves three major steps, sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
 %
@@
 When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
-And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be \change{We have used 4 connected in results!
-2 strongly or 4 what to put?}2-strongly connected.
+And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 4-connected.
 

### 2019-04-08 papers/journal/encoding.tex
Minor Fixes in BMC encoding

@@
 
-To specify the stability condition, we use nondeterminism to perform enumeration.
-%
+To specify the stability condition, we use nondeterminism to encode the existence of a path. 
+%
+The nondeterminism can be viewed as a guess of the correct path if it exists. 
+%
+We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ from an edge $E$.
+%
+A basic encoding of it using enumeration is shown.
 %Nondeterminism can be viewed as an oracle that guesses a correct path for a specific $m$ if it exists. 
@@
 %
-Note that the enumeration is done only for an unwinding depth of $w$.
-%
-The encoding presented below is a simpler version of the implementation. 
+%Only partial enumeration up to an unwinding depth of $w$ is performed.
+Note that the enumeration is performed only up to an unwinding depth of $w$.
+%
+%The encoding presented below uses a nondeterministic path and perform enumeration to find it. 
 \subsubsection{Constraints for stability condition}
@@
 %
-In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using \improve{Do not show up in the encoding}nondeterminism.
+In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using nondeterminism.
 %

### 2019-04-09 papers/journal/encoding.tex
Hyphen problem fixed

--- 2019-04-08 papers/journal/encoding.tex
@@
 \end{align*}
-\noindent We define \texttt{ActivityC} to group all the molecule activity related constraints. 
+\noindent We define \texttt{ActivityC} to collect all the molecule activity related constraints. 
 \texttt{ActivityC} states that all active molecules are present.
@@
 \end{align*}
-We define \texttt{FusionC} to group all the fusion related constraints.
+We define \texttt{FusionC} \change{Use of the word collect looks weird! change it.}to collect all the fusion related constraints.
 % 
@@
 \label{enc:bmc}
-\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search problem~\cite{shukla2017discovering}.
+\noindent Our first attempt was to encode the existential condition as a $\fbmc$ search \unsure{Should we cite it here or not?}problem~\cite{shukla2017discovering}.
 %
@@
 %
-This can be due to the fact that directly translating a quantified formula into a quantifier-free by introducing a vector of variables for each boolean possibility can lead to exponential increase in the formula size.
+This can be due to the fact that directly translating a quantified formula into a quantifier-free by introducing a vector of variables for each boolean possibility \change{Increase the formula size exponentially..
+the current statement is a repeat of the forth line.
+Improve.}will blow up the size of the formula and may not be solvable by a solver.
 %

### 2019-04-09 papers/journal/intro.tex

--- 2019-04-08 papers/journal/intro.tex
@@
 %
-However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
+However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}\change{Should only cite 3?}. 
 %The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
@@
 \subsubsection{Vesicle budding} \unsure{Somya should we say it involve three mojor steps?
-This line is not optimal.}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
+This line is not optimal.
+Use of "see" okay?}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment, see Figure~\ref{fig:vts}.
 %
-Cargo sorting is performed by cytosolic adaptor proteins. 
+\unsure{new line start or this is ok?}Cargo sorting is performed by cytosolic adaptor proteins. 
 Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
@@
 
-\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.
+\subsubsection{Vesicle fusion} \info{Calling them process okay?}The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.
 
@@
 %
-Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the sake of simplicity, we assume a uniform size for intracellular vesicles.
+Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the \unsure{Is it a simplification or simplification to suite our Boolean Model.
+Should we say Boolean model?
+Or this looks fine?}sake of simplicity, we assume a uniform size for intracellular vesicles.
 %The assumptions 
@@
 %
-Not all sets of Q and R-SNAREs are allowed to fuse with each other.
+Not all sets of \unsure{R-SNARE? or R SNARE is Okay?}Q and R SNAREs are allowed to fuse with each other.
 %
@@
 %
-Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R-SNAREs. 
+Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R SNAREs. 
 % equal number of Q and R SNAREs as a part of node and edge label.
@@
 %
-In Figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
+In Figure~\ref{fig:M1}, \improve{require improvement in the description of this example}we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
 %
@@
 The activity of the molecules on an edge is determined by the corresponding pairing matrix.
-%
-Note that molecules $X$ and $Y$ do not take part in the fusion but play a part in determining activity at the corresponding nodes.
 %
@@
 %
-The VTS transports a large number of molecules but the molecules that actively control the system are in their tens~\cite{lodish2008molecular}. 
+The VTS transports a large number of molecules but the molecules that actively control the system are in their tens \change{What is this? A drug?}[MBOC]. 
 %
@@
 %
-We can use our stability and k-connectivity constraints as a basis for this investigation.   
+We can use our stability and k-connectivity \info{do you think use of constraint is well stated? very Minor!}constraints as a basis for this investigation.   
 %

### 2019-04-09 papers/journal/prelim.tex

@@
-\noindent We will use lower case variables like $e,r,s$ etc to represent vectors of
+\noindent We will use lower case variables like $e,r,s$, etc to represent vectors of
 Boolean variables, possibly indexed, with multiple dimensions.
@@
 %
-$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
-collection of formulas respectively.
+$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over a collection of formulas respectively.
 %
@@
 An assignment may satisfy a formula if the interpretation of Boolean operators
-reduce the whole Formula into 1.
+reduces the whole Formula into 1.
 %
@@
 %
-The problem of finding satisfying assignment for QBFs is even harder problem~\cite{arora2009computational}.\\
+The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{stockmeyer1973word, arora2009computational}.\\
 %
@@
 %
-The modern solvers are result of several decades of research
+The modern solvers are the result of several decades of research
 and implement sophisticated algorithms.
@@
 %1
-The QBF solver add support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
+The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
 

### 2019-04-09 papers/journal/synth-dia.tex

@@
 	  %le <-> pm
-	  \path (le) edge[bend right=55] node [above] {$Q_{bc7}$} (pm);
-	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);
+	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$, $Q_{c7}$} (pm);
+	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
 
@@
 	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
-	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{a2}$} (ee);
+	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
 	\end{tikzpicture}
@@
 	  %le <-> pm
-	  	  \path (le) edge[bend right=45] node [above] {$Q_{bc7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
+	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$, $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
 	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
@@
 	  %ee -> le
-	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);
+	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
 %	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);
@@
 	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
-	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{a2}$, \color{blue} {$R_{3}$}} (ee);
+	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{    $R_{3}$}}} (ee);
 %	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    

### 2019-04-09 papers/journal/intro.tex
Dia Update

--- 2019-04-08 papers/journal/intro.tex
@@
 %
-The molecular interaction network that controls the \unsure{Transport/Traffic}vesicle transport system involves dozens of varieties of molecules that regulate the flow of cargo. 
+The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
 %
@@
 
-\subsubsection{Vesicle budding} The process of vesicle budding involves three major steps, sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
+\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
 %
@@
 When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
-And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 4-connected.
+And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2 strongly connected.
 

### 2019-04-10 papers/journal/conclusion.tex
asd

--- 2019-04-04 papers/journal/conclusion.tex
@@
 %
-\todo{Just a template}
+%\todo{copied frm the PLOS paper to Just a template}
 We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
@@
 %
-However, our current knowledge of the actual vesicle transport graph of a cell is very poor: it is likely that there are many vesicle transport routes that are still uncharacterized.
-Even in those instances where vesicles are known to exist, the precise molecular drivers of their creation and fusion are often unknown.
+However, our current knowledge of the actual vesicle transport graph
+of a cell is very limited: it is likely that there are many vesicle
+transport routes that are still uncharacterized. Even in those
+instances where vesicles are known to exist, the precise molecular
+drivers of their creation and fusion are often unknown.
 %
-Therefore, a direct verification of our predictions based on graph connectedness alone is not likely. 
+Therefore, a direct verification of our predictions based on graph connectedness
+alone is not likely. 
 %
@@
 
-%\todo{Copid just to create a template}
-In the experiments, we have demonstrated the power of SMT solvers and the
-value of careful encoding of the problems into SMT queries. 
+In the experiments, we have demonstrated the power of SMT solvers in a {\em novel} application
+and the value of careful encoding of the problems into SMT queries. 
 %
-We manage to scale the tool upto the size that makes tool biologically relevant. However, there are many further search problems or extensions that are of interest. 
+We manage to scale the tool upto the size that makes tool biologically relevant.
 %
-For example, are there any k-connected graphs that can not be annotated into a VTS? 
+% However, there are many further search problems or extensions that are of interest. 
+% %
+% For example, are there any $k$-connected graphs that can not be annotated into a VTS?
+
 %
-This problem induces a quantifier alternation in an encoding. Therefore, a simple call to SAT solver will not work. 
+We explored various variations of the search problems, such as
+are there any $k$-connected VTSs.
 %
-We are planning to use QBF(quantified Boolean
+The problem of searching for $k$-connected VTSs
+induces quantifier alternations in the encodings.
+%
+Therefore, a simple call to SAT solver may not work efficiently. 
+%
+We used QBF(quantified Boolean
 formulas) solvers or develop iterative search algorithm for such queries.
 %
-One may be interested in counting the number of graphs that satisfy a given
-property. 
+One may also be interested in counting the number of graphs that satisfy
+a given property. 
 %
@@
 
-We do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries.
+We do not have a complete picture of the VTS graph, and so far,
+discoveries of new vesicles and molecular components are being made by
+groups interested in finding the path of a particular molecule, or
+they are chance discoveries. 
 %
-%\todo{Copied till para end! Need revision}
-In this paper, we presented encodings of the synthesis problems
-that may arise from VTSs.
+We also presented encodings of the synthesis problems that may arise from VTSs.
 %
-%
-We demonstrated that our tool based on the encodings
+We also demonstrated that our tool based on the encodings
 scale up to the relevant sizes of the VTSs for some synthesis queries.
@@
 %
-With this tool, we made an attempt to present multiple new testable predictions. 
+With the tool, we made an attempt to present multiple new testable predictions. 
 %
-We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
+We will take this tool to the biologists and develop wet experiments that may
+validate some synthesis results from the tool.
 %
-These predictions may very likely increase to hasten discoveries in this field alongside pushing forward the use of formal methods in the biological field.
-
-%Our model of VTSs is static graphs.
+These predictions may very likely increase to hasten discoveries in this field
+alongside pushing forward the use of formal methods in the biological field.
 %
-However, there are a few aspects in the modeling that we have relaxed.
-%  \item What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
-%\end{enumerate}
-%\textbf{Encode Dynamic behaviour of the VTS}
-A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation. 
+Since our current knowledge of VTSs is not extensive and there are many missing parts,
+there is a huge space of potential predictions.
+%
+We also developing methods to prioritize predictions considering addition biological
+information and using a refined model.
+%
+For example, a major aspect of the biological cell’s VTS that the current model is missing
+is compartment maturation. 
 %
@@
 Including this behaviour of the compartments in the model would allow it to make more accurate predictions.
+
+%Our model of VTSs is static graphs.
+%
+% There are a few aspects in the modeling that we have relaxed.
+%  \item What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
+%\end{enumerate}
+%\textbf{Encode Dynamic behaviour of the VTS}
+
 %%% Local Variables:

### 2019-04-11 papers/journal/conclusion.tex
Conclusion section

@@
 \noindent 
-%
-%\todo{copied frm the PLOS paper to Just a template}
 We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
 %
-Our results contain many predictions which can in
-principle be tested through cell-biological experiments. 
+The constraints implied by SNARE protein properties translates into
+mathematically elegant properties of the transport graph, namely its connectivity.
 %
-However, our current knowledge of the actual vesicle transport graph
-of a cell is very limited: it is likely that there are many vesicle
-transport routes that are still uncharacterized. Even in those
-instances where vesicles are known to exist, the precise molecular
-drivers of their creation and fusion are often unknown.
+Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
+We manage to scale the tool up to the size that makes the tool biologically relevant.
 %
-Therefore, a direct verification of our predictions based on graph connectedness
-alone is not likely. 
-%
-However, more indirect predictions based on how SNAREs are regulated can be
-explored. 
-%
-In this context, the Sec/MUNC proteins or SNARE longin domains are interesting
-targets of study~\cite{van2010one,rossi2004longins}.
 
-In the experiments, we have demonstrated the power of SMT solvers in a {\em novel} application
-and the value of careful encoding of the problems into SMT queries. 
-%
-We manage to scale the tool upto the size that makes tool biologically relevant.
-%
-% However, there are many further search problems or extensions that are of interest. 
-% %
-% For example, are there any $k$-connected graphs that can not be annotated into a VTS?
-
-%
-We explored various variations of the search problems, such as
-are there any $k$-connected VTSs.
-%
-The problem of searching for $k$-connected VTSs
-induces quantifier alternations in the encodings.
+However, the problem of searching for all $k$-connected VTSs induces quantifier alternation in the encodings.
 %
@@
 %
-We used QBF(quantified Boolean
-formulas) solvers or develop iterative search algorithm for such queries.
+We used QBF (quantified Boolean
+formulas) solvers for such queries.
 %
@@
 %
-We are also planning to employ some methods for approximate counting
-of solutions.
+We are planning to employ approximate counting methods for finding the solution.
+%
+Our results contain many predictions which can in principle be tested through cell-biological experiments.
 
-We do not have a complete picture of the VTS graph, and so far,
-discoveries of new vesicles and molecular components are being made by
-groups interested in finding the path of a particular molecule, or
-they are chance discoveries. 
-%
 We also presented encodings of the synthesis problems that may arise from VTSs.
 %
-We also demonstrated that our tool based on the encodings
+We demonstrated that our tool based on the encodings
 scale up to the relevant sizes of the VTSs for some synthesis queries.
@@
 %
+
 Since our current knowledge of VTSs is not extensive and there are many missing parts,
@@
 %
-For example, a major aspect of the biological cell’s VTS that the current model is missing
-is compartment maturation. 
+For example, in this work, we have only analyzed the VTS as static graphs.
+A major aspect of the biological cell’s VTS that the current model is missing is \textit{compartment maturation}, imbalances in incoming and outgoing molecular flux on vesicles.
 %
-We have only analyzed the VTS as a static graphs.
+In the future, we will study the dynamic behaviors of VTSs.
 %
-Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.
+%Maturation is evident in the Golgi in the endocytic system. 
 %
-Maturation  is  evident  in  the  Golgi  apparatus  and  in  the  endocytic system. 
-%
-Including this behaviour of the compartments in the model would allow it to make more accurate predictions.
+%Including this behavior of the compartments in the model would allow it to make more accurate predictions.
 

### 2019-04-11 papers/journal/conclusion.tex
conclusion

@@
 \noindent 
-We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
+To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
 %
@@
 
-However, the problem of searching for all $k$-connected VTSs induces quantifier alternation in the encodings.
+The problem of searching for all $k$-connected VTSs induces quantifier alternation in the encodings.
 %
@@
 %
+Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
+%Our connectivity results for VTS contains many predictions which can in
+%principle be tested through cell-biological experiments. 
+%%
+%However, our current knowledge of the actual vesicle transport graph of a cell is very poor: it is likely that there are many vesicle transport routes that are still uncharacterized.
+Even in those instances where vesicles are known to exist, the precise molecular drivers of their creation and fusion are often unknown.
+%%
+%Therefore, a direct verification of our predictions based on graph connectedness alone is not likely. 
+%%
+%However, more indirect predictions based on how SNAREs are regulated can be
+%explored. 
+%%
+%In this context, the Sec/MUNC proteins or SNARE longin domains are interesting
+%targets of study~\cite{van2010one,rossi2004longins}
 One may also be interested in counting the number of graphs that satisfy
@@
 %
-Our results contain many predictions which can in principle be tested through cell-biological experiments.
 

### 2019-06-15 papers/journal/abstract.tex
First Update for revision

@@
-Vesicle Traffic Systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
+Vesicle traffic systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
 %
@@
 Our work illustrates the potential of novel biological applications of
-SAT soling technology.
+SAT solving technology.
 

### 2019-06-15 papers/journal/conclusion.tex
First Update for revision

--- 2019-04-11 papers/journal/conclusion.tex
@@
-\noindent 
-We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
+To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
 %
@@
 %
-We used QBF (quantified Boolean
-formulas) solvers for such queries.
+We used QBF solvers for such queries.
+%
+Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
 %
@@
 %
-Our results contain many predictions which can in principle be tested through cell-biological experiments.
+%Our results contain many predictions which can in principle be tested through cell-biological experiments.
 
@@
 %
-These predictions may very likely increase to hasten discoveries in this field
-alongside pushing forward the use of formal methods in the biological field.
+%These predictions may very likely increase to hasten discoveries in this field alongside pushing forward the use of formal methods in the biological field.
 %
@@
 In the future, we will study the dynamic behaviors of VTSs.
-%
-%Maturation is evident in the Golgi in the endocytic system. 
-%
-%Including this behavior of the compartments in the model would allow it to make more accurate predictions.
-
-%Our model of VTSs is static graphs.
-%
-% There are a few aspects in the modeling that we have relaxed.
-%  \item What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
-%\end{enumerate}
-%\textbf{Encode Dynamic behaviour of the VTS}
 

### 2019-06-15 papers/journal/encoding.tex
First Update for revision

--- 2019-04-08 papers/journal/encoding.tex
@@
-%\externaldocument{sat-table}
-%\externaldocument{smt-table}
-%\externaldocument{qbf-table}
 \noindent In the previous section, we have discussed in total four problems, $\fbmc$ search, $\fsmt$ search, $\fqbf$ search and synthesis problem.
@@
 \noindent We define \texttt{ActivityC} to group all the molecule activity related constraints. 
-\texttt{ActivityC} states that all active molecules are present.
+The \texttt{ActivityC} states that all active molecules are present.
 \begin{align*}
@@
 %
-We denote the particular choice of node and edge function combined by \texttt{ActivityFun}.
+We denote the particular choice of node and edge function by \texttt{ActivityFun}.
 \begin{align*}
@@
 \begin{align*}
-\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
+\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m \mhyphen path_{ij})~\texttt{=}\texttt{=}~l)
 \end{align*}
@@
 \begin{align*}
-	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) == 1) \limplies \npath(m, j, i, w)
+	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m)~\texttt{=}\texttt{=}~1) \limplies \npath(m, j, i, w)
 \end{align*}
@@
 
-\input{variation-table}
+\input{table1}
 
@@
 %
-\input{satqbf-table}
-\noindent The specification for universal condition~\ref{sec:property} requires quantifier alternation. 
+\input{table2}
+\noindent The specification for universal condition Section~\ref{sec:property} requires quantifier alternation. 
 %
@@
 %\end{align*}
-
+%
 \subsection{Encoding for the synthesis problem}
@@
 %
-In that, $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
+Where, the constraint $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
 \begin{align*}

### 2019-06-15 papers/journal/ex-vts.tex
First Update for revision

@@
 \subsection{Mammalian VTS}
-\input{fig-mukund-vts}
+\input{fig5}
 
-The Figure~\ref{fig:mukund-vts} represent mammalian SNARE map
+The Fig.~\ref{fig:mukund-vts} represent mammalian SNARE map
 created by studying the wide array of literature.
@@
 
-\input{fig-yeast-vts}
+\input{fig6}
 
-In Figure~\ref{fig:yeast-vts}, we present the yeast VTS.
+In Fig.~\ref{fig:yeast-vts}, we present the yeast VTS.
 %

### 2019-06-15 papers/journal/experiments.tex
Minor fix of ref
First Update for revision

@@
-%\externaldocument{sat-table}
 %We have developed four different tools (\sattool, \smttool, \qbftool, \ourtool) for implementation of proposed encodings.
 %
-\noindent We have developed the {\vtstool} tool to conjecture the properties of the VTS (explained in Section 6). 
+\noindent We have developed the {\vtstool}\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}} tool to conjecture the properties of the VTS (Section~\ref{sec:encoding}). 
 %
@@
 %\textbf{{
-\subsubsection{{\sattool} (Bounded model checker based tool)}
+\subsubsection{{\sattool} (BMC based tool)}
 %}}
@@
 %
-It verifies property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
+It verifies property for all the possible states, up to a certain ``depth”, a parametric limit on the size of the model.
 %
@@
 %	
-The vesicle transport network was modeled as a non-deterministic C-program manipulating an annotated graph. 
+The VTS was modeled as a non-deterministic C-program manipulating an annotated graph. 
 %
@@
 \subsubsection{{\ourtool} (QBF based synthesis tool)}
-\input{synth-table}
-The synthesis encodings (Section~\ref{enc:synth}) is implemented  in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
+The synthesis encodings (Section~\ref{enc:synth}) is implemented  in~\ourtool.
 %
@@
 
-\input{smt-table}
-
+\input{table3}
 The minimal connectivity results for each variation of the existential condition are presented in Table~\ref{tab:smt-grph}.
@@
 %
-For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the vesicle transport networks in the stable state.
+For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the VTS in the stable state.
 %
@@
 
+\input{table4}
 %
-The Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
+Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
 %
@@
 
-\input{qbf-table}
+\input{table5}
 %\textbf{Universal Condition:}
 
-The Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
+Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
 %
@@
 %\textbf{Synthesis}:
+\input{table6}
 
@@
 %
-The results are presented in Figure~\ref{tab:synth-graph} for both the solvers
+The results are presented in Table~\ref{tab:synth-graph} for both the solvers
 \depqbf and \zthree.
@@
 
-In the Figure~\ref{tab:synth-graph}, we report five synthesis queries.
+In the Table~\ref{tab:synth-graph}, we report five synthesis queries.
 %

### 2019-06-15 papers/journal/fig3.tex
First Update for revision

--- 2019-04-08 papers/journal/synth-dia.tex
@@
 	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
-	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}};
-	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}};
-	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}};
+	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}} ...};
+	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}} ...};
+	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}} ...};
 
@@
 	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
-	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}...};
-	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}...};
-	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}...};
+	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}} ...};
+	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}} ...};
+	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}} ...};
 
@@
 	  %pm <-> ee
-	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
+	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, \\ {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
 	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{a2}$, \color{blue} {$R_{3}$}} (ee);
@@
   \end{subfigure}%
-  \caption{An example of synthesis of edge and molecules in the partial VTS.} \label{fig:synth-vts}
+  \caption{An example of synthesis of edge and molecules in the partial VTS} \label{fig:synth-vts}
 \end{figure}

### 2019-06-15 papers/journal/intro.tex
First Update for revision

@@
 %
-These compartments exchange molecules amongst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
+These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
 %
@@
 %
-Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
+Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
 %
@@
 %
+%\vspace{-0.5cm}
 \subsection{Vesicle traffic system}
 %Vesicles were discovered decades ago, in the early 1950s, and s
-\noindent The major molecules involved in the vesicle traffic system~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
+\noindent The major molecules involved in the VTS~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
 %
@@
 \begin{figure}
-	\includegraphics[height=10cm,width=12cm]{diavts.eps}
-	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
+  \begin{center}
+
+	\includegraphics[height=10cm,width=12cm]{fig1.eps}
+	\end{center}
+
+	\caption{Schematic of the VTS. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
 	%
@@
 	%
-	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents.}
+	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents}
     \label{fig:vts}
@@
 
-\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
+\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
 %
@@
 
-\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Figure~\ref{fig:vts}).
+\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}).
 
@@
 %\somya{schematic of intracellular compartments and  major routes}
-\subsubsection{Major paths in the vesicle transport network}
+\subsubsection{Major paths in the VTS}
 Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
@@
 \begin{itemize}
-	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus~\cite{alberts2002molecular}.
+	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane (from where they are secreted out of the cell) via the Golgi apparatus~\cite{alberts2002molecular}.
 	%
@@
 %
-\vspace{-0.5cm}
+\input{fig2}
+%
 \begin{example}
 %
-In Figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
+In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
 %
@@
 %
-Note that molecules $X$ and $Y$ do not take part in the fusion but play a part in determining activity at the corresponding nodes.
+Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
 %
@@
 %
-\input{pm-1-matrix}
 %\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
@@
 \subsection{Combinatorial problem and use of Formal methods}
-\noindent The analysis of vesicle traffic systems is a difficult problem
+\noindent The analysis of VTS is a difficult problem
 because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
@@
 %
-Precise analysis of the properties of the VTS would be hindered by the same reason.
+Precise analysis of the properties of the VTS would be hindered for the same reason.
 
@@
 \subsubsection{Size of the VTS system}
-Let us discuss the rough sizes of the system and expected behaviors.
+%Let us discuss the rough sizes of the system and expected behaviors.
 %%
@@
 \subsection{Synthesis of VTS }
-\noindent The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
+\noindent The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
 %
-Completing the vesicle traffic network is a difficult task for the many important reasons: 
+Completing the VTS is a difficult task for many important reasons: 
 \begin{enumerate}
-    \item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms~\cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
-
+    \item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
     \item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
-
     \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
     \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
-
     \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
@@
 
-Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
+Nonetheless, completing the VTS for different organisms is very useful. 
 %
-Many diseases are caused by the malfunction of the vesicle traffic network. 
+Many diseases are caused by the malfunction of the VTS. 
 %
@@
 %
-At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
+At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
 %
@@
 %
+\input{fig3}
 \begin{example}
+    In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments.
+Fig.~\ref{fig:synth-vts2} present it's complete output VTS.
+Every molecule present on the node is active.
+The activity of the molecules on an edge is determined by the presence of the other molecules.
+Each label represent particular type of molecule.
+The synthesis is performed against the stability and 3-connectivity.
+Synthesized edge is in red color and synthesized molecules are presented in blue.
+The synthesis adds one edge and 7 molecules to complete the partial VTS.
+For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
+\end{example}
 %
-    In Figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
-    %
-    The synthesis is performed against the steady state property and 3-connectivity. 
-    %The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for a proper discussion about the nodes and molecules depicted in the diagram). 
-    %
-    Synthesized edge is in red color and synthesized molecules are presented in blue.
-    %
-    The synthesis adds one edge and 7 molecules to complete the partial VTS.
-    %
-    For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
-
-\end{example}
-\input{synth-dia}
-
 We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 

### 2019-06-15 papers/journal/prelim.tex
First Update for revision

@@
-\noindent We will use lower case variables like $e,r,s$, etc to represent vectors of
+\noindent We will use lower case variables like $e$, $r$, $s$, etc to represent vectors of
 Boolean variables, possibly indexed, with multiple dimensions.
@@
 
-Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
+QBFs also allow quantifiers over Boolean variables.
 %
@@
 %
-The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{stockmeyer1973word, arora2009computational}.\\
+The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{savitch1970relationships, stockmeyer1973word}.
 %
@@
 %
-We will use BMC, SMT and QBF solvers to get the satisfying assignments.
+We will use SAT, SMT and QBF solvers to get the satisfying assignments.
 %

### 2019-06-15 papers/journal/problem.tex
dia on top
First Update for revision

--- 2019-04-08 papers/journal/problem.tex
@@
 %
-We categorize the search problem (Figure~\ref{fig:vts-search}) into three different categories, search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
+We categorize the search problem (Fig.~\ref{fig:vts-search}) into three different categories, search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
 %
@@
 
-\begin {figure}[!h]
+\begin {figure}[!t]
 \centering
-\begin{adjustbox}{width=\columnwidth}
+\begin{adjustbox}{width=0.9\columnwidth}
 {\Large
@@
 	[\textbf{1.Existential Condition}, for tree={fill=fv, child}, 
-	[BMC Section 6.2, for tree={fill=ai, child}]
-	[SMT Section 6.1\\, for tree={fill=ai, child}]
+	[BMC, for tree={fill=ai, child}]
+	[SMT, for tree={fill=ai, child}]
 	]
 	[\textbf{2.Universal Condition}, for tree={fill=fv, child},
-	[QBF \\ Section 6.3, for tree={fill=ai, child}]
+	[QBF, for tree={fill=ai, child}]
 	]
 	[\textbf{3.VTS Synthesis}, for tree={fill=fv,child}, 
-	[Synthesis Section 6.4, for tree={fill=ai, child}]
+	[Synthesis, for tree={fill=ai, child}]
 	]
@@
 
-\caption{Overview of the VTS search problems with respective encodings}
+\caption{An overview of the VTS search problems with their respective encodings}
 \label{fig:vts-search}
@@
 %
-We have used a form of this technique called satisfiability modulo theories (SMT)~\cite{nieuwenhuis2006solving, barrett2018satisfiability}.
+We have used a form of this technique known as SMT~\cite{nieuwenhuis2006solving, barrett2018satisfiability}.
 %
@@
 %Here we will present the QBF.
-\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
+\noindent We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
 %
@@
 %
-The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.
+The QBFs enables potentially more succinct encodings than SAT~\cite{jussila2007compressing} although much more difficult~\cite{savitch1970relationships, stockmeyer1973word} to solve.
 

### 2019-06-15 papers/journal/related.tex
First Update for revision

@@
-\noindent \improve{Not upto the mark}The previous analysis of vesicle traffic system used simulation and statistical reasoning~\cite{mani2016stacking}. 
+\noindent The previous analysis of VTS used simulation and statistical reasoning~\cite{mani2016stacking}. 
 %
@@
 
-The Boolean satisfiability (SAT) solvers are used to solve a wide range of problems including
+The SAT solvers are used to solve a wide range of problems including
 %
@@
 
-We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system (VTS). 
+We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely VTS. 
 %
@@
 % 
-To our best knowledge, this series of work is the first application
-of formal methods to the vesicle traffic networks.
+%To our best knowledge, this series of work is the first application
+%of formal methods to the vesicle traffic networks.
 
@@
 %%% End:
-~

### 2019-06-15 papers/journal/table6.tex
First Update for revision

--- 2019-04-03 papers/journal/synth-table.tex
@@
-\begin{sidewaysfigure}[t]
+%\begin{figure}[t]
+\begin{table}[t]
+
 	\centering
+	\resizebox{\textwidth}{!}{
 	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
@@
 		plos2-dia[4C] & 2.02 & 0   & 2.38 & 0  & 4.27  & 0 & 5.94 & 0 &  3.30 & 0 \\\hline
-		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 7 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -4AN. +1 E, +5PE, +4N, +3AN, +3AE. \\\hline
+		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 7 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -4AN. +1 E, +6PE, +8N, +3AN, +3AE. \\\hline
 		node4[3C]  & 5.93  & 1 E   &  13.72 & 12 PE  &  5.09  & $\infty$ & 4.30 &$\infty$& 7.21  & -2 E, -2PE, -1 N, -1AN, -1 AE. +18N, +8E, +1PE.\\\hline
@@
 		%    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
-	\end{tabular}
+	\end{tabular}}
 	% \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
@@
 	% \end{table}
+	\resizebox{\textwidth}{!}{
 	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
@@
 		plos2-dia & 3.97 & 0 &  2.26 & 0  & 5.46 & 0 & 5.35 & 0 & 3.24 & 0 \\\hline
-		sub-mammal & 3.22 & 1 E  & 4.18 & 7 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -4AN. +1 E, +5PE, +4N, +3AN, +3AE \\\hline
+		sub-mammal & 3.22 & 1 E  & 4.18 & 7 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -4AN. +1 E, +6PE, +8N, +3AN, +3AE \\\hline
 		node4  & 4.01  & 1 E  & 10.19  & 12 PE & 4.26  & $\infty$ & 4.13 &$\infty$&  6.89  & -2 E, -2PE, -1N, -1AN, -1AE. +18N, +8E, +1PE \\\hline
@@
 		mammal-graph   &  T/O     & N/A  &  T/O    & N/A    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A\\\hline
-	\end{tabular}
+	\end{tabular}}
 	\caption{Run-times for synthesis queries.
@@
 In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge.
-The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}
+The [kC] stands for k graph connectedness which is part of only DepQBF experiments}
 
@@
 	\label{tab:synth-graph}
-\end{sidewaysfigure}
+	\end{table}
+
+%\end{figure}

### 2019-06-15 papers/journal/conclusion.tex

@@
+\noindent 
 To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
@@
 %
-%Our results contain many predictions which can in principle be tested through cell-biological experiments.
 

### 2019-06-15 papers/journal/experiments.tex
Update first iteration on Review

@@
 	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
-The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
+The tool is based on CBMC~\cite{ckl2004}, a successful bounded model checker, for C and C++ programs. 
 %
@@
 %
-The tool is based on industrial strength SMT solver, Z3. 
+The tool is based on industrial strength SMT solver, Z3~\cite{de2008z3}. 
 %

### 2019-06-15 papers/journal/intro.tex
Update first iteration on Review

@@
 %
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
+We have also tested \cite{shukla2017discovering} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}.
 %
@@
 %
-In the VTS, labels are a string of molecule, where we show active molecules in red color.
+In the VTS, labels are a set of molecule, where we show active molecules in red color.
 %

### 2019-06-15 papers/journal/related.tex
Update first iteration on Review

@@
 
-One of the prominent areas of application of SAT and SMT solvers is modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
+One of the prominent areas of application of SAT and SMT solvers is modeling and understanding the gene regulatory networks (GRN)~\cite{giacobbe2015model,rosenblueth2014inference, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
 %

### 2019-06-23 papers/journal/bio.tex
Added new Bio section

--- 2019-03-12 papers/journal/bio.tex
@@
-First, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
-
+%\section{Vesicle traffic system background}
+The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
+%
+Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
+%
+%\vspace{-0.5cm}
 \subsection{Vesicle traffic system}
-Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}.
-These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
+%Vesicles were discovered decades ago, in the early 1950s, and s
+\noindent The major molecules involved in the VTS~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
+%
 Below, we give a brief description of the sequence of steps involved in the vesicle transport process. 
+%
 Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.
 
-%\includegraphics{akbar}
+\begin{figure}
+  \begin{center}
+	\includegraphics[height=9cm,width=12cm]{fig.png}
+	\end{center}
 
-\begin{figure}
-	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
-	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
+	\caption{Schematic of the VTS. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
 	%
@@
 	%
-	Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
+	Here, different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
 	%
-	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. 
+	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin. 
 	%
-	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment.
-At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
+	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex which is linked to the target compartment. 
+	%
+	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents}
     \label{fig:vts}
@@
 
-\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
+\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
 %
@@
 The next step is membrane deformation, which involves cytosolic coat proteins. 
+%
 Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
+%
 These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
+%
 A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
 %
-There are three major types of coat proteins; Clathrin, COP2 and COP1.
-These act on different compartments; the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.
-
-Finally, transport vesicles bud out from the source compartment.
-This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}.
+There are three major types of coat proteins: Clathrin, COP2, and COP1.
+These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
+%
+Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
 %
@@
 
-\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.
+\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}).
 
@@
 Distinct compartments of the cell are associated with distinct Rabs.
-For example, Rab5 is associated early endosomes and  Rab7 with late endosomes\cite{rink2005rab}.
-Rabs are master regulators; in their active form Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment.
-~\cite{muller2018molecular}
+For example, Rab5 is associated with early endosomes and Rab7 with late endosomes~\cite{rink2005rab}.
+%
+Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment~\cite{muller2018molecular}.
 
 Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion. 
+%
 They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion. 
-A clear mechanism for action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle associated Rabs, SNAREs and SNARE regulators.
+%
+A clear mechanism for the action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle, associated Rabs, SNAREs and SNARE regulators.
+%
 They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.
 
-The final step in vesicle transport is fusion of vesicle with the target compartment.This is brought about by SNARE proteins. 
+The final step in vesicle transport is the fusion of the vesicle with the target compartment is brought about by SNARE proteins. 
+%
 There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type. 
-In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment (A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs)~\cite{yoon2018snare}.
+%
+In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment. 
+%
+A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs~\cite{yoon2018snare}.
 
-\somya{schematic of snare regulatory network}
-In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
+%\somya{schematic of snare regulatory network}
+\subsubsection{Schematic of snare regulatory network}
+In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
 %
-\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
-\newline SM proteins have multiple modes of SNARE regulation: 
+Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
+%
+Whereas, SM proteins have following multiple modes of SNARE regulation: 
 \begin{itemize}
@@
 
-\somya{schematic of intracellular compartments and  major routes}
-\textbf{Major paths in the vesicle transport network}:
+%\somya{schematic of intracellular compartments and  major routes}
+\subsubsection{Major paths in the VTS}
 Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
@@
 \begin{itemize}
-	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
+	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane (from where they are secreted out of the cell) via the Golgi apparatus~\cite{alberts2002molecular}.
 	%
@@
 Other paths are used for cross talk between the secretory and the endocytic routes.
-For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}.
+For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes (endocytic route)~\cite{progida2016bidirectional}.
 Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus.
-The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.
-
+The molecules involved in these routes are as yet unknown~\cite{nickel2018unconventional}.
 %
-
 %\begin{table}
@@
 %\end{table}
+
+\subsection{The model}
+\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
+%
+On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
+%
+The following are the basic component and assumptions of our model. 
+\begin{enumerate}
+\item A cell is a set of compartments exchanging vesicles.
+\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
+\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
+\item Molecules are neither created nor destroyed~\cite{he2009differential}.
+\item Molecules move via vesicles of uniform size.
+\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
+\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
+%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
+\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
+\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
+. 
+\end{enumerate}
+%
+All our assumptions, except assumption 5, are held up by cell biological results.
+%
+Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the sake of simplicity, we assume a uniform size for intracellular vesicles.
+%The assumptions 
+%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
+%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
+
 \subsection{Abstraction of VTS as a graph problem}
@@
 
-\textbf{Steady state:} 
+\subsubsection{Steady state} 
 The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
 %
-In our model, we assume that the cell is in steady state.
+In our model, we assume that the cell is in a steady state.
 As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
@@
 %
-Not all sets of Q and R SNAREs are allowed to fuse with each other.
+Not all sets of Q and R-SNAREs are allowed to fuse with each other.
 %
-In the model, we assume that the cell has an equal number of Q and R SNARE types.
+%In the model, we assume that the cell has an equal number of Q and R SNARE types.
 %
-Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with an equal number of Q and R SNAREs. 
+Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R-SNAREs. 
 % equal number of Q and R SNAREs as a part of node and edge label.
@@
 %The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
+\subsection{Graph connectivity is an interesting and accessible property of the VTS} 
+%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
+\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
+%
+The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
+%
+But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.
 
-\subsubsection{Graph connectivity is an interesting and accessible property of the VTS}
-\ankit{This section requires serious work and best written by Mukund.}
-%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
-Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
-The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments.
-But we do not know if this information is complete.
-In order to assess how completely we know the VTS, we need easily readable benchmarks.
-
-\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
-One such benchmark is provided by our result about connectivity of the VTS graph.
+One such benchmark is provided by our result about the connectivity of the VTS graph.
 Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected.
@@
 Therefore the underlying undirected graph is 2-connected.
-From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity.
+From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity.
 When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
-And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].
+And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2 strongly connected.
 
-\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
-\somya{But this is the para where we explain why connectivity is interesting an biological property}
+%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
+%\somya{But this is the para where we explain why connectivity is interesting an biological property}
+%\ankit{Yes; Both of our remark looks correct!}
 The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
@@
 Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
-
-\ankit{Added this as a template. Will change it soon.}
+%
+%\begin{table}[!t]
+%	\caption{Table Caption}
+%	\label{tab1}
+%	\centering
+%	{\setlength\tabcolsep{0.1pt}%
+%		\begin{tabular}{ccccccccccccccc}
+%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
+%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
+%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
+%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
+%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
+%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
+%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
+%	\end{tabular}}
+%\end{table}
+%
+\input{fig2}
+%
 \begin{example}
 %
-In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
+In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
 %
-Molecules are numbered 0-7.
+%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
 %
-In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
+In the VTS, labels are a set of molecule, where we show active molecules in red color.
 %
-Every molecule on the node is active.
+The activity of the molecules on the node is controlled
+by the presence of the other molecules (exact Boolean function is not shown). 
 %
-The activity of the molecules on an edge are controlled
-by presence of the other molecules on the edge.
+The activity of the molecules on an edge is determined by the corresponding pairing matrix.
 %
-On the right side of the figure, we show the pairing matrix.
+Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
 %
-An entry 1 represents pairing between molecules.
+Below the VTS, we show the pairing matrix.
 %
-$\times$ represents no pairing.
+Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
 %
-Rows corresponds to the labels of edges, and
-columns corresponds to the labels of nodes.
+An entry 1 represents pairing between molecules and 0 represents no pairing.
 %
@@
 %
-This is a 3-connected graph.
+This is a 4-connected graph.
 \end{example}
-
-\input{pm-1-matrix}
+%
 %\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
@@
 %
+\subsection{Combinatorial problem and use of Formal methods}
+\noindent The analysis of VTS is a difficult problem
+because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
+%
+%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
+%
+%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
+If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
+%
+Precise analysis of the properties of the VTS would be hindered for the same reason.
+
+In previous work, a sampling approach was undertaken. 
+%
+The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached.
+%
+With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
+%
+Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
+%
+It is possible that a different scheme for the dynamics could lead to a different set of solutions.
+
+%Previous analyses of vesicle traffic networks dealt with this combinatorial
+%explosion by using a sampling approach~\cite{mani2016stacking}. 
+%
+%In these analyses, vesicle traffic is modelled as an update system. 
+%
+%The traffic rule specifies how the system transitions from one
+%time point to the next. 
+%
+%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
+%
+%The update rule defines the flux transition for the next step. 
+%
+%This process is performed until a steady state is reached. 
+%
+%
+%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
+%
+
+In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
+%
+We would also like to directly make statements about steady state properties, rather
+than using transition dynamics to the first search for steady states. 
+%
+Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
+%
+The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
+%
+
+\subsubsection{Size of the VTS system}
+%Let us discuss the rough sizes of the system and expected behaviors.
+%%
+%A typical VTS may have about 10 compartments.
+%%
+%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
+%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
+%%
+%The VTS may transport a large number of molecules but the molecules that
+%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
+%%
+%According to the definition the activity of molecules can be controlled by
+%the presence of all other molecules.
+%%
+%However, in practice the activity of a molecule is controlled by
+%the presence of ~2-3 other molecules.
+A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
+%
+The organellar content of cells varies across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhoptries and micronemes~\cite{gubbels2012evolution}.
+%
+The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
+%
+Also, across different cell-types, these organelles may be more or less differentiated, for example, the number of stacks in the Golgi varies across different cells~\cite{polishchuk2004structural}. 
+%
+
+Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
+%
+The VTS transports a large number of molecules but the molecules that actively control the system are in their tens~\cite{lodish2008molecular}. 
+%
+By definition, the activity of any VTS molecules can be controlled by all other molecules.
+%
+However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}.
+%
+Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
+%
+But most VTS molecules have more localized influence.
+%
+We use the above information during the encoding of all search problems presented later.
 
@@
 \subsection{Synthesis of VTS }
-The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.
+\noindent The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
 %
-Completing the vesicle traffic network is a difficult task for the many important reasons: 
+Completing the VTS is a difficult task for many important reasons: 
 \begin{enumerate}
-	\item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.
-
+    \item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
     \item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
-
-	\item Molecules can have redundant routes within the cell ~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
-	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.
-
-	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
+    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
+    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
+    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
 \end{enumerate}
 
-Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
+Nonetheless, completing the VTS for different organisms is very useful. 
 %
-Many diseases are caused by the malfunction of the vesicle traffic network. 
+Many diseases are caused by the malfunction of the VTS. 
 %
-Knowledge of the complete network would be helpful in identifying the root causes~\cite{bexiga2013human,gissen2007cargos}. 
+Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
 %
-At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
+At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
+%
+This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
 
@@
 %
-
+\input{fig3}
+\begin{example}
+    In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments.
+Fig.~\ref{fig:synth-vts2} present it's complete output VTS.
+Every molecule present on the node is active.
+The activity of the molecules on an edge is determined by the presence of the other molecules.
+Each label represent particular type of molecule.
+The synthesis is performed against the stability and 3-connectivity.
+Synthesized edge is in red color and synthesized molecules are presented in blue.
+The synthesis adds one edge and 7 molecules to complete the partial VTS.
+For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
+\end{example}
+%
 We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
@@
 %
-Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research. \\
+Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
 %
 
-\ankit{Added this as a template. Will change it soon.}
-\begin{example}
 %
-	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool.
-
-\end{example}
-\input{synth-dia}
-
 The rest of the paper is organized as follows. 
 %
-In Sect.~\ref{sec:prelim}, we present the notations we use in this paper. 
+In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
 %
-In Sect.~\ref{sec:model}, we present graph model of VTSs and  properties of interest in Sect.~\ref{sec:property}.
+In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
 %
-%encoding of several constraints on VTSs. 
+In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
 %
-%In , we present the
+In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
 %
-In Sect.~\ref{sec:problem}, we present the complete formal problem statement of the verification properties.
+In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
 %
-In Sect.~\ref{sec:encoding}, we present the encoding of BMC, SMT, QBF and Synthesis into SAT, SMT and QBF satisfiability. 
+In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
 %
-In Sect.~\ref{sec:experiments}, we present our implementation and experimental results. 
-%
-In Sect.~\ref{sec:related}, we discuss related work and conclude in Sect.~\ref{sec:conclusion}.
-
-%\textbf{Biological Model of VTS}
-%
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:
+~

### 2019-06-23 papers/journal/intro.tex
Added new Bio section

--- 2019-06-15 papers/journal/intro.tex
@@
 %
-The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
-%
-Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
-%
-%\vspace{-0.5cm}
-\subsection{Vesicle traffic system}
-%Vesicles were discovered decades ago, in the early 1950s, and s
-\noindent The major molecules involved in the VTS~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments.
-%
-Below, we give a brief description of the sequence of steps involved in the vesicle transport process. 
-%
-Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.
-
-\begin{figure}
-  \begin{center}
-
-	\includegraphics[height=10cm,width=12cm]{fig1.eps}
-	\end{center}
-
-	\caption{Schematic of the VTS. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
-	%
-	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
-	%
-	Here, different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
-	%
-	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin. 
-	%
-	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex which is linked to the target compartment. 
-	%
-	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents}
-    \label{fig:vts}
-\end{figure}
-
-\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
-%
-Cargo sorting is performed by cytosolic adaptor proteins. 
-Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
-%
-Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
-%
-Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
-%
-
-The next step is membrane deformation, which involves cytosolic coat proteins. 
-%
-Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
-%
-These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
-%
-A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
-%
-There are three major types of coat proteins: Clathrin, COP2, and COP1.
-These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
-%
-Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
-%
-The vesicle is now ready for transport and subsequent fusion with a target compartment.
-
-\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}).
-
-Target compartment recognition involves molecular switches called Rabs and tethering complexes.
-Distinct compartments of the cell are associated with distinct Rabs.
-For example, Rab5 is associated with early endosomes and Rab7 with late endosomes~\cite{rink2005rab}.
-%
-Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment~\cite{muller2018molecular}.
-
-Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion. 
-%
-They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion. 
-%
-A clear mechanism for the action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle, associated Rabs, SNAREs and SNARE regulators.
-%
-They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.
-
-The final step in vesicle transport is the fusion of the vesicle with the target compartment is brought about by SNARE proteins. 
-%
-There are four kinds of SNAREs: R, Qa, Qb, and Qc; and vesicle fusion requires formation of a SNARE complex containing one of each type. 
-%
-In all known cases, one SNARE protein of the complex is contributed by the vesicle and the other three SNAREs by the target compartment. 
-%
-A few SNARE proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs~\cite{yoon2018snare}.
-
-%\somya{schematic of snare regulatory network}
-\subsubsection{Schematic of snare regulatory network}
-In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
-%
-Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
-%
-Whereas, SM proteins have following multiple modes of SNARE regulation: 
-\begin{itemize}
-	\item SM proteins can hold
-	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
-	complexes.
-	%
-	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can form.
-	%
-	\item Finally, SM proteins bind the fully assembled
-	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
-	%
-	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
-\end{itemize}
-
-%\somya{schematic of intracellular compartments and  major routes}
-\subsubsection{Major paths in the VTS}
-Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
-%
-\begin{itemize}
-	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane (from where they are secreted out of the cell) via the Golgi apparatus~\cite{alberts2002molecular}.
-	%
-	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
-\end{itemize}
-Other paths are used for cross talk between the secretory and the endocytic routes.
-For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes (endocytic route)~\cite{progida2016bidirectional}.
-Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus.
-The molecules involved in these routes are as yet unknown~\cite{nickel2018unconventional}.
-%
-%\begin{table}
-%	\begin{center}
-%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-%			\hline
-%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
-%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
-%			\hline
-%		\end{tabular}
-%		\label{tab:threec}
-%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
-%	\end{center}	
-%\end{table}
-
-\subsection{The model}
-\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
-%
-On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
-%
-The following are the basic component and assumptions of our model. 
-\begin{enumerate}
-\item A cell is a set of compartments exchanging vesicles.
-\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
-\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
-\item Molecules are neither created nor destroyed~\cite{he2009differential}.
-\item Molecules move via vesicles of uniform size.
-\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
-\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
-%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
-\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
-\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
-. 
-\end{enumerate}
-%
-All our assumptions, except assumption 5, are held up by cell biological results.
-%
-Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the sake of simplicity, we assume a uniform size for intracellular vesicles.
-%The assumptions 
-%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
-%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
-
-\subsection{Abstraction of VTS as a graph problem}
-
-%In this section, we will describe the basic constraints imposed by cell biology. These are all incorporated into an abstract model of a VTS, whose properties will then be explored using SMT solvers.
-
-\noindent In this section, we will abstract from the biological description of the VTS and represent the whole network as an annotated transport graph. 
-%
-The constraints imposed by cell biology are incorporated in the annotations of the graph.
-
-\subsubsection{The cell as a transport graph} 
-%We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph.
-Every compartment or vesicle has a set of molecular labels, such as SNARE proteins, associated with it.
-The cell can be abstractly represented as an annotated graph. 
-Every compartment in the cell can be represented as a node in the graph. 
-%
-The set of molecules present in the compartment, for example, SNARE proteins associated with it, are represented as a label to the corresponding nodes.
-%
-The label of each node will be unique molecules present on the compartment, i.e we abstract over the quantity of the molecule present in a compartment.
-%This represents the flux of the molecule type present at that compartment.
-%
-The transport vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
-% 
-The label represents the associated flux of all molecular types carried by the corresponding vesicle.
-%
-%
-
-\subsubsection{Steady state} 
-The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
-%
-In our model, we assume that the cell is in a steady state.
-As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
-Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
-%
-In this paper, we refer to the steady state of the cell (referred to as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.
-
-%Each edge is associated with a flux of all the molecular types carried by the corresponding vesicle.
-The total amount of each molecular type on each compartment can therefore increase or decrease.
-We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales.
-Therefore, incoming and outgoing fluxes are balanced for each molecular type at each compartment; it is the \textit{stability cond1ition}.
-
-\subsubsection{Vesicle fusion}
-%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
-%
-%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
-% 
-%The molecular composition and hence the properties of the transfer vesicle 
-%is the crucial factor to which target compartment the vesicle will fuse to.
-%
-%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
-%  
-%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
-%
-%Once a vesicle has budded out of the source, the molecules it carries determine its properties.
-In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment.
-Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
-%
-%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
-Vesicle fusion requires a pairing of 3 Q-SNAREs and 1 R-SNARE that are distributed between the transfer vesicle and the target compartment. 
-%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
-%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
-%
-%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
-%
-Not all sets of Q and R-SNAREs are allowed to fuse with each other.
-%
-%In the model, we assume that the cell has an equal number of Q and R SNARE types.
-%
-Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R-SNAREs. 
-% equal number of Q and R SNAREs as a part of node and edge label.
-%
-%
-Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.
-
-\subsubsection{Molecular regulation} 
-Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
-%We assume that for fusion to occur, the pair of 
-%
-The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
-%
-In our abstract model, 
-we create a hierarchy of variants for varying degrees of regulation of SNARE activity.
-%we create a set of variations of different kind of molecular regulations.
-%
-Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
-%
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
-%
-This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
-%
-
-%We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state.
-Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively.
-We test many different versions of this kind of molecular regulation.
-Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle.
-We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
-This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
-
-%\textbf{Difficulty of the analysis:}
-
-%
-%Properties of the VTS would be hindered by the same reason. 
-%3-connected graphs and all possible variations of SNARE regulation rules. 
-%
-%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
-\subsection{Graph connectivity is an interesting and accessible property of the VTS} 
-%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
-\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
-%
-The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
-%
-But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.
-
-One such benchmark is provided by our result about the connectivity of the VTS graph.
-Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected.
-For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph.
-Therefore the underlying undirected graph is 2-connected.
-From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity.
-When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
-And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2 strongly connected.
-
-%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
-%\somya{But this is the para where we explain why connectivity is interesting an biological property}
-%\ankit{Yes; Both of our remark looks correct!}
-The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
-%
-In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
-%
-These predictions are intended to be used as guides for future experiments. 
-%
-A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
-%
-Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
-%
-%\begin{table}[!t]
-%	\caption{Table Caption}
-%	\label{tab1}
-%	\centering
-%	{\setlength\tabcolsep{0.1pt}%
-%		\begin{tabular}{ccccccccccccccc}
-%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
-%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
-%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
-%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
-%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
-%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
-%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
-%	\end{tabular}}
-%\end{table}
-%
-\input{fig2}
-%
-\begin{example}
-%
-In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
-%
-%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
-%
-In the VTS, labels are a string of molecule, where we show active molecules in red color.
-%
-The activity of the molecules on the node is controlled
-by the presence of the other molecules (exact Boolean function is not shown). 
-%
-The activity of the molecules on an edge is determined by the corresponding pairing matrix.
-%
-Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
-%
-Below the VTS, we show the pairing matrix.
-%
-Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
-%
-An entry 1 represents pairing between molecules and 0 represents no pairing.
-%
-Every molecule flows on a cycle, ensuring steady state.
-%
-This is a 4-connected graph.
-\end{example}
-%
-%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
-\label{subsec:graphmodel}
-%
-\subsection{Combinatorial problem and use of Formal methods}
-\noindent The analysis of VTS is a difficult problem
-because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
-%
-%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
-%
-%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
-If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
-%
-Precise analysis of the properties of the VTS would be hindered for the same reason.
-
-In previous work, a sampling approach was undertaken. 
-%
-The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached.
-%
-With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
-%
-Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
-%
-It is possible that a different scheme for the dynamics could lead to a different set of solutions.
-
-%Previous analyses of vesicle traffic networks dealt with this combinatorial
-%explosion by using a sampling approach~\cite{mani2016stacking}. 
-%
-%In these analyses, vesicle traffic is modelled as an update system. 
-%
-%The traffic rule specifies how the system transitions from one
-%time point to the next. 
-%
-%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
-%
-%The update rule defines the flux transition for the next step. 
-%
-%This process is performed until a steady state is reached. 
-%
-%
-%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
-%
-
-In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
-%
-We would also like to directly make statements about steady state properties, rather
-than using transition dynamics to the first search for steady states. 
-%
-Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
-%
-The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
-%
-
-\subsubsection{Size of the VTS system}
-%Let us discuss the rough sizes of the system and expected behaviors.
-%%
-%A typical VTS may have about 10 compartments.
-%%
-%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
-%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
-%%
-%The VTS may transport a large number of molecules but the molecules that
-%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
-%%
-%According to the definition the activity of molecules can be controlled by
-%the presence of all other molecules.
-%%
-%However, in practice the activity of a molecule is controlled by
-%the presence of ~2-3 other molecules.
-A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
-%
-The organellar content of cells varies across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhoptries and micronemes~\cite{gubbels2012evolution}.
-%
-The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
-%
-Also, across different cell-types, these organelles may be more or less differentiated, for example, the number of stacks in the Golgi varies across different cells~\cite{polishchuk2004structural}. 
-%
-
-Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
-%
-The VTS transports a large number of molecules but the molecules that actively control the system are in their tens~\cite{lodish2008molecular}. 
-%
-By definition, the activity of any VTS molecules can be controlled by all other molecules.
-%
-However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}.
-%
-Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
-%
-But most VTS molecules have more localized influence.
-%
-We use the above information during the encoding of all search problems presented later.
-
-% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
-%
-%
-% Note that the formulas define among other things constraints over
-% paths between nodes in the graph model of VTS. Similarly, one can
-% define fusion rules as constraints over the boolean functions modeling
-% the regulations.  
-% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
-%\begin{itemize}
-%\item \srivas{Detailed BIO to Graph problem}
-%\end{itemize}
-%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e.
-the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.
-Here we have defined the property by checking over existence of any fusion/budding rules.
-We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
-%
-%\subsection{Converting the Graph Problem into Boolean SAT problem}
-%\label{subsec:satproblem}
-%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.
-In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.
-We then used the CBMC model checker to convert the graph problem into a SAT problem.
-One of the challenges we had in our earlier work is dealing with quantifiers.
-Note that the connectedness property defined in Listing~1.2 has quantifier alternation.
-Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.
-CBMC supports only a quantifier-free logic n its assertion language.
-In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.
-This enumeration was one source of bottleneck for scaling in our earlier work.
-In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.
-The details of te hnew encding will described in subsequent sections.
-%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
-%
-%This property of VTSs has been considered informative and studied by~\cite{shukla}.
-%
-%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
-\subsection{Synthesis of VTS }
-\noindent The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
-%
-Completing the VTS is a difficult task for many important reasons: 
-\begin{enumerate}
-    \item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
-    \item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
-    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
-    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
-    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
-\end{enumerate}
-
-Nonetheless, completing the VTS for different organisms is very useful. 
-%
-Many diseases are caused by the malfunction of the VTS. 
-%
-Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
-%
-At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
-%
-This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
-
-%\subsection{Synthesis of VTS:}
-%
-The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
-%
-In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
-%
-We can use our stability and k-connectivity constraints as a basis for this investigation.   
-%
-The incomplete VTS might not respect these constraints. 
-%
-In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
-%
-We output various completed versions of VTS against these properties which can then be tested experimentally.
-%
-\input{fig3}
-\begin{example}
-    In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments.
-Fig.~\ref{fig:synth-vts2} present it's complete output VTS.
-Every molecule present on the node is active.
-The activity of the molecules on an edge is determined by the presence of the other molecules.
-Each label represent particular type of molecule.
-The synthesis is performed against the stability and 3-connectivity.
-Synthesized edge is in red color and synthesized molecules are presented in blue.
-The synthesis adds one edge and 7 molecules to complete the partial VTS.
-For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
-\end{example}
-%
-We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
-%
-We have applied our tool on several VTSs including
-two found-in-nature VTSs.
-%
-Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
-%
-
-%
-The rest of the paper is organized as follows. 
-%
-In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
-%
-In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
-%
-In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
-%
-In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
-%
-In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
-%
-In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
 %

### 2019-06-23 papers/journal/bio.tex
Updated draft with the reviews contents

@@
 
-	\caption{Schematic of the VTS. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
-	%
-	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
-	%
-	Here, different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
-	%
-	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin. 
-	%
-	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex which is linked to the target compartment. 
-	%
-	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents}
+	\caption{(A) Schematic of the vesicle transport system. Steps involved in vesicle transport between
+		two compartments: a source and a target compartment, are shown. The symbols used for different
+		molecules involved in vesicle traffic are explained in the key. At the source compartment,
+		transmembrane cargo proteins are sorted by cytosolic adaptor proteins. Here, different colours
+		indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming
+		vesicle by adaptor proteins. Note here that a single type of coat protein can interact with multiple
+		types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin
+		protein. Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and
+		the vesicle is recognized and bound by a tethering complex which is linked to the target compartment.
+		At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents. (B)
+		SNARE regulation network. Here, the dark blue, light blue, green and red stripes represent Qa, Qb,
+		Qc and R SNAREs respectively. These 4 SNAREs interact to form a SNARE complex. SNARE
+		complex formation is regulated by SM proteins and Sec 17/18. SM proteins inhibit SNARE complex
+		formation by inactivating Qa SNAREs. They also enhance SNARE complex formation by stabilizing
+		intermediate structures, and by inhibiting premature SNARE complex resolution. Sec17/18 aid in
+		SNARE complex resolution. (C) A schematic of the typic eukaryotic cell's VTS. Large circles
+		represent compartments, and edges represent vesicle routes. Identities of compartments are written
+		inside or beside them; ER = endoplasmic reticulum, Golgi = Golgi apparatus, PM = plasma
+		membrane, EE = early endosome, LE = late endosome, Lys = lysosome. The two major vesicle routes;
+		the secretory and the endocytic routes are in blue and orange, respectively. The routes in green
+		represent vesicles that allow cross-talk between the secretory and the endocytic routes. }
     \label{fig:vts}
@@
 
-\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
+\subsubsection{Vesicle budding} 
+The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}). 
 %
 Cargo sorting is performed by cytosolic adaptor proteins. 
-Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
 %
-Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
+Adaptor proteins bind to cargo molecules on the source
+compartment and thereby sequester them for packaging \cite{paczkowski2015cargo}. 
 %
-Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
+Next, cytosolic coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins \cite{faini2013vesicle}. 
 %
-
-The next step is membrane deformation, which involves cytosolic coat proteins. 
+Coat proteins cause membrane deformation. 
 %
-Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
-%
-These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
-%
-A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
-%
-There are three major types of coat proteins: Clathrin, COP2, and COP1.
-These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
-%
-Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
+Finally, transport vesicles bud out from the source
+compartment \cite{cocucci2014dynamin}. 
 %
 The vesicle is now ready for transport and subsequent fusion with a target compartment.
+%
+%The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
+%%
+%Cargo sorting is performed by cytosolic adaptor proteins. 
+%Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.
+%%
+%Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
+%%
+%Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
+%%
+%
+%The next step is membrane deformation, which involves cytosolic coat proteins. 
+%%
+%Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
+%%
+%These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
+%%
+%A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
+%%
+%There are three major types of coat proteins: Clathrin, COP2, and COP1.
+These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
+%%
+%Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
+%%
+%The vesicle is now ready for transport and subsequent fusion with a target compartment.
 
-\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}).
-
-Target compartment recognition involves molecular switches called Rabs and tethering complexes.
-Distinct compartments of the cell are associated with distinct Rabs.
-For example, Rab5 is associated with early endosomes and Rab7 with late endosomes~\cite{rink2005rab}.
+\subsubsection{Vesicle fusion} 
+The process of vesicle fusion involves two steps: recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}). 
 %
-Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment~\cite{muller2018molecular}.
-
-Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion. 
+Target compartment recognition involves molecular
+switches called Rabs and tethering complexes \cite{rink2005rab}. 
 %
-They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion. 
+Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment \cite{muller2018molecular}.
 %
-A clear mechanism for the action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle, associated Rabs, SNAREs and SNARE regulators.
-%
-They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.
+Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two
+before fusion \cite{baker2016chaperoning}.
 
@@
 %
+Pairing inhibition can be encoded as a pairing matrix $P$, whose rows and columns represent the molecule types present in the VTS. 
+%
+$P(i,j)$ = 1 implies that molecule $i$ binds molecule $j$.
+%
+In our simple pairing inhibition scheme, if $P(i,j)$ = 1 and both molecules $i$ and $j$ are present on the same compartment, $i$ and $j$ are inactive, and therefore cannot cause fusion.
 
@@
 %\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
-\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
+%\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
+%%
+%The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
+%%
+%But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks. 
 %
-The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
+%One such benchmark is provided by our result about the connectivity of the VTS graph.
+Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected.
+%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
+Suppose we are given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model.
+This information is then sufficient to check the following properties, which summarise the cell-biological constraints described above:
+\begin{enumerate}
+	\item We can determine which molecules are active on every compartment or vesicle.
+	\item For every vesicle fusing to a compartment, we can determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
+	\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we can verify that there is no pairing of active molecules on the
+	vesicle and compartment that could drive their fusion.
+	\item We can verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set.
+This is the steady state condition.
+In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
+\end{enumerate}
+
+The biological problem often boils down to such an analysis.
+A cell biologist might determine which molecules flow between which set of compartments, and biochemical experiments could be used to see how these molecules activate one another.
+We can then ask: is this a complete and consistent description?
+That is, do all the required properties listed above hold, given what the experimentalists have told us?
+It is often the case that biological data is missing.
+For example, only a few of the dozens of molecules involved in real VTSs have been mapped out.
+Therefore, it is extremely likely that the description provided by the cell biologist is incomplete.
+We can use our model to find out which properties have failed to hold, and thus prescribe new experiments in order to fill in the missing information.
+
+Can we find a simple test to see whether any information is missing, given the experimental data? It has shown that graph k-connectedness furnishes precisely such a test \cite{shukla2017discovering}.
 %
-But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.
+If the data provided by cell-biologists, suitably represented as a graph, does not have a certain degree of connectivity, this implies that some biological data has been missed.
+(The converse is not true: even if the required connectivity does hold, there might of course be more information missing.)
 
-One such benchmark is provided by our result about the connectivity of the VTS graph.
-Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected.
-For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph.
+%The result about k-connectedness being a useful test of missing information \cite{shukla2017discovering} was obtained using SAT solvers for graphs up to a certain size, and a certain number of molecules.
+This was due to limitations in how we encoded the problem.
+Here we present a much more natural encoding that allows our result to be extended to graph sizes and molecule numbers that are typical of those found in real cells.
+
+%For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph.
 Therefore the underlying undirected graph is 2-connected.
-From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity.
+%From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity.
 When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
@@
 %\ankit{Yes; Both of our remark looks correct!}
-The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
-%
-In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
-%
-These predictions are intended to be used as guides for future experiments. 
-%
-A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
-%
-Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
-%
+%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
+%%
+%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
+%%
+%These predictions are intended to be used as guides for future experiments. 
+%%
+%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
+%%
+%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
+%%
 %\begin{table}[!t]

### 2019-06-23 papers/journal/conclusion.tex
Updated draft with the reviews contents

@@
 \noindent 
-To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
+We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate
+into a global, observable properties of the VTS. 
 %
-The constraints implied by SNARE protein properties translates into
-mathematically elegant properties of the transport graph, namely its connectivity.
+Interactions between SNARE proteins and their
+regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological
+properties of the transport graph; all VTSs based on v-SNARE t-SNARE interactions must be 2-strongly connected.
 % 
-Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
-We manage to scale the tool up to the size that makes the tool biologically relevant.
+Additionally, we demonstrate how we can aid in predicting new vesicles given an incomplete VTS as input. 
+%
+Our approach demonstrates the power of SMT solvers in a novel application and the value of careful encoding of the problems into SMT queries. 
+%
+We manage to scale the tool up
+to the size that makes the tool biologically relevant.
+%To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
+%%
+%The constraints implied by SNARE protein properties translates into
+%mathematically elegant properties of the transport graph, namely its connectivity.
+%%
+%Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
+%We manage to scale the tool up to the size that makes the tool biologically relevant.
 %

### 2019-06-25 papers/journal/bio.tex
Minor Update
Introduction is added with the Synthesis as a Part

@@
 \end{example}
+\input{fig3}
+\begin{example}
+	In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments.
+Fig.~\ref{fig:synth-vts2} present it's complete output VTS.
+Every molecule present on the node is active.
+The activity of the molecules on an edge is determined by the presence of the other molecules.
+Each label represent particular type of molecule.
+The synthesis is performed against the stability and 3-connectivity.
+Synthesized edge is in red color and synthesized molecules are presented in blue.
+The synthesis adds one edge and 7 molecules to complete the partial VTS.
+For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
+	%The presented graph is a subgraph of a VTS discussed in details in appendix.
+\end{example}
+
 %
@@
 %
-\subsection{Combinatorial problem and use of Formal methods}
-\noindent The analysis of VTS is a difficult problem
-because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
+%\subsection{Combinatorial problem and use of Formal methods}
+%\noindent 
+%The analysis of VTS is a difficult problem
+%because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
 %
@@
 %
-%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
-If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
-%
-Precise analysis of the properties of the VTS would be hindered for the same reason.
-
-In previous work, a sampling approach was undertaken. 
-%
-The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached.
-%
-With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
-%
-Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
-%
-It is possible that a different scheme for the dynamics could lead to a different set of solutions.
-
-%Previous analyses of vesicle traffic networks dealt with this combinatorial
-%explosion by using a sampling approach~\cite{mani2016stacking}. 
-%
-%In these analyses, vesicle traffic is modelled as an update system. 
-%
-%The traffic rule specifies how the system transitions from one
-%time point to the next. 
-%
-%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
-%
-%The update rule defines the flux transition for the next step. 
-%
-%This process is performed until a steady state is reached. 
-%
-%
-%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
-%
-
-In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
-%
-We would also like to directly make statements about steady state properties, rather
-than using transition dynamics to the first search for steady states. 
-%
-Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
-%
-The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
-%
+%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool
 
@@
 %Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
-\subsection{Synthesis of VTS }
-\noindent The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
-%
-Completing the VTS is a difficult task for many important reasons: 
-\begin{enumerate}
-    \item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
-    \item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
-    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
-    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
-    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
-\end{enumerate}
+%\subsection{Synthesis of VTS }
 
-Nonetheless, completing the VTS for different organisms is very useful. 
-%
-Many diseases are caused by the malfunction of the VTS. 
-%
-Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
-%
-At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
-%
-This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
-
-%\subsection{Synthesis of VTS:}
-%
-The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
-%
-In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
-%
-We can use our stability and k-connectivity constraints as a basis for this investigation.   
-%
-The incomplete VTS might not respect these constraints. 
-%
-In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
-%
-We output various completed versions of VTS against these properties which can then be tested experimentally.
-%
-\input{fig3}
-\begin{example}
-    In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments.
-Fig.~\ref{fig:synth-vts2} present it's complete output VTS.
-Every molecule present on the node is active.
-The activity of the molecules on an edge is determined by the presence of the other molecules.
-Each label represent particular type of molecule.
-The synthesis is performed against the stability and 3-connectivity.
-Synthesized edge is in red color and synthesized molecules are presented in blue.
-The synthesis adds one edge and 7 molecules to complete the partial VTS.
-For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
-\end{example}
-%
-We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
-%
-We have applied our tool on several VTSs including
-two found-in-nature VTSs.
-%
-Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
 %
 
-%
-The rest of the paper is organized as follows. 
-%
-In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
-%
-In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
-%
-In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
-%
-In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
-%
-In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
-%
-In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
 %

### 2019-06-25 papers/journal/intro.tex
Introduction is added with the Synthesis as a Part

@@
-\noindent A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
+\noindent 
+%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
+The cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the
+nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
+%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
 %
-These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
+%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
 %
-The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
+%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
 %
-Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
+%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
 %
-Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
+%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
+%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
+%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
 %
-However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
-%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
-In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
 %
+Cargo is moved between these organelles in small membrane-bound
+transporters known as vesicles \cite{stenmark2009rab}.
+%s
+
+This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
+%
+Membrane traffic underpins nearly every aspect of eukaryotic cellular
+physiology, including human cellular physiology.
+%
+Defects in membrane traffic lead to a variety of disorders or even
+cell death \cite{stenmark2009rab}.
+%
+Understanding how membrane traffic functions is therefore one of the
+central challenges of cell biology.
+%
+Some progress has been made, as cell biologists have assembled a
+“parts list” of molecules that drive vesicle
+traffic~\cite{dacks2007evolution}.
+%
+The essential processes involve the creation of vesicles loaded with
+cargo from source organelles, known as “budding”, and the depositing
+of those vesicles and cargo into target organelles, known as “fusion”
+\cite{munro2004organelle}.
+%
+Budding is regulated by proteins known as coats and adaptors that
+select cargo.
+%
+Fusion is regulated by proteins known as SNAREs and tethers, that
+ensure that vesicles fuse to the correct target
+\cite{mani2016stacking}.
+%
+Although we know a great deal about molecular-level details, there has
+been very little work done on how such processes are integrated across
+scales to build the entire vesicle traffic system (VTS).
+%
+We have recently attempted to use ideas of graph theory to address
+this question \cite{mani2016stacking,shukla2017discovering}.
+
+The SNARE proteins and the constraints that SNARE-to-SNARE regulations
+impose on feasibile behaviors of VTSs are the focus of
+our current work.
+%
+Abstractly, we can think of these proteins as labels that are
+collected from the source compartment and taken to the target
+compartment on vesicles.
+%
+There is a corresponding set of label molecules on the target compartments.
+%
+If the two sets of labels (on vesicles and targets) are compatible,
+then the vesicle will fuse.
+%
+The question is: does this physical picture place any constrains on
+the global topology of the traffic graph? We have previously shown that one informative constraint is graph connectivity \cite{shukla2017discovering}.
+%
+The intricacies of SNARE regulation are largely unknown.
+%
+How stringent SNARE regulation is can determine whether graph
+topologies of particular level of connectivity are biologically
+realizable.
+%
+For example, if SNAREs are completely unregulated and thus always
+active, they cannot be used to generate a traffic network.
+%
+If these SNAREs are regulated by relatively simple rules then only
+highly connected traffic networks can be generated using them.
+%
+The question is can we work toward a predictive analytical framework
+of VTSs?
+
+Another interesting question is the completion of the VTS. 
+%
+The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
+%
+Completing the VTS is a difficult task for many important reasons: 
+\begin{enumerate}
+	\item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
+	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
+	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
+	\item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
+	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
+\end{enumerate}
+
+Nonetheless, completing the VTS for different organisms is very useful. 
+%
+Many diseases are caused by the malfunction of the VTS. 
+%
+Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
+%
+At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
+%
+This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
+
+%\subsection{Synthesis of VTS:}
+%
+The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
+%
+In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
+%
+We can use our stability and k-connectivity constraints as a basis for this investigation.   
+%
+The incomplete VTS might not respect these constraints. 
+%
+In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
+%
+We output various completed versions of VTS against these properties which can then be tested experimentally.
+%
+
+The analysis of VTSs is a difficult problem because
+of the combinatorial scaling of possible traffic topologies and
+regulatory rules.
+%
+If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
+%
+Precise analysis of the properties of the VTS would be hindered for the same reason.
+
+In previous work, a sampling approach was undertaken. 
+%
+The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached.
+%
+With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
+%
+Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
+%
+It is possible that a different scheme for the dynamics could lead to a different set of solutions.
+
+%Previous analyses of vesicle traffic networks dealt with this combinatorial
+%explosion by using a sampling approach~\cite{mani2016stacking}. 
+%
+%In these analyses, vesicle traffic is modelled as an update system. 
+%
+%The traffic rule specifies how the system transitions from one
+%time point to the next. 
+%
+%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
+%
+%The update rule defines the flux transition for the next step. 
+%
+%This process is performed until a steady state is reached. 
+%
+%
+%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
+%
+
+In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
+%
+We would also like to directly make statements about steady state properties, rather
+than using transition dynamics to the first search for steady states. 
+%
+Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
+%
+Formal verification tools, such as model checkers
+\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
+	cimatti2000nusmv, holzmann1997model} and SAT solvers
+\cite{moskewicz2001chaff,een2004extensible} serve precisely this
+purpose.
+%
+The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
+%
+
+%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
+\subsection{Previous work and our Contribution}
+In a recent work, we employed the model checker CBMC \cite{CKY03,
+	ckl2004} meant to analyze ANSI C programs for studying this problem.
+%
+In this work, VTSs and SNARE regulations were modeled as C code mostly
+using arrays to represent graphs and boolean tables.
+%
+Queries about graph connectivity requirements for different variations
+of SNARE Regulations were modeled as logical assertions to be checked
+by the model checker.
+%
+CBMC uses its own built-in encodings to reduce the analysis problem to
+boolean satisfiability problem which is solved using SAT solvers.
+%
+This work was successful in demonstrating the feasibility of this
+technology to this domain.
+%
+However, the scalability of this approach was limited (up to VTSs
+with 7-8 nodes) due to the following reasons:
+\begin{enumerate}
+	\item The encoding used to model VTSs was not completely fine-tuned
+	to the structure of the problem.
+	\item The queries to be solved involve quantified formulas, i.e., we
+	needed to solve queries of the form ``\emph{for all} graphs does there
+	\emph{exist} SNARE regulation constraints that satisfy biological
+	steady state.
+\end{enumerate} As CBMC does not directly support solving such
+quantified formulas, we had to use a technique that combined
+non-determinism and partial enumeration that is not as
+efficient.\newline
+
+%
+In this paper, we have developed a novel SAT encoding for
+searching a VTS that satisfy the given properties.
+%
+We improved the encoding of some of the conditions for VTSs.
+%
+In the earlier implementation, reachability was encoded by
+enumeration of paths.
+%
+In our encoding, we have recursively defined the reachability condition
+such that that we avoid the exponential enumeration.
+%
+We have also encoded $k$-connectivity in the similar fashion and
+avoided a blowup in the formula size.
+%
+
+We have implemented the encoding using Z3~\cite{z3} python API and searched for
+VTS satisfying various properties upto size 14-18 nodes as compare
+earlier tool that could only search graph upto size 7-8 nodes.
+%
+Since most VTSs in the cells are of 10 compartments,
+our tool will be useful for biologists to study VTSs.
+%
+Furthermore, our encoding supports several variations of
+the conditions.\newline
+
+The following are the contributions of this work:
+\begin{itemize}
+	\item We have added novel encoding reachability and 3-4 connectivity
+	\item Direct encoding into the SAT solver
+	\item A user friendly and scalable tool based on well known SMT solver Z3
+\end{itemize}
+
+\par We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
+%
+We have applied our tool on several VTSs including
+two found-in-nature VTSs.
+%
+Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
+%
+
+%
+The rest of the paper is organized as follows. 
+%
+In Section~\ref{sec:bio}, we present the biological background and details to understand the VTS. 
+%
+In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
+%
+In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
+%
+In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
+%
+In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
+%
+In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
+%
+In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
 %

### 2019-06-25 papers/journal/conclusion.tex
Minor Update

@@
 regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological
-properties of the transport graph; all VTSs based on v-SNARE t-SNARE interactions must be 2-strongly connected.
+properties of the transport graph; all VTSs based on V-SNARE T-SNARE interactions must be 2-strongly connected.
 % 

### 2019-06-28 papers/journal/intro.tex
Minor update in intro and addition of the rebuttle letter

@@
 transporters known as vesicles \cite{stenmark2009rab}.
-%s
-
+%
 This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
@@
 %
+
 Some progress has been made, as cell biologists have assembled a
@@
 %
-We would also like to directly make statements about steady state properties, rather
-than using transition dynamics to the first search for steady states. 
+Formal verification tools like model checkers, SAT,  SMT and QBF solvers serve precisely this purpose. 
 %
-Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
-%
-Formal verification tools, such as model checkers
-\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
-	cimatti2000nusmv, holzmann1997model} and SAT solvers
-\cite{moskewicz2001chaff,een2004extensible} serve precisely this
-purpose.
-%
+%Formal verification tools, such as model checkers
+%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
+%	cimatti2000nusmv, holzmann1997model} and SAT solvers
+%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
+%purpose.
+%%
 The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
@@
 \subsection{Previous work and our Contribution}
-In a recent work, we employed the model checker CBMC \cite{CKY03,
-	ckl2004} meant to analyze ANSI C programs for studying this problem.
-%
-In this work, VTSs and SNARE regulations were modeled as C code mostly
-using arrays to represent graphs and boolean tables.
-%
-Queries about graph connectivity requirements for different variations
-of SNARE Regulations were modeled as logical assertions to be checked
-by the model checker.
-%
-CBMC uses its own built-in encodings to reduce the analysis problem to
-boolean satisfiability problem which is solved using SAT solvers.
-%
-This work was successful in demonstrating the feasibility of this
-technology to this domain.
-%
-However, the scalability of this approach was limited (up to VTSs
-with 7-8 nodes) due to the following reasons:
-\begin{enumerate}
-	\item The encoding used to model VTSs was not completely fine-tuned
-	to the structure of the problem.
-	\item The queries to be solved involve quantified formulas, i.e., we
-	needed to solve queries of the form ``\emph{for all} graphs does there
-	\emph{exist} SNARE regulation constraints that satisfy biological
-	steady state.
-\end{enumerate} As CBMC does not directly support solving such
+
+As CBMC does not directly support solving such
 quantified formulas, we had to use a technique that combined

### 2019-06-28 papers/journal/intro.tex
Added synthesis reference

@@
 
-Another interesting question is the completion of the VTS. 
+Another interesting question is the completion of the VTS \cite{synthesisGupta}. 
 %
@@
 %
-Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
+Knowledge of the complete network would be helpful in identifying the root causes of~\cite{bexiga2013human,gissen2007cargos}. 
 %
@@
 %
-We can use our stability and k-connectivity constraints as a basis for this investigation.   
+We can use our graph connectivity results as a basis for this investigation.   
 %
@@
 
+\subsection{Analysis is difficult problem}
 The analysis of VTSs is a difficult problem because

### 2019-06-30 papers/journal/intro.tex
intro rewritten

@@
 %
-We can use our graph connectivity results as a basis for this investigation.   
+We use our graph connectivity results as a basis for this investigation.   
 %
@@
 
-\subsection{Analysis is difficult problem}
+%\subsection{Analysis is difficult problem}
 The analysis of VTSs is a difficult problem because
@@
 %
-If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
+Analysis on a large number of graphs~\footnote{There are total 68715 simple (no parallel edges) 3-connected graphs with 8 nodes} jointly with combinatorially many possible regulatory rules (all compatible labels of edges and nodes etc.) will be difficult to handle by any tool.
 %
@@
 
+In a recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
+%
+VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
+%
+The graph connectivity question for different variations of SNARE regulations were modeled as logical assertions to be checked by the model checker. 
+%
+Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle system with just 8 compartments).
+%
+Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper we call it universal condition) was partly handled using sampling and left open as a future work.
+%
+In this paper we present both the SMT and QBF encoding to address these two problems.
+%
 %These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
-\subsection{Previous work and our Contribution}
+%\subsection{Previous work and our Contribution}
+%
+%The following are the contributions of this work:
+%\begin{itemize}
+%	\item We have added novel encoding reachability and 3-4 connectivity
+%	\item Direct encoding into the SAT solver
+%	\item A user friendly and scalable tool based on well known SMT solver Z3
+%\end{itemize}
 
-As CBMC does not directly support solving such
-quantified formulas, we had to use a technique that combined
-non-determinism and partial enumeration that is not as
-efficient.\newline
-
+\par We have implemented the encoding in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
 %
-In this paper, we have developed a novel SAT encoding for
-searching a VTS that satisfy the given properties.
 %
-We improved the encoding of some of the conditions for VTSs.
+We have applied our synthesis tool on several VTSs including
+two found-in-nature VTSs.
 %
-In the earlier implementation, reachability was encoded by
-enumeration of paths.
-%
-In our encoding, we have recursively defined the reachability condition
-such that that we avoid the exponential enumeration.
-%
-We have also encoded $k$-connectivity in the similar fashion and
-avoided a blowup in the formula size.
-%
-
-We have implemented the encoding using Z3~\cite{z3} python API and searched for
-VTS satisfying various properties upto size 14-18 nodes as compare
-earlier tool that could only search graph upto size 7-8 nodes.
-%
-Since most VTSs in the cells are of 10 compartments,
-our tool will be useful for biologists to study VTSs.
-%
-Furthermore, our encoding supports several variations of
-the conditions.\newline
-
-The following are the contributions of this work:
-\begin{itemize}
-	\item We have added novel encoding reachability and 3-4 connectivity
-	\item Direct encoding into the SAT solver
-	\item A user friendly and scalable tool based on well known SMT solver Z3
-\end{itemize}
-
-\par We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
-%
-We have applied our tool on several VTSs including
-two found-in-nature VTSs.
+We manage to scale the tool upto the size that makes tool biologically relevant. 
 %

### 2019-06-30 papers/journal/intro.tex
minor update

@@
 %
-Formal verification tools like model checkers, SAT,  SMT and QBF solvers serve precisely this purpose. 
+Formal verification tools like model checkers, SAT,  SMT, and QBF solvers serve precisely this purpose. 
 %
@@
 %
-
 In a recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
@@
 %
-The graph connectivity question for different variations of SNARE regulations were modeled as logical assertions to be checked by the model checker. 
+The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
 %
-Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle system with just 8 compartments).
+Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle the system with just 8 compartments).
 %
-Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper we call it universal condition) was partly handled using sampling and left open as a future work.
+Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled using sampling and left open as future work.
 %
-In this paper we present both the SMT and QBF encoding to address these two problems.
+In this paper, we present both the SMT and QBF encodings to address these two problems.
 %
@@
 %
-%
 We have applied our synthesis tool on several VTSs including
@@
 %
-We manage to scale the tool upto the size that makes tool biologically relevant. 
+We manage to scale the tool to the size that makes the tool biologically relevant. 
 %

### 2019-06-30 papers/journal/intro.tex
merged problem stat with the property section

@@
 %
-Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled using sampling and left open as future work.
+Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled using sampling and left open.
 %
@@
 %
-In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
-%
-In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
+In Section~\ref{sec:model}, we present a formal model of VTSs and in section~\ref{sec:problem}, we present the property of interest with their formal problem statements of different search problems of VTS.
 %

### 2019-06-30 papers/journal/prelim.tex
Update first iteration on Review
merged problem stat with the property section

@@
 \subsubsection{Solvers}
-In this paper, we will encode several problems into finding satisfying
-solutions of a Boolean formula or QBFs.
+In this paper, we will encode several problems into finding satisfying solutions of a Boolean formula or QBFs.
 %
@@
 %
+%
 A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
 %1
+SMT solvers~\cite{nieuwenhuis2006solving, barrett2018satisfiability} in addition adds supports for some first order theories like arithmetic, arrays etc.
+%
+
 The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
 
+We also use bounded model checkers that implements Bounded model checking (BMC) technique~\cite{biere1999symbolic1, biere2003bounded} to performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
 %

### 2019-06-30 papers/journal/problem.tex
Update first iteration on Review
merged problem stat with the property section

@@
-\noindent This section will present the different search problems of VTS.
+\noindent %\improve{The weakest part of the paper; Need a serious rewrite!}
+We analyze the model against our desired properties.
 %
+%Since in biology there are no declared specifications or properties, we conjecture some properties that appear to be 
+%true in  relevant inall the known biological systems.
+%
+In this paper, we choose graph connectedness to be a key property.
+
 We categorize the search problem (Fig.~\ref{fig:vts-search}) into three different categories, search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
@@
 
-\subsection{Existential condition}
-\noindent We employ two techniques to examine the existential condition. 
+%
+We will also seek two kinds of questions give the property.
+% %
+% In this paper,
+% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
+% regulation rules of the VTS.
+% %
+% We are interested in the following two type of properties of the transport graph:
+\begin{enumerate}
+\item {\em Existential condition}:
+if there is a VTS that satisfies the connectedness property.
+
+\item {\em Universal condition}:
+  if there is a connectedness property that is satisfied by each valid VTS.
+\end{enumerate}
+The goal is to find the minimum graph connectivity properties for each of the condition.
+% In our program, the rules VTS needs to follow 
+% %
+% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
+% %
+% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
+% %
+% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
+% %
+% We will show in later sections how we encode these Boolean functions. 
+\subsubsection{Search for existential condition} 
+%
+% To ensure that k-connectedness is an existential condition,
+%
+We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
+%
+We also aim to find the minimum $k$. 
+%
+%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
+%
+To find a k-connected graph we specify our property as a query for the existence
+of a model for a conjunction of the formula representing stability, fusion and specific
+graph connectivity constraint. 
+%
+% \begin{align*}
+%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
+%  \tag{E}\label{eq:existcond}
+% \end{align*}
+%
+We will start with the value of $k = 1$ and check for the satisfiability of the formula.
+%
+In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
+%
+If the formula is not satisfiable we increment the $k$ by $1$ and repeat the same procedure. 
+%
+In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
+satisfies the existential condition.
+%
+% Used E as edge and L_e L_n as label for node and the edge,
+
+ We employ two techniques to examine the existential condition. 
 %
@@
 %The Bounded model checking technique
-BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
-%
-The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
-%
-In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
-%
-For our case, the unwinding depth is the length of the path of the underline graph.
+%BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
+%%
+%The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
+%%
+%In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
+%%
+%For our case, the unwinding depth is total number of nodes in the graph.
+%the maximum length of the path of the underline graph.
 %
 %
-For the experimentation, we restrict the check only to the elementary cycles; cycles of length one. 
-%
-This restriction puts an upper limit of the number of nodes on the length of the searched path. 
+%For the experimentation, we restrict the check only to the elementary cycles; cycles of length one. 
+%%
+%This restriction puts an upper limit of the number of nodes on the length of the searched path. 
 %
@@
 %and the upper bound is the number of nodes $N$.
-
 Second, using constraint solving, where the rules are represented as a constraint over the variables defined in the system.
@@
 %
-We have used a form of this technique known as SMT~\cite{nieuwenhuis2006solving, barrett2018satisfiability}.
-%
-The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors, etc.
-%
-%It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
-% is satisfiability of formulas with respect to some background theory.
-%
+We have used SMT solving.
+
 Throughout the paper, we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
@@
 
-%\noindent
-%The notion of stability and connectivity varies slightly for BMC encoding. 
-%%In this subsection, we will present the concept of stability and connectivity for BMC encoding. 
-%%
-%We call a graph $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
-%there exists a $m$-path in G with $n_1 = n'$ and $n_\ell = n$.
-%%
-%%
-%We call a graph $G$ {\em connected} if for each $n,n' \in \nodes$,
-%$n'$ there is a path from $n$ to $n'$ in G.
+\subsubsection{Search for universal condition}
 %
-%We call a graph $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
-%VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
-%%	
-%We use $m$-${path}_i^j$ to denote an $m$-path between source node i and target node is j. 
+% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
+For some $k>0$,
+we have to ensure that every graph of $k$-connected structure satisfies all
+the rules of the system.
 %
+We also aim to find the minimum $k$. 
+% We also have to ensure that the particular k is the least one. 
 %
-%Creating a formula to search a path of length N-1 for each molecule m on every edge E will be extremely large and harder for the solvers to handle.  
-%%
-%Even if there exist shorter paths we have to create the formula of maximum size N-1. 
-%% 
-%To resolve these problems we will use a technique called bounded model checking, where the depth of the path can be specified and consequently increased or decreased.  
+This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
 %
-
-\subsection{Universal condition}
-%Here we will present the QBF.
-\noindent We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
+% \begin{align*}
+%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
+%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
+%   \tag{U}\label{eq:univcond}
+% \end{align*}
+%
+We will use the same procedure as the existential condition to ensure the k to be the least one.
+%
+The formula for the problem has quantifier alternation. 
+%
+Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
+%
+We need a QBF solver for such queries.
+%
+We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
 %
@@
 %
-% Our tool is easily modifiable to support any other property that may be deemed 
-% interesting by the biologists.
 
+%To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.
+%
 %%% Local Variables:

### 2019-06-30 papers/journal/problem.tex
Improved problem stat section

@@
 In this paper, we choose graph connectedness to be a key property.
-
+%
 We categorize the search problem (Fig.~\ref{fig:vts-search}) into three different categories, search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
@@
 
-%
-We will also seek two kinds of questions give the property.
+\vspace{0.2cm}
+\noindent We will also seek two kinds of questions give the property.
 % %
@@
 % We will show in later sections how we encode these Boolean functions. 
-\subsubsection{Search for existential condition} 
+\subsection{Search for existential condition} 
 %
@@
 %
-First, using the bounded model checking (BMC) technique~\cite{biere1999symbolic1, biere2003bounded}.
+First, using the BMC and second using SMT solving.
 %
-%It  represents the executions of a program symbolically and 
-%
-%The Bounded model checking technique
-%BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}).
-%%
-%The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
-%%
-%In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
-%%
-%For our case, the unwinding depth is total number of nodes in the graph.
-%the maximum length of the path of the underline graph.
-%
-%
-%For the experimentation, we restrict the check only to the elementary cycles; cycles of length one. 
-%%
-%This restriction puts an upper limit of the number of nodes on the length of the searched path. 
-%
-%
-%and the upper bound is the number of nodes $N$.
-Second, using constraint solving, where the rules are represented as a constraint over the variables defined in the system.
-%
-The search problem is to find an assignment of variables that satisfies all the specified constraints.
-%
-We have used SMT solving.
-
 Throughout the paper, we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
-%The existential condition search problem is represented as a bounded model checking and constraint solving. 
-%
-%Based upon earlier discussion, we need to answer the following search question among VTSs.
 %
@@
 
-\subsubsection{Search for universal condition}
+\subsection{Search for universal condition}
 %

### 2019-06-30 papers/journal/fig3.tex
Update on the fig 2 legend

@@
   \end{subfigure}%
-  \caption{An example of synthesis of edge and molecules in the partial VTS} \label{fig:synth-vts}
+  \caption{An example of the synthesis of edge and molecules in the partial VTS.
+Black edges correspond to the edges in the input VTS and the synthesized edge is shown in the red color.
+Similarly, synthesized molecules are shown in blue color.} \label{fig:synth-vts}
 \end{figure}

### 2019-07-03 papers/journal/intro.tex
Update on the fig 2 legend
Minor Updated suggested By Somya
Minor Updated suggested By Somya. Without a ref.

@@
 %A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
-The cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the
-nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
+Eukaryotic cells contain distinct membrane-bound objects known as organelles: endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
 %These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
@@
 \end{enumerate}
+        \item Lastly, interpreting experimental results can be difficult, since behaviour of traffic molecules in vitro is different from their behavior inside cells.
 
@@
 
-\par We have implemented the encoding in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
+\par We have implemented the encodings in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
 %

### 2019-07-07 papers/journal/intro.tex
Update might be Complie erros

@@
 Some progress has been made, as cell biologists have assembled a
-“parts list” of molecules that drive vesicle
+``parts list” of molecules that drive vesicle
 traffic~\cite{dacks2007evolution}.
@@
 \end{enumerate}
-        \item Lastly, interpreting experimental results can be difficult, since behaviour of traffic molecules in vitro is different from their behavior inside cells.
+     %   \item Lastly, interpreting experimental results can be difficult, since behaviour of traffic molecules in vitro is different from their behavior inside cells.
 

### 2019-07-08 papers/journal/prelim.tex
Added the rebuttal First Draft

@@
 The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
+%
+We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
+%
+The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
+%
+The QBFs enables potentially more succinct encodings than SAT~\cite{jussila2007compressing} although much more difficult~\cite{savitch1970relationships, stockmeyer1973word} to solve.
 

### 2019-07-08 papers/journal/problem.tex
Added the rebuttal First Draft

@@
 %
-We will use the same procedure as the existential condition to ensure the k to be the least one.
+We will use the same procedure as the existential condition to ensure the $k$ to be the least one.
 %
@@
 %
-We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
-%
-The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
-%
-The QBFs enables potentially more succinct encodings than SAT~\cite{jussila2007compressing} although much more difficult~\cite{savitch1970relationships, stockmeyer1973word} to solve.
 

### 2019-07-08 papers/journal/problem.tex
Fixed missing part objection

@@
 %
-Our objective is to find the missing parts.
+Our objective is to find the missing components.
 %
-The missing parts can be in any of the components of VTS. 
+The missing component can
+% be in any of the components of VTS. 
 %
-For example, some undiscovered edges or nodes, or insufficient
+%For example, 
+be some undiscovered edges or nodes, or insufficient
 knowledge about the presence of molecules in some part of the VTS.

### 2019-07-08 papers/journal/encoding.tex
Update on the fig 2 legend
Fixed missing part objection

@@
 \input{table2}
-\noindent The specification for universal condition Section~\ref{sec:property} requires quantifier alternation. 
+\noindent The specification for universal condition Section~\ref{sec:problem} requires quantifier alternation. 
 %
@@
 One will encode the variable part in the synthesis problem and
-the other encodes the fixed parts.
+the other encodes the fixed components.
 %
@@
 %
-\texttt{FixedForEdge} encodes the parts of the VTS that are not allowed to change.
+\texttt{FixedForEdge} encodes the components of the VTS that are not allowed to change.
 \begin{align*}
@@
 In the later synthesis problems, we will construct a similar QBF
-formula with same first two parts and the last two are due the
+formula with same first two components and the last two are due the
 requirements of the synthesis problem.
@@
 
-\subsubsection{Fixing VTS by both adding/deleting parts}
+\subsubsection{Fixing VTS by both adding/deleting components}
 %
@@
 %
-Where, the constraint $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
+Where, the constraint $\texttt{FixedForNodeRepair}$ encodes all the components of VTS that do not change.
 \begin{align*}

### 2019-07-08 papers/journal/prelim.tex
adde dSMT

--- 2019-06-30 papers/journal/prelim.tex
@@
 
-QBFs also allow quantifiers over Boolean variables.
+The SMT~\cite{barrett2018satisfiability} is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-
+vectors, etc.
 %
+For example, $f(f(u,v),v)=f(u,v)$ where $f$ is some unspecified function of two arguments has equality involving uninterpreted terms and function symbols.
+
+%QBFs also allow quantifiers over Boolean variables.
+%
+The QBF~\cite{buning2009theory, benedetti2008qbf} is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
+%
+The QBFs enables potentially more succinct encodings than SAT~\cite{jussila2007compressing} although much more difficult~\cite{savitch1970relationships, stockmeyer1973word} to solve.
 For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
@@
 %
-The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{savitch1970relationships, stockmeyer1973word}.
+%The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{savitch1970relationships, stockmeyer1973word}.
 %
@@
 % 
-
 The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
+%
+%We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
+%
 

### 2019-07-09 papers/journal/prelim.tex
Added new reference for SAT

@@
 %
-An assignment may satisfy a formula if the interpretation of Boolean operators
-reduces the whole Formula into 1.
+An assignment may satisfy a formula if the interpretation of Boolean operators reduces the whole Formula into 1.
 %
-The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
+The SAT~\cite{biere2009handbook} is the problem of determining if there exists an interpretation that satisfies a given Boolean formula and is known to be hard~\cite{cook1971complexity}.
 %
 
-The SMT~\cite{barrett2018satisfiability} is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-
+The SMT~\cite{nieuwenhuis2006solving, barrett2018satisfiability} is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-
 vectors, etc.
@@
 %1
-SMT solvers~\cite{nieuwenhuis2006solving, barrett2018satisfiability} in addition adds supports for some first order theories like arithmetic, arrays etc.
+SMT solvers~\cite{barrett2018satisfiability} in addition adds supports for some first order theories like arithmetic, arrays etc.
 % 

### 2019-07-11 papers/journal/bio.tex
Added reference to the Appendix fig
Updated the rebuttal

@@
 
+In this work, we use the term activity to have very specific scope; it only implies the ability to cause membrane fusion and it only applies to SNAREs. 
+%
+In this sense, it indeed does not matter whether the molecule interacting with the SNARE is active or not. 
+%
+For example, Qa-SNAREs are only active on target compartments (regulation by SM proteins achieves this \cite{baker2016chaperoning}), but when present on vesicles with its other cognate SNAREs, it nevertheless will participate in SNARE complex formation within the same vesicle membrane, and thus inhibit its SNARE partners from causing vesicle fusion.
 %We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state.
@@
 For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
+This synthetic example is a sub-graph of the VTS shown in the \ref{fig:mukund-vts}.
+Please refer to \ref{sec:ex-vts} for complete detail.
 	%The presented graph is a subgraph of a VTS discussed in details in appendix.

### 2019-07-11 papers/journal/conclusion.tex
Updated the rebuttal

@@
 \noindent 
-We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate
-into a global, observable properties of the VTS. 
+We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate into a global, observable properties of the VTS. 
 %
-Interactions between SNARE proteins and their
-regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological
-properties of the transport graph; all VTSs based on V-SNARE T-SNARE interactions must be 2-strongly connected.
+Interactions between SNARE proteins and their regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological properties of the transport graph; all VTSs based on SNARE protein interactions must be 2-strongly connected.
 %
@@
 %
-We manage to scale the tool up
-to the size that makes the tool biologically relevant.
+We manage to scale the tool up to the size that makes the tool biologically relevant.
+%
 %To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
@@
 %
-We used QBF solvers for such queries.
+We used QBF solvers for such queries. Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
 %
-Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
+For any input VTS, our tool outputs multiple possible solutions in the form of predictions of undiscovered vesicles and cargo molecules on specific vesicles. 
 %
-One may also be interested in counting the number of graphs that satisfy
-a given property. 
+Such predictions could be used to guide biological experiments.
+Since a VTS that is close to completion is expected to have fewer alternative solutions to test, we expect that testing the predictions of our tool would become more tractable as more and more vesicles are discovered.
 %
-Exact counting of the graphs using SAT solvers may prove to be very
-difficult. 
+One may also be interested in counting the number of graphs that satisfy a given property. 
 %
-We are planning to employ approximate counting methods for finding the solution.
-%
+Exact counting of the graphs using SAT solvers may prove to be very difficult. We are planning to employ approximate counting methods for finding the solution.
 

### 2019-07-11 papers/journal/bio.tex
Added left out comment: addressed

@@
 \subsubsection{Steady state} 
-The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
+%The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
+%
+%In our model, we assume that the cell is in a steady state.
+As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
+%Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
+%
+%In this paper, we refer to the steady state of the cell (referred to as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.
+
+In eukaryotic cells, vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
 %
@@
 As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
+%
+This is much stronger than the constraint that each molecule type entering a compartment must also leave it.
+%
+But, since our model is essentially binary, the two statements become equivalent. 
+%
 Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
 %
-In this paper, we refer to the steady state of the cell (referred to as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.
+In this paper, we refer to the steady state of the cell (referred to as homeostasis in biological literature) as the stability condition over the annotated graph.
 

### 2019-07-12 papers/journal/intro.tex
adde dSMT
asd

--- 2019-07-03 papers/journal/intro.tex
@@
 %A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
-Eukaryotic cells contain distinct membrane-bound objects known as organelles: endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
+Eukaryotic cells contain distinct membrane-bound objects known as organelles: endoplasmic reticulum (ER), Golgi apparatus, vacuoles, and lysosomes are examples of these.
 %These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
@@
 %
-Cargo is moved between these organelles in small membrane-bound
+Some of the material of the cell needs to move
+between these organelles in small membrane-bound
 transporters known as vesicles \cite{stenmark2009rab}.
 %
-This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
+This organization resembles a transport logistics network
+and is commonly known as the membrane traffic system.
 %
@@
 %
-Understanding how membrane traffic functions is therefore one of the
+Understanding how membrane traffic functions are, therefore, one of the
 central challenges of cell biology.
@@
 
-Some progress has been made, as cell biologists have assembled a
+The cell biologists have made some progress by assembling a
 “parts list” of molecules that drive vesicle
@@
 %
-Budding is regulated by proteins known as coats and adaptors that
-select cargo.
+Proteins that are called coats and the adaptors that select the cargo regulate budding.
 %
-Fusion is regulated by proteins known as SNAREs and tethers, that
-ensure that vesicles fuse to the correct target
+The proteins that are known as SNAREs and tethers that ensure that vesicles
+fuse to the correct target regulate fusion
 \cite{mani2016stacking}.
@@
 %
-We have recently attempted to use ideas of graph theory to address
+We have recently attempted to use the ideas of graph theory to address
 this question \cite{mani2016stacking,shukla2017discovering}.
@@
 The SNARE proteins and the constraints that SNARE-to-SNARE regulations
-impose on feasibile behaviors of VTSs are the focus of
+impose on the feasible behaviors of VTSs are the focus of
 our current work.
@@
 %
-The question is: does this physical picture place any constrains on
+The question is: does this physical picture place any constraints on
 the global topology of the traffic graph? We have previously shown that one informative constraint is graph connectivity \cite{shukla2017discovering}.
@@
 %
-How stringent SNARE regulation is can determine whether graph
-topologies of particular level of connectivity are biologically
+How stringent SNARE regulation is can determine whether the graph
+topologies of a particular level of connectivity are biologically
 realizable.
@@
 %
-If these SNAREs are regulated by relatively simple rules then only
+If relatively simple rules regulate the SNAREs, then only
 highly connected traffic networks can be generated using them.
 %
-The question is can we work toward a predictive analytical framework
+The question is, can we work toward a predictive analytical framework
 of VTSs?
@@
 %
-The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}.
+The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and
+researchers are discovering new vesicle routes every
+year~\cite{nickel2018unconventional,weill2018toolbox}. 
 %
@@
 \begin{enumerate}
-	\item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
+	\item The core VTS is similar across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
 	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
 	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
-	\item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
+	\item The behavior of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
 	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
+        \item Lastly, interpreting experimental results can be difficult, since the behavior of traffic molecules in vitro is different from their behavior inside cells.
 \end{enumerate}
-        \item Lastly, interpreting experimental results can be difficult, since behaviour of traffic molecules in vitro is different from their behavior inside cells.
 
@@
 %
-Many diseases are caused by the malfunction of the VTS. 
+The malfunction of the VTS causes many diseases.
 %
-Knowledge of the complete network would be helpful in identifying the root causes of~\cite{bexiga2013human,gissen2007cargos}. 
+The knowledge of the complete network would help identify the root causes of
+the diseases~\cite{bexiga2013human,gissen2007cargos}. 
 %
@@
 %
-This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.
+The network knowledge would also allow us to decipher features such as parts of the traffic system that is unchanging and therefore likely to be its core, and more plastic parts~\cite{barlow2017seeing}.
 
@@
 %
-The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
+The underlying cell biology dictates the set of basic constraints the VTS should follow.
 %

### 2019-07-12 papers/journal/intro.tex
asd

@@
 %
-We output various completed versions of VTS against these properties which can then be tested experimentally.
+We output various completed versions of VTS against these properties, which we can then test experimentally.
 %
@@
 %
-Analysis on a large number of graphs~\footnote{There are total 68715 simple (no parallel edges) 3-connected graphs with 8 nodes} jointly with combinatorially many possible regulatory rules (all compatible labels of edges and nodes etc.) will be difficult to handle by any tool.
+An analysis of a large number of graphs~\footnote{There are total 68715 simple (no parallel edges) 3-connected graphs with 8 nodes} jointly with combinatorially many possible regulatory rules (all compatible labels of edges and nodes etc.) will be difficult to handle by any tool.
 %
-Precise analysis of the properties of the VTS would be hindered for the same reason.
+The same reason would hinder the precise analysis of the properties of the VTS.
 
-In previous work, a sampling approach was undertaken. 
+A previous work used a sampling approach. 
 %
-The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached.
+The study used a rule-based approach~\cite{mani2016stacking}.
+Given an initial condition of the cell and rules for molecular traffic,
+the approach updates the state of each compartment in the cell until the cell reaches a steady-state. 
 %
@@
 
-In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset.
+In contrast, here we seek to understand the properties of vesicle traffic networks
+over all possible update rules, not just for a sampled subset.
 %
-Formal verification tools like model checkers, SAT,  SMT, and QBF solvers serve precisely this purpose. 
+Formal verification tools like model checkers, SAT (Boolean satisfiability), SMT (satisfiability modulo theories) and QBF (quantified Boolean formula) solvers serve precisely this purpose. 
 %
@@
 %%
-The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
+The tools model the computation symbolically for the graphs of finite size and can predict the hypothesis for all possible states of the system without explicit enumeration of rules. 
 %
-In a recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
+In recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
 %
@@
 %
-Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle the system with just 8 compartments).
+Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient. The tool was able to handle the system with just eight compartments.
 %
-Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled using sampling and left open.
+Another interesting question of property involving quantifiers (was termed as sufficient condition i
+n \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
+using sampling and left open.
 %
-In this paper, we present both the SMT and QBF encodings to address these two problems.
+In this paper, we present both the SMT and QBF encodings to address the two problems.
+%
+
 %
@@
 
-\par We have implemented the encodings in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
+\par We have implemented the encodings in a flexible tool, which can handle both connectivity questions and a wide range of synthesis queries. 
 %
-We have applied our synthesis tool on several VTSs including
+We have applied our synthesis tool on several VTSs, including
 two found-in-nature VTSs.
@@
 %
-The rest of the paper is organized as follows. 
+We organized the rest of the paper as follows. 
 %
@@
 %
-In Section~\ref{sec:model}, we present a formal model of VTSs and in section~\ref{sec:problem}, we present the property of interest with their formal problem statements of different search problems of VTS.
+In Section~\ref{sec:model}, we present a formal model of VTSs, and in section~\ref{sec:problem}, we present the property of interest with their formal problem statements of different search problems of VTS.
 %

### 2019-07-12 papers/journal/intro.tex
asd

@@
 %
-In this paper, we present both the SMT and QBF encodings to address the two problems.
+We also worked on the synthesis of the unknown pieces may
+be {\em assisted} by computation on the graph model of VTSs~\cite{synthesisGupta}.
+%
+In the work, we developed encoding for the synthesis problem.
+%
+This paper brings together the above encodings with extended experiments and more detailed
+expositions for the benefit of both biological and computation community.
+We additionally explored QBF based encoding of some of the problems.
+
+% In this paper, we present both the SMT and QBF encodings to address the two problems.
 %

### 2019-07-12 papers/journal/intro.tex
Minor fix

@@
 %
-Another interesting question of property involving quantifiers (was termed as sufficient condition i
-n \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
+Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
 using sampling and left open.

### 2019-07-12 papers/journal/intro.tex
asd

@@
 %
-In recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
+In recent work~\cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
 %
@@
 using sampling and left open.
+%
+In~\cite{smtVTS}, we developed more efficient direct encoding to SMT solvers. 
 %

### 2019-09-09 papers/journal/intro.tex
Added rebuttal outline
Updates from Overleaf

@@
 %
-Understanding how membrane traffic functions are, therefore, one of the
+Understanding how membrane traffic functions is, therefore, one of the
 central challenges of cell biology.
@@
 
-The cell biologists have made some progress by assembling a
+Cell biologists have made some progress by assembling a
 “parts list” of molecules that drive vesicle
@@
 %
-The network knowledge would also allow us to decipher features such as parts of the traffic system that is unchanging and therefore likely to be its core, and more plastic parts~\cite{barlow2017seeing}.
+The network knowledge would also allow us to decipher features such as parts of the traffic system that are unchanging and therefore likely to be its core, and more plastic parts~\cite{barlow2017seeing}.
 
@@
 %
-We also worked on the synthesis of the unknown pieces may
+We also worked on the synthesis of the unknown pieces that may
 be {\em assisted} by computation on the graph model of VTSs~\cite{synthesisGupta}.
 %
-In the work, we developed encoding for the synthesis problem.
+In the work, we developed an encoding for the synthesis problem.
 %

### 2019-09-09 papers/journal/encoding.tex

@@
 \end{align*}
+
+%We have used logarithmic bitwise encoding to express the cardinality constraint that exactly $k-1$ edges are dropped. 
+%To encode exactly $k$ edges are dropped we need to express cardinality constraint to allow exactly $k$ edges to be true from set of all present edges $e$. 
+%
 We need to define reachability in the modified VTS, therefore we use
@@
 \input{table2}
-\noindent The specification for universal condition Section~\ref{sec:problem} requires quantifier alternation. 
+\noindent The specification for the universal condition described in Section~\ref{sec:problem} requires quantifier alternation. 
 %

### 2019-09-09 papers/journal/problem.tex
Fixed missing part objection

@@
 \vspace{0.2cm}
-\noindent We will also seek two kinds of questions give the property.
+\noindent We will also seek to answer two kinds of questions given the property.
 % %
@@
 %
-We will use the same procedure as the existential condition to ensure the $k$ to be the least one.
+We will use the same procedure as the existential condition to ensure that $k$ is minimized.
 %
@@
 	% - Function dependence with var occurring once.
-	\item  Fixing VTS by both adding/deleting parts
+	\item  Fixing VTS by both adding/deleting components
 \end{enumerate}

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
renamed it to .txt

% Reviewer 1:
    No Comments!

% Reviewer 3:

> I believe that most issues highlighted previously have been 
  addressed adequately. In particular, the structure of the 
  revised manuscript has been improved significantly. 
  I still found the paper challenging to read, but this is 
  largely due to the complexity of the biological system and 
  the necessary encoding details presented in the manuscript.

  Pt #1:
-------- Handle by Mukund and Ashutosh --------------
  One point that I think requires further attention is the 
  motivation for using connectedness and the explanation of 
  this property, which is at the core of the proposed approach. 
  I did not find the additional explanations provided in the 
  response and the revised manuscript sufficient. Simply stating 
  that "The graph k-connectedness furnishes precisely" a test to 
  determine if information is missing from the model and that 
  "If the data […] does not have a certain degree of connectivity, 
  this implies that some biological data has been missed" does not 
  justify connectedness as a fundamental and required biological 
  property that all valid models should respect. The intuition of 
  connectedness as a robustness property provided elsewhere in the 
  manuscript helps but it is still not clear what evidence supports 
  the fact that VTSs are indeed robust. In addition, the problem as 
  formulated does not seem to seek the most robust networks as 
  explained in the following.

  Pt #2: 
-------- Handle by Ankit --------------
  I also found the formulation of the main problems with respect 
  to connectedness somewhat confusing. For example, in Sec. 5.1.1 
  and Sec. 5.1.2 the problems are formulated as a search for VTS G 
  such that G is not k-connected. Yet, Sec. 5.1 specifies that 
  "In case the formula is satisfiable the procedure terminates and 
   we report the value of k", which seems contradictory. Finally, 
   it is not clear why the goal is to find the minimum graph 
   connectivity, given that larger connectivity corresponds to a 
   more robust network. I was expecting an approach involving 
   incrementing k to find the smallest value that makes the formula 
   unsatisfiable, thus identifying the maximum graph connectedness 
   possible for a given VTS with all other constraints being 
   satisfied. However, to the best of my understanding, this is not 
   what the paper is currently proposing, or else further  
   clarifications are needed.

  Pt #3: 
-------- Handle by Ashutosh --------------   
  Another point that should be revised further is around 
  clarifying the contributions of this paper. The response 
  document summarizes nicely that, together with additional 
  QBF encoding, "this paper brings together all the results 
  with extended experiments and more detailed expositions for 
  the benefit of both biological and computation community." 
  However, I did not find a similar concise statement of the 
  contributions in the text. In addition, some of the stated 
  advances over previous approaches seem incremental and minor. 
  For example, for the previous CBMC-based method it is stated 
  that "...the scalability of the method was insufficient. 
  The tool was able to handle the system with just eight 
  compartments". Yet, we learn that "A typical eukaryotic 
  cell contains 9 organelles" and even one of the methods 
  presented in this paper fails for some of the experimental 
  evaluations with 7 or more compartments. The contributions 
  of this work, perhaps in the integration and evaluation of
  several methods reported previously, should be stated clearly 
  and accurately in the main text.

  Pt #4: 
-------- Handle by Ankit and Ashutosh--------------  
  A final minor point is about the use of "Synthesis" as 
  an encoding in Fig 4 and the relevant explanations. 
  Since the other problems list verification techniques 
  and solvers (e.g. BMC, SMT, QBF) and no novel synthesis 
  algorithms were developed for this problem, it would be 
  more appropriate to specify QBF as the encoding used for 
  the "VTS synthesis" problem.

% Reviewer 4:

  Pt #1:
-------- Handle by Somya--------------  
  Point 6 on page 3 is the same as point 4.

  Pt #2:
-------- Handle by Somya--------------  
  I would argue still that the biological section has 
  unnecessary detail and could be simplified further.

  Pt #3:
-------- Handle by Somya--------------  
  That the steady-state condition corresponds to the 
  biological meaning of homeostasis is repeated. This 
  only needs to be mentioned once.

  Pt #4:
-------- Handle by Ankit--------------  
   There is overlap in the 3rd and 6th paragraphs of 
   the 'Related Work' section, which refer to the use 
   of SAT/SMT in GRNs.

Minor points: 
-------- Handle by Lakhsman--------------   
  Small typos / grammatical errors. There are a number 
  of these throughout the text, some of which are listed 
  below (this is not exhaustive, so I recommend carefully 
  reading the manuscript to ensure clarity):

  Page 2, lines 11-12: Understanding how membrane traffic 
  functions *is*, therefore,…

  Page 2, line 13: Cell biologists have made… (not 'The')

   Page 3, line 14: "…parts of the traffic system that 
   *are* unchanging…"

   Page 4, line 6: "We also worked on the synthesis of the 
   unknown pieces *that* may be assisted…" Just after this: 
   "In the work, we developed *an* encoding for the 
    synthesis problem."

   Figure 1 legend, line 44: "typical" not "typic"

   Page 7, line 11: "We have tried to capture important 
   *aspects* of *the* Rothman-Schekman-Sudhof (RSS) model 
   of *the* vesicle…" Also "components" not "component"

   Example 1, line 40: "labels are a set of molecules"

   Example 2, line 36: "Fig. 3b presents its complete output VTS."

   Page 14, line 16: "We will also seek *to answer* two 
   kinds of questions, *given* the property."

   Page 15, line 14: "to ensure the k to be the least one" 
   -> "to ensure that k is minimized"

   Page 22: "The specification for *the* universal condition 
   *described in* Section 5"

### 2019-09-09 papers/journal/bio.tex

@@
 		intermediate structures, and by inhibiting premature SNARE complex resolution. Sec17/18 aid in
-		SNARE complex resolution. (C) A schematic of the typic eukaryotic cell's VTS. Large circles
+		SNARE complex resolution. (C) A schematic of the typical eukaryotic cell's VTS. Large circles
 		represent compartments, and edges represent vesicle routes. Identities of compartments are written
@@
 %
-On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
+On the timescales of minutes, we have tried to capture important aspects of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
 %
-The following are the basic component and assumptions of our model. 
+The following are the basic components and assumptions of our model. 
 \begin{enumerate}
@@
 %
-In the VTS, labels are a set of molecule, where we show active molecules in red color.
+In the VTS, labels are a set of molecules, where we show active molecules in red color.
 %
@@
 	In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments.
-Fig.~\ref{fig:synth-vts2} present it's complete output VTS.
+Fig.~\ref{fig:synth-vts2} presents its complete output VTS.
 Every molecule present on the node is active.

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Updated draft with Somya's bio updates

@@
 % Reviewer 1:
-    No Comments!
+ > My comments and concerns have been addressed in detail. Thank you.
 
@@
 
-  Pt #1:
--------- Handle by Somya--------------  
-  Point 6 on page 3 is the same as point 4.
+  > Point 6 on page 3 is the same as point 4.
 
-  Pt #2:
--------- Handle by Somya--------------  
-  I would argue still that the biological section has 
+  Authors response: We thank the reviewer for pointing 
+  this out. The two points were indeed duplicates. We 
+  have now removed point 6.
+
+  > I would argue still that the biological section has 
     unnecessary detail and could be simplified further.
 
-  Pt #3:
--------- Handle by Somya--------------  
-  That the steady-state condition corresponds to the 
+  Authors response: We acknowledge that in the paper, 
+  we only deal explicitly with SNARE proteins. Although 
+  it is not required for an understanding of the work, 
+  we feel a glimpse of the kinds of processes involved 
+  in vesicle traffic, and its molecular machinery might 
+  help the reader appreciate why we have built our model 
+  in this particular way.
+
+  > That the steady-state condition corresponds to the 
     biological meaning of homeostasis is repeated. This 
     only needs to be mentioned once.
+
+  Authors response: We now state the equivalence of our 
+  steady state condition and homeostasis of compartments
+  only in section 2.3.2.
 

### 2019-09-09 papers/journal/bio.tex
Updated draft with Somya's bio updates

@@
 %
-Next, cytosolic coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins \cite{faini2013vesicle}. 
+Membrane deformation is caused by coat proteins which are recruited by adaptor proteins \cite{faini2013vesicle}. 
 %
-Coat proteins cause membrane deformation. 
+Although here we mention only these two molecule types, many other molecules play a role in regulation and orchestration of these processes.
+%Next, cytosolic coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins \cite{faini2013vesicle}. 
+%
+%Coat proteins cause membrane deformation. 
 %
@@
 %
-In this paper, we refer to the steady state of the cell (referred to as homeostasis in biological literature) as the stability condition over the annotated graph.
+In this paper, we refer to the steady state of the cell \cite{mani2016stacking} as the stability condition over the annotated graph.
 
@@
 This is the steady state condition.
-In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
+	% In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
 \end{enumerate}

### 2019-09-09 papers/journal/intro.tex
Updated draft with Somya's bio updates

@@
 Cell biologists have made some progress by assembling a
-“parts list” of molecules that drive vesicle
+``parts list” of molecules that drive vesicle
 traffic~\cite{dacks2007evolution}.
@@
 The essential processes involve the creation of vesicles loaded with
-cargo from source organelles, known as “budding”, and the depositing
-of those vesicles and cargo into target organelles, known as “fusion”
+cargo from source organelles, known as ``budding”, and the depositing
+of those vesicles and cargo into target organelles, known as ``fusion”
 \cite{munro2004organelle}.
@@
 	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
-	\item The behavior of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
+	 \item Interpreting experimental results can be difficult, since the behavior of traffic molecules in vitro is different from their behavior inside cells \cite{furukawa2014multiple}.
 	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
-        \item Lastly, interpreting experimental results can be difficult, since the behavior of traffic molecules in vitro is different from their behavior inside cells.
+
 \end{enumerate}

### 2019-09-09 papers/journal/bio.tex
Updated draft with Somya's bio updates-02

@@
 %
-Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment \cite{muller2018molecular}.
+%Rabs are master regulators; in their active form, 
+Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment \cite{muller2018molecular}. 
 %
@@
 
-The final step in vesicle transport is the fusion of the vesicle with the target compartment is brought about by SNARE proteins. 
+%The final step in vesicle transport is the fusion of the vesicle with the target compartment is brought about by SNARE proteins. 
+%
+The final step in vesicle transport is the fusion of the vesicle with the target compartment. 
+%
+It is brought about by SNARE proteins.
 %

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
related work

@@
 
-  Pt #4:
--------- Handle by Ankit--------------  
-   There is overlap in the 3rd and 6th paragraphs of 
+  > There is overlap in the 3rd and 6th paragraphs of 
     the 'Related Work' section, which refer to the use 
     of SAT/SMT in GRNs.
+  Authors response: The use of SAT/SMT in GRN is presented
+  in two different context (non-overlapping references). 
+  The third paragrah points to general use of SAT/SMT 
+  solvers in GRN, whereas 6th paragraph refers to a specific
+  use (synthesis). We have updated the text to improve this
+  distinction.
 

### 2019-09-09 papers/journal/related.tex
related work

@@
 
-There has been some work in applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}.
-A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
+There has been some work in applying synthesis technique in biology. %especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. 
+A recent work by \cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
+%
+In \cite{shavit2016automated} synthesis of switching GRN (with changing topology) is performed.
+%
+The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques whereas \cite{shavit2016automated} uses SMT to perform synthesis. 
+%
 Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
-The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis.
-The paper~\cite{cardelli2017syntax} in addition to using SMT over ODE, uses a template-guided approach.
-In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem.
+%
+%
+The work
+%The paper \cite{cardelli2017syntax} in addition to using SMT over  ODE, 
+use a template-guided approach in addition to using SMT over ODE. In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. 
+%
 To our best knowledge, this is the first application of synthesis in VTS.

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
related work

@@
 
-  Pt #4: 
--------- Handle by Ankit and Ashutosh--------------  
-  A final minor point is about the use of "Synthesis" as 
+  > A final minor point is about the use of "Synthesis" as 
     an encoding in Fig 4 and the relevant explanations. 
@@
     the "VTS synthesis" problem.
+
+  Authors response: We have now incorporated this information 
+  in Fig 4.
 
@@
     of SAT/SMT in GRNs.
+
   Authors response: The use of SAT/SMT in GRN is presented

### 2019-09-09 papers/journal/problem.tex
related work

@@
 			[\textbf{3.VTS Synthesis}, for tree={fill=fv,child}, 
-			[Synthesis, for tree={fill=ai, child}]
+			[Synthesis (QBF), for tree={fill=ai, child}]
 			]

### 2019-09-09 papers/journal/related.tex
related work

@@
 
-There has been some work in applying synthesis technique in biology. %especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. 
-A recent work by \cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
+There has been some work in applying synthesis technique in biology. 
+%
+Recent work by \cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
 %
@@
 %
-The work
-%The paper \cite{cardelli2017syntax} in addition to using SMT over  ODE, 
-use a template-guided approach in addition to using SMT over ODE. In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. 
+The work uses a template-guided approach in addition to using SMT over ODE. In our case, queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. 
 %

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Lakhsman's Typo fixes adapted

@@
   Pt #1:
--------- Handle by Mukund and Ashutosh --------------
+-------- Handle by Mukund --------------
   One point that I think requires further attention is the 
@@
 Minor points:
--------- Handle by Lakhsman--------------   
-  Small typos / grammatical errors. There are a number 
+
+  > Small typos / grammatical errors. There are a number 
     of these throughout the text, some of which are listed 
@@
 
-  Page 2, lines 11-12: Understanding how membrane traffic 
+  > Page 2, lines 11-12: Understanding how membrane traffic 
     functions *is*, therefore,…
+  Authors response: Correction incorporated.
 
-  Page 2, line 13: Cell biologists have made… (not 'The')
+  > Page 2, line 13: Cell biologists have made… (not 'The')
+  Authors response: Correction incorporated.
 
-   Page 3, line 14: "…parts of the traffic system that 
+  > Page 3, line 14: "…parts of the traffic system that 
     *are* unchanging…"
+  Authors response: Correction incorporated.
 
-   Page 4, line 6: "We also worked on the synthesis of the 
+  > Page 4, line 6: "We also worked on the synthesis of the 
     unknown pieces *that* may be assisted…" Just after this: 
@@
     synthesis problem."
+  Authors response: Both corrections are incorporated.
 
-   Figure 1 legend, line 44: "typical" not "typic"
+  > Figure 1 legend, line 44: "typical" not "typic"
+  Authors response: Corrections incorporated 
+  (typic was in caption of Fig. 1).
 
-   Page 7, line 11: "We have tried to capture important 
+  > Page 7, line 11: "We have tried to capture important 
     *aspects* of *the* Rothman-Schekman-Sudhof (RSS) model 
     of *the* vesicle…" Also "components" not "component" 
+  Authors response: Both corrections are incorporated.
 
-   Example 1, line 40: "labels are a set of molecules"
+  > Example 1, line 40: "labels are a set of molecules"
+  Authors response: Correction incorporated.
 
-   Example 2, line 36: "Fig. 3b presents its complete output VTS."
+  > Example 2, line 36: "Fig. 3b presents its complete output VTS."
+  Authors response: Correction incorporated.
 
-   Page 14, line 16: "We will also seek *to answer* two 
+  > Page 14, line 16: "We will also seek *to answer* two 
     kinds of questions, *given* the property."
+  Authors response: Both corrections are incorporated.
 
-   Page 15, line 14: "to ensure the k to be the least one" 
+  > Page 15, line 14: "to ensure the k to be the least one" 
     -> "to ensure that k is minimized"
+  Authors response: Correction incorporated.
 
-   Page 22: "The specification for *the* universal condition 
+  > Page 22: "The specification for *the* universal condition 
    *described in* Section 5" 
+  Authors response: Both corrections are incorporated.

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Added additional points

@@
+We would like to thank the reviewers for their very detailed and
+helpful comments. In the following, we ellaborate on how we addressed
+the feed in the revised version of our paper.
+
 % Reviewer 1:
@@
     reading the manuscript to ensure clarity):
+  Authors response: We thank the reviewer for pointing these 
+  out. We have corrected the listed errors and performed 
+  multiple careful readings fixing other errors that we found.
 

### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Added additional points

@@
 
-  Pt #2: 
--------- Handle by Ankit --------------
-  I also found the formulation of the main problems with respect 
+  > I also found the formulation of the main problems with respect 
     to connectedness somewhat confusing. For example, in Sec. 5.1.1 
@@
     clarifications are needed.
+
+  Authors response: Sec. 5 gives a high-level explanation of 
+  the problems and present a formal search statement 
+  (implementation based). We have now rewritten the parts of 
+  the text to address the clarity and the distinction between 
+  high-level overview and the implementation. 
+  We have also removed the specific search problems (as suggested 
+  by Reviewer #3 in the first revision) for clarity and accessibility.
 

### 2019-09-09 papers/journal/problem.tex
Added additional points

@@
 %
-Here, we present both the $\fbmc$ and $\fsmt$ search problem for the existential condition.
-
-\subsubsection{$\fbmc$ search problem.}
-For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
-we are searching for well-structured, stable, and well-fused VTS
-$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected, within $w$ depth of unwinding.
-
-\subsubsection{$\fsmt$ search problem.}
-For a given $k$, size $\nu$, and molecule number $\mu$,
-we are searching for well-structured, stable, and well-fused VTS
-$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
-$|\nodes| = \nu$, $|\mols| = \mu$, and
-$G$ is not $k$-connected.
+%Here, we present both the $\fbmc$ and $\fsmt$ search problem for the existential condition.
+%
+%\subsubsection{$\fbmc$ search problem.}
+%For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
+%we are searching for well-structured, stable, and well-fused VTS
+%$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
+%$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected, within $w$ depth of unwinding.    
+%
+%\subsubsection{$\fsmt$ search problem.}
+%For a given $k$, size $\nu$, and molecule number $\mu$,
+%we are searching for well-structured, stable, and well-fused VTS
+%$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
+%$|\nodes| = \nu$, $|\mols| = \mu$, and
+%$G$ is not $k$-connected.
 
@@
 
-%\ankit{This is a dummy template. need a rewrite.} 
-\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
+%%\ankit{This is a dummy template. need a rewrite.} 
+%\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
 

### 2019-09-16 papers/journal/problem.tex
Added the connectivity fix

@@
 %
-We categorize the search problem (Fig.~\ref{fig:vts-search}) into three different categories, search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
+We categorize the search problem into three different categories (Fig.~\ref{fig:vts-search}), search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
 %
@@
 %
-To find a k-connected graph we specify our property as a query for the existence
+To find a $k$-connected graph we specify our property as a query for the existence
 of a model for a conjunction of the formula representing stability, fusion and specific
@@
 %
+
+The $k$-connectedness property is computationally challenging as it requires reasoning about all possible $k - 1$ edge removals. 
+%
+So instead of checking for the graph to be $k$-connected, the encoding and the implementation checks whether the graph is not $k+1$-connected.
+%
+Note that this check is sufficient as we are starting from smallest $k$ ($k = 1$) and subsequently incrementing it by one.     
 % Used E as edge and L_e L_n as label for node and the edge,
@@
 %
-This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
+This condition can be specified as: for every $k$-connected graph, there exists a satisfiable assignment following the rules of the system. 
 %

### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Added the connectivity fix
Update rebuttal

--- 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
@@
 
-  Pt #1:
+  Pt #1a:
 -------- Handle by Mukund --------------
@@
 
-  Pt #2: 
--------- Handle by Ankit --------------
-  I also found the formulation of the main problems with respect 
-  to connectedness somewhat confusing. For example, in Sec. 5.1.1 
-  and Sec. 5.1.2 the problems are formulated as a search for VTS G 
-  such that G is not k-connected. Yet, Sec. 5.1 specifies that 
-  "In case the formula is satisfiable the procedure terminates and 
-   we report the value of k", which seems contradictory. Finally, 
-   it is not clear why the goal is to find the minimum graph 
+  Pt #1b:
+-------- Handle by Mukund [Subpoint added]--------------
+    Finally, it is not clear why the goal is to find the minimum graph 
     connectivity, given that larger connectivity corresponds to a 
@@
     clarifications are needed.
+
+  > I also found the formulation of the main problems with respect 
+    to connectedness somewhat confusing. For example, in Sec. 5.1.1 
+    and Sec. 5.1.2 the problems are formulated as a search for VTS G 
+    such that G is not k-connected. Yet, Sec. 5.1 specifies that 
+    "In case the formula is satisfiable the procedure terminates and 
+    we report the value of k", which seems contradictory.
+
+  Authors response: In Sec. 5 we try to achieve two aims: give a 
+  high-level explanation of the problem, followed by a formal search 
+  statement (from a prespective of an efficient implementation). 
+  This difference was only hinted but not explicitely stated. We have 
+  now rewritten the parts of the text to address the distinction 
+  between high-level overview and the implementation. 
+  We have also removed the specific search problems (as suggested by 
+  Reviewer #3 in the first revision) for further apparent accessibility 
+  of the subject matter.
 
@@
   out. We have corrected the listed errors and performed 
-  multiple careful readings fixing other errors that we found.
+  careful readings fixing other errors that we found.
 

### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Update rebuttal

@@
   Pt #1a:
--------- Handle by Mukund --------------
-  One point that I think requires further attention is the 
+-------- Mukund --------------
+  > One point that I think requires further attention is the 
   motivation for using connectedness and the explanation of 
@@
 
+  Authors response: ...
+
   Pt #1b:
--------- Handle by Mukund [Subpoint added]--------------
-    Finally, it is not clear why the goal is to find the minimum graph 
+-------- Mukund [Subpoint added]--------------
+  > Finally, it is not clear why the goal is to find the minimum graph 
     connectivity, given that larger connectivity corresponds to a 
@@
     clarifications are needed.
+
+  Authors response: ...
 

### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Ashutosh rebuttal added

@@
 
-  Pt #3: 
--------- Handle by Ashutosh --------------   
-  Another point that should be revised further is around 
+  > Another point that should be revised further is around 
     clarifying the contributions of this paper. The response 
@@
     and accurately in the main text.
+
+  Authors response: We clarified the concerns of the reviewers 
+  and clearly stated in the Sec 1. Introduction that the CBMC 
+  method does not scale and the direct encoding does. 
+  We have also stated that the key purpose of this paper is 
+  one unified exposition of our work.
 

### 2019-09-16 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Univ cond update

@@
 % Reviewer 1:
- > My comments and concerns have been addressed in detail. Thank you.
+  > My comments and concerns have been addressed in detail. 
+    Thank you.
+  Authors response: Thank you for your valuable comments.
 
@@
 
-  Authors response: In Sec. 5 we try to achieve two aims: give a 
-  high-level explanation of the problem, followed by a formal search 
-  statement (from a prespective of an efficient implementation). 
+  Authors response: In Sec. 5 we try to give a high-level 
+  explanation of the procedure, followed by a formal search statement 
+  from the prespective of an efficient implementation. 
   This difference was only hinted but not explicitely stated. We have 

### 2019-09-16 papers/journal/problem.tex
Univ cond update

@@
 %
+
+For the implementation purpose, to conclude that a given $k$-connectedness is not a universal condition it is suffice to search for a $k$-connected graph that has no satisfying assignment of all the rules of the system (checking the negation of the condition is unsatisfiable).
+
 The formula for the problem has quantifier alternation. 
@@
 %
+%
 We need a QBF solver for such queries. 
+%
+We refer the corresponding search problem as $\fqbf$ search problem.
 %

### 2019-09-16 papers/journal/problem.tex
inor update

--- 2019-09-16 papers/journal/problem.tex
@@
 
-The $k$-connectedness property is computationally challenging as it requires reasoning about all possible $k - 1$ edge removals. 
+The specification of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
 %
@@
 %
+
+%For the implementation purpose, to conclude that a given $k$-connectedness is not a universal condition it is suffice to search for a $k$-connected graph that has no satisfying assignment of all the rules of the system (checking the negation of the condition is unsatisfiable).
+In the implementation, to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
+%
+
 The formula for the problem has quantifier alternation. 

### 2019-09-16 papers/journal/problem.tex
Connectivity is handled

--- 2019-09-16 papers/journal/problem.tex
@@
 
-The $k$-connectedness property is computationally challenging as it requires reasoning about all possible $k - 1$ edge removals. 
+The specification of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
 %
-So instead of checking for the graph to be $k$-connected, the encoding and the implementation checks whether the graph is not $k+1$-connected.
+So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected.
 %
@@
 %
+
+%In the implementation, to conclude that a given $k$-connectedness is not a universal condition it is suffice to search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
+%In the implementation, to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
+%
+In the implementation instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable.
+That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system.
+
 The formula for the problem has quantifier alternation. 

### 2019-09-17 papers/journal/intro.tex
sad
Updates from Overleaf

@@
 The essential processes involve the creation of vesicles loaded with
-cargo from source organelles, known as ``budding”, and the depositing
+cargo from source organelles, known as ``budding”, and the deposition
 of those vesicles and cargo into target organelles, known as ``fusion”
@@
 %
-Proteins that are called coats and the adaptors that select the cargo regulate budding.
+Proteins called coats and adaptors select cargo and regulate budding.
 %
-The proteins that are known as SNAREs and tethers that ensure that vesicles
-fuse to the correct target regulate fusion
+Proteins known as SNAREs and tethers ensure that vesicles
+fuse to correct target compartments and regulate fusion
 \cite{mani2016stacking}.
@@
 
-The SNARE proteins and the constraints that SNARE-to-SNARE regulations
+SNARE proteins and the constraints that SNARE-to-SNARE regulations
 impose on the feasible behaviors of VTSs are the focus of
@@
 %
-There is a corresponding set of label molecules on the target compartments.
+There is a corresponding set of labels on the target compartment.
 %
@@
 The question is: does this physical picture place any constraints on
-the global topology of the traffic graph? We have previously shown that one informative constraint is graph connectivity \cite{shukla2017discovering}.
+the global topology of the vesicle traffic graph? We have previously shown that one informative constraint is graph connectivity \cite{shukla2017discovering}.
 %
@@
 %
-How stringent SNARE regulation is can determine whether the graph
+The stringency of SNARE regulation can determine whether the graph
 topologies of a particular level of connectivity are biologically
@@
 If relatively simple rules regulate the SNAREs, then only
-highly connected traffic networks can be generated using them.
+highly connected traffic networks can be generated.
 %
@@
 %
-The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and
+The current picture of VTS is far from complete; for many cellular proteins, we do not know how they reach their resident compartments within the cell, and
 researchers are discovering new vesicle routes every
@@
 %
-Completing the VTS is a difficult task for many important reasons: 
+Completing the VTS is a difficult task for many reasons: 
 \begin{enumerate}
@@
 %
-At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network.
+At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the vesicle traffic network.
 %
-The network knowledge would also allow us to decipher features such as parts of the traffic system that are unchanging and therefore likely to be its core, and more plastic parts~\cite{barlow2017seeing}.
+knowing the vesicle traffic network would also allow us to decipher features such as parts of the traffic system that are unchanging and therefore likely to be its core, and the more plastic parts~\cite{barlow2017seeing}.
 
@@
 %
-In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
+In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should have in spite of basic constraints. 
 %
@@
 
-A previous work used a sampling approach. 
+In previous work, a sampling approach was used. 
 %
@@
 %
-Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient. The tool was able to handle the system with just eight compartments.
+Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient.
 %
-Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
+The tool was able to handle the system with just eight compartments
+and failed to scale.
+% 
+Another interesting question about a property involving quantifiers (termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it the universal condition) was partly handled
 using sampling and left open.
 %
-In~\cite{smtVTS}, we developed more efficient direct encoding to SMT solvers. 
+We have included this method in the current paper for completeness of the
+exposition.
+
+%
+In~\cite{smtVTS}, we developed a more efficient direct encoding to SMT solvers. 
 %
@@
 %
-In the work, we developed an encoding for the synthesis problem.
+In this work, we have developed an encoding for the synthesis problem.
 %
 This paper brings together the above encodings with extended experiments and more detailed
-expositions for the benefit of both biological and computation community.
-We additionally explored QBF based encoding of some of the problems.
+expositions for the benefit of both the biological and the computation communities.
+We additionally explored QBF based encodings of some of the problems.
 
@@
 
-\par We have implemented the encodings in a flexible tool, which can handle both connectivity questions and a wide range of synthesis queries. 
+\par We have implemented these encodings in a flexible tool, which can handle both connectivity questions and a wide range of synthesis queries. 
 %
@@
 %
-In Section~\ref{sec:bio}, we present the biological background and details to understand the VTS. 
+In Section~\ref{sec:bio}, we present biological background and details to understand the VTS. 
 %

### 2019-09-17 papers/journal/bio.tex
Added the connectivity fix

@@
 %
-The final step in vesicle transport is the fusion of the vesicle with the target compartment. 
+The final step in vesicle transport is fusion of the vesicle with the target compartment. 
 %
@@
 %
-Whereas, SM proteins have following multiple modes of SNARE regulation: 
+Whereas, SM proteins have multiple modes of SNARE regulation: 
 \begin{itemize}
@@
 \subsubsection{Major paths in the VTS}
-Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
+Molecules traverse the cell in a series of vesicles. There are two major routes of vesicle transport in all eukaryotic cells.
 %
@@
 \item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
-\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
+\item Each compartment is in steady state, where gain and loss of molecules is balanced~\cite{braell1984glycoprotein}.
 \item Molecules are neither created nor destroyed~\cite{he2009differential}.
@@
 %
-The set of molecules present in the compartment, for example, SNARE proteins associated with it, are represented as a label to the corresponding nodes.
+The set of molecules present in compartments, for example, SNARE proteins associated with it, are represented as labels to the corresponding nodes.
 %
@@
 %
-Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
+Indeed, it is well accepted that on the scale of minutes and hours the molecular composition of compartments remains the same. 
 %
@@
 %
-Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
+Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on the compartment or vesicle. 
 %
-We have also tested \cite{shukla2017discovering} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}.
+We have also tested \cite{shukla2017discovering} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is \textit{pairing inhibition}.
 %
@@
 %
-In this sense, it indeed does not matter whether the molecule interacting with the SNARE is active or not. 
+In this sense, it does not matter whether the molecule interacting with the SNARE is active or not. 
 %
@@
 
-Can we find a simple test to see whether any information is missing, given the experimental data? It has shown that graph k-connectedness furnishes precisely such a test \cite{shukla2017discovering}.
+Can we find a simple test to see whether any information is missing, given the experimental data?
+It has been shown that graph $k$-connectedness furnishes precisely such a test \cite{shukla2017discovering}.
 %
@@
 
-%The result about k-connectedness being a useful test of missing information \cite{shukla2017discovering} was obtained using SAT solvers for graphs up to a certain size, and a certain number of molecules.
+%The result about $k$-connectedness being a useful test of missing information \cite{shukla2017discovering} was obtained using SAT solvers for graphs up to a certain size, and a certain number of molecules.
 This was due to limitations in how we encoded the problem.
@@
 Therefore the underlying undirected graph is 2-connected.
-%From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity.
+%From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain $k$-connectivity.
 When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected.
@@
 %
-In the VTS, labels are a set of molecules, where we show active molecules in red color.
+In the VTS, labels are sets of molecules, where we show active molecules in red color.
 %
@@
 %
-Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
+Note that molecules $X$ and $Y$ do not take part in fusion but determine the activity of molecules at the corresponding nodes.
 %
@@
 %
-Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
+Rows in the matrix correspond to edge-labels, and columns correspond to node-labels.
 %
@@
 Every molecule present on the node is active.
-The activity of the molecules on an edge is determined by the presence of the other molecules.
-Each label represent particular type of molecule.
-The synthesis is performed against the stability and 3-connectivity.
-Synthesized edge is in red color and synthesized molecules are presented in blue.
+The activity of molecules on an edge is determined by the presence of other molecules on the edge.
+Each label represents a particular type of molecule.
+The synthesis is performed against the stability and 3-connectivity conditions.
+The synthesized edge is in red color and synthesized molecules are presented in blue.
 The synthesis adds one edge and 7 molecules to complete the partial VTS.
@@
 This synthetic example is a sub-graph of the VTS shown in the \ref{fig:mukund-vts}.
-Please refer to \ref{sec:ex-vts} for complete detail.
+Please refer to \ref{sec:ex-vts} for details.
 	%The presented graph is a subgraph of a VTS discussed in details in appendix.
@@
 %
-By definition, the activity of any VTS molecules can be controlled by all other molecules.
+By definition, the activity of any VTS molecule can be controlled by all other VTS molecules.
 %

### 2019-09-22 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Mukund's push

@@
-We would like to thank the reviewers for their very detailed and
-helpful comments. In the following, we ellaborate on how we addressed
-the feed in the revised version of our paper.
+We would like to thank the reviewers for their very detailed and helpful comments. In the following, we elaborate on how we addressed the feedback in the revised version of our paper.
 
@@
 
-  Pt #1a:
--------- Mukund --------------
+  Authors response: Thank you for this feedback.
+As we are trying to reach an interdisciplinary audience we are forced to balance to some extent the biological detail with the technical discussions.
+We appreciate the feedback from the reviewers, which has helped us improve readability.
+
   > One point that I think requires further attention is the 
@@
   that "The graph k-connectedness furnishes precisely" a test to 
-  determine if information is missing from the model and that 
-  "If the data […] does not have a certain degree of connectivity, 
-  this implies that some biological data has been missed" does not 
-  justify connectedness as a fundamental and required biological 
-  property that all valid models should respect. The intuition of 
-  connectedness as a robustness property provided elsewhere in the 
-  manuscript helps but it is still not clear what evidence supports 
-  the fact that VTSs are indeed robust. In addition, the problem as 
-  formulated does not seem to seek the most robust networks as 
-  explained in the following.
+  determine if information is missing from the model.
 
-  Authors response: ...
+Authors response:
 
-  Pt #1b:
--------- Mukund [Subpoint added]--------------
-  > Finally, it is not clear why the goal is to find the minimum graph 
-    connectivity, given that larger connectivity corresponds to a 
-    more robust network. I was expecting an approach involving 
-    incrementing k to find the smallest value that makes the formula 
-    unsatisfiable, thus identifying the maximum graph connectedness 
-    possible for a given VTS with all other constraints being 
-    satisfied. However, to the best of my understanding, this is not 
-    what the paper is currently proposing, or else further  
-    clarifications are needed.
+We have removed the word ``precisely'', which the Reviewer has correctly pointed out is too strong.
+We have replaced this by the sentence ``It has been shown that graph $k$-connectedness furnishes one such test''.
 
-  Authors response: ...
+>  "If the data […] does not have a certain degree of connectivity,  this implies that some biological data has been missed" does not  justify connectedness as a fundamental and required biological  property that all valid models should respect.
+The intuition of  connectedness as a robustness property provided elsewhere in the  manuscript helps but it is still not clear what evidence supports  the fact that VTSs are indeed robust.
+In addition, the problem as  formulated does not seem to seek the most robust networks as  explained in the following.
 
-  > I also found the formulation of the main problems with respect 
-    to connectedness somewhat confusing. For example, in Sec. 5.1.1 
-    and Sec. 5.1.2 the problems are formulated as a search for VTS G 
-    such that G is not k-connected. Yet, Sec. 5.1 specifies that 
-    "In case the formula is satisfiable the procedure terminates and 
-    we report the value of k", which seems contradictory.
+Author response: We have added several paragraphs to motivate our focus on k-edge-connectedness:
+
+``The informativeness and usefulness of using $k$-connectedness is motivated by the following example.
+...
+In summary, the higher the edge-connectedness of a measured VTS graph, the more of the underlying biological constraints can be satisfied by appropriately placing SNAREs on each node and edge.''
+
+  > Finally, it is not clear why the goal is to find the minimum graph connectivity, given that larger connectivity corresponds to a more robust network.
+I was expecting an approach involving incrementing k to find the smallest value that makes the formula unsatisfiable, thus identifying the maximum graph connectedness possible for a given VTS with all other constraints being satisfied.
+However, to the best of my understanding, this is not what the paper is currently proposing, or else further clarifications are needed.
+
+Author response: We apologise for the confusing structure of our text. To clarify this point we have added a new paragraph:
+
+``It is perhaps counter-intuitive that, beyond a certain degree of edge-connectedness, any VTS graph can be implemented as a biological system.
+This is because we have not placed any constraints on the number of distinct SNAREs and other trafficking molecules a cell contains.
+In practice there is an upper bound on the number of molecules a cell can genetically encode.
+This question (``What is the maximum edge-connectedness possible given a certain number of SNAREs?'') is complementary to the question we have asked here (``What is the minimum edge-connectedness possible given any number of SNARES operating under certain physical constraints?'').''
+
+  > I also found the formulation of the main problems with respect to connectedness somewhat confusing.
+For example, in Sec.
+5.1.1 and Sec.
+5.1.2 the problems are formulated as a search for VTS G such that G is not k-connected.
+Yet, Sec.
+5.1 specifies that "In case the formula is satisfiable the procedure terminates and we report the value of k", which seems contradictory.
 
   Authors response: In Sec. 5 we try to give a high-level 
-  explanation of the procedure, followed by a formal search statement 
-  from the prespective of an efficient implementation. 
-  This difference was only hinted but not explicitely stated. We have 
-  now rewritten the parts of the text to address the distinction 
-  between high-level overview and the implementation. 
-  We have also removed the specific search problems (as suggested by 
-  Reviewer #3 in the first revision) for further apparent accessibility 
-  of the subject matter.
+  explanation of the procedure, followed by a formal search statement from the perspective of an efficient implementation. 
+  This difference was only hinted but not explicitly stated.
+We have  now rewritten the parts of the text to address the distinction between high-level overview and the implementation.
+We have also removed the specific search problems (as suggested by Reviewer #3 in the first revision) for further apparent accessibility of the subject matter.
 

### 2019-09-22 papers/journal/bio.tex
Mukund's push

@@
 We can then ask: is this a complete and consistent description?
-That is, do all the required properties listed above hold, given what the experimentalists have told us?
+That is, do all the required properties listed above hold, given what the experiments have told us?
 It is often the case that biological data is missing.
@@
 
-Can we find a simple test to see whether any information is missing, given the experimental data?
-It has been shown that graph $k$-connectedness furnishes precisely such a test \cite{shukla2017discovering}.
-%
-If the data provided by cell-biologists, suitably represented as a graph, does not have a certain degree of connectivity, this implies that some biological data has been missed.
-(The converse is not true: even if the required connectivity does hold, there might of course be more information missing.)
+Can we find a simple test to see whether any information is missing, given the experimental data? It has been shown that graph $k$-connectedness furnishes one such test \cite{shukla2017discovering}.
+
+The informativeness and usefulness of using $k$-connectedness is motivated by the following example.
+A necessary condition for the VTS graph to be in a steady state is that the graph is strongly connected.
+By Robbins' Theorem, these are precisely the 2-edge-connected graphs.
+However this is not sufficient for the biological problem, due to the additional constraints imposed by SNARE interaction rules.
+For example, if two edges of the graph have distinct target compartments, it must be they have distinct SNARE compositions to appropriately enforce those targets.
+While 2-edge-connectedness is not sufficient to guarantee this, 3-edge-connectedness is.
+This is because when edges of a strongly-connected 3-edge-connected graph are labeled by their cycle membership, no two edges belong to the same set of cycles.
+
+In summary, the higher the edge-connectedness of a measured VTS graph, the more of the underlying biological constraints can be satisfied by appropriately placing SNAREs on each node and edge.
+If the data provided by cell biologists does not have a certain degree of connectedness, this implies that some biological data has been missed.
+Our goal here is to make this connection precise, by framing these constraints as a SAT instance.
+
+It is perhaps counter-intuitive that, beyond a certain degree of edge-connectedness, any VTS graph can be implemented as a biological system.
+This is because we have not placed any constraints on the number of distinct SNAREs and other trafficking molecules a cell contains.
+In practice there is an upper bound on the number of molecules a cell can genetically encode.
+This question (``What is the maximum edge-connectedness possible given a certain number of SNAREs?'') is complementary to the question we have asked here (``What is the minimum edge-connectedness possible given any number of SNARES operating under certain physical constraints?'').
 

### 2019-09-22 papers/journal/intro.tex
Mukund's push

@@
 %
-knowing the vesicle traffic network would also allow us to decipher features such as parts of the traffic system that are unchanging and therefore likely to be its core, and the more plastic parts~\cite{barlow2017seeing}.
+Knowing the vesicle traffic network would also allow us to decipher features such as parts of the traffic system that are unchanging and therefore likely to be its core, and the more plastic parts~\cite{barlow2017seeing}.
 
@@
 %
-The study used a rule-based approach~\cite{mani2016stacking}.
+The study used a rule-based specification~\cite{mani2016stacking}.
 Given an initial condition of the cell and rules for molecular traffic,
-the approach updates the state of each compartment in the cell until the cell reaches a steady-state. 
+that approach updates the state of each compartment in the cell until the cell reaches a steady-state. 
 %
-With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
+With this previous study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
 %
-Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
+Also, this previous study did not consider specific mechanisms of SNARE regulation. 
 %
-It is possible that a different scheme for the dynamics could lead to a different set of solutions.
+It is possible that a different scheme for the SNARE regulation could lead to a different set of solutions.
 

### 2019-09-22 papers/journal/problem.tex
Updated the Spec text

@@
 %
-In the implementation instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable.
-That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system.
 
@@
 
+For the efficient implementation of the specification instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. 
+%
+That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment to all the rules of the system.
+%
+In case no such graph exists for a specific $k$ we reported the corresponding $k$.
 %%\ankit{This is a dummy template. need a rewrite.} 

### 2019-09-22 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Updated the Spec text
Minor updates in k-coonectivity

@@
-We would like to thank the reviewers for their very detailed and helpful comments. In the following, we elaborate on how we addressed the feedback in the revised version of our paper.
+We would like to thank the reviewers for their very detailed 
+and helpful comments. 
+In the following, we elaborate on how we addressed the feedback 
+in the revised version of our paper.
 
 % Reviewer 1:
-  > My comments and concerns have been addressed in detail. 
+  >> My comments and concerns have been addressed in detail. 
     Thank you.
@@
 
-> I believe that most issues highlighted previously have been 
+  >> I believe that most issues highlighted previously have been 
   addressed adequately. In particular, the structure of the 
@@
 
-  Authors response: Thank you for this feedback.
-As we are trying to reach an interdisciplinary audience we are forced to balance to some extent the biological detail with the technical discussions.
-We appreciate the feedback from the reviewers, which has helped us improve readability.
+  Authors response: Thank you for this feedback. As we are trying 
+  to reach an interdisciplinary audience we are forced to balance 
+  to some extent the biological detail with the technical discussions. 
+  We appreciate the feedback from the reviewers, which has helped us 
+  improve readability.
 
-  > One point that I think requires further attention is the 
+  >> One point that I think requires further attention is the 
   motivation for using connectedness and the explanation of 
@@
 
-Authors response:
+  Authors response: We have removed the word "precisely", 
+  which the Reviewer has correctly pointed out is too strong. 
+  We have replaced this by the sentence 
+  "It has been shown that graph $k$-connectedness furnishes one such test".
 
-We have removed the word ``precisely'', which the Reviewer has correctly pointed out is too strong.
-We have replaced this by the sentence ``It has been shown that graph $k$-connectedness furnishes one such test''.
+  >> "If the data […] does not have a certain degree of 
+  connectivity, this implies that some biological data has been 
+  missed" does not  justify connectedness as a fundamental and 
+  required biological  property that all valid models should respect. 
+  The intuition of connectedness as a robustness property provided 
+  elsewhere in the  manuscript helps but it is still not clear what 
+  evidence supports  the fact that VTSs are indeed robust. In addition, 
+  the problem as  formulated does not seem to seek the most robust 
+  networks as  explained in the following.
 
->  "If the data […] does not have a certain degree of connectivity,  this implies that some biological data has been missed" does not  justify connectedness as a fundamental and required biological  property that all valid models should respect.
-The intuition of  connectedness as a robustness property provided elsewhere in the  manuscript helps but it is still not clear what evidence supports  the fact that VTSs are indeed robust.
-In addition, the problem as  formulated does not seem to seek the most robust networks as  explained in the following.
+  Author response: We have added several paragraphs 
+  to motivate our focus on k-edge-connectedness:
 
-Author response: We have added several paragraphs to motivate our focus on k-edge-connectedness:
+  "The informativeness and usefulness of using $k$-connectedness 
+  is motivated by the following example. ... In summary, the higher 
+  the edge-connectedness of a measured VTS graph, the more of the 
+  underlying biological constraints can be satisfied by appropriately 
+  placing SNAREs on each node and edge."
 
-``The informativeness and usefulness of using $k$-connectedness is motivated by the following example.
-...
-In summary, the higher the edge-connectedness of a measured VTS graph, the more of the underlying biological constraints can be satisfied by appropriately placing SNAREs on each node and edge.''
+  >> Finally, it is not clear why the goal is to find the minimum 
+  graph connectivity, given that larger connectivity corresponds 
+  to a more robust network. I was expecting an approach involving 
+  incrementing k to find the smallest value that makes the formula 
+  unsatisfiable, thus identifying the maximum graph connectedness 
+  possible for a given VTS with all other constraints being satisfied. 
+  However, to the best of my understanding, this is not what the paper 
+  is currently proposing, or else further clarifications are needed.
 
-  > Finally, it is not clear why the goal is to find the minimum graph connectivity, given that larger connectivity corresponds to a more robust network.
-I was expecting an approach involving incrementing k to find the smallest value that makes the formula unsatisfiable, thus identifying the maximum graph connectedness possible for a given VTS with all other constraints being satisfied.
-However, to the best of my understanding, this is not what the paper is currently proposing, or else further clarifications are needed.
+  Author response: We apologise for the confusing structure 
+  of our text. To clarify this point we have added a new paragraph:
 
-Author response: We apologise for the confusing structure of our text. To clarify this point we have added a new paragraph:
+  "It is perhaps counter-intuitive that, beyond a certain degree 
+  of edge-connectedness, any VTS graph can be implemented as a 
+  biological system. This is because we have not placed any 
+  constraints on the number of distinct SNAREs and other trafficking 
+  molecules a cell contains. In practice there is an upper bound on the 
+  number of molecules a cell can genetically encode. This question 
+  ("What is the maximum edge-connectedness possible given a 
+  certain number of SNAREs?") is complementary to the question we 
+  have asked here ("What is the minimum edge-connectedness possible 
+  given any number of SNARES operating under certain physical constraints?")."
 
-``It is perhaps counter-intuitive that, beyond a certain degree of edge-connectedness, any VTS graph can be implemented as a biological system.
-This is because we have not placed any constraints on the number of distinct SNAREs and other trafficking molecules a cell contains.
-In practice there is an upper bound on the number of molecules a cell can genetically encode.
-This question (``What is the maximum edge-connectedness possible given a certain number of SNAREs?'') is complementary to the question we have asked here (``What is the minimum edge-connectedness possible given any number of SNARES operating under certain physical constraints?'').''
-
-  > I also found the formulation of the main problems with respect to connectedness somewhat confusing.
-For example, in Sec.
-5.1.1 and Sec.
-5.1.2 the problems are formulated as a search for VTS G such that G is not k-connected.
-Yet, Sec.
-5.1 specifies that "In case the formula is satisfiable the procedure terminates and we report the value of k", which seems contradictory.
+  >> I also found the formulation of the main problems with 
+  respect to connectedness somewhat confusing. For example, 
+  in Sec. 5.1.1 and Sec. 5.1.2 the problems are formulated   
+  as a search for VTS G such that G is not k-connected. 
+  Yet, Sec. 5.1 specifies that "In case the formula is 
+  satisfiable the procedure terminates and we report the 
+  value of k", which seems contradictory.
 
   Authors response: In Sec. 5 we try to give a high-level 
-  explanation of the procedure, followed by a formal search statement from the perspective of an efficient implementation. 
+  specification of the procedure, followed by a formal search 
+  statement from a perspective of an efficient implementation. 
   This difference was only hinted but not explicitly stated. 
-We have  now rewritten the parts of the text to address the distinction between high-level overview and the implementation.
-We have also removed the specific search problems (as suggested by Reviewer #3 in the first revision) for further apparent accessibility of the subject matter.
+  We have now rewritten the parts of the text to address the 
+  distinction between high-level overview and the implementation.
+  We have also removed the specific search problems (as suggested 
+  by Reviewer #3 in the first revision) for further apparent 
+  accessibility of the subject matter. 
+  The use of "k" in the 6.1.6 k-connectivity constraints, 
+  is overloaded. It just specifies how we encode a graph 
+  that is not k-connected.
 
-  > Another point that should be revised further is around 
+  >> Another point that should be revised further is around 
     clarifying the contributions of this paper. The response 
@@
 
-  Authors response: We clarified the concerns of the reviewers 
-  and clearly stated in the Sec 1. Introduction that the CBMC 
-  method does not scale and the direct encoding does. 
-  We have also stated that the key purpose of this paper is 
-  one unified exposition of our work.
+  Authors response: We clarified the concerns of the reviewers and 
+  clearly stated in the Sec 1. Introduction that the CBMC method 
+  does not scale and the direct encoding does. 
+  We have also stated that the key purpose of this paper 
+  is one unified exposition of our work.
 
-  > A final minor point is about the use of "Synthesis" as 
+  >> A final minor point is about the use of "Synthesis" as 
     an encoding in Fig 4 and the relevant explanations. 
@@
 
-  > Point 6 on page 3 is the same as point 4.
+  >> Point 6 on page 3 is the same as point 4.
 
@@
 
-  > I would argue still that the biological section has 
+  >> I would argue still that the biological section has 
     unnecessary detail and could be simplified further.
@@
 
-  > That the steady-state condition corresponds to the 
+  >> That the steady-state condition corresponds to the 
     biological meaning of homeostasis is repeated. This 
@@
 
-  > There is overlap in the 3rd and 6th paragraphs of 
+  >> There is overlap in the 3rd and 6th paragraphs of 
     the 'Related Work' section, which refer to the use 

### 2019-09-22 papers/journal/encoding.tex
Added the connectivity fix
Minor updates in k-coonectivity

@@
 \subsubsection{$k$-connectivity constraints}
-To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
+%To check whether $k$-connected is a necessary condition, 
+We remove (drop) $k-1$ edges from the graph and if it
 disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
@@
 \end{align*}
-We define $\texttt{Connected}(k)$ that says graph is not k-connected.
+We define $\texttt{Connected}(k)$ that says graph is not $k$-connected.
 \begin{align*}

### 2019-09-22 papers/journal/problem.tex
Updated the Spec text
Minor updates in k-coonectivity

@@
 
-The specification of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
+The implementation of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
 %
@@
 %
-In case no such graph exists for a specific $k$ we reported the corresponding $k$.
+%In case no such graph exists for a specific $k$ we report the $k$.
 %%\ankit{This is a dummy template. need a rewrite.} 

### 2019-09-22 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Minor updates in k-coonectivity

@@
   distinction between high-level overview and the implementation.
+
+  "The implementation of the k-connectedness property is 
+  challenging as it requires reasoning about all possible k − 1 
+  edge removals. So instead of checking for the graph to be 
+  k-connected, the encoding (and the implementation) checks 
+  whether the graph is not k + 1-connected..."
+
+  The use of "k" in the 6.1.6 k-connectivity constraints, 
+  is overloaded. This subsection specifies how we encode 
+  a graph that is not k-connected.
+
   We have also removed the specific search problems (as suggested 
@@
   accessibility of the subject matter.
-  The use of "k" in the 6.1.6 k-connectivity constraints, 
-  is overloaded. It just specifies how we encode a graph 
-  that is not k-connected.
 

### 2019-09-23 papers/journal/2019_ACTA_Rebuttal_Rd2.txt
Minor updates in k-coonectivity

@@
   The use of "k" in the 6.1.6 k-connectivity constraints, 
-  is overloaded. This subsection specifies how we encode 
+  is overloaded. This subsection simply specifies how we encode 
   a graph that is not k-connected.
@@
 
-  Authors response: We clarified the concerns of the reviewers and 
-  clearly stated in the Sec 1. Introduction that the CBMC method 
-  does not scale and the direct encoding does. 
-  We have also stated that the key purpose of this paper 
-  is one unified exposition of our work.
+  Authors response: We have stated that the key purpose of this 
+  paper is one unified exposition of our work.
+
+  "This paper brings together the above encodings with extended
+   experiments and more detailed expositions for the benefit of
+   both the biological and the computation communities..."
+
+  We clarified the concerns of the reviewers and clearly 
+  stated in the Sec 1. Introduction that the CBMC 
+  method does not scale and the direct encoding does.
 
@@
 
-  Authors response: We have now incorporated this information 
-  in Fig 4.
+  Authors response: This is indeed the case. We have now 
+  incorporated this information in Fig 4.
 

### 2019-09-24 papers/journal/conclusion.tex
Somya's Typo fixes.

@@
 \noindent 
-We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate into a global, observable properties of the VTS. 
+We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate into global, observable properties of the VTS. 
 %
@@
 %
-We manage to scale the tool up to the size that makes the tool biologically relevant.
+We manage to scale the tool up to the size that makes it biologically relevant.
 %
@@
 %
-Therefore, a simple call to SAT solver may not work efficiently. 
+Therefore, a simple call to SAT solvers may not work efficiently. 
 %
@@
 %
-We demonstrated that our tool based on the encodings
-scale up to the relevant sizes of the VTSs for some synthesis queries.
+We demonstrated that our tool based on encodings
+scales up to the relevant sizes of the VTSs for some synthesis queries.
 %
-Our tool timed out on larger examples.
-%
-We are working to improve the performance of our tool.
+Our tool timed out on larger examples, and we are working to improve its performance.
 %
 %
-With the tool, we made an attempt to present multiple new testable predictions. 
+With the tool, we have made an attempt to present multiple new testable predictions. 
 %
-We will take this tool to the biologists and develop wet experiments that may
-validate some synthesis results from the tool.
+We plan to take this tool to biologists and develop wet experiments that may
+validate some of our synthesis results.
 %
@@
 %
-We also developing methods to prioritize predictions considering addition biological
+We are also developing methods to prioritize predictions considering additional biological
 information and using a refined model.
 %
-For example, in this work, we have only analyzed the VTS as static graphs.
-A major aspect of the biological cell’s VTS that the current model is missing is \textit{compartment maturation}, imbalances in incoming and outgoing molecular flux on vesicles.
+For example, in this work, we have only analyzed VTSs as static graphs.
+A major aspect of the biological cell’s VTS that the current model is missing is \textit{compartment maturation} that arises from imbalances in incoming and outgoing molecular flux on vesicles.
 %
-In the future, we will study the dynamic behaviors of VTSs.
+In the future, we will study dynamic behaviors of VTSs.
 

### 2019-09-24 papers/journal/problem.tex
Updated draft
Somya's Typo fixes.

@@
 %
-We categorize the search problem into three different categories (Fig.~\ref{fig:vts-search}), search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
+%We categorize the search problem into three different categories (Fig.~\ref{fig:vts-search}), search problem for the existential condition, search problem for the universal condition, and performing synthesis on the incomplete VTS.
 %
-We will present two encodings for existential condition and one each for universal condition and synthesis.
+%We will present two encodings for the existential condition and one each for the universal condition and synthesis.
 
@@
 \vspace{0.2cm}
-\noindent We will also seek to answer two kinds of questions given the property.
+\noindent We seek to answer three kinds of questions given the property (Fig.~\ref{fig:vts-search}).
 % %
@@
   if there is a connectedness property that is satisfied by each valid VTS.
+\item{\em synthesis on incomplete VTS}:
+    Given an incomplete VTS, if we can predict missing parts.
 \end{enumerate}
 The goal is to find the minimum graph connectivity properties for each of the condition.
+We will present two encodings for the existential condition and one each for the universal condition and synthesis.
 % In our program, the rules VTS needs to follow 
@@
 To find a $k$-connected graph we specify our property as a query for the existence
-of a model for a conjunction of the formula representing stability, fusion and specific
+of a model for a conjunction of the formula representing stability, fusion and the specific
 graph connectivity constraint. 
@@
 %
-If the formula is not satisfiable we increment the $k$ by $1$ and repeat the same procedure. 
+If the formula is not satisfiable we increment $k$ by $1$ and repeat the same procedure. 
 %
@@
 
-We employ two techniques to examine the existential condition. 
-%
-First, using the BMC and second using SMT solving.
+We employ two techniques to examine the existential condition: first, using BMC and second using SMT solving.
 %
@@
 For some $k>0$,
-we have to ensure that every graph of $k$-connected structure satisfies all
+we have to ensure that every $k$-connected graph satisfies all
 the rules of the system.
 %
-We also aim to find the minimum $k$. 
+We also aim to find the minimum such $k$. 
 % We also have to ensure that the particular k is the least one. 
@@
 
-For the efficient implementation of the specification instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. 
+For an efficient implementation of the specification, instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. 
 %
-That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment to all the rules of the system.
+That is, to conclude that a given $k$-connectedness is not a universal condition, we search for a $k$-connected graph that has no satisfying assignment to all the rules of the system.
 %
@@
 %
-\noindent We also consider another variant of analysis of VTSs.
+\noindent We consider another variant of analysis of VTSs.
 %
-We will assume that we are given a VTS, whose all components
+We will assume that we are given a VTS, all of whose components
 are not specified.
@@
 %For example, 
-be some undiscovered edges or nodes, or insufficient
+be undiscovered edges or nodes, or insufficient
 knowledge about the presence of molecules in some part of the VTS.

### 2019-09-24 papers/journal/related.tex
Somya's Typo fixes.

@@
-\noindent The previous analysis of VTS used simulation and statistical reasoning~\cite{mani2016stacking}. 
+\noindent Previous analysis of VTS used simulation and statistical reasoning~\cite{mani2016stacking}. 
 %
-Such analysis is far from complete and can only make statistical claims about VTS based on a subset of samples. 
+Such analysis is far from complete and can only make statistical claims about the VTS based on a subset of samples. 
 %
@@
 
-The SAT solvers are used to solve a wide range of problems including
+SAT solvers are used to solve a wide range of problems including
 %
@@
 %
-The enormous progress in the performance of SAT and SMT solvers
+Enormous progress in the performance of SAT and SMT solvers
 %Improvement in SAT and SMT solvers
@@
 %
-Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
+Many of these applications involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
 % and hence can be reduced to solving a SAT/SMT question. 
@@
 
-One of the prominent areas of application of SAT and SMT solvers is modeling and understanding the gene regulatory networks (GRN)~\cite{giacobbe2015model,rosenblueth2014inference, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
+One of the prominent areas of application of SAT and SMT solvers is modeling and understanding gene regulatory networks (GRN)~\cite{giacobbe2015model,rosenblueth2014inference, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
 %
-The gene regulatory network question is encoded either directly as a Boolean satisfiability problem or in addition with the combinations of background theories.
+The gene regulatory network question is encoded either directly as a Boolean satisfiability problem or in addition with combinations of background theories.
 %
@@
 %
-The~\cite{rosenblueth2014inference} uses symbolic model checking approach on the qualitative
+~\cite{rosenblueth2014inference} uses a symbolic model checking approach on qualitative
 models of regulatory networks.
 %
-Whereas,~\cite{dunn2014defining}  uses symbolic, SAT-based approach on the Boolean network model. 
+Whereas,~\cite{dunn2014defining} uses a symbolic, SAT-based approach on the Boolean network model. 
 %
-The~\cite{giacobbe2015model, yordanov2016method} presents an SMT based encoding of the problem based on the presented Boolean model.
+~\cite{giacobbe2015model, yordanov2016method} presents an SMT based encoding of the problem based on the presented Boolean model.
 %
 
-We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely VTS. 
+We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking}, namely VTS. 
 %
-We have presented both SAT and SMT based encoding for our Boolean model of the VTS.
+We have presented both SAT and SMT based encodings for our Boolean model of the VTS.
 %
@@
 
-In recent years, there has been a wide range of methods
-developed for similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
+In recent years, a wide range of methods
+have been developed for similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
 %
-They range from filling gaps an implementation of C programs from the pool of template predicates to learn a program from the example
+They range from filling gaps in implementation of C programs from the pool of template predicates, to learning a program from the example
 runs of the program.
@@
 %
-The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques whereas \cite{shavit2016automated} uses SMT to perform synthesis. 
+~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques, whereas \cite{shavit2016automated} uses SMT to perform synthesis. 
 %
-Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
+A synthesis technique is also used in optimal synthesis of chemical reaction networks~\cite{cardelli2017syntax}.
 %

### 2019-09-24 papers/journal/problem.tex
Update on connectedness property

@@
   if there is a connectedness property that is satisfied by each valid VTS.
-\item{\em synthesis on incomplete VTS}:
-    Given an incomplete VTS, if we can predict missing parts.
+\item{\em Synthesis on incomplete VTS}:
+    given an incomplete VTS, if we can predict missing parts.
 \end{enumerate}
@@
 
-The implementation of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
+The implementation of the $k$-connectedness property is challenging as it requires reasoning about each combination of $k - 1$ edge removal. 
 %
-So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected.
+%The implementation of the k-connectedness property is challenging as it requires reasoning about every possible k − 1 edge removals.
 %
-Note that this check is sufficient as we are starting from smallest $k$ ($k = 1$) and subsequently incrementing it by one.     
+So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected, i.e., search for a $k$ edge removal that disconnects the graph.
+%
+Note that this suffices to find the exact $k$, as we are starting from the smallest value of $k$ and subsequently incrementing it by one.
+%Note that this suffice to find the correct $k$ as we are starting from smallest $k$ ($k = 1$) and subsequently increment it by one.     
 % Used E as edge and L_e L_n as label for node and the edge,

### 2019-09-24 papers/journal/model.tex
First Update for revision
Update on connectedness property

@@
 to be on the other side of the fusion.
+
 % $\pairs(M'')$ are not active in any other node.
@@
 %
+We use \textit{$e$ edge removal} for removing exactly $e$ present edges from the underlying graph.
+%
 We will check if a VTS $G$ is $k$-connected or not.
@@
 The property of $k$-connectedness is a robustness property that one
-expects from a biological systems.
+expects from biological systems.
 %
